### 2013-02-20 paper/Analisis.tex
new paper directory

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Template for a LaTex article in English.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{article}

%\usepackage[latin1]{inputenc}

\usepackage[english]{babel}
% AMS packages:
\usepackage{amsmath, amsthm, amsfonts, graphicx, float, caption, subfigure}

% Theorems
%-----------------------------------------------------------------
\newtheorem{thm}{Theorem}[section]
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\theoremstyle{remark}
\newtheorem{rem}[thm]{Remark}

% Shortcuts.
% One can define new commands to shorten frequently used
% constructions. As an example, this defines the R and Z used
% for the real and integer numbers.
%-----------------------------------------------------------------
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}

% Similarly, one can define commands that take arguments. In this
% example we define a command for the absolute value.
% -----------------------------------------------------------------
\newcommand{\abs}[1]{\left\vert#1\right\vert}

% Operators
% New operators must defined as such to have them typeset
% correctly. As an example we define the Jacobian:
% -----------------------------------------------------------------
\DeclareMathOperator{\Jac}{Jac}

%---------------------------------------------------------------

\begin{document}

\section*{Models}

We propose several models which include differents rotational velocities and optical depths. We also take into account the dust within the gas and two differents initial distributions of the photons, central and homogeneous. At the end we study 48 models, those are resumed in Table[1]\\
\\
\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|}
\hline
Velocity(km/s) & 50, 100, 200, 300\\
\hline
Optical Depth & $\tau = 10^{5},10^{6},10^{7}$\\
\hline
Photons Distributions & Central, Homogeneous\\
\hline
\end{tabular}
\caption{Models, If we take into account all these possibles combinations we get 24 models with dust and 24 without dust for a total of 48 models.}
\end{center}
\end{table}

We later study this models taking into account the posititon of the observer respect to the axis of rotation of the cloud.

\subsection*{Rotational Effect}

Due to the resonant nature of the lyman alpha line, gas kinematics play an important role in the shape of this line. In particular we study the case in which this gas is spherically symmetric and its rotating.\\

In cartesian coordinates the rotational velocity around de the z-axys is defined by:\\

\begin{subequations}
\begin{align}
    v_{x}=-\dfrac{y}{R}v \label{subeq1}\\
    v_{y}=\dfrac{x}{R}v \label{subeq2}
\end{align}
\end{subequations}
\\
Where $x$ and $y$ define de position of the gas atoms and dust particles. The minus sign in the x-component of the velocity is due to the direction of rotation, in this case we assume that as seeing from the top,the rotation is anticlockwise.\\

In Figure[1] the effect that rotation have in the spectra is shown, for both distributions central (Left) and homogeneous (right). This is a general case in the sense that is independent of the position of an external observer.

\begin{figure}[H]

  \centering

  \label{HOMandCentral}\caption{Shape of the lyman alpha line for differents velocities. The left panel show the central distribution while the right panel show the homogeneous distribution. }

  \begin{tabular}{cc}

    \includegraphics[width=60mm]{7tDifSpeedsZ.png}&

    \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\

  \end{tabular}

\end{figure}
Now if we take into account the position of the observer and compute this for differents angles of observation $\theta$ the outcoming spectra is modified as is shown in figure[2]. The main feature here is that as the angle increases the line high decreases. It means that a observer in the poles will observe a higher double peak than a observer in the ecuator. We will understand this in more details when we present the resaults of the scape fraction in section[].

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.45]{Observers.png}
\end{center}
\caption{Spectra for different observers. Model:$V=300km/s$, Optical Depth $\tau=10^{7}$ and Central Distribution without dust.}
\end{figure}

%describir los modelos, poner las ecuaciones de la velocidad de rotacion, %poner las graficas para un modelo dado poner el efecto de la rotación (poner %uno con velocidad cero) y del observador.

\section*{Resaults and Discussion}
\label{sec:Results_ly_Rotation}

%Ver correo de Jaime y tratar de explicar a que se deben estos efectos.

In the previous section we describe the models that we study the effect of rotation in the Lyman alpha line and see the effect of rotation in the specrtums. Now we show the main resaults that we obtain, in particual we pay spetial attention to the position of the maximums, the width of the line and the escape fraction in function of the rotational velocity and the angle of observation $\theta$.

\subsection*{Maximums Position}

\begin{figure}[H]

  \centering

  \label{figur}\caption{Width of the lyman-alpha line for all the models. }

  \begin{tabular}{cc}

    \includegraphics[width=40mm]{0maximum7t.png}&

    \includegraphics[width=40mm]{0maximum6t.png}

    \includegraphics[width=40mm]{0maximum5t.png}

   \end{tabular}

\end{figure}
(comparar con la grafica del apendice de clara con el eje x el optical depth y en el eje-y los maximos)

The maximus position gives information about the wave lenght of the mayority of the outcoming photons after they interact with the gas, in addition as a photon have more scatterings its wave lenght would be larger than the initial which is $1216$ {\AA}.
As we can see in Fig.[3] the position of the maximums does not change with rotational velocity. But it change from homogeneous and central.

\subsection*{Line Width}

%el ancho sirve para saber el rango de scattering que tienen los fotones.
Another effect that the rotation of the gas produce is in the  width of the lyman alpha line. The width of the line provide information of the the how many phtons scape with a particular wave lenght, in the ideal case in which all the photons scape with the same wave lenght the outcoming spectrum would be narrow. For all the models we study we found that as the rotational velocity increase as the line width increase this is show in Fig.[4].\\

\begin{figure}[H]

  \centering

  \label{figur}\caption{Width of the lyman-alpha line for all the models. }

  \begin{tabular}{cc}

    \includegraphics[width=60mm]{WidthCentral.png}&

    \includegraphics[width=60mm]{WidthHomogeneous.png}\\

    \includegraphics[width=60mm]{Width6.png}&

    \includegraphics[width=60mm]{Width6HOM.png}\\

    \includegraphics[width=60mm]{Width5.png}&

    \includegraphics[width=60mm]{Width5HOM.png}\\

  \end{tabular}

\end{figure}

We also found that the width for a particular model is not the same for differents angles of observation in particular as the angle increase the width also increase, it means that as the angle increase the number of scatterings of the photons increasse for this reason we see a broader line. Fig.[5]\\

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.45]{WidthvsTheta.png}
\caption{Width variation in function of theta}
\end{center}
\end{figure}

\subsection*{Escape Fraction}

The fraction of photons that escape from de cloud of gas and dust is defined as:\\

\begin{equation}
F_{e}=\dfrac{\Sigma_{NI} \vec{k}\cdot \vec{o}}{\Sigma_{NF}\vec{k}\cdot \vec{o}}
\end{equation}

Where NI is the initial number of photons and NF is the final. This escape fraction is computed for all the models which resaults are shown in Fig.[6]\\

\begin{figure}[H]

  \centering

  \label{figur}\caption{Escape fraction for all the models. Left panels show the central distribution, while right panels show the homogeneous distribution}

  \begin{tabular}{cc}

    \includegraphics[width=60mm]{FECentral5.png}&

    \includegraphics[width=60mm]{FEHOM5.png}\\

    \includegraphics[width=60mm]{FECentral6.png}&

    \includegraphics[width=60mm]{FEHOM6.png}\\

    \includegraphics[width=60mm]{FECentral7.png}&

    \includegraphics[width=60mm]{FEHOM7.png}\\

  \end{tabular}

\end{figure}

When the distribution is homogeneous the effect of velocity in the escape fraction is clear while in the central model the effect is not noterous.
The main effect is that the escape fraction increase as the velocity increase.

\section*{Observational effect.}

\section*{Tables}

Maximos\\

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline          
Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ 
\hline 
50 & -16.2695 & 16.23705 \\ 
\hline 
100 & -15.66496 & 15.33504 \\ 
\hline 
200 & -16.93149 & 14.56851 \\ 
\hline 
300 & -13.40048 & 16.09952 \\ 
\hline 
\end{tabular} 
\caption{Optical Depth $\tau= 10^{7}$, Central Distribution}
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity (Km/s) & Maximum 1 position & Maximum 2 position\\ 
\hline 
50 & -7.46286 & 6.53714 \\ 
\hline 
100 & -7.53357 & 6.96643 \\ 
\hline 
200 & -8.17453 & 7.32547 \\ 
\hline 
300 & -6.81487 & 6.18513 \\ 
\hline 
\end{tabular} 
\end{center}
\caption{Optical Depth $\tau = 10^{6}$, Central Distribution}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ 
\hline 
50 & -4.33708 & 3.66292 \\ 
\hline 
100 & -4.27326 & 3.72674 \\ 
\hline 
200 & -3.7737 & 3.7263   \\ 
\hline 
300 & -3.84903 & 4.15097 \\ 
\hline 
\end{tabular}
\caption{Optical Depth $\tau=10^{5}$, Central distribution} 
\end{center}
\end{table}

Line width\\

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
Velocity(Km/s) & FWHM & $\theta$\\ 
\hline 
50 & 12.62 & $0^{o}$ \\ 
\hline 
50 & 12.72 & $45^{o}$ \\ 
\hline 
50 & 12.93 & $90^{o}$ \\ 
\hline 
100 & 14.07 & $0^{o}$ \\ 
\hline
100 & 14.48 & $45^{o}$ \\ 
\hline 
100 & 15.00 & $90^{o}$ \\ 
\hline 
200 & 16.90 & $0^{o}$  \\ 
\hline 
200 & 18.51 & $45^{o}$ \\ 
\hline 
200 & 21.24 & $90^{o}$ \\ 
\hline 
300 & $24.69^{*}$ & $0^{o}$ \\ 
\hline 
300 & $25.79^{*}$ & $45^{o}$  \\ 
\hline  
300 & $27.73^{*}$ & $90^{o}$ \\ 
\hline  
\end{tabular}
\caption{Lines Widhts for a Central Distribution and $\tau=10^{7}$} 
\end{center}
\end{table}

Scape fracton\\

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ 
\hline 
Homogeneous & 50 & $0^{o}$& 13293.06 &49939.53\\ 
\hline 
Homogeneous & 50 & $45^{o}$& 13291.04 &50001.59\\ 
\hline 
Homogeneous & 50 & $90^{o}$ & 13348.76 &49922.73\\ 
\hline 
Homogeneous & 100 & $0^{o}$ & 15527.69 &50114.11\\ 
\hline
Homogeneous & 100 & $45^{o}$ & 15511.56 &49967.17\\ 
\hline
Homogeneous & 100 & $90^{o}$ & 15401.71 & 49833.65\\ 
\hline 
Homogeneous & 200 & $0^{o}$  & 17830.85 & 50078.69\\ 
\hline 
Homogeneous & 200 & $45^{o}$ & 17932.87 & 50064.42\\ 
\hline 
Homogeneous & 200 & $90^{o}$ & 17830.85  & 49931.748\\ 
\hline
Homogeneous & 300 & $ 0^{o}$ & 18687.33 & 50048.33 \\ 
\hline 
Homogeneous & 300 & $45^{o}$ & 18572.12& 49922.67\\ 
\hline  
Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ 
\hline  
\end{tabular}
\caption{Escape fraction for a Homogeneous Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}

\begin{table}[H]
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline 
Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\ 
\hline 
Central & 50 & $0^{o}$ & 4809.881 & 49917.069 \\ 
\hline 
Central & 50 & $45^{o}$ & 4829.21 & 49811.79 \\ 
\hline 
Central & 50 & $90^{o}$ & 4845.108 & 49853.039\\ 
\hline 
Central & 100 & $0^{o}$ & 4809.665 & 49921.30 \\  
\hline
Central & 100 & $45^{o}$ & 4828.65 & 49820.13 \\ 
\hline
Central & 100 & $90^{o}$ & 4846.45 & 49854.0 \\ 
\hline 
Central & 200 & $0^{o}$  & 4809.63 & 49917.64 \\ 
\hline 
Central & 200 & $45^{o}$ & 4829.25 & 49818.49 \\ 
\hline 
Central & 200 & $90^{o}$ & 4844.89 & 49856.66 \\ 
\hline 
Central & 300 & $ 0^{o}$ & 4810.56 & 49922.98\\ 
\hline 
Central & 300 & $45^{o}$ & 4831.16 & 49823.33\\ 
\hline  
Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ 
\hline  
\end{tabular}
\caption{Escape fraction for the central Distribution and optical depth $10^{5}$.} 
\end{center}
\end{table}

% Bibliography
%-----------------------------------------------------------------
%\begin{thebibliography}{99}

%\bibitem{Cd94} Author, \emph{Title}, Journal/Editor, (year)

%\end{thebibliography}

\end{document}

### 2013-02-20 paper/Analisis.tex
added line breaks

@@
 
-We propose several models which include differents rotational velocities and optical depths.
-We also take into account the dust within the gas and two differents initial distributions of the photons, central and homogeneous.
-At the end we study 48 models, those are resumed in Table[1]\\
+We propose several models which include differents rotational
+velocities and optical depths. We also take into account the dust
+within the gas and two differents initial distributions of the
+photons, central and homogeneous. At the end we study 48 models, those
+are resumed in Table[1]\\ 
 \\
@@
 \end{tabular}
-\caption{Models, If we take into account all these possibles combinations we get 24 models with dust and 24 without dust for a total of 48 models.}
+\caption{Models, If we take into account all these possibles
+  combinations we get 24 models with dust and 24 without dust for a
+  total of 48 models.} 
 \end{center}
@@
 
-We later study this models taking into account the posititon of the observer respect to the axis of rotation of the cloud.
+We later study this models taking into account the posititon of the
+observer respect to the axis of rotation of the cloud.
 
@@
 
-Due to the resonant nature of the lyman alpha line, gas kinematics play an important role in the shape of this line.
-In particular we study the case in which this gas is spherically symmetric and its rotating.\\
+Due to the resonant nature of the lyman alpha line, gas kinematics
+play an important role in the shape of this line. In particular we
+study the case in which this gas is spherically symmetric and its
+rotating.
 
-In cartesian coordinates the rotational velocity around de the z-axys is defined by:\\
+In cartesian coordinates the rotational velocity around de the z-axys
+is defined by:
 
@@
 \end{subequations}
-\\
-Where $x$ and $y$ define de position of the gas atoms and dust particles.
-The minus sign in the x-component of the velocity is due to the direction of rotation, in this case we assume that as seeing from the top,the rotation is anticlockwise.\\
 
-In Figure[1] the effect that rotation have in the spectra is shown, for both distributions central (Left) and homogeneous (right).
-This is a general case in the sense that is independent of the position of an external observer.
+Where $x$ and $y$ define de position of the gas atoms and dust
+particles. The minus sign in the x-component of the velocity is due to
+the direction of rotation, in this case we assume that as seeing from
+the top,the rotation is anticlockwise.
+
+In Figure[1] the effect that rotation have in the spectra is shown,
+for both distributions central (Left) and homogeneous (right). This is
+a general case in the sense that is independent of the position of an
+external observer.
 
@@
 
-  \label{HOMandCentral}\caption{Shape of the lyman alpha line for differents velocities. The left panel show the central distribution while the right panel show the homogeneous distribution. }
+  \label{HOMandCentral}\caption{Shape of the lyman alpha line for
+    differents velocities. The left panel show the central
+    distribution while the right panel show the homogeneous
+    distribution. }
 
   \begin{tabular}{cc}    
-
     \includegraphics[width=60mm]{7tDifSpeedsZ.png}&
-
     \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\
-
   \end{tabular}
@@
 \end{figure}
-Now if we take into account the position of the observer and compute this for differents angles of observation $\theta$ the outcoming spectra is modified as is shown in figure[2].
-The main feature here is that as the angle increases the line high decreases.
-It means that a observer in the poles will observe a higher double peak than a observer in the ecuator.
-We will understand this in more details when we present the resaults of the scape fraction in section[].
+Now if we take into account the position of the observer and compute
+this for differents angles of observation $\theta$ the outcoming
+spectra is modified as is shown in figure[2]. The main feature here is
+that as the angle increases the line high decreases. It means that a
+observer in the poles will observe a higher double peak than a
+observer in the ecuator. We will understand this in more details when
+we present the resaults of the scape fraction in section[].
 
@@
 
-%describir los modelos, poner las ecuaciones de la velocidad de rotacion, %poner las graficas para un modelo dado poner el efecto de la rotación (poner %uno con velocidad cero) y del observador.
+%describir los modelos, poner las ecuaciones de la velocidad de
+%rotacion, %poner las graficas para un modelo dado poner el efecto de
+%la rotación (poner %uno con velocidad cero) y del observador.
 
@@
 
-In the previous section we describe the models that we study the effect of rotation in the Lyman alpha line and see the effect of rotation in the specrtums.
-Now we show the main resaults that we obtain, in particual we pay spetial attention to the position of the maximums, the width of the line and the escape fraction in function of the rotational velocity and the angle of observation $\theta$.
+In the previous section we describe the models that we study the
+effect of rotation in the Lyman alpha line and see the effect of
+rotation in the specrtums. Now we show the main resaults that we
+obtain, in particual we pay spetial attention to the position of the
+maximums, the width of the line and the escape fraction in function of
+the rotational velocity and the angle of observation $\theta$.
 
@@
 %el ancho sirve para saber el rango de scattering que tienen los fotones.
-Another effect that the rotation of the gas produce is in the  width of the lyman alpha line.
-The width of the line provide information of the the how many phtons scape with a particular wave lenght, in the ideal case in which all the photons scape with the same wave lenght the outcoming spectrum would be narrow.
-For all the models we study we found that as the rotational velocity increase as the line width increase this is show in Fig.[4].\\
+Another effect that the rotation of the gas produce is in the  width
+of the lyman alpha line. The width of the line provide information of
+the the how many phtons scape with a particular wave lenght, in the
+ideal case in which all the photons scape with the same wave lenght
+the outcoming spectrum would be narrow. For all the models we study we
+found that as the rotational velocity increase as the line width
+increase this is show in Fig.[4].\\
 
@@
 
-We also found that the width for a particular model is not the same for differents angles of observation in particular as the angle increase the width also increase, it means that as the angle increase the number of scatterings of the photons increasse for this reason we see a broader line.
-Fig.[5]\\
+We also found that the width for a particular model is not the same
+for differents angles of observation in particular as the angle
+increase the width also increase, it means that as the angle increase
+the number of scatterings of the photons increasse for this reason we
+see a broader line. Fig.[5]\\
 
@@
 
-The fraction of photons that escape from de cloud of gas and dust is defined as:\\
+The fraction of photons that escape from de cloud of gas and dust is
+defined as:\\
 
@@
 
-Where NI is the initial number of photons and NF is the final. This escape fraction is computed for all the models which resaults are shown in Fig.[6]\\
+Where NI is the initial number of photons and NF is the final. This
+escape fraction is computed for all the models which resaults are
+shown in Fig.[6]\\
 
@@
 
-  \label{figur}\caption{Escape fraction for all the models. Left panels show the central distribution, while right panels show the homogeneous distribution}
+  \label{figur}\caption{Escape fraction for all the models. Left
+    panels show the central distribution, while right panels show the
+    homogeneous distribution}
 
@@
 
-When the distribution is homogeneous the effect of velocity in the escape fraction is clear while in the central model the effect is not noterous.
-The main effect is that the escape fraction increase as the velocity increase.
+When the distribution is homogeneous the effect of velocity in the
+escape fraction is clear while in the central model the effect is not
+noterous. 
+The main effect is that the escape fraction increase as the velocity
+increase.
 

### 2013-02-20 paper/Analisis.tex
added line breaks
paragraph editting

@@
 
-\section*{Models}
-
-We propose several models which include differents rotational
-velocities and optical depths. We also take into account the dust
-within the gas and two differents initial distributions of the
-photons, central and homogeneous. At the end we study 48 models, those
-are resumed in Table[1]\\ 
-\\
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-Velocity(km/s) & 50, 100, 200, 300\\
-\hline
-Optical Depth & $\tau = 10^{5},10^{6},10^{7}$\\
-\hline
-Photons Distributions & Central, Homogeneous\\
-\hline
-\end{tabular}
-\caption{Models, If we take into account all these possibles
-  combinations we get 24 models with dust and 24 without dust for a
-  total of 48 models.} 
-\end{center}
-\end{table}
-
-We later study this models taking into account the posititon of the
-observer respect to the axis of rotation of the cloud.
-
-\subsection*{Rotational Effect}
+\section{Introduction}
 
@@
 
-In cartesian coordinates the rotational velocity around de the z-axys
-is defined by:
+\section{Implementation of Rotation in CLARA}
+
+We implement into CLARA the simplest model whereby a sphere rotates
+with homogeneous angular velocity. We define a cartesian coordinate
+system with its origin at the center of the sphere and the rotation
+axis to be the $z$-axis, the velocity field in the gas can be written as
+
+%In cartesian coordinates the rotational velocity around de the z-axys
+%is defined by:
 
@@
 \begin{align}
-    v_{x}=-\dfrac{y}{R}v \label{subeq1}\\
-    v_{y}=\dfrac{x}{R}v \label{subeq2}
+    v_{x}=-\dfrac{y}{R}V_{\max} \label{subeq1}\\
+    v_{y}=\dfrac{x}{R}V_{\max} \label{subeq2}
 \end{align}
@@
 external observer.
+
+\section{Simulated Models in CLARA}
+\label{sec:models}
+
+%We propose several models which include differents rotational
+%velocities and optical depths. We also take into account the dust
+%within the gas and two differents initial distributions of the
+%photons, central and homogeneous. At the end we study 48 models, those
+%are resumed in Table[1]\\
+
+We compute the emergent Lyman-$\alpha$ line for several models with
+differents values for the maximal rotational velocity, hydrogend optical
+depth, dust optical depth and initial distributions of the photons
+with respect to the gas. There are in total 60 models with the input
+parameters summarized in Table  \ref{table:models}.
+
+% JF: digo que son 60 modelos porque estoy incluyendo los de velocidad cero.
+
+%We later study this models taking into account the posititon of the
+%observer respect to the axis of rotation of the cloud.
+
+Additionaly in the postprocessing process we will take into account
+different observer positions with respecto the cloud rotation
+axis.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{ccc}\hline
+Velocity (km s$^{-1}$) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
+Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
+Dust Optical Depth & $\tau_{A}$ & XXX \\
+Photons Distributions & & Central, Homogeneous\\
+\hline
+\end{tabular}
+\caption{
+Values for the varying input parameters in CLARA. Taking into account
+all the possible combinations for these models
+%odels, If we take into account all these possibles
+% combinations we get 24 models with dust and 24 without dust for a
+% total of 48 models 
+} 
+\label{table:models}
+\end{center}
+\end{table}
 
@@
 \end{center}
-\caption{Spectra for different observers. Model:$V=300km/s$, Optical Depth $\tau=10^{7}$ and Central Distribution without dust.}
+\caption{Spectra for different observers. Model:$V=300km/s$, Optical
+  Depth $\tau=10^{7}$ and Central Distribution without dust.} 
 \end{figure}
@@
 \end{figure}
-(comparar con la grafica del apendice de clara con el eje x el optical depth y en el eje-y los maximos)
+(comparar con la grafica del apendice de clara con el eje x el optical
+depth y en el eje-y los maximos)
 
-The maximus position gives information about the wave lenght of the mayority of the outcoming photons after they interact with the gas, in addition as a photon have more scatterings its wave lenght would be larger than the initial which is $1216$ {\AA}.
-As we can see in Fig.[3] the position of the maximums does not change with rotational velocity. But it change from homogeneous and central.
+The maximus position gives information about the wave lenght of the
+mayority of the outcoming photons after they interact with the gas, in
+addition as a photon have more scatterings its wave lenght would be
+larger than the initial which is $1216$ {\AA}. 
+As we can see in Fig.[3] the position of the maximums does not change
+with rotational velocity. But it change from homogeneous and central.
 

### 2013-02-20 paper/Analisis.tex
heavy reformatting

@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% Template for a LaTex article in English.
-%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[usenatbib]{mn2e} 
+\usepackage{amsmath} 
+\usepackage{amssymb} 
+\usepackage{graphics}
+\usepackage{graphicx}
+\usepackage{epsfig}  
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
 
-\documentclass{article}
+% To highlight comments 
+\usepackage{color}
+\definecolor{red}{rgb}{1,0.0,0.0}
+\newcommand{\red}{\color{red}}
+\definecolor{blue}{rgb}{0.1,0.3,0.9}
+\newcommand{\blue}{\color{blue}}
 
-%\usepackage[latin1]{inputenc}
+\usepackage[normalem]{ulem}
+\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
+\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
+\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
 
-\usepackage[english]{babel}
-% AMS packages:
-\usepackage{amsmath, amsthm, amsfonts, graphicx, float, caption, subfigure}
+\newcommand{\LCDM}{$\Lambda$CDM~}
+\newcommand{\beq}{\begin{eqnarray}}  
+\newcommand{\eeq}{\end{eqnarray}}  
+\newcommand{\zz}{$z\sim 3$} 
+\newcommand{\apj}{ApJ}  
+\newcommand{\apjs}{ApJS}  
+\newcommand{\apjl}{ApJL}  
+\newcommand{\aj}{AJ}  
+\newcommand{\mnras}{MNRAS}  
+\newcommand{\mnrassub}{MNRAS accepted}  
+\newcommand{\aap}{A\&A}  
+\newcommand{\aaps}{A\&AS}  
+\newcommand{\araa}{ARA\&A}  
+\newcommand{\nat}{Nature}  
+\newcommand{\physrep}{PhR}
+\newcommand{\pasp}{PASP}    
+\newcommand{\pasj}{PASJ}    
+\newcommand{\avg}[1]{\langle{#1}\rangle}  
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
+\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
+\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
+\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\lya}{{Lyman$\alpha$~}}
+\newcommand{\clara}{{\texttt{CLARA}}~}
+\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
+\newcommand{\hs}{{\hspace{1mm}}}
 
-% Theorems
-%-----------------------------------------------------------------
-\newtheorem{thm}{Theorem}[section]
-\newtheorem{cor}[thm]{Corollary}
-\newtheorem{lem}[thm]{Lemma}
-\newtheorem{prop}[thm]{Proposition}
-\theoremstyle{definition}
-\newtheorem{defn}[thm]{Definition}
-\theoremstyle{remark}
-\newtheorem{rem}[thm]{Remark}
+% definition to produce a "less than or similar to" symbol
+\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
 
-% Shortcuts.
-% One can define new commands to shorten frequently used
-% constructions. As an example, this defines the R and Z used
-% for the real and integer numbers.
-%-----------------------------------------------------------------
-\def\RR{\mathbb{R}}
-\def\ZZ{\mathbb{Z}}
-
-% Similarly, one can define commands that take arguments. In this
-% example we define a command for the absolute value.
-% -----------------------------------------------------------------
-\newcommand{\abs}[1]{\left\vert#1\right\vert}
-
-% Operators
-% New operators must defined as such to have them typeset
-% correctly. As an example we define the Jacobian:
-% -----------------------------------------------------------------
-\DeclareMathOperator{\Jac}{Jac}
-
-%---------------------------------------------------------------
+% definition to produce a "greater than or similar to" symbol
+\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
 
 \begin{document}
+
+\title[Rotation in the Lyman-$\alpha$ line]{Effects of bulk gas rotation on
+  the emergent Lyman-$\alpha$ line in distant galaxies}
+\author[N. Garavito and J.E. Forero-Romero]{
+\parbox[t]{\textwidth}{\raggedright 
+  Nicolas Garavito.$^{1}$ 
+  Jaime E. Forero-Romero$^{2}$ 
+}
+\vspace*{6pt}\\
+$^{1}$Uni A
+$^{2}$Uni B
+}
+\maketitle
+
+\begin{abstract}
+
+\end{abstract}
+\begin{keywords}
+galaxies: high-redshift - galaxies: star formation - line: formation
+\end{keywords}
 
@@
 
-\section{Implementation of Rotation in CLARA}
+\section{Implementation of Bulk Gas Rotation}
 
@@
 system with its origin at the center of the sphere and the rotation
-axis to be the $z$-axis, the velocity field in the gas can be written as
+axis to be the $z$-axis, the components in the bulk velocity field, $\vec{v}
+= v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{z}$. in the gas can be written as
 
@@
 \begin{align}
-    v_{x}=-\dfrac{y}{R}V_{\max} \label{subeq1}\\
-    v_{y}=\dfrac{x}{R}V_{\max} \label{subeq2}
+    v_{x}=-\dfrac{y}{R}V_{\rm max}, \label{subeq1}\\
+    v_{y}=\dfrac{x}{R}V_{\rm max}, \label{subeq2}\\
+    v_{z}=0, \label{subeq3}
 \end{align}
@@
 
-Where $x$ and $y$ define de position of the gas atoms and dust
-particles. The minus sign in the x-component of the velocity is due to
-the direction of rotation, in this case we assume that as seeing from
-the top,the rotation is anticlockwise.
+%Where $x$ and $y$ define de position of the gas atoms and dust
+%particles. 
+%The minus sign in the x-component of the velocity is due to
+%the direction of rotation, in this case we assume that as seeing from
+%the top,the rotation is anticlockwise.
+where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
+velocity at the sphere's surface. The minus sign in the x-component of the velocity is due to
+the direction of rotation, in this case we assume that the angular
+velocity vector goes in the $\hat{k}$ direction.
 
-In Figure[1] the effect that rotation have in the spectra is shown,
-for both distributions central (Left) and homogeneous (right). This is
-a general case in the sense that is independent of the position of an
-external observer.
-
-\section{Simulated Models in CLARA}
+\section{Grid of Simulated Models}
 \label{sec:models}
@@
 
-\begin{figure}[H]
-
-  \centering
-
-  \label{HOMandCentral}\caption{Shape of the lyman alpha line for
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{7tDifSpeedsZ.png}
+  \includegraphics[width=0.45\textwidth]{7tHOMDifSpeeds1.png}
+  \label{fig:HOMandCentral}\caption{Shape of the lyman alpha line for
     differents velocities. The left panel show the central
     distribution while the right panel show the homogeneous
-    distribution. }
+    distribution.}
+\end{figure*}
 
-  \begin{tabular}{cc}    
-    \includegraphics[width=60mm]{7tDifSpeedsZ.png}&
-    \includegraphics[width=60mm]{7tHOMDifSpeeds1.png}\\
-  \end{tabular}
-
-\end{figure}
 Now if we take into account the position of the observer and compute
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
@@
 
-\section*{Resaults and Discussion}
-\label{sec:Results_ly_Rotation}
+\section{Results}
+\label{sec:Results}
 
@@
 
-\subsection*{Maximums Position}
+In Figure[1] the effect that rotation have in the spectra is shown,
+for both distributions central (Left) and homogeneous (right). This is
+a general case in the sense that is independent of the position of an
+external observer.
 
-\begin{figure}[H]
+\subsection{Maximums Position}
 
-  \centering
-
-  \label{figur}\caption{Width of the lyman-alpha line for all the models. }
-
-  \begin{tabular}{cc}
-
-    \includegraphics[width=40mm]{0maximum7t.png}&
-
-    \includegraphics[width=40mm]{0maximum6t.png}
-
-    \includegraphics[width=40mm]{0maximum5t.png}
-
-   \end{tabular}
-
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{0maximum7t.png}
+    \includegraphics[width=0.45\textwidth]{0maximum6t.png}
+    \includegraphics[width=0.45\textwidth]{0maximum5t.png}
+  \label{figure:maxima}\caption{Width of the lyman-alpha line for all the models. }
 \end{figure}
@@
 
-\subsection*{Line Width}
+\subsection{Line Width}
 
@@
 
-\begin{figure}[H]
-
-  \centering
-
-  \label{figur}\caption{Width of the lyman-alpha line for all the models. }
-
-  \begin{tabular}{cc}
-
-    \includegraphics[width=60mm]{WidthCentral.png}&
-
-    \includegraphics[width=60mm]{WidthHomogeneous.png}\\
-
-    \includegraphics[width=60mm]{Width6.png}&
-
-    \includegraphics[width=60mm]{Width6HOM.png}\\
-
-    \includegraphics[width=60mm]{Width5.png}&
-
-    \includegraphics[width=60mm]{Width5HOM.png}\\
-
-  \end{tabular}
-
-\end{figure}
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
+    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
+    \includegraphics[width=0.45\textwidth]{Width6.png}
+    \includegraphics[width=0.45\textwidth]{Width6HOM.png}
+    \includegraphics[width=0.45\textwidth]{Width5.png}
+    \includegraphics[width=0.45\textwidth]{Width5HOM.png}
+  \label{figure:width}\caption{Width of the lyman-alpha line for all the models. }
+\end{figure*}
 
@@
 
-\begin{figure}[H]
+\begin{figure}
 \begin{center}
-\includegraphics[scale=0.45]{WidthvsTheta.png}
+\includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
 \caption{Width variation in function of theta}
@@
 
-\subsection*{Escape Fraction}
+\subsection{Escape Fraction}
 
@@
 
-\begin{figure}[H]
-
-  \centering
-
-  \label{figur}\caption{Escape fraction for all the models. Left
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{FECentral5.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
+  \includegraphics[width=0.45\textwidth]{FECentral6.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
+  \includegraphics[width=0.45\textwidth]{FECentral7.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
+  \label{figure:escape}\caption{Escape fraction for all the models. Left
     panels show the central distribution, while right panels show the
     homogeneous distribution} 
-
-  \begin{tabular}{cc}
-
-    \includegraphics[width=60mm]{FECentral5.png}&
-
-    \includegraphics[width=60mm]{FEHOM5.png}\\
-
-    \includegraphics[width=60mm]{FECentral6.png}&
-
-    \includegraphics[width=60mm]{FEHOM6.png}\\
-
-    \includegraphics[width=60mm]{FECentral7.png}&
-
-    \includegraphics[width=60mm]{FEHOM7.png}\\
-
-  \end{tabular}
-
-\end{figure}
+\end{figure*}
 
@@
 
-\section*{Observational effect.}
+\section{Discussion}
+\label{sec:discussion}
 
-\section*{Tables}
+\section{Observational implications}
 
-Maximos\\
+\section{Conclusions}
 
-\begin{table}[H]
+\section*{Acknowledgements}
+
+\section*{Appendix A: Tables}
+
+\begin{table}
 \begin{center}
-\begin{tabular}{|c|c|c|}
-\hline          
-Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ 
-\hline 
+\begin{tabular}{ccc}\hline          
+Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ \hline
 50 & -16.2695 & 16.23705 \\ 
-\hline 
 100 & -15.66496 & 15.33504 \\ 
-\hline 
 200 & -16.93149 & 14.56851 \\ 
-\hline 
-300 & -13.40048 & 16.09952 \\ 
-\hline 
+300 & -13.40048 & 16.09952 \\ \hline 
 \end{tabular} 
@@
 
-\begin{table}[H]
+\begin{table}
 \begin{center}
-\begin{tabular}{|c|c|c|}
-\hline 
-Velocity (Km/s) & Maximum 1 position & Maximum 2 position\\ 
-\hline 
+\begin{tabular}{ccc}\hline 
+Velocity (km/s) & Maximum 1 position & Maximum 2 position\\ \hline
 50 & -7.46286 & 6.53714 \\ 
-\hline 
 100 & -7.53357 & 6.96643 \\ 
-\hline 
 200 & -8.17453 & 7.32547 \\ 
-\hline 
-300 & -6.81487 & 6.18513 \\ 
-\hline 
+300 & -6.81487 & 6.18513 \\ \hline 
 \end{tabular} 
@@
 
-\begin{table}[H]
+\begin{table}
 \begin{center}
-\begin{tabular}{|c|c|c|}
-\hline 
-Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ 
-\hline 
+\begin{tabular}{ccc}\hline 
+Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ \hline
 50 & -4.33708 & 3.66292 \\ 
-\hline 
 100 & -4.27326 & 3.72674 \\ 
-\hline 
 200 & -3.7737 & 3.7263   \\ 
-\hline 
-300 & -3.84903 & 4.15097 \\ 
-\hline 
+300 & -3.84903 & 4.15097 \\ \hline 
 \end{tabular}
@@
 
-\begin{table}[H]
+\begin{table}
 \begin{center}
-\begin{tabular}{|c|c|c|}
-\hline 
-Velocity(Km/s) & FWHM & $\theta$\\ 
-\hline 
+\begin{tabular}{ccc}\hline 
+Velocity(Km/s) & FWHM & $\theta$\\ \hline 
 50 & 12.62 & $0^{o}$ \\ 
-\hline 
 50 & 12.72 & $45^{o}$ \\ 
-\hline 
 50 & 12.93 & $90^{o}$ \\ 
-\hline 
 100 & 14.07 & $0^{o}$ \\ 
-\hline
 100 & 14.48 & $45^{o}$ \\ 
-\hline 
 100 & 15.00 & $90^{o}$ \\ 
-\hline 
 200 & 16.90 & $0^{o}$  \\ 
-\hline 
 200 & 18.51 & $45^{o}$ \\ 
-\hline 
 200 & 21.24 & $90^{o}$ \\ 
-\hline 
 300 & $24.69^{*}$ & $0^{o}$ \\ 
-\hline 
 300 & $25.79^{*}$ & $45^{o}$  \\ 
-\hline  
-300 & $27.73^{*}$ & $90^{o}$ \\ 
-\hline  
+300 & $27.73^{*}$ & $90^{o}$ \\ \hline
 \end{tabular}
@@
 
-Scape fracton\\
+Escape fraction\\
 
@@
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline 
-Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ 
-\hline 
+\begin{tabular}{ccccc}\hline 
+Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ \hline 
 Homogeneous & 50 & $0^{o}$& 13293.06 &49939.53\\ 
-\hline 
 Homogeneous & 50 & $45^{o}$& 13291.04 &50001.59\\ 
-\hline 
 Homogeneous & 50 & $90^{o}$ & 13348.76 &49922.73\\ 
-\hline 
 Homogeneous & 100 & $0^{o}$ & 15527.69 &50114.11\\ 
-\hline
 Homogeneous & 100 & $45^{o}$ & 15511.56 &49967.17\\ 
-\hline
 Homogeneous & 100 & $90^{o}$ & 15401.71 & 49833.65\\ 
-\hline 
 Homogeneous & 200 & $0^{o}$  & 17830.85 & 50078.69\\ 
-\hline 
 Homogeneous & 200 & $45^{o}$ & 17932.87 & 50064.42\\ 
-\hline 
 Homogeneous & 200 & $90^{o}$ & 17830.85  & 49931.748\\ 
-\hline
 Homogeneous & 300 & $ 0^{o}$ & 18687.33 & 50048.33 \\ 
-\hline 
 Homogeneous & 300 & $45^{o}$ & 18572.12& 49922.67\\ 
-\hline  
-Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ 
-\hline  
+Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ \hline
 \end{tabular}
@@
 
-\begin{table}[H]
+\begin{table}
 \begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline 
-Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\ 
-\hline 
+\begin{tabular}{ccccc} \hline 
+Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\  \hline 
 Central & 50 & $0^{o}$ & 4809.881 & 49917.069 \\ 
-\hline 
 Central & 50 & $45^{o}$ & 4829.21 & 49811.79 \\ 
-\hline 
 Central & 50 & $90^{o}$ & 4845.108 & 49853.039\\ 
-\hline 
 Central & 100 & $0^{o}$ & 4809.665 & 49921.30 \\  
-\hline
 Central & 100 & $45^{o}$ & 4828.65 & 49820.13 \\ 
-\hline
 Central & 100 & $90^{o}$ & 4846.45 & 49854.0 \\ 
-\hline 
 Central & 200 & $0^{o}$  & 4809.63 & 49917.64 \\ 
-\hline 
 Central & 200 & $45^{o}$ & 4829.25 & 49818.49 \\ 
-\hline 
 Central & 200 & $90^{o}$ & 4844.89 & 49856.66 \\ 
-\hline 
 Central & 300 & $ 0^{o}$ & 4810.56 & 49922.98\\ 
-\hline 
 Central & 300 & $45^{o}$ & 4831.16 & 49823.33\\ 
-\hline  
-Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ 
-\hline  
+Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ \hline
 \end{tabular}

### 2013-02-22 paper/Analisis.tex
Version_0.2 More text, and Fixed Pictures

@@
 \usepackage{epsfig} 
+\usepackage{float} 
 \def\be{\begin{equation}}
@@
 \parbox[t]{\textwidth}{\raggedright 
-  Nicolas Garavito.$^{1}$ 
+  Nicolas Garavito-Camargo.$^{1}$ 
   Jaime E. Forero-Romero$^{2}$ 
@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 \section{Implementation of Bulk Gas Rotation}
+\label{sec:implementation}
 
@@
 axis to be the $z$-axis, the components in the bulk velocity field, $\vec{v}
-= v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{z}$. in the gas can be written as
+= v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{k}$. in the gas can be written as
 
@@
 Additionaly in the postprocessing process we will take into account
-different observer positions with respecto the cloud rotation
+different observer positions with respect to the cloud rotation
 axis.
@@
 all the possible combinations for these models
-%odels, If we take into account all these possibles
-% combinations we get 24 models with dust and 24 without dust for a
-% total of 48 models 
 } 
@@
 this for differents angles of observation $\theta$ the outcoming
-spectra is modified as is shown in figure[2]. The main feature here is
-that as the angle increases the line high decreases. It means that a
-observer in the poles will observe a higher double peak than a
-observer in the ecuator. We will understand this in more details when
-we present the resaults of the scape fraction in section[].
+spectra is modified as is shown in Figure~\ref{DifferentObservers}.
+The main feature here is that as the angle increases the line height decreases.
+It means that a observer in the poles will observe a higher double peak than a
+observer in the ecuator. We will understand this in more detail when
+we present the results of the scape fraction in section~\ref{sec:EF}.
 
@@
   Depth $\tau=10^{7}$ and Central Distribution without dust.} 
+  \label{DifferentObservers}
 \end{figure}
@@
 
-In the previous section we describe the models that we study the
-effect of rotation in the Lyman alpha line and see the effect of
-rotation in the specrtums. Now we show the main resaults that we
+In the previous section we describe the models that we use to study the
+effect of rotation in the Lyman alpha line for this we saw the outcoming specrtums including rotation. Now we show the main results that we
 obtain, in particual we pay spetial attention to the position of the
@@
 
-In Figure[1] the effect that rotation have in the spectra is shown,
+In Figure~\ref{fig:HOMandCentral} the effect that rotation have in the spectra is shown,
 for both distributions central (Left) and homogeneous (right). This is
@@
 
-\subsection{Maximums Position}
+\subsection{Maxima Positions}
+\label{sec:MP}
 
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{0maximum7t.png}
-    \includegraphics[width=0.45\textwidth]{0maximum6t.png}
-    \includegraphics[width=0.45\textwidth]{0maximum5t.png}
-  \label{figure:maxima}\caption{Width of the lyman-alpha line for all the models. }
+    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
+    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
+  \label{figure:maximavsOD}\caption{Position of the maxima in the outgoing spectra for differents Optical Depths, (up)Central Distriution, (Down) Homogeneous Distribution.}
 \end{figure}
-(comparar con la grafica del apendice de clara con el eje x el optical
-depth y en el eje-y los maximos)
 
-The maximus position gives information about the wave lenght of the
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODCentral.png}
+    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODHOM.png}
+  \label{figure:maximumsvsvelocities}\caption{Position of the maxima in the outgoing spectra for differents Rotational velocities, (up)Central Distriution, (Down) Homogeneous Distribution.}
+\end{figure}
+
+The maximums position gives information about the wave lenght of the
 mayority of the outcoming photons after they interact with the gas, in
@@
 larger than the initial which is $1216$ {\AA}. 
-As we can see in Fig.[3] the position of the maximums does not change
-with rotational velocity. But it change from homogeneous and central.
+As we can see in Figure ~\ref{figure:maximumsvsvelocities} the position of the maximums does not change with rotational velocity for the central dsitribution.
+On the other hand for the homogeneous distriution the maxima position $X_{m}$ change for $Log_{10}\tau=5$, this is because at higher rotational velocities photons escape with less scatterings, for $v=100\dfrac{km}{s}$ the majority of the photons still escape with scatterings but for $v=200\dfrac{km}{s}$ the number of photons that escape with a few or any scatterings is higher, this is why the maxima change to the center of the spectra.\\
+
+If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase (include reference of previous articles) the maxima position increase and this is a well known result, but when rotation is included the dependence is not linear.
+%(think a lit bit more on this, maybe make a regression)
+%explain the method to find the maxima position
 
 \subsection{Line Width}
+\label{sec:LW}
 
-%el ancho sirve para saber el rango de scattering que tienen los fotones.
 Another effect that the rotation of the gas produce is in the  width
 of the lyman alpha line. The width of the line provide information of
-the the how many phtons scape with a particular wave lenght, in the
+how many photons scape with a particular wave lenght, in the
 ideal case in which all the photons scape with the same wave lenght
-the outcoming spectrum would be narrow. For all the models we study we
-found that as the rotational velocity increase as the line width
+the outcoming spectrum would be narrower. For all the models we study we
+found that as the rotational velocity increase the line width
 increase this is show in Fig.[4].\\
@@
 \begin{figure*}
-    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
-    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
+    \includegraphics[width=0.45\textwidth]{Width7Central.png}
+    \includegraphics[width=0.45\textwidth]{Width7Homogeneous.png}
     \includegraphics[width=0.45\textwidth]{Width6.png}
@@
 \subsection{Escape Fraction}
+\label{sec:EF}
 
-The fraction of photons that escape from de cloud of gas and dust is
+The fraction of photons that escape from the cloud of gas and dust is
 defined as:\\
@@
 Where NI is the initial number of photons and NF is the final. This
-escape fraction is computed for all the models which resaults are
+escape fraction is computed for all the models which results are
 shown in Fig.[6]\\
@@
 escape fraction is clear while in the central model the effect is not
-noterous. 
+notorious. 
 The main effect is that the escape fraction increase as the velocity

### 2013-02-22 paper/Analisis.tex
more text and fits table

@@
 %explain the method to find the maxima position
-
-\subsection{Line Width}
+% Nscatt plots should give a hint about central maxima.
+\subsection{Line Equivalent Width}
 \label{sec:LW}
 
-Another effect that the rotation of the gas produce is in the  width
-of the lyman alpha line. The width of the line provide information of
+The width of the line provide information of
 how many photons scape with a particular wave lenght, in the
 ideal case in which all the photons scape with the same wave lenght
-the outcoming spectrum would be narrower. For all the models we study we
-found that as the rotational velocity increase the line width
-increase this is show in Fig.[4].\\
+the outcoming spectrum would be narrower. \\
+We found a dependency of the equivalent width with the rotation of the gas cloud for all the models we study, this is shown in Figure ~\ref{figure:width}.
+As velocity increase also the equivalent width increase, it means that some photons escape with fewer scatterings than the static case but at the same time some photons escape with more scatterings.\\
+
+% I dont understand this at all, hope Nscatts plot helps
 
@@
 
-We also found that the width for a particular model is not the same
-for differents angles of observation in particular as the angle
-increase the width also increase, it means that as the angle increase
-the number of scatterings of the photons increasse for this reason we
-see a broader line. Fig.[5]\\
+We also found that the equivalent width is not the same for differents angles of observation in particular as the angle increase the width also increase Figure ~\ref{fig:withvstheta}, this is related with the fact that photons escape easily (with less scatterings) in the $\hat{k}$ direction\\
+Following the convention of Verhamme et al 2012 we define $\mu=cos(\theta)$, we can make a polynomial fit the $EW(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
+%make comparison with Verhamme et al
 
-\begin{figure}
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifODHOM.png}
+    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifOD.png}
+    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeedsHOM.png}
+    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeeds.png}
+  \label{figure:widthvstheta}\caption{Width of the lyman-alpha line for all the models. }
+\end{figure*}
+
+% fix this table is too big
+\begin{table}
 \begin{center}
-\includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
-\caption{Width variation in function of theta}
+\begin{tabular}{cc}\hline
+Model & Fit\\
+Central, $\tau=10^5, V=200\dfrac{km}{s}$ &$EW(\mu)=-59-1677\mu-17864\mu^{2}+84509\mu^{3}-149877\mu^{4}$\\
+Central, $\tau=10^6, V=200\dfrac{km}{s}$ &$EW(\mu)=-1+53.8\mu-1080\mu^{2}+9644\mu^{3}-32264\mu^{4}$\\
+Central, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=0.011+0.9\mu-27\mu^{2}+359\mu^{3}-1791\mu^{4}$\\
+Hom, $\tau=10^5, V=200\dfrac{km}{s}$ & $EW(\mu)=11.66-187.22\mu-54.58\mu^{2}+12932.5\mu^{3}-51882.9\mu^{4}$ \\
+Hom, $\tau=10^6, V=200\dfrac{km}{s}$ & $EW(\mu)=-361.64+17158.92\mu-305268.4\mu^{2}+2413478\mu^{3}-7154649\mu^{4}$ \\
+Hom, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=-0.28+23.29\mu-721\mu^{2}+9912\mu^{3}-51074\mu^{4}$ \\
+\hline
+\end{tabular}
+\caption{Fits for EW models} 
+\label{table:fits}
 \end{center}
-\end{figure}
+\end{table}
 
@@
 \section{Observational implications}
+% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
 

### 2013-02-22 paper/Analisis.tex
new text edits, issues from this version were already posted

@@
 \newcommand{\hs}{{\hspace{1mm}}}  
+\newcommand{\kms}{\,km~s$^{-1}$}
 
@@
 
-\title[Rotation in the Lyman-$\alpha$ line]{Effects of bulk gas rotation on
-  the emergent Lyman-$\alpha$ line in distant galaxies}
+\title[Rotation in the Lyman-$\alpha$ line]{Effects of rotation on the
+  Lyman-$\alpha$ line morphology in distant galaxies}
 \author[N. Garavito and J.E. Forero-Romero]{
@@
 Due to the resonant nature of the lyman alpha line, gas kinematics
-play an important role in the shape of this line. In particular we
-study the case in which this gas is spherically symmetric and its
-rotating.
+play an important role shaping its morphology. In the literature there
+has been extensive studies of outflow/inflow configurations.
+
+In this paper we study for the first time the impact of rotation on
+the morphology of the Lyman $\alpha$ line. To isolate the effects of
+rotation we focus on a simple system: the gas distribution is
+spherical, with homogenous density and the gas rotates as a solid
+body.
+
+This paper is paper is structured as follows.
 
@@
 
-%In cartesian coordinates the rotational velocity around de the z-axys
-%is defined by:
-
 \begin{subequations}
@@
 
-%Where $x$ and $y$ define de position of the gas atoms and dust
-%particles. 
-%The minus sign in the x-component of the velocity is due to
-%the direction of rotation, in this case we assume that as seeing from
-%the top,the rotation is anticlockwise.
 where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
-velocity at the sphere's surface. The minus sign in the x-component of the velocity is due to
-the direction of rotation, in this case we assume that the angular
-velocity vector goes in the $\hat{k}$ direction.
+velocity at the sphere's surface. The minus sign in the x-component of
+the velocity indicates the direction of rotation, in this case we
+assume that the angular velocity vector goes in the $\hat{k}$
+direction.  The linear dependence of the velocity on the radial
+distance describes the case of constant angular velocity
+$\omega=V_{\rm max}/R$.
+
+We take the polar angle $\theta$ that a unitary vector makes with the
+rotation axis as defined by the dot product $\cos\theta =
+{\hat{u}\cdot\hat{k}}$. In the Section \ref{sec:results} we will
+present in detail how the line differs at different observing angles
+$\theta$.
 
@@
 \label{sec:models}
-
-%We propose several models which include differents rotational
-%velocities and optical depths. We also take into account the dust
-%within the gas and two differents initial distributions of the
-%photons, central and homogeneous. At the end we study 48 models, those
-%are resumed in Table[1]\\
 
@@
 
-% JF: digo que son 60 modelos porque estoy incluyendo los de velocidad cero.
-
-%We later study this models taking into account the posititon of the
-%observer respect to the axis of rotation of the cloud.
-
-Additionaly in the postprocessing process we will take into account
-different observer positions with respect to the cloud rotation
-axis.
-
 \begin{table}
@@
 \begin{tabular}{ccc}\hline
-Velocity (km s$^{-1}$) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
+Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
 Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
@@
 
+%poner las graficas para un modelo dado poner el efecto de
+%la rotación (poner %uno con velocidad cero) y del observador.
+
+\section{Results}
+\label{sec:results}
+
+The central result of this paper is summarized in Figure
+\ref{fig:HOMandCentral} where we show that rotation as a considerable
+effect on the morphology of the emergent Lyman-alpha line both in the
+case where the photons are emitted at the sphere's center and when
+they are initialized with an homogeneous distribution all over the
+gas volume.
+
+The results for this outgoing spectra are integrated over the whole
+sphere, meaning that all the escaping photons were taking into account
+regardless of the direction of the outgoing photons. Figure
+\ref{fig:Different Observers} shows how if one gives a weight to each outgoing
+photon according to its direction when escaping the gas distribution
+it is posible to detect notable differences in the spectrum for
+different viewing angles.
+
 \begin{figure*}
@@
   \label{fig:HOMandCentral}\caption{Shape of the lyman alpha line for
-    differents velocities. The left panel show the central
-    distribution while the right panel show the homogeneous
-    distribution.}
+    differents velocities. The left (right) panel shows the central
+    (homogeneous) photon distribution.}
 \end{figure*}
-
-Now if we take into account the position of the observer and compute
-this for differents angles of observation $\theta$ the outcoming
-spectra is modified as is shown in Figure~\ref{DifferentObservers}.
-The main feature here is that as the angle increases the line height decreases.
-It means that a observer in the poles will observe a higher double peak than a
-observer in the ecuator. We will understand this in more detail when
-we present the results of the scape fraction in section~\ref{sec:EF}.
 
@@
 \end{center}
-\caption{Spectra for different observers. Model:$V=300km/s$, Optical
+\caption{Spectra for different observers. Model:$V=300$\kms, Optical
   Depth $\tau=10^{7}$ and Central Distribution without dust.} 
-  \label{DifferentObservers}
+  \label{fig:DifferentObservers}
 \end{figure}
-
-%describir los modelos, poner las ecuaciones de la velocidad de
-%rotacion, %poner las graficas para un modelo dado poner el efecto de
-%la rotación (poner %uno con velocidad cero) y del observador.
-
-\section{Results}
-\label{sec:Results}
-
-%Ver correo de Jaime y tratar de explicar a que se deben estos efectos.
-
-In the previous section we describe the models that we use to study the
-effect of rotation in the Lyman alpha line for this we saw the outcoming specrtums including rotation. Now we show the main results that we
-obtain, in particual we pay spetial attention to the position of the
-maximums, the width of the line and the escape fraction in function of
-the rotational velocity and the angle of observation $\theta$.
-
-In Figure~\ref{fig:HOMandCentral} the effect that rotation have in the spectra is shown,
-for both distributions central (Left) and homogeneous (right). This is
-a general case in the sense that is independent of the position of an
-external observer.
 
@@
 larger than the initial which is $1216$ {\AA}. 
-As we can see in Figure ~\ref{figure:maximumsvsvelocities} the position of the maximums does not change with rotational velocity for the central dsitribution.
-On the other hand for the homogeneous distriution the maxima position $X_{m}$ change for $Log_{10}\tau=5$, this is because at higher rotational velocities photons escape with less scatterings, for $v=100\dfrac{km}{s}$ the majority of the photons still escape with scatterings but for $v=200\dfrac{km}{s}$ the number of photons that escape with a few or any scatterings is higher, this is why the maxima change to the center of the spectra.\\
+As we can see in Figure ~\ref{figure:maximumsvsvelocities} the
+position of the maxima does not change with rotational velocity for
+the central dsitribution. On the other hand for the homogeneous
+distriution the maxima position $X_{m}$ change for $Log_{10}\tau=5$,
+this is because at higher rotational velocities photons escape with
+less scatterings, for $v=100$\kms the majority of the photons
+still escape with scatterings but for $v=200$\kms the number
+of photons that escape with a few or any scatterings is higher, this
+is why the maxima change to the center of the spectra.\\
 
@@
 % fix this table is too big
-\begin{table}
+\begin{table*}
 \begin{center}
@@
 Model & Fit\\
-Central, $\tau=10^5, V=200\dfrac{km}{s}$ &$EW(\mu)=-59-1677\mu-17864\mu^{2}+84509\mu^{3}-149877\mu^{4}$\\
-Central, $\tau=10^6, V=200\dfrac{km}{s}$ &$EW(\mu)=-1+53.8\mu-1080\mu^{2}+9644\mu^{3}-32264\mu^{4}$\\
-Central, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=0.011+0.9\mu-27\mu^{2}+359\mu^{3}-1791\mu^{4}$\\
-Hom, $\tau=10^5, V=200\dfrac{km}{s}$ & $EW(\mu)=11.66-187.22\mu-54.58\mu^{2}+12932.5\mu^{3}-51882.9\mu^{4}$ \\
-Hom, $\tau=10^6, V=200\dfrac{km}{s}$ & $EW(\mu)=-361.64+17158.92\mu-305268.4\mu^{2}+2413478\mu^{3}-7154649\mu^{4}$ \\
-Hom, $\tau=10^7, V=200\dfrac{km}{s}$ & $EW(\mu)=-0.28+23.29\mu-721\mu^{2}+9912\mu^{3}-51074\mu^{4}$ \\
+Central, $\tau=10^5, V=200$\kms &$EW(\mu)=-59-1677\mu-17864\mu^{2}+84509\mu^{3}-149877\mu^{4}$\\
+Central, $\tau=10^6, V=200$\kms &$EW(\mu)=-1+53.8\mu-1080\mu^{2}+9644\mu^{3}-32264\mu^{4}$\\
+Central, $\tau=10^7, V=200$\kms & $EW(\mu)=0.011+0.9\mu-27\mu^{2}+359\mu^{3}-1791\mu^{4}$\\
+Hom, $\tau=10^5, V=200$\kms & $EW(\mu)=11.66-187.22\mu-54.58\mu^{2}+12932.5\mu^{3}-51882.9\mu^{4}$ \\
+Hom, $\tau=10^6, V=200$\kms & $EW(\mu)=-361.64+17158.92\mu-305268.4\mu^{2}+2413478\mu^{3}-7154649\mu^{4}$ \\
+Hom, $\tau=10^7, V=200$\kms & $EW(\mu)=-0.28+23.29\mu-721\mu^{2}+9912\mu^{3}-51074\mu^{4}$ \\
 \hline
@@
 \end{center}
-\end{table}
+\end{table*}
 
@@
 % taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
+
+... The results derived in this paper have consequences on the
+interpreation of galaxy observations in the Lyman alpha line.
 

### 2013-02-27 paper/Analisis.tex
version_0.4

@@
 The central result of this paper is summarized in Figure
-\ref{fig:HOMandCentral} where we show that rotation as a considerable
+~\ref{fig:HOMandCentral} where we show that rotation as a considerable
 effect on the morphology of the emergent Lyman-alpha line both in the
@@
 regardless of the direction of the outgoing photons. Figure
-\ref{fig:Different Observers} shows how if one gives a weight to each outgoing
+\ref{fig:DifferentObservers} shows how if one gives a weight to each outgoing
 photon according to its direction when escaping the gas distribution
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.45]{Observers.png}
-\end{center}
+\begin{figure*}
+\includegraphics[scale=0.45]{Observers7t.png}
+\includegraphics[scale=0.45]{Observers7tHOM.png}
 \caption{Spectra for different observers. Model:$V=300$\kms, Optical
@@
   \label{fig:DifferentObservers}
-\end{figure}
+\end{figure*}
 
-\subsection{Maxima Positions}
+\subsection{Maximums Position}
 \label{sec:MP}
@@
 
-The maximums position gives information about the wave lenght of the
-mayority of the outcoming photons after they interact with the gas, in
-addition as a photon have more scatterings its wave lenght would be
-larger than the initial which is $1216$ {\AA}. 
+Maximums position provides information about the wave length of the
+majority of the outgoing photons after they interact with the gas cloud, as a photon escapes with more scatterings its wave length would be
+farthest than the initial which is $1216$ {\AA}. 
 As we can see in Figure ~\ref{figure:maximumsvsvelocities} the
 position of the maxima does not change with rotational velocity for
-the central dsitribution. On the other hand for the homogeneous
-distriution the maxima position $X_{m}$ change for $Log_{10}\tau=5$,
+the central distribution while for the homogeneous
+distriution there is a variation in the maxima position $X_{m}$ for an optical depth $Log_{10}\tau=5$,
 this is because at higher rotational velocities photons escape with
-less scatterings, for $v=100$\kms the majority of the photons
-still escape with scatterings but for $v=200$\kms the number
-of photons that escape with a few or any scatterings is higher, this
-is why the maxima change to the center of the spectra.\\
+less scatterings (fig:ref), for $v=100$\kms the majority of the photons
+still escape with scatterings (double-peaked line) but for $v=200$\kms the number
+of photons that escape with a few or any scatterings is higher (single-peaked line), this
+is one of the main effects of rotation. \\
 
-If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase (include reference of previous articles) the maxima position increase and this is a well known result, but when rotation is included the dependence is not linear.
-%(think a lit bit more on this, maybe make a regression)
-%explain the method to find the maxima position
-% Nscatt plots should give a hint about central maxima.
-\subsection{Line Equivalent Width}
+If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase the maximum position increase and this is a well-known result (include references), we found that this result is not modified by rotation.\\
+
+Finally when we take into account the viewing angle Fig ~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on it, but again there is a threshold for the homogeneous distribution in which  the double peaked merged into a single peak but this time it is just the angle of viewing effect.
+
+% try a Nscatt plot as a function of theta
+%explain the method
+\subsection{Full Width at Half Maximum of the Lyman alpha line}
 \label{sec:LW}
 
-The width of the line provide information of
-how many photons scape with a particular wave lenght, in the
-ideal case in which all the photons scape with the same wave lenght
-the outcoming spectrum would be narrower. \\
-We found a dependency of the equivalent width with the rotation of the gas cloud for all the models we study, this is shown in Figure ~\ref{figure:width}.
-As velocity increase also the equivalent width increase, it means that some photons escape with fewer scatterings than the static case but at the same time some photons escape with more scatterings.\\
+The width of the line provide information about the range of the wave lengths of the outgoing photons, in the ideal case in which all the photons escape with the same wave length the outgoing spectrum would be the narrower, therefore as the number of scatterings increase the width increases too (reference).	\\
 
+We use the full width at half maximum (FWHM) in order to study the width of the line for all the models that we propose.
+We found a dependency of the width with the rotation velocity of the gas cloud, this results are summarize in Figure ~\ref{figure:width}.
+As velocity increase also the equivalent width increase (for both homogeneous and central distribution), it means that some photons escape with fewer scatterings than the static case but at the same time a few photons escape with more scatterings, this can be seen clearly in Figure.
+(Nscatt)\\
+
+We also found a dependency with the viewing angles, in particular as the angle increase the width also increase Figure ~\ref{fig:withvstheta}, this was also found in Verhemme et al.
+2012 for a rotating disk but the pure effect of rotation can not been study as it is in our case.
+Following the convention of Verhamme et al 2012 we define $\mu=cos(\theta)$, and we can make a polynomial fit for the $FWHM(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
+% explicar como se mide el ancho para algunos casos
 % I dont understand this at all, hope Nscatts plot helps 
+ %make comparison with Verhamme et al
 
@@
 \end{figure*}
-
-We also found that the equivalent width is not the same for differents angles of observation in particular as the angle increase the width also increase Figure ~\ref{fig:withvstheta}, this is related with the fact that photons escape easily (with less scatterings) in the $\hat{k}$ direction\\
-Following the convention of Verhamme et al 2012 we define $\mu=cos(\theta)$, we can make a polynomial fit the $EW(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
-%make comparison with Verhamme et al
 
@@
 Model & Fit\\
-Central, $\tau=10^5, V=200$\kms &$EW(\mu)=-59-1677\mu-17864\mu^{2}+84509\mu^{3}-149877\mu^{4}$\\
-Central, $\tau=10^6, V=200$\kms &$EW(\mu)=-1+53.8\mu-1080\mu^{2}+9644\mu^{3}-32264\mu^{4}$\\
-Central, $\tau=10^7, V=200$\kms & $EW(\mu)=0.011+0.9\mu-27\mu^{2}+359\mu^{3}-1791\mu^{4}$\\
-Hom, $\tau=10^5, V=200$\kms & $EW(\mu)=11.66-187.22\mu-54.58\mu^{2}+12932.5\mu^{3}-51882.9\mu^{4}$ \\
-Hom, $\tau=10^6, V=200$\kms & $EW(\mu)=-361.64+17158.92\mu-305268.4\mu^{2}+2413478\mu^{3}-7154649\mu^{4}$ \\
-Hom, $\tau=10^7, V=200$\kms & $EW(\mu)=-0.28+23.29\mu-721\mu^{2}+9912\mu^{3}-51074\mu^{4}$ \\
+Central, $\tau=10^5, V=200$\kms &$FWHM(\mu)=-149877+84509\mu-17864\mu^{2}-1677\mu^{3}-59\mu^{4}$\\
+Central, $\tau=10^6, V=200$\kms &$FWHM(\mu)=-32264+9644\mu-1080\mu^{2}+53.8\mu^{3}-\mu^{4}$\\
+Central, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-1791+359\mu-27\mu^{2}+0.9\mu^{3}+0.011\mu^{4}$\\
+Hom, $\tau=10^5, V=200$\kms & $FWHM(\mu)=-51882.9+12932.5\mu-54.58\mu^{2}-187.22\mu^{3}+11.66\mu^{4}$ \\
+Hom, $\tau=10^6, V=200$\kms & $FWHM(\mu)=-7154649+2413478\mu-305268.4\mu^{2}+17158.92\mu^{3}-361.64\mu^{4}$ \\
+Hom, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-51074+9912\mu-721\mu^{2}+23.29\mu^{3}-0.28\mu^{4}$ \\
 \hline
@@
 
-Where NI is the initial number of photons and NF is the final. This
-escape fraction is computed for all the models which results are
-shown in Fig.[6]\\
+Where NI is the initial number of photons and NF is the final, $\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer direction.
+With this definition we compute the escape fraction for all of our models, the results are shown in Fig ~\ref{figure:escape}\\
 
@@
 
-When the distribution is homogeneous the effect of velocity in the
-escape fraction is clear while in the central model the effect is not
-notorious. 
-The main effect is that the escape fraction increase as the velocity
-increase.
+We found that for the central distribution the escape fraction does not depend in velocity neither in the angle of observation, while it does in the optical depth, this result was already known from previous works (references).
+On the other hand for the homogeneous distribution we found that for higher velocities photons escape easily.
+The difference between this two results is due to the fact that in the homogeneous distribution photons are emitted closer to the escape surface and this makes this configuration more sensitive to rotation.
+This last argument also explain the fact that in the homogeneous distribution the optical depth does not affects the escape fraction .
 

### 2013-02-27 paper/Analisis.tex
heavy editting

@@
 Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
-Dust Optical Depth & $\tau_{A}$ & XXX \\
+Dust Optical Depth & $\tau_{A}$ & $0$,$1$\\
 Photons Distributions & & Central, Homogeneous\\
@@
 
-The central result of this paper is summarized in Figure
-~\ref{fig:HOMandCentral} where we show that rotation as a considerable
-effect on the morphology of the emergent Lyman-alpha line both in the
-case where the photons are emitted at the sphere's center and when
-they are initialized with an homogeneous distribution all over the
-gas volume.
+The central result of this paper is summarized in
+Fig.~\ref{fig:DifferentVelocities} where we show that rotation has a
+considerable effect on the morphology of the emergent Lyman-alpha line
+both in the case where the photons are emitted at the sphere's center
+and when they are initialized with an homogeneous distribution all
+over the gas volume.
 
-The results for this outgoing spectra are integrated over the whole
+The results for these outgoing spectra are integrated over the whole
 sphere, meaning that all the escaping photons were taking into account
@@
   \includegraphics[width=0.45\textwidth]{7tHOMDifSpeeds1.png}
-  \label{fig:HOMandCentral}\caption{Shape of the lyman alpha line for
+\caption{Shape of the lyman alpha line for
     differents velocities. The left (right) panel shows the central
-    (homogeneous) photon distribution.}
+    (homogeneous) photon distribution. All photons were taken into
+    account regardless of their outgoing direction of propagation.
+  \label{fig:differentvelocities}}
 \end{figure*}
@@
 \begin{figure*}
-\includegraphics[scale=0.45]{Observers7t.png}
-\includegraphics[scale=0.45]{Observers7tHOM.png}
-\caption{Spectra for different observers. Model:$V=300$\kms, Optical
-  Depth $\tau=10^{7}$ and Central Distribution without dust.} 
-  \label{fig:DifferentObservers}
+\includegraphics[width=0.45\textwidth]{Observers7t.png}
+\includegraphics[width=0.45\textwidth]{Observers7tHOM.png}
+\caption{Same as Figure \ref{fig:differentvelocities} but this time
+  the differen lines show the line morphology for different polar angles
+  $\theta$ with respect to the rotation axis. In this case each photon
+  has a weight dependent on their outgoing direction. All spectra correspond
+  to the same $V_{\rm max}=300$\kms, Optical   Depth $\tau=10^{7}$ and
+  Central Distribution without dust.}  
+  \label{fig:differentobservers}
 \end{figure*}
 
-\subsection{Maximums Position}
-\label{sec:MP}
+In the following subsections we quantify the trends observed in
+Fig. \ref{fig:differentvelocities} and
+Fig. \ref{fig:differentobservers} as a function of the maximum
+rotation velocity $V_{\rm max}$ and the position of the observer with
+respect to the rotation angle, $\mu = \cos{\theta}$. All the results
+in this section will be expressed in terms of frequencies expressed in
+velocities.
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
-    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
-  \label{figure:maximavsOD}\caption{Position of the maxima in the outgoing spectra for differents Optical Depths, (up)Central Distriution, (Down) Homogeneous Distribution.}
-\end{figure}
+Next, we  quantify the line by its full width at half maximum
+(FWHM) and the peak positions. In the next subsection we take a look
+at the escape fraction. We conclude the section by estimating the
+expected line flux for top hat filters at a fixed center and varying
+width.
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODCentral.png}
-    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODHOM.png}
-  \label{figure:maximumsvsvelocities}\caption{Position of the maxima in the outgoing spectra for differents Rotational velocities, (up)Central Distriution, (Down) Homogeneous Distribution.}
-\end{figure}
-
-Maximums position provides information about the wave length of the
-majority of the outgoing photons after they interact with the gas cloud, as a photon escapes with more scatterings its wave length would be
-farthest than the initial which is $1216$ {\AA}. 
-As we can see in Figure ~\ref{figure:maximumsvsvelocities} the
-position of the maxima does not change with rotational velocity for
-the central distribution while for the homogeneous
-distriution there is a variation in the maxima position $X_{m}$ for an optical depth $Log_{10}\tau=5$,
-this is because at higher rotational velocities photons escape with
-less scatterings (fig:ref), for $v=100$\kms the majority of the photons
-still escape with scatterings (double-peaked line) but for $v=200$\kms the number
-of photons that escape with a few or any scatterings is higher (single-peaked line), this
-is one of the main effects of rotation. \\
-
-If we now study the effect of the optical depth $\tau$ in the maxima position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the optical depth increase the maximum position increase and this is a well-known result (include references), we found that this result is not modified by rotation.\\
-
-Finally when we take into account the viewing angle Fig ~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on it, but again there is a threshold for the homogeneous distribution in which  the double peaked merged into a single peak but this time it is just the angle of viewing effect.
-
-% try a Nscatt plot as a function of theta
-%explain the method
-\subsection{Full Width at Half Maximum of the Lyman alpha line}
-\label{sec:LW}
-
-The width of the line provide information about the range of the wave lengths of the outgoing photons, in the ideal case in which all the photons escape with the same wave length the outgoing spectrum would be the narrower, therefore as the number of scatterings increase the width increases too (reference).	\\
-
-We use the full width at half maximum (FWHM) in order to study the width of the line for all the models that we propose.
-We found a dependency of the width with the rotation velocity of the gas cloud, this results are summarize in Figure ~\ref{figure:width}.
-As velocity increase also the equivalent width increase (for both homogeneous and central distribution), it means that some photons escape with fewer scatterings than the static case but at the same time a few photons escape with more scatterings, this can be seen clearly in Figure.
-(Nscatt)\\
-
-We also found a dependency with the viewing angles, in particular as the angle increase the width also increase Figure ~\ref{fig:withvstheta}, this was also found in Verhemme et al.
-2012 for a rotating disk but the pure effect of rotation can not been study as it is in our case.
-Following the convention of Verhamme et al 2012 we define $\mu=cos(\theta)$, and we can make a polynomial fit for the $FWHM(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
-% explicar como se mide el ancho para algunos casos
-% I dont understand this at all, hope Nscatts plot helps 
- %make comparison with Verhamme et al
+\subsection{Line width and peak maxima}
+\label{sec:widthpeak}
 
@@
     \includegraphics[width=0.45\textwidth]{Width5HOM.png}
-  \label{figure:width}\caption{Width of the lyman-alpha line for all the models. }
+\caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
 \end{figure*}
@@
     \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeeds.png}
-  \label{figure:widthvstheta}\caption{Width of the lyman-alpha line for all the models. }
+\caption{Width of the lyman-alpha line for all the models. 
+  \label{figure:widthvstheta}
+}
 \end{figure*}
 
+The first quantitative conclusion of the effect of rotation in the
+Lyman alpha line is that the double peaks in the line tend to broaden
+until they reach a single broad emission peak. This is most evident in
+the case of Lyman-alpha sources homogeneously distributed in the gas
+distributions (Fig. \ref{differentvelocities} right panel).
+
+To quantify the line broadening we measure a modified version of the full
+width at half maximum (FWHM) for half of the line, $W_{1/2}$. It means that in
+the case of double peaked emission, $W_{1/2}$ corresponds to the with
+one of thepeaks, while in the extreme case when the line is converted
+into a single peak, $W_{1/2}$ corresponds to half of the full width.
+
+This definition allows us to quantify the line width both in the cases
+of double and single peak emission. Furthermore it has the advantage
+that this line width should have a direct observational correspondence
+to the observed line feature once the Inter-Galactic Medium (IGM)
+effects are taken into account, which have the central effect of
+strongly reducing the intensity of the blue peak of the line.
+
+Figure~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
+as a function of $V_{\rm max}$. The line width increases with the
+rotational velocity of the gas cloud. This increase can be of a factor
+of $2-3$ with respect to the width with respect to the static
+case. This trend is conserved at all optical depths regardless of the
+initial source distribution.
+
+This result includes all the outgoing photons, regardless of the
+position of the observer. In Figure~\ref{fig:widthvstheta} we
+take into account the different positions of the observer in the
+measurement of the half-width $W_{1/2}$. From this we conclude
+that observers with a line of sight perpendicular to the axis of
+rotation (i.e. edge-on in the case of spiral galaxy) tend to meaure
+larger line widths than observers aligned with the rotation axis
+(i.e. face-on). The influence of the observer position on the line
+width, amounting always less than $15\%$ of a difference with respect
+to the result that takes into account all the outgoing photons with
+the same weight regardless of the relative observer position.
+
+%Both for central and homogeneous distribution of sources, We found a
+%dependency of the width with the rotation velocity of the gas cloud,
+%this results are summarize in Figure ~\ref{figure:width}. As velocity
+%increase also the equivalent width increase (for both homogeneous and
+%central distribution), it means that some photons escape with fewer
+%scatterings than the static case but at the same time a few photons escape with% more scatterings, this can be seen clearly in
+%Figure. (Nscatt)\\
+
+%We also found a dependency with the viewing angles, in particular as
+%the angle increase the width also increase Figure
+%~\ref{fig:withvstheta}, this was also found in Verhemme et al. 2012
+%for a rotating disk but the pure effect of rotation can not been study
+%as it is in our case. Following the convention of Verhamme et al 2012
+%we define $\mu=cos(\theta)$, and we can make a polynomial fit for the
+%$FWHM(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
+
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODCentral.png}
+    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODHOM.png}
+\caption{Position of the maxima
+    in the outgoing spectra for differents Rotational velocities,
+    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
+\end{figure*}
+
+The second feature in the line that we use to quantify the effect of
+rotation is the position of the line maxima. These provide information
+on the wavelength of the majority of the outgoing photons after
+they interact with the neutral hydrogen atoms in the gas cloud. If
+most of the photon escapes with a low number of scattering, its
+outgoing frequency will be close to its initial frequency, that is in
+the center of the line. On the contrary if the number of scatterings
+is large for the average photon, its outgoing frequency will be far
+from the line center. Such reasoning can be made more quantitative to
+understand the dependence of the peak maxima as a function of the
+hydrogen optical depth in the cloud [citation needed].
+
+In Figure ~\ref{figure:maximumsvsvelocities} we present the position
+of the maxima as a function of $V_{\rm max}$. For the photons emitted
+in the line center we do not find any variation in the position of the
+maxima in the range of explored parameter space. However in the
+homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
+that the double peak is converted into a single peak.
+
+This transition to a single peak line occurs for the systems where it
+becomes easiear for a bulk of the photons to escape with the lowest
+number of scatterings possible. This can explain how the single peak
+stage can be achieved in the homogeneous source distribution where
+there is fraction of the photons inside a photosphere region with
+$\tau_{H}\sim 1$ which allows them to escape within one
+scatter. Increasing the rotational velocity makes it easier for the
+photons in this photosphere region to escape.
+
+%rotational velocities photons escape with
+%less scatterings (fig:ref), for $v=100$\kms the majority of the photons
+%still escape with scatterings (double-peaked line) but for $v=200$\kms
+%the number of photons that escape with a few or any scatterings is higher
+%(single-peaked line), this is one of the main effects of rotation. \\
+
+If we now study the effect of the optical depth $\tau$ in the maxima
+position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the
+optical depth increase the maximum position increase and this is a
+well-known result (include references), we found that this result is
+not modified by rotation.\\
+
+Finally when we take into account the viewing angle Fig
+~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
+it, but again there is a threshold for the homogeneous distribution in
+which  the double peaked merged into a single peak but this time it is
+just the angle of viewing effect.
+
+% try a Nscatt plot as a function of theta
+%explain the method
+\subsection{Full Width at Half Maximum of the Lyman alpha line}
+\label{sec:LW}
+
+% explicar como se mide el ancho para algunos casos
+% I dont understand this at all, hope Nscatts plot helps 
+ %make comparison with Verhamme et al
+
+%\begin{figure}
+%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
+%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
+%  \label{fig:maximavsOD}\caption{Position of the maxima in the
+%    outgoing spectra for differents Optical Depths, (up)Central
+%    Distriution, (Down) Homogeneous Distribution.} 
+%\end{figure}
+
 % fix this table is too big
-\begin{table*}
-\begin{center}
-\begin{tabular}{cc}\hline
-Model & Fit\\
-Central, $\tau=10^5, V=200$\kms &$FWHM(\mu)=-149877+84509\mu-17864\mu^{2}-1677\mu^{3}-59\mu^{4}$\\
-Central, $\tau=10^6, V=200$\kms &$FWHM(\mu)=-32264+9644\mu-1080\mu^{2}+53.8\mu^{3}-\mu^{4}$\\
-Central, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-1791+359\mu-27\mu^{2}+0.9\mu^{3}+0.011\mu^{4}$\\
-Hom, $\tau=10^5, V=200$\kms & $FWHM(\mu)=-51882.9+12932.5\mu-54.58\mu^{2}-187.22\mu^{3}+11.66\mu^{4}$ \\
-Hom, $\tau=10^6, V=200$\kms & $FWHM(\mu)=-7154649+2413478\mu-305268.4\mu^{2}+17158.92\mu^{3}-361.64\mu^{4}$ \\
-Hom, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-51074+9912\mu-721\mu^{2}+23.29\mu^{3}-0.28\mu^{4}$ \\
-\hline
-\end{tabular}
-\caption{Fits for EW models} 
-\label{table:fits}
-\end{center}
-\end{table*}
+%\begin{table*}
+%\begin{center}
+%\begin{tabular}{cc}\hline
+%Model & Fit\\
+%Central, $\tau=10^5, V=200$\kms &$FWHM(\mu)=-149877+84509\mu-17864\mu^{2}-1677\mu^{3}-59\mu^{4}$\\
+%Central, $\tau=10^6, V=200$\kms &$FWHM(\mu)=-32264+9644\mu-1080\mu^{2}+53.8\mu^{3}-\mu^{4}$\\
+%Central, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-1791+359\mu-27\mu^{2}+0.9\mu^{3}+0.011\mu^{4}$\\
+%Hom, $\tau=10^5, V=200$\kms & $FWHM(\mu)=-51882.9+12932.5\mu-54.58\mu^{2}-187.22\mu^{3}+11.66\mu^{4}$ \\
+%Hom, $\tau=10^6, V=200$\kms & $FWHM(\mu)=-7154649+2413478\mu-305268.4\mu^{2}+17158.92\mu^{3}-361.64\mu^{4}$ \\
+%Hom, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-51074+9912\mu-721\mu^{2}+23.29\mu^{3}-0.28\mu^{4}$ \\
+%\hline
+%\end{tabular}
+%\caption{Fits for EW models} 
+%\label{table:fits}
+%\end{center}
+%\end{table*}
 

### 2013-02-27 paper/Analisis.tex
minor edits

@@
 
-Next, we  quantify the line by its full width at half maximum
-(FWHM) and the peak positions. In the next subsection we take a look
-at the escape fraction. We conclude the section by estimating the
+First we quantify the line by its full width at half maximum
+(FWHM) and the peak positions. In order to interpret these results we
+measure how the rotation affects the average number of scatterings
+for each Lyman-alpha photon in the simulation. This help us to
+introduce the next subsection on the escape fraction in our models
+including dust. We conclude the section by estimating the
 expected line flux for top hat filters at a fixed center and varying
@@
 
+%\begin{figure}
+%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
+%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
+%  \label{fig:maximavsOD}\caption{Position of the maxima in the
+%    outgoing spectra for differents Optical Depths, (up)Central
+%    Distriution, (Down) Homogeneous Distribution.} 
+%\end{figure}
+
 The second feature in the line that we use to quantify the effect of
@@
 
-In Figure ~\ref{figure:maximumsvsvelocities} we present the position
+In Figure ~\ref{fig:maximavsvelocity} we present the position
 of the maxima as a function of $V_{\rm max}$. For the photons emitted
@@
 
+In Figure ~\ref{fig:maximavsangle} we present the position of the
+maxima as a function of the viewing angle $\mu$ for all the optical
+depths and rotational velocities and the two different photon
+distributions [FALTA LA GRAFICA].
+
+%Finally when we take into account the viewing angle Fig
+%~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
+%it, but again there is a threshold for the homogeneous distribution in
+%which  the double peaked merged into a single peak but this time it is
+%just the angle of viewing effect.
+
 %rotational velocities photons escape with
@@
 
-If we now study the effect of the optical depth $\tau$ in the maxima
-position $X_{m}$ Figure~\ref{figure:maximavsOD}, we found that as the
-optical depth increase the maximum position increase and this is a
-well-known result (include references), we found that this result is
-not modified by rotation.\\
-
-Finally when we take into account the viewing angle Fig
-~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
-it, but again there is a threshold for the homogeneous distribution in
-which  the double peaked merged into a single peak but this time it is
-just the angle of viewing effect.
-
 % try a Nscatt plot as a function of theta
 %explain the method
-\subsection{Full Width at Half Maximum of the Lyman alpha line}
-\label{sec:LW}
 
@@
 
-%\begin{figure}
-%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
-%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
-%  \label{fig:maximavsOD}\caption{Position of the maxima in the
-%    outgoing spectra for differents Optical Depths, (up)Central
-%    Distriution, (Down) Homogeneous Distribution.} 
-%\end{figure}
+Finally we also report on the effect of the neutral Hydrogen
+optical depth $\tau_{H}$ on the maxima position $x_{m}$
+Figure~\ref{figure:maximavsOD}. We find that, at fixed
+rotation velocity, the position of the maxima increases with optical
+depth as expected from basic theoretical consideraions. We compare
+our results with the expected theoretical escaling for an infinnite
+slab.
+
+\subsection{Average Number of Scatterings}
+
+\subsection{Escape Fraction}
+\label{sec:EF}
+
+We have seen in the previous section that rotation affects the number
+of scatterings that
+
+The fraction of photons that escape from the cloud of gas and dust is
+defined as:\\
+
+\begin{equation}
+F_{e}=\dfrac{\Sigma_{NI} \vec{k}\cdot \vec{o}}{\Sigma_{NF}\vec{k}\cdot \vec{o}}
+\end{equation}
+
+Where NI is the initial number of photons and NF is the final,
+$\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer
+direction. With this definition we compute the escape fraction for all
+of our models, the results are shown in Fig ~\ref{figure:escape}\\
+
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{FECentral5.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
+  \includegraphics[width=0.45\textwidth]{FECentral6.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
+  \includegraphics[width=0.45\textwidth]{FECentral7.png}
+  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
+  \label{figure:escape}\caption{Escape fraction for all the models. Left
+    panels show the central distribution, while right panels show the
+    homogeneous distribution} 
+\end{figure*}
+
+We found that for the central distribution the escape fraction does
+not depend in velocity neither in the angle of observation, while it
+does in the optical depth, this result was already known from previous
+works (references). On the other hand for the homogeneous distribution
+we found that for higher velocities photons escape easily. The
+difference between this two results is due to the fact that in the
+homogeneous distribution photons are emitted closer to the escape
+surface and this makes this configuration more sensitive to
+rotation. This last argument also explain the fact that in the
+homogeneous distribution the optical depth does not affects the escape
+fraction .
+
+\subsection{Integrated flux}
+
+\section{Discussion}
+\label{sec:discussion}
+
+\section{Observational implications}
+% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
+
+... The results derived in this paper have consequences on the
+interpreation of galaxy observations in the Lyman alpha line.
+
+\section{Conclusions}
+
+\section*{Acknowledgements}
+
+\section*{Appendix A: Tables}
+
+\end{document}
 
@@
 %\end{table*}
-
-\subsection{Escape Fraction}
-\label{sec:EF}
-
-The fraction of photons that escape from the cloud of gas and dust is
-defined as:\\
-
-\begin{equation}
-F_{e}=\dfrac{\Sigma_{NI} \vec{k}\cdot \vec{o}}{\Sigma_{NF}\vec{k}\cdot \vec{o}}
-\end{equation}
-
-Where NI is the initial number of photons and NF is the final, $\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer direction.
-With this definition we compute the escape fraction for all of our models, the results are shown in Fig ~\ref{figure:escape}\\
-
-\begin{figure*}
-  \includegraphics[width=0.45\textwidth]{FECentral5.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
-  \includegraphics[width=0.45\textwidth]{FECentral6.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
-  \includegraphics[width=0.45\textwidth]{FECentral7.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
-  \label{figure:escape}\caption{Escape fraction for all the models. Left
-    panels show the central distribution, while right panels show the
-    homogeneous distribution} 
-\end{figure*}
-
-We found that for the central distribution the escape fraction does not depend in velocity neither in the angle of observation, while it does in the optical depth, this result was already known from previous works (references).
-On the other hand for the homogeneous distribution we found that for higher velocities photons escape easily.
-The difference between this two results is due to the fact that in the homogeneous distribution photons are emitted closer to the escape surface and this makes this configuration more sensitive to rotation.
-This last argument also explain the fact that in the homogeneous distribution the optical depth does not affects the escape fraction .
-
-\section{Discussion}
-\label{sec:discussion}
-
-\section{Observational implications}
-% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
-
-... The results derived in this paper have consequences on the
-interpreation of galaxy observations in the Lyman alpha line.
-
-\section{Conclusions}
-
-\section*{Acknowledgements}
-
-\section*{Appendix A: Tables}
 
@@
 %\end{thebibliography}
-
-\end{document}

### 2013-03-11 paper/Analisis.tex
minor change
Mejoras de algunas graficas
a little modification
plots Xm vs costheta
follow-up idea

@@
 respect to the rotation angle, $\mu = \cos{\theta}$. All the results
-in this section will be expressed in terms of frequencies expressed in
-velocities.
+in this section will be expressed in terms of resframe wavelength.
 
@@
 
+%ideas:
+Keep in mind making a follow up paper on the results of Yamada et atl http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line morphology at z=3.1.
+How many of these laes can be considered to have rotation features?
+In principle, all of then should have them.
+How to make the case convincing in the statistical sense?
+
 % Bibliography

### 2013-03-26 Analisis.tex
More text  in Escape Fraction

--- 2013-03-11 paper/Analisis.tex
@@
 \vspace*{6pt}\\
-$^{1}$Uni A
+$^{1}$Universidad de los Andes
 $^{2}$Uni B
@@
 \begin{figure*}
-    \includegraphics[width=0.45\textwidth]{Width7Central.png}
-    \includegraphics[width=0.45\textwidth]{Width7Homogeneous.png}
-    \includegraphics[width=0.45\textwidth]{Width6.png}
-    \includegraphics[width=0.45\textwidth]{Width6HOM.png}
-    \includegraphics[width=0.45\textwidth]{Width5.png}
-    \includegraphics[width=0.45\textwidth]{Width5HOM.png}
+    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
+    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
    \caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
@@
 
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
+    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
+\caption{Position of the maxima
+    in the outgoing spectra for differents Rotational velocities,
+    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
+\end{figure*}
+
 %\begin{figure}
@@
 
+as we think Nscatt is related with the double peacked line and maxima positions
+
+\begin{figure*}[ht]
+    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
+    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
+\caption{Nscatt\label{fig:Nscatt}} 
+\end{figure*}
+
 \subsection{Escape Fraction}
@@
 We have seen in the previous section that rotation affects the number
-of scatterings that
+of scatterings that ..\\
 
-The fraction of photons that escape from the cloud of gas and dust is
-defined as:\\
+Of particular interest is to compute the escape fraction of Lyman $\alpha$ photons coming from the most distant galaxies, due to the fact that with the observed intensity of the lyman alpha line quantities as the LF and SFR can be derived (put some references).
+\\
+
+Previous studies have shown the correlation of the Escape fraction with galctic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust.
+In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass.
+We compute the escape fraction for the models described in Table \ref{table:models}.\\
+
+For a realistic model we also take into account the viewing angle, first we fixed the viewing angle at $\theta = 0$  Fig.
+and then we fixed the velocity in order to see the escape fraction correlation with the viewing angle.
+Therefore we define the escape fraction as:\\
 
@@
 direction. With this definition we compute the escape fraction for all
-of our models, the results are shown in Fig ~\ref{figure:escape}\\
+of our models, the results are shown in Fig \ref{figure:escape}\\
 
 \begin{figure*}
-  \includegraphics[width=0.45\textwidth]{FECentral5.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
-  \includegraphics[width=0.45\textwidth]{FECentral6.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
-  \includegraphics[width=0.45\textwidth]{FECentral7.png}
-  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
-  \label{figure:escape}\caption{Escape fraction for all the models. Left
+  \includegraphics[width=0.45\textwidth]{FECENTRAL.png}
+  \includegraphics[width=0.45\textwidth]{FEHOMOGENEOUS.png}
+   \label{figure:efvsv}\caption{Escape fraction for all the models. Left
     panels show the central distribution, while right panels show the
@@
 
-We found that for the central distribution the escape fraction does
-not depend in velocity neither in the angle of observation, while it
-does in the optical depth, this result was already known from previous
-works (references). On the other hand for the homogeneous distribution
+In Figure \ref{figure:efvsv} we found that in the central distribution the escape fraction does not change with velocity while it
+does in the optical depth. On the other hand for the homogeneous distribution
 we found that for higher velocities photons escape easily. The
-difference between this two results is due to the fact that in the
+difference between this two results relly in the fact that in the
 homogeneous distribution photons are emitted closer to the escape
 surface and this makes this configuration more sensitive to
-rotation. This last argument also explain the fact that in the
-homogeneous distribution the optical depth does not affects the escape
-fraction .
+rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation.
+
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
+ \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
+\end{figure*}
 

### 2013-04-11 paper/Analisis.tex
afiliacion

@@
 \begin{abstract}
+Rotation is present in the gas kinematics of galaxies up to the
+highest redshifts. In this paper we present for the first time
+radiative transfer calculations that show the impact of rotation on
+the morphology of the Lyman $\alpha$ line. To this end we construct
+simplified models where a galaxy is modeled as an homogeneous sphere
+composed as an homogenous mixture of dust and hydrogen at a constant
+temperature. These spheres have an solid-body rotation with linear
+velocities at the surface in the range $0-300$ \kms. We consider
+radiation sources both in the center of the rotating cloud and also
+homogeneously distributed around the sphere. We find that higher
+rotational velocities increase the width of each peak in the outgoing
+line profile while it also increases the amount of Lyman alpha photons
+escaping in the line center. This trends makes that for high
+rotational velocities and large Hydrogen optical depths the double
+peak of the line tends to be erased an be replaced by a single peak the
+lines center. This is more pronounced for radiation sources
+homogeneously distributed. Concerning the escape fraction we find that
+rotation does not have any effect, provided that all the sources are
+centrally emitted. However in the case of homogeneously emitted
+sources we measure an increase of about a factor of $2$ in the escape
+fraction for higher rotational velocity vealues.
+
+Our work shows clearly that gas rotation has a non
+negligeable impact on the shape of the Lyman $\alpha$ line.
 

### 2013-04-19 paper/Analisis.tex
New Histograms
Some Comments about the averga number of scatterings

@@
 
-as we think Nscatt is related with the double peacked line and maxima positions
+Untill know we have focus in how rotation affect the morphology of the lyman alpha line, now we turn to study deeply the posible causes of this effects.
+As recombination is the main cause of the lyman alpha, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelenght.
+\\
+
+As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}.
+For the central distribution the number of scattering does not change with $V_{max}$ , this implies that..., For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation..
+
+In order to understand the double peack we make a histogram..
+
+as we think Nscatt is related with the double peacked line and maxima positions.
 
@@
 \caption{Nscatt\label{fig:Nscatt}} 
+\end{figure*}
+
+\begin{figure*}[ht]
+    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
+    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
+\caption{Nscatt\label{fig:NscattHisto}} 
 \end{figure*}

### 2013-04-29 paper/Analisis.tex
FEHOMOGENEOUS plot upgrade + a bit more of text
added references and first paragraph in the conclusions

@@
 \def\ea{\end{eqnarray}}
-
+\bibliographystyle{mn2e}
 % To highlight comments 
@@
 
-\title[Rotation in the Lyman-$\alpha$ line]{Effects of rotation on the
+\title[Rotation in the Lyman-$\alpha$ line]{Rotation effects on the
   Lyman-$\alpha$ line morphology in distant galaxies}
@@
 \parbox[t]{\textwidth}{\raggedright 
-  Nicolas Garavito-Camargo.$^{1}$ 
-  Jaime E. Forero-Romero$^{2}$ 
+  Nicolas Garavito-Camargo$^{1}$,
+  Jaime E. Forero-Romero$^{1}$ 
 }
 \vspace*{6pt}\\
-$^{1}$Universidad de los Andes
-$^{2}$Uni B
+$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
 }
@@
 spherical, with homogenous density and the gas rotates as a solid
-body.
+body. We base our work on the Monte Carlo base radiative transfer code
+CLARA \citep{CLARA}.
 
@@
 
-In Figure \ref{figure:efvsv} we found that in the central distribution the escape fraction does not change with velocity while it
-does in the optical depth. On the other hand for the homogeneous distribution
-we found that for higher velocities photons escape easily. The
-difference between this two results relly in the fact that in the
-homogeneous distribution photons are emitted closer to the escape
-surface and this makes this configuration more sensitive to
-rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation.
+In Figure \ref{figure:efvsv} we found that in the central distribution
+the escape fraction does not change with velocity while it does in the
+optical depth. On the other hand for the homogeneous distribution we
+found that for higher velocities photons escape easily. The difference
+between this two results relly in the fact that in the homogeneous
+distribution photons are emitted closer to the escape surface and this
+makes this configuration more sensitive to rotation while in the
+central configuration the escape fraction depends mainly in the amount
+of gas rather than in rotation.
+
+Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot)
 
@@
 
-\subsection{Integrated flux}
+\subsection{Integrated flux in a narrow band filter}
 
@@
 
-\section{Observational implications}
-% taking into account equivalent widths results with narrow band filters we can make a criterium in order to select wich galaxie could be seen in actual observations.
+... Comparison with Verhamme et al. results on the rotation
 
@@
 interpreation of galaxy observations in the Lyman alpha line.
+% taking into account equivalent widths results with narrow band
+% filters we can make a criterium in order to select wich galaxie
+% could be seen in actual observations.
 
 \section{Conclusions}
+In this paper we have estimated the effects of gas bulk rotation on
+the emission  of the Lyman $\alpha$ line. We based the study on the
+study of a simplified configuration of an homogeneous sphere rotating
+as a solid body. We explored  a range of models by varying the
+rotation speed, hydrogen optical depth, dust optical depth and initial
+distribution of Lyman$\alpha$ photons with respect to the gas
+density. This was implemented in CLARA, a Monte-Carlo
+radiative transfer code already used to study the Lyman $\alpha$
+line.
 
 \section*{Acknowledgements}
+
+\bibliography{references}
 
@@
 How to make the case convincing in the statistical sense?
-
-% Bibliography
-%-----------------------------------------------------------------
-%\begin{thebibliography}{99}
-
-%\bibitem{Cd94} Author, \emph{Title}, Journal/Editor, (year)
-
-%\end{thebibliography}

### 2013-04-29 paper/Analisis.tex
small changes

--- 2013-04-19 paper/Analisis.tex
@@
 \begin{figure*}
-    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifODHOM.png}
-    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifOD.png}
-    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeedsHOM.png}
-    \includegraphics[width=0.45\textwidth]{WidthvsThetaDifSpeeds.png}
+    \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
+    \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
     \caption{Width of the lyman-alpha line for all the models. 
@@
 the case of double peaked emission, $W_{1/2}$ corresponds to the with
-one of thepeaks, while in the extreme case when the line is converted
+one of the peaks, while in the extreme case when the line is converted
 into a single peak, $W_{1/2}$ corresponds to half of the full width.
@@
 surface and this makes this configuration more sensitive to
-rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation.
+rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation. \\
+
+Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot) \\
 

### 2013-04-29 paper/Analisis.tex

--- 2013-04-29 paper/Analisis.tex
@@
 As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}.
-For the central distribution the number of scattering does not change with $V_{max}$ , this implies that..., For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation..
+For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution.
+it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.
 
-In order to understand the double peack we make a histogram..
+In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$
 
@@
 
-\begin{figure*}[ht]
+\begin{figure*}
     \includegraphics[width=0.45\textwidth]{NscattCentral.png}
@@
 
-\begin{figure*}[ht]
+\begin{figure*}
     \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
-\caption{Nscatt\label{fig:NscattHisto}} 
+\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
+\end{figure*}
+
+\begin{figure*}
+    \includegraphics[width=0.45\textwidth]{2dHistogramt5HOM.png}
+    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
 \end{figure*}

### 2013-05-02 paper/Analisis.tex
+ text for Nscatt section

@@
 
-In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$
-
-as we think Nscatt is related with the double peacked line and maxima positions.
+In order to understand the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both central Fig.
+~\ref{fig:NscattHisto} and homogeneous distribution Fig.
+~\ref{fig:NscattHistoHOM}.
+For the central distribution we found that for some value (put the value) of $N_{scatt}$ there is a predominant shift $X_{m}$.
+(Make position analysis of this photons).
+For te homogenepus distribution we found that most of the photons escape with just one scattering as a consequence that there are more photons near the surface and that rotating helps photons to escape easier.
+(improve this arguments with initial position analysis.)
 

### 2013-05-15 paper/Analisis.tex
Nscatt Histograms, Homogeneous & Central
Average Num. of Scatt Section

--- 2013-04-29 paper/Analisis.tex
@@
 For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution.
-it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.
+it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.\\
 
-In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$
+In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig.
+~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}.
+For the central distribution and for lower velocities we found that for some value (put the value) of $N_{scatt}$ the mayority of photons have a defined value of $X_{m}$.
+While for higher velocities photons tend spread out in $X_{m}$(Make position analysis of this photons).\\
 
-as we think Nscatt is related with the double peacked line and maxima positions.
+For the homogenepus distribution we found the same effect but also, for highest velocities the mayority of the photons near the surface escape with much less scatterings that in the static case.
+This analysis let us conclude that rotation make photons escape with less scatterings and it spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.
 
@@
 \begin{figure*}
-    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
-    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
+    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
 \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
@@
 \begin{figure*}
-    \includegraphics[width=0.45\textwidth]{2dHistogramt5HOM.png}
+     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous
+
     \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 

### 2013-05-17 paper/Analisis.tex
ideas

@@
 
-Previous studies have shown the correlation of the Escape fraction with galctic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust.
+Previous studies have shown the correlation of the Escape fraction with galactic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust.
 In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass.
@@
 the escape fraction does not change with velocity while it does in the
-optical depth. On the other hand for the homogeneous distribution we
+optical depth (See Verhamme 2006, an argument about this). On the other hand for the homogeneous distribution we
 found that for higher velocities photons escape easily. The difference
@@
 
-Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others. In order to study this FIG.(CLARA plot)
+Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others.
+In order to study this in more detal FIG.(CLARA plot)
 
@@
 
+..compare steidel et al (2011)
+
 \section{Discussion}
@@
 ... Comparison with Verhamme et al. results on the rotation
+... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha line convert double peak profiles into a single one. comments about rotation with inflows and outflows.
 

### 2013-05-19 paper/Analisis.tex
Escape fraction text

@@
 
-Of great importance is to notest that for the homogeneous distribution the optical depth of $\tau_{H}=10^5$ does not follow the trend known for the others.
-In order to study this in more detal FIG.(CLARA plot)
+As a final test we compare our results with the analytical solution of the slab developed by (Neufeld 1990) Fig.
+~\ref{figure:efvsNeufeld}, as the geometry we use is different from the one described for Neufeld, we dont expect the same results, in fact we found that for the homogenous sphere the escape fraction is higer than the slab (see ref, mark).
+Also we notest that for $\tau<10^{6}$ the escape fraction does not increase as it will be expected, This is due to the fact that the condition $a\tau_{h}>>\tau_{d}$ in not valid anymore.
 
@@
 \end{figure*}
+
+\begin{figure}
+  \includegraphics[width=0.45\textwidth]{Neufeld.png}
+ \label{figure:efvsNeufeld}\caption{Escape fraction of this work compared with Neufeld analytical solution} 
+\end{figure}
 

### 2013-05-22 paper/Analisis.tex
First draft in the Integrated Flux section

@@
 
-\begin{figure*}
-    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
-    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
-\caption{Position of the maxima
-    in the outgoing spectra for differents Rotational velocities,
-    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
-\end{figure*}
+%\begin{figure*}
+%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
+%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
+%\caption{Position of the maxima
+%    in the outgoing spectra for differents Rotational velocities,
+%    (up)Central Distriution, (Down) Homogeneous Distribution.%\label{fig:maximumsvsvelocity}} 
+%\end{figure*}
 
@@
 
-..compare steidel et al (2011)
+Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position and the effect of the position of an observer.
+It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line.
+By far this is not and extensive study, it is just and ....
+
+One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, this implies..(explain a lit of bit the method)
+
+We make this analysis based in the results obtained by Steidel (2011) in this work (EXPLAIN a lit of bit more about their work) they used tree narrowband filters for tree different redshifts resumed in Table~\ref{table:NBfilters}, We want to know how much the integrated flux change due to rotational effects in this NB filters, for the models we simulated with CLARA.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{cccc}\hline
+Model & SSA22a 4980/80  & HS1700 4018/90 & HS1549 4667/80\\
+\hline
+V0HOM & 99965 / 98658 / & &\\
+V100HOM & 99221 / 95517 / 75058 & &\\
+V200HOM & 90630 / 90630 / 73938 & &\\
+V300HOM & 82180 / 82180 / 71953 & &\\
+V0HOMDust & 99968 / 99798 / 93132 & &\\
+V100HOMDust & 99445 / 98579 / 91208 & &\\
+V200HOMDust & 91439 / 90723 / 86134 & &\\
+V300HOMDust & 83116 / 82630 / 79943 & &\\
+\hline
+\end{tabular}
+\caption{
+Values of fluxes for tree different NB and the our models simulated with CLARA
+} 
+\label{table:NBfilters}
+\end{center}
+\end{table}
+
+As a first approach we may see that
 
@@
 interpreation of galaxy observations in the Lyman alpha line.
+..compare steidel et al (2011)
 % taking into account equivalent widths results with narrow band

### 2013-05-24 paper/Analisis.tex
label adentro del caption
Plots merged central and Homogeneous
2nd draft in sec 4.4 and in conclusions

@@
   to the same $V_{\rm max}=300$\kms, Optical   Depth $\tau=10^{7}$ and
-  Central Distribution without dust.}  
-  \label{fig:differentobservers}
+  Central Distribution without dust.
+  \label{fig:differentobservers}}
+
 \end{figure*}
@@
 
-\begin{figure*}
-    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
-    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
 \caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure*}%QUITARLA Y COMENTARLA
     \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
@@
 
-\begin{figure*}
-    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODCentral.png}
-    \includegraphics[width=0.45\textwidth]{maximumvsvelocitiesDifODHOM.png}
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
 \caption{Position of the maxima
@@
     (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
-    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
 \caption{Nscatt\label{fig:Nscatt}} 
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
     \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
 \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
-\end{figure*}
+\end{figure}
 
-\begin{figure*}
+\begin{figure}
      \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous
@@
     \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
-  \includegraphics[width=0.45\textwidth]{FECENTRAL.png}
-  \includegraphics[width=0.45\textwidth]{FEHOMOGENEOUS.png}
-   \label{figure:efvsv}\caption{Escape fraction for all the models. Left
-    panels show the central distribution, while right panels show the
-    homogeneous distribution} 
-\end{figure*}
+\begin{figure}
+  \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
+    \label{figure:efvsv}\caption{Escape fraction for all the models. Left panels show the central distribution, while right panels show the homogeneous distribution} 
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}%QUITARLA Y COMENTARLA
   \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
  \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
-\end{figure*}
+\end{figure}
 
@@
 
-\subsection{Integrated flux in a narrow band filter}
+\subsection{Integrated flux in a narrowband filter}
 
-Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position and the effect of the position of an observer.
+Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position, also we see that shape the outgoing spectra depends in the position of an esternl observer.
 It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line.
@@
 
-One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, this implies..(explain a lit of bit the method)
+One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, for this reason we focus this analysis with the
 
@@
 
-\begin{table}
+\begin{table*}
 \begin{center}
 \begin{tabular}{cccc}\hline
-Model & SSA22a 4980/80  & HS1700 4018/90 & HS1549 4667/80\\
+Model & SSA22a 4980/80   & HS1549 4667/80 & HS1700 4018/90\\
 \hline
-V0HOM & 99965 / 98658 / & &\\
-V100HOM & 99221 / 95517 / 75058 & &\\
-V200HOM & 90630 / 90630 / 73938 & &\\
-V300HOM & 82180 / 82180 / 71953 & &\\
-V0HOMDust & 99968 / 99798 / 93132 & &\\
-V100HOMDust & 99445 / 98579 / 91208 & &\\
-V200HOMDust & 91439 / 90723 / 86134 & &\\
-V300HOMDust & 83116 / 82630 / 79943 & &\\
+V0HOM & 0.997 / 0.906 / 0.405 & 0.999 / 0.965 / 0.523 & 0.999 / 0.991 / 0.662 \\
+V100HOM & 0.948 / 0.819 / 0.404 & 0.981 / 0.905 / 0.511 & 0.995 / 0.962 / 0.64 \\
+V200HOM & 0.748 / 0.748 / 0.403 & 0.815 / 0.815 / 0.488 & 0.879 / 0.879 / 0.59 \\
+V300HOM & 0.597 / 0.597 / 0.391 & 0.661 / 0.661 / 0.457 & 0.735 / 0.735 / 0.542 \\
+V0HOMDust & 0.999 / 0.997 / 0.931 & 0.999 / 0.993 / 0.863 & 0.999 / 0.998 / 0.927\\
+V100HOMDust & 0.994 / 0.985 / 0.912 & 0.986 / 0.967 / 0.863 & 0.996 / 0.989 / 0.9\\
+V200HOMDust & 0.914 / 0.907 / 0.861 & 0.833 / 0.815 / 0.728 & 0.889 / 0.879 / 0.81\\
+V300HOMDust & 0.831 / 0.826 / 0.799 & 0.676 / 0.668 / 0.618 & 0.749 / 0.744 / 0.702\\
 \hline
@@
 \end{center}
-\end{table}
+\end{table*}
 
-As a first approach we may see that
+In table \ref{table:NBfilters} we present the results of the flux in every narrowband filter for the homogenous model at different velocity and hydrogen optical depth $\tau_{0}$.
+As is well known an increase in the optical depth makes the line peacks separation bigger.
+In fact for some cases the line width is larger than the NB filer width fig.(put ref fig) for those cases we modify the redshift in order to make the peak maxima match the NB filter center.
+For all cases we found that as velocity increase the flux is less.
+\\
+In the case of the dusty model we found the same trend of the flux with the velocity but in this cases the effect is no that strong. 
+We also found some dependency ith the viewing angle.
 
@@
 radiative transfer code already used to study the Lyman $\alpha$
-line.
+line. \\
+
+1. Width and maxima effects
+
+2. Avg N of scatterings
+
+3. Integrated flux.
 

### 2013-05-27 paper/Analisis.tex
two more paragraphs in conclusions

@@
 composed as an homogenous mixture of dust and hydrogen at a constant
-temperature. These spheres have an solid-body rotation with linear
+temperature. These spheres have a solid-body rotation with linear
 velocities at the surface in the range $0-300$ \kms. We consider
@@
 
-Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position, also we see that shape the outgoing spectra depends in the position of an esternl observer.
+Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position, also we see that shape of the outgoing spectra depends on the position of the observer.
 It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line.
-By far this is not and extensive study, it is just and ....
 
-One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, for this reason we focus this analysis with the
-
-We make this analysis based in the results obtained by Steidel (2011) in this work (EXPLAIN a lit of bit more about their work) they used tree narrowband filters for tree different redshifts resumed in Table~\ref{table:NBfilters}, We want to know how much the integrated flux change due to rotational effects in this NB filters, for the models we simulated with CLARA.
+One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, we make this analysis based on the results obtained by Steidel (2011) in this work (EXPLAIN a lit of bit more about their work) they used tree narrowband filters for tree different redshifts resumed in Table~\ref{table:NBfilters}, We want to know how much the integrated flux change due to rotational effects in this NB filters, for the models we simulated with CLARA.
 
@@
 
-In table \ref{table:NBfilters} we present the results of the flux in every narrowband filter for the homogenous model at different velocity and hydrogen optical depth $\tau_{0}$.
+In table \ref{table:NBfilters} we present the results of the flux in every narrowband filter for the homogenous model at different velocities and hydrogen optical depth $\tau_{0}$.
 As is well known an increase in the optical depth makes the line peacks separation bigger.
@@
 In the case of the dusty model we found the same trend of the flux with the velocity but in this cases the effect is no that strong. 
-We also found some dependency ith the viewing angle.
+We also found some dependency with the viewing angle.
 
@@
 
-1. Width and maxima effects
+As first we see how the width of the line changes using a modified FWHM explained in section \ref{sec:widthpeak}, and we found that as gas bulk rotation incrase also the width increase in a factor of $2-3$ in comparison with the static case.
+we also take into account the influence of the observer position is and we found that for observers with a line of sight perpendicular to the axis of rotation measure a larger ($15\%$) line width than those aligned with the rotation axis.\\
 
-2. Avg N of scatterings
+As many observational Ly$\alpha$ (Kulas et al) spectra are double peaked  and those provide important information about the inflows/outflows of gas content, we study the effect of rotation in the position of this peaks and we find that the position of the maxima does not change with rotation.\\
 
-3. Integrated flux.
+One of the key features in the study of the Ly$\alpha$ line is the escape fraction, when rotational effects are taking into account we found that the escape fraction increase in about $20\%-30\%$ for the homogenous sphere model.
+(Nscatt)
+
+4. Integrated flux.
 

### 2013-05-30 paper/Analisis.tex
Conclusions

@@
 simplified models where a galaxy is modeled as an homogeneous sphere
-composed as an homogenous mixture of dust and hydrogen at a constant
+composed as an homogeneous mixture of dust and hydrogen at a constant
 temperature. These spheres have a solid-body rotation with linear
@@
 sources we measure an increase of about a factor of $2$ in the escape
-fraction for higher rotational velocity vealues.
-
+fraction for higher rotational velocity values. 
 Our work shows clearly that gas rotation has a non
-negligeable impact on the shape of the Lyman $\alpha$ line.
+negligible impact on the shape of the Lyman $\alpha$ line.
 
@@
 
-Due to the resonant nature of the lyman alpha line, gas kinematics
+Due to the resonant nature of the Lyman alpha line, gas kinematics
 play an important role shaping its morphology. In the literature there
@@
 rotation we focus on a simple system: the gas distribution is
-spherical, with homogenous density and the gas rotates as a solid
+spherical, with homogeneous density and the gas rotates as a solid
 body. We base our work on the Monte Carlo base radiative transfer code
@@
 The central result of this paper is summarized in
-Fig.~\ref{fig:DifferentVelocities} where we show that rotation has a
+Fig.~\ref{fig:differentvelocities} where we show that rotation has a
 considerable effect on the morphology of the emergent Lyman-alpha line
@@
 regardless of the direction of the outgoing photons. Figure
-\ref{fig:DifferentObservers} shows how if one gives a weight to each outgoing
+\ref{fig:differentobservers} shows how if one gives a weight to each outgoing
 photon according to its direction when escaping the gas distribution
-it is posible to detect notable differences in the spectrum for
+it is possible to detect notable differences in the spectrum for
 different viewing angles.
@@
 \caption{Shape of the lyman alpha line for
-    differents velocities. The left (right) panel shows the central
+    different velocities. The left (right) panel shows the central
     (homogeneous) photon distribution. All photons were taken into
@@
 \caption{Same as Figure \ref{fig:differentvelocities} but this time
-  the differen lines show the line morphology for different polar angles
+  the different lines show the line morphology for different polar angles
   $\theta$ with respect to the rotation axis. In this case each photon
@@
 respect to the rotation angle, $\mu = \cos{\theta}$. All the results
-in this section will be expressed in terms of resframe wavelength.
+in this section will be expressed in terms of rest frame wavelength.
 
@@
 \label{sec:widthpeak}
+\label{fig:differentvelocities}
 
@@
     \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
-\caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
+\caption{Width of the lyman-alpha line for all the models.\label{fig:widthvsvelocity}}
 \end{figure}
 
-\begin{figure*}%QUITARLA Y COMENTARLA
-    \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
-    \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
-    \caption{Width of the lyman-alpha line for all the models. 
-  \label{figure:widthvstheta}
-}
-\end{figure*}
+%\begin{figure*}%QUITARLA Y COMENTARLA
+  %  \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
+   % \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
+    %\caption{Width of the lyman-alpha line for all the models. 
+ % \label{figure:widthvstheta}
+%}
+%\end{figure*}
 
@@
 the case of Lyman-alpha sources homogeneously distributed in the gas
-distributions (Fig. \ref{differentvelocities} right panel).
+distributions (Fig.~\ref{fig:differentvelocities} Right panel).
 
@@
 
+%Im not sure about this anymore
 This result includes all the outgoing photons, regardless of the
@@
 that observers with a line of sight perpendicular to the axis of
-rotation (i.e. edge-on in the case of spiral galaxy) tend to meaure
+rotation (i.e. edge-on in the case of spiral galaxy) tend to measure
 larger line widths than observers aligned with the rotation axis
@@
 %increase also the equivalent width increase (for both homogeneous and
-%central distribution), it means that some photons escape with fewer
+%central distribSi Limonution), it means that some photons escape with fewer
 %scatterings than the static case but at the same time a few photons escape with% more scatterings, this can be seen clearly in
@@
 %We also found a dependency with the viewing angles, in particular as
-%the angle increase the width also increase Figure
+%the angle incre ase the width also increase Figure
 %~\ref{fig:withvstheta}, this was also found in Verhemme et al. 2012
@@
 
-In Figure ~\ref{fig:maximavsvelocity} we present the position
+In Figure~\ref{fig:maximumsvsvelocity} we present the position
 of the maxima as a function of $V_{\rm max}$. For the photons emitted
 in the line center we do not find any variation in the position of the
-maxima in the range of explored parameter space. However in the
+maxima in the range of explored parameter space (dash lines). However in the
 homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
@@
 This transition to a single peak line occurs for the systems where it
-becomes easiear for a bulk of the photons to escape with the lowest
+becomes easier for a bulk of the photons to escape with the lowest
 number of scatterings possible. This can explain how the single peak
@@
 
-In Figure ~\ref{fig:maximavsangle} we present the position of the
-maxima as a function of the viewing angle $\mu$ for all the optical
-depths and rotational velocities and the two different photon
-distributions [FALTA LA GRAFICA].
+We also take into account the viewing angle $\mu$ for all the optical 
+depths and rotational velocities and the two different photon distribution.
+But we don't find any dependency meaning that the peaks would be placed in
+the same place no matter the position of an external observer.
+
+%In Figure ~\ref{fig:maximavsangle} we present the position of the
+%maxima as a function of the viewing angle $\mu$ for all the optical
+%depths and rotational velocities and the two different photon
+%distributions [FALTA LA GRAFICA].
 
@@
 optical depth $\tau_{H}$ on the maxima position $x_{m}$
-Figure~\ref{figure:maximavsOD}. We find that, at fixed
+Figure~\ref{fig:maximumsvsvelocity}. We find that, at fixed
 rotation velocity, the position of the maxima increases with optical
-depth as expected from basic theoretical consideraions. We compare
-our results with the expected theoretical escaling for an infinnite
+depth as expected from basic theoretical considerations. We compare
+our results with the expected theoretical scaling for an infinite
 slab.
@@
 
-Untill know we have focus in how rotation affect the morphology of the lyman alpha line, now we turn to study deeply the posible causes of this effects.
-As recombination is the main cause of the lyman alpha, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelenght.
-\\
+Until know we have focus in how rotation affect the morphology of the Lyman alpha line, now we turn to study deeply the possible causes of this effects.
+As recombination is the main cause of the emission of the Lyman alpha line, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelength.
 
-As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}.
-For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution.
-it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.\\
+As a first approach we study the number of scatterings of all the photons at different velocities and for both photon distributions Figure~\ref{fig:Nscatt}.
+For the central distribution we found that the average number of scattering does not have a relevant change ($\sim 0.5\%$) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease in a$\sim 39\%$, it means that rotation makes photons to escape easier from the cloud.
+The reason why this is not observed in the central distribution is because the amount of gas that every photon has to break through is so large that the average number of scatterings is large too, making the effect of rotation unobservable.
 
-In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig.
-~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}.
+In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}.
 For the central distribution and for lower velocities we found that for some value (put the value) of $N_{scatt}$ the mayority of photons have a defined value of $X_{m}$.
@@
 
-For the homogenepus distribution we found the same effect but also, for highest velocities the mayority of the photons near the surface escape with much less scatterings that in the static case.
+For the homogeneous distribution we found the same effect but also, for highest velocities the mayority of the photons near the surface escape with much less scatterings that in the static case.
 This analysis let us conclude that rotation make photons escape with less scatterings and it spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.
@@
     \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
-\caption{Nscatt\label{fig:Nscatt}} 
+\caption{Log of the Average number of scatterings of the outgoing photons as function of the velocity. \label{fig:Nscatt}} 
 \end{figure}
@@
 
-We have seen in the previous section that rotation affects the number
-of scatterings that ..\\
+Until now we have studied models in absence of dust, but is known (REFERENCE) that there is presence of dust in high redshift galaxies.
+Our models with dust are treated as is explained in detail in  the appendix of (Forero et al 2011).
 
-Of particular interest is to compute the escape fraction of Lyman $\alpha$ photons coming from the most distant galaxies, due to the fact that with the observed intensity of the lyman alpha line quantities as the LF and SFR can be derived (put some references).
-\\
+Of particular interest is to compute the escape fraction of Lyman $\alpha$ photons coming from the most distant galaxies, due to the fact that with the observed intensity of the Lyman alpha line quantities as the LF and SFR can be derived (put some references).
 
-Previous studies have shown the correlation of the Escape fraction with galactic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust.
+Previous studies have shown the correlation of the Escape fraction with galactic mass (Laursen et al 2009, Dayal et al 2010) abundances and the kinematics of dust.
 In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass.
-We compute the escape fraction for the models described in Table \ref{table:models}.\\
+We compute the escape fraction for the models described in Table \ref{table:models}.
 
-For a realistic model we also take into account the viewing angle, first we fixed the viewing angle at $\theta = 0$  Fig.
-and then we fixed the velocity in order to see the escape fraction correlation with the viewing angle.
+For a realistic model we also take into account the viewing angle, first we fixed the viewing angle at $\theta = 0$  Fig.~\ref{figure:efvsv} and then we fixed the velocity in order to see the escape fraction correlation with the viewing angle.
 Therefore we define the escape fraction as:\\
@@
 Where NI is the initial number of photons and NF is the final,
-$\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer
+$\vec{k}$ is the rotation axis direction and ${o}$ the observer
 direction. With this definition we compute the escape fraction for all
-of our models, the results are shown in Fig \ref{figure:escape}\\
+of our models, the results are presented in Fig \ref{figure:efvsv}\\
 
@@
   \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
-    \label{figure:efvsv}\caption{Escape fraction for all the models. Left panels show the central distribution, while right panels show the homogeneous distribution} 
+   \caption{Escape fraction for all the models. continious lines represent the homogenous models, while dashed lines represent the central models}\label{figure:efvsv}
 \end{figure}
@@
 the escape fraction does not change with velocity while it does in the
-optical depth (See Verhamme 2006, an argument about this). On the other hand for the homogeneous distribution we
+optical depth (See Verhamme 2006, an argument about this). On the other
+hand for the homogeneous distribution we
 found that for higher velocities photons escape easily. The difference
-between this two results relly in the fact that in the homogeneous
+between this two results rely in the fact that in the homogeneous
 distribution photons are emitted closer to the escape surface and this
@@
 
-As a final test we compare our results with the analytical solution of the slab developed by (Neufeld 1990) Fig.
-~\ref{figure:efvsNeufeld}, as the geometry we use is different from the one described for Neufeld, we dont expect the same results, in fact we found that for the homogenous sphere the escape fraction is higer than the slab (see ref, mark).
-Also we notest that for $\tau<10^{6}$ the escape fraction does not increase as it will be expected, This is due to the fact that the condition $a\tau_{h}>>\tau_{d}$ in not valid anymore.
+As a final test we compare our results with the analytical solution of 
+the slab developed by (Neufeld 1990) Fig. ~\ref{figure:efvsNeufeld}, as 
+the geometry we use is different from the one described for Neufeld, we 
+dont expect the same results, in fact we found that for the homogenous 
+sphere the escape fraction is higer than the slab (see ref, mark). Also 
+we notest that for $\tau<10^{6}$ the escape fraction does not increase 
+as it will be expected, This is due to the fact that the condition 
+$a\tau_{h}>>\tau_{d}$ in not valid any more.
 
@@
 
+\subsection{Inhomogeneous model}
+
+Now we set up a test model when the photons are placed in an inhomogeneous model,
+
 \subsection{Integrated flux in a narrowband filter}
 
-Untill now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM the maxima position, also we see that shape of the outgoing spectra depends on the position of the observer.
+Until now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM, the maxima position, also we see that shape of the outgoing spectra depends on the position of the observer.
 It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line.
@@
 \hline
-V0HOM & 0.997 / 0.906 / 0.405 & 0.999 / 0.965 / 0.523 & 0.999 / 0.991 / 0.662 \\
-V100HOM & 0.948 / 0.819 / 0.404 & 0.981 / 0.905 / 0.511 & 0.995 / 0.962 / 0.64 \\
-V200HOM & 0.748 / 0.748 / 0.403 & 0.815 / 0.815 / 0.488 & 0.879 / 0.879 / 0.59 \\
-V300HOM & 0.597 / 0.597 / 0.391 & 0.661 / 0.661 / 0.457 & 0.735 / 0.735 / 0.542 \\
-V0HOMDust & 0.999 / 0.997 / 0.931 & 0.999 / 0.993 / 0.863 & 0.999 / 0.998 / 0.927\\
-V100HOMDust & 0.994 / 0.985 / 0.912 & 0.986 / 0.967 / 0.863 & 0.996 / 0.989 / 0.9\\
-V200HOMDust & 0.914 / 0.907 / 0.861 & 0.833 / 0.815 / 0.728 & 0.889 / 0.879 / 0.81\\
-V300HOMDust & 0.831 / 0.826 / 0.799 & 0.676 / 0.668 / 0.618 & 0.749 / 0.744 / 0.702\\
+V0HOM & 0.99 / 0.90 / 0.40 & 1.0 / 0.96 / 0.52 & 1.0 / 0.99 / 0.66 \\
+V100HOM & 0.94 / 0.81 / 0.40 & 0.98 / 0.90 / 0.51 & 0.99 / 0.96 / 0.64 \\
+V200HOM & 0.74 / 0.74 / 0.40 & 0.81 / 0.81 / 0.48 & 0.87 / 0.87 / 0.59 \\
+V300HOM & 0.59 / 0.59 / 0.39 & 0.66 / 0.66 / 0.45 & 0.73 / 0.73 / 0.54 \\
+V0HOMDust & 0.99 / 0.99 / 0.93 & 0.99 / 0.99 / 0.86 & 0.99 / 0.99 / 0.92\\
+V100HOMDust & 0.99 / 0.98 / 0.91 & 0.98 / 0.96 / 0.86 & 0.99 / 0.98 / 0.9\\
+V200HOMDust & 0.91 / 0.90 / 0.86 & 0.83 / 0.81 / 0.72 & 0.88 / 0.87 / 0.81\\
+V300HOMDust & 0.83 / 0.82 / 0.79 & 0.67 / 0.66 / 0.61 & 0.74 / 0.74 / 0.70\\
 \hline
@@
 
-In table \ref{table:NBfilters} we present the results of the flux in every narrowband filter for the homogenous model at different velocities and hydrogen optical depth $\tau_{0}$.
-As is well known an increase in the optical depth makes the line peacks separation bigger.
-In fact for some cases the line width is larger than the NB filer width fig.(put ref fig) for those cases we modify the redshift in order to make the peak maxima match the NB filter center.
+In table \ref{table:NBfilters} we present the results of the flux in every 
+narrowband filter for the homogeneous model at different velocities and hydrogen 
+optical depth $\tau_{0}$. As is well known an increase in the optical depth makes 
+the line peaks separation bigger. In fact for some cases the line width is larger 
+than the NB filer width fig.(put ref fig) for those cases we modify the redshift 
+in the available range in order to make the peak maxima match the NB filter center. 
 For all cases we found that as velocity increase the flux is less.
-\\
-In the case of the dusty model we found the same trend of the flux with the velocity but in this cases the effect is no that strong. 
+
+In the case of the dusty model we found the same trend of the flux with the velocity 
+but in this cases the effect is no that strong. 
 We also found some dependency with the viewing angle.
+
+\begin{figure}
+  \includegraphics[width=0.45\textwidth]{NB7tDifVHOM.png}
+ \label{figure:efvsNeufeld}\caption{NB filter located at the center of the maxima, with different redshift} 
+\end{figure}
 
@@
 ... The results derived in this paper have consequences on the
-interpreation of galaxy observations in the Lyman alpha line.
+interpretation of galaxy observations in the Lyman alpha line.
 ..compare steidel et al (2011)
@@
 rotation speed, hydrogen optical depth, dust optical depth and initial
-distribution of Lyman$\alpha$ photons with respect to the gas
+distribution of Ly$\alpha$ photons with respect to the gas
 density. This was implemented in CLARA, a Monte-Carlo
 radiative transfer code already used to study the Lyman $\alpha$
-line. \\
+line.
 
-As first we see how the width of the line changes using a modified FWHM explained in section \ref{sec:widthpeak}, and we found that as gas bulk rotation incrase also the width increase in a factor of $2-3$ in comparison with the static case.
-we also take into account the influence of the observer position is and we found that for observers with a line of sight perpendicular to the axis of rotation measure a larger ($15\%$) line width than those aligned with the rotation axis.\\
+As first we see how the width of the line changes using a modified FWHM
+explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
+rotation increase also the width increase in a factor of $2-3$ in comparison 
+with the static case. We also take into account the influence of the observer 
+viewing angle, we found that observers with a line of sight perpendicular  
+to the axis of rotation measure a $15\%$ larger line width than those 
+aligned with the rotation axis.
 
-As many observational Ly$\alpha$ (Kulas et al) spectra are double peaked  and those provide important information about the inflows/outflows of gas content, we study the effect of rotation in the position of this peaks and we find that the position of the maxima does not change with rotation.\\
+As many observational spectra Ly$\alpha$ emission line (Kulas et al) is double 
+peaked, these peaks provide important information concerning gas kinematics and geometry, 
+which can be partially explained with inflows/outflows of gas content. 
+We study the effect of rotation in the position of this peaks, and we find 
+that the position of the maxima does change with rotation for the homogeneous 
+models when the double peak merged into a single peak as velocity increase. 
+This effect is not seen for the central distribution when the double peak 
+remains constant as the velocity increase. We also find that there is no 
+dependency in the observer viewing angle with the maxima position.
 
-One of the key features in the study of the Ly$\alpha$ line is the escape fraction, when rotational effects are taking into account we found that the escape fraction increase in about $20\%-30\%$ for the homogenous sphere model.
-(Nscatt)
+Concerning the escape fraction under rotational effects on the Ly$\alpha$ 
+emission line, we found that the escape fraction increase in about $20\%-30\%$
+for the homogeneous sphere model. While rotational effects are negligible for
+the central models and the escape fraction remains constant. Also the observer
+viewing angle have no effect in the escape fraction neither for the homogeneous
+and central models. Complementing this analysis we study the average number of 
+scatterings $<N_{scatt}>$ that photons perform before escaping of the cloud
+taking into account rotational effects. The main result here is for the homogeneous
+models for which as velocity increase photons escape with about $\sim 39\%$ 
+less scatterings than in the static case.
 
-4. Integrated flux.
+As an application of these results we compute the integrated flux taking 
+into account the narrow band filters used by (Steidel et al 2011), for 
+our models we found an important decrease up to $~40\%$ for the homogeneous models, 
+and up to $22\%$ for the dusty homogeneous models in the flux as velocity increase. 
+Also we calculate at what redshift should the filter be in order to get the maximum 
+flux, and for the tree filters we get values that rely in the filter redshift range.
+This effects would have a relevant implication at the time to find high redshift 
+galaxies.
+
+This paper illustrates for the first time the main effects of rotation in  
+the morphology of the Ly$\alpha$ emission line, we estimate the range of this effects
+for simplified models.
 

### 2013-05-31 paper/Analisis.tex
minor changes

@@
 sphere, meaning that all the escaping photons were taking into account
-regardless of the direction of the outgoing photons. Figure
-\ref{fig:differentobservers} shows how if one gives a weight to each outgoing
+regardless of the direction of the outgoing photons. Fig.~\ref{fig:differentobservers}
+shows how if one gives a weight to each outgoing
 photon according to its direction when escaping the gas distribution
@@
 
-Figure~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
+Fig.~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
 as a function of $V_{\rm max}$. The line width increases with the
@@
 
-%Im not sure about this anymore
+%Im not sure about this anymore---TALK to Jaime about this!
 This result includes all the outgoing photons, regardless of the
@@
 
-In Figure~\ref{fig:maximumsvsvelocity} we present the position
+In Fig.~\ref{fig:maximumsvsvelocity} we present the position
 of the maxima as a function of $V_{\rm max}$. For the photons emitted
@@
 optical depth $\tau_{H}$ on the maxima position $x_{m}$
-Figure~\ref{fig:maximumsvsvelocity}. We find that, at fixed
+Fig.~\ref{fig:maximumsvsvelocity}. We find that, at fixed
 rotation velocity, the position of the maxima increases with optical
@@
 
-Until know we have focus in how rotation affect the morphology of the Lyman alpha line, now we turn to study deeply the possible causes of this effects.
-As recombination is the main cause of the emission of the Lyman alpha line, it is important to study the relationship between the number of times that a photon is absorbed and re emitted hereafter scatterings with it's shift in the wavelength.
+Until know we have focus in how rotation affect the morphology of the 
+Lyman alpha line, now we turn to study deeply the possible causes of 
+this effects. As recombination is the main cause of the emission of the 
+Lyman alpha line, it is important to study the relationship between the 
+number of times that a photon is absorbed and re emitted that we simply 
+take as scatterings with it's shift in the wavelength.
 
-As a first approach we study the number of scatterings of all the photons at different velocities and for both photon distributions Figure~\ref{fig:Nscatt}.
-For the central distribution we found that the average number of scattering does not have a relevant change ($\sim 0.5\%$) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease in a$\sim 39\%$, it means that rotation makes photons to escape easier from the cloud.
-The reason why this is not observed in the central distribution is because the amount of gas that every photon has to break through is so large that the average number of scatterings is large too, making the effect of rotation unobservable.
+As a first approach we study the number of scatterings of all the photons 
+at different velocities and for both photon distributions Figure~\ref{fig:Nscatt}. 
+For the central distribution we found that the average number of scattering 
+does not have a relevant change ($\sim 0.5\%$) with $V_{max}$, For the 
+Homogeneous distribution we found that as $V_{max}$ increase the average 
+number of scatterings decrease in a$\sim 39\%$, it means that rotation 
+makes photons to escape easier from the cloud. The reason why this is not 
+observed in the central distribution is because the amount of gas that every 
+photon has to break through is so large that the average number of scatterings 
+is large too, making the effect of rotation unobservable.
 
-In order to understand the effects of rotation in the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution Fig.~\ref{fig:NscattHistoHOM}.
-For the central distribution and for lower velocities we found that for some value (put the value) of $N_{scatt}$ the mayority of photons have a defined value of $X_{m}$.
-While for higher velocities photons tend spread out in $X_{m}$(Make position analysis of this photons).\\
+In order to understand the effects of rotation in the morphology of the line
+ we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the 
+ central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution 
+ Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower 
+ velocities we found that for some value (put the value) of $N_{scatt}$ the 
+ mayority of photons have a defined value of $X_{m}$. While for higher 
+ velocities photons tend spread out in $X_{m}$(Make position analysis of 
+ this photons).
 
-For the homogeneous distribution we found the same effect but also, for highest velocities the mayority of the photons near the surface escape with much less scatterings that in the static case.
-This analysis let us conclude that rotation make photons escape with less scatterings and it spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.
+For the homogeneous distribution we found the same effect but also, for 
+highest velocities the mayority of the photons near the surface escape 
+with much less scatterings that in the static case. This analysis let us 
+conclude that rotation make photons escape with less scatterings and it 
+spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.
 
@@
     \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
-\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
+\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
 \end{figure}
@@
 
-    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
+    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
 \end{figure}
@@
 
-Until now we have studied models in absence of dust, but is known (REFERENCE) that there is presence of dust in high redshift galaxies.
-Our models with dust are treated as is explained in detail in  the appendix of (Forero et al 2011).
+Until now we have studied models in absence of dust, but is known (REFERENCE) 
+that there is presence of dust in high redshift galaxies. Our models with 
+dust are treated as is explained in detail in  the appendix of (Forero et al 2011).
 
-Of particular interest is to compute the escape fraction of Lyman $\alpha$ photons coming from the most distant galaxies, due to the fact that with the observed intensity of the Lyman alpha line quantities as the LF and SFR can be derived (put some references).
+Of particular interest is to compute the escape fraction of Lyman $\alpha$ 
+photons coming from the most distant galaxies, due to the fact that with the 
+observed intensity of the Lyman alpha line quantities as the LF and SFR can 
+be derived (put some references).
 
-Previous studies have shown the correlation of the Escape fraction with galactic mass (Laursen et al 2009, Dayal et al 2010) abundances and the kinematics of dust.
-In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass.
-We compute the escape fraction for the models described in Table \ref{table:models}.
+Previous studies have shown the correlation of the Escape fraction with galactic 
+mass (Laursen et al 2009, Dayal et al 2010) abundances and the kinematics of dust. 
+In order to study pure rotational effects in the escape fraction we fixed the dust 
+abundance $\tau_{A}=0.01$ and the galaxy mass. We compute the escape fraction for 
+the models described in Table \ref{table:models}.
 
-For a realistic model we also take into account the viewing angle, first we fixed the viewing angle at $\theta = 0$  Fig.~\ref{figure:efvsv} and then we fixed the velocity in order to see the escape fraction correlation with the viewing angle.
+For a realistic model we also take into account the viewing angle, first we fixed 
+the viewing angle at $\theta = 0$  Fig.~\ref{figure:efvsv} and then we fixed the 
+velocity in order to see the escape fraction correlation with the viewing angle. 
 Therefore we define the escape fraction as:\\

### 2013-05-31 paper/Analisis.tex
2 paragraphs in Inhomogeneous section + plots :)

@@
 
-Now we set up a test model when the photons are placed in an inhomogeneous model,
+As we know there is unlikely to find galaxies with radiation sources 
+distributed homogeneously. Most of them are in a clumpy distribution 
+(Larsen et al 2013*) which affected the resulting spectra. In order 
+to study an inhomogeneous distribution we set up a model in which we 
+select certain photons that are placed in a specific place but that 
+are not symmetrically Fig.~\ref{figure:distributions}.
+
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{Distribution1.png}
+  \includegraphics[width=0.45\textwidth]{Distribution2.png}
+ \caption{Inhomogeneous distributions of 
+ photons, red area are the selected photons, the arrow points to the 
+ observer position, left panel Distribution 1, right panel Distribution 2\label{figure:distributions}} 
+\end{figure*}
+
+In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
+distribution 1 and 2, the most important result is to see the 
+asymmetry  of the line in particular the photons selected in 
+distribution 1 present a blueshift while photons selected in 
+distribution 2 present a redshift. Is also important to see that
+as velocity increases this shifts became stronger.
+
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
+  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
+ \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ , left panel with $\tau=10^5$, right panel with $\tau=10^5$\label{figure:inhomogeneous}} 
+\end{figure*}
 

### 2013-06-05 paper/Analisis.tex
Nscatt Histrograms + text in off center model

--- 2013-05-31 paper/Analisis.tex
@@
 
-\begin{figure}
-    \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
-\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
-\end{figure}
+%\begin{figure}
+ %   \includegraphics[width=0.54\textwidth]{test4.png}
+  %  \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
 
-\begin{figure}
-     \includegraphics[width=0.54\textwidth]{test3.png}%this is the homogeneous
+%\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
+%\end{figure}
 
-    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
-\end{figure}
+\begin{figure*}
+     \includegraphics[width=0.40\textwidth]{2dHistogram0t5HOM.png}
+     \includegraphics[width=0.40\textwidth]{2dHistogram300t5HOM.png}
+
+    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous distribution, left for $V_{max}=0km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
+\end{figure*}
+
+\begin{figure*}
+     \includegraphics[width=0.40\textwidth]{2dHistogram50t5.png}
+     \includegraphics[width=0.40\textwidth]{2dHistogram300t5.png}
+
+    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central distribution, left for $V_{max}=50km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
+\end{figure*}
 
@@
 
-\begin{figure}%QUITARLA Y COMENTARLA
-  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
- \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
-\end{figure}
+%\begin{figure}%QUITARLA Y COMENTARLA
+ % \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
+ %\label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the %homogeneous configuration.} 
+%\end{figure}
 
@@
 
-Now we set up a test model when the photons are placed in an inhomogeneous model,
+As we know there is unlikely to find galaxies with radiation sources 
+distributed homogeneously. Most of them are in a clumpy distribution 
+(Laursen et al 2013*) which affected the resulting spectra. In order 
+to study an inhomogeneous distribution we set up a model in which we 
+select certain photons that are placed in a specific place but that 
+are not symmetrically distributed Fig.~\ref{figure:distributions} shows
+the distributions we set up.
+
+\begin{figure}
+  \includegraphics[width=0.40\textwidth]{Distribution.png}
+  \caption{Inhomogeneous distributions of 
+ photons, Blue area represents the photons in distribution 1 while red area are the selected photons for distribution 2. The arrow points to the observer position\label{figure:distributions}} 
+\end{figure}
+
+In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
+distribution 1 and 2, the first effect we see is the asymmetry of the
+double peak, in the homogeneous and central distribution we see double
+peaks with the same height, while in this case one peak is higher than 
+the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
+peak is higher than the redshifted, and for distribution 2 the redshifted
+peak is the highest.
+
+An other important fact here is the asymmetry of the spectra with respect 
+to the line center, in particular photons selected in distribution 1 
+present a blueshift in their spectra while photons selected in distribution 
+2 present a redshift. This effect becomes stronger as velocity increase 
+~\ref{figure:inhomogeneous}
+
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
+  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
+ \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ , (left) with $\tau=10^5$, (right) with $\tau=10^6$\label{figure:inhomogeneous}} 
+\end{figure*}
 

### 2013-06-05 paper/Analisis.tex
some new paragraphs

@@
   Nicolas Garavito-Camargo$^{1}$,
-  Jaime E. Forero-Romero$^{1}$ 
+  Jaime E. Forero-Romero$^{1}$ and 
+  Mark Dijkstra$^2$
 }
@@
 $^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia 
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
+$^2$
 }
@@
 negligible impact on the shape of the Lyman $\alpha$ line.
-
 \end{abstract}
@@
 Due to the resonant nature of the Lyman alpha line, gas kinematics
-play an important role shaping its morphology. In the literature there
-has been extensive studies of outflow/inflow configurations.
+play an important role shaping its morphology.
+
+There is an extensive literature studying the influence of
+outflow/inflow configurations in the shape of the outgoing Lyman-alpha
+line.
 
@@
 spherical, with homogeneous density and the gas rotates as a solid
-body. We base our work on the Monte Carlo base radiative transfer code
-CLARA \citep{CLARA}.
+body. We base our work on two independent Monte Carlo based radiative
+transfer codes CLARA \citep{CLARA} and XX \citep{DijkstraKramer}.
 
@@
 
-\section{Implementation of Bulk Gas Rotation}
+In this paper we experess a photon's frequency in terms of the
+dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_\alpha$, where
+$\nu_{\alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
+frequency,  $\Delta_{\alpha} \equiv
+\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th} $ is the doppler
+broadening of the line which depends on the neutral gas temperature
+$T$ scattering the radiation or equivalently the thermal velocity
+$v_{\rm th}$ of the atoms.
+
+\section{Modeling Bulk Gas Rotation}
 \label{sec:implementation}
 
-We implement into CLARA the simplest model whereby a sphere rotates
-with homogeneous angular velocity. We define a cartesian coordinate
+Describing the kinematics of gas rotation in all generality is a
+complex task. There is great variation in the shape of the rotation
+curve as observed in HI emission as a function of the distance to the
+galaxy center. However there are two features that are observed very
+often. First, in the central region the velocity increases
+proportional to the radius following the behaviour in a body with
+solid rotation. Second, beyond a certain radius the rotation curve
+tends to flatten. Furthermore, a thorough observational account of gas
+rotation in the redshifts of interest for the study of LAEs ($z>1.0$)
+is still missing.
+
+An ab-initio description of realistic rotation curves in simulations
+depends on having access to the dynamic evoluction the mass components
+in the galaxy: stars, gas and dark matter. Such level of realism is
+extremely complex to achive, specially of one wants to get a
+systematic description based on statistics of simulated objects.
+
+Following the tradition of studies of Lyman$\alpha$ emitting systems,
+we implement a model with a simplified geoemtry and gas
+distribution. We assume that the gas is homogeneously distributed in a
+sphere that rotates as a solid body with constant angular
+velocity. This simple model will contain only one parameter: the
+linear velocity at the sphere's surface, $V_{\rm max}$.
+
+\subsection{The implementation}
+ We define a cartesian coordinate
 system with its origin at the center of the sphere and the rotation
@@
 
-\section{Grid of Simulated Models}
+\subsection{Grid of Simulated Models}
 \label{sec:models}
@@
 \end{table}
-
-%poner las graficas para un modelo dado poner el efecto de
-%la rotación (poner %uno con velocidad cero) y del observador.
 
@@
 
-%\begin{figure*}%QUITARLA Y COMENTARLA
-  %  \includegraphics[width=0.45\textwidth]{WidthvsThetaCentral.png}
-   % \includegraphics[width=0.45\textwidth]{WidthvsTheta.png}
-    %\caption{Width of the lyman-alpha line for all the models. 
- % \label{figure:widthvstheta}
-%}
-%\end{figure*}
-
 The first quantitative conclusion of the effect of rotation in the
@@
 
-%\begin{figure*}
-%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
-%    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
-%\caption{Position of the maxima
-%    in the outgoing spectra for differents Rotational velocities,
-%    (up)Central Distriution, (Down) Homogeneous Distribution.%\label{fig:maximumsvsvelocity}} 
-%\end{figure*}
-
-%\begin{figure}
-%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsCentral.png}
-%    \includegraphics[width=0.45\textwidth]{maximumvsODDifSpeedsHOM.png}
-%  \label{fig:maximavsOD}\caption{Position of the maxima in the
-%    outgoing spectra for differents Optical Depths, (up)Central
-%    Distriution, (Down) Homogeneous Distribution.} 
-%\end{figure}
-
 The second feature in the line that we use to quantify the effect of
@@
 the same place no matter the position of an external observer.
-
-%In Figure ~\ref{fig:maximavsangle} we present the position of the
-%maxima as a function of the viewing angle $\mu$ for all the optical
-%depths and rotational velocities and the two different photon
-%distributions [FALTA LA GRAFICA].
-
-%Finally when we take into account the viewing angle Fig
-%~\ref{fig:DifferentObservers} we found that $X_{m}$ does not depend on
-%it, but again there is a threshold for the homogeneous distribution in
-%which  the double peaked merged into a single peak but this time it is
-%just the angle of viewing effect.
-
-%rotational velocities photons escape with
-%less scatterings (fig:ref), for $v=100$\kms the majority of the photons
-%still escape with scatterings (double-peaked line) but for $v=200$\kms
-%the number of photons that escape with a few or any scatterings is higher
-%(single-peaked line), this is one of the main effects of rotation. \\
-
-% try a Nscatt plot as a function of theta
-%explain the method
-
-% explicar como se mide el ancho para algunos casos
-% I dont understand this at all, hope Nscatts plot helps 
- %make comparison with Verhamme et al
 
@@
 \end{figure}
-
-%\begin{figure}
- %   \includegraphics[width=0.54\textwidth]{test4.png}
-  %  \includegraphics[width=0.54\textwidth]{test4.png}%this is the central}
-
-%\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution, The upper plot is for $V_{max}=50km/s $, the bottom plot is for $V_{max}=300km/s$ \label{fig:NscattHisto}} 
-%\end{figure}
 
@@
 
-%\begin{figure}%QUITARLA Y COMENTARLA
- % \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
- %\label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the %homogeneous configuration.} 
-%\end{figure}
-
 \begin{figure}
   \includegraphics[width=0.45\textwidth]{Neufeld.png}
- \label{figure:efvsNeufeld}\caption{Escape fraction of this work compared with Neufeld analytical solution} 
+ \label{figure:efvsNeufeld}\caption{Escape fraction of this work
+   compared with Neufeld analytical solution}  
 \end{figure}
 
-\subsection{Inhomogeneous model}
+\subsection{The Case of Asymmetric Emission}
 
@@
   \caption{Inhomogeneous distributions of 
- photons, Blue area represents the photons in distribution 1 while red area are the selected photons for distribution 2. The arrow points to the observer position\label{figure:distributions}} 
+ photons, Blue area represents the photons in distribution 1 while red
+ area are the selected photons for distribution 2. The arrow points to
+ the observer position\label{figure:distributions}}  
 \end{figure}
@@
   \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
- \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ , (left) with $\tau=10^5$, (right) with $\tau=10^6$\label{figure:inhomogeneous}} 
+ \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ ,
+   (left) with $\tau=10^5$, (right) with
+   $\tau=10^6$\label{figure:inhomogeneous}}  
 \end{figure*}
@@
 
-Until now we have shown the main effects of gas and dust rotation in the Ly$\alpha$ line morphology such as the escape fraction, the FWHM, the maxima position, also we see that shape of the outgoing spectra depends on the position of the observer.
-It is important to see if rotational effects are detectable in observational methods involving the Ly$\alpha$ line.
+Until now we have shown the main effects of gas and dust rotation in
+the Ly$\alpha$ line morphology such as the escape fraction, the FWHM,
+the maxima position, also we see that shape of the outgoing spectra
+depends on the position of the observer. It is important to see if
+rotational effects are detectable in observational methods involving
+the Ly$\alpha$ line.
 
-One of the most used methods to detect high redshift galaxies using the Ly$\alpha$ line is using a narrowband selection, we make this analysis based on the results obtained by Steidel (2011) in this work (EXPLAIN a lit of bit more about their work) they used tree narrowband filters for tree different redshifts resumed in Table~\ref{table:NBfilters}, We want to know how much the integrated flux change due to rotational effects in this NB filters, for the models we simulated with CLARA.
+One of the most used methods to detect high redshift galaxies using
+the Ly$\alpha$ line is using a narrowband selection, we make this
+analysis based on the results obtained by Steidel (2011) in this work
+(EXPLAIN a lit of bit more about their work) they used tree narrowband
+filters for tree different redshifts resumed in
+Table~\ref{table:NBfilters}, We want to know how much the integrated
+flux change due to rotational effects in this NB filters, for the
+models we simulated with CLARA.
 
@@
 \hline
-V0HOM & 0.99 / 0.90 / 0.40 & 1.0 / 0.96 / 0.52 & 1.0 / 0.99 / 0.66 \\
-V100HOM & 0.94 / 0.81 / 0.40 & 0.98 / 0.90 / 0.51 & 0.99 / 0.96 / 0.64 \\
-V200HOM & 0.74 / 0.74 / 0.40 & 0.81 / 0.81 / 0.48 & 0.87 / 0.87 / 0.59 \\
-V300HOM & 0.59 / 0.59 / 0.39 & 0.66 / 0.66 / 0.45 & 0.73 / 0.73 / 0.54 \\
-V0HOMDust & 0.99 / 0.99 / 0.93 & 0.99 / 0.99 / 0.86 & 0.99 / 0.99 / 0.92\\
-V100HOMDust & 0.99 / 0.98 / 0.91 & 0.98 / 0.96 / 0.86 & 0.99 / 0.98 / 0.9\\
-V200HOMDust & 0.91 / 0.90 / 0.86 & 0.83 / 0.81 / 0.72 & 0.88 / 0.87 / 0.81\\
-V300HOMDust & 0.83 / 0.82 / 0.79 & 0.67 / 0.66 / 0.61 & 0.74 / 0.74 / 0.70\\
-\hline
 \end{tabular}
 \caption{
-Values of fluxes for tree different NB and the our models simulated with CLARA
+Fluxes for tree different narrow band filters.
 } 
@@
 
-In table \ref{table:NBfilters} we present the results of the flux in every 
-narrowband filter for the homogeneous model at different velocities and hydrogen 
-optical depth $\tau_{0}$. As is well known an increase in the optical depth makes 
-the line peaks separation bigger. In fact for some cases the line width is larger 
-than the NB filer width fig.(put ref fig) for those cases we modify the redshift 
-in the available range in order to make the peak maxima match the NB filter center. 
-For all cases we found that as velocity increase the flux is less.
+In table \ref{table:NBfilters} we present the results of the flux in
+every  narrowband filter for the homogeneous model at different
+velocities and hydrogen  optical depth $\tau_{0}$. As is well known an
+increase in the optical depth makes  the line peaks separation
+bigger. In fact for some cases the line width is larger  than the NB
+filer width fig.(put ref fig) for those cases we modify the redshift
+in the available range in order to make the peak maxima match the NB
+filter center.  For all cases we found that as velocity increase the
+flux is less.
 
-In the case of the dusty model we found the same trend of the flux with the velocity 
-but in this cases the effect is no that strong. 
-We also found some dependency with the viewing angle.
+In the case of the dusty model we found the same trend of the flux
+with the velocity  but in this cases the effect is no that strong.  We
+also found some dependency with the viewing angle.
 
@@
   \includegraphics[width=0.45\textwidth]{NB7tDifVHOM.png}
- \label{figure:efvsNeufeld}\caption{NB filter located at the center of the maxima, with different redshift} 
+ \label{figure:efvsNeufeld}\caption{NB filter located at the center of
+   the maxima, with different redshift}  
 \end{figure}
@@
 ... Comparison with Verhamme et al. results on the rotation
-... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha line convert double peak profiles into a single one. comments about rotation with inflows and outflows.
+... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha
+line convert double peak profiles into a single one. comments about
+rotation with inflows and outflows.
 
@@
 
-As many observational spectra Ly$\alpha$ emission line (Kulas et al) is double 
-peaked, these peaks provide important information concerning gas kinematics and geometry, 
-which can be partially explained with inflows/outflows of gas content. 
-We study the effect of rotation in the position of this peaks, and we find 
-that the position of the maxima does change with rotation for the homogeneous 
-models when the double peak merged into a single peak as velocity increase. 
-This effect is not seen for the central distribution when the double peak 
-remains constant as the velocity increase. We also find that there is no 
-dependency in the observer viewing angle with the maxima position.
+As many observational spectra Ly$\alpha$ emission line (Kulas et al)
+is double  peaked, these peaks provide important information
+concerning gas kinematics and geometry,  which can be partially
+explained with inflows/outflows of gas content.  We study the effect
+of rotation in the position of this peaks, and we find  that the
+position of the maxima does change with rotation for the homogeneous
+models when the double peak merged into a single peak as velocity
+increase. This effect is not seen for the central distribution when
+the double peak  remains constant as the velocity increase. We also
+find that there is no dependency in the observer viewing angle with
+the maxima position.
 
-Concerning the escape fraction under rotational effects on the Ly$\alpha$ 
-emission line, we found that the escape fraction increase in about $20\%-30\%$
-for the homogeneous sphere model. While rotational effects are negligible for
-the central models and the escape fraction remains constant. Also the observer
-viewing angle have no effect in the escape fraction neither for the homogeneous
-and central models. Complementing this analysis we study the average number of 
-scatterings $<N_{scatt}>$ that photons perform before escaping of the cloud
-taking into account rotational effects. The main result here is for the homogeneous
-models for which as velocity increase photons escape with about $\sim 39\%$ 
-less scatterings than in the static case.
+Concerning the escape fraction under rotational effects on the
+Ly$\alpha$ emission line, we found that the escape fraction increase
+in about $20\%-30\%$for the homogeneous sphere model. While rotational
+effects are negligible for the central models and the escape fraction
+remains constant. Also the observer viewing angle have no effect in
+the escape fraction neither for the homogeneous and central
+models. Complementing this analysis we study the average number of
+scatterings $<N_{scatt}>$ that photons perform before escaping of the
+cloud taking into account rotational effects. The main result here is
+for the homogeneous models for which as velocity increase photons
+escape with about $\sim 39\%$  less scatterings than in the static
+case.
 
-As an application of these results we compute the integrated flux taking 
-into account the narrow band filters used by (Steidel et al 2011), for 
-our models we found an important decrease up to $~40\%$ for the homogeneous models, 
-and up to $22\%$ for the dusty homogeneous models in the flux as velocity increase. 
-Also we calculate at what redshift should the filter be in order to get the maximum 
-flux, and for the tree filters we get values that rely in the filter redshift range.
-This effects would have a relevant implication at the time to find high redshift 
-galaxies.
+As an application of these results we compute the integrated flux
+taking into account the narrow band filters used by (Steidel et al
+2011), for our models we found an important decrease up to $~40\%$ for
+the homogeneous models, and up to $22\%$ for the dusty homogeneous
+models in the flux as velocity increase.  Also we calculate at what
+redshift should the filter be in order to get the maximum  flux, and
+for the tree filters we get values that rely in the filter redshift
+range. This effects would have a relevant implication at the time to
+find high redshift galaxies.
 
-This paper illustrates for the first time the main effects of rotation in  
-the morphology of the Ly$\alpha$ emission line, we estimate the range of this effects
-for simplified models.
+This paper illustrates for the first time the main effects of rotation
+in the morphology of the Ly$\alpha$ emission line, we estimate the
+range of this effects for simplified models.
 
@@
 
-% fix this table is too big
-%\begin{table*}
-%\begin{center}
-%\begin{tabular}{cc}\hline
-%Model & Fit\\
-%Central, $\tau=10^5, V=200$\kms &$FWHM(\mu)=-149877+84509\mu-17864\mu^{2}-1677\mu^{3}-59\mu^{4}$\\
-%Central, $\tau=10^6, V=200$\kms &$FWHM(\mu)=-32264+9644\mu-1080\mu^{2}+53.8\mu^{3}-\mu^{4}$\\
-%Central, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-1791+359\mu-27\mu^{2}+0.9\mu^{3}+0.011\mu^{4}$\\
-%Hom, $\tau=10^5, V=200$\kms & $FWHM(\mu)=-51882.9+12932.5\mu-54.58\mu^{2}-187.22\mu^{3}+11.66\mu^{4}$ \\
-%Hom, $\tau=10^6, V=200$\kms & $FWHM(\mu)=-7154649+2413478\mu-305268.4\mu^{2}+17158.92\mu^{3}-361.64\mu^{4}$ \\
-%Hom, $\tau=10^7, V=200$\kms & $FWHM(\mu)=-51074+9912\mu-721\mu^{2}+23.29\mu^{3}-0.28\mu^{4}$ \\
-%\hline
-%\end{tabular}
-%\caption{Fits for EW models} 
-%\label{table:fits}
-%\end{center}
-%\end{table*}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccc}\hline          
-Velocity (Km/s) & Maximum 1 position & Maximum 2 position \\ \hline
-50 & -16.2695 & 16.23705 \\ 
-100 & -15.66496 & 15.33504 \\ 
-200 & -16.93149 & 14.56851 \\ 
-300 & -13.40048 & 16.09952 \\ \hline 
-\end{tabular} 
-\caption{Optical Depth $\tau= 10^{7}$, Central Distribution}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccc}\hline 
-Velocity (km/s) & Maximum 1 position & Maximum 2 position\\ \hline
-50 & -7.46286 & 6.53714 \\ 
-100 & -7.53357 & 6.96643 \\ 
-200 & -8.17453 & 7.32547 \\ 
-300 & -6.81487 & 6.18513 \\ \hline 
-\end{tabular} 
-\end{center}
-\caption{Optical Depth $\tau = 10^{6}$, Central Distribution}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccc}\hline 
-Velocity(Km/s) & Maximum 1 position & Maximum 2 position\\ \hline
-50 & -4.33708 & 3.66292 \\ 
-100 & -4.27326 & 3.72674 \\ 
-200 & -3.7737 & 3.7263   \\ 
-300 & -3.84903 & 4.15097 \\ \hline 
-\end{tabular}
-\caption{Optical Depth $\tau=10^{5}$, Central distribution} 
-\end{center}
-\end{table}
-
-Line width\\
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccc}\hline 
-Velocity(Km/s) & FWHM & $\theta$\\ \hline 
-50 & 12.62 & $0^{o}$ \\ 
-50 & 12.72 & $45^{o}$ \\ 
-50 & 12.93 & $90^{o}$ \\ 
-100 & 14.07 & $0^{o}$ \\ 
-100 & 14.48 & $45^{o}$ \\ 
-100 & 15.00 & $90^{o}$ \\ 
-200 & 16.90 & $0^{o}$  \\ 
-200 & 18.51 & $45^{o}$ \\ 
-200 & 21.24 & $90^{o}$ \\ 
-300 & $24.69^{*}$ & $0^{o}$ \\ 
-300 & $25.79^{*}$ & $45^{o}$  \\ 
-300 & $27.73^{*}$ & $90^{o}$ \\ \hline
-\end{tabular}
-\caption{Lines Widhts for a Central Distribution and $\tau=10^{7}$} 
-\end{center}
-\end{table}
-
-Escape fraction\\
-
-\begin{table}[H]
-\begin{center}
-\begin{tabular}{ccccc}\hline 
-Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$\\ \hline 
-Homogeneous & 50 & $0^{o}$& 13293.06 &49939.53\\ 
-Homogeneous & 50 & $45^{o}$& 13291.04 &50001.59\\ 
-Homogeneous & 50 & $90^{o}$ & 13348.76 &49922.73\\ 
-Homogeneous & 100 & $0^{o}$ & 15527.69 &50114.11\\ 
-Homogeneous & 100 & $45^{o}$ & 15511.56 &49967.17\\ 
-Homogeneous & 100 & $90^{o}$ & 15401.71 & 49833.65\\ 
-Homogeneous & 200 & $0^{o}$  & 17830.85 & 50078.69\\ 
-Homogeneous & 200 & $45^{o}$ & 17932.87 & 50064.42\\ 
-Homogeneous & 200 & $90^{o}$ & 17830.85  & 49931.748\\ 
-Homogeneous & 300 & $ 0^{o}$ & 18687.33 & 50048.33 \\ 
-Homogeneous & 300 & $45^{o}$ & 18572.12& 49922.67\\ 
-Homogeneous & 300 & $90^{o}$ & 18421.79 & 49979.37\\ \hline
-\end{tabular}
-\caption{Escape fraction for a Homogeneous Distribution and optical depth $10^{5}$.} 
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{ccccc} \hline 
-Model & Velocity (km/s) & $\theta$ & Dust $\sum (s)$& $\sum (s)$ \\  \hline 
-Central & 50 & $0^{o}$ & 4809.881 & 49917.069 \\ 
-Central & 50 & $45^{o}$ & 4829.21 & 49811.79 \\ 
-Central & 50 & $90^{o}$ & 4845.108 & 49853.039\\ 
-Central & 100 & $0^{o}$ & 4809.665 & 49921.30 \\  
-Central & 100 & $45^{o}$ & 4828.65 & 49820.13 \\ 
-Central & 100 & $90^{o}$ & 4846.45 & 49854.0 \\ 
-Central & 200 & $0^{o}$  & 4809.63 & 49917.64 \\ 
-Central & 200 & $45^{o}$ & 4829.25 & 49818.49 \\ 
-Central & 200 & $90^{o}$ & 4844.89 & 49856.66 \\ 
-Central & 300 & $ 0^{o}$ & 4810.56 & 49922.98\\ 
-Central & 300 & $45^{o}$ & 4831.16 & 49823.33\\ 
-Central & 300 & $90^{o}$ & 4845.33 & 49858.48\\ \hline
-\end{tabular}
-\caption{Escape fraction for the central Distribution and optical depth $10^{5}$.} 
-\end{center}
-\end{table}
-
 %ideas:
-Keep in mind making a follow up paper on the results of Yamada et atl http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line morphology at z=3.1.
-How many of these laes can be considered to have rotation features?
-In principle, all of then should have them.
-How to make the case convincing in the statistical sense?
+Keep in mind making a follow up paper on the results of Yamada et atl
+http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line
+morphology at z=3.1. How many of t hese laes can be considered to have
+rotation features? In principle, all of then should have them. How to
+make the case convincing in the statistical sense?

### 2013-06-06 paper/Analisis.tex

@@
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
-\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha}\else{Ly$\alpha$}\fi}}
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
 \newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
@@
   Lyman-$\alpha$ line morphology in distant galaxies}
-\author[N. Garavito and J.E. Forero-Romero]{
+\author[Garavito-Camargo, Forero-Romero \& Dijkstra]{
 \parbox[t]{\textwidth}{\raggedright 
@@
 fraction for higher rotational velocity values. 
-Our work shows clearly that gas rotation has a non
-negligible impact on the shape of the Lyman $\alpha$ line.
+Our work shows clearly that gas rotation has a non negligible impact
+on the shape of the Lyman $\alpha$ line. 
 \end{abstract}
@@
 Due to the resonant nature of the Lyman alpha line, gas kinematics
-play an important role shaping its morphology.
+play an important role shaping its morphology...
 
@@
 outflow/inflow configurations in the shape of the outgoing Lyman-alpha
-line.
+line...
 
@@
 
-This paper is paper is structured as follows.
+This paper is paper is structured as follows...
 
-In this paper we experess a photon's frequency in terms of the
+In this paper we express a photon's frequency in terms of the
 dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_\alpha$, where
@@
 
-\subsection{The implementation}
- We define a cartesian coordinate
-system with its origin at the center of the sphere and the rotation
-axis to be the $z$-axis, the components in the bulk velocity field, $\vec{v}
-= v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{k}$. in the gas can be written as
+\subsection{Detailed Implementation of Rotation}
+
+ In the MonteCarlo code we define a cartesian coordinate system to
+ define the position of each photon. The origin of this system
+ coincides withthe center of the sphere and the rotation axis is defined
+ to be $z$-axis. With this choice, the components of the gas bulk velocity
+ field, $\vec{v} = v_{x}\hat{i} + v_{y}\hat{j} + v_{z}\hat{k}$, can be
+ written as
 
@@
 \end{subequations}
+%
+where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
+velocity at the sphere's surface. The minus/plus sign in the
+$x$/$y$-component of the velocity indicates the direction of
+rotation. In this case we take the angular velocity in the same
+direction as the $\hat{k}$ unit vector. With these definitions we can
+write the angular velocity as $\omega=V_{\rm max}/R$.
 
-where $R$ is the radius of the sphere and $V_{\rm max}$ is the linear
-velocity at the sphere's surface. The minus sign in the x-component of
-the velocity indicates the direction of rotation, in this case we
-assume that the angular velocity vector goes in the $\hat{k}$
-direction.  The linear dependence of the velocity on the radial
-distance describes the case of constant angular velocity
-$\omega=V_{\rm max}/R$.
+In contrast with spherically symmetric models (static, outflow,
+inflow) the rotation now defines a preferred direction in the
+problem. In Section \ref{sec:results} we quantify this differences by
+varying the line of sight of a mock observer with respect to the
+rotation axis. The results are parameterized by the polar angle
+$\theta$ as defined by the dot product $\cos\theta =
+{\hat{u}\cdot\hat{k}}$.
 
-We take the polar angle $\theta$ that a unitary vector makes with the
-rotation axis as defined by the dot product $\cos\theta =
-{\hat{u}\cdot\hat{k}}$. In the Section \ref{sec:results} we will
-present in detail how the line differs at different observing angles
-$\theta$.
-
-\subsection{Grid of Simulated Models}
+\subsection{Grid of Simulated Galaxies}
 \label{sec:models}
 
-We compute the emergent Lyman-$\alpha$ line for several models with
-differents values for the maximal rotational velocity, hydrogend optical
-depth, dust optical depth and initial distributions of the photons
+In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
+numerical photons through different spherical galaxies, each one
+varying in at least one of the following parameters: the maximum
+rotational velocity $V_{\rm max}$, hydrogen optical depth $\tau_{H}$,
+dust optical depth $\tau_{a}$ and the initial disitrbution of photons
 with respect to the gas. There are in total 60 models with the input
@@
 \begin{center}
-\begin{tabular}{ccc}\hline
+\begin{tabular}{llc}\hline\hline
+Physical Parameter (units) & Symbol & Values\\\hline
 Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
 Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
-Dust Optical Depth & $\tau_{A}$ & $0$,$1$\\
-Photons Distributions & & Central, Homogeneous\\
-\hline
+Dust Optical Depth & $\tau_{a}$ & $0$,$1$\\
+Photons Distributions & & Central, Homogeneous\\\hline\hline
 \end{tabular}
 \caption{
-Values for the varying input parameters in CLARA. Taking into account
-all the possible combinations for these models
-} 
+List of the physical parameters that define the spherical models we
+have simulated using Monte Carlo calculations. For each parameter we
+vary the values in the range listed in the last column. Takig into
+account all the possible combinations we end up with $60$ different
+models. } 
 \label{table:models}
@@
 The central result of this paper is summarized in
-Fig.~\ref{fig:differentvelocities} where we show that rotation has a
-considerable effect on the morphology of the emergent Lyman-alpha line
-both in the case where the photons are emitted at the sphere's center
-and when they are initialized with an homogeneous distribution all
-over the gas volume.
+Fig.~\ref{fig:differentvelocities} that shows clearly the considerable
+impact of rotation on the morphology of the emergent \ly line. Both
+panels in the Figure focus on the results for $\tau_{H}=10^{7}$,
+showing that the influence of rotation is present both when the
+photons are either homogeneusly or centrally initialized over the gas
+volume.
 
-The results for these outgoing spectra are integrated over the whole
-sphere, meaning that all the escaping photons were taking into account
-regardless of the direction of the outgoing photons. Fig.~\ref{fig:differentobservers}
-shows how if one gives a weight to each outgoing
-photon according to its direction when escaping the gas distribution
-it is possible to detect notable differences in the spectrum for
-different viewing angles.
+These results for these outgoing spectra are constructed by taking into
+account all outgoing photons regardless of the direction of
+propagation. In subsection \ref{subsec:direction} we report different
+statistics aiming at quantifying the changes in the observed spectra
+for observers with different viewing angles.
 
@@
 
-\begin{figure*}
-\includegraphics[width=0.45\textwidth]{Observers7t.png}
-\includegraphics[width=0.45\textwidth]{Observers7tHOM.png}
-\caption{Same as Figure \ref{fig:differentvelocities} but this time
-  the different lines show the line morphology for different polar angles
-  $\theta$ with respect to the rotation axis. In this case each photon
-  has a weight dependent on their outgoing direction. All spectra correspond
-  to the same $V_{\rm max}=300$\kms, Optical   Depth $\tau=10^{7}$ and
-  Central Distribution without dust.
-  \label{fig:differentobservers}}
-
-\end{figure*}
-
 In the following subsections we quantify the trends observed in
@@
 respect to the rotation angle, $\mu = \cos{\theta}$. All the results
-in this section will be expressed in terms of rest frame wavelength.
+in this section will be expressed in terms of the adimensional
+frequency $x$.
 
@@
     \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
-\caption{Log of the Average number of scatterings of the outgoing photons as function of the velocity. \label{fig:Nscatt}} 
+\caption{Log of the Average number of scatterings of the outgoing
+  photons as function of the velocity. \label{fig:Nscatt}}  
 \end{figure}
@@
      \includegraphics[width=0.40\textwidth]{2dHistogram300t5HOM.png}    
-
-    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous distribution, left for $V_{max}=0km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
+    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous
+      distribution, left for $V_{max}=0km/s $, right for
+      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
 \end{figure*}
@@
      \includegraphics[width=0.40\textwidth]{2dHistogram300t5.png}    
-
-    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central distribution, left for $V_{max}=50km/s $, right for $V_{max}=300km/s$ \label{fig:NscattHistoHOM}} 
+    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central
+      distribution, left for $V_{max}=50km/s $, right for
+      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
 \end{figure*}

### 2013-06-08 paper/Analisis.tex
Fig 1. fixed
updated results subsection on maxima

@@
 \newcommand{\hs}{{\hspace{1mm}}}  
-\newcommand{\kms}{\,km~s$^{-1}$}
+\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
 
@@
 
+\begin{figure*}
+  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
+  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
+\caption{Shape of the \ly line for
+    different velocities rotational velocities for spherical
+    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows the central
+    (homogeneous) photon distribution. All photons were taken into
+    account regardless of their propagation direction.
+  \label{fig:differentvelocities}}
+\end{figure*}
+
 The central result of this paper is summarized in
@@
 
-These results for these outgoing spectra are constructed by taking into
+In the following subsections we characterize the line morphology by
+the half-width at half intensity and the peak maxima. In order to
+intepret the morphological changes in the line we also report the
+median number of scatter for each \ly photon in the
+simulation. Finally we measure the bulk escape fraction as a function
+of rotational velocity in the presence of dust.
+
+All the results in this section are constructed by taking into
 account all outgoing photons regardless of the direction of
-propagation. In subsection \ref{subsec:direction} we report different
-statistics aiming at quantifying the changes in the observed spectra
-for observers with different viewing angles.
-
-\begin{figure*}
-  \includegraphics[width=0.45\textwidth]{7tDifSpeedsZ.png}
-  \includegraphics[width=0.45\textwidth]{7tHOMDifSpeeds1.png}
-\caption{Shape of the lyman alpha line for
-    different velocities. The left (right) panel shows the central
-    (homogeneous) photon distribution. All photons were taken into
-    account regardless of their outgoing direction of propagation.
-  \label{fig:differentvelocities}}
-\end{figure*}
-
-In the following subsections we quantify the trends observed in
-Fig. \ref{fig:differentvelocities} and
-Fig. \ref{fig:differentobservers} as a function of the maximum
-rotation velocity $V_{\rm max}$ and the position of the observer with
-respect to the rotation angle, $\mu = \cos{\theta}$. All the results
-in this section will be expressed in terms of the adimensional
-frequency $x$.
-
-First we quantify the line by its full width at half maximum
-(FWHM) and the peak positions. In order to interpret these results we
-measure how the rotation affects the average number of scatterings
-for each Lyman-alpha photon in the simulation. This help us to
-introduce the next subsection on the escape fraction in our models
-including dust. We conclude the section by estimating the
-expected line flux for top hat filters at a fixed center and varying
-width.
+propagation. In the next section \ref{subsec:direction} we quantify 
+the changes in the observed spectra for observers with different
+viewing angles.
 
@@
 
+The first quantitative conclusion of the effect of rotation in the
+\ly line is that double peaks broaden and reduce their intensity,
+while the line center rises. This procudes the impresion that, as the
+rotational velocity increases, the double peaks are merged into a
+single broad emission peak. This is msot evident in the highest
+rotational velocities for the homogeneously distributed sources
+(right panel in Fig.~\ref{fig:differentvelocities}).
+
+To quantify the line broadening we measure a modified version of the full
+width at half maximum (FWHM). Instead we measure it only for half of
+the line, $W_{1/2}$. This definition allows us to quantify the line
+width both in the cases of double and single peak emission.  In the
+case of double peaked emission $W_{1/2}$ corresponds to the width of a
+single peak, while in the extreme case of high rotational velocities,
+when the double peak is erased, it simply correspond to half FWHM.
+
+Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases with
+rotational velocity. Continous (dashed) lines connect the results for
+homogeneous (central) source distribution. The line width increases
+with rotational velocity up to factors of $\sim 2$ at $300$\kms with
+respect to the static case. For the temperature $T=10^4$K used in our
+radiative transfer calculations calculations the thermal velocity is
+$v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means that the
+half-width can increase up to $350$\kms (at $V_{\rm max}=300$\kms)
+compared to a half-width of $150$\kms in the static case.
+
 \begin{figure}
     \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
-\caption{Width of the lyman-alpha line for all the models.\label{fig:widthvsvelocity}}
+    \caption{Half-width for the non-dusty models as a function of
+      rotational velocity $V_{\rm max}$. Continous (dashed) lines
+      correspond to homogeneous (central) source
+      distributions. \label{fig:widthvsvelocity}} 
 \end{figure}
-
-The first quantitative conclusion of the effect of rotation in the
-Lyman alpha line is that the double peaks in the line tend to broaden
-until they reach a single broad emission peak. This is most evident in
-the case of Lyman-alpha sources homogeneously distributed in the gas
-distributions (Fig.~\ref{fig:differentvelocities} Right panel).
-
-To quantify the line broadening we measure a modified version of the full
-width at half maximum (FWHM) for half of the line, $W_{1/2}$. It means that in
-the case of double peaked emission, $W_{1/2}$ corresponds to the with
-one of the peaks, while in the extreme case when the line is converted
-into a single peak, $W_{1/2}$ corresponds to half of the full width.
-
-This definition allows us to quantify the line width both in the cases
-of double and single peak emission. Furthermore it has the advantage
-that this line width should have a direct observational correspondence
-to the observed line feature once the Inter-Galactic Medium (IGM)
-effects are taken into account, which have the central effect of
-strongly reducing the intensity of the blue peak of the line.
-
-Fig.~\ref{fig:widthvsvelocity} summarizes our findings for $W_{1/2}$
-as a function of $V_{\rm max}$. The line width increases with the
-rotational velocity of the gas cloud. This increase can be of a factor
-of $2-3$ with respect to the width with respect to the static
-case. This trend is conserved at all optical depths regardless of the
-initial source distribution.
-
-%Im not sure about this anymore---TALK to Jaime about this!
-This result includes all the outgoing photons, regardless of the
-position of the observer. In Figure~\ref{fig:widthvstheta} we
-take into account the different positions of the observer in the
-measurement of the half-width $W_{1/2}$. From this we conclude
-that observers with a line of sight perpendicular to the axis of
-rotation (i.e. edge-on in the case of spiral galaxy) tend to measure
-larger line widths than observers aligned with the rotation axis
-(i.e. face-on). The influence of the observer position on the line
-width, amounting always less than $15\%$ of a difference with respect
-to the result that takes into account all the outgoing photons with
-the same weight regardless of the relative observer position.
-
-%Both for central and homogeneous distribution of sources, We found a
-%dependency of the width with the rotation velocity of the gas cloud,
-%this results are summarize in Figure ~\ref{figure:width}. As velocity
-%increase also the equivalent width increase (for both homogeneous and
-%central distribSi Limonution), it means that some photons escape with fewer
-%scatterings than the static case but at the same time a few photons escape with% more scatterings, this can be seen clearly in
-%Figure. (Nscatt)\\
-
-%We also found a dependency with the viewing angles, in particular as
-%the angle incre ase the width also increase Figure
-%~\ref{fig:withvstheta}, this was also found in Verhemme et al. 2012
-%for a rotating disk but the pure effect of rotation can not been study
-%as it is in our case. Following the convention of Verhamme et al 2012
-%we define $\mu=cos(\theta)$, and we can make a polynomial fit for the
-%$FWHM(\mu)$ for our models, this is resumed in Table ~\ref{table:fits}
 
@@
     \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
-\caption{Position of the maxima
-    in the outgoing spectra for differents Rotational velocities,
-    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
+\caption{Position of the peak maxima as a function of rotational
+  velocity $V_{\rm max}$. Continous (dashed) lines correspond to
+  homogeneous (central) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:maximumsvsvelocity}}  
 \end{figure}
 
-The second feature in the line that we use to quantify the effect of
-rotation is the position of the line maxima. These provide information
-on the wavelength of the majority of the outgoing photons after
-they interact with the neutral hydrogen atoms in the gas cloud. If
-most of the photon escapes with a low number of scattering, its
-outgoing frequency will be close to its initial frequency, that is in
-the center of the line. On the contrary if the number of scatterings
-is large for the average photon, its outgoing frequency will be far
-from the line center. Such reasoning can be made more quantitative to
-understand the dependence of the peak maxima as a function of the
-hydrogen optical depth in the cloud [citation needed].
+Figure \ref{fig:maximumsvsvelocity} shows the position for the peak
+maxima as a function of the rotational velocity $V_{\rm max}$. This
+figure shows us clearly that in the case of central distributed
+sources there is barely any change with rotational velocity, at least
+in the range of explirea parameters. However, in the case of
+homogeneously emitted sources the maxima position remain close to
+constant until beyond some velocity threshold the line becomes single
+peaked with $x_{\rm max}=0$.
 
-In Fig.~\ref{fig:maximumsvsvelocity} we present the position
-of the maxima as a function of $V_{\rm max}$. For the photons emitted
-in the line center we do not find any variation in the position of the
-maxima in the range of explored parameter space (dash lines). However in the
-homogeneous case we can see how the maxima goes to $x_{m}=0$, meaning
-that the double peak is converted into a single peak.
+The transition to a single peak line most probably occurs for systems
+where it  becomes easier for the bulk of the photons to escape with the lowest
+number of scatterings possible, allowing them not to move very far
+from the center of the line. This hypothesis can also help to explain how the
+single peak stage is easily achieved in the homogeneous source
+distribution compared to the central distribution. In the homogeneous
+case there is a fraction of the photons that are inside a photosphere region with
+$\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical depth from
+the radius of emission to the sphere's surface. This conditions allows
+the photons to escape with much less scatterings compared to the
+photons emitted at the very center of the sphere. In turn, it gives
+the photons less scatterings to be placed far from the line
+center. Increasing the rotational velocity $V_{\rm max}$ reduces the
+optical depth making the  photosphere region effectively larger,
+increasing the number of photons escaping close to the lines's center.
 
-This transition to a single peak line occurs for the systems where it
-becomes easier for a bulk of the photons to escape with the lowest
-number of scatterings possible. This can explain how the single peak
-stage can be achieved in the homogeneous source distribution where
-there is fraction of the photons inside a photosphere region with
-$\tau_{H}\sim 1$ which allows them to escape within one
-scatter. Increasing the rotational velocity makes it easier for the
-photons in this photosphere region to escape.
-
-We also take into account the viewing angle $\mu$ for all the optical 
-depths and rotational velocities and the two different photon distribution.
-But we don't find any dependency meaning that the peaks would be placed in
-the same place no matter the position of an external observer.
-
-Finally we also report on the effect of the neutral Hydrogen
-optical depth $\tau_{H}$ on the maxima position $x_{m}$
-Fig.~\ref{fig:maximumsvsvelocity}. We find that, at fixed
-rotation velocity, the position of the maxima increases with optical
-depth as expected from basic theoretical considerations. We compare
-our results with the expected theoretical scaling for an infinite
-slab.
+For larger values of $\tau_{H}$ the transitional velocity $V_{\rm
+  trans}$ is also larger. In our models we find the following
+correspondance between the optical depth $\tau_{\rm H}=\{10^5, 10^6,
+10^7\}$ and the transitional velocities $V_{\rm
+  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be
+constrained to be in the range of velocities in the models that gave a $x_{\rm
+  max}\neq 0$ and $x_{\rm max}=0$.
 

### 2013-06-10 paper/Analisis.tex
some words on the average number of scatterings

@@
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
+\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
 \newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
@@
 figure shows us clearly that in the case of central distributed
-sources there is barely any change with rotational velocity, at least
-in the range of explirea parameters. However, in the case of
+sources there is barely any change with rotational velocity in the
+range of explored parameters. However, in the case of
 homogeneously emitted sources the maxima position remain close to
@@
 
-The transition to a single peak line most probably occurs for systems
+It is probable that the transition to a single peak line occurs for systems
 where it  becomes easier for the bulk of the photons to escape with the lowest
 number of scatterings possible, allowing them not to move very far
-from the center of the line. This hypothesis can also help to explain how the
+from the center of the line. This hypothesis can help to explain how the
 single peak stage is easily achieved in the homogeneous source
-distribution compared to the central distribution. In the homogeneous
-case there is a fraction of the photons that are inside a photosphere region with
-$\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical depth from
-the radius of emission to the sphere's surface. This conditions allows
-the photons to escape with much less scatterings compared to the
-photons emitted at the very center of the sphere. In turn, it gives
-the photons less scatterings to be placed far from the line
-center. Increasing the rotational velocity $V_{\rm max}$ reduces the
-optical depth making the  photosphere region effectively larger,
-increasing the number of photons escaping close to the lines's center.
+distribution. In this case there is a fraction of the photons that are
+inside a photosphere region with $\tau_{H,r}\ll \tau_{H}$ where
+$\tau_{H,r}$ is the optical depth from the radius of emission to the
+sphere's surface. This conditions allows the photons to escape with
+much less scatterings compared to the photons emitted at the very
+center of the sphere. In turn, it gives the photons less scatterings
+to be placed far from the line center. Increasing the rotational
+velocity $V_{\rm max}$ reduces the optical depth making the
+photosphere region effectively larger, increasing the number of
+photons escaping close to the lines's center. For the central case the
+photosphere is not present, and other mechanisms must be at play in
+the steady reduction of the double peak.
 
@@
 constrained to be in the range of velocities in the models that gave a $x_{\rm
-  max}\neq 0$ and $x_{\rm max}=0$.
+  max}\neq 0$ and $x_{\rm max}=0$.   In the next section explore the
+origin of this trends and consider to what extent the hypothesis of a low
+number of scatterings is correlated with the emergence of a single
+peak.
 
@@
 
-Until know we have focus in how rotation affect the morphology of the 
-Lyman alpha line, now we turn to study deeply the possible causes of 
-this effects. As recombination is the main cause of the emission of the 
-Lyman alpha line, it is important to study the relationship between the 
-number of times that a photon is absorbed and re emitted that we simply 
-take as scatterings with it's shift in the wavelength.
+The number of times that a \ly photon is absorbed and re-emmited is
+connected to the final frequency that it can have after escaping the
+galaxy. In the case of static gas geometries, a large value of the
+optical depth is immediatly followed by a high number of
+scatterings. In turn a large optical depth increases the probability
+that a \lya photon will be found far from the center of the line. The
+peak maxima shifting away form the line center as the amount of
+neutral hydrogen increases.
 
-As a first approach we study the number of scatterings of all the photons 
-at different velocities and for both photon distributions Figure~\ref{fig:Nscatt}. 
-For the central distribution we found that the average number of scattering 
-does not have a relevant change ($\sim 0.5\%$) with $V_{max}$, For the 
-Homogeneous distribution we found that as $V_{max}$ increase the average 
-number of scatterings decrease in a$\sim 39\%$, it means that rotation 
-makes photons to escape easier from the cloud. The reason why this is not 
-observed in the central distribution is because the amount of gas that every 
-photon has to break through is so large that the average number of scatterings 
-is large too, making the effect of rotation unobservable.
+In Figure \ref{fig:Nscatt} we see the average number of scatterings
+$\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
+$V_{\rm max}$. For the central distributions we find that there is not
+a significante change for increasing rotational
+velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
+for different velocities. In this case we also find that the average
+number of scatterings is proportional to the optical depth, as
+expected in analogy from the analytic result for the homogeneous
+infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
+\citep{Adams72,Harrington73}. In our experiments we find  $\langle N_{\rm
+  scatt}\rangle= XXX\tau_{\rm   H}$.
+
+However, for the homogeneous distribution there is a clear decrease of
+$\langle N_{\rm  scatt}\rangle$ as the  $V_{\rm max}$ increases. This
+effect more pronounced for the lower values of the optical depth. For
+$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
+$XX\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
+
+The analytic expectation for the slab with homogeneously emitted
+sources is $\langle N_{\rm  scatt}\rangle=1.16\tau_{\rm   H}$
+\citep{Harrington73}, a factor of $0.72$ lower than the case of the
+centrally emitted photons. In our case we find that for the static
+spheres this factor is $XXX$.
+
+%%%%%
 

### 2013-06-11 paper/Analisis.tex
Change name of addfig in Nscatt Section, from 2dHistogram50t5. to 2dHistogram0t5.
new paragraph in Nscatt section

@@
 
-In order to understand the effects of rotation in the morphology of the line
- we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the 
- central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution 
- Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower 
- velocities we found that for some value (put the value) of $N_{scatt}$ the 
- mayority of photons have a defined value of $X_{m}$. While for higher 
- velocities photons tend spread out in $X_{m}$(Make position analysis of 
- this photons).
-
-For the homogeneous distribution we found the same effect but also, for 
-highest velocities the mayority of the photons near the surface escape 
-with much less scatterings that in the static case. This analysis let us 
-conclude that rotation make photons escape with less scatterings and it 
-spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.
+In order to gain a deeper understading of these results we 2D
+histograms for the number of scaterrings as a function of the outgoing
+dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
+the results of such histogram in the case $\tau{\rm H}=10^5$ for the
+static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
+results for the homogeneous (central) source distribution. The color
+scale is logarithmic in the number of photons at a certain value
+$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
+the photosphere in the homogeneous distribution, in this case most of
+the photons that left with $x\sim 0$ have escaped with less than $10$
+scatterings, clearly explaining the origin of a single central
+peak. However, for a central distribution the situation is
+different. In this case the number of scatterings remains high, on the
+order of the optical depth, but the two peaks do get closer to each
+other. In this situation each scattering leaves the photon closer to
+the center of the line than the static case.
 
@@
 \begin{figure*}
-     \includegraphics[width=0.40\textwidth]{2dHistogram0t5HOM.png}
-     \includegraphics[width=0.40\textwidth]{2dHistogram300t5HOM.png}    
-    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous
-      distribution, left for $V_{max}=0km/s $, right for
-      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
+     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
+     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
+     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
+     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
+    \caption{2D histogram of $N_{scatt}$ vs $x$. The upper (lower) pannels
+      show the homogeneous (central) source distribution. Left
+      corresponds to the static case and the right
+      $V_{max}=300km/s$. The colour scale is locarithmic\label{fig:Nscatt2D}}  
 \end{figure*}
 
-\begin{figure*}
-     \includegraphics[width=0.40\textwidth]{2dHistogram50t5.png}
-     \includegraphics[width=0.40\textwidth]{2dHistogram300t5.png}    
-    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central
-      distribution, left for $V_{max}=50km/s $, right for
-      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
-\end{figure*}
-
+%%%%
 \subsection{Escape Fraction}

### 2013-06-11 paper/Analisis.tex
text in the escape fraction subsection

@@
 \newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-
 \newcommand{\LCDM}{$\Lambda$CDM~}
@@
     different velocities rotational velocities for spherical
-    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows the central
-    (homogeneous) photon distribution. All photons were taken into
-    account regardless of their propagation direction.
-  \label{fig:differentvelocities}}
+    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
+    the central    (homogeneous) photon distribution. All photons were
+    taken into     account regardless of their propagation
+    direction.    \label{fig:differentvelocities}}  
 \end{figure*}
@@
 \label{sec:widthpeak}
-\label{fig:differentvelocities}
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
+    \caption{Half-width for the non-dusty models as a function of
+      rotational velocity $V_{\rm max}$. Continous (dashed) lines
+      correspond to homogeneous (central) source
+      distributions. \label{fig:widthvsvelocity}} 
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
+\caption{Position of the peak maxima as a function of rotational
+  velocity $V_{\rm max}$. Continous (dashed) lines correspond to
+  homogeneous (central) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:maximumsvsvelocity}}  
+\end{figure}
 
@@
 compared to a half-width of $150$\kms in the static case.
-
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
-    \caption{Half-width for the non-dusty models as a function of
-      rotational velocity $V_{\rm max}$. Continous (dashed) lines
-      correspond to homogeneous (central) source
-      distributions. \label{fig:widthvsvelocity}} 
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
-\caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continous (dashed) lines correspond to
-  homogeneous (central) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
-  peaked. \label{fig:maximumsvsvelocity}}  
-\end{figure}
 
@@
 
+\begin{figure}
+    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
+\caption{Logarithm of the average number of scatterings as function of
+  the velocity. \label{fig:Nscatt}}   
+\end{figure}
+
+\begin{figure*}
+     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
+     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
+     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
+     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}
+
+    \caption{2D histogram of $N_{scatt}$ vs $x$. The upper (lower) pannels
+      show the homogeneous (central) source distribution. Left
+      corresponds to the static case and the right
+      $V_{max}=300km/s$. The colour scale is locarithmic\label{fig:Nscatt2D}}  
+\end{figure*}
+
 The number of times that a \ly photon is absorbed and re-emmited is
@@
 centrally emitted photons. In our case we find that for the static
-spheres this factor is $XXX$.
+spheres this factor is $xxxx$.
 
-%%%%%
-
-In order to gain a deeper understading of these results we 2D
+In order to gain a deeper understanding of these results we 2D
 histograms for the number of scaterrings as a function of the outgoing
@@
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
-\caption{Log of the Average number of scatterings of the outgoing
-  photons as function of the velocity. \label{fig:Nscatt}}  
-\end{figure}
-
-\begin{figure*}
-     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
-     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
-     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
-     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
-    \caption{2D histogram of $N_{scatt}$ vs $x$. The upper (lower) pannels
-      show the homogeneous (central) source distribution. Left
-      corresponds to the static case and the right
-      $V_{max}=300km/s$. The colour scale is locarithmic\label{fig:Nscatt2D}}  
-\end{figure*}
-
-%%%%
-\subsection{Escape Fraction}
-\label{sec:EF}
-
-Until now we have studied models in absence of dust, but is known (REFERENCE) 
-that there is presence of dust in high redshift galaxies. Our models with 
-dust are treated as is explained in detail in  the appendix of (Forero et al 2011).
-
-Of particular interest is to compute the escape fraction of Lyman $\alpha$ 
-photons coming from the most distant galaxies, due to the fact that with the 
-observed intensity of the Lyman alpha line quantities as the LF and SFR can 
-be derived (put some references).
-
-Previous studies have shown the correlation of the Escape fraction with galactic 
-mass (Laursen et al 2009, Dayal et al 2010) abundances and the kinematics of dust. 
-In order to study pure rotational effects in the escape fraction we fixed the dust 
-abundance $\tau_{A}=0.01$ and the galaxy mass. We compute the escape fraction for 
-the models described in Table \ref{table:models}.
-
-For a realistic model we also take into account the viewing angle, first we fixed 
-the viewing angle at $\theta = 0$  Fig.~\ref{figure:efvsv} and then we fixed the 
-velocity in order to see the escape fraction correlation with the viewing angle. 
-Therefore we define the escape fraction as:\\
-
-\begin{equation}
-F_{e}=\dfrac{\Sigma_{NI} \vec{k}\cdot \vec{o}}{\Sigma_{NF}\vec{k}\cdot \vec{o}}
-\end{equation}
-
-Where NI is the initial number of photons and NF is the final,
-$\vec{k}$ is the rotation axis direction and ${o}$ the observer
-direction. With this definition we compute the escape fraction for all
-of our models, the results are presented in Fig \ref{figure:efvsv}\\
+\subsection{Dusty Clouds: Escape Fraction}
+\label{sec:escapefraction}
 
@@
   \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
-   \caption{Escape fraction for all the models. continious lines represent the homogenous models, while dashed lines represent the central models}\label{figure:efvsv}
+   \caption{Escape fraction as a function of rotational velcity. The
+     continous (dashed) lines correspond to homogeneous (central)
+     models.
+     \label{fig:efvsv}}
 \end{figure}
-
-In Figure \ref{figure:efvsv} we found that in the central distribution
-the escape fraction does not change with velocity while it does in the
-optical depth (See Verhamme 2006, an argument about this). On the other
-hand for the homogeneous distribution we
-found that for higher velocities photons escape easily. The difference
-between this two results rely in the fact that in the homogeneous
-distribution photons are emitted closer to the escape surface and this
-makes this configuration more sensitive to rotation while in the
-central configuration the escape fraction depends mainly in the amount
-of gas rather than in rotation.
-
-As a final test we compare our results with the analytical solution of 
-the slab developed by (Neufeld 1990) Fig. ~\ref{figure:efvsNeufeld}, as 
-the geometry we use is different from the one described for Neufeld, we 
-dont expect the same results, in fact we found that for the homogenous 
-sphere the escape fraction is higer than the slab (see ref, mark). Also 
-we notest that for $\tau<10^{6}$ the escape fraction does not increase 
-as it will be expected, This is due to the fact that the condition 
-$a\tau_{h}>>\tau_{d}$ in not valid any more.
 
@@
   \includegraphics[width=0.45\textwidth]{Neufeld.png}
- \label{figure:efvsNeufeld}\caption{Escape fraction of this work
-   compared with Neufeld analytical solution}  
+ \label{fig:efvsNeufeld}\caption{Escape fraction as a function of the
+   product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
+   the infinite is slab shown as a continous line. Different dashed
+   lines correspond to different rotational velocities.}   
 \end{figure}
 
-\subsection{The Case of Asymmetric Emission}
+If there is a change in the number of scatterings with rotational
+velocity, there must be a change in the probability of being absorbed
+if dust is present. We study how rotation impacts the escape fraction
+of \ly photons.
 
-As we know there is unlikely to find galaxies with radiation sources 
-distributed homogeneously. Most of them are in a clumpy distribution 
-(Laursen et al 2013*) which affected the resulting spectra. In order 
-to study an inhomogeneous distribution we set up a model in which we 
-select certain photons that are placed in a specific place but that 
-are not symmetrically distributed Fig.~\ref{figure:distributions} shows
-the distributions we set up.
+Taking into account the results in the previous section, we do not expect any
+change in the case of central distributions given that the average
+number of scatterings remain constant. On the other hand, in the
+homogeneous distribution there is a considerable drop in the number of
+scatterings as $V_{\rm max}$ increases, this preconditions the escape
+fraction to increase as well.
 
-\begin{figure}
-  \includegraphics[width=0.40\textwidth]{Distribution.png}
-  \caption{Inhomogeneous distributions of 
- photons, Blue area represents the photons in distribution 1 while red
- area are the selected photons for distribution 2. The arrow points to
- the observer position\label{figure:distributions}}  
-\end{figure}
+Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
+a function of rotational velocity. This Figure illustrates how our
+reasoning in the previous paragraph is correct. The escape fraction
+barely changes for the central source distribution, while it rises
+as the velocity $V_{\rm max}$ increases for the homogeneous case. The
+velocity has a higher relative impact in the models with low optical
+depth $\tau_{\rm H}=10^5$,$10^{6}$, where it can raise from $xxx$ in
+the static case up to $xxx$ at $V_{\rm rot}=300$\kms.
 
-In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
-distribution 1 and 2, the first effect we see is the asymmetry of the
-double peak, in the homogeneous and central distribution we see double
-peaks with the same height, while in this case one peak is higher than 
-the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
-peak is higher than the redshifted, and for distribution 2 the redshifted
-peak is the highest.
+In Figure \ref{fig:efvsNeufeld} we put these results in the context of
+the analytical solution for the infinite slab \citep{Neufeld90} shown
+by the continous line. In this setup the analytic solution depends
+solely on the product $(a\tau_{\rm   H})^{1/3}\tau_{a}$. This valid
+only in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
+\ref{fig:efvsNeufeld} corespond to the cases of different
+velocities. We observe that in all cases the escape fraction is higher
+than in the slab configuration. We also note that for $\tau_{\rm H}=10^{5}$
+the escape fraction does not increase as expected, This is
+due to the fact that the condition $a\tau_{h}\gg 1$ does not hold.
 
-An other important fact here is the asymmetry of the spectra with respect 
-to the line center, in particular photons selected in distribution 1 
-present a blueshift in their spectra while photons selected in distribution 
-2 present a redshift. This effect becomes stronger as velocity increase 
-~\ref{figure:inhomogeneous}
+\subsection{Different line of sights}
 
-\begin{figure*}
-  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
-  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
- \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ ,
-   (left) with $\tau=10^5$, (right) with
-   $\tau=10^6$\label{figure:inhomogeneous}}  
-\end{figure*}
+\subsection{Off-Centered emission}
 
-\subsection{Integrated flux in a narrowband filter}
+%As we know there is unlikely to find galaxies with radiation sources 
+%distributed homogeneously. Most of them are in a clumpy distribution 
+%(Laursen et al 2013*) which affected the resulting spectra. In order 
+%to study an inhomogeneous distribution we set up a model in which we 
+%select certain photons that are placed in a specific place but that 
+%are not symmetrically distributed Fig.~\ref{figure:distributions} shows
+%the distributions we set up.
 
-Until now we have shown the main effects of gas and dust rotation in
-the Ly$\alpha$ line morphology such as the escape fraction, the FWHM,
-the maxima position, also we see that shape of the outgoing spectra
-depends on the position of the observer. It is important to see if
-rotational effects are detectable in observational methods involving
-the Ly$\alpha$ line.
+%\begin{figure}
+%  \includegraphics[width=0.40\textwidth]{Distribution.png}
+%  \caption{Inhomogeneous distributions of 
+% photons, Blue area represents the photons in distribution 1 while red
+% area are the selected photons for distribution 2. The arrow points to
+% the observer position\label{figure:distributions}}  
+%\end{figure}
 
-One of the most used methods to detect high redshift galaxies using
-the Ly$\alpha$ line is using a narrowband selection, we make this
-analysis based on the results obtained by Steidel (2011) in this work
-(EXPLAIN a lit of bit more about their work) they used tree narrowband
-filters for tree different redshifts resumed in
-Table~\ref{table:NBfilters}, We want to know how much the integrated
-flux change due to rotational effects in this NB filters, for the
-models we simulated with CLARA.
+%In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
+%distribution 1 and 2, the first effect we see is the asymmetry of the
+%double peak, in the homogeneous and central distribution we see double
+%peaks with the same height, while in this case one peak is higher than 
+%the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
+%peak is higher than the redshifted, and for distribution 2 the redshifted
+%peak is the highest.
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{cccc}\hline
-Model & SSA22a 4980/80   & HS1549 4667/80 & HS1700 4018/90\\
-\hline
-\end{tabular}
-\caption{
-Fluxes for tree different narrow band filters.
-} 
-\label{table:NBfilters}
-\end{center}
-\end{table*}
+%An other important fact here is the asymmetry of the spectra with respect 
+%to the line center, in particular photons selected in distribution 1 
+%present a blueshift in their spectra while photons selected in distribution 
+%2 present a redshift. This effect becomes stronger as velocity increase 
+%~\ref{figure:inhomogeneous}
 
-In table \ref{table:NBfilters} we present the results of the flux in
-every  narrowband filter for the homogeneous model at different
-velocities and hydrogen  optical depth $\tau_{0}$. As is well known an
-increase in the optical depth makes  the line peaks separation
-bigger. In fact for some cases the line width is larger  than the NB
-filer width fig.(put ref fig) for those cases we modify the redshift
-in the available range in order to make the peak maxima match the NB
-filter center.  For all cases we found that as velocity increase the
-flux is less.
+%\begin{figure*}
+%  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
+%  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
+% \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ ,
+%   (left) with $\tau=10^5$, (right) with
+%   $\tau=10^6$\label{figure:inhomogeneous}}  
+%\end{figure*}
 
-In the case of the dusty model we found the same trend of the flux
-with the velocity  but in this cases the effect is no that strong.  We
-also found some dependency with the viewing angle.
+%\subsection{Integrated flux in a narrowband filter}
 
-\begin{figure}
-  \includegraphics[width=0.45\textwidth]{NB7tDifVHOM.png}
- \label{figure:efvsNeufeld}\caption{NB filter located at the center of
-   the maxima, with different redshift}  
-\end{figure}
+%Until now we have shown the main effects of gas and dust rotation in
+%the Ly$\alpha$ line morphology such as the escape fraction, the FWHM,
+%the maxima position, also we see that shape of the outgoing spectra
+%depends on the position of the observer. It is important to see if
+%rotational effects are detectable in observational methods involving
+%the Ly$\alpha$ line.
+
+%One of the most used methods to detect high redshift galaxies using
+%the Ly$\alpha$ line is using a narrowband selection, we make this
+%analysis based on the results obtained by Steidel (2011) in this work
+%(EXPLAIN a lit of bit more about their work) they used tree narrowband
+%filters for tree different redshifts resumed in
+%Table~\ref{table:NBfilters}, We want to know how much the integrated
+%flux change due to rotational effects in this NB filters, for the
+%models we simulated with CLARA.
+
+%\begin{table*}
+%\begin{center}
+%\begin{tabular}{cccc}\hline
+%Model & SSA22a 4980/80   & HS1549 4667/80 & HS1700 4018/90\\
+%\hline
+%\end{tabular}
+%\caption{
+%Fluxes for tree different narrow band filters.
+%} 
+%\label{table:NBfilters}
+%\end{center}
+%\end{table*}
+
+%In table \ref{table:NBfilters} we present the results of the flux in
+%every  narrowband filter for the homogeneous model at different
+%velocities and hydrogen  optical depth $\tau_{0}$. As is well known an
+%increase in the optical depth makes  the line peaks separation
+%bigger. In fact for some cases the line width is larger  than the NB
+%filer width fig.(put ref fig) for those cases we modify the redshift
+%in the available range in order to make the peak maxima match the NB
+%filter center.  For all cases we found that as velocity increase the
+%flux is less.
+
+%In the case of the dusty model we found the same trend of the flux
+%with the velocity  but in this cases the effect is no that strong.  We
+%also found some dependency with the viewing angle.
+
+%\begin{figure}
+%  \includegraphics[width=0.45\textwidth]{NB7tDifVHOM.png}
+% \label{figure:efvsNeufeld}\caption{NB filter located at the center of
+%   the maxima, with different redshift}  
+%\end{figure}
 
@@
 ... Comparison with Verhamme et al. results on the rotation
+
 ... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha
@@
 interpretation of galaxy observations in the Lyman alpha line.
+
 ..compare steidel et al (2011)
+
 % taking into account equivalent widths results with narrow band

### 2013-06-28 paper/Analisis.tex
A Better Plots
updated in latex

@@
 \newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
-\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
 \newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
@@
 The first quantitative conclusion of the effect of rotation in the
-\ly line is that double peaks broaden and reduce their intensity,
-while the line center rises. This procudes the impresion that, as the
+\ly line is that double peaks broaden and reduce their intensity
+while the line center rises. This produces the impresion that, as the
 rotational velocity increases, the double peaks are merged into a
@@
      \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
-     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
+     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png} 
      \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
@@
 
-In order to gain a deeper understanding of these results we 2D
+In order to gain a deeper understanding of these results we prepare 2D
 histograms for the number of scaterrings as a function of the outgoing
@@
 
-If there is a change in the number of scatterings with rotational
-velocity, there must be a change in the probability of being absorbed
-if dust is present. We study how rotation impacts the escape fraction
-of \ly photons.
+We also study a dusty cloud configuration to measure the effect of
+rotation on the escape fraction. We expect that the modified number of
+scatterings to be reflected in this amount of photons aborbed by
+dust. Following this line of thought,  we do not expect any change in
+for a dusty cloud with central source of radiation given that the
+number of scatterings remains close to constant. On the other hand, in
+the case of an homogenous radiation source the number of scatterings
+drops as $V_{\rm max}$ increases, which might be reflected as an
+increasing escape farction.
 
-Taking into account the results in the previous section, we do not expect any
-change in the case of central distributions given that the average
-number of scatterings remain constant. On the other hand, in the
-homogeneous distribution there is a considerable drop in the number of
-scatterings as $V_{\rm max}$ increases, this preconditions the escape
-fraction to increase as well.
+%If there is a change in the number of scatterings with rotational
+%velocity, there must be a change in the probability of being absorbed
+%if dust is present. We study how rotation impacts the escape fraction
+%of \ly photons.
+
+%Taking into account the results in the previous section, we do not expect any
+%change in the case of central distributions given that the average
+%number of scatterings remain constant. On the other hand, in the
+%homogeneous distribution there is a considerable drop in the number of
+%scatterings as $V_{\rm max}$ increases, this preconditions the escape
+%fraction to increase as well.
 
 Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
-a function of rotational velocity. This Figure illustrates how our
-reasoning in the previous paragraph is correct. The escape fraction
-barely changes for the central source distribution, while it rises
-as the velocity $V_{\rm max}$ increases for the homogeneous case. The
-velocity has a higher relative impact in the models with low optical
-depth $\tau_{\rm H}=10^5$,$10^{6}$, where it can raise from $xxx$ in
-the static case up to $xxx$ at $V_{\rm rot}=300$\kms.
+a function of the maximum rotational velocity, confirming that our
+intuitions in this respect is correct. For the central source
+distribution the escape fraction barely shows any change, while for
+the homogeneous case there is a clear rise in the escape fraction for
+high rotational velocities.  Rotation has a higher relative impact in
+the models with low optical depth $\tau_{\rm H}=10^5$,$10^{6}$, where
+it can raise from $xxx$ in the static case up to $xxx$ at $V_{\rm
+  rot}=300$\kms.
+
+%This Figure illustrates how our
+%reasoning in the previous paragraph is correct. 
+%The escape fraction
+%barely changes for the central source distribution, while it rises
+%as the velocity $V_{\rm max}$ increases for the homogeneous case.
 

### 2013-06-28 paper/Analisis.tex
update to the escape fraction section

@@
 \begin{figure}
-  \includegraphics[width=0.45\textwidth]{EscapeFraction.png}
+  \includegraphics[width=0.45\textwidth]{escapefraction.png}
    \caption{Escape fraction as a function of rotational velcity. The
@@
 In Figure \ref{fig:efvsNeufeld} we put these results in the context of
-the analytical solution for the infinite slab \citep{Neufeld90} shown
-by the continous line. In this setup the analytic solution depends
-solely on the product $(a\tau_{\rm   H})^{1/3}\tau_{a}$. This valid
-only in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
+the analytical solution for the infinite slab \citep{Neufeld90}. In
+Neufeld's setup the analytic solution depends solely on the product
+$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
+in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
 \ref{fig:efvsNeufeld} corespond to the cases of different
-velocities. We observe that in all cases the escape fraction is higher
-than in the slab configuration. We also note that for $\tau_{\rm H}=10^{5}$
-the escape fraction does not increase as expected, This is
-due to the fact that the condition $a\tau_{h}\gg 1$ does not hold.
+velocities. We observe that the escape fraction is higher
+by factors of $2-10$  than the expected values for the slab
+configuration. We also see that for the lower value $\tau_{\rm
+  H}=10^{5}$ the escape fraction does not increase with respect to the
+solution for $\tau_{\rm H}=10^{6}$ as expected, however we not that we
+are in a regime where the condition for the analytic expectations 
+($a\tau_{h}\gg 1$) does not hold.
 

### 2013-07-03 paper/Analisis.tex
corrected some typos

@@
 An ab-initio description of realistic rotation curves in simulations
-depends on having access to the dynamic evoluction the mass components
+depends on having access to the dynamic evolution the mass components
 in the galaxy: stars, gas and dark matter. Such level of realism is
-extremely complex to achive, specially of one wants to get a
+extremely complex to achieve, specially of one wants to get a
 systematic description based on statistics of simulated objects.
@@
 Following the tradition of studies of Lyman$\alpha$ emitting systems,
-we implement a model with a simplified geoemtry and gas
+we implement a model with a simplified geometry and gas
 distribution. We assume that the gas is homogeneously distributed in a
@@
  define the position of each photon. The origin of this system
- coincides withthe center of the sphere and the rotation axis is defined
+ coincides with the center of the sphere and the rotation axis is defined
  to be $z$-axis. With this choice, the components of the gas bulk velocity
@@
 varying the line of sight of a mock observer with respect to the
-rotation axis. The results are parameterized by the polar angle
+rotation axis. The results are parametrized by the polar angle
 $\theta$ as defined by the dot product $\cos\theta =
@@
 rotational velocity $V_{\rm max}$, hydrogen optical depth $\tau_{H}$,
-dust optical depth $\tau_{a}$ and the initial disitrbution of photons
+dust optical depth $\tau_{a}$ and the initial distribution of photons
 with respect to the gas. There are in total 60 models with the input
@@
 showing that the influence of rotation is present both when the
-photons are either homogeneusly or centrally initialized over the gas
+photons are either homogeneously or centrally initialized over the gas
 volume.
@@
 the half-width at half intensity and the peak maxima. In order to
-intepret the morphological changes in the line we also report the
+interpret the morphological changes in the line we also report the
 median number of scatter for each \ly photon in the
@@
     \caption{Half-width for the non-dusty models as a function of
-      rotational velocity $V_{\rm max}$. Continous (dashed) lines
+      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
       correspond to homogeneous (central) source
@@
 \caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continous (dashed) lines correspond to
+  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
   homogeneous (central) source distributions. A value of $x_{\rm
@@
 \ly line is that double peaks broaden and reduce their intensity
-while the line center rises. This produces the impresion that, as the
+while the line center rises. This produces the impression that, as the
 rotational velocity increases, the double peaks are merged into a
-single broad emission peak. This is msot evident in the highest
+single broad emission peak. This is most evident in the highest
 rotational velocities for the homogeneously distributed sources
@@
 Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases with
-rotational velocity. Continous (dashed) lines connect the results for
+rotational velocity. Continuous (dashed) lines connect the results for
 homogeneous (central) source distribution. The line width increases
@@
   trans}$ is also larger. In our models we find the following
-correspondance between the optical depth $\tau_{\rm H}=\{10^5, 10^6,
+correspondence between the optical depth $\tau_{\rm H}=\{10^5, 10^6,
 10^7\}$ and the transitional velocities $V_{\rm
@@
 
-The number of times that a \ly photon is absorbed and re-emmited is
+The number of times that a \ly photon is absorbed and re-emitted is
 connected to the final frequency that it can have after escaping the
 galaxy. In the case of static gas geometries, a large value of the
-optical depth is immediatly followed by a high number of
+optical depth is immediately followed by a high number of
 scatterings. In turn a large optical depth increases the probability
@@
 $V_{\rm max}$. For the central distributions we find that there is not
-a significante change for increasing rotational
+a significant change for increasing rotational
 velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
@@
 In order to gain a deeper understanding of these results we prepare 2D
-histograms for the number of scaterrings as a function of the outgoing
+histograms for the number of scatterings as a function of the outgoing
 dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
@@
   \includegraphics[width=0.45\textwidth]{escapefraction.png}
-   \caption{Escape fraction as a function of rotational velcity. The
-     continous (dashed) lines correspond to homogeneous (central)
+   \caption{Escape fraction as a function of rotational velocity. The
+     continuous (dashed) lines correspond to homogeneous (central)
      models.
@@
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
-   the infinite is slab shown as a continous line. Different dashed
+   the infinite is slab shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.}   
@@
 rotation on the escape fraction. We expect that the modified number of
-scatterings to be reflected in this amount of photons aborbed by
+scatterings to be reflected in this amount of photons absorbed by
 dust. Following this line of thought,  we do not expect any change in
@@
 number of scatterings remains close to constant. On the other hand, in
-the case of an homogenous radiation source the number of scatterings
+the case of an homogeneous radiation source the number of scatterings
 drops as $V_{\rm max}$ increases, which might be reflected as an
-increasing escape farction.
+increasing escape fraction.
 
@@
 in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
-\ref{fig:efvsNeufeld} corespond to the cases of different
+\ref{fig:efvsNeufeld} correspond to the cases of different
 velocities. We observe that the escape fraction is higher

### 2013-08-01 paper/Analisis.tex
Some typos

@@
 in the galaxy: stars, gas and dark matter. Such level of realism is
-extremely complex to achieve, specially of one wants to get a
+extremely complex to achieve, specially if one wants to get a
 systematic description based on statistics of simulated objects.
@@
 respect to the static case. For the temperature $T=10^4$K used in our
-radiative transfer calculations calculations the thermal velocity is
+radiative transfer calculations the thermal velocity is
 $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means that the
@@
 dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
-the results of such histogram in the case $\tau{\rm H}=10^5$ for the
+the results of such histogram in the case $\tau_{\rm H}=10^5$ for the
 static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
@@
   \includegraphics[width=0.45\textwidth]{Neufeld.png}
- \label{fig:efvsNeufeld}\caption{Escape fraction as a function of the
+ \caption{Escape fraction as a function of the
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
    the infinite is slab shown as a continuous line. Different dashed
-   lines correspond to different rotational velocities.}   
+   lines correspond to different rotational velocities.
+   \label{fig:efvsNeufeld}}   
 \end{figure}

### 2013-08-13 paper/Analisis.tex
Nscatt section, minor calc. finished

@@
 $\nu_{\alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
-frequency,  $\Delta_{\alpha} \equiv
+frequency,  $\Delta\nu_{\alpha} \equiv
 \nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th} $ is the doppler
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{WidthvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{WidthVvsVmax.png}
     \caption{Half-width for the non-dusty models as a function of
@@
 scatterings. In turn a large optical depth increases the probability
-that a \lya photon will be found far from the center of the line. The
+that a \ly photon will be found far from the center of the line. The
 peak maxima shifting away form the line center as the amount of
@@
 \citep{Adams72,Harrington73}. In our experiments we find  $\langle N_{\rm
-  scatt}\rangle= XXX\tau_{\rm   H}$.
+  scatt}\rangle= (1.505, 1.002, 0.918)\tau_{\rm   H}$, for $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
 
@@
 $\tau_{\rm H}=10^5$ the average number of scatterings decreases by
-$XX\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
+$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
 
@@
 centrally emitted photons. In our case we find that for the static
-spheres this factor is $xxxx$.
+spheres this factor is $(1.510553, 1.002823, 0.9188793)$ for $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
 

### 2013-08-16 paper/Analisis.tex
some edits

@@
 
-\title[Rotation in the Lyman-$\alpha$ line]{Rotation effects on the
-  Lyman-$\alpha$ line morphology in distant galaxies}
+\title[Rotation in the Lyman-$\alpha$ line]{The impact of gas bulk
+  rotation on the Lyman-$\alpha$ line} 
 \author[Garavito-Camargo, Forero-Romero \& Dijkstra]{
@@
 highest redshifts. In this paper we present for the first time
-radiative transfer calculations that show the impact of rotation on
-the morphology of the Lyman $\alpha$ line. To this end we construct
-simplified models where a galaxy is modeled as an homogeneous sphere
-composed as an homogeneous mixture of dust and hydrogen at a constant
-temperature. These spheres have a solid-body rotation with linear
-velocities at the surface in the range $0-300$ \kms. We consider
-radiation sources both in the center of the rotating cloud and also
-homogeneously distributed around the sphere. We find that higher
-rotational velocities increase the width of each peak in the outgoing
-line profile while it also increases the amount of Lyman alpha photons
-escaping in the line center. This trends makes that for high
-rotational velocities and large Hydrogen optical depths the double
-peak of the line tends to be erased an be replaced by a single peak the
-lines center. This is more pronounced for radiation sources
-homogeneously distributed. Concerning the escape fraction we find that
-rotation does not have any effect, provided that all the sources are
-centrally emitted. However in the case of homogeneously emitted
-sources we measure an increase of about a factor of $2$ in the escape
-fraction for higher rotational velocity values. 
-Our work shows clearly that gas rotation has a non negligible impact
-on the shape of the Lyman $\alpha$ line. 
+radiative transfer calculations that show the impact of gas bulk rotation on
+the morphology of the Lyman $\alpha$ line. To this end we model a
+galaxy as an homogeneous sphere composed as an homogeneous mixture of
+dust and hydrogen at a constant temperature. These spheres have a
+solid-body rotation with linear velocities at the surface in the range
+$0-300$ \kms and neutral hydrogen optical depths in the range
+$\tau_{\rm H}=10^{5}-10^{7}$. We consider radiation sources both in
+the center of the rotating cloud and also homogeneously distributed in
+the volume. We find that higher rotational velocities increase the
+width of each peak in the outgoing line profile while it also
+increases the amount of Lyman alpha photons escaping in the line
+center. This trends makes that for high rotational velocities and
+large Hydrogen optical depths the double peak of the line tends to be
+erased an be replaced by a single peak a the line center. This trend
+is more pronounced for radiation sources homogeneously
+distributed. Concerning the escape fraction we find that rotation does
+not have any effect, provided that all the sources are centrally
+emitted. However, in the case of homogeneously emittedsources we
+measure an increase of about a factor of $2$ in the escape  fraction
+for higher rotational velocity values. This work shows that gas bulk
+rotation has a non negligible impact on the shape of the Lyman
+$\alpha$ line.   
 \end{abstract}
@@
 
-Due to the resonant nature of the Lyman alpha line, gas kinematics
-play an important role shaping its morphology...
+[Due to the resonant nature of the Lyman alpha line, gas kinematics
+play an important role shaping its morphology.]
 
-There is an extensive literature studying the influence of
+[Line morphology is being measured observationally.]
+
+[There is an extensive literature studying the influence of
 outflow/inflow configurations in the shape of the outgoing Lyman-alpha
-line...
+line.]
+
+[Rotation is present in high redshift galaxies.]
 
@@
 Describing the kinematics of gas rotation in all generality is a
-complex task. There is great variation in the shape of the rotation
-curve as observed in HI emission as a function of the distance to the
-galaxy center. However there are two features that are observed very
-often. First, in the central region the velocity increases
-proportional to the radius following the behaviour in a body with
-solid rotation. Second, beyond a certain radius the rotation curve
-tends to flatten. Furthermore, a thorough observational account of gas
-rotation in the redshifts of interest for the study of LAEs ($z>1.0$)
-is still missing.
+complex task, specially at high redshifts where there is still missing
+a thorough observational account of rotation in galaxies beyond
+$z>1.0$. Furthermore, at low redshifts it has been observed a great
+variation in the shape of the rotation curve as observed in HI
+emission as a function of the distance to the galaxy center. However
+there are two features that are observed very often. First, in the
+central region the velocity increases proportional to the radius,
+following the behaviour in a body with solid rotation. Second, beyond
+a certain radius the rotation curve tends to flatten.
 
 An ab-initio description of realistic rotation curves in simulations
-depends on having access to the dynamic evolution the mass components
+depends on having access to the dynamic evolution of all mass components
 in the galaxy: stars, gas and dark matter. Such level of realism is
@@
 In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
-numerical photons through different spherical galaxies, each one
-varying in at least one of the following parameters: the maximum
-rotational velocity $V_{\rm max}$, hydrogen optical depth $\tau_{H}$,
-dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are in total 60 models with the input
-parameters summarized in Table \ref{table:models}.
+numerical photons through different spherical galaxies. Each galaxy
+model varies at least one of the following parameters: the maximum
+rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
+the dust optical depth $\tau_{a}$ and the initial distribution of photons
+with respect to the gas. There are in total 60 models combining all
+the input parameters summarized in Table \ref{table:models}.
+
+We have used two independently developed Monte Carlo codes
+\citep{CLARA,DijkstraKramer} to perform the calculations of the
+non-dusty models. The results we report here are robust in the sense
+that they are obtained by both codes.
 
@@
 \caption{
-List of the physical parameters that define the spherical models we
-have simulated using Monte Carlo calculations. For each parameter we
+  List of the physical parameters that define the spherical models 
+  imulated using Monte Carlo calculations. For each parameter we
   vary the values in the range listed in the last column. Takig into

### 2013-08-16 paper/Analisis.tex
number of scatterings

@@
 
-To quantify the line broadening we measure a modified version of the full
-width at half maximum (FWHM). Instead we measure it only for half of
+To quantify the line broadening we use a modified version of the full
+width at half maximum (FWHM). We measure it only for half of
 the line, $W_{1/2}$. This definition allows us to quantify the line
-width both in the cases of double and single peak emission.  In the
+width and see the transition from double to single peak emission.  In the
 case of double peaked emission $W_{1/2}$ corresponds to the width of a
@@
 maxima as a function of the rotational velocity $V_{\rm max}$. This
-figure shows us clearly that in the case of central distributed
+Figure shows us clearly that in the case of central distributed
 sources there is barely any change with rotational velocity in the
@@
 
-It is probable that the transition to a single peak line occurs for systems
+The transition to a single peak line occurs for systems
 where it  becomes easier for the bulk of the photons to escape with the lowest
 number of scatterings possible, allowing them not to move very far
-from the center of the line. This hypothesis can help to explain how the
-single peak stage is easily achieved in the homogeneous source
-distribution. In this case there is a fraction of the photons that are
-inside a photosphere region with $\tau_{H,r}\ll \tau_{H}$ where
-$\tau_{H,r}$ is the optical depth from the radius of emission to the
-sphere's surface. This conditions allows the photons to escape with
-much less scatterings compared to the photons emitted at the very
-center of the sphere. In turn, it gives the photons less scatterings
-to be placed far from the line center. Increasing the rotational
-velocity $V_{\rm max}$ reduces the optical depth making the
-photosphere region effectively larger, increasing the number of
-photons escaping close to the lines's center. For the central case the
-photosphere is not present, and other mechanisms must be at play in
-the steady reduction of the double peak.
+from the center of the line. This explains how the single peak stage
+is easily achieved in the homogeneous source distribution. In this
+case there is a fraction of the photons that are inside a photosphere
+region with $\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical
+depth from the radius of emission to the sphere's surface. This
+conditions allows the photons to escape with much less scatterings
+compared to the photons emitted at the very center of the sphere. In
+turn, it gives the photons less scatterings to be placed far from the
+line center. Increasing the rotational velocity $V_{\rm max}$ reduces
+the optical depth making the photosphere region effectively larger,
+increasing the number of photons escaping close to the lines's
+center. For the central case the photosphere is not present, and other
+mechanisms must be at play in the steady reduction of the double peak.
 
-For larger values of $\tau_{H}$ the transitional velocity $V_{\rm
-  trans}$ is also larger. In our models we find the following
-correspondence between the optical depth $\tau_{\rm H}=\{10^5, 10^6,
-10^7\}$ and the transitional velocities $V_{\rm
-  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be
-constrained to be in the range of velocities in the models that gave a $x_{\rm
+For larger values of $\tau_{H}$ the transition to a single peaked
+emission occurs for larger values of the rotation velocity. In our
+models we find the following correspondence between the optical depth
+$\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional velocities $V_{\rm
+  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be constrained to be in the range of velocities in the models that gave a $x_{\rm
   max}\neq 0$ and $x_{\rm max}=0$.   In the next section explore the
-origin of this trends and consider to what extent the hypothesis of a low
-number of scatterings is correlated with the emergence of a single
-peak.
+origin of this trends and show to what extent a low number of
+scatterings is correlated with the emergence of a single peak.
 
@@
 
-    \caption{2D histogram of $N_{scatt}$ vs $x$. The upper (lower) pannels
+    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) pannels
       show the homogeneous (central) source distribution. Left
       corresponds to the static case and the right
-      $V_{max}=300km/s$. The colour scale is locarithmic\label{fig:Nscatt2D}}  
+      $V_{max}=300km/s$. The colour scale is logarithmic on the
+      number of photons with given values of $N_{\rm scatt}$ and
+      $x$. \label{fig:Nscatt2D}}   
 \end{figure*}
@@
 scatterings. In turn a large optical depth increases the probability
-that a \ly photon will be found far from the center of the line. The
-peak maxima shifting away form the line center as the amount of
+that a \ly photon to be found far from the center of the line. In this
+case, the peak maxima shift away form the line center as the amount of
 neutral hydrogen increases.
 
-In Figure \ref{fig:Nscatt} we see the average number of scatterings
+In Figure \ref{fig:Nscatt} we show the average number of scatterings
 $\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
@@
 infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}. In our experiments we find  $\langle N_{\rm
-  scatt}\rangle= (1.505, 1.002, 0.918)\tau_{\rm   H}$, for $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
+\citep{Adams72,Harrington73}. In our experiments we find  that for the
+static spheres with centraly distributed sources $\langle N_{\rm
+  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$. for optical depths
+$\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$
 
-However, for the homogeneous distribution there is a clear decrease of
-$\langle N_{\rm  scatt}\rangle$ as the  $V_{\rm max}$ increases. This
-effect more pronounced for the lower values of the optical depth. For
-$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
-$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
+Figure \ref{fig:Nscatt} shows that for the homogeneous distribution
+there is a clear decrease of $\langle N_{\rm  scatt}\rangle$ as the
+$V_{\rm max}$ increases. This effect more pronounced for the lower
+values of the optical depth. For $\tau_{\rm H}=10^5$ the average
+number of scatterings decreases by $61\%$ at $V_{\rm max}=300\kms$ in
+comparison to the static case.
 
@@
 centrally emitted photons. In our case we find that for the static
-spheres this factor is $(1.510553, 1.002823, 0.9188793)$ for $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
+, while for homogeneously distributed source $\langle N_{\rm
+  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$. {\bf seguro ????}
 

### 2013-08-16 paper/Analisis.tex
finished with Nscatt section

@@
 the photons that left with $x\sim 0$ have escaped with less than $10$
-scatterings, clearly explaining the origin of a single central
+scatterings, explaining the origin of a single central
 peak. However, for a central distribution the situation is
@@
 order of the optical depth, but the two peaks do get closer to each
-other. In this situation each scattering leaves the photon closer to
-the center of the line than the static case.
+other. In this case the physical picture is that each scattering, due
+to the bulk velocity of the gas, is inefficient in driving the photon
+outside the line center.
 

### 2013-08-19 paper/Analisis.tex
Chcked homogeneous Nscatt factors

@@
 , while for homogeneously distributed source $\langle N_{\rm
-  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$. {\bf seguro ????}
+  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents 
+  a factor of $(0.66, 0.59, 0.51)$ lower than the centrally emitted photons.
 

### 2013-09-02 paper/Analisis.tex
Fixed peak maxima plot in the paper
short paragram on anisotripic emission

@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{maximumvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{maximumVvsVmax.png}
 \caption{Position of the peak maxima as a function of rotational
@@
 
-\subsection{Different line of sights}
+\subsection{Anisotropic emission}
+
+We study the deviations of the received flux on the surface of the
+sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
+observer located at an angle $\Theta$ (distant observer angle)
+normalized to the isotropic flux:
+
+\begin{equation}
+F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
+\end{equation}
+%
+where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+$\Delta N$ is the number of photons in a angular bin $\Delta
+\Theta$. This definition satifies the condition
+$int_{-1}^{1}F(\mu)d\mu/2=1$.
+
+In Figure 2 we show the angular dependencty of the flux for the
+central (left) and homogeneous (right) source distributions. This
+shows that observers at different directions would infer luminosities
+different from the isotropical value only at levels $< 3\%$.
 

### 2013-09-02 paper/Analisis.tex
Updated escape fraction section

@@
 the models with low optical depth $\tau_{\rm H}=10^5$,$10^{6}$, where
-it can raise from $xxx$ in the static case up to $xxx$ at $V_{\rm
+it can raise from $(0.26, 0.28)$ respectively in the static case up to $(0.37, 0.39)$ at $V_{\rm
   rot}=300$\kms.
@@
 $\Delta N$ is the number of photons in a angular bin $\Delta
-\Theta$. This definition satifies the condition
+\Theta$. This definition satisfies the condition
 $int_{-1}^{1}F(\mu)d\mu/2=1$.
 
-In Figure 2 we show the angular dependencty of the flux for the
+In Figure 2 we show the angular dependency of the flux for the
 central (left) and homogeneous (right) source distributions. This

### 2013-09-03 paper/Analisis.tex
first paragraph in the introduction. added some references

@@
 
-[Due to the resonant nature of the Lyman alpha line, gas kinematics
-play an important role shaping its morphology.]
+The detection of strong \ly emission lines has become an essential
+method in extragalactic astronomy to find distant star-forming
+galaxies
+\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}. The
+galaxies detected using this method receive the 
+name of \ly emitters (LAEs). A detailed examination of this galaxy
+population has diverse implications for galaxy formation, reonization
+and the large scale structure of the Universe. Attempts to fully
+exploit the physical information included in the \ly line require an
+understading of all the physical factor sinvolved in shaping the
+line. Due to the resonant nature of this line, these physical factors
+include temperature, density and bulk velocity field of the neutral
+Hydrogen in the emitting galaxy and its surroundings.
 
@@
 $\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional velocities $V_{\rm
-  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be constrained to be in the range of velocities in the models that gave a $x_{\rm
-  max}\neq 0$ and $x_{\rm max}=0$.   In the next section explore the
+  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be
+constrained to be in the range of velocities in the models that gave a
+$x_{\rm max}\neq 0$ and $x_{\rm max}=0$.   In the next section explore the
 origin of this trends and show to what extent a low number of

### 2013-09-04 paper/Analisis.tex
one more paragraph full of historical references

@@
 galaxies
-\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}. The
-galaxies detected using this method receive the 
+\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}.
+The galaxies detected using this method receive the 
 name of \ly emitters (LAEs). A detailed examination of this galaxy
@@
 exploit the physical information included in the \ly line require an
-understading of all the physical factor sinvolved in shaping the
+understading of all the physical factors involved in shaping the
 line. Due to the resonant nature of this line, these physical factors
@@
 
-[Line morphology is being measured observationally.]
+A basic understanding for the quantitative behaviour of the \ly line
+has been reached through analytical studies in the case of a static
+configurations, such as uniform slabs
+\citep{Harrington73,Neufeld90} and  uniform spheres
+\citep{Dijkstra06}. Analytical studies of configurations including
+some kind of bulk flow only include the case of a sphere with a Hubble
+like expansion flow \citep{LoebRybicki}.
+
+A more detailed quantification of the \ly line has been reached using
+Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. In the last
+two decades these studies have become more popular due to the
+availability of computing power. Early into the 21st century the first
+studies focused on on homogeneous and static media
+\citep{Ahn00,Ahn01,Zheng02}. Later on the effects of clumpy media
+\citep{Hansen06} and expanding/contracting shell/spherical geometries started to
+be studied \citep{Verhamme06,Dijkstra06}. Similar codes have applied
+these results to semi-analytical models of galaxy formation \citep{Orsi12} and
+results of large hydrodynamical simulations
+\citep{CLARA,Forero-Romero12}. Recently Monte Carlo codes have also
+been applied to the results of high resolution hydrodynamical
+simulations \citep{Laursen09,Yajima12}.
+
+. In this
+context a lot of attention has been paid to effects that might induce
+asymmetric line profiles and to the estimation of the escape fraction in the presence of dust.
+
+The bulk gas velocity
+plays a central role in the theoretical studies of the \ly line.
 

### 2013-09-05 paper/Analisis.tex
one more couple of references
a couple of paragraphs in the introduction. added new references

@@
 results of large hydrodynamical simulations
-\citep{CLARA,Forero-Romero12}. Recently Monte Carlo codes have also
+\citep{CLARA,Forero12,Behrens13}. Recently Monte Carlo codes have also
 been applied to the results of high resolution hydrodynamical
-simulations \citep{Laursen09,Yajima12}.
+simulations \citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Recent developments have been
+focused on the study of clumpy outflows \citep{DijkstraKramer}and
+anisotropic velocity configurations \citep{Zheng2013}.
 
-. In this
-context a lot of attention has been paid to effects that might induce
-asymmetric line profiles and to the estimation of the escape fraction in the presence of dust.
+The recent studies of galaxies in hydrodynamical simulations
+\citep{Laursen09,Barnes11,Verhamme12,Yajima12} have all shown
+systematic variations in the \ly line with the viewing angle. These
+variations are a complex superpositions of anisotropic density
+configurations (i.e. edge-on vs. face-on view of a galaxy), the
+inflows observaed by gas cooling and the outflows included in the
+supernova feedback process of the simulation. These bulk flows
+physically correspond to the circumgalactic and intergalactic medium
+(CGM and IGM). These effects have been systematically studied
+different anisotropic models of hydrogen clouds  varying the density
+and wind characteristics \citep{Zheng2013}.
 
-The bulk gas velocity
-plays a central role in the theoretical studies of the \ly line.
+However, in all these systematics efforts the effect of rotation, which is an ubiquitous
+feature in galaxies, has not been systematically studied. The
+processing of the \ly photons in a rotating interstellar medium (ISM)
+must have an impact in the line morphology. It is necessary to investigate to
+what extent bulk gas rotation has an measurable impact in the \ly
+alpha line.
 
-[There is an extensive literature studying the influence of
-outflow/inflow configurations in the shape of the outgoing Lyman-alpha
-line.]
-
-[Rotation is present in high redshift galaxies.]
-
-In this paper we study for the first time the impact of rotation on
-the morphology of the Lyman $\alpha$ line. To isolate the effects of
-rotation we focus on a simple system: the gas distribution is
-spherical, with homogeneous density and the gas rotates as a solid
-body. We base our work on two independent Monte Carlo based radiative
-transfer codes CLARA \citep{CLARA} and XX \citep{DijkstraKramer}.
+Performing that study is the main goal of this paper. We study for the
+first time the impact of rotation on the morphology of the Lyman
+$\alpha$ line. We focus on a simplified system, a spherical gas claud
+with homogeneous density and solid body rotation. We base our work on two independent Monte
+Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
+\citep{DijkstraKramer} .
 

### 2013-09-06 paper/Analisis.tex
first version of the introduction

@@
 
-However, in all these systematics efforts the effect of rotation, which is an ubiquitous
-feature in galaxies, has not been systematically studied. The
-processing of the \ly photons in a rotating interstellar medium (ISM)
-must have an impact in the line morphology. It is necessary to investigate to
-what extent bulk gas rotation has an measurable impact in the \ly
-alpha line.
+However, in all these systematics efforts the effect of rotation,
+which is an ubiquitous feature in galaxies, has not been
+systematically studied. The processing of the \ly photons in a
+rotating interstellar medium (ISM) must have an impact in the line
+morphology. It is necessary to investigate to what extent bulk gas
+rotation has an measurable impact in the \ly alpha line.
 
-Performing that study is the main goal of this paper. We study for the
+Performing that study is the main goal of this paper. We investigate for the
 first time the impact of rotation on the morphology of the Lyman
-$\alpha$ line. We focus on a simplified system, a spherical gas claud
-with homogeneous density and solid body rotation. We base our work on two independent Monte
-Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
+$\alpha$ line. We focus on a simplified system, a spherical gas cloud
+with homogeneous density and solid body rotation. We focus our study
+on the line morphology, anisotropic integrated emission and the escape
+fraction in the presence of dust. We base our work on two independent
+Monte Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
 \citep{DijkstraKramer} .
 
-This paper is paper is structured as follows...
+This paper is paper is structured as follows. In \S
+\ref{sec:implementation} we present the implementation of bulk
+rotation into the Monte Carlo codes, paying special attention to coordinate
+definitions. There we also list the different physical parementers in
+the simulated grid of models. In the next section we present the
+results of the simulations, with special detail to quantities in the
+line that show a clear evolution as a function of the cloud's
+rotational velocity. In \S \ref{sec:dicussion} we discuss the
+implications of our results in the interpretation of LAEs
+observations and further refinements that can be implemented in the
+theoretical modelling of the \ly line. In the last section we preset
+our conclusiones.
 
@@
 \section{Conclusions}
+\label{sec:conclusions}
 In this paper we have estimated the effects of gas bulk rotation on

### 2013-09-08 paper/Analisis.tex
New flux plots in anisotropic emission subsection

@@
 
-In Figure 2 we show the angular dependency of the flux for the
+In Figure \ref{fig:flux} we show the angular dependency of the flux for the
 central (left) and homogeneous (right) source distributions. This
@@
 different from the isotropical value only at levels $< 3\%$.
+
+\begin{figure*}
+\includegraphics[scale=0.3]{mu_central.png}
+\includegraphics[scale=0.3]{mu_homogeneous.png}
+\caption{Flux angular dependency for the central (left) and homogeneous
+(right) source distributions, different line widths illustrate different
+rotational velocities.
+   \label{fig:flux}} 
+\end{figure*}
 

### 2013-09-09 paper/Analisis.tex
updated section 2

@@
 
-\section{Modeling Bulk Gas Rotation}
+\section{Models of bulk gas rotation}
 \label{sec:implementation}
@@
  In the MonteCarlo code we define a cartesian coordinate system to
- define the position of each photon. The origin of this system
+ describe the position of each photon. The origin of this system
  coincides with the center of the sphere and the rotation axis is defined
@@
 
-In contrast with spherically symmetric models (static, outflow,
-inflow) the rotation now defines a preferred direction in the
-problem. In Section \ref{sec:results} we quantify this differences by
-varying the line of sight of a mock observer with respect to the
-rotation axis. The results are parametrized by the polar angle
-$\theta$ as defined by the dot product $\cos\theta =
-{\hat{u}\cdot\hat{k}}$.
+For each photon in the simulation we have its initial position inside
+the sphere, direction of propagation $\hat{k}_{in}$ and reduced
+frequency $x_{in}$. The photon's propagation stops once they cross the
+surface of the sphere. At this point we store the position, the outgoing direction
+of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
+define the angle $\Theta$ by $\cos\Theta = \hat{k}\cdot
+\hat{k}_{out}$, that is the polar angle of the outgoing photon with
+respect to the $z$ axis. Following \cite{Zheng2013} we make the study
+of the anisotropic emission in terms of this angle $\Theta$.
 
@@
 In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
-numerical photons through different spherical galaxies. Each galaxy
-model varies at least one of the following parameters: the maximum
+numerical photons through different spherical galaxies. For each galaxy
+we vary at least one of the following parameters: the maximum
 rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
 the dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are in total 60 models combining all
-the input parameters summarized in Table \ref{table:models}.
+with respect to the gas. There are in total $60$ models combining all
+the input parameters. Table \ref{table:models} presents a summary of
+all the models.
 
-We have used two independently developed Monte Carlo codes
-\citep{CLARA,DijkstraKramer} to perform the calculations of the
+Additionally, we have used two independently developed Monte Carlo
+codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
 non-dusty models. The results we report here are robust in the sense
@@
   List of the physical parameters that define the spherical models 
-  imulated using Monte Carlo calculations. For each parameter we
+  simulated in our Monte Carlo calculations. For each parameter we
   vary the values in the range listed in the last column. Takig into
   account all the possible combinations we end up with $60$ different
-  models. } 
+  models.} 
 \label{table:models}

### 2013-09-09 paper/Analisis.tex
minor changes in off center emission

--- 2013-09-08 paper/Analisis.tex
@@
 \Theta$. This definition satisfies the condition
-$int_{-1}^{1}F(\mu)d\mu/2=1$.
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.
 
@@
 
-%As we know there is unlikely to find galaxies with radiation sources 
-%distributed homogeneously. Most of them are in a clumpy distribution 
-%(Laursen et al 2013*) which affected the resulting spectra. In order 
-%to study an inhomogeneous distribution we set up a model in which we 
-%select certain photons that are placed in a specific place but that 
-%are not symmetrically distributed Fig.~\ref{figure:distributions} shows
-%the distributions we set up.
+As we know there is unlikely to find galaxies with radiation sources 
+distributed homogeneously. Most of them are in a clumpy distribution 
+(Laursen et al 2013*) which affected the resulting spectra. In order 
+to study an inhomogeneous distribution we set up a model in which we 
+select certain photons that are placed in a specific place but that 
+are not symmetrically distributed Fig. shows the distributions we 
+set up, basically we take photons located in a sphere of $0.5 R$ and 
+we moved $0.2 R$ in the x axis.
 
@@
 %the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
-%peak is higher than the redshifted, and for distribution 2 the redshifted
+%peak is higher than the reds~\ref{figure:distributionshifted, and for distribution 2 the redshifted
 %peak is the highest.

### 2013-09-12 paper/Analisis.tex
down to section 3.1

@@
     the central (homogeneous) photon distribution. All photons were
-    taken into     account regardless of their propagation
-    direction.    \label{fig:differentvelocities}}  
+    taken into  account regardless of their final direction of propagation.
+    \label{fig:differentvelocities}}  
 \end{figure*}
 
-The central result of this paper is summarized in
-Fig.~\ref{fig:differentvelocities} that shows clearly the considerable
+The central result of this paper is summarized in Figure
+\ref{fig:differentvelocities}. It shows the considerable
 impact of rotation on the morphology of the emergent \ly line. Both
@@
 median number of scatter for each \ly photon in the
-simulation. Finally we measure the bulk escape fraction as a function
-of rotational velocity in the presence of dust.
-
-All the results in this section are constructed by taking into
-account all outgoing photons regardless of the direction of
-propagation. In the next section \ref{subsec:direction} we quantify 
-the changes in the observed spectra for observers with different
-viewing angles.
+simulation. For the models where dust is included we measure the bulk
+escape fraction as a function of rotational velocity. Finally, we make
+an estimate of the anisotriopic emission of the models in comparison
+with static spheres.
 
@@
 rotational velocity increases, the double peaks are merged into a
-single broad emission peak. This is most evident in the highest
+single broad emission peak. This is most evident at the highest
 rotational velocities for the homogeneously distributed sources
-(right panel in Fig.~\ref{fig:differentvelocities}).
+(right panel in Figure \ref{fig:differentvelocities}).
 
@@
 rotational velocity. Continuous (dashed) lines connect the results for
-homogeneous (central) source distribution. The line width increases
-with rotational velocity up to factors of $\sim 2$ at $300$\kms with
-respect to the static case. For the temperature $T=10^4$K used in our
-radiative transfer calculations the thermal velocity is
-$v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means that the
-half-width can increase up to $350$\kms (at $V_{\rm max}=300$\kms)
-compared to a half-width of $150$\kms in the static case.
+homogeneous (central) source distribution. For the temperature
+$T=10^4$K used in our radiative transfer calculations the thermal
+velocity is $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means
+that the half-width can increase up to $350$\kms (at $V_{\rm
+  max}=300$\kms) compared to a half-width of $150$\kms in the static
+case.
 
@@
 maxima as a function of the rotational velocity $V_{\rm max}$. This
-Figure shows us clearly that in the case of central distributed
+Figure clearly shows that in the case of central distributed
 sources there is barely any change with rotational velocity in the
@@
 constant until beyond some velocity threshold the line becomes single
-peaked with $x_{\rm max}=0$.
+peaked with $x_{\rm max}=0$ \kms.
 
-The transition to a single peak line occurs for systems
+The transition to a single peak line seems to occur for systems
 where it becomes easier for the bulk of the photons to escape with the lowest
 number of scatterings possible, allowing them not to move very far
-from the center of the line. This explains how the single peak stage
+from the center of the line. This might explain how the single peak stage
 is easily achieved in the homogeneous source distribution. In this
@@
 turn, it gives the photons less scatterings to be placed far from the
-line center. Increasing the rotational velocity $V_{\rm max}$ reduces
+line center.
+
+Increasing the rotational velocity $V_{\rm max}$ reduces
 the optical depth making the photosphere region effectively larger,
 increasing the number of photons escaping close to the lines's
-center. For the central case the photosphere is not present, and other
-mechanisms must be at play in the steady reduction of the double peak.
+center. In our models we find the following correspondence between the
+optical depth $\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional
+velocities $V_{\rm   trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$
+which can only be constrained to be in the range of velocities in the
+models that gave a $x_{\rm max}\neq 0$ and $x_{\rm max}=0$.
 
-For larger values of $\tau_{H}$ the transition to a single peaked
-emission occurs for larger values of the rotation velocity. In our
-models we find the following correspondence between the optical depth
-$\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional velocities $V_{\rm
-  trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$ which can only be
-constrained to be in the range of velocities in the models that gave a
-$x_{\rm max}\neq 0$ and $x_{\rm max}=0$.   In the next section explore the
-origin of this trends and show to what extent a low number of
-scatterings is correlated with the emergence of a single peak.
+For the central emission the transition to a single peak is never
+completed in the range of parameters explored here. The nonappearence
+of a single peak phase can be in part explained to the absence of a
+photosphere, as is the case in the homogeneous
+distribution. Nevertheless, there is a rise in the intensity at the
+line center as the rotational velocity increases. This hints that the
+encounters with a nonstatic medium are inefficient in changing a
+photons' frequency outside the line center.
+
+In the next section we quantify the number of scatterings and explore
+to what extent this is related to the emergence of single peak.
 
@@
 \caption{Logarithm of the average number of scatterings as function of
-  the velocity. \label{fig:Nscatt}}   
+  the velocity. Continuous/dashed lines represent an
+  homogeneous/central distribution of sources. \label{fig:Nscatt}}    
 \end{figure}

### 2013-09-16 paper/Analisis.tex
New text & plots in off-center section

@@
 
+As a primer approach we study the angular dependency in the same manner as
+we do in section(). In Fig. \ref{fig:OCflux} the angular for two different
+off-center distribution the bold line shows an off center sphere located
+at $0.5 R$ of the homogeneous sphere, while the narrow line shows sphere 
+located at $0.25 R$. This is done for the model with $\tau=10^{5}$ and 
+$V=50 km s^{-1}$, we find that the maximum change in flux would be up to.
+
+\begin{figure}
+\includegraphics[scale=0.3]{mu_OC.png}
+\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
+off-center positions.
+   \label{fig:OCflux}} 
+\end{figure}
+
+The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
+is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
+they are the most sensitive to rotational velocities. We found that off-center emission 
+would generate asymmetric spectra, in particular depending in the location of the 
+sphere the double peak would came out with different heights.
+
+\begin{figure}
+\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
+\caption{Spectra for two off-center spheres
+   \label{fig:OCspectra}} 
+\end{figure}
+
 %\begin{figure}

### 2013-09-17 paper/Analisis.tex
New plot showing the Off center set up

@@
 select certain photons that are placed in a specific place but that 
-are not symmetrically distributed Fig. shows the distributions we 
+are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
 set up, basically we take photons located in a sphere of $0.5 R$ and 
 we moved $0.2 R$ in the x axis.
+
+\begin{figure}
+\includegraphics[scale=0.3]{OF_spheres.png}
+\caption{The two solid circles show up the photons we select in order to make the anisotropic emission
+		rotation is defined to be $\mathrm{z}$-axis. we also select photons in the negative side of 				        $\mathrm{x}$ (dashed circles) in order to see the complete effect of rotation. 
+   \label{fig:OCspheres}} 
+\end{figure}
 

### 2013-09-25 paper/Analisis.tex
minor changes in conclusions

@@
 rotation increase also the width increase in a factor of $2-3$ in comparison 
-with the static case. We also take into account the influence of the observer 
+with the static case. 'We also take into account the influence of the observer 
 viewing angle, we found that observers with a line of sight perpendicular  
 to the axis of rotation measure a $15\%$ larger line width than those 
-aligned with the rotation axis.
+aligned with the rotation axis.'
 
-As many observational spectra Ly$\alpha$ emission line (Kulas et al)
+As many observational spectra Ly$\alpha$ emission line (Kulas et al, Yamada et al)
 is double  peaked, these peaks provide important information
@@
 
-As an application of these results we compute the integrated flux
-taking into account the narrow band filters used by (Steidel et al
-2011), for our models we found an important decrease up to $~40\%$ for
-the homogeneous models, and up to $22\%$ for the dusty homogeneous
-models in the flux as velocity increase.  Also we calculate at what
-redshift should the filter be in order to get the maximum  flux, and
-for the tree filters we get values that rely in the filter redshift
-range. This effects would have a relevant implication at the time to
-find high redshift galaxies.
+%As an application of these results we compute the integrated flux
+%taking into account the narrow band filters used by (Steidel et al
+%2011), for our models we found an important decrease up to $~40\%$ for
+%the homogeneous models, and up to $22\%$ for the dusty homogeneous
+%models in the flux as velocity increase.  Also we calculate at what
+%redshift should the filter be in order to get the maximum  flux, and
+%for the tree filters we get values that rely in the filter redshift
+%range. This effects would have a relevant implication at the time to
+%find high redshift galaxies.
 

### 2013-09-30 paper/Analisis.tex
Two more paragraphs in off-center emission

@@
 set up, basically we take photons located in a sphere of $0.5 R$ and 
-we moved $0.2 R$ in the x axis.
+we choose two speheres in each side of the $\hat{\textbf{x}}$ axis
+two at $0.25 R$ and the other two at $0.5 R$
 
@@
 is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
-they are the most sensitive to rotational velocities. We found that off-center emission 
-would generate asymmetric spectra, in particular depending in the location of the 
-sphere the double peak would came out with different heights.
-
+they are the most sensitive to rotational velocities.
 \begin{figure}
@@
 \end{figure}
+
+There are two new morphological featueres that off-center emission in 
+rotating galaxies produces. First in some of our models with especific 
+values of velocity and opitcal depth an asymmetry in the peak heights 
+is presented, those off-center spheres \textit{(put image reference)} 
+located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
+present a higher peak in the redshifted part, while those spheres located
+at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
+we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.
+This can be apreciated for both set of spheres at $0.25 R$ and $0.5 R$,
+ but the effect shows a stronger asymmetry for spheres located at $0.25 R$
+ this due to the fact that photons escaping from this spheres goes through 
+ a larger hidrogen medium than photons located in the spheres at $0.5 R$.
+%poner valores de velocidad y optical depth porcentaje de asimetria
+
+Also for all the off-center models we found that the $Ly\alpha$ line 
+width ...
+
+Also for photons located in the spheres at $0.5 R$, we found that for 
+some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
+the line presents three peaks (blue-shifted, centered, red-shifted). In order to gain a better interpretation of this three peaks trend we run this models with $N_{\gamma} = 10^6$.
 
@@
 
-... Comparison with Verhamme et al. results on the rotation
+... Comparison with Verhamme et al. results on the rotation (Viewing angle)
 
@@
 ..compare steidel et al (2011)
+
+% BUSCAR asimetrias en observaciones, KUlas, YAMADA  off-center emission
 

### 2013-10-01 paper/Analisis.tex
New ideas in discussion + one paragraph

@@
 
+Following the classification of $Ly\alpha$ profiles made for (Kulas et al, put reference) 
+we divide our results in $3$ different groups. Group I represents profiles in which the flux in the red side 
+is stronger that in the blue part, while Group II represents profiles in which the blue side
+is the stronger. Group III represents single peaked profiles while Group IV represents multipeaked  
+profiles.
+
+Group I profiles may be explained in our model when off-center emission is present and the location 
+of this photons emission is stronger in the , while Group II profiles correspond to emissions in the ..
+
+Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\
 ... Comparison with Verhamme et al. results on the rotation (Viewing angle)
@@
 
-% BUSCAR asimetrias en observaciones, KUlas, YAMADA  off-center emission
+% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail observaciones, Kulas, YAMADA  off-center emission
 

### 2013-10-03 paper/Analisis.tex
More text in off-center emission specialy in the angular dependency part

@@
 are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
-set up, basically we take photons located in a sphere of $0.5 R$ and 
-we choose two speheres in each side of the $\hat{\textbf{x}}$ axis
-two at $0.25 R$ and the other two at $0.5 R$
+set up, basically we take photons located in a sphere of $0.5 R$ where
+$R$ is the radii of the homogeneous sphere and 
+we choose two spheres in each side of the $\hat{\textbf{x}}$ axis
+two at $0.25 R$ and the other two at $0.5 R$.
 
@@
 As a primer approach we study the angular dependency in the same manner as
-we do in section(). In Fig. \ref{fig:OCflux} the angular for two different
-off-center distribution the bold line shows an off center sphere located
-at $0.5 R$ of the homogeneous sphere, while the narrow line shows sphere 
-located at $0.25 R$. This is done for the model with $\tau=10^{5}$ and 
-$V=50 km s^{-1}$, we find that the maximum change in flux would be up to.
+we do in section \ref{sec:results}, but with the set up of the off-center models
+where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis,  the observer is 
+located at . In Fig. \ref{fig:OCflux} the angular 
+dependency for two different off-center distribution are shown. the bold line  
+represents an off center sphere located at $0.25 R$ in the homogeneous sphere, while 
+the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
+with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
+show exactly the same trend. We find a high dependency in the viewing angle,
+in particular observers at .
 
@@
 The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
-is shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
-they are the most sensitive to rotational velocities.
+are shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
+they are most sensitive to the effect of rotation.
+
 \begin{figure}
@@
 
-There are two new morphological featueres that off-center emission in 
-rotating galaxies produces. First in some of our models with especific 
-values of velocity and opitcal depth an asymmetry in the peak heights 
+There are two new morphological features that off-center emission in 
+rotating galaxies produces. First in some of our models with specific 
+values of velocity and optical depth an asymmetry in the peak heights 
 is presented, those off-center spheres \textit{(put image reference)} 
@@
 we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.
-This can be apreciated for both set of spheres at $0.25 R$ and $0.5 R$,
+
+This can be appreciated for both set of spheres at $0.25 R$ and $0.5 R$,
  but the effect shows a stronger asymmetry for spheres located at $0.25 R$
  this due to the fact that photons escaping from this spheres goes through 
- a larger hidrogen medium than photons located in the spheres at $0.5 R$.
+ a larger hydrogen medium than photons located in the spheres at $0.5 R$.
 %poner valores de velocidad y optical depth porcentaje de asimetria
@@
 Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\
+
 ... Comparison with Verhamme et al. results on the rotation (Viewing angle)
@@
 %ideas:
-Keep in mind making a follow up paper on the results of Yamada et atl
+Keep in mind making a follow up paper on the results of Yamada et al
 http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line
-morphology at z=3.1. How many of t hese laes can be considered to have
+morphology at z=3.1. How many of these laes can be considered to have
 rotation features? In principle, all of then should have them. How to

### 2013-10-03 paper/Analisis.tex
Paragraph about mu anular dependency

@@
 we do in section \ref{sec:results}, but with the set up of the off-center models
-where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis,  the observer is 
-located at . In Fig. \ref{fig:OCflux} the angular 
-dependency for two different off-center distribution are shown. the bold line  
-represents an off center sphere located at $0.25 R$ in the homogeneous sphere, while 
+where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
+located at $\mathrm{\theta = \pi/2}$. In Fig. \ref{fig:OCflux} the angular 
+dependency for two different off-center distribution are shown. The bold line  
+represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
 the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
 with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
-show exactly the same trend. We find a high dependency in the viewing angle,
-in particular observers at .
+show exactly the same trend. We find a high dependency in the viewing angle
+in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
+at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
+galaxies are oriented in random directions which implies that off-center emission
+is not going to be observed in all the observed galaxies.
 
@@
 located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
-present a higher peak in the redshifted part, while those spheres located
+present a higher peak in the red-shifted part, while those spheres located
 at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
-we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ where one peak is $20\%$ higher than the other.
+we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ 
+where one peak is $20\%$ higher than the other.
 

### 2013-10-13 paper/Analisis.tex
Delelted OC_5t_vel100.jpg

@@
 
-\begin{figure}
-\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
-\caption{Spectra for two off-center spheres
-   \label{fig:OCspectra}} 
-\end{figure}
+%\begin{figure}
+%\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
+%\caption{Spectra for two off-center spheres
+%   \label{fig:OCspectra}} 
+%\end{figure}
 
@@
 
-... Comparison with Verhamme et al. results on the rotation (Viewing angle)
+Comparing with the sample of (Kulas et al) we observe that rotational effects could be 
+associated in group IV and V in galaxies where the difference between the two peaks is 
+small and .
 
-... Compare with Kulas et al (Figure 3), Rotation on the lyman alpha
-line convert double peak profiles into a single one. comments about
-rotation with inflows and outflows.
+No effects asociated with inflows or outflows
 

### 2013-10-14 paper/Analisis.tex
Merged Anisotropic emission section with Off-center section

@@
 
-\subsection{Anisotropic emission}
-
-We study the deviations of the received flux on the surface of the
-sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
-observer located at an angle $\Theta$ (distant observer angle)
-normalized to the isotropic flux:
-
-\begin{equation}
-F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
-\end{equation}
-%
-where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
-$\Delta N$ is the number of photons in a angular bin $\Delta
-\Theta$. This definition satisfies the condition
-$\int_{-1}^{1}F(\mu)d\mu/2=1$.
-
-In Figure \ref{fig:flux} we show the angular dependency of the flux for the
-central (left) and homogeneous (right) source distributions. This
-shows that observers at different directions would infer luminosities
-different from the isotropical value only at levels $< 3\%$.
-
-\begin{figure*}
-\includegraphics[scale=0.3]{mu_central.png}
-\includegraphics[scale=0.3]{mu_homogeneous.png}
-\caption{Flux angular dependency for the central (left) and homogeneous
-(right) source distributions, different line widths illustrate different
-rotational velocities.
-   \label{fig:flux}} 
-\end{figure*}
-
 \subsection{Off-Centered emission}
@@
 
-As a primer approach we study the angular dependency in the same manner as
-we do in section \ref{sec:results}, but with the set up of the off-center models
+We study the deviations of the received flux on the surface of the
+sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
+observer located at an angle $\Theta$ (distant observer angle)
+normalized to the isotropic flux:
+
+\begin{equation}
+F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
+\end{equation}
+%
+where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+$\Delta N$ is the number of photons in a angular bin $\Delta
+\Theta$. This definition satisfies the condition
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.
+
+For the central and homogeneous source distributions we find
+that observers at different directions do not present an angular 
+dependency, in particular they would infer luminosities
+different from the isotropical value only at levels $< 3\%$.
+
+But with the set up of the off-center models
 where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
-located at $\mathrm{\theta = \pi/2}$. In Fig. \ref{fig:OCflux} the angular 
-dependency for two different off-center distribution are shown. The bold line  
+located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
+off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
 represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
@@
 they are most sensitive to the effect of rotation.
-
-%\begin{figure}
-%\includegraphics[scale=0.3]{OC_5t_vel100.jpg}
-%\caption{Spectra for two off-center spheres
-%   \label{fig:OCspectra}} 
-%\end{figure}
 

### 2013-10-16 paper/Analisis.tex
changed from MNRAS to ApJ

@@
-\documentclass[usenatbib]{mn2e} 
-\usepackage{amsmath} 
-\usepackage{amssymb} 
+\documentclass{emulateapj}
+\submitted{{\it Submitted for publication in ApJ}}
+\usepackage{multirow,color,wrapfig,ulem}
+\usepackage {graphicx}
+%\bibliographystyle{apj}
 \usepackage{graphics}
-\usepackage{graphicx}
-\usepackage{epsfig} 
-\usepackage{float} 
-\def\be{\begin{equation}}
-\def\ee{\end{equation}}
-\def\ba{\begin{eqnarray}}
-\def\ea{\end{eqnarray}}
-\bibliographystyle{mn2e}
+\usepackage[dvips]{epsfig}
+
+%\documentclass[usenatbib]{mn2e} 
+%\usepackage{amsmath} 
+%\usepackage{amssymb} 
+%\usepackage{graphics}
+%\usepackage{graphicx}
+%\usepackage{epsfig} 
+%\usepackage{float} 
+%\def\be{\begin{equation}}
+%\def\ee{\end{equation}}
+%\def\ba{\begin{eqnarray}}
+%\def\ea{\end{eqnarray}}
+%\bibliographystyle{mn2e}
 % To highlight comments 
-\usepackage{color}
-\definecolor{red}{rgb}{1,0.0,0.0}
-\newcommand{\red}{\color{red}}
-\definecolor{blue}{rgb}{0.1,0.3,0.9}
-\newcommand{\blue}{\color{blue}}
+%\usepackage{color}
+%\definecolor{red}{rgb}{1,0.0,0.0}
+%\newcommand{\red}{\color{red}}
+%\definecolor{blue}{rgb}{0.1,0.3,0.9}
+%\newcommand{\blue}{\color{blue}}
 
-\usepackage[normalem]{ulem}
-\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-\newcommand{\LCDM}{$\Lambda$CDM~}
-\newcommand{\beq}{\begin{eqnarray}}  
-\newcommand{\eeq}{\end{eqnarray}}  
-\newcommand{\zz}{$z\sim 3$} 
-\newcommand{\apj}{ApJ}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
+%\usepackage[normalem]{ulem}
+%\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
+%\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
+%\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
+%\newcommand{\LCDM}{$\Lambda$CDM~}
+%\newcommand{\beq}{\begin{eqnarray}}  
+%\newcommand{\eeq}{\end{eqnarray}}
+
+%\newcommand{\zz}{$z\sim 3$} 
+%\newcommand{\apj}{ApJ}  
+%\newcommand{\apjs}{ApJS}  
+%\newcommand{\apjl}{ApJL}  
+%\newcommand{\aj}{AJ}  
+%\newcommand{\mnras}{MNRAS}  
+%\newcommand{\mnrassub}{MNRAS accepted}  
+%\newcommand{\aap}{A\&A}  
+%\newcommand{\aaps}{A\&AS}  
+%\newcommand{\araa}{ARA\&A}  
+%\newcommand{\nat}{Nature}  
+%\newcommand{\physrep}{PhR}
+%\newcommand{\pasp}{PASP}    
+%\newcommand{\pasj}{PASJ}    
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 
-\title[Rotation in the Lyman-$\alpha$ line]{The impact of gas bulk
-  rotation on the Lyman-$\alpha$ line} 
-\author[Garavito-Camargo, Forero-Romero \& Dijkstra]{
-\parbox[t]{\textwidth}{\raggedright 
-  Nicolas Garavito-Camargo$^{1}$,
-  Jaime E. Forero-Romero$^{1}$ and 
-  Mark Dijkstra$^2$
+\title{The impact of gas bulk rotation on the Lyman-$\alpha$ line} 
+\author{
+  Nicolas Garavito-Camargo\altaffilmark{1},
+  Jaime E. Forero-Romero\altaffilmark{1},
+  Mark Dijkstra\altaffilmark{2}
 }
-\vspace*{6pt}\\
-$^{1}$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia \\
-$^2$
-}
-\maketitle
+
+\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
+\altaffiltext{2}{--}
 
@@
 \end{abstract}
+
 \begin{keywords}
-galaxies: high-redshift - galaxies: star formation - line: formation
+{galaxies: high-redshift,galaxies: star formation, line: formation}
 \end{keywords}
@@
 
-\begin{subequations}
-\begin{align}
-    v_{x}=-\dfrac{y}{R}V_{\rm max}, \label{subeq1}\\
-    v_{y}=\dfrac{x}{R}V_{\rm max}, \label{subeq2}\\
+\begin{equation}
+    v_{x}=-\frac{y}{R}V_{\rm max}, \label{subeq1}
+\end{equation}
+\begin{equation}
+    v_{y}=\frac{x}{R}V_{\rm max}, \label{subeq2}
+\end{equation}
+\begin{equation}
     v_{z}=0, \label{subeq3}
-\end{align}
-\end{subequations}
+\end{equation}
 %
@@
 
+\bibliographystyle{apj}
 \bibliography{references}

### 2013-10-17 paper/Analisis.tex
small edits in the analysis section

@@
 \usepackage {graphicx}
-%\bibliographystyle{apj}
+
 \usepackage{graphics}
@@
 
-%\documentclass[usenatbib]{mn2e} 
-%\usepackage{amsmath} 
-%\usepackage{amssymb} 
-%\usepackage{graphics}
-%\usepackage{graphicx}
-%\usepackage{epsfig} 
-%\usepackage{float} 
-%\def\be{\begin{equation}}
-%\def\ee{\end{equation}}
-%\def\ba{\begin{eqnarray}}
-%\def\ea{\end{eqnarray}}
-%\bibliographystyle{mn2e}
-% To highlight comments 
-%\usepackage{color}
-%\definecolor{red}{rgb}{1,0.0,0.0}
-%\newcommand{\red}{\color{red}}
-%\definecolor{blue}{rgb}{0.1,0.3,0.9}
-%\newcommand{\blue}{\color{blue}}
-
-%\usepackage[normalem]{ulem}
-%\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
-%\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
-%\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
-%\newcommand{\LCDM}{$\Lambda$CDM~}
-%\newcommand{\beq}{\begin{eqnarray}}  
-%\newcommand{\eeq}{\end{eqnarray}}
-
-%\newcommand{\zz}{$z\sim 3$} 
-%\newcommand{\apj}{ApJ}  
-%\newcommand{\apjs}{ApJS}  
-%\newcommand{\apjl}{ApJL}  
-%\newcommand{\aj}{AJ}  
-%\newcommand{\mnras}{MNRAS}  
-%\newcommand{\mnrassub}{MNRAS accepted}  
-%\newcommand{\aap}{A\&A}  
-%\newcommand{\aaps}{A\&AS}  
-%\newcommand{\araa}{ARA\&A}  
-%\newcommand{\nat}{Nature}  
-%\newcommand{\physrep}{PhR}
-%\newcommand{\pasp}{PASP}    
-%\newcommand{\pasj}{PASJ}    
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 
-Following the classification of $Ly\alpha$ profiles made for (Kulas et al, put reference) 
-we divide our results in $3$ different groups. Group I represents profiles in which the flux in the red side 
-is stronger that in the blue part, while Group II represents profiles in which the blue side
-is the stronger. Group III represents single peaked profiles while Group IV represents multipeaked  
-profiles.
+Gas bulk rotation has a noticeable effect on the morphology of the \ly line. In
+this section we discuss the observational implications of these
+findings.
 
-Group I profiles may be explained in our model when off-center emission is present and the location 
-of this photons emission is stronger in the , while Group II profiles correspond to emissions in the ..
+We start by a quantitative discussion of the line morphology. Here we
+follow  following a classification of $Ly\alpha$ profiles made by
+\cite{Kulas12}. They presented observational results for star forming
+galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
+They classified the observed lines into four groups. In Group I the
+red peak is stronger that in the blue, in Group II the blue peak is
+stronger, in Group III there are single peaked profiles while while
+Group IV containes multipeaked lines.
 
-Group III profiles are better represented by galaxies rotating at $V > 100 kms^{-1}$\\
+Neither Group I nor II can be explained by rotation. However, the
+morphologies of the lines in Group III and IV are similar to some of
+the results obtained in this paper.
+
+Group III profiles are better represented by galaxies rotating at $V >
+100 kms^{-1}$\\
 
@@
 
-% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail observaciones, Kulas, YAMADA  off-center emission
+% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail
+% observaciones, Kulas, YAMADA  off-center emission
 

### 2013-10-17 paper/Analisis.tex
More on discussion

@@
 
+An other interesting sample of LAEs was presented by (Yamada.T el al)
+for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
+a single peak profile, if this single peak is present an asymmetry it 
+can be explained with the outflow model (Verhamme) due to the fact that 
+we don't find any asymmetry due to rotation in  both homogeneous and central
+models, while in the off-center model... But if it is not the 
+case (put LAEs name for those that do not present asymmetry) now they can
+be understanding with rotation.
+
 No effects asociated with inflows or outflows

### 2013-10-17 paper/Analisis.tex
A couple of paragraphs in discussion section

--- 2013-10-17 paper/Analisis.tex
@@
 
-Gas bulk rotation has a noticeable effect on the morphology of the \ly line. In
-this section we discuss the observational implications of these
-findings.
+Gas bulk rotation has a noticeable effect on the morphology of the
+ \ly line. In this section we discuss the observational implications 
+ of these findings.
 
 We start by a quantitative discussion of the line morphology. Here we
-follow  following a classification of $Ly\alpha$ profiles made by
+follow a classification of $Ly\alpha$ profiles made by
 \cite{Kulas12}. They presented observational results for star forming
@@
 They classified the observed lines into four groups. In Group I the
-red peak is stronger that in the blue, in Group II the blue peak is
-stronger, in Group III there are single peaked profiles while while
-Group IV containes multipeaked lines.
+red peak is stronger than the blue, For our porpoises Group II and Group II
+with the blue peak stronger are the same, Group IV contains double-peak
+profiles with roughly the same flux and finally group IV present multi-peaked 
+lines.
 
-Neither Group I nor II can be explained by rotation. However, the
-morphologies of the lines in Group III and IV are similar to some of
-the results obtained in this paper.
+Neither Group I nor II  and III can be fully explained by rotation. However,
+ some comments about some of the galaxies in this groups must be done, in 
+ particular for those galaxies in which the flux in between the two peaks is
+ high rotation must be present due to the fact this is until now the most 
+ efficient mechanism which produces this effect.
 
-Group III profiles are better represented by galaxies rotating at $V >
-100 kms^{-1}$\\
+The same argument explained above applies to group IV in which the flux
+in between of the two peaks is high ( $ \geq 70 \%$ of the highest peak), 
+concerning group V in which multiple-peaks appear homogeneous and central
+models can not reproduce such a profiles. While the off-center model could 
+generate similar profiles which is the case of (put reference when the fig.
+is ready) when tree peaks could appear but with roughly the same flux, this
+multiple-peaks still need a better comprehension of the gas kinematics.
 
-Comparing with the sample of (Kulas et al) we observe that rotational effects could be 
-associated in group IV and V in galaxies where the difference between the two peaks is 
-small and .
+An other interesting sample of LAEs was presented by \cite{Yamada2012} 
+for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
+a single peak profile, if this single peak is present an asymmetry it 
+can be explained with the outflow model \cite{Verhamme2008} due to the fact that 
+we don't find any asymmetry due to rotation in  both homogeneous and central
+models, while in the off-center model ---. But if it is not the 
+case (put LAEs name for those that do not present asymmetry) now they can
+be understanding with rotation.
 
-No effects asociated with inflows or outflows
+Even in profiles where the double-peaked is presented rotation also could 
+be present as it is seen in Fig.\ref{fig:differentvelocities} where rotation
+makes that the central part of the line is higher than in profiles where 
+there is no rotation. This could be the case of 13 LAEs in the sample of 
+\cite{Kulas12} where there is a double-peak profile with similar heigh and 
+a central notorious part.
 
-... The results derived in this paper have consequences on the
-interpretation of galaxy observations in the Lyman alpha line.
-
-..compare steidel et al (2011)
+Until now when single peaked profiles are present we associate this to
+the presence of inflows and outflows due to the asymmetry of the line
+, but in the case in which the profile have symmetry we could say that
+rotation in the principal effect governing the galaxy. For this reason 
+a detailed study involving inflows/outflows and rotation kinematics would 
+give as better understanding of the $\mathrm{Ly} \alpha$ profiles we 
+measured.
 
@@
 % observaciones, Kulas, YAMADA  off-center emission 
+% See steidel et al (2011) findings.
 
@@
 
-\section*{Appendix A: Tables}
-
 \end{document}

### 2013-10-18 paper/Analisis.tex
New off-center profile  plot
minor changes

@@
 $R$ is the radii of the homogeneous sphere and 
-we choose two spheres in each side of the $\hat{\textbf{x}}$ axis
-two at $0.25 R$ and the other two at $0.5 R$.
+we choose two spheres in each side of the $\hat{\textbf{x}}$ axis,
+two at $\mp 0.25 R$ and the other two at $\mp 0.5 R$.
 
@@
 
-But with the set up of the off-center models
-where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
-located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
-off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
-represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
-the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
-with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
-show exactly the same trend. We find a high dependency in the viewing angle
-in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
-at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
-galaxies are oriented in random directions which implies that off-center emission
-is not going to be observed in all the observed galaxies.
+In the case of the Off-center model the 
+%But with the set up of the off-center models
+%where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
+%located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
+%off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
+%represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
+%the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
+%with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
+%show exactly the same trend. We find a high dependency in the viewing angle
+%in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
+%at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
+%galaxies are oriented in random directions which implies that off-center emission
+%is not going to be observed in all the observed galaxies.
 
@@
 
-The outgoing spectra for two different spheres located at $-0.25R$ and $0.25R$ respectively
-are shown in Fig. \ref{fig:OCspectra}, we have shown this positions because
-they are most sensitive to the effect of rotation.
+The outgoing spectra for two different spheres located at $\pm 0.5R$ 
+are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
+the resulting profiles show more interesting morphologies than in the
+$\pm 0.25R$ case.
 
@@
 where one peak is $20\%$ higher than the other.
+
+\begin{figure*}
+\includegraphics[scale=0.3]{OC_profiles.png}
+\caption{Off-center distribution $\mathrm{Ly}\alpha$ profiles, 
+off-center positions.
+   \label{fig:OC_profiles}} 
+\end{figure*}
 

### 2013-10-18 paper/Analisis.tex
Corrected paragraph in Off-Center section

@@
 For the central and homogeneous source distributions we find
-that observers at different directions do not present an angular 
-dependency, in particular they would infer luminosities
+that for observers located at  $\theta = pi/2$ the
+angular dependency represented by $\mu$ doesn't show a considerable
+variation in particular the observer would infer luminosities 
 different from the isotropical value only at levels $< 3\%$.
 
-In the case of the Off-center model the 
-%But with the set up of the off-center models
-%where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
-%located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
-%off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
-%represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
-%the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
-%with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
-%show exactly the same trend. We find a high dependency in the viewing angle
-%in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
-%at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
-%galaxies are oriented in random directions which implies that off-center emission
-%is not going to be observed in all the observed galaxies.
+In the case of the Off-center model with the set up showed in 
+Fig.\ref{fig:OCspheres} where the galaxy is rotating around the  
+$\hat{\textbf{z}}$ axis and the observer is also located at 
+$\mathrm{\theta = \pi/2}$. The first result we get is that 
+the angular dependency is almost the same for all the models
+with different $\tau_{H}$ and $V_{max}$. Both spheres located 
+at $R = 0.25$ and $R = 0.5$ show variation in the flux just at
+values $< 14 \%$ this results are shown in \ref{fig:OCflux}.
 
@@
 are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
-the resulting profiles show more interesting morphologies than in the
+the resulting profiles show new interesting morphologies than in the
 $\pm 0.25R$ case.
@@
 values of velocity and optical depth an asymmetry in the peak heights 
-is presented, those off-center spheres \textit{(put image reference)} 
-located at the positive side of $\hat{\textbf{x}}$ in Fig.\ref{fig:OCspheres}
-present a higher peak in the red-shifted part, while those spheres located
-at the negative side of $\hat{\textbf{x}}$ present a higher blue shifted peak,
-we found that the higher asymmetry is for model with $\tau=10^7, V=200 kms^{-1}$ 
-where one peak is $20\%$ higher than the other.
+is presented. Those off-center spheres located at the positive side of 
+$\hat{\textbf{x}}$ (solid lines) in Fig.\ref{fig:OCspheres} have a slightly
+shift to redder part of the spectra while those located at the negative 
+side of $\hat{\textbf{x}}$ are shifted to the bluer part, the model in 
+which this is most notorious is for $R = 0.25$, $V_{max} = 50$ and $\tau=10^{5}$.
 
@@
 some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
-the line presents three peaks (blue-shifted, centered, red-shifted). In order to gain a better interpretation of this three peaks trend we run this models with $N_{\gamma} = 10^6$.
+the line presents three peaks (blue-shifted, centered, red-shifted). In order 
+to gain a better interpretation of this three peaks trend we run this models
+ with $N_{\gamma} = 10^6$.
 

### 2013-10-18 paper/Analisis.tex
new abstract

--- 2013-10-18 paper/Analisis.tex
@@
 \begin{abstract} 
-Rotation is present in the gas kinematics of galaxies up to the
-highest redshifts. In this paper we present for the first time 
-radiative transfer calculations that show the impact of gas bulk rotation on
-the morphology of the Lyman $\alpha$ line. To this end we model a
-galaxy as an homogeneous sphere composed as an homogeneous mixture of
-dust and hydrogen at a constant temperature. These spheres have a
-solid-body rotation with linear velocities at the surface in the range
-$0-300$ \kms and neutral hydrogen optical depths in the range
-$\tau_{\rm H}=10^{5}-10^{7}$. We consider radiation sources both in
-the center of the rotating cloud and also homogeneously distributed in
-the volume. We find that higher rotational velocities increase the
-width of each peak in the outgoing line profile while it also
-increases the amount of Lyman alpha photons escaping in the line
-center. This trends makes that for high rotational velocities and
-large Hydrogen optical depths the double peak of the line tends to be
-erased an be replaced by a single peak a the line center. This trend
-is more pronounced for radiation sources homogeneously
-distributed. Concerning the escape fraction we find that rotation does
-not have any effect, provided that all the sources are centrally
-emitted. However, in the case of homogeneously emittedsources we
-measure an increase of about a factor of $2$ in the escape  fraction
-for higher rotational velocity values. This work shows that gas bulk
-rotation has a non negligible impact on the shape of the Lyman
+We present novel results of radiative transfer calculations to measure
+the impact of gas bulk rotation on the morphology of the Lyman
+$\alpha$ line in galaxies. We model a galaxy as as sphere with an
+homogeneous mixture of dust and hydrogen at a constant
+temperature. These spheres have a solid-body rotation with 
+maximum velocities in the range $0-300$ \kms. The neutral
+hydrogen optical depths are in the range $\tau_{\rm
+  H}=10^{5}-10^{7}$. We also consider two kinds of spatial
+distribution for the radiation sources with respect to the sphere:
+central and homogeneous. We find that the line width and the amount of
+Lyman alpha photons ecapine in the line center increase with
+rotational velocity. higher rotational velocities increase the width
+of each peak in the outgoing line profile while it also increases the
+amount of Lyman alpha photons escaping in the line. For large
+rotational velocities and high Hydrogen optical depths the outgoing
+line presents single peak a the line center. This trend is more
+pronounced for radiation sources homogeneously distributed in the
+sphere. Rotation increses by a factor of $2$ the escape fraction for
+systems with homogeneously distributed sources. For radiation sources
+located off-center, the line morphology  presents a range of single,
+double and triple peak lines. This work demonstrates that gas bulk
+rotation has a non negligible impact on the morphology of the Lyman
 $\alpha$ line.   
@@
      \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
-
     \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) pannels

### 2013-10-18 paper/Analisis.tex
removed comments

@@
 
-%If there is a change in the number of scatterings with rotational
-%velocity, there must be a change in the probability of being absorbed
-%if dust is present. We study how rotation impacts the escape fraction
-%of \ly photons.
-
-%Taking into account the results in the previous section, we do not expect any
-%change in the case of central distributions given that the average
-%number of scatterings remain constant. On the other hand, in the
-%homogeneous distribution there is a considerable drop in the number of
-%scatterings as $V_{\rm max}$ increases, this preconditions the escape
-%fraction to increase as well.
-
 Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
@@
   rot}=300$\kms.
-
-%This Figure illustrates how our
-%reasoning in the previous paragraph is correct. 
-%The escape fraction
-%barely changes for the central source distribution, while it rises
-%as the velocity $V_{\rm max}$ increases for the homogeneous case.
 
@@
 In the case of the Off-center model the
-%But with the set up of the off-center models
-%where the galaxy is rotating around the  $\hat{\textbf{z}}$ axis and the observer is 
-%located at $\mathrm{\theta = \pi/2}$ we do find and angular dependency for both  
-%off-center distributions, this is shown in Fig. \ref{fig:OCflux}. The bold line  
-%represents an off-center sphere located at $0.25 R$ in the homogeneous sphere, while 
-%the narrow line shows a sphere located at $-0.25 R$. This is done for the model 
-%with $\tau=10^{5}$ and $V=50 km s^{-1}$, but results with the rest of models
-%show exactly the same trend. We find a high dependency in the viewing angle
-%in particular the flux at $\mathrm{\theta = \pi/2}$ is $\simeq 88\%$ stronger than 
-%at $\mathrm{\theta = \pi/3}$ this have important consequences in observations when 
-%galaxies are oriented in random directions which implies that off-center emission
-%is not going to be observed in all the observed galaxies.
 
@@
  a larger hydrogen medium than photons located in the spheres at $0.5 R$.
-%poner valores de velocidad y optical depth porcentaje de asimetria
 
@@
 the line presents three peaks (blue-shifted, centered, red-shifted). In order to gain a better interpretation of this three peaks trend we run this models with $N_{\gamma} = 10^6$.
-
-%\begin{figure}
-%  \includegraphics[width=0.40\textwidth]{Distribution.png}
-%  \caption{Inhomogeneous distributions of 
-% photons, Blue area represents the photons in distribution 1 while red
-% area are the selected photons for distribution 2. The arrow points to
-% the observer position\label{figure:distributions}}  
-%\end{figure}
-
-%In Fig.~\ref{figure:inhomogeneous} we show the resulting spectra of 
-%distribution 1 and 2, the first effect we see is the asymmetry of the
-%double peak, in the homogeneous and central distribution we see double
-%peaks with the same height, while in this case one peak is higher than 
-%the other. For $\tau=10^{5}$ we found that in distribution 1 the blueshifted
-%peak is higher than the reds~\ref{figure:distributionshifted, and for distribution 2 the redshifted
-%peak is the highest.
-
-%An other important fact here is the asymmetry of the spectra with respect 
-%to the line center, in particular photons selected in distribution 1 
-%present a blueshift in their spectra while photons selected in distribution 
-%2 present a redshift. This effect becomes stronger as velocity increase 
-%~\ref{figure:inhomogeneous}
-
-%\begin{figure*}
-%  \includegraphics[width=0.45\textwidth]{InomogeneousModelt5.png}
-%  \includegraphics[width=0.45\textwidth]{InomogeneousModelt6.png}
-% \caption{Inhomogeneous model for velocities $50km/s$ and $300km/s$ ,
-%   (left) with $\tau=10^5$, (right) with
-%   $\tau=10^6$\label{figure:inhomogeneous}}  
-%\end{figure*}
-
-%\subsection{Integrated flux in a narrowband filter}
-
-%Until now we have shown the main effects of gas and dust rotation in
-%the Ly$\alpha$ line morphology such as the escape fraction, the FWHM,
-%the maxima position, also we see that shape of the outgoing spectra
-%depends on the position of the observer. It is important to see if
-%rotational effects are detectable in observational methods involving
-%the Ly$\alpha$ line.
-
-%One of the most used methods to detect high redshift galaxies using
-%the Ly$\alpha$ line is using a narrowband selection, we make this
-%analysis based on the results obtained by Steidel (2011) in this work
-%(EXPLAIN a lit of bit more about their work) they used tree narrowband
-%filters for tree different redshifts resumed in
-%Table~\ref{table:NBfilters}, We want to know how much the integrated
-%flux change due to rotational effects in this NB filters, for the
-%models we simulated with CLARA.
-
-%\begin{table*}
-%\begin{center}
-%\begin{tabular}{cccc}\hline
-%Model & SSA22a 4980/80   & HS1549 4667/80 & HS1700 4018/90\\
-%\hline
-%\end{tabular}
-%\caption{
-%Fluxes for tree different narrow band filters.
-%} 
-%\label{table:NBfilters}
-%\end{center}
-%\end{table*}
-
-%In table \ref{table:NBfilters} we present the results of the flux in
-%every  narrowband filter for the homogeneous model at different
-%velocities and hydrogen  optical depth $\tau_{0}$. As is well known an
-%increase in the optical depth makes  the line peaks separation
-%bigger. In fact for some cases the line width is larger  than the NB
-%filer width fig.(put ref fig) for those cases we modify the redshift
-%in the available range in order to make the peak maxima match the NB
-%filter center.  For all cases we found that as velocity increase the
-%flux is less.
-
-%In the case of the dusty model we found the same trend of the flux
-%with the velocity  but in this cases the effect is no that strong.  We
-%also found some dependency with the viewing angle.
-
-%\begin{figure}
-%  \includegraphics[width=0.45\textwidth]{NB7tDifVHOM.png}
-% \label{figure:efvsNeufeld}\caption{NB filter located at the center of
-%   the maxima, with different redshift}  
-%\end{figure}
 
@@
 
-% BUSCAR asimetrias enhttps://pod51044.outlook.com/owa/#path=/mail
-% observaciones, Kulas, YAMADA  off-center emission 
-% See steidel et al (2011) findings.
-
-% taking into account equivalent widths results with narrow band
-% filters we can make a criterium in order to select wich galaxie
-% could be seen in actual observations.
-
 \section{Conclusions}
@@
 
-%As an application of these results we compute the integrated flux
-%taking into account the narrow band filters used by (Steidel et al
-%2011), for our models we found an important decrease up to $~40\%$ for
-%the homogeneous models, and up to $22\%$ for the dusty homogeneous
-%models in the flux as velocity increase.  Also we calculate at what
-%redshift should the filter be in order to get the maximum  flux, and
-%for the tree filters we get values that rely in the filter redshift
-%range. This effects would have a relevant implication at the time to
-%find high redshift galaxies.
-
 This paper illustrates for the first time the main effects of rotation
@@
 \end{document}
-
-%ideas:
-Keep in mind making a follow up paper on the results of Yamada et al
-http://adsabs.harvard.edu/abs/2012ApJ...751...29Y on the line
-morphology at z=3.1. How many of these laes can be considered to have
-rotation features? In principle, all of then should have them. How to
-make the case convincing in the statistical sense?

### 2013-10-18 paper/Analisis.tex

@@
 \begin{abstract}
-We present novel results of radiative transfer calculations to measure
-the impact of gas bulk rotation on the morphology of the Lyman
-$\alpha$ line in galaxies. We model a galaxy as as sphere with an
-homogeneous mixture of dust and hydrogen at a constant
-temperature. These spheres have a solid-body rotation with 
-maximum velocities in the range $0-300$ \kms. The neutral
-hydrogen optical depths are in the range $\tau_{\rm
-  H}=10^{5}-10^{7}$. We also consider two kinds of spatial
-distribution for the radiation sources with respect to the sphere:
-central and homogeneous. We find that the line width and the amount of
-Lyman alpha photons ecapine in the line center increase with
-rotational velocity. higher rotational velocities increase the width
-of each peak in the outgoing line profile while it also increases the
-amount of Lyman alpha photons escaping in the line. For large
-rotational velocities and high Hydrogen optical depths the outgoing
-line presents single peak a the line center. This trend is more
-pronounced for radiation sources homogeneously distributed in the
-sphere. Rotation increses by a factor of $2$ the escape fraction for
-systems with homogeneously distributed sources. For radiation sources
-located off-center, the line morphology  presents a range of single,
-double and triple peak lines. This work demonstrates that gas bulk
-rotation has a non negligible impact on the morphology of the Lyman
+Rotation is present in the gas kinematics of galaxies up to the
+highest redshifts. In this paper we present for the first time 
+radiative transfer calculations that show the impact of gas bulk rotation on
+the morphology of the Lyman $\alpha$ line. To this end we model a
+galaxy as an homogeneous sphere composed as an homogeneous mixture of
+dust and hydrogen at a constant temperature. These spheres have a
+solid-body rotation with linear velocities at the surface in the range
+$0-300$ \kms and neutral hydrogen optical depths in the range
+$\tau_{\rm H}=10^{5}-10^{7}$. We consider radiation sources both in
+the center of the rotating cloud and also homogeneously distributed in
+the volume. We find that higher rotational velocities increase the
+width of each peak in the outgoing line profile while it also
+increases the amount of Lyman alpha photons escaping in the line
+center. This trends makes that for high rotational velocities and
+large Hydrogen optical depths the double peak of the line tends to be
+erased an be replaced by a single peak a the line center. This trend
+is more pronounced for radiation sources homogeneously
+distributed. Concerning the escape fraction we find that rotation does
+not have any effect, provided that all the sources are centrally
+emitted. However, in the case of homogeneously emittedsources we
+measure an increase of about a factor of $2$ in the escape  fraction
+for higher rotational velocity values. This work shows that gas bulk
+rotation has a non negligible impact on the shape of the Lyman
 $\alpha$ line.   
@@
 For the central and homogeneous source distributions we find
-that observers at different directions do not present an angular 
-dependency, in particular they would infer luminosities
+that for observers located at  $\theta = pi/2$ the
+angular dependency represented by $\mu$ doesn't show a considerable
+variation in particular the observer would infer luminosities 
 different from the isotropical value only at levels $< 3\%$.
 
-In the case of the Off-center model the
+In the case of the Off-center model with the set up showed in 
+Fig.\ref{fig:OCspheres} where the galaxy is rotating around the  
+$\hat{\textbf{z}}$ axis and the observer is also located at 
+$\mathrm{\theta = \pi/2}$. The first result we get is that 
+the angular dependency is almost the same for all the models
+with different $\tau_{H}$ and $V_{max}$. Both spheres located 
+at $R = 0.25$ and $R = 0.5$ show variation in the flux just at
+values $< 14 \%$ this results are shown in \ref{fig:OCflux}.
 

### 2013-10-18 paper/Analisis.tex

--- 2013-10-18 paper/Analisis.tex
@@
 $\alpha$ line.
+
 \end{abstract}

### 2013-10-19 paper/Analisis.tex
Finish off-center, discusion an a new paragraph in conclusiones

@@
 the impact of gas bulk rotation on the morphology of the Lyman
-$\alpha$ line in galaxies. We model a galaxy as as sphere with an
+$\alpha$ line in galaxies. We model a galaxy as a sphere with an
 homogeneous mixture of dust and hydrogen at a constant
@@
 central and homogeneous. We find that the line width and the amount of
-Lyman alpha photons ecapine in the line center increase with
+Lyman alpha photons escaping in the line center increase with
 rotational velocity. higher rotational velocities increase the width
@@
 pronounced for radiation sources homogeneously distributed in the
-sphere. Rotation increses by a factor of $2$ the escape fraction for
+sphere. Rotation increases by a factor of $2$ the escape fraction for
 systems with homogeneously distributed sources. For radiation sources
@@
 name of \ly emitters (LAEs). A detailed examination of this galaxy
-population has diverse implications for galaxy formation, reonization
+population has diverse implications for galaxy formation, reionization
 and the large scale structure of the Universe. Attempts to fully
 exploit the physical information included in the \ly line require an
-understading of all the physical factors involved in shaping the
+understanding of all the physical factors involved in shaping the
 line. Due to the resonant nature of this line, these physical factors
@@
 configurations (i.e. edge-on vs. face-on view of a galaxy), the
-inflows observaed by gas cooling and the outflows included in the
+inflows observed by gas cooling and the outflows included in the
 supernova feedback process of the simulation. These bulk flows
@@
 rotation into the Monte Carlo codes, paying special attention to coordinate
-definitions. There we also list the different physical parementers in
+definitions. There we also list the different physical parameters in
 the simulated grid of models. In the next section we present the
@@
 observations and further refinements that can be implemented in the
-theoretical modelling of the \ly line. In the last section we preset
-our conclusiones.
+theoretical modelling of the \ly line. In the last section we present
+our conclusions.
 
@@
   simulated in our Monte Carlo calculations. For each parameter we
-  vary the values in the range listed in the last column. Takig into
+  vary the values in the range listed in the last column. Taking into
   account all the possible combinations we end up with $60$ different
@@
 For the central emission the transition to a single peak is never
-completed in the range of parameters explored here. The nonappearence
+completed in the range of parameters explored here. The non appearance
 of a single peak phase can be in part explained to the absence of a
@@
 line center as the rotational velocity increases. This hints that the
-encounters with a nonstatic medium are inefficient in changing a
+encounters with a non static medium are inefficient in changing a
 photons' frequency outside the line center.
@@
 \citep{Adams72,Harrington73}. In our experiments we find  that for the
-static spheres with centraly distributed sources $\langle N_{\rm
+static spheres with centrally distributed sources $\langle N_{\rm
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$. for optical depths
@@
 the analytical solution for the infinite slab \citep{Neufeld90}. In
-Neufeld's setup the analytic solution depends solely on the product
+Neufeld's set-up the analytic solution depends solely on the product
 $(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
@@
 select certain photons that are placed in a specific place but that 
-are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the distributions we 
-set up, basically we take photons located in a sphere of $0.5 R$ where
-$R$ is the radii of the homogeneous sphere and 
+are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the 
+distributions we set up, basically we take photons located in a sphere
+ of $0.5 R$ where $R$ is the radii of the homogeneous sphere and 
 we choose two spheres in each side of the $\hat{\textbf{x}}$ axis,
@@
 %
-where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
 $\Delta N$ is the number of photons in a angular bin $\Delta
@@
 $\hat{\textbf{z}}$ axis and the observer is also located at 
-$\mathrm{\theta = \pi/2}$. The first result we get is that 
-the angular dependency is almost the same for all the models
-with different $\tau_{H}$ and $V_{max}$. Both spheres located 
-at $R = 0.25$ and $R = 0.5$ show variation in the flux just at
-values $< 14 \%$ this results are shown in \ref{fig:OCflux}.
+$\mathrm{\theta = \pi/2}$, For the special purpose to get a
+better sample we used $\tau_{\gamma} = 10^{6}$. The first result 
+we get is that the angular dependency is almost the same for 
+all the models with different $\tau_{H}$ and $V_{max}$ for 
+$R = 0.25$. While for spheres located at and $R = 0.5$ show 
+variation in the flux in values $< 14 \%$ in particular at 
+$\mu = 0$ the flux in stronger. This results are shown 
+in Fig. \ref{fig:OCflux}.
 
@@
 are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
-the resulting profiles show new interesting morphologies than in the
-$\pm 0.25R$ case.
+the resulting profiles show new interesting morphologies than are not
+found in the $\pm 0.25R$ case.
 
-There are two new morphological features that off-center emission in 
-rotating galaxies produces. First in some of our models with specific 
-values of velocity and optical depth an asymmetry in the peak heights 
-is presented. Those off-center spheres located at the positive side of 
-$\hat{\textbf{x}}$ (solid lines) in Fig.\ref{fig:OCspheres} have a slightly
-shift to redder part of the spectra while those located at the negative 
-side of $\hat{\textbf{x}}$ are shifted to the bluer part, the model in 
-which this is most notorious is for $R = 0.25$, $V_{max} = 50$ and $\tau=10^{5}$.
+The main effect we found in the off-center emission is that for 
+some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
+the line presents three peaks (blue-shifted, centred, red-shifted), 
+For models with ($\left[ \tau = 10^{5}, V=100 km s^{-1} \right]$ ,
+$\left[\tau = 10^6, V=200 km s^{-1} \right]$ and $ \left[\tau = 10^{7}, 
+V=300 km s^{-1}\right]$) the centred line is dominant but the presence of
+the redder and bluer peak in also present which is also a new result.
+Also as in the homogeneous / central model the line is broader at high 
+rotational velocities.
 
@@
 \includegraphics[scale=0.3]{OC_profiles.png}
-\caption{Off-center distribution $\mathrm{Ly}\alpha$ profiles, 
-off-center positions.
+\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
+dashed lines represents spheres locate at $-0,5R$ while solid lines 
+represents spheres at $0.5R$)
    \label{fig:OC_profiles}} 
 \end{figure*}
-
-This can be appreciated for both set of spheres at $0.25 R$ and $0.5 R$,
- but the effect shows a stronger asymmetry for spheres located at $0.25 R$
- this due to the fact that photons escaping from this spheres goes through 
- a larger hydrogen medium than photons located in the spheres at $0.5 R$.
-
-Also for all the off-center models we found that the $Ly\alpha$ line 
-width ...
-
-Also for photons located in the spheres at $0.5 R$, we found that for 
-some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
-the line presents three peaks (blue-shifted, centered, red-shifted). In order 
-to gain a better interpretation of this three peaks trend we run this models
- with $N_{\gamma} = 10^6$.
 
@@
 for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
-a single peak profile, if this single peak is present an asymmetry it 
-can be explained with the outflow model \cite{Verhamme2008} due to the fact that 
-we don't find any asymmetry due to rotation in  both homogeneous and central
-models, while in the off-center model ---. But if it is not the 
-case (put LAEs name for those that do not present asymmetry) now they can
-be understanding with rotation.
+a single peak profile, if in this single peak there is an asymmetry it 
+can be explained with the outflow/inflow model \cite{Verhamme2008, Dijkstra06}.
+ But if it is not the case now they can be understanding with rotation, 
+ in particular in this sample there are single peaks with a strong asymmetry 
+ and there are peaks that this asymmetry its not notorious.
+
+Between the 91 LAEs 8 reveal profiles with a central peak and two smaller
+peaks at the redder and bluer side, this also could be explained by our
+off-center model when higher velocities are involved in rotation.
 
@@
 , but in the case in which the profile have symmetry we could say that
-rotation in the principal effect governing the galaxy. For this reason 
+gas bulk rotation is the principal effect governing the galaxy. For this reason 
 a detailed study involving inflows/outflows and rotation kinematics would 
@@
 
+Comparing our results with recent observed LAEs we find that many 
+morphological features such as high central line flux, single peak
+profiles and multi-peaked profiles could be explained by gas bulk 
+rotation present in this LAEs.
+
 This paper illustrates for the first time the main effects of rotation

### 2013-10-21 paper/ms.tex

--- 2013-10-19 paper/Analisis.tex
@@
 Lyman alpha photons escaping in the line center increase with
-rotational velocity. higher rotational velocities increase the width
+rotational velocity. Higher rotational velocities increase the width
 of each peak in the outgoing line profile while it also increases the
@@
 line that show a clear evolution as a function of the cloud's
-rotational velocity. In \S \ref{sec:dicussion} we discuss the
+rotational velocity. In \S \ref{sec:discussion} we discuss the
 implications of our results in the interpretation of LAEs
@@
 constant until beyond some velocity threshold the line becomes single
-peaked with $x_{\rm max}=0$ \kms.
+peaked with $X_{\rm max}=0$ \kms.
 

### 2013-10-21 paper/ms.tex
Fig 10 fixed bugs

--- 2013-10-19 paper/Analisis.tex
@@
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
-\altaffiltext{2}{--}
+\altaffiltext{2}{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85741, Garching, Germany}
 
@@
 temperature. These spheres have a solid-body rotation with
-maximum velocities in the range $0-300$ \kms. The neutral
-hydrogen optical depths are in the range $\tau_{\rm
+maximum velocities in the range $0-300$ \kms and neutral
+hydrogen optical depths in the range $\tau_{\rm
 H}=10^{5}-10^{7}$. We also consider two kinds of spatial
@@
 central and homogeneous. We find that the line width and the amount of
-Lyman alpha photons escaping in the line center increase with
-rotational velocity. higher rotational velocities increase the width
-of each peak in the outgoing line profile while it also increases the
-amount of Lyman alpha photons escaping in the line. For large
+Lyman $\alpha$ photons escaping in the line center increase with
+the rotational velocity. For large
 rotational velocities and high Hydrogen optical depths the outgoing
@@
 pronounced for radiation sources homogeneously distributed in the
-sphere. Rotation increases by a factor of $2$ the escape fraction for
+sphere. Rotation also increases by a factor of $2$ the escape fraction for
 systems with homogeneously distributed sources. For radiation sources
 located off-center, the line morphology presents a range of single,
-double and triple peak lines. This work demonstrates that gas bulk
+double and triple peaked lines. This work demonstrates that gas bulk
 rotation has a non negligible impact on the morphology of the Lyman
@@
 They classified the observed lines into four groups. In Group I the
-red peak is stronger than the blue, For our porpoises Group II and Group II
-with the blue peak stronger are the same, Group IV contains double-peak
-profiles with roughly the same flux and finally group IV present multi-peaked 
-lines.
+red peak is stronger than the blue, in Group II the blue peak is
+stronger, in Group III the two peaks have the same strength and Group
+IV LAEs present multiple peaks.
 

### 2013-10-23 paper/ms.tex
minor edits

@@
 \begin{figure*}
+\begin{center}
   \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
-     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png} 
+  \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}\\
   \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
   \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
+\end{center}
     \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) pannels
@@
 The number of times that a \ly photon is absorbed and re-emitted is
-connected to the final frequency that it can have after escaping the
+affects the final frequency that it will have after escaping the
 galaxy. In the case of static gas geometries, a large value of the
-optical depth is immediately followed by a high number of
-scatterings. In turn a large optical depth increases the probability
-that a \ly photon to be found far from the center of the line. In this
-case, the peak maxima shift away form the line center as the amount of
-neutral hydrogen increases.
+optical depth correlates with a high number of
+scatterings. This increases the probability of finding
+a \ly photon far from the center of the line. In summary, the peak
+maxima shift away form the line center as the amount of neutral
+hydrogen increases.
 
@@
 $\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
-$V_{\rm max}$. For the central distributions we find that there is not
-a significant change for increasing rotational
+$V_{\rm max}$. For the central distributions the average number of
+scatterings has a modes change for increasing rotational
 velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
-for different velocities. In this case we also find that the average
+for different velocities. In the same setup the average
 number of scatterings is proportional to the optical depth, as
@@
 infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}. In our experiments we find  that for the
-static spheres with centrally distributed sources $\langle N_{\rm
-  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$. for optical depths
+\citep{Adams72,Harrington73}. In static spheres 
+with centrally distributed sources we find $\langle N_{\rm
+  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depths
 $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$

### 2013-10-23 paper/ms.tex
edits in the discussion section

@@
 red peak is stronger than the blue, in Group II the blue peak is
-stronger, in Group III the two peaks have the same strength and Group
-IV LAEs present multiple peaks.
+stronger, in both cases the peaks are symmetrically located around the
+line center. In Group III the blue peak also dominates but there is a
+overall redward shift of the zero point. Group IV presents two similar
+peaks symmetrically located around the zero point. Group V presents
+three peaks.
 
-Neither Group I nor II  and III can be fully explained by rotation. However,
- some comments about some of the galaxies in this groups must be done, in 
- particular for those galaxies in which the flux in between the two peaks is
- high rotation must be present due to the fact this is until now the most 
- efficient mechanism which produces this effect.
+The asymmetries in Groups I, II  and III cannot be fully explained by
+rotation. However, some galaxies in those groups have a high flux between
+the two peaks; an effect that can be induced by rotation. The same
+argument applies to galaxies in the group IV in which the flux
+in between of the two peaks is high ($ \geq 70 \%$ of the intensity in
+the highest peak). Finally, the triple peaked lines in Galaxies in
+Group V can be easily reproduced by rotation with off-centered
+emission.
 
-The same argument explained above applies to group IV in which the flux
-in between of the two peaks is high ( $ \geq 70 \%$ of the highest peak), 
-concerning group V in which multiple-peaks appear homogeneous and central
-models can not reproduce such a profiles. While the off-center model could 
-generate similar profiles which is the case of (put reference when the fig.
-is ready) when tree peaks could appear but with roughly the same flux, this
-multiple-peaks still need a better comprehension of the gas kinematics.
+Another relevant sample of lines was presented by \cite{Yamada2012} 
+for 91 LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
+a single peak profile. Some of the peaks have a stron symmetry, while
+others do not. The symmetric single peaked progile can be explained by
+rotation effects, while the assymetric cases naturally arise in
+outflow/inflow models \citep{Verhamme2008, Dijkstra06}. Among the 91
+LAEs, 8 reveal triple peaked profiles with a central peak and two
+smaller peaks at the redder and bluer side, a feature that is present
+in our off-center emission models with rotation.
 
-An other interesting sample of LAEs was presented by \cite{Yamada2012} 
-for 91 LAEs at $z=3.1$. From that sample 31 LAEs ($\sim 33 \%$) present 
-a single peak profile, if in this single peak there is an asymmetry it 
-can be explained with the outflow/inflow model \cite{Verhamme2008, Dijkstra06}.
- But if it is not the case now they can be understanding with rotation, 
- in particular in this sample there are single peaks with a strong asymmetry 
- and there are peaks that this asymmetry its not notorious.
-
-Between the 91 LAEs 8 reveal profiles with a central peak and two smaller
-peaks at the redder and bluer side, this also could be explained by our
-off-center model when higher velocities are involved in rotation.
-
-Even in profiles where the double-peaked is presented rotation also could 
-be present as it is seen in Fig.\ref{fig:differentvelocities} where rotation
-makes that the central part of the line is higher than in profiles where 
-there is no rotation. This could be the case of 13 LAEs in the sample of 
-\cite{Kulas12} where there is a double-peak profile with similar heigh and 
-a central notorious part.
-
-Until now when single peaked profiles are present we associate this to
-the presence of inflows and outflows due to the asymmetry of the line
-, but in the case in which the profile have symmetry we could say that
-gas bulk rotation is the principal effect governing the galaxy. For this reason 
-a detailed study involving inflows/outflows and rotation kinematics would 
-give as better understanding of the $\mathrm{Ly} \alpha$ profiles we 
-measured.
+The presence of single peaked profiles has been associated to
+inflow/outflow dynamics \citep{XXX}. In this paper we show that gas
+bulk rotation can also be considered as a probable origin for that
+behaviour, provided that the observed single peak is highly
+symmetric. Similarly, in the case of double peaked lines with a high
+level of flux at the line center, rotation also deserveds to be considered in
+the pool of possible bulk flows responsible for that feature,
+specially if the two peaks have similar intensities. The case of
+triple peaked lines is another clear feature of gas rotation, this
+time with the additional condition of an off-centered emission.
 

### 2013-10-23 paper/ms.tex
minor update in the conclusions

@@
 \label{sec:conclusions}
-In this paper we have estimated the effects of gas bulk rotation on
-the emission  of the Lyman $\alpha$ line. We based the study on the
-study of a simplified configuration of an homogeneous sphere rotating
-as a solid body. We explored  a range of models by varying the
+In this paper, we have estimated the effects of gas bulk rotation on
+the morphology of the Lyman $\alpha$ line in galaxies. The results are
+based on the study of a set of simplified configuration of an
+homogeneous sphere rotating as a solid body. We explored  a range of models by varying the
 rotation speed, hydrogen optical depth, dust optical depth and initial

### 2013-10-25 paper/ms.tex
editting the results section

--- 2013-10-23 paper/ms.tex
@@
 Gas bulk rotation has a noticeable effect on the morphology of the
- \ly line. In this section we discuss the observational implications 
- of these findings.
+ \ly line. In this section we discuss the implications of this
+ findings for the interpretation of available observational data. Our
+ dicussion will focus on the qualitative aspects of diverse
+ morpohological features observerd by \cite{Kulas12} ans \cite{Yamada2012}
 
-We start by a quantitative discussion of the line morphology. Here we
-follow a classification of $Ly\alpha$ profiles made by
+We follow a classification of $Ly\alpha$ profiles made by
 \cite{Kulas12}. They presented observational results for star forming
 galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
-They classified the observed lines into four groups. In Group I the
-red peak is stronger than the blue, in Group II the blue peak is
+They classified the observed lines into five groups. In Group I the
+red peak is stronger than the blue, while in Group II the blue peak is
 stronger, in both cases the peaks are symmetrically located around the
@@
 \label{sec:conclusions}
-In this paper we have estimated the effects of gas bulk rotation on
-the emission  of the Lyman $\alpha$ line. We based the study on the
-study of a simplified configuration of an homogeneous sphere rotating
-as a solid body. We explored  a range of models by varying the
-rotation speed, hydrogen optical depth, dust optical depth and initial
-distribution of Ly$\alpha$ photons with respect to the gas
-density. This was implemented in CLARA, a Monte-Carlo
-radiative transfer code already used to study the Lyman $\alpha$
-line.
+
+In this paper, we have estimated the effects of gas bulk rotation on
+the morphology of the Lyman $\alpha$ line in star forming
+galaxies. The results are based on the study of an homogeneous sphere
+rotating as a solid body. We explored  a range of models by varying
+the rotation speed, hydrogen optical depth, dust optical depth and
+initial distribution of Ly$\alpha$ photons with respect to the gas
+density. As a cross-validation, we obtaine our results from two
+independently developed Monte-Carlo radiative transfer codes.
 
@@
 rotation increase also the width increase in a factor of $2-3$ in comparison 
-with the static case. 'We also take into account the influence of the observer 
-viewing angle, we found that observers with a line of sight perpendicular  
-to the axis of rotation measure a $15\%$ larger line width than those 
-aligned with the rotation axis.'
+with the static case.
 

### 2013-10-25 paper/ms.tex
more editting in the conclusions

@@
 
-As first we see how the width of the line changes using a modified FWHM
-explained in section \ref{sec:widthpeak}, and we found that as gas bulk 
-rotation increase also the width increase in a factor of $2-3$ in comparison 
-with the static case.
+Our main result is that rotation clearly impacte the \ly line
+morphology. Double peaked lines can make transitions into single
+peaked lines as the rotational velocity increases, off-centered
+can result into triple peaked lines.
 
-As many observational spectra Ly$\alpha$ emission line (Kulas et al, Yamada et al)
-is double  peaked, these peaks provide important information
-concerning gas kinematics and geometry,  which can be partially
-explained with inflows/outflows of gas content.  We study the effect
-of rotation in the position of this peaks, and we find  that the
-position of the maxima does change with rotation for the homogeneous
-models when the double peak merged into a single peak as velocity
-increase. This effect is not seen for the central distribution when
-the double peak  remains constant as the velocity increase. We also
-find that there is no dependency in the observer viewing angle with
-the maxima position.
+We have quantified the results in different aspects. In Section
+\ref{sec:widthpeak} we show that the line width increases up to a
+factor of $2-3$ in comparison to the static case. Simultaneously, the
+flux in the line center also increases with rotational velocity. This
+increase induces the transition form a double peak to a single peak
+line in the models where the radiation sources are homogeneusly
+distributed.
+
+In the case of homogeneously distributed sources, the changes in
+line morphology are linked to the reduction in the average number of
+scatterings. In the second part of Section \ref{sec:widthpeak} we show
+that, as rotational velocity increases, a large fraction of photons
+escape with less than $10$ scatterings. This makes highly improbable
+that a photon's frequency can move away from the line's center.
+
+In contrast, for centrally located sources, the number of scatterings
+does not significantly decrease. However, due to the increasing
+bulk velocity of the gas, each scattering is inefficient in shifting
+photons away from the line's center.
+
+The changes in the number of scattering has a direct bearing on the
+escape fraction. In Section \ref{}
 
@@
 case.
+
+As many observational spectra Ly$\alpha$ emission line (Kulas et al,
+Yamada et al) is double  peaked, these peaks provide important information
+concerning gas kinematics and geometry,  which can be partially
+explained with inflows/outflows of gas content.  We study the effect
+of rotation in the position of this peaks, and we find  that the
+position of the maxima does change with rotation for the homogeneous
+models when the double peak merged into a single peak as velocity
+increase. This effect is not seen for the central distribution when
+the double peak  remains constant as the velocity increase. We also
+find that there is no dependency in the observer viewing angle with
+the maxima position.
 

### 2013-10-25 paper/ms.tex
editting the conclusions

@@
 that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings. This makes highly improbable
-that a photon's frequency can move away from the line's center.
+escape with less than $10$ scatterings. On average there are $40\%$
+less scatterings. This makes highly improbable that a photon's
+frequency can move away from the line's center.
 
@@
 
-The changes in the number of scattering has a direct bearing on the
-escape fraction. In Section \ref{}
-
-Concerning the escape fraction under rotational effects on the
-Ly$\alpha$ emission line, we found that the escape fraction increase
-in about $20\%-30\%$for the homogeneous sphere model. While rotational
-effects are negligible for the central models and the escape fraction
-remains constant. Also the observer viewing angle have no effect in
-the escape fraction neither for the homogeneous and central
-models. Complementing this analysis we study the average number of
-scatterings $<N_{scatt}>$ that photons perform before escaping of the
-cloud taking into account rotational effects. The main result here is
-for the homogeneous models for which as velocity increase photons
-escape with about $\sim 39\%$  less scatterings than in the static
-case.
+These changes in the number of scatterings have a direct bearing on
+the escape fraction in the presence of dust.  In Section
+\ref{sec:escapefraction} we find that the escape fraction increases in
+$20\%-30\%$ for the homogeneous source distribution. In the centrally
+located emission, the rotational effects are negligible on the escape
+fraction.
 

### 2013-10-28 paper/ms.tex
edits in: author list, abstract and introduction

@@
 \author{
-  Nicolas Garavito-Camargo\altaffilmark{1},
+  Juan N. Garavito-Camargo\altaffilmark{1},
   Jaime E. Forero-Romero\altaffilmark{1},
@@
 \begin{abstract}
-We present novel results of radiative transfer calculations to measure
+We present results of radiative transfer calculations to measure
 the impact of gas bulk rotation on the morphology of the Lyman
@@
 Lyman $\alpha$ photons escaping in the line center increase with
-the rotational velocity. For large
-rotational velocities and high Hydrogen optical depths the outgoing
-line presents single peak a the line center. This trend is more
-pronounced for radiation sources homogeneously distributed in the
-sphere. Rotation also increases by a factor of $2$ the escape fraction for
-systems with homogeneously distributed sources. For radiation sources
-located off-center, the line morphology presents a range of single,
-double and triple peaked lines. This work demonstrates that gas bulk
-rotation has a non negligible impact on the morphology of the Lyman
-$\alpha$ line.
-
+the rotational velocity. In the case of homogeneously distributed
+sources, for large rotational velocities the line transforms from a
+double peak to a single peak a the line center. Under the same
+conditions the escape fraction increases by a factor of $\sim 2$. For
+radiation sources located off-center, the line morphology presents a
+range of single, double and triple peaked lines. We show how these results are
+useful to interpret recent spectroscopic results of distant $z\sim 2-3$ star
+forming galaxies.
 \end{abstract}
@@
 line. Due to the resonant nature of this line, these physical factors
-include temperature, density and bulk velocity field of the neutral
+notably include temperature, density and bulk velocity field of the neutral
 Hydrogen in the emitting galaxy and its surroundings.
 
-A basic understanding for the quantitative behaviour of the \ly line
+A basic understanding of the quantitative behaviour of the \ly line
 has been reached through analytical studies in the case of a static
@@
 
-A more detailed quantification of the \ly line has been reached using
+A quantitative description of the \ly line has been reached through
 Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. In the last
-two decades these studies have become more popular due to the
+two decades these studies have become popular due to the
 availability of computing power. Early into the 21st century the first
-studies focused on on homogeneous and static media
+studies focused on homogeneous and static media
 \citep{Ahn00,Ahn01,Zheng02}. Later on the effects of clumpy media
@@
 been applied to the results of high resolution hydrodynamical
-simulations \citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Recent developments have been
-focused on the study of clumpy outflows \citep{DijkstraKramer}and
-anisotropic velocity configurations \citep{Zheng2013}.
+simulations of individual
+galaxies\citep{Laursen09,Barnes11,Verhamme12,Yajima12}. While, recent
+developments have been focused on the systematic study of clumpy
+outflows \citep{DijkstraKramer}and anisotropic velocity configurations
+\citep{Zheng2013}.
 
@@
 systematic variations in the \ly line with the viewing angle. These
-variations are a complex superpositions of anisotropic density
+variations are a complex superposition of anisotropic density
 configurations (i.e. edge-on vs. face-on view of a galaxy), the
@@
 physically correspond to the circumgalactic and intergalactic medium
-(CGM and IGM). These effects have been systematically studied
-different anisotropic models of hydrogen clouds  varying the density
-and wind characteristics \citep{Zheng2013}.
+(CGM and IGM). These effects are starting to be studied
+ in simplified configurations that vary the density and wind
+ characteristics \citep{Zheng2013}.
 
-However, in all these systematics efforts the effect of rotation,
+However, in all these efforts the effect of rotation,
 which is an ubiquitous feature in galaxies, has not been
 systematically studied. The processing of the \ly photons in a
-rotating interstellar medium (ISM) must have an impact in the line
-morphology. It is necessary to investigate to what extent bulk gas
-rotation has an measurable impact in the \ly alpha line.
+rotating interstellar medium (ISM) must have some kind of impact in
+the \ly line morphology.
 
@@
 $\alpha$ line. We focus on a simplified system, a spherical gas cloud
-with homogeneous density and solid body rotation. We focus our study
-on the line morphology, anisotropic integrated emission and the escape
-fraction in the presence of dust. We base our work on two independent
-Monte Carlo based radiative transfer codes CLARA \citep{CLARA} and XX
-\citep{DijkstraKramer} .
+with homogeneous density and solid body rotation, to study the line
+morphology and the escape  fraction in the presence of dust. We base
+our work on two independent Monte Carlo based radiative transfer codes
+CLARA \citep{CLARA} and XX \citep{DijkstraKramer} .
 
@@
 rotation into the Monte Carlo codes, paying special attention to coordinate
-definitions. There we also list the different physical parameters in
-the simulated grid of models. In the next section we present the
+definitions. We also list the different physical parameters in
+the simulated grid of models. In the next \S \ref{sec:results} we present the
 results of the simulations, with special detail to quantities in the
-line that show a clear evolution as a function of the cloud's
+line that show a clear evolution as a function of the sphere
 rotational velocity. In \S \ref{sec:dicussion} we discuss the

### 2013-10-28 paper/ms.tex
edits: models and table 1

@@
 line that show a clear evolution as a function of the sphere
-rotational velocity. In \S \ref{sec:dicussion} we discuss the
+rotational velocity. In \S \ref{sec:discussion} we discuss the
 implications of our results in the interpretation of LAEs
@@
 frequency,  $\Delta\nu_{\alpha} \equiv
-\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th} $ is the doppler
+\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the doppler
 broadening of the line which depends on the neutral gas temperature
@@
 a thorough observational account of rotation in galaxies beyond
-$z>1.0$. Furthermore, at low redshifts it has been observed a great
+$z>1.0$. Event at low redshifts there is a great
 variation in the shape of the rotation curve as observed in HI
 emission as a function of the distance to the galaxy center. However
-there are two features that are observed very often. First, in the
-central region the velocity increases proportional to the radius,
-following the behaviour in a body with solid rotation. Second, beyond
-a certain radius the rotation curve tends to flatten.
+there are two recurrent features. First, in the
+central galactic region the velocity increases proportional to the radius,
+following a solid rotation behaviour. Second, beyond a certain radius
+the rotation curve tends to flatten.
 
@@
 
-Following the tradition of studies of Lyman$\alpha$ emitting systems,
-we implement a model with a simplified geometry and gas
-distribution. We assume that the gas is homogeneously distributed in a
-sphere that rotates as a solid body with constant angular
-velocity. This simple model will contain only one parameter: the
-linear velocity at the sphere's surface, $V_{\rm max}$.
+Following the tradition of studies of \ly emitting systems,
+we implement a model with simplified geometry. We assume that the gas
+is homogeneously distributed in a sphere that rotates as a solid body
+with constant angular velocity. This simple model will contain only
+one free parameter: the linear velocity at the sphere's surface, $V_{\rm
+  max}$.
 
@@
 respect to the $z$ axis. Following \cite{Zheng2013} we make the study
-of the anisotropic emission in terms of this angle $\Theta$.
+of the anisotropic emission in terms of this angle..
 
@@
 the dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are in total $60$ models combining all
-the input parameters. Table \ref{table:models} presents a summary of
-all the models.
+with respect to the gas. There are $60$ models intotal combining all
+variations of the input parameters. Table \ref{table:models}
+summarizes the models.
 
@@
 codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
-non-dusty models. The results we report here are robust in the sense
+non-dusty models. The results we report are robust in the sense
 that they are obtained by both codes.

### 2013-10-28 paper/ms.tex
edits in the results section. not done yet.

@@
 distribution for the radiation sources with respect to the sphere:
-central and homogeneous. We find that the line width and the amount of
-Lyman $\alpha$ photons escaping in the line center increase with
-the rotational velocity. In the case of homogeneously distributed
+central and homogeneous. We find that the line width and the intensity
+at the line's center increase with rotational velocity. In the case of homogeneously distributed
 sources, for large rotational velocities the line transforms from a
 double peak to a single peak a the line center. Under the same
-conditions the escape fraction increases by a factor of $\sim 2$. For
+conditions the escape fraction increases $\sim 30\%$. For
 radiation sources located off-center, the line morphology presents a
@@
 The central result of this paper is summarized in Figure
-\ref{fig:differentvelocities}. It shows the considerable
+\ref{fig:differentvelocities}. It shows the evident
 impact of rotation on the morphology of the emergent \ly line. Both
-panels in the Figure focus on the results for $\tau_{H}=10^{7}$,
-showing that the influence of rotation is present both when the
-photons are either homogeneously or centrally initialized over the gas
-volume.
+panels focus on the results for $\tau_{H}=10^{7}$, showing that the
+influence of rotation is present both when the photons are either
+homogeneously or centrally initialized over the gas volume.
 
-In the following subsections we characterize the line morphology by
+In the next subsections we characterize the line morphology by
 the half-width at half intensity and the peak maxima. In order to
@@
 median number of scatter for each \ly photon in the
-simulation. For the models where dust is included we measure the bulk
+simulation. For the models where dust is included we measure the 
 escape fraction as a function of rotational velocity. Finally, we make
@@
 
-To quantify the line broadening we use a modified version of the full
-width at half maximum (FWHM). We measure it only for half of
-the line, $W_{1/2}$. This definition allows us to quantify the line
-width and see the transition from double to single peak emission.  In the
-case of double peaked emission $W_{1/2}$ corresponds to the width of a
-single peak, while in the extreme case of high rotational velocities,
-when the double peak is erased, it simply correspond to half FWHM.
-
-Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases with
-rotational velocity. Continuous (dashed) lines connect the results for
-homogeneous (central) source distribution. For the temperature
-$T=10^4$K used in our radiative transfer calculations the thermal
-velocity is $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it means
-that the half-width can increase up to $350$\kms (at $V_{\rm
-  max}=300$\kms) compared to a half-width of $150$\kms in the static
-case.
+To quantify the line broadening we use the width at half maximum
+(FWHM), $W$. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
+with rotational velocity. Continuous (dashed) lines connect the
+results for homogeneous (central) source distribution. For the
+temperature $T=10^4$K used in our radiative transfer calculations the
+thermal velocity is $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it
+means that the FWHM increase up to $350$\kms (at $V_{\rm
+  max}=300$\kms) compared to $150$\kms in the static case.
 
@@
 constant until beyond some velocity threshold the line becomes single
-peaked with $x_{\rm max}=0$ \kms.
+peaked with $x_{\rm m}=0$ \kms.
 
-The transition to a single peak line seems to occur for systems
-where it becomes easier for the bulk of the photons to escape with the lowest
+The transition to a single peaked line seems to occur in systems
+where it is easier for the bulk of the photons to escape with the lowest
 number of scatterings possible, allowing them not to move very far
@@
 For the central emission the transition to a single peak is never
-completed in the range of parameters explored here. The non appearance
+completed in the range of explored parameters. The non appearance
 of a single peak phase can be in part explained to the absence of a
@@
 line center as the rotational velocity increases. This hints that the
-encounters with a non static medium are inefficient in changing a
-photons' frequency outside the line center.
+encounters with a non static medium are inefficient in pushing photons
+outside the line's center.
 
-In the next section we quantify the number of scatterings and explore
-to what extent this is related to the emergence of single peak.
+In the next sub-section we quantify the number of scatterings and explore
+to what extent this is related to the emergence of single peaked emission.
 
@@
 \caption{Logarithm of the average number of scatterings as function of
-  the velocity. Continuous/dashed lines represent an
-  homogeneous/central distribution of sources. \label{fig:Nscatt}}    
+  rotational velocity velocity. Continuous (dashed) lines represent an
+  homogeneous (central) distribution of sources. \label{fig:Nscatt}}    
 \end{figure}
@@
 \end{center}
-    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) pannels
+    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
       show the homogeneous (central) source distribution. Left
@@
 
-The number of times that a \ly photon is absorbed and re-emitted is
-affects the final frequency that it will have after escaping the
-galaxy. In the case of static gas geometries, a large value of the
-optical depth correlates with a high number of
-scatterings. This increases the probability of finding
-a \ly photon far from the center of the line. In summary, the peak
-maxima shift away form the line center as the amount of neutral
-hydrogen increases.
+The number of \ly photon scatterings affects its final frequency after
+escaping the galaxy. In static gas geometries, a large value of the
+optical depth correlates with a high number of scatterings, increasing
+the probability of finding a \ly photon far from the center of the
+line. In these cases the peak maxima shift away form the line center as
+the amount of neutral hydrogen increases.
 
@@
 $V_{\rm max}$. For the central distributions the average number of
-scatterings has a modes change for increasing rotational
+scatterings has a modest change for increasing rotational
 velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
@@
 infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}. In static spheres 
-with centrally distributed sources we find $\langle N_{\rm
+\citep{Adams72,Harrington73}. In the spheres with centrally
+distributed sources we find $\langle N_{\rm
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depths
@@
 there is a clear decrease of $\langle N_{\rm  scatt}\rangle$ as the
-$V_{\rm max}$ increases. This effect more pronounced for the lower
+$V_{\rm max}$ increases. This effect is more pronounced for lower
 values of the optical depth. For $\tau_{\rm H}=10^5$ the average
@@
 
-The analytic expectation for the slab with homogeneously emitted
+The analytic expectation for the slab with homogeneously distributed
 sources is $\langle N_{\rm  scatt}\rangle=1.16\tau_{\rm   H}$
@@
   scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents 
-  a factor of $(0.66, 0.59, 0.51)$ lower than the centrally emitted photons.
+  factors of $(0.66, 0.59, 0.55)$ lower than the centrally emitted
+  photons.
 
-In order to gain a deeper understanding of these results we prepare 2D
+In order to gain a deeper understanding of these results we make 2D
 histograms for the number of scatterings as a function of the outgoing
 dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
-the results of such histogram in the case $\tau_{\rm H}=10^5$ for the
+such histogram in the case $\tau_{\rm H}=10^5$ for the
 static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
@@
 scale is logarithmic in the number of photons at a certain value
-$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
-the photosphere in the homogeneous distribution, in this case most of
+$x-N_{\rm scatt}$.
+
+Figure \ref{fig:Nscatt2D} supports our hypothesis about
+the photosphere in the homogeneous distribution. In that case most of
 the photons that left with $x\sim 0$ have escaped with less than $10$
-scatterings, explaining the origin of a single central
+scatterings. This explains the origin of a single central
 peak. However, for a central distribution the situation is
@@
 
-We also study a dusty cloud configuration to measure the effect of
-rotation on the escape fraction. We expect that the modified number of
-scatterings to be reflected in this amount of photons absorbed by
-dust. Following this line of thought,  we do not expect any change in
-for a dusty cloud with central source of radiation given that the
-number of scatterings remains close to constant. On the other hand, in
-the case of an homogeneous radiation source the number of scatterings
-drops as $V_{\rm max}$ increases, which might be reflected as an
-increasing escape fraction.
+The average number of scatterings is also reflected in the amount of
+photons absorbed by dust. Under this considerations we do not expect
+any change in the escape fraction for a dusty cloud with central
+source of radiation given that the number of scatterings remains close
+to constant. On the other hand, in the case of an homogeneous
+radiation source the number of scatterings drops as $V_{\rm max}$
+increases, which has to be reflected as an increasing escape fraction.
 
 Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
-a function of the maximum rotational velocity, confirming that our
-intuitions in this respect is correct. For the central source
+a function of the maximum rotational velocity, confirming our expectations. For the central source
 distribution the escape fraction barely shows any change, while for
@@
 the models with low optical depth $\tau_{\rm H}=10^5$,$10^{6}$, where
-it can raise from $(0.26, 0.28)$ respectively in the static case up to $(0.37, 0.39)$ at $V_{\rm
-  rot}=300$\kms.
+it can rise from $(0.26, 0.28)$ ($V_{\rm}=0$\kms) up to $(0.37, 0.39)$ ($V_{\rm
+  rot}=300$ \kms).
 
@@
 \ref{fig:efvsNeufeld} correspond to the cases of different
-velocities. We observe that the escape fraction is higher
-by factors of $2-10$  than the expected values for the slab
-configuration. We also see that for the lower value $\tau_{\rm
-  H}=10^{5}$ the escape fraction does not increase with respect to the
-solution for $\tau_{\rm H}=10^{6}$ as expected, however we not that we
-are in a regime where the condition for the analytic expectations 
-($a\tau_{h}\gg 1$) does not hold.
+velocities. First of all we note that the escape fraction does not
+increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
+explained because we are in a regime where the condition for the
+analytic expectations  ($a\tau_{h}\gg 1$) does not hold. This figure
+also shows that the escape fraction is higher by factors of $2-10$
+than the expectation for a slab with centrally distributed
+sources. Furthermore, the decrease of the escape fraction with
+increasing optical depth is also slower.
 
@@
 
-As we know there is unlikely to find galaxies with radiation sources 
-distributed homogeneously. Most of them are in a clumpy distribution 
-(Laursen et al 2013*) which affected the resulting spectra. In order 
-to study an inhomogeneous distribution we set up a model in which we 
-select certain photons that are placed in a specific place but that 
-are not symmetrically distributed Fig. \ref{fig:OCspheres} shows the 
-distributions we set up, basically we take photons located in a sphere
- of $0.5 R$ where $R$ is the radii of the homogeneous sphere and 
-we choose two spheres in each side of the $\hat{\textbf{x}}$ axis,
-two at $\mp 0.25 R$ and the other two at $\mp 0.5 R$.
-
 \begin{figure}
   \includegraphics[scale=0.3]{OF_spheres.png}
-\caption{The two solid circles show up the photons we select in order to make the anisotropic emission
-		rotation is defined to be $\mathrm{z}$-axis. we also select photons in the negative side of 				        $\mathrm{x}$ (dashed circles) in order to see the complete effect of rotation. 
+  \caption{The two solid circles show the two different spherical off-centered emitting
+    regions. The angular velocity vector is defined to be along the
+    $\hat{\i}$ direction and the observer is along the $\hat{\j}$ direction (where
+    the reader is). 
     \label{fig:OCspheres}} 
@@
 
-We study the deviations of the received flux on the surface of the
+The model with homogeneous radiation sources allows to study the
+effect of radiation sources distributed with a different symmetry than
+the gas. We select photons emitted in spheres that are off-centered
+with respect to the gas distribution.
+
+Figure \ref{fig:OCspheres} shows the 
+two spherical regions we define. Each has a radius of $0.5$R and can
+have to possible centers positions $C$ along the $\hat{\i}$ direction:
+$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
+direction, such that the emitting sphere centered on $+C\hat{\i}$ moves away
+from the observer and the sphere centered on $+C\hat{\i}$ moves towards
+the observer. We consider two values for $C=(0.25,0.50)R$.
+
+We study first the deviations of the received flux on the surface of the
 sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
@@
 
-For the central and homogeneous source distributions we find
-that for observers located at  $\theta = pi/2$ the
-angular dependency represented by $\mu$ doesn't show a considerable
-variation in particular the observer would infer luminosities 
-different from the isotropical value only at levels $< 3\%$.
+For the central and homogeneous source distributions we find that the
+level of isotropy angular dependency represented by $\mu$ doesn't show
+a considerable variation in particular the observer would infer
+luminosities  different from the isotropical value only at levels $<
+3\%$. This values were obtained for a run with $V_{\rm max}=XX$ and
+$\tau_{\rm H}=XXX$ and $N_{\gamma}=10^{6}$ photons.
 
-In the case of the Off-center model with the set up showed in 
-Fig.\ref{fig:OCspheres} where the galaxy is rotating around the  
-$\hat{\textbf{z}}$ axis and the observer is also located at 
-$\mathrm{\theta = \pi/2}$, For the special purpose to get a
-better sample we used $\tau_{\gamma} = 10^{6}$. The first result 
-we get is that the angular dependency is almost the same for 
-all the models with different $\tau_{H}$ and $V_{max}$ for 
-$R = 0.25$. While for spheres located at and $R = 0.5$ show 
-variation in the flux in values $< 14 \%$ in particular at 
-$\mu = 0$ the flux in stronger. This results are shown 
-in Fig. \ref{fig:OCflux}.
+%%%%%%%
+
+The outgoing spectra for two different spheres located at $\pm 0.5R$ 
+are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
+the resulting profiles show new interesting morphologies than are not
+found in the $\pm 0.25R$ case.
 
@@
 \end{figure}
-
-The outgoing spectra for two different spheres located at $\pm 0.5R$ 
-are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
-the resulting profiles show new interesting morphologies than are not
-found in the $\pm 0.25R$ case.
 

### 2013-10-28 paper/ms.tex
Fixed Fig. 11 labels
New paragraph in off center emission

@@
 effect of radiation sources distributed with a different symmetry than
-the gas. We select photons emitted in spheres that are off-centered
+the gas. We select photons emitted in spheres that are off-centred
 with respect to the gas distribution.
@@
 two spherical regions we define. Each has a radius of $0.5$R and can
-have to possible centers positions $C$ along the $\hat{\i}$ direction:
+have to possible centres positions $C$ along the $\hat{\i}$ direction:
 $\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
-direction, such that the emitting sphere centered on $+C\hat{\i}$ moves away
-from the observer and the sphere centered on $+C\hat{\i}$ moves towards
+direction, such that the emitting sphere centred on $+C\hat{\i}$ moves away
+from the observer and the sphere centred on $+C\hat{\i}$ moves towards
 the observer. We consider two values for $C=(0.25,0.50)R$.
@@
 the line presents three peaks (blue-shifted, centred, red-shifted),
-For models with ($\left[ \tau = 10^{5}, V=100 km s^{-1} \right]$ ,
-$\left[\tau = 10^6, V=200 km s^{-1} \right]$ and $ \left[\tau = 10^{7}, 
-V=300 km s^{-1}\right]$) the centred line is dominant but the presence of
+to obtain clearest profiles concerning this results we run three models 
+with $\tau_{\gamma}=10^{6}$, This profiles are shown in 
+Fig.\ref{fig:OC_profiles_N6}, where we clearly observe the presence of 
+three peaks, and also we do not find any asymmetry in the line 
+produced by the off-center emission.
+
+For models with ($[\tau = 10^{5}, V=100 km s^{-1}]$ ,
+$[\tau = 10^6, V=200 km s^{-1}]$ and $ [\tau = 10^{7}, 
+V=300 km s^{-1}]$) the centred line is dominant but the presence of
 the redder and bluer peak in also present which is also a new result.
@@
    \label{fig:OC_profiles}} 
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{NewPanel_N6_atpm5.png}
+\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
+green lines represents spheres locate at $-0,5R$ while red lines 
+represents spheres at $0.5R$)
+   \label{fig:OC_profiles_N6}} 
 \end{figure*}
@@
 the highest peak). Finally, the triple peaked lines in Galaxies in
-Group V can be easily reproduced by rotation with off-centered
+Group V can be easily reproduced by rotation with off-centred
 emission.
@@
 for 91 LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
-a single peak profile. Some of the peaks have a stron symmetry, while
-others do not. The symmetric single peaked progile can be explained by
-rotation effects, while the assymetric cases naturally arise in
+a single peak profile. Some of the peaks have a strong symmetry, while
+others do not. The symmetric single peaked profile can be explained by
+rotation effects, while the asymmetric cases naturally arise in
 outflow/inflow models \citep{Verhamme2008, Dijkstra06}. Among the 91
@@
 symmetric. Similarly, in the case of double peaked lines with a high
-level of flux at the line center, rotation also deserveds to be considered in
+level of flux at the line center, rotation also deserves to be considered in
 the pool of possible bulk flows responsible for that feature,
@@
 triple peaked lines is another clear feature of gas rotation, this
-time with the additional condition of an off-centered emission.
+time with the additional condition of an off-centred emission.
 
@@
 initial distribution of Ly$\alpha$ photons with respect to the gas
-density. As a cross-validation, we obtaine our results from two
+density. As a cross-validation, we obtain our results from two
 independently developed Monte-Carlo radiative transfer codes.
 
-Our main result is that rotation clearly impacte the \ly line
+Our main result is that rotation clearly impact the \ly line
 morphology. Double peaked lines can make transitions into single
-peaked lines as the rotational velocity increases, off-centered
+peaked lines as the rotational velocity increases, off-centred
 can result into triple peaked lines.
@@
 increase induces the transition form a double peak to a single peak
-line in the models where the radiation sources are homogeneusly
+line in the models where the radiation sources are homogeneously
 distributed.

### 2013-10-28 paper/ms.tex
Coments about mu in the off-center

@@
 luminosities  different from the isotropical value only at levels $<
-3\%$. This values were obtained for a run with $V_{\rm max}=XX$ and
-$\tau_{\rm H}=XXX$ and $N_{\gamma}=10^{6}$ photons.
+3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
+100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
+10^{7}$ and $N_{\gamma}=10^{5}$ photons.
 
+For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
+$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
+ $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
+$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
+$\bigtriangleup\mu\leq 15\%$.
 %%%%%%%

### 2013-10-29 paper/ms.tex
Comments about new plots
corrected some typos

@@
 \ly line is that double peaks broaden and reduce their intensity
-while the line center rises. This produces the impression that, as the
+while the line center rises. This gives the impression that, as the
 rotational velocity increases, the double peaks are merged into a
@@
 region with $\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical
-depth from the radius of emission to the sphere's surface. This
+depth from the radius of emission to the sphere's surface. These
 conditions allows the photons to escape with much less scatterings
@@
 the probability of finding a \ly photon far from the center of the
-line. In these cases the peak maxima shift away form the line center as
+line. In these cases the peak maxima shifts away from the line center as
 the amount of neutral hydrogen increases.
@@
 comparison to the static case.
+
+%NEXT PARAGRAPH IS STRANGE
 
@@
 peak. However, for a central distribution the situation is
-different. In this case the number of scatterings remains high, on the
+different. In this case the number of scatterings remains high, in the
 order of the optical depth, but the two peaks do get closer to each
@@
    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
-   the infinite is slab shown as a continuous line. Different dashed
+   the infinite slab is shown as a continuous line. Different dashed
    lines correspond to different rotational velocities.
@@
 The average number of scatterings is also reflected in the amount of
-photons absorbed by dust. Under this considerations we do not expect
+photons absorbed by dust. Under these considerations we do not expect
 any change in the escape fraction for a dusty cloud with central
 source of radiation given that the number of scatterings remains close
-to constant. On the other hand, in the case of an homogeneous
+to constant. On the other hand, in the case of a homogeneous
 radiation source the number of scatterings drops as $V_{\rm max}$
@@
 distribution the escape fraction barely shows any change, while for
-the homogeneous case there is a clear rise in the escape fraction for
+the homogeneous case there is a clear increase in the escape fraction for
 high rotational velocities.  Rotation has a higher relative impact in
@@
 the analytical solution for the infinite slab \citep{Neufeld90}. In
-Neufeld's set-up the analytic solution depends solely on the product
+Neufeld's set-up the analytic solution depends uniquely on the product
 $(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
-in the limits $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
+in the limits where $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
 \ref{fig:efvsNeufeld} correspond to the cases of different
@@
 increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
-explained because we are in a regime where the condition for the
+explained since we are in a regime where the condition for the
 analytic expectations  ($a\tau_{h}\gg 1$) does not hold. This figure
@@
 
-\subsection{Off-Centered emission}
+\subsection{Off-Centred emission}
 
@@
   \includegraphics[scale=0.3]{OF_spheres.png}
-  \caption{The two solid circles show the two different spherical off-centered emitting
+  \caption{The two solid circles show the two different spherical off-centred emitting
     regions. The angular velocity vector is defined to be along the
@@
 $\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
-$\bigtriangleup\mu\leq 15\%$.
+$\bigtriangleup\mu\leq 15\%$. This would imply that the amount of flux
+we measure would depend in the angle between our line of sight and 
+the rotation axis of the galaxy. 
 %%%%%%%
@@
 Gas bulk rotation has a noticeable effect on the morphology of the
- \ly line. In this section we discuss the implications of this
+ \ly line. In this section we discuss the implications of these
  findings for the interpretation of available observational data. Our
- dicussion will focus on the qualitative aspects of diverse
- morpohological features observerd by \cite{Kulas12} ans \cite{Yamada2012}
+ discussion will focus on the qualitative aspects of diverse
+ morphological features observed by \cite{Kulas12} ans \cite{Yamada2012}
 
@@
 stronger, in both cases the peaks are symmetrically located around the
-line center. In Group III the blue peak also dominates but there is a
+line center. In Group III the blue peak also dominates but there is an
 overall redward shift of the zero point. Group IV presents two similar
@@
 smaller peaks at the redder and bluer side, a feature that is present
-in our off-center emission models with rotation.
+in our off-centre emission models with rotation.
 
@@
 the morphology of the Lyman $\alpha$ line in star forming
-galaxies. The results are based on the study of an homogeneous sphere
+galaxies. The results are based on the study of a homogeneous sphere
 rotating as a solid body. We explored a range of models by varying
@@
 flux in the line center also increases with rotational velocity. This
-increase induces the transition form a double peak to a single peak
+increase induces the transition from a double peak to a single peak
 line in the models where the radiation sources are homogeneously
@@
 profiles and multi-peaked profiles could be explained by gas bulk 
-rotation present in this LAEs.
+rotation present in these LAEs.
 

### 2013-10-29 paper/ms.tex
fixed some typos

@@
 the impact of gas bulk rotation on the morphology of the Lyman
-$\alpha$ line in galaxies. We model a galaxy as a sphere with an
+$\alpha$ line in galaxies. We model a galaxy as a sphere with a
 homogeneous mixture of dust and hydrogen at a constant
@@
 central and homogeneous. We find that the line width and the intensity
-at the line's center increase with rotational velocity. In the case of homogeneously distributed
+at the line's centre increases with rotational velocity. In the case of homogeneously distributed
 sources, for large rotational velocities the line transforms from a
-double peak to a single peak a the line center. Under the same
+double peak to a single peak at the line center. Under the same
 conditions the escape fraction increases $\sim 30\%$. For
-radiation sources located off-center, the line morphology presents a
+radiation sources located off-centre, the line morphology presents a
 range of single, double and triple peaked lines. We show how these results are

### 2013-11-01 paper/ms.tex
edits in the off-center section

@@
 \begin{figure*}
+\begin{center}
   \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
   \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
+\end{center}
 \caption{Shape of the \ly line for
@@
 \begin{figure}
-  \includegraphics[scale=0.3]{OF_spheres.png}
-  \caption{The two solid circles show the two different spherical off-centred emitting
-    regions. The angular velocity vector is defined to be along the
-    $\hat{\i}$ direction and the observer is along the $\hat{\j}$ direction (where
-    the reader is). 
+  \includegraphics[scale=0.35]{OF_spheres.png}
+  \caption{The two solid circles show the two different spherical
+    off-centred emitting  regions. The angular velocity vector is
+    defined to be along the $\hat{\i}$ direction and the observer is
+    along the $\hat{\j}$ direction (where the reader is). 
     \label{fig:OCspheres}} 
@@
 effect of radiation sources distributed with a different symmetry than
-the gas. We select photons emitted in spheres that are off-centred
+the gas. We select photons emitted in off-centred spheres 
 with respect to the gas distribution.
 
-Figure \ref{fig:OCspheres} shows the 
-two spherical regions we define. Each has a radius of $0.5$R and can
-have to possible centres positions $C$ along the $\hat{\i}$ direction:
-$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
-direction, such that the emitting sphere centred on $+C\hat{\i}$ moves away
-from the observer and the sphere centred on $+C\hat{\i}$ moves towards
-the observer. We consider two values for $C=(0.25,0.50)R$.
+Figure \ref{fig:OCspheres} shows the two spherical regions we
+define. Each has a radius of $0.5$R and can have to possible centres
+positions $C$ along the $\hat{\i}$ direction: $\pm C\hat{\i}$. We also
+place an observer along the $\hat{\j}$ direction, such that the
+emitting sphere centred on $+C\hat{\i}$ moves away from the observer
+and the sphere centred on $+C\hat{\i}$ moves towards the observer. We
+consider two values for $C=(0.25,0.50)R$.
 
-We study first the deviations of the received flux on the surface of the
-sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
-observer located at an angle $\Theta$ (distant observer angle)
-normalized to the isotropic flux:
+We study first the angular deviations of the outgoing photons with respect
+to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
+as a function of the angle $\Theta$ formed by the outgoing photons and
+a fixed direction (the $\vec{k}$ direction in this case). This is
+expressed by
 
@@
 %
-Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
 $\Delta N$ is the number of photons in a angular bin $\Delta
@@
 
-For the central and homogeneous source distributions we find that the
-level of isotropy angular dependency represented by $\mu$ doesn't show
-a considerable variation in particular the observer would infer
-luminosities  different from the isotropical value only at levels $<
-3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
-100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
-10^{7}$ and $N_{\gamma}=10^{5}$ photons.
+In the the off-center emission the variations  in the $\mu$ distribution
+$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
+ $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
+and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
+$\tau$??). This implies a strong dependence of the observed flux on
+the relative position of an observer.  In contrast,the central and
+homogeneous source distributions only show a weak anisotropy at the level of
+$\Delta\mu\leq 3\%$.
 
-For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
-$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
- $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
-$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
-$\bigtriangleup\mu\leq 15\%$. This would imply that the amount of flux
-we measure would depend in the angle between our line of sight and 
-the rotation axis of the galaxy. 
-%%%%%%%
+Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
+spheres located at $C=\pm0.5R$.  The most interesting effect is that
+emission is that in  some models ($\tau = 10^6, V=100,200$\kms and $\tau =
+10^7, V=200,300$\kms) the line presents three peaks (blue-shifted,
+centred, red-shifted). However, we do not find any asymmetry in the line 
+produced by the off-center emission. As in the homogeneous / central
+model the line gets broader as the rotational velocity increases.
 
-The outgoing spectra for two different spheres located at $\pm 0.5R$ 
-are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
-the resulting profiles show new interesting morphologies than are not
-found in the $\pm 0.25R$ case.
+The results for the off-centered spheres placed closed to the center
+at $C=\pm 0.25R$ do not display the features discussed above for the
+spheres at $C=\pm0.5R$.
 
 \begin{figure}
-\includegraphics[scale=0.3]{mu_OC.png}
-\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
-off-center positions.
-   \label{fig:OCflux}} 
+\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
+  dependency for off-center distribution. Different line widths
+  illustrate different rotational velocities.\label{fig:OCflux}} 
 \end{figure}
-
-The main effect we found in the off-center emission is that for 
-some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
-the line presents three peaks (blue-shifted, centred, red-shifted),
-to obtain clearest profiles concerning this results we run three models 
-with $\tau_{\gamma}=10^{6}$, This profiles are shown in 
-Fig.\ref{fig:OC_profiles_N6}, where we clearly observe the presence of 
-three peaks, and also we do not find any asymmetry in the line 
-produced by the off-center emission.
-
-For models with ($[\tau = 10^{5}, V=100 km s^{-1}]$ ,
-$[\tau = 10^6, V=200 km s^{-1}]$ and $ [\tau = 10^{7}, 
-V=300 km s^{-1}]$) the centred line is dominant but the presence of
-the redder and bluer peak in also present which is also a new result.
-Also as in the homogeneous / central model the line is broader at high 
-rotational velocities.
 
@@
 \includegraphics[scale=0.3]{OC_profiles.png}
-\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
-dashed lines represents spheres locate at $-0,5R$ while solid lines 
-represents spheres at $0.5R$)
+\caption{\ly profiles for the off-center positions. Dashed/solide
+  lines represents spheres centered at $-0,5R/+0.5R$.
    \label{fig:OC_profiles}} 
-\end{figure*}
-
-\begin{figure*}
-\includegraphics[scale=0.3]{NewPanel_N6_atpm5.png}
-\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
-green lines represents spheres locate at $-0,5R$ while red lines 
-represents spheres at $0.5R$)
-   \label{fig:OC_profiles_N6}} 
 \end{figure*}

### 2013-11-01 paper/ms.tex
new edits in the discussion and conclusions

@@
     defined to be along the $\hat{\i}$ direction and the observer is
-    along the $\hat{\j}$ direction (where the reader is). 
+    along the $\hat{\j}$ direction (where the reader is) (THE ANGLE
+    THETA IS WRONG. IT IS THE ANGLE WITH THE OBSERVER, RIGHT?). 
     \label{fig:OCspheres}} 
@@
 
-The model with homogeneous radiation sources allows to study the
-effect of radiation sources distributed with a different symmetry than
-the gas. We select photons emitted in off-centred spheres 
-with respect to the gas distribution.
+The raw data from the model with homogeneous radiation sources allows
+to study the effect of radiation sources distributed with a different
+symmetry than the gas. We can select photons emitted in off-centred spheres 
+with respect to the gas distribution and check whether this produces
+asymetries in the line.
 
 Figure \ref{fig:OCspheres} shows the two spherical regions we
-define. Each has a radius of $0.5$R and can have to possible centres
-positions $C$ along the $\hat{\i}$ direction: $\pm C\hat{\i}$. We also
-place an observer along the $\hat{\j}$ direction, such that the
-emitting sphere centred on $+C\hat{\i}$ moves away from the observer
-and the sphere centred on $+C\hat{\i}$ moves towards the observer. We
-consider two values for $C=(0.25,0.50)R$.
+define to test for this effect. Each has a radius of $0.5$R and can
+have to possible centres positions $C$ along the $\hat{\i}$ direction:
+$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
+direction, such that the emitting sphere centred on $+C\hat{\i}$ moves
+away from the observer and the sphere centred on $+C\hat{\i}$ moves
+towards the observer. We consider two values for $C=(0.25,0.50)R$.
 
@@
 as a function of the angle $\Theta$ formed by the outgoing photons and
-a fixed direction (the $\vec{k}$ direction in this case). This is
-expressed by
+a the observer. This is expressed by
 
@@
 Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
-spheres located at $C=\pm0.5R$.  The most interesting effect is that
-emission is that in  some models ($\tau = 10^6, V=100,200$\kms and $\tau =
-10^7, V=200,300$\kms) the line presents three peaks (blue-shifted,
-centred, red-shifted). However, we do not find any asymmetry in the line 
-produced by the off-center emission. As in the homogeneous / central
-model the line gets broader as the rotational velocity increases.
+spheres located at $C=\pm0.5R$.  In this case we only use photons that
+have outgoing directions aligned with the observer. The most
+interesting effect is that emission is that in  some models ($\tau =
+10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
+presents three peaks (blue-shifted,centred, red-shifted). However, we
+do not find any asymmetry in the line produced by the off-center
+emission. As in the homogeneous / central model the line gets broader
+as the rotational velocity increases.
 
@@
  findings for the interpretation of available observational data. Our
- discussion will focus on the qualitative aspects of diverse
+ discussion focuses on the qualitative aspects of diverse
  morphological features observed by \cite{Kulas12} ans \cite{Yamada2012}
 
-We follow a classification of $Ly\alpha$ profiles made by
+We follow a classification of \ly profiles made by
 \cite{Kulas12}. They presented observational results for star forming
-galaxies at $z=2$-$3$ that showed multiple peaks in their emission.
+galaxies at $z=2$-$3$ with multiple peaks in their \ly emission.
 They classified the observed lines into five groups. In Group I the
@@
 overall redward shift of the zero point. Group IV presents two similar
-peaks symmetrically located around the zero point. Group V presents
+peaks symmetrically located around the zero point and Group V galaxies show
 three peaks.
 
-The asymmetries in Groups I, II  and III cannot be fully explained by
+The asymmetries in Groups I, II  and III cannot be explained by
 rotation. However, some galaxies in those groups have a high flux between
-the two peaks; an effect that can be induced by rotation. The same
+the two peaks; an effect can be induced by rotation. The same
 argument applies to galaxies in the group IV in which the flux
@@
 Group V can be easily reproduced by rotation with off-centred
-emission.
+emission given the right amount of asymmetry between the emitting
+region and neutral hydrogen distribution.
 
-Another relevant sample of lines was presented by \cite{Yamada2012} 
+Another relevant sample of observations was presented by \cite{Yamada2012} 
 for 91 LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
@@
 specially if the two peaks have similar intensities. The case of
-triple peaked lines is another clear feature of gas rotation, this
-time with the additional condition of an off-centred emission.
+triple peaked lines is another clear feature of gas rotation under the
+additional condition of an off-centred emission.
 
@@
 the morphology of the Lyman $\alpha$ line in star forming
-galaxies. The results are based on the study of a homogeneous sphere
-rotating as a solid body. We explored a range of models by varying
-the rotation speed, hydrogen optical depth, dust optical depth and
+galaxies. The results are based on the study of an homogeneous sphere
+with solid body rotation. We explored a range of models by varying
+the rotational speed, hydrogen optical depth, dust optical depth and
 initial distribution of Ly$\alpha$ photons with respect to the gas
@@
 morphology. Double peaked lines can make transitions into single
-peaked lines as the rotational velocity increases, off-centred
-can result into triple peaked lines.
+peaked lines as the rotational velocity increases. Additional
+off-centred emission can result into triple peaked lines.
 
@@
 
-As many observational spectra Ly$\alpha$ emission line (Kulas et al,
-Yamada et al) is double  peaked, these peaks provide important information
-concerning gas kinematics and geometry,  which can be partially
-explained with inflows/outflows of gas content.  We study the effect
-of rotation in the position of this peaks, and we find  that the
-position of the maxima does change with rotation for the homogeneous
-models when the double peak merged into a single peak as velocity
-increase. This effect is not seen for the central distribution when
-the double peak remains constant as the velocity increase. We also
-find that there is no dependency in the observer viewing angle with
-the maxima position.
+We also studied the effect of rotation in the position of the peaks in
+the line. We find that in the regions with central emission the peaks
+do not shift as rotation increases. However, in the homogeneous models
+the double peak merges into a single peak.
 

### 2013-11-01 paper/ms.tex
typos

@@
 central and homogeneous. We find that the line width and the intensity
-at the line's centre increases with rotational velocity. In the case of homogeneously distributed
+at the line's center increases with rotational velocity. In the case of homogeneously distributed
 sources, for large rotational velocities the line transforms from a
@@
 conditions the escape fraction increases $\sim 30\%$. For
-radiation sources located off-centre, the line morphology presents a
+radiation sources located off-center, the line morphology presents a
 range of single, double and triple peaked lines. We show how these results are
@@
 The detection of strong \ly emission lines has become an essential
-method in extragalactic astronomy to find distant star-forming
+method in extra-galactic astronomy to find distant star-forming
 galaxies
@@
 
-A basic understanding of the quantitative behaviour of the \ly line
-has been reached through analytical studies in the case of a static
+A basic understanding of the quantitative behavior of the \ly line
+has been reached through analytic studies in the case of a static
 configurations, such as uniform slabs
 \citep{Harrington73,Neufeld90} and uniform spheres
-\citep{Dijkstra06}. Analytical studies of configurations including
+\citep{Dijkstra06}. Analytic studies of configurations including
 some kind of bulk flow only include the case of a sphere with a Hubble
@@
 be studied \citep{Verhamme06,Dijkstra06}. Similar codes have applied
-these results to semi-analytical models of galaxy formation \citep{Orsi12} and
-results of large hydrodynamical simulations
+these results to semi-analytic models of galaxy formation \citep{Orsi12} and
+results of large hydrodynamic simulations
 \citep{CLARA,Forero12,Behrens13}. Recently Monte Carlo codes have also
-been applied to the results of high resolution hydrodynamical
+been applied to the results of high resolution hydrodynamic
 simulations of individual
@@
 
-The recent studies of galaxies in hydrodynamical simulations
+The recent studies of galaxies in hydrodynamic simulations
 \citep{Laursen09,Barnes11,Verhamme12,Yajima12} have all shown
@@
 Performing that study is the main goal of this paper. We investigate for the
-first time the impact of rotation on the morphology of the Lyman
-$\alpha$ line. We focus on a simplified system, a spherical gas cloud
+first time the impact of rotation on the morphology of the \ly line. We focus on a simplified system, a spherical gas cloud
 with homogeneous density and solid body rotation, to study the line
@@
 observations and further refinements that can be implemented in the
-theoretical modelling of the \ly line. In the last section we present
+theoretical modeling of the \ly line. In the last section we present
 our conclusions.
@@
 frequency,  $\Delta\nu_{\alpha} \equiv
-\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the doppler
+\nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the Doppler
 broadening of the line which depends on the neutral gas temperature
@@
 Describing the kinematics of gas rotation in all generality is a
-complex task, specially at high redshifts where there is still missing
+complex task, specially at high redshift where there is still missing
 a thorough observational account of rotation in galaxies beyond
-$z>1.0$. Event at low redshifts there is a great
+$z>1.0$. Event at low red-shifts there is a great
 variation in the shape of the rotation curve as observed in HI
@@
 central galactic region the velocity increases proportional to the radius,
-following a solid rotation behaviour. Second, beyond a certain radius
+following a solid rotation behavior. Second, beyond a certain radius
 the rotation curve tends to flatten.
@@
 
- In the MonteCarlo code we define a cartesian coordinate system to
+ In the Monte Carlo code we define a Cartesian coordinate system to
  describe the position of each photon. The origin of this system
@@
 the dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are $60$ models intotal combining all
+with respect to the gas. There are $60$ models initial combining all
 variations of the input parameters. Table \ref{table:models}
@@
 is easily achieved in the homogeneous source distribution. In this
-case there is a fraction of the photons that are inside a photosphere
+case there is a fraction of the photons that are inside a photo-sphere
 region with $\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical
@@
 Increasing the rotational velocity $V_{\rm max}$ reduces
-the optical depth making the photosphere region effectively larger,
-increasing the number of photons escaping close to the lines's
+the optical depth making the photo-sphere region effectively larger,
+increasing the number of photons escaping close to the line's
 center. In our models we find the following correspondence between the
@@
 of a single peak phase can be in part explained to the absence of a
-photosphere, as is the case in the homogeneous
+photo-sphere, as is the case in the homogeneous
 distribution. Nevertheless, there is a rise in the intensity at the
@@
       corresponds to the static case and the right
-      $V_{max}=300km/s$. The colour scale is logarithmic on the
+      $V_{max}=300km/s$. The color scale is logarithmic on the
       number of photons with given values of $N_{\rm scatt}$ and
@@
 
-%NEXT PARAGRAPH IS STRANGE
-
-The analytic expectation for the slab with homogeneously distributed
-sources is $\langle N_{\rm  scatt}\rangle=1.16\tau_{\rm   H}$
-\citep{Harrington73}, a factor of $0.72$ lower than the case of the
-centrally emitted photons. In our case we find that for the static
-, while for homogeneously distributed source $\langle N_{\rm
-  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents 
-  factors of $(0.66, 0.59, 0.55)$ lower than the centrally emitted
-  photons.
+The analytic expectation for the average number of scatterigs in a
+slab with homogeneously distributed sources is $\langle N_{\rm
+  scatt}\rangle=1.16\tau_{\rm   H}$ \citep{Harrington73}. This is
+$0.72$ times lower than the same case with photons emitted in the
+slab's center. In our case we find that for the static case and the
+homogeneously distributed sources $\langle N_{\rm scatt}\rangle=
+(0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents factors of $(0.66,
+0.59, 0.55)$ lower than the centrally emitted  photons.
 
@@
 Figure \ref{fig:Nscatt2D} supports our hypothesis about
-the photosphere in the homogeneous distribution. In that case most of
+the photo-sphere in the homogeneous distribution. In that case most of
 the photons that left with $x\sim 0$ have escaped with less than $10$
@@
 In Figure \ref{fig:efvsNeufeld} we put these results in the context of
-the analytical solution for the infinite slab \citep{Neufeld90}. In
+the analytic solution for the infinite slab \citep{Neufeld90}. In
 Neufeld's set-up the analytic solution depends uniquely on the product
@@
 
-\subsection{Off-Centred emission}
+\subsection{Off-Centered emission}
 
@@
   \caption{The two solid circles show the two different spherical
-    off-centred emitting  regions. The angular velocity vector is
+    off-centered emitting  regions. The angular velocity vector is
     defined to be along the $\hat{\i}$ direction and the observer is
@@
 to study the effect of radiation sources distributed with a different
-symmetry than the gas. We can select photons emitted in off-centred spheres 
+symmetry than the gas. We can select photons emitted in off-centered spheres 
 with respect to the gas distribution and check whether this produces
-asymetries in the line.
+asymmetries in the line.
 
@@
 define to test for this effect. Each has a radius of $0.5$R and can
-have to possible centres positions $C$ along the $\hat{\i}$ direction:
+have to possible centers positions $C$ along the $\hat{\i}$ direction:
 $\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
-direction, such that the emitting sphere centred on $+C\hat{\i}$ moves
-away from the observer and the sphere centred on $+C\hat{\i}$ moves
+direction, such that the emitting sphere centered on $+C\hat{\i}$ moves
+away from the observer and the sphere centered on $+C\hat{\i}$ moves
 towards the observer. We consider two values for $C=(0.25,0.50)R$.
@@
 10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
-presents three peaks (blue-shifted,centred, red-shifted). However, we
+presents three peaks (blue-shifted,centered, red-shifted). However, we
 do not find any asymmetry in the line produced by the off-center
@@
 the highest peak). Finally, the triple peaked lines in Galaxies in
-Group V can be easily reproduced by rotation with off-centred
+Group V can be easily reproduced by rotation with off-centered
 emission given the right amount of asymmetry between the emitting
@@
 smaller peaks at the redder and bluer side, a feature that is present
-in our off-centre emission models with rotation.
+in our off-center emission models with rotation.
 
@@
 bulk rotation can also be considered as a probable origin for that
-behaviour, provided that the observed single peak is highly
+behavior, provided that the observed single peak is highly
 symmetric. Similarly, in the case of double peaked lines with a high
@@
 triple peaked lines is another clear feature of gas rotation under the
-additional condition of an off-centred emission.
+additional condition of an off-centered emission.
 
@@
 In this paper, we have estimated the effects of gas bulk rotation on
-the morphology of the Lyman $\alpha$ line in star forming
+the morphology of the \ly line in star forming
 galaxies. The results are based on the study of an homogeneous sphere
@@
 the rotational speed, hydrogen optical depth, dust optical depth and
-initial distribution of Ly$\alpha$ photons with respect to the gas
+initial distribution of \ly photons with respect to the gas
 density. As a cross-validation, we obtain our results from two
@@
 peaked lines as the rotational velocity increases. Additional
-off-centred emission can result into triple peaked lines.
+off-centered emission can result into triple peaked lines.
 
@@
 This paper illustrates for the first time the main effects of rotation
-in the morphology of the Ly$\alpha$ emission line, we estimate the
+in the morphology of the \ly emission line, we estimate the
 range of this effects for simplified models.

### 2013-11-14 paper/ms.tex
minor changes

--- 2013-11-01 paper/ms.tex
@@
 
-This paper is paper is structured as follows. In \S
+This paper is structured as follows. In \S
 \ref{sec:implementation} we present the implementation of bulk
@@
 \begin{figure*}
-\begin{center}
   \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
   \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
-\end{center}
 \caption{Shape of the \ly line for
@@
 \begin{figure}
-  \includegraphics[scale=0.35]{OF_spheres.png}
-  \caption{The two solid circles show the two different spherical
-    off-centred emitting  regions. The angular velocity vector is
-    defined to be along the $\hat{\i}$ direction and the observer is
-    along the $\hat{\j}$ direction (where the reader is). 
+  \includegraphics[scale=0.3]{OF_spheres.png}
+  \caption{The two solid circles show the two different spherical off-centred emitting
+    regions. The angular velocity vector is defined to be along the
+    $\hat{\i}$ direction and the observer is along the $\hat{\j}$ direction (where
+    the reader is). 
     \label{fig:OCspheres}} 
@@
 effect of radiation sources distributed with a different symmetry than
-the gas. We select photons emitted in off-centred spheres 
+the gas. We select photons emitted in spheres that are off-centred
 with respect to the gas distribution.
 
-Figure \ref{fig:OCspheres} shows the two spherical regions we
-define. Each has a radius of $0.5$R and can have to possible centres
-positions $C$ along the $\hat{\i}$ direction: $\pm C\hat{\i}$. We also
-place an observer along the $\hat{\j}$ direction, such that the
-emitting sphere centred on $+C\hat{\i}$ moves away from the observer
-and the sphere centred on $+C\hat{\i}$ moves towards the observer. We
-consider two values for $C=(0.25,0.50)R$.
+Figure \ref{fig:OCspheres} shows the 
+two spherical regions we define. Each has a radius of $0.5$R and can
+have to possible centres positions $C$ along the $\hat{\i}$ direction:
+$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
+direction, such that the emitting sphere centred on $+C\hat{\i}$ moves away
+from the observer and the sphere centred on $+C\hat{\i}$ moves towards
+the observer. We consider two values for $C=(0.25,0.50)R$.
 
-We study first the angular deviations of the outgoing photons with respect
-to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
-as a function of the angle $\Theta$ formed by the outgoing photons and
-a fixed direction (the $\vec{k}$ direction in this case). This is
-expressed by
+We study first the deviations of the received flux on the surface of the
+sphere. We follow \cite{Zheng2013} to estimate the flux seen by an
+observer located at an angle $\Theta$ (distant observer angle)
+normalized to the isotropic flux:
 
@@
 
-In the the off-center emission the variations  in the $\mu$ distribution
-$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
- $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
-and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
-$\tau$??). This implies a strong dependence of the observed flux on
-the relative position of an observer.  In contrast,the central and
-homogeneous source distributions only show a weak anisotropy at the level of
-$\Delta\mu\leq 3\%$.
+For the central and homogeneous source distributions we find that the
+level of isotropy angular dependency represented by $\mu$ doesn't show
+a considerable variation in particular the observer would infer
+luminosities  different from the isotropical value only at levels $<
+3\%$. This values were obtained for a run with $V_{\rm max}=(50kms^{-1}, 
+100kms^{-1}, 200kms^{-1}, 300kms^{-1})$ and $\tau_{\rm H}=10^{5}, 10^{6}, 
+10^{7}$ and $N_{\gamma}=10^{5}$ photons.
 
-Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
-spheres located at $C=\pm0.5R$.  The most interesting effect is that
-emission is that in  some models ($\tau = 10^6, V=100,200$\kms and $\tau =
-10^7, V=200,300$\kms) the line presents three peaks (blue-shifted,
-centred, red-shifted). However, we do not find any asymmetry in the line 
-produced by the off-center emission. As in the homogeneous / central
-model the line gets broader as the rotational velocity increases.
+For the Off-center emission Fig.\ref{fig:OCflux} the variations of 
+$\mu$ increase as the rotational velocity increase, for $V_{\rm max}=(50kms^{-1}$
+ $\bigtriangleup\mu \leq 7\%$ , for $V_{\rm max}=(100kms^{-1}$
+$\bigtriangleup\mu\leq 12\%$ and finally for $V_{\rm max}=(200kms^{-1}$
+$\bigtriangleup\mu\leq 15\%$. This would imply that the amount of flux
+we measure would depend in the angle between our line of sight and 
+the rotation axis of the galaxy. 
+%%%%%%%
 
-The results for the off-centered spheres placed closed to the center
-at $C=\pm 0.25R$ do not display the features discussed above for the
-spheres at $C=\pm0.5R$.
+The outgoing spectra for two different spheres located at $\pm 0.5R$ 
+are shown in Fig.\ref{fig:OC_profiles}, we have shown this positions because
+the resulting profiles show new interesting morphologies than are not
+found in the $\pm 0.25R$ case.
 
 \begin{figure}
-\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
-  dependency for off-center distribution. Different line widths
-  illustrate different rotational velocities.\label{fig:OCflux}} 
+\includegraphics[scale=0.3]{mu_OC.png}
+\caption{Flux angular dependency for Off-center distribution, different line widths illustrate different
+off-center positions.
+   \label{fig:OCflux}} 
 \end{figure}
+
+The main effect we found in the off-center emission is that for 
+some models ($\tau = 10^6, V=100 km s^{-1}$ and $\tau = 10^7, V=200 km s^{-1}$)
+the line presents three peaks (blue-shifted, centred, red-shifted),
+to obtain clearest profiles concerning this results we run three models 
+with $\tau_{\gamma}=10^{6}$, This profiles are shown in 
+Fig.\ref{fig:OC_profiles_N6}, where we clearly observe the presence of 
+three peaks, and also we do not find any asymmetry in the line 
+produced by the off-center emission.
+
+For models with ($[\tau = 10^{5}, V=100 km s^{-1}]$ ,
+$[\tau = 10^6, V=200 km s^{-1}]$ and $ [\tau = 10^{7}, 
+V=300 km s^{-1}]$) the centred line is dominant but the presence of
+the redder and bluer peak in also present which is also a new result.
+Also as in the homogeneous / central model the line is broader at high 
+rotational velocities.
 
@@
 \includegraphics[scale=0.3]{OC_profiles.png}
-\caption{\ly profiles for the off-center positions. Dashed/solide
-  lines represents spheres centered at $-0,5R/+0.5R$.
+\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
+dashed lines represents spheres locate at $-0,5R$ while solid lines 
+represents spheres at $0.5R$)
    \label{fig:OC_profiles}} 
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{NewPanel_N6_atpm5.png}
+\caption{$\mathrm{Ly}\alpha$ profiles for the off-center positions.
+green lines represents spheres locate at $-0,5R$ while red lines 
+represents spheres at $0.5R$)
+   \label{fig:OC_profiles_N6}} 
 \end{figure*}

### 2013-12-04 paper/ms.tex
mu

--- 2013-11-01 paper/ms.tex
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{WidthVvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.png}
     \caption{Half-width for the non-dusty models as a function of
@@
 
-In the the off-center emission the variations  in the $\mu$ distribution
+In the off-centre emission the variations in the $\mu$ distribution
 $\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
@@
 
-Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
+Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
 spheres located at $C=\pm0.5R$.  In this case we only use photons that
@@
 10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
-presents three peaks (blue-shifted,centered, red-shifted). However, we
+presents three peaks (blue-shifted,centred, red-shifted). However, we
 do not find any asymmetry in the line produced by the off-center
@@
 
-The results for the off-centered spheres placed closed to the center
-at $C=\pm 0.25R$ do not display the features discussed above for the
-spheres at $C=\pm0.5R$.
+The results for the off-centred spheres placed closer to the centre
+at $C=\pm 0.25R$ do not display such a stronger features discussed above for the
+spheres at $C=\pm0.5R$, there is only one model which slightly shows a 
+three peak morphology with $\mathrm{V=300km s^{1}}$ and $\tau = 10^{7}$.
 

### 2014-01-08 paper/ms.tex
paper update

@@
   \includegraphics[width=0.45\textwidth]{escapefraction.png}
-   \caption{Escape fraction as a function of rotational velocity. The
+   \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
      continuous (dashed) lines correspond to homogeneous (central)
@@
     off-centered emitting  regions. The angular velocity vector is
-    defined to be along the $\hat{\i}$ direction and the observer is
-    along the $\hat{\j}$ direction (where the reader is) (THE ANGLE
-    THETA IS WRONG. IT IS THE ANGLE WITH THE OBSERVER, RIGHT?). 
+    defined to be along the $\hat{\i}$ direction (where the reader is) 
+    and the observer is along the $\hat{\j}$ direction. 
     \label{fig:OCspheres}} 
@@
 define to test for this effect. Each has a radius of $0.5$R and can
-have to possible centers positions $C$ along the $\hat{\i}$ direction:
+have to possible centers positions $C$ along the $\hat{\j}$ direction:
 $\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
-direction, such that the emitting sphere centered on $+C\hat{\i}$ moves
-away from the observer and the sphere centered on $+C\hat{\i}$ moves
+direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
+away from the observer and the sphere centered on $+C\hat{\j}$ moves
 towards the observer. We consider two values for $C=(0.25,0.50)R$.
@@
 spheres located at $C=\pm0.5R$.  In this case we only use photons that
-have outgoing directions aligned with the observer. The most
-interesting effect is that emission is that in  some models ($\tau =
+have outgoing directions aligned with the observer ($\vert \mu \vert > 0.9$ $\&$ $\vert \mu \vert < 1.0]$). The most
+interesting effect is that emission in  some models ($\tau =
 10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
@@
 \includegraphics[scale=0.3]{OC_profiles.png}
-\caption{\ly profiles for the off-center positions. Dashed/solide
+\caption{\ly profiles for the off-center positions. Dashed/solid
   lines represents spheres centered at $-0,5R/+0.5R$.
    \label{fig:OC_profiles}} 
+\end{figure*}
+
+\subsection{Three-Peak Profiles}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{3peaks.png}
+\caption{Three-Peak profiles for the off-center positions. 
+   \label{fig:3p_profiles}} 
+\end{figure*}
+
+As mentioned in Sec 3.4 Off-centered emission shows signs of three peak 
+profiles, to analyse this in more detail we use the same method of the spheres
+explained in Sec 3.4. We select spheres at $C=\pm 0.25, 0.5, 0.75$ for all the 
+models, for those who present signs of three peak profiles such as $(V_{max}=50kms^{1} 
+\& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), (V_{max}=200kms^{1}
+\& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ with the aim 
+of get a stronger profile.
+
+Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
+a relation between optical depth, rotational velocity and $C$ must be accomplish.
+In particular we found that for the outer spheres $C=\pm 0.75$ the three
+peak arise for all of our models with $\tau_{\gamma}=10^{6}$. The main effect of
+the rotational velocity is to give rise to the central peak. If the rotational velocity is 
+high also the optical depth have to be high in order to compensate the height of the wings 
+of the line with the central peak.
+
+Finally we take into account the finite spectral resolution to see if three peaks 
+profiles produced by rotation could be observed. Fig.\ref{fig:3p_res} show that even
+with a low resolution a three-peak profile would be observed.
+
+\begin{figure*}
+\includegraphics[scale=0.3]{3p_res.png}
+\caption{Three-Peak profiles for different resolutions. 
+   \label{fig:3p_res}} 
 \end{figure*}
@@
 
+JNGC thanks the support of Universidad de los Andes given as TA
+Also ISAAC 2012 summer school which provide computer time where some of this 
+models where ran.
+
 \bibliographystyle{apj}

### 2014-01-09 paper/ms.tex
Three peak section

@@
 \subsection{Off-Centered emission}
-
+\label{sec:off-center}
 \begin{figure}
@@
 define to test for this effect. Each has a radius of $0.5$R and can
-have to possible centers positions $C$ along the $\hat{\j}$ direction:
+have two possible centers positions $C$ along the $\hat{\j}$ direction:
 $\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
@@
 away from the observer and the sphere centered on $+C\hat{\j}$ moves
-towards the observer. We consider two values for $C=(0.25,0.50)R$.
+towards the observer. We consider $C=0.5 R$.
 
@@
 
-In the off-centre emission the variations in the $\mu$ distribution
+In the off-center emission the variations in the $\mu$ distribution
 $\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
@@
 spheres located at $C=\pm0.5R$.  In this case we only use photons that
-have outgoing directions aligned with the observer ($\vert \mu \vert > 0.9$ $\&$ $\vert \mu \vert < 1.0]$). The most
-interesting effect is that emission in  some models ($\tau =
-10^6, V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) the line
-presents three peaks (blue-shifted,centred, red-shifted). However, we
-do not find any asymmetry in the line produced by the off-center
-emission. As in the homogeneous / central model the line gets broader
-as the rotational velocity increases.
-
-The results for the off-centred spheres placed closer to the centre
-at $C=\pm 0.25R$ do not display such a stronger features discussed above for the
-spheres at $C=\pm0.5R$, there is only one model which slightly shows a 
-three peak morphology with $\mathrm{V=300km s^{1}}$ and $\tau = 10^{7}$.
+have outgoing directions aligned with the observer ($\vert \mu \vert > 
+0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
+the line produced by the off-center emission, The difference
+ between the profiles corresponding to the spheres located at $C=-0.5R$ 
+ and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
+central model the line gets broader as the rotational velocity also 
+the central part of the line becomes predominant . 
+There is also a signature of possible three peaks profiles for  some models ($\tau = 10^6,
+V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
+in detail in the Sec.\ref{sec:3p}
 
@@
 \subsection{Three-Peak Profiles}
-
+\label{sec:3p}
 \begin{figure*}
@@
 
-As mentioned in Sec 3.4 Off-centered emission shows signs of three peak 
+As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
 profiles, to analyse this in more detail we use the same method of the spheres
-explained in Sec 3.4. We select spheres at $C=\pm 0.25, 0.5, 0.75$ for all the 
-models, for those who present signs of three peak profiles such as $(V_{max}=50kms^{1} 
-\& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), (V_{max}=200kms^{1}
-\& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ with the aim 
-of get a stronger profile.
+explained in that section. We select spheres at $C=\pm 0.25R, 0.5R, 0.75R$ with a radii of
+$0.25R$ for all the models, for those who present signs of three peak profiles such as 
+$(V_{max}=50kms^{1} \& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), 
+(V_{max}=200kms^{1} \& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
+with the aim of get a stronger profile.
 
@@
 In particular we found that for the outer spheres $C=\pm 0.75$ the three
-peak arise for all of our models with $\tau_{\gamma}=10^{6}$. The main effect of
-the rotational velocity is to give rise to the central peak. If the rotational velocity is 
-high also the optical depth have to be high in order to compensate the height of the wings 
-of the line with the central peak.
+peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
+the fact that the wings of the line move away from the central part as $C$ increase. 
+Another requirement is that a high optical must be balanced with a high velocity 
+in order to make the wings and the central peak similar in 
+height.
 
-Finally we take into account the finite spectral resolution to see if three peaks 
-profiles produced by rotation could be observed. Fig.\ref{fig:3p_res} show that even
-with a low resolution a three-peak profile would be observed.
+Fig.\ref{fig:3p_res} show that even with a low resolution a three-peak profile 
+would be observed, this is important for observational porpoises due to the finite 
+spectral resolution.
 

### 2014-01-09 paper/ms.tex
sections 3.4 and 3.5 done

@@
 
-Figure \ref{fig:Nscatt2D} supports our hypothesis about
+The top right panel of Figure \ref{fig:Nscatt2D} supports our hypothesis about
 the photo-sphere in the homogeneous distribution. In that case most of
@@
 away from the observer and the sphere centered on $+C\hat{\j}$ moves
-towards the observer. We consider $C=0.5 R$.
+towards the observer.
 
@@
 as a function of the angle $\Theta$ formed by the outgoing photons and
-a the observer. This is expressed by
+the observer. This is expressed by
 
@@
 
-In the off-center emission the variations in the $\mu$ distribution
-$\mu$ increase with the rotational velocity. For $V_{\rm max}= 50$\kms
- $\Delta \mu \leq 7\%$; $V_{\rm max}=100$\kms, $\Delta \mu\leq 12\%$
-and $V_{\rm max}=200$\kms, $\Delta\mu\leq 15\%$ (NOTE: regardless of
-$\tau$??). This implies a strong dependence of the observed flux on
-the relative position of an observer.  In contrast,the central and
-homogeneous source distributions only show a weak anisotropy at the level of
-$\Delta\mu\leq 3\%$.
+\begin{figure}
+  \includegraphics[scale=0.35]{muhisto.png}
+  \caption{$\mu$ histogram showing the orientation effects for the different
+  distributions Central(Points line), Homogeneous(Dashed) and Off-Center(Solid line).  
+    \label{fig:muhisto}} 
+\end{figure}
+
+The variations in the $\mu$ distribution is shown in Fig.\ref{fig:muhisto},
+for the Off-Center model there is a strong dependence of the 
+observed flux on the relative position of an observer with $\Delta\mu\leq 25\%$.
+In contrast,the central and homogeneous source distributions only show a 
+weak anisotropy at the level of $\Delta\mu\leq 3\%$. On the other hand the variations
+in $\mu$ does not depend on the rotational velocity while increasing the optical depth $\tau_{H}$
+would also increase the variation of $\Delta\mu$ up to a $15\%$.
 
@@
  and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
-central model the line gets broader as the rotational velocity also 
+central model the line gets broader as the rotational velocity increase also 
 the central part of the line becomes predominant . 
@@
 in detail in the Sec.\ref{sec:3p}
-
-\begin{figure}
-\includegraphics[scale=0.35]{mu_OC.png} \caption{Flux angular 
-  dependency for off-center distribution. Different line widths
-  illustrate different rotational velocities.\label{fig:OCflux}} 
-\end{figure}
 
@@
 \label{sec:3p}
+
 \begin{figure*}
@@
 profiles, to analyse this in more detail we use the same method of the spheres
-explained in that section. We select spheres at $C=\pm 0.25R, 0.5R, 0.75R$ with a radii of
+explained in that section. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
 $0.25R$ for all the models, for those who present signs of three peak profiles such as 
-$(V_{max}=50kms^{1} \& \tau_{H}=10^{5}), (V_{max}=100kms^{1} \& \tau_{H}=10^{6}), 
-(V_{max}=200kms^{1} \& \tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
+$(V_{max}=50kms^{1}$ \& $\tau_{H}=10^{5}), (V_{max}=100kms^{1}$ \& $\tau_{H}=10^{6}), 
+(V_{max}=200kms^{1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
 with the aim of get a stronger profile.
@@
 the fact that the wings of the line move away from the central part as $C$ increase. 
-Another requirement is that a high optical must be balanced with a high velocity 
+Another requirement is that a high optical depth must be balanced with a high velocity 
 in order to make the wings and the central peak similar in 

### 2014-01-09 paper/ms.tex
Fixed plots in sec 3.3

@@
 V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
-in detail in the Sec.\ref{sec:3p}
+in detail in \S \ref{sec:3p}.
 
@@
 
-As mentioned in Sec\ref{sec:off-center} Off-centered emission shows signs of three peak 
+As mentioned in \S \ref{sec:off-center} Off-centered emission shows signs of three peak 
 profiles, to analyse this in more detail we use the same method of the spheres
-explained in that section. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
+explained in \S \ref{sec:off-center}. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
 $0.25R$ for all the models, for those who present signs of three peak profiles such as 

### 2014-01-09 paper/ms.tex
Section 3.3 revised

@@
    the infinite slab is shown as a continuous line. Different dashed
-   lines correspond to different rotational velocities.
+   lines correspond to different rotational velocities, for this models 
+   $\tau_a = 1$.
    \label{fig:efvsNeufeld}}   
@@
 increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
-explained since we are in a regime where the condition for the
-analytic expectations  ($a\tau_{h}\gg 1$) does not hold. This figure
-also shows that the escape fraction is higher by factors of $2-10$
+explained since there is a transition from a opaque to an extremely opaque medium
+which affect affects how \ly photons scape from the medium: single flight 
+vs single excursion.
+ %we are in a regime where the condition for the analytic expectations  ($a\tau_{h}\gg 1$) does not hold. 
+This figure also shows that the escape fraction is higher by factors of $2-10$
 than the expectation for a slab with centrally distributed
@@
 increasing optical depth is also slower.
+
+transition from the opaque to
+  extremely opaque medium, which affects how Lya photons escape from
+  the medium: single flight vs single excursion
 

### 2014-01-09 paper/ms.tex
minor changes in text

@@
 \begin{abstract}
-We present results of radiative transfer calculations to measure
-the impact of gas bulk rotation on the morphology of the Lyman
-$\alpha$ line in galaxies. We model a galaxy as a sphere with a
+For the first time the effect of gas bulk rotation on the morphology 
+of the Lyman $\alpha$ line is studied using radiative transfer calculations.
+%We present results of radiative transfer calculations to measure
+%the impact of gas bulk rotation on the morphology of the Lyman $\alpha$ line in galaxies. 
+We model a galaxy as a sphere with a
 homogeneous mixture of dust and hydrogen at a constant
@@
 velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
-for different velocities. In the same setup the average
+for different velocities. In the same set-up the average
 number of scatterings is proportional to the optical depth, as

### 2014-01-09 paper/ms.tex
update conclusions

@@
 \begin{abstract}
-For the first time the effect of gas bulk rotation on the morphology 
-of the Lyman $\alpha$ line is studied using radiative transfer calculations.
-%We present results of radiative transfer calculations to measure
-%the impact of gas bulk rotation on the morphology of the Lyman $\alpha$ line in galaxies. 
+%For the first the effect of gas bulk rotation on the morphology 
+%of the Lyman $\alpha$ line is studied using radiative transfer calculations.
+We present results of radiative transfer calculations to measure
+the impact of gas bulk rotation on the morphology of the Lyman $\alpha$ line in galaxies. 
 We model a galaxy as a sphere with a
@@
 
-In this paper, we have estimated the effects of gas bulk rotation on
-the morphology of the \ly line in star forming
-galaxies. The results are based on the study of an homogeneous sphere
+This paper illustrates for the first time the main effects of rotation
+in the morphology of the \ly emission line in star forming galaxies. 
+The results are based on the study of an homogeneous sphere
 with solid body rotation. We explored a range of models by varying
@@
 peaked lines as the rotational velocity increases. Additional
-off-centered emission can result into triple peaked lines.
+off-centered emission result into triple peaked lines for certain 
+values of optical depth and velocities.
 
-We have quantified the results in different aspects. In Section
-\ref{sec:widthpeak} we show that the line width increases up to a
-factor of $2-3$ in comparison to the static case. Simultaneously, the
+\begin{itemize}
+\item For central sources we find that the number of scatterings
+does not significantly decrease with rotation, this is due to the 
+fact that the vast majority of scatterings events are resonant 
+during which the mean free path is very short and the effect of gas
+bulk rotation is not enough to affect \ly photons.
+The escape fraction does not depend on the rotational velocity neither
+the position of the peaks, but there is an increase 
+in the flux on the central parts of the line for high rotational 
+velocities.
+
+\item For homogeneous sources we find the changes in the
+line morphology are linked to the reduction in the average number of
+scatterings. In the second part of \S \ref{sec:widthpeak} we show
+that, as rotational velocity increases, a large fraction of photons
+escape with less than $10$ scatterings and on average 
+with $40\%$ less scatterings than in the static case. This makes highly improbable 
+that a photon's frequency can move away from the line's center. 
+In \S \ref{sec:widthpeak} For typical column densities of $N_{HI}=1^{19}-1^{20}$, 
+we find that rotational velocities of 100-300 \kms broaden the line profile up 
+to a factor of $2-3$ in comparison to the static case. Simultaneously, the
 flux in the line center also increases with rotational velocity. This
@@
 line in the models where the radiation sources are homogeneously
-distributed.
+distributed. Also the escape fraction increase by factors of $2-10$ with 
+respect to the slab with centrally sources.
 
-In the case of homogeneously distributed sources, the changes in
-line morphology are linked to the reduction in the average number of
-scatterings. In the second part of Section \ref{sec:widthpeak} we show
-that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings. On average there are $40\%$
-less scatterings. This makes highly improbable that a photon's
-frequency can move away from the line's center.
+\item For non-symmetric sources we find that three peak profiles
+could emerge for models in which the rotational velocity is the necessary 
+to give rise to a central peak but also not that high to decrease the
+amount of photons in the wings. When initial off-center sources are 
+selected from the outer parts of the galaxy the wings of the line are stronger.
+Also off-center emission do not produce any considerable asymmetries in the line.\\
+\end{itemize}
 
-In contrast, for centrally located sources, the number of scatterings
-does not significantly decrease. However, due to the increasing
-bulk velocity of the gas, each scattering is inefficient in shifting
-photons away from the line's center.
+%We have quantified the results in different aspects.
 
-These changes in the number of scatterings have a direct bearing on
-the escape fraction in the presence of dust.  In Section
-\ref{sec:escapefraction} we find that the escape fraction increases in
-$20\%-30\%$ for the homogeneous source distribution. In the centrally
-located emission, the rotational effects are negligible on the escape
-fraction.
+%These changes in the number of scatterings have a direct bearing on
+%the escape fraction in the presence of dust.  In Section
+%\ref{sec:escapefraction} we find that the escape fraction increases in
+%$20\%-30\%$ for the homogeneous source distribution. In the centrally
+%located emission, the rotational effects are negligible on the escape
+%fraction.
 
-We also studied the effect of rotation in the position of the peaks in
-the line. We find that in the regions with central emission the peaks
-do not shift as rotation increases. However, in the homogeneous models
-the double peak merges into a single peak.
+%We also studied the effect of rotation in the position of the peaks in
+%the line. We find that in the regions with central emission the peaks
+%do not shift as rotation increases. However, in the homogeneous models
+%the double peak merges into a single peak.
 
@@
 
-This paper illustrates for the first time the main effects of rotation
-in the morphology of the \ly emission line, we estimate the
-range of this effects for simplified models.
-
 \section*{Acknowledgements}
 
-JNGC thanks the support of Universidad de los Andes given as TA
-Also ISAAC 2012 summer school which provide computer time where some of this 
-models where ran.
+JNGC thanks the support of Universidad de los Andes given as teaching assistant, 
+Also to the  ISAAC 2012 summer school in San Diego which provide computer time
+ where some of this models where ran.
 

### 2014-01-09 paper/ms.tex
minor updates

@@
 To quantify the line broadening we use the width at half maximum
-(FWHM), $W$. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
+(FWHM), $W_{1/2}$. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
 with rotational velocity. Continuous (dashed) lines connect the
@@
 In contrast,the central and homogeneous source distributions only show a 
-weak anisotropy at the level of $\Delta\mu\leq 3\%$. On the other hand the variations
+weak anisotropy at the level of $\Delta\mu\leq 3\%$. The variations
 in $\mu$ does not depend on the rotational velocity while increasing the optical depth $\tau_{H}$
@@
 
-Figure \ref{fig:OC_profiles} show the spectra for the two off-centred
+Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
 spheres located at $C=\pm0.5R$.  In this case we only use photons that
-have outgoing directions aligned with the observer ($\vert \mu \vert > 
-0.9$ $\&$ $\vert \mu \vert < 1.0]$).  We do not find any asymmetry in 
-the line produced by the off-center emission, The difference
+have outgoing directions aligned with the observer i.e $\vert \mu \vert > 
+0.9$ $\&$ $\vert \mu \vert < 1.0]$.  We do not find any asymmetry in 
+the line produced by the off-center emission, the difference
  between the profiles corresponding to the spheres located at $C=-0.5R$ 
@@
 V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
-in detail in \S \ref{sec:3p}.
+in detail in the next section.
 
@@
 
-As mentioned in \S \ref{sec:off-center} Off-centered emission shows signs of three peak 
+As mentioned above Off-centered emission shows signs of three peak 
 profiles, to analyse this in more detail we use the same method of the spheres
@@
 $0.25R$ for all the models, for those who present signs of three peak profiles such as 
-$(V_{max}=50kms^{1}$ \& $\tau_{H}=10^{5}), (V_{max}=100kms^{1}$ \& $\tau_{H}=10^{6}), 
-(V_{max}=200kms^{1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
+$(V_{max}=50km$ $s^{-1}$ \& $\tau_{H}=10^{5}), (V_{max}=100km$ $s^{-1}$ \& $\tau_{H}=10^{6}), 
+(V_{max}=200km$ $s^{-1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
 with the aim of get a stronger profile.
@@
 in order to make the wings and the central peak similar in 
-height.
+height, for models in which the velocity is low spheres at $C = \pm 0.25$ produce 
+noise three peak profiles.
 
@@
 that a photon's frequency can move away from the line's center. 
-In \S \ref{sec:widthpeak} For typical column densities of $N_{HI}=1^{19}-1^{20}$, 
+In \S \ref{sec:widthpeak} For typical column densities of $N_{HI}=1e^{19}-1e^{20}$, 
 we find that rotational velocities of 100-300 \kms broaden the line profile up 
@@
 selected from the outer parts of the galaxy the wings of the line are stronger.
-Also off-center emission do not produce any considerable asymmetries in the line.\\
+Also off-center emission do not produce any considerable asymmetries in the line.
 \end{itemize}

### 2014-01-12 paper/ms.tex
Almost

@@
 
+% No entiendo bien esta ultima frase, la comparasion es entre que modelos? con que \tau_H?. Nicolas
+
 Figure \ref{fig:maximumsvsvelocity} shows the position for the peak
@@
 models that gave a $x_{\rm max}\neq 0$ and $x_{\rm max}=0$.
+
+% No entiendo la restricción!
 
@@
 number of scatterings is proportional to the optical depth, as
-expected in analogy from the analytic result for the homogeneous
+expected in analogy from the analytic result for the central
 infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
@@
 peak. However, for a central distribution the situation is
-different. In this case the number of scatterings remains high, in the
+different (lower panels). In this case the number of scatterings remains high, in the
 order of the optical depth, but the two peaks do get closer to each
@@
 explained since there is a transition from a opaque to an extremely opaque medium
-which affect affects how \ly photons scape from the medium: single flight 
+which affect affects how \ly photons escape from the medium: single flight 
 vs single excursion.
@@
 increasing optical depth is also slower.
-
-transition from the opaque to
-  extremely opaque medium, which affects how Lya photons escape from
-  the medium: single flight vs single excursion
 
@@
 direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
-away from the observer and the sphere centered on $+C\hat{\j}$ moves
+away from the observer and the sphere centered on $-C\hat{\j}$ moves
 towards the observer.
@@
 
-The variations in the $\mu$ distribution is shown in Fig.\ref{fig:muhisto},
+The variations in the $\mu$ distribution is shown in Figure \ref{fig:muhisto},
 for the Off-Center model there is a strong dependence of the 
@@
  between the profiles corresponding to the spheres located at $C=-0.5R$ 
- and that ones located at $C=0.5R$ is negligible.  As in the homogeneous / 
+ and that ones located at $C=0.5R$ is negligible.  As in the homogeneous/
 central model the line gets broader as the rotational velocity increase also 
@@
 (V_{max}=200km$ $s^{-1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
-with the aim of get a stronger profile.
+with the aim of get stronger profiles.
 
-Fig. \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
+Figure \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
 a relation between optical depth, rotational velocity and $C$ must be accomplish.
@@
 height, for models in which the velocity is low spheres at $C = \pm 0.25$ produce 
-noise three peak profiles.
+noise three peak profiles due to the high value of $\tau_{H, r}$.
 
-Fig.\ref{fig:3p_res} show that even with a low resolution a three-peak profile 
+Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
 would be observed, this is important for observational porpoises due to the finite 
@@
  discussion focuses on the qualitative aspects of diverse
- morphological features observed by \cite{Kulas12} ans \cite{Yamada2012}
+ morphological features observed by \cite{Kulas12} and \cite{Yamada2012}
 
@@
 rotation. However, some galaxies in those groups have a high flux between
-the two peaks; an effect can be induced by rotation. The same
+the two peaks; an effect that can be induced by rotation. The same
 argument applies to galaxies in the group IV in which the flux
@@
 smaller peaks at the redder and bluer side, a feature that is present
-in our off-center emission models with rotation.
+in our off-center emission models with rotation Figure \ref{fig:3p_profiles}.
 
@@
 does not significantly decrease with rotation, this is due to the 
-fact that the vast majority of scatterings events are resonant 
+fact that the vast majority of scatterings events are resonant, 
 during which the mean free path is very short and the effect of gas
@@
 
-\item For homogeneous sources we find the changes in the
+\item For homogeneous sources we find that the changes in the
 line morphology are linked to the reduction in the average number of
@@
 could emerge for models in which the rotational velocity is the necessary 
-to give rise to a central peak but also not that high to decrease the
+to give rise to a central peak, but not that high to decrease the
 amount of photons in the wings. When initial off-center sources are 
 selected from the outer parts of the galaxy the wings of the line are stronger.
-Also off-center emission do not produce any considerable asymmetries in the line.
+Also we do not find any considerable asymmetries in the line produced by off-center 
+emission.
 \end{itemize}
@@
 JNGC thanks the support of Universidad de los Andes given as teaching assistant, 
-Also to the  ISAAC 2012 summer school in San Diego which provide computer time
+Also to the  ISAAC 2012 summer school held University of California San Diego which provide computer time
  where some of this models where ran.

### 2014-01-12 paper/ms.tex
Last Version, some typos/labels/captions corrected

@@
 two decades these studies have become popular due to the
-availability of computing power. Early into the 21st century the first
+availability of computing power. Early into the 21st century, the first
 studies focused on homogeneous and static media
-\citep{Ahn00,Ahn01,Zheng02}. Later on the effects of clumpy media
+\citep{Ahn00,Ahn01,Zheng02}; Later on, the effects of clumpy media
 \citep{Hansen06} and expanding/contracting shell/spherical geometries started to
@@
 results of large hydrodynamic simulations
-\citep{CLARA,Forero12,Behrens13}. Recently Monte Carlo codes have also
+\citep{CLARA,Forero12,Behrens13}. Recently, Monte Carlo codes have also
 been applied to the results of high resolution hydrodynamic
 simulations of individual
-galaxies\citep{Laursen09,Barnes11,Verhamme12,Yajima12}. While, recent
+galaxies\citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Meanwhile, recent
 developments have been focused on the systematic study of clumpy
@@
 Performing that study is the main goal of this paper. We investigate for the
-first time the impact of rotation on the morphology of the \ly line. We focus on a simplified system, a spherical gas cloud
+first time the impact of rotation on the morphology of the \ly line. We focus on a simplified system: a spherical gas cloud
 with homogeneous density and solid body rotation, to study the line
@@
 
-This paper is structured as follows. In \S
+This paper is structured as follows: In \S
 \ref{sec:implementation} we present the implementation of bulk
@@
       rotational velocity $V_{\rm max}$. Continuous (dashed) lines
-      correspond to homogeneous (central) source
+      correspond to central (homogeneous) source
       distributions. \label{fig:widthvsvelocity}} 
@@
   velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  homogeneous (central) source distributions. A value of $x_{\rm
+  central (homogeneous) source distributions. A value of $x_{\rm
     max}=0$ indicates that line becomes single
@@
   rotational velocity velocity. Continuous (dashed) lines represent an
-  homogeneous (central) distribution of sources. \label{fig:Nscatt}}    
+  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
 \end{figure}
@@
    \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
-     continuous (dashed) lines correspond to homogeneous (central)
+     continuous (dashed) lines correspond to central (homogeneous)
      models.
@@
   \caption{$\mu$ histogram showing the orientation effects for the different
-  distributions Central(Points line), Homogeneous(Dashed) and Off-Center(Solid line).  
+  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
     \label{fig:muhisto}} 
@@
 \includegraphics[scale=0.3]{OC_profiles.png}
-\caption{\ly profiles for the off-center positions. Dashed/solid
-  lines represents spheres centered at $-0,5R/+0.5R$.
+\caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
+  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
    \label{fig:OC_profiles}} 
@@
 \includegraphics[scale=0.3]{3peaks.png}
-\caption{Three-Peak profiles for the off-center positions. 
+\caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
    \label{fig:3p_profiles}} 
@@
 \includegraphics[scale=0.3]{3p_res.png}
-\caption{Three-Peak profiles for different resolutions. 
+\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
    \label{fig:3p_res}} 

### 2014-01-15 paper/ms.tex
minor changes
revised abstract

@@
 \begin{abstract}
-%For the first the effect of gas bulk rotation on the morphology 
-%of the Lyman $\alpha$ line is studied using radiative transfer calculations.
-We present results of radiative transfer calculations to measure
-the impact of gas bulk rotation on the morphology of the Lyman $\alpha$ line in galaxies. 
-We model a galaxy as a sphere with a
-homogeneous mixture of dust and hydrogen at a constant
-temperature. These spheres have a solid-body rotation with
-maximum velocities in the range $0-300$ \kms and neutral
-hydrogen optical depths in the range $\tau_{\rm
-H}=10^{5}-10^{7}$. We also consider two kinds of spatial
-distribution for the radiation sources with respect to the sphere:
-central and homogeneous. We find that the line width and the intensity
-at the line's center increases with rotational velocity. In the case of homogeneously distributed
-sources, for large rotational velocities the line transforms from a
-double peak to a single peak at the line center. Under the same
-conditions the escape fraction increases $\sim 30\%$. For
-radiation sources located off-center, the line morphology presents a
-range of single, double and triple peaked lines. We show how these results are
-useful to interpret recent spectroscopic results of distant $z\sim 2-3$ star
+
+We present results of radiative transfer calculations to measure the
+impact of gas bulk rotation on the morphology of the Lyman $\alpha$
+emission line in distant galaxies. We model a galaxy as a sphere with
+a homogeneous mixture of dust and hydrogen at a constant
+temperature. These spheres have a solid-body rotation with maximum
+velocities in the range $0-300$ \kms and neutral hydrogen optical
+depths in the range $\tau_{\rm H}=10^{5}-10^{7}$. We also consider two
+kinds of spatial distribution for the radiation sources with respect
+to the sphere: central and homogeneous. Our main finding is that the
+line width and the intensity at the line's center increase with
+rotational velocity. For homogeneously distributed sources the line
+becomes single peaked at large rotational velocities. Under the same
+conditions the escape fraction increases $\sim 30\%$. For radiation
+sources located off-center, the line morphology presents a range of
+single, double and triple peaks. We show how these results are useful
+to interpret recent spectroscopic results of distant $z\sim 2-3$ star
 forming galaxies. 
@@
 \begin{keywords}
-{galaxies: high-redshift,galaxies: star formation, line: formation}
+{galaxies: high-redshift, galaxies: star formation, line: formation}
 \end{keywords}

### 2014-01-15 paper/ms.tex
two more items in the conclusions

@@
 rotational velocity. For homogeneously distributed sources the line
-becomes single peaked at large rotational velocities. Under the same
+becomes single peaked at rotational velocities larger than the line
+width in the static case. Under the same
 conditions the escape fraction increases $\sim 30\%$. For radiation
@@
 forming galaxies.
+
 \end{abstract}
@@
 
-This paper illustrates for the first time the main effects of rotation
-in the morphology of the \ly emission line in star forming galaxies. 
-The results are based on the study of an homogeneous sphere
-with solid body rotation. We explored a range of models by varying
+This paper quantifies for the first time in the literature the effects
+of rotation in the morphology of the \ly emission line in star forming
+galaxies.  The results are based on the study of an homogeneous sphere
+of gas with solid body rotation. We explore a range of models by varying
 the rotational speed, hydrogen optical depth, dust optical depth and
@@
 
-Our main result is that rotation clearly impact the \ly line
+Our main result is that rotation clearly impacts the \ly line
 morphology. Double peaked lines can make transitions into single
-peaked lines as the rotational velocity increases. Additional
+peaked lines as the rotational velocity increases. In the case of
 off-centered emission result into triple peaked lines for certain
-values of optical depth and velocities.
+values of optical depth and rotational velocities.
+
+Quantitatively the main results of our study are summarized in the
+following items.
 
 \begin{itemize}
+
+\item The line width increases with rotational velocity. The line with
+  approximately follows the functional form $W_{\rm 1/2}^2 = W_{\rm
+    1/2,0}^2 + (V_{\rm max}/\lambda)^2$ where $V_{\rm 1/2,0}$ indicates the line
+  width for the static case. $\lambda$ is a constat determined from
+  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
+  $\lambda_{\rm h}=YY$ for the central and homogeneous source
+  distribution, respectively.
+
+\item A single peaked line emerges for high rotational velocities in
+  the case of homgeneously distributed sources. The cases of single
+  peaked lines occur when the rotational velocity is larger than the
+  line width measured in the static case.
+
 \item For central sources we find that the number of scatterings
@@
 
-%We have quantified the results in different aspects.
-
-%These changes in the number of scatterings have a direct bearing on
-%the escape fraction in the presence of dust.  In Section
-%\ref{sec:escapefraction} we find that the escape fraction increases in
-%$20\%-30\%$ for the homogeneous source distribution. In the centrally
-%located emission, the rotational effects are negligible on the escape
-%fraction.
-
-%We also studied the effect of rotation in the position of the peaks in
-%the line. We find that in the regions with central emission the peaks
-%do not shift as rotation increases. However, in the homogeneous models
-%the double peak merges into a single peak.
-
 Comparing our results with recent observed LAEs we find that many 
@@
 
-JNGC thanks the support of Universidad de los Andes given as teaching assistant, 
-Also to the  ISAAC 2012 summer school held University of California San Diego which provide computer time
- where some of this models where ran.
+JNGC acknowledges financial support from Universidad de los
+Andes.
+
+JEFR acknowledges financial support from Vicerrectoria de
+Investigaciones at Universidad de los Andes through a FAPA grant.
+
+We thank the International Summer School on AstroComputing
+2012 organized by the University of California High-Performance
+AstroComputing Center (UC-HiPACC) for providing computational
+resources where some of the calculations were done.
 

### 2014-01-21 paper/ms.tex
Figure Size labels
new subsection describing the radiative transfer codes

@@
 Additionally, we have used two independently developed Monte Carlo
-codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
+codes \cite{CLARA,DijkstraKramer} to perform the calculations of the
 non-dusty models. The results we report are robust in the sense
@@
 \end{table}
+
+\subsection{Brief Description of the Radiative Transfer Codes}
+
+Here we briefly describe the relevant points for the two radiative
+transfer codes we have used. For a detailed description we refer the
+reader to the original papers \cite{CLARA,DijkstraKramer}.
+
+The codes follow the individual scatterings of \ly photons as it
+travels through a 3D distribution of neutral Hydrogen. At each
+scattering the frequency of the photon (in the laboratory frame) and
+its direction of propagation change. This change in frequency is due
+to the peculiar velocities of the Hydrogen atom that absorbed and
+reemitted the photon. If dust is present, the photon can interact
+either with a Hydrogen atom or dust grain. In the case of a dust
+interaction the photon can be either absorbed or scattered, this
+probability is encoded in the dust albedo, $A$, which we chose to be
+$1/2$. In order to obtain accurate values for the escape fraction of
+photons in the presence of dust, we do not use any accelerating
+mechanism in the radiative transfer.  Once the photons escape the gas
+distribution we store their direction at their direction of
+propagation and frequency at their last scattering.
+
+The photons are thus emitted in some region of the gas distribution
+and follow a random walk in space and frequency until they escape the
+gas distribution or are absorbed by a dust grain. The initialization
+process for the \ly photons has to specify its position, frequency and
+direction of propagation. In our case we select the initial frequency
+to be exactly the \ly restframe frequency ($x=0$) and the direction of
+propagation to be random following an flat probability distribution
+over the sphere.
+
+The gas is completely defined by its geometry (i.e. sphere or slab),
+temperature $T$, Hydrogen optical depth $\tau_{\rm H}$, dust optical
+depth $\tau_{\rm a}$ and the bulk velocity field $\vec{v}$.  Here we
+treat the gas as homogeneous in density ($\tau_{\rm H}$, $\tau_{\rm
+  a}$) and temperature.
 
@@
 \begin{figure}
-  \includegraphics[scale=0.35]{OF_spheres.png}
+  \includegraphics[scale=0.3]{OF_spheres.png}
   \caption{The two solid circles show the two different spherical

### 2014-01-23 paper/ms.tex
Almost all figures with big labels and in .eps
restoring section on the radiative transfer codes

@@
 
-\subsection{Grid of Simulated Galaxies}
-\label{sec:models}
-
-In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
-numerical photons through different spherical galaxies. For each galaxy
-we vary at least one of the following parameters: the maximum
-rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
-the dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are $60$ models initial combining all
-variations of the input parameters. Table \ref{table:models}
-summarizes the models.
-
-Additionally, we have used two independently developed Monte Carlo
-codes \cite{CLARA,DijkstraKramer} to perform the calculations of the
-non-dusty models. The results we report are robust in the sense
-that they are obtained by both codes.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{llc}\hline\hline
-Physical Parameter (units) & Symbol & Values\\\hline
-Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
-Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
-Dust Optical Depth & $\tau_{a}$ & $0$,$1$\\
-Photons Distributions & & Central, Homogeneous\\\hline\hline
-\end{tabular}
-\caption{
-  List of the physical parameters that define the spherical models 
-  simulated in our Monte Carlo calculations. For each parameter we
-  vary the values in the range listed in the last column. Taking into
-  account all the possible combinations we end up with $60$ different
-  models.} 
-\label{table:models}
-\end{center}
-\end{table}
-
 \subsection{Brief Description of the Radiative Transfer Codes}
@@
 
+\subsection{Grid of Simulated Galaxies}
+\label{sec:models}
+
+In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
+numerical photons through different spherical galaxies. For each galaxy
+we vary at least one of the following parameters: the maximum
+rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
+the dust optical depth $\tau_{a}$ and the initial distribution of photons
+with respect to the gas. There are $60$ models initial combining all
+variations of the input parameters. Table \ref{table:models}
+summarizes the models.
+
+Additionally, we have used two independently developed Monte Carlo
+codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
+non-dusty models. The results we report are robust in the sense
+that they are obtained by both codes.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{llc}\hline\hline
+Physical Parameter (units) & Symbol & Values\\\hline
+Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
+Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
+Dust Optical Depth & $\tau_{a}$ & $0$,$1$\\
+Photons Distributions & & Central, Homogeneous\\\hline\hline
+\end{tabular}
+\caption{
+  List of the physical parameters that define the spherical models 
+  simulated in our Monte Carlo calculations. For each parameter we
+  vary the values in the range listed in the last column. Taking into
+  account all the possible combinations we end up with $60$ different
+  models.} 
+\label{table:models}
+\end{center}
+\end{table}
+
 \section{Results}
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesCentral.png}
-  \includegraphics[width=0.45\textwidth]{SpectraDifVelocitiesHOM.png}
+  \includegraphics[width=0.45\textwidth]{f1_1.eps}
+  \includegraphics[width=0.45\textwidth]{f1_2.eps}
 \end{center}
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{maximumVvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{f3.eps}
 \caption{Position of the peak maxima as a function of rotational
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{NscattvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{f4.eps}
 \caption{Logarithm of the average number of scatterings as function of
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
-  \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}\\
-  \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
-  \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
+  \includegraphics[width=0.45\textwidth]{f5_1.eps}
+  \includegraphics[width=0.45\textwidth]{f5_2.eps}\\
+  \includegraphics[width=0.45\textwidth]{f5_3.eps}
+  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
 \end{center}
@@
 \begin{figure}
-  \includegraphics[width=0.45\textwidth]{escapefraction.png}
+  \includegraphics[width=0.45\textwidth]{f6.eps}
    \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
@@
 \begin{figure}
-  \includegraphics[width=0.45\textwidth]{Neufeld.png}
+  \includegraphics[width=0.45\textwidth]{f7.eps}
  \caption{Escape fraction as a function of the
@@
 \begin{figure}
-  \includegraphics[scale=0.3]{OF_spheres.png}
+  \includegraphics[scale=0.3]{f8.eps}
   \caption{The two solid circles show the two different spherical
@@
 \begin{figure}
-  \includegraphics[scale=0.35]{muhisto.png}
+  \includegraphics[scale=0.35]{f9.eps}
   \caption{$\mu$ histogram showing the orientation effects for the different
@@
 \begin{figure*}
-\includegraphics[scale=0.3]{OC_profiles.png}
+\includegraphics[scale=0.3]{f10.eps}
 \caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
@@
 \begin{figure*}
-\includegraphics[scale=0.3]{3peaks.png}
+\includegraphics[scale=0.3]{f11.eps}
 \caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
@@
 \begin{figure*}
-\includegraphics[scale=0.3]{3p_res.png}
+\includegraphics[scale=0.3]{f12.eps}
 \caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 

### 2014-01-23 paper/ms.tex
working on the results section

@@
 Performing that study is the main goal of this paper. We investigate for the
-first time the impact of rotation on the morphology of the \ly line. We focus on a simplified system: a spherical gas cloud
-with homogeneous density and solid body rotation, to study the line
+first time the impact of rotation on the morphology of the \ly
+line. We focus on a simplified system: a spherical gas cloud with
+homogeneous density and solid body rotation, to study the line
 morphology and the escape fraction in the presence of dust. We base
@@
 
-This paper is structured as follows: In \S
-\ref{sec:implementation} we present the implementation of bulk
-rotation into the Monte Carlo codes, paying special attention to coordinate
-definitions. We also list the different physical parameters in
-the simulated grid of models. In the next \S \ref{sec:results} we present the
-results of the simulations, with special detail to quantities in the
-line that show a clear evolution as a function of the sphere
-rotational velocity. In \S \ref{sec:discussion} we discuss the
-implications of our results in the interpretation of LAEs
-observations and further refinements that can be implemented in the
-theoretical modeling of the \ly line. In the last section we present
+This paper is structured as follows: In \S \ref{sec:implementation} we
+present the implementation of bulk rotation into the Monte Carlo
+codes, paying special attention to coordinate definitions. We also
+present a short review of how the \ly radiative transfer codes work
+and list the different physical parameters in the simulated grid of
+models. In the next \S \ref{sec:results} we present the results of the
+simulations, with special detail to quantities in the line that show a
+clear evolution as a function of the sphere rotational velocity. In \S
+\ref{sec:discussion} we discuss the implications of our results in the
+interpretation of LAEs observations. In the last section we present
 our conclusions.
@@
 $T$ scattering the radiation or equivalently the thermal velocity
-$v_{\rm th}$ of the atoms.
+$v_{\rm th}$ of the atoms.  For the temperature $T=10^4$K used in our
+radiative transfer calculations the thermal velocity is
+$v_{th}=12.8$\kms.
 
@@
 
-The first quantitative conclusion of the effect of rotation in the
-\ly line is that double peaks broaden and reduce their intensity
-while the line center rises. This gives the impression that, as the
-rotational velocity increases, the double peaks are merged into a
-single broad emission peak. This is most evident at the highest
-rotational velocities for the homogeneously distributed sources
-(right panel in Figure \ref{fig:differentvelocities}).
+There are three clear effects on the line's morphology as the
+rotational veloctiy increases. First, the line
+broadens; second, the double peaks reduce their intensity; and third,
+the intensity at the line center rises. The two last effects give the
+impresion that the double peaks are merger into one at high rotational
+velocities, a result that is evident for the homogeneously distributed
+sources as shown in right panel in Figure \ref{fig:differentvelocities}.
 
-To quantify the line broadening we use the width at half maximum
-(FWHM), $W_{1/2}$. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
-with rotational velocity. Continuous (dashed) lines connect the
-results for homogeneous (central) source distribution. For the
-temperature $T=10^4$K used in our radiative transfer calculations the
-thermal velocity is $v_{th}=12.8$\kms. For a model with $\tau_{H}$ it
-means that the FWHM increase up to $350$\kms (at $V_{\rm
-  max}=300$\kms) compared to $150$\kms in the static case.
+We use the full width at half maximum (FWHM), $W_{1/2}$to quantify the line
+broadening. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
+with rotational velocity. {\bf Here we need to check the numbers to
+  say something more specific.}
 
-% No entiendo bien esta ultima frase, la comparasion es entre que modelos? con que \tau_H?. Nicolas
+We parameterize the dependency of the linewidth as $W_{1/2}^2 =
+W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
+velocity width in the static case and $\lambda$ is a positive
+scalar to be determined as a fit to the data. With this test we want
+to know to what extent the new velocity witdth can be expressed as a
+quadratic sum of the two relevant velocities in the problem. We find
+that for the
 

### 2014-01-23 paper/ms.tex
finished maxima subsection

@@
 quadratic sum of the two relevant velocities in the problem. We find
-that for the
+that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
+(homogeneous) sources.
 
-Figure \ref{fig:maximumsvsvelocity} shows the position for the peak
-maxima as a function of the rotational velocity $V_{\rm max}$. This
-Figure clearly shows that in the case of central distributed
-sources there is barely any change with rotational velocity in the
-range of explored parameters. However, in the case of
-homogeneously emitted sources the maxima position remain close to
-constant until beyond some velocity threshold the line becomes single
-peaked with $x_{\rm m}=0$ \kms.
+In order to quantify the transition to a single peak we measure the
+position for the peak maxima as a function of the rotational
+velocity. Our results are presented in Figure
+\ref{fig:maximumsvsvelocity} where it is clear that for central
+sources there are always two peaks with fixed positions as the rotational
+velocity changes. However, in the case of homogeneously emitted
+sources the maxima position remain close to constant until some
+velocity threshold the line becomes single peaked with $x_{\rm m}=0$
+\kms. {\bf By inspection we find that in all cases the transition has
+occurred when the rotational velocity is larger than the intrinsic
+linewidth OR HALF WIDTH ONCE THE NUMBERS ARE FIXED?}.
 
-The transition to a single peaked line seems to occur in systems
-where it is easier for the bulk of the photons to escape with the lowest
-number of scatterings possible, allowing them not to move very far
-from the center of the line. This might explain how the single peak stage
-is easily achieved in the homogeneous source distribution. In this
-case there is a fraction of the photons that are inside a photo-sphere
-region with $\tau_{H,r}\ll \tau_{H}$ where $\tau_{H,r}$ is the optical
-depth from the radius of emission to the sphere's surface. These
-conditions allows the photons to escape with much less scatterings
-compared to the photons emitted at the very center of the sphere. In
-turn, it gives the photons less scatterings to be placed far from the
-line center.
+One possible explanation for the emergence of the single peak in the
+homogeneous source systems is that some photons close to the surface
+(a sort of photosphere) can escape with a low number of scatterings,
+allowing them to stay close to the line's center. Increasing the
+rotational velocity $V_{\rm max}$ reduces the optical depth making the
+photosphere region effectively larger, increasing the number of
+photons escaping close to the line's center.
 
-Increasing the rotational velocity $V_{\rm max}$ reduces
-the optical depth making the photo-sphere region effectively larger,
-increasing the number of photons escaping close to the line's
-center. In our models we find the following correspondence between the
-optical depth $\tau_{\rm H}=\{10^5, 10^6, 10^7\}$ and the transitional
-velocities $V_{\rm   trans}=\{50-100\kms, 100-200\kms, 200-300\kms\}$
-which can only be constrained to be in the range of velocities in the
-models that gave a $x_{\rm max}\neq 0$ and $x_{\rm max}=0$.
+However, for the central emission the transition to a single peak is
+never completed in the range of explored parameters. The absence
+of a single peak phase could be partially explained by the absence of a
+photosphere, in this case the average number of scatterings to escape
+should remain close to constant as the rotational velocity
+increases. The rise in intensity at the line's center could instead
+mean that the scattering in a medium with bulk motion are inefficient
+in driving photons outside that frequency region.
 
-% No entiendo la restricción!
-
-For the central emission the transition to a single peak is never
-completed in the range of explored parameters. The non appearance
-of a single peak phase can be in part explained to the absence of a
-photo-sphere, as is the case in the homogeneous
-distribution. Nevertheless, there is a rise in the intensity at the
-line center as the rotational velocity increases. This hints that the
-encounters with a non static medium are inefficient in pushing photons
-outside the line's center.
-
-In the next sub-section we quantify the number of scatterings and explore
-to what extent this is related to the emergence of single peaked emission.
+In order to explore our interpretation for these two scenarios we now 
+quantify the effect of rotation on the number of scatterings.
 

### 2014-01-23 paper/ms.tex
one more paragraph in the maxima section

@@
 
-We use the full width at half maximum (FWHM), $W_{1/2}$to quantify the line
-broadening. Figure \ref{fig:widthvsvelocity} shows how $W_{1/2}$ increases
+We use the full width at half maximum (FWHM), $W$, to quantify the line
+broadening. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
 with rotational velocity. {\bf Here we need to check the numbers to
@@
 
-We parameterize the dependency of the linewidth as $W_{1/2}^2 =
-W_{1/2,0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{1/2,0}$ is the
+We parameterize the dependency of the linewidth as $W^2 =
+W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
 velocity width in the static case and $\lambda$ is a positive
@@
 \caption{Logarithm of the average number of scatterings as function of
-  rotational velocity velocity. Continuous (dashed) lines represent an
+  rotational velocity. Continuous (dashed) lines represent an
   central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
@@
       show the homogeneous (central) source distribution. Left
-      corresponds to the static case and the right
-      $V_{max}=300km/s$. The color scale is logarithmic on the
+      corresponds to the static case and right
+      $V_{\rm max}=300km/s$. The color scale is logarithmic on the
       number of photons with given values of $N_{\rm scatt}$ and
@@
 
-The number of \ly photon scatterings affects its final frequency after
-escaping the galaxy. In static gas geometries, a large value of the
-optical depth correlates with a high number of scatterings, increasing
-the probability of finding a \ly photon far from the center of the
-line. In these cases the peak maxima shifts away from the line center as
-the amount of neutral hydrogen increases.
+The number of scatterings affects the escape frequency of a \ly photon.
+In static cases, a large value of the optical depth correlates with a
+high number of scatterings, increasing the probability of finding a
+\ly photon far from the line's center. The result is that he peak maxima
+shifts from the center as the amount of neutral hydrogen
+increases. This can be precisely quantifyied in for the static slab
+with central sources, in that case the maxima position are related to
+the optical depth and the temperature as $x_{m}=\pm 1.066(a\tau_{\rm
+  H})^{1/3}$ \citep{Harrington73}.
+
+%%%% JEFR.
 
@@
 \item The line width increases with rotational velocity. The line with
-  approximately follows the functional form $W_{\rm 1/2}^2 = W_{\rm
-    1/2,0}^2 + (V_{\rm max}/\lambda)^2$ where $V_{\rm 1/2,0}$ indicates the line
+  approximately follows the functional form $W^2 = W_{
+    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
   width for the static case. $\lambda$ is a constat determined from

### 2014-01-27 paper/ms.tex
editando

@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.png}
+    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.eps}
     \caption{Half-width for the non-dusty models as a function of
@@
   \includegraphics[width=0.45\textwidth]{f5_1.eps}
-  \includegraphics[width=0.45\textwidth]{f5_2.eps}\\
+  \includegraphics[width=0.45\textwidth]{f5_2.eps}
   \includegraphics[width=0.45\textwidth]{f5_3.eps}
@@
       corresponds to the static case and right
-      $V_{\rm max}=300km/s$. The color scale is logarithmic on the
+      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
       number of photons with given values of $N_{\rm scatt}$ and
@@
 high number of scatterings, increasing the probability of finding a
-\ly photon far from the line's center. The result is that he peak maxima
+\ly photon far from the line's center. As a result the peak maxima
 shifts from the center as the amount of neutral hydrogen
-increases. This can be precisely quantifyied in for the static slab
-with central sources, in that case the maxima position are related to
+increases. This can be precisely quantifyied in the static slab
+with central sources where the maxima position are related to
 the optical depth and the temperature as $x_{m}=\pm 1.066(a\tau_{\rm
-  H})^{1/3}$ \citep{Harrington73}.
-
-%%%% JEFR.
+  H})^{1/3}$ \citep{Harrington73}. In the same model the average
+number of scatterings depends only on the optical depth $\langle
+N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
+\citep{Adams72,Harrington73}, in the case of homogeneously distributed
+sources $\langle N_{\rm   scatt}\rangle=1.16\tau_{\rm   H}$
+\citep{Harrington73}.
 
@@
 $\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
-$V_{\rm max}$. For the central distributions the average number of
-scatterings has a modest change for increasing rotational
-velocities, $\langle N_{\rm scatt}\rangle$ changes less than $0.5\%$
-for different velocities. In the same set-up the average
-number of scatterings is proportional to the optical depth, as
-expected in analogy from the analytic result for the central
-infinite-slab $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}. In the spheres with centrally
-distributed sources we find $\langle N_{\rm
-  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depths
-$\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$
+$V_{\rm max}$. For the central source distribution the average number of
+scatterings $\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$
+for different velocities. In this setup the number of scatterings is
+proportional to the optical depth, with $\langle N_{\rm
+  scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
+values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively
 
-Figure \ref{fig:Nscatt} shows that for the homogeneous distribution
-there is a clear decrease of $\langle N_{\rm  scatt}\rangle$ as the
-$V_{\rm max}$ increases. This effect is more pronounced for lower
-values of the optical depth. For $\tau_{\rm H}=10^5$ the average
-number of scatterings decreases by $61\%$ at $V_{\rm max}=300\kms$ in
-comparison to the static case.
+From Figure \ref{fig:Nscatt} is also clear that for the homogeneous
+distribution there is a clear decrease of $\langle N_{\rm
+  scatt}\rangle$ as the $V_{\rm max}$ increases. For instance, for
+$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
+$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
 
-The analytic expectation for the average number of scatterigs in a
-slab with homogeneously distributed sources is $\langle N_{\rm
-  scatt}\rangle=1.16\tau_{\rm   H}$ \citep{Harrington73}. This is
-$0.72$ times lower than the same case with photons emitted in the
-slab's center. In our case we find that for the static case and the
-homogeneously distributed sources $\langle N_{\rm scatt}\rangle=
-(0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents factors of $(0.66,
-0.59, 0.55)$ lower than the centrally emitted  photons.
+In this case we find that for a static sphere $\langle N_{\rm
+  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
+representsfactors of $(0.66, 0.59, 0.55)$ lower than the centrally
+emitted photons. In contrast the analytic solution for the homogeneous
+slab gives $0.72$ times less scatterings in the homogeneous case than
+in the central one.
 
-In order to gain a deeper understanding of these results we make 2D
+In order to gain a deeper understanding of these results and explain
+the results for the maxima in the line morphology we make 2D
 histograms for the number of scatterings as a function of the outgoing
@@
 scale is logarithmic in the number of photons at a certain value
-$x-N_{\rm scatt}$.
+$x$-$N_{\rm scatt}$.
 
-The top right panel of Figure \ref{fig:Nscatt2D} supports our hypothesis about
-the photo-sphere in the homogeneous distribution. In that case most of
+The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
+high rotational velocity) supports our hypothesis about
+the photo-sphere in the homogeneous distribution. In this case most of
 the photons that left with $x\sim 0$ have escaped with less than $10$
-scatterings. This explains the origin of a single central
-peak. However, for a central distribution the situation is
-different (lower panels). In this case the number of scatterings remains high, in the
-order of the optical depth, but the two peaks do get closer to each
-other. In this case the physical picture is that each scattering, due
-to the bulk velocity of the gas, is inefficient in driving the photon
-outside the line center.
+scatterings. This also explains the decrease in the average number of
+scatterings observed in Figure \ref{fig:Nscatt}.
+
+However, for a central distribution the situation is quite different
+(lower panels). In this case the number of scatterings remains high,
+in the order of the optical depth, but the two peaks do get closer to each
+other. Here the most probable physical picture is that each
+scattering, due to the bulk velocity of the gas, is inefficient in
+driving the photon outside the line center.
 
@@
   \includegraphics[width=0.45\textwidth]{f6.eps}
-   \caption{Escape fraction as a function of rotational velocity, for these models we took $\tau_{a}=1$. The
-     continuous (dashed) lines correspond to central (homogeneous)
-     models.
+  \caption{Escape fraction as a function of rotational velocity. All
+    these models have $\tau_{a}=1$. The continuous (dashed) lines
+    correspond to central (homogeneous) models.
     \label{fig:efvsv}}
@@
     the infinite slab is shown as a continuous line. Different dashed
-   lines correspond to different rotational velocities, for this models 
-   $\tau_a = 1$.
+    lines correspond to different rotational velocities.
+    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
     \label{fig:efvsNeufeld}}   
@@
 
-The average number of scatterings is also reflected in the amount of
-photons absorbed by dust. Under these considerations we do not expect
-any change in the escape fraction for a dusty cloud with central
-source of radiation given that the number of scatterings remains close
-to constant. On the other hand, in the case of a homogeneous
-radiation source the number of scatterings drops as $V_{\rm max}$
-increases, which has to be reflected as an increasing escape fraction.
+In the case of dusty clouds, all changes in the average number
+of scatterings presented in the previous subsection have a direct
+bearing on the escape fraction. From the results we have just obtained
+we can predict that for central source distributions the escape
+fraction will barely change, while larger effects should be expecte
+for homogeneously distributed sources.
 
-Figure \ref{fig:efvsv} shows the dependence of the escape fraction as
-a function of the maximum rotational velocity, confirming our expectations. For the central source
-distribution the escape fraction barely shows any change, while for
-the homogeneous case there is a clear increase in the escape fraction for
-high rotational velocities.  Rotation has a higher relative impact in
-the models with low optical depth $\tau_{\rm H}=10^5$,$10^{6}$, where
-it can rise from $(0.26, 0.28)$ ($V_{\rm}=0$\kms) up to $(0.37, 0.39)$ ($V_{\rm
-  rot}=300$ \kms).
+Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
+fraction as a function of the rotational velocity. The curves for the
+central source distribution stay flat, while for the homogeneous case
+there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
+the models with low optical depth. For instance, in models with
+$\tau_{\rm H}=10^5$, the static scape fraction is $0.26$ and increases
+to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
+all the values for the escape fraction {\bf We also need a table
+  listing the escape  fraction values.}
 
@@
 $(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
-in the limits where $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
-\ref{fig:efvsNeufeld} correspond to the cases of different
+in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
+\ref{fig:efvsNeufeld} show the results for the different rotational
 velocities. First of all we note that the escape fraction does not
-increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, this is
-explained since there is a transition from a opaque to an extremely opaque medium
+increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
+that is explained since there is a transition from a opaque to an extremely opaque medium
 which affect affects how \ly photons escape from the medium: single flight 
-vs single excursion.
- %we are in a regime where the condition for the analytic expectations  ($a\tau_{h}\gg 1$) does not hold. 
-This figure also shows that the escape fraction is higher by factors of $2-10$
-than the expectation for a slab with centrally distributed
-sources. Furthermore, the decrease of the escape fraction with
-increasing optical depth is also slower.
+vs. single excursion. {\bf Que quiere decir eso de single flight y
+  single excursion, porque explica eso la fraccion de escape?} 
+ %we are in a regime where the condition for the analytic expectations
+ %($a\tau_{h}\gg 1$) does not hold.
 
-\subsection{Off-Centered emission}
+\subsection{Anisotropy and off-centered emission}
+
 \label{sec:off-center}
@@
   \includegraphics[scale=0.3]{f8.eps}
-  \caption{The two solid circles show the two different spherical
-    off-centered emitting  regions. The angular velocity vector is
-    defined to be along the $\hat{\i}$ direction (where the reader is) 
-    and the observer is along the $\hat{\j}$ direction. 
+  \caption{The two small circles show the two different spherical
+    off-centered emitting regions with respect to the larger spherical
+    gas distribution. The angular velocity vector is
+    defined to be along the $\hat{\i}$ direction (outwards the
+    page). In order to study a possible anysotropy we place an
+    observer along the the $\hat{\j}$ direction. The vector
+    $\hat{k}_{\rm out}$ represents the outgoing direction of an
+    escaping \ly photon. {\bf Si el observador esta en j, entonces las
+    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
+    hacer las dos circulos pequenos punteados}
     \label{fig:OCspheres}} 
 \end{figure}
+
+Rotation breaks the spherical symmetry of the static model and
+introduces a prefered axis
 

### 2014-01-28 paper/ms.tex
Improving plots
figures

@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{f1_1.eps}
+  \includegraphics[width=0.45\textwidth]{f1_2.eps}
+\end{center}
+\caption{Shape of the \ly line for
+    different velocities rotational velocities for spherical
+    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
+    the central (homogeneous) photon distribution. All photons were
+    taken into  account regardless of their final direction of propagation.
+    \label{fig:differentvelocities}}  
+\end{figure*}
+
 \subsection{Grid of Simulated Galaxies}
@@
 \label{sec:results}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.45\textwidth]{f1_1.eps}
-  \includegraphics[width=0.45\textwidth]{f1_2.eps}
-\end{center}
-\caption{Shape of the \ly line for
-    different velocities rotational velocities for spherical
-    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
-    the central (homogeneous) photon distribution. All photons were
-    taken into  account regardless of their final direction of propagation.
-    \label{fig:differentvelocities}}  
-\end{figure*}
 
@@
     dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
-    hacer las dos circulos pequenos punteados}
+    hacer las dos circulos pequenos punteados.}
     \label{fig:OCspheres}} 
@@
 
+\begin{figure}
+  \includegraphics[scale=0.35]{f9.eps}
+  \caption{$\mu$ histogram showing the orientation effects for the different
+  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
+    \label{fig:muhisto}} 
+\end{figure}
+
 Rotation breaks the spherical symmetry of the static model and
-introduces a prefered axis
+introduces the rotation axis as a preferred direction. This motivates
+us to study the anisotropy of the outgoing photons. In order to study
+possible deviations with respect to an isotropic flux we follow
+\cite{Zheng2013} to estimate the flux as a function of the angle
+$\Theta$ formed by the outgoing photons and the observer. Figure
+\ref{fig:OCspheres} presents a geometric scheme to clarify the
+definition of all relevant directions in the problem.
 
-The raw data from the model with homogeneous radiation sources allows
-to study the effect of radiation sources distributed with a different
-symmetry than the gas. We can select photons emitted in off-centered spheres 
-with respect to the gas distribution and check whether this produces
-asymmetries in the line.
-
-Figure \ref{fig:OCspheres} shows the two spherical regions we
-define to test for this effect. Each has a radius of $0.5$R and can
-have two possible centers positions $C$ along the $\hat{\j}$ direction:
-$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
-direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
-away from the observer and the sphere centered on $-C\hat{\j}$ moves
-towards the observer.
-
-We study first the angular deviations of the outgoing photons with respect
-to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
-as a function of the angle $\Theta$ formed by the outgoing photons and
-the observer. This is expressed by
-
+An estimator for the anysotropy is represented by
+%
 \begin{equation}
@@
 \Theta$. This definition satisfies the condition
-$\int_{-1}^{1}F(\mu)d\mu/2=1$.
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the isotropic
+emission is characterized by a flat $F(\mu)$ distribution.
 
-\begin{figure}
-  \includegraphics[scale=0.35]{f9.eps}
-  \caption{$\mu$ histogram showing the orientation effects for the different
-  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
-    \label{fig:muhisto}} 
-\end{figure}
+Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
+distribution for an sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
+  max}=200$\kms. The dashed and dotted lines represent the homogeneous
+and central source distribution, respectively. This shows that the
+level of anisotropy induced by rotation does not surpasses the $5\%$
+level. We performed the same test with all the models and we do not
+fina any significant anisotropic effect.
+
+We explore other kind of anisotropy by study the effect
+of radiation sources distributed with a different symmetry than the
+gas. To this end we select a subset of the photons in the homogeneous
+models such as they are emitted from off-centered spheres with respect
+to the gas distribution.
+
+Figure \ref{fig:OCspheres} shows the two spherical regions we
+define to test for this effect. Each has a radius of $0.5R$, where $R$
+is the radius of the gaseus sphere. Provided that there is an observer
+located along the $\hat{j}$ direction, we pick two possible positions
+to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
+this configuration the emitting sphere centered on $+C\hat{k}$ moves
+away from the observer and the sphere centered on $-C\hat{j}$ moves
+towards the observer.
+
+%JEFR
 
@@
 
-\begin{figure*}
+\begin{figure}
+\begin{center}
 \includegraphics[scale=0.3]{f12.eps}
+\end{center}
 \caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
    \label{fig:3p_res}} 
-\end{figure*}
+\end{figure}
 

### 2014-01-28 paper/ms.tex
edits

@@
     dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
-    hacer las dos circulos pequenos punteados.}
+    hacer las dos circulos pequenos punteados. Por otro lado, como se
+    habian definido las velocidades, el eje de rotacion es el eje k}
     \label{fig:OCspheres}} 
@@
 \end{figure}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[scale=0.3]{f10.eps}
+\end{center}
+\caption{\ly profiles for the off-centered emission. Dashed/solid
+  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
+   \label{fig:OC_profiles}} 
+\end{figure*}
+
+\subsection{Three-Peak Profiles}
+\label{sec:3p}
+
+\begin{figure*}
+\includegraphics[scale=0.3]{f11.eps}
+\caption{Triple peaked profiles for three different off-center positions
+  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
+  line) and for different rotational velocities.  
+   \label{fig:3p_profiles}} 
+\end{figure*}
 
@@
 and central source distribution, respectively. This shows that the
-level of anisotropy induced by rotation does not surpasses the $5\%$
-level. We performed the same test with all the models and we do not
-fina any significant anisotropic effect.
+the  anisotropy induced by rotation is at the $3\%$ level. We
+performed the same test with all the models and find that the
+variation in $\mu$ does not depend on the rotational velocity;
+however, high optical depth values can increase the variation of
+$\mu$ up to a $15\%$.
 
-We explore other kind of anisotropy by study the effect
-of radiation sources distributed with a different symmetry than the
-gas. To this end we select a subset of the photons in the homogeneous
-models such as they are emitted from off-centered spheres with respect
-to the gas distribution.
-
-Figure \ref{fig:OCspheres} shows the two spherical regions we
-define to test for this effect. Each has a radius of $0.5R$, where $R$
-is the radius of the gaseus sphere. Provided that there is an observer
-located along the $\hat{j}$ direction, we pick two possible positions
-to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
+We also explore a different source of anisotropy by studying the effect
+of radiation sources located in off-centered spheres with respect to
+the gas distribution. Figure \ref{fig:OCspheres} shows the two
+spherical regions we define to test for this effect. Each has a radius
+of $0.5R$, where $R$ is the radius of the gaseus sphere. With an
+observer located along the $\hat{j}$ direction, we pick two possible
+positions to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
 this configuration the emitting sphere centered on $+C\hat{k}$ moves
@@
 
+In this case the $\mu$ distribution is not homogeneous as shown in
+Figure \ref{fig:muhisto}. The off-center emision shows a variation at
+the level of $20\%$ in intensity with the angle $\Theta$. {\bf Como se
+ven los plots de otras velocidades y tau? Tambien son variaciones del
+20\%?}. This variation implies that that the line is more intense in
+the plane perpendicular to the rotation axis.
+
+We also explore the effects of off-centered emission in the line
+morphology. Figure \ref{fig:OC_profiles} show sthe spectra for the two
+off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
+only use photons that have outgoing directions aligned with the
+observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
+asymmetry in the line morphology.
+
+However, we find some cases where there is a possible signature of
+three peaks. This is only present in some models ($\tau = 10^6,
+V=100$\kms and $\tau = 10^7, V=300$\kms) and could be the result of
+two competing effects: the rise in the line's center as the photons in
+the photosphere escape in a single excursion and the broadening in the
+two peaks as the photons closer from the center have to scatter to
+escape.
+
 %JEFR
-
-The variations in the $\mu$ distribution is shown in Figure \ref{fig:muhisto},
-for the Off-Center model there is a strong dependence of the 
-observed flux on the relative position of an observer with $\Delta\mu\leq 25\%$.
-In contrast,the central and homogeneous source distributions only show a 
-weak anisotropy at the level of $\Delta\mu\leq 3\%$. The variations
-in $\mu$ does not depend on the rotational velocity while increasing the optical depth $\tau_{H}$
-would also increase the variation of $\Delta\mu$ up to a $15\%$.
-
-Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
-spheres located at $C=\pm0.5R$.  In this case we only use photons that
-have outgoing directions aligned with the observer i.e $\vert \mu \vert > 
-0.9$ $\&$ $\vert \mu \vert < 1.0]$.  We do not find any asymmetry in 
-the line produced by the off-center emission, the difference
- between the profiles corresponding to the spheres located at $C=-0.5R$ 
- and that ones located at $C=0.5R$ is negligible.  As in the homogeneous/
-central model the line gets broader as the rotational velocity increase also 
-the central part of the line becomes predominant . 
-There is also a signature of possible three peaks profiles for some models ($\tau = 10^6,
-V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
-in detail in the next section.
-
-\begin{figure*}
-\includegraphics[scale=0.3]{f10.eps}
-\caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
-  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
-   \label{fig:OC_profiles}} 
-\end{figure*}
-
-\subsection{Three-Peak Profiles}
-\label{sec:3p}
-
-\begin{figure*}
-\includegraphics[scale=0.3]{f11.eps}
-\caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
-   \label{fig:3p_profiles}} 
-\end{figure*}
 

### 2014-01-28 paper/ms.tex
finished editing section on the triple peak

@@
 
-\subsection{Three-Peak Profiles}
-\label{sec:3p}
-
 \begin{figure*}
@@
 two peaks as the photons closer from the center have to scatter to
-escape.
+escape. We examine in greater detail these cases in the next
+sub-section.
 
-%JEFR
+\subsection{Triple Peaked Profiles}
+\label{sec:3p}
 
-As mentioned above Off-centered emission shows signs of three peak 
-profiles, to analyse this in more detail we use the same method of the spheres
-explained in \S \ref{sec:off-center}. We select spheres at $C=(\pm 0.25R, \pm0.5R, \pm0.75R)$ with a radii of
-$0.25R$ for all the models, for those who present signs of three peak profiles such as 
-$(V_{max}=50km$ $s^{-1}$ \& $\tau_{H}=10^{5}), (V_{max}=100km$ $s^{-1}$ \& $\tau_{H}=10^{6}), 
-(V_{max}=200km$ $s^{-1}$ \& $\tau_{H}=10^{7})$ we made another run with $\tau_{\gamma}=10^{6}$ 
-with the aim of get stronger profiles.
+The off-centered cases with hints of triple peaked emision motivate us
+to explore this in more detail. The first condition is to increase the
+number of photons in the radiative transfer calculation. In the line
+profiles presented in the previous subsection, only $\sim 10^4$ photons
+have the geometric conditions to build the line profile. We run a few
+models with $N_{\gamma} = 10^6$ in order to improve the statistics and
+explore smaller radii for the off-centered spheres.
 
-Figure \ref{fig:3p_profiles} shows our findings, in order to get such profiles 
-a relation between optical depth, rotational velocity and $C$ must be accomplish.
-In particular we found that for the outer spheres $C=\pm 0.75$ the three
-peak arises for all of our models with $\tau_{\gamma}=10^{6}$ this is due to 
-the fact that the wings of the line move away from the central part as $C$ increase. 
-Another requirement is that a high optical depth must be balanced with a high velocity 
-in order to make the wings and the central peak similar in 
-height, for models in which the velocity is low spheres at $C = \pm 0.25$ produce 
-noise three peak profiles due to the high value of $\tau_{H, r}$.
+We re-simulate four models that presented some signs of triple peaked
+profiles: $V_{\rm max}=50\kms$, $\tau_{\rm H}=10^{5}$; $V_{\rm
+  max}=100\kms$, $\tau_{H}=10^{6}$; $V_{\rm max}=150\kms$, $\tau_{\rm
+  H}=10^6$; and $V_{\rm max}=200\kms$, $\tau_{\rm H}=10^{7}$. We
+select the photons that were emitted within spheres of radius $0.25R$
+centered at $C=(0.25R, 0.5R, 0.75R)$, following the same
+geometry presented in Figure \ref{fig:OCspheres}.
 
-Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
+Figure \ref{fig:3p_profiles} summarizes the results for all these
+models. In all cases the stronger triple peaked signatures is
+presented by the emitting spheres close centered at $0.75R$ close to
+the surface. Emitting spheres closer to the center do not show clear
+signatures for a triple peaked emission.
+
+Furthermore, taking into account all the models that do not event present hints for
+a triple peaked emission it would seem that the rotational velocity
+and optical depth must balance each other in order to show this feature
+feature. Namely, if the rotational velocity is close to half the HFWM
+of the line, the triple peaks are more likely to occurr. This is the
+same threshold that in the case of centered emission marks the
+difference between double and single peaked lines.
+
+Are these features observable with current instrumental capabilities?
+As an order of magnitude estimate we can consider that the width of
+each one of the triple peaks is close to $1/3$ of the FWHM of the line
+at a given $V_{\rm max}$. For the cases we have studied in this
+subsection those values would be close to $50\kms$, $100\kms$ and
+$200\kms$ for optical depths of $10^5$, $10^6$, and $10^7$
+respectively. At a redshift of $z\sim 2-3$ each one of these widths
+is multiplied by factors of $z+1\sim 3-4$. Considering a nominal value
+for the resolution of $\Delta v=200\kms$ for a Near-IR spectrograph capable of observing
+those galaxies \citep{Kulas12}, we find that only the case of triple
+peaked emission for the most massive object $\tau_{\rm H}, 10^{7}$,
+$V_{\rm max}=200\kms$ would have a chance to be spectrally resolved.
+
+{\bf Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
 would be observed, this is important for observational porpoises due to the finite 
-spectral resolution.
+spectral resolution. Seguro? Que es baja resolucion y que es alta
+resolucion en este contexto?}
 

### 2014-02-03 paper/ms.tex
fianlly FWHM plot included
my version

@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.eps}
+    \includegraphics[width=0.45\textwidth]{f2.eps}
     \caption{Half-width for the non-dusty models as a function of
@@
 introduces the rotation axis as a preferred direction. This motivates
-us to study the anisotropy of the outgoing photons. In order to study
-possible deviations with respect to an isotropic flux we follow
-\cite{Zheng2013} to estimate the flux as a function of the angle
-$\Theta$ formed by the outgoing photons and the observer. Figure
-\ref{fig:OCspheres} presents a geometric scheme to clarify the
-definition of all relevant directions in the problem.
+us to study deviations from an isotropic flux for the outgoing
+photons. We follow \cite{Zheng2013} to estimate the flux as a function
+of the angle $\Theta$ formed by the outgoing photons and the observer. Figure
+\ref{fig:OCspheres} shows a geometric scheme with all the angles and
+vectors relevant to this problem.
 
@@
 
-The off-centered cases with hints of triple peaked emision motivate us
-to explore this in more detail. The first condition is to increase the
-number of photons in the radiative transfer calculation. In the line
-profiles presented in the previous subsection, only $\sim 10^4$ photons
-have the geometric conditions to build the line profile. We run a few
-models with $N_{\gamma} = 10^6$ in order to improve the statistics and
-explore smaller radii for the off-centered spheres.
+We now study in more detail the conditions for the triple peaked
+emission. To do this we perform new calculations with $N_{\gamma} =
+10^6$ in order to improve the statistics and explore smaller radii for
+the off-centered spheres.
 
@@
 Figure \ref{fig:3p_profiles} summarizes the results for all these
-models. In all cases the stronger triple peaked signatures is
-presented by the emitting spheres close centered at $0.75R$ close to
-the surface. Emitting spheres closer to the center do not show clear
-signatures for a triple peaked emission.
+models. In all cases the stronger triple peaked signatures are
+present in the emitting spheres close to the surface, centered at
+$0.75R$. Emitting spheres closer to the center do not show
+clear signatures for a triple peaked emission.
 
-Furthermore, taking into account all the models that do not event present hints for
-a triple peaked emission it would seem that the rotational velocity
+Taking into account all the models that do not show any hint for
+a triple peaked emission suggests that the rotational velocity
 and optical depth must balance each other in order to show this feature
-feature. Namely, if the rotational velocity is close to half the HFWM
-of the line, the triple peaks are more likely to occurr. This is the
-same threshold that in the case of centered emission marks the
-difference between double and single peaked lines.
+feature. If the rotational velocity is close to half the HFWM
+of the line in the static case, the triple peaks are more likely to
+occurr. This is close to the threshold that marks the difference
+between double and single peaked lines.
 
@@
 is multiplied by factors of $z+1\sim 3-4$. Considering a nominal value
-for the resolution of $\Delta v=200\kms$ for a Near-IR spectrograph capable of observing
-those galaxies \citep{Kulas12}, we find that only the case of triple
-peaked emission for the most massive object $\tau_{\rm H}, 10^{7}$,
-$V_{\rm max}=200\kms$ would have a chance to be spectrally resolved.
+for the resolution of $\Delta v=200\kms$ for a Near-IR spectrograph
+capable of observing those galaxies \citep{Kulas12}, we find that only
+the case of triple peaked emission for the most massive object
+$\tau_{\rm H}, 10^{7}$, $V_{\rm max}=200\kms$ would have a chance to
+be spectrally resolved.
 
-{\bf Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
-would be observed, this is important for observational porpoises due to the finite 
-spectral resolution. Seguro? Que es baja resolucion y que es alta
-resolucion en este contexto?}
+%{\bf Figure \ref{fig:3p_res} show that even with a low resolution a
+%  three-peak profile  would be observed, this is important for
+%  observational porpoises due to the finite  spectral
+%  resolution. Seguro? Que es baja resolucion y que es alta resolucion en este contexto?}
 
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.3]{f12.eps}
-\end{center}
-\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
-   \label{fig:3p_res}} 
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%\includegraphics[scale=0.3]{f12.eps}
+%\end{center}
+%\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
+%   \label{fig:3p_res}} 
+%\end{figure}
 
@@
 We follow a classification of \ly profiles made by
-\cite{Kulas12}. They presented observational results for star forming
+\cite{Kulas12}. They presented observational results for $18$ star forming
 galaxies at $z=2$-$3$ with multiple peaks in their \ly emission.
@@
 stronger, in both cases the peaks are symmetrically located around the
-line center. In Group III the blue peak also dominates but there is an
-overall redward shift of the zero point. Group IV presents two similar
+line center. In Group III the blue peakdominates but there is an
+overall redward shift of the velocity zero point. Group IV presents two similar
 peaks symmetrically located around the zero point and Group V galaxies show
@@
 in between of the two peaks is high ($ \geq 70 \%$ of the intensity in
-the highest peak). Finally, the triple peaked lines in Galaxies in
-Group V can be easily reproduced by rotation with off-centered
-emission given the right amount of asymmetry between the emitting
-region and neutral hydrogen distribution.
+the srongest peak). Finally, the spectrum of the single galaxy in
+Group V out of the total $18$ can be produced by rotation with
+off-centered emission given the right amount of asymmetry between the
+emitting region and neutral hydrogen distribution.
 
 Another relevant sample of observations was presented by \cite{Yamada2012} 
-for 91 LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
+for $91$ LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
 a single peak profile. Some of the peaks have a strong symmetry, while
@@
 specially if the two peaks have similar intensities. The case of
-triple peaked lines is another clear feature of gas rotation under the
+triple peaked lines is clear feature of gas rotation under the
 additional condition of an off-centered emission.
@@
 of rotation in the morphology of the \ly emission line in star forming
-galaxies.  The results are based on the study of an homogeneous sphere
-of gas with solid body rotation. We explore a range of models by varying
+galaxies.  The results are based on the study of an homogeneous
+gaseous sphere with solid body rotation. We explore a range of models by varying
 the rotational speed, hydrogen optical depth, dust optical depth and
 initial distribution of \ly photons with respect to the gas
-density. As a cross-validation, we obtain our results from two
+distribution. As a cross-validation, we obtain our results from two
 independently developed Monte-Carlo radiative transfer codes.
@@
 peaked lines as the rotational velocity increases. In the case of
-off-centered emission result into triple peaked lines for certain
-values of optical depth and rotational velocities.
+off-centered emission triple peaked lines are also possible for
+certain values of optical depth and rotational velocities.
 
@@
 
-\item The line width increases with rotational velocity. The line with
-  approximately follows the functional form $W^2 = W_{
-    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
-  width for the static case. $\lambda$ is a constat determined from
-  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
-  $\lambda_{\rm h}=YY$ for the central and homogeneous source
-  distribution, respectively.
+\item The line width increases with rotational velocity, following the
+  functional form $W^2 = W_{0}^2 + (V_{\rm max}/\lambda)^2$ where
+  $W_{0}$ indicates the line width for the static case. $\lambda$ is a
+  constant determined from the radiative transfer results it is
+  $\lambda_{\rm c}=XX$ and $\lambda_{\rm h}=YY$ for the central and
+  homogeneous source distribution, respectively.
 
-\item A single peaked line emerges for high rotational velocities in
-  the case of homgeneously distributed sources. The cases of single
-  peaked lines occur when the rotational velocity is larger than the
-  line width measured in the static case.
+\item For homogeneously distributed sources the double peaked line
+  transforms into a single peaked line for high rotational
+  velocities. This occurs when the rotational velocity is larger than half the
+  line width measured in the static case. In the case of central
+  sources the double peaked line was always present in the range of
+  explored rotational velocities.
 
-\item For central sources we find that the number of scatterings
-does not significantly decrease with rotation, this is due to the 
-fact that the vast majority of scatterings events are resonant, 
-during which the mean free path is very short and the effect of gas
-bulk rotation is not enough to affect \ly photons.
-The escape fraction does not depend on the rotational velocity neither
-the position of the peaks, but there is an increase 
-in the flux on the central parts of the line for high rotational 
-velocities.
+\item For homogeneously distributes sources the average number of
+  scatterings before escaping decreases with rotational velocity, this
+  is driven by the existence of a photo-sphere where photons can
+  escape after a single scattering. For central sources this
+  photo-sphere does not exist and we do not find any significant
+  change in the average number of scatterings.
 
-\item For homogeneous sources we find that the changes in the
-line morphology are linked to the reduction in the average number of
-scatterings. In the second part of \S \ref{sec:widthpeak} we show
-that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings and on average 
-with $40\%$ less scatterings than in the static case. This makes highly improbable 
-that a photon's frequency can move away from the line's center. 
-In \S \ref{sec:widthpeak} For typical column densities of $N_{HI}=1e^{19}-1e^{20}$, 
-we find that rotational velocities of 100-300 \kms broaden the line profile up 
-to a factor of $2-3$ in comparison to the static case. Simultaneously, the
-flux in the line center also increases with rotational velocity. This
-increase induces the transition from a double peak to a single peak
-line in the models where the radiation sources are homogeneously
-distributed. Also the escape fraction increase by factors of $2-10$ with 
-respect to the slab with centrally sources.
+\item As a consequence of the change in the average number of
+  scatterings there is an impact on the escape fraction. Consistent
+  with the picture summarized in the previous item, the escape
+  fraction increases (up to a factor of $XXX$) with rotational
+  velocity for the spheres with homogeneous sources, while it stays
+  constant in the case of central sources.
 
-\item For non-symmetric sources we find that three peak profiles
-could emerge for models in which the rotational velocity is the necessary 
-to give rise to a central peak, but not that high to decrease the
-amount of photons in the wings. When initial off-center sources are 
-selected from the outer parts of the galaxy the wings of the line are stronger.
-Also we do not find any considerable asymmetries in the line produced by off-center 
-emission.
+\item We explore the deviations in photon intensity from an isotropic
+  flux. We find that the variations are always less than $5\%$ with
+  respect to the homogeneous emission from the
+
+\item In the case of off-centered emission it is possible to find
+  spectra with a triple peaked profile. This feature is clearly present for
+  sources emitted close to the surface of the sphere in cases where
+  the rotational velocity is half the FWHM measured in the static case.
+
+\item Comparing our results with recent detailed observations of the
+  \ly profile at redshifts $z\sim 2-3$ we find that morphological
+  features such as high central line flux, single peak profiles and
+  multi-peaked profiles could be explained by gas bulk  rotation
+  present in these LAEs. 
 \end{itemize}
-
-Comparing our results with recent observed LAEs we find that many 
-morphological features such as high central line flux, single peak
-profiles and multi-peaked profiles could be explained by gas bulk 
-rotation present in these LAEs.
 

### 2014-02-10 paper/ms.tex
fig 1.eps
Width plot in the paper
Fig 8 improved
Lambda dertmined

--- 2014-01-28 paper/ms.tex
@@
 \usepackage {graphicx}
-
 \usepackage{graphics}
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{f1_1.eps}
-  \includegraphics[width=0.45\textwidth]{f1_2.eps}
+  \includegraphics[width=1.0\textwidth]{f1.eps}
 \end{center}
@@
 \ref{fig:differentvelocities}. It shows the evident
-impact of rotation on the morphology of the emergent \ly line. Both
-panels focus on the results for $\tau_{H}=10^{7}$, showing that the
+impact of rotation on the morphology of the emergent \ly line.
+The panel focus on the results for all of our symmetric models
+ $\tau_{H}=10^{6}, 10^{6}, 10^{5}$, showing that the
 influence of rotation is present both when the photons are either
@@
 
-\begin{figure}
-    \includegraphics[width=0.45\textwidth]{NewWidthVvsVmax.eps}
+\begin{figure*}
+    \includegraphics[width=1.0\textwidth]{f2.eps}
     \caption{Half-width for the non-dusty models as a function of
@@
       distributions. \label{fig:widthvsvelocity}} 
-\end{figure}
+\end{figure*}
 
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{f3.eps}
+    \includegraphics[scale=0.4]{f3.eps}
 \caption{Position of the peak maxima as a function of rotational
@@
 quadratic sum of the two relevant velocities in the problem. We find
-that for $\lambda = x\pm y$ ($\lambda=x\pm y$) for the central
+that for $\lambda = 3.895$ ($\lambda= 1.982$) for the central
 (homogeneous) sources.
@@
 velocity threshold the line becomes single peaked with $x_{\rm m}=0$
-\kms. {\bf By inspection we find that in all cases the transition has
-occurred when the rotational velocity is larger than the intrinsic
-linewidth OR HALF WIDTH ONCE THE NUMBERS ARE FIXED?}.
+\kms. By inspection we find that in all cases the transition has
+occurred when the rotational velocity is larger than half width .
 
@@
 \begin{figure}
-    \includegraphics[width=0.45\textwidth]{f4.eps}
+    \includegraphics[scale=0.4]{f4.eps}
 \caption{Logarithm of the average number of scatterings as function of
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{f5_1.eps}
-  \includegraphics[width=0.45\textwidth]{f5_2.eps}
-  \includegraphics[width=0.45\textwidth]{f5_3.eps}
-  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
+  \includegraphics[scale=0.35]{f5_1.eps}
+  \includegraphics[scale=0.35]{f5_2.eps}
+  \includegraphics[scale=0.35]{f5_3.eps}
+  \includegraphics[scale=0.35]{f5_4.eps}    
 \end{center}
@@
 \begin{figure}
-  \includegraphics[width=0.45\textwidth]{f6.eps}
+  \includegraphics[scale=0.4]{f6.eps}
   \caption{Escape fraction as a function of rotational velocity. All
@@
 \begin{figure}
-  \includegraphics[width=0.45\textwidth]{f7.eps}
+  \includegraphics[scale=0.4]{f7.eps}
   \caption{Escape fraction as a function of the
@@
 we can predict that for central source distributions the escape
-fraction will barely change, while larger effects should be expecte
+fraction will barely change, while larger effects should be expected
 for homogeneously distributed sources.
@@
 \begin{figure}
-  \includegraphics[scale=0.3]{f8.eps}
+\begin{center}
+  \includegraphics[scale=0.4]{f8.eps}
   \caption{The two small circles show the two different spherical
@@
     $\hat{k}_{\rm out}$ represents the outgoing direction of an
-    escaping \ly photon. {\bf Si el observador esta en j, entonces las
-    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
-    hacer las dos circulos pequenos punteados. Por otro lado, como se
-    habian definido las velocidades, el eje de rotacion es el eje k}
+    escaping \ly photon. 
     \label{fig:OCspheres}}
+
+\end{center}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[scale=0.35]{f9.eps}
+  \includegraphics[scale=0.4]{f9.eps}
   \caption{$\mu$ histogram showing the orientation effects for the different
@@
 \begin{center}
-\includegraphics[scale=0.3]{f10.eps}
+\includegraphics[scale=0.35]{f10.eps}
 \end{center}
@@
 \begin{figure*}
-\includegraphics[scale=0.3]{f11.eps}
+\includegraphics[scale=0.4]{f11.eps}
 \caption{Triple peaked profiles for three different off-center positions
@@
 $V_{\rm max}=200\kms$ would have a chance to be spectrally resolved.
-
-{\bf Figure \ref{fig:3p_res} show that even with a low resolution a three-peak profile 
-would be observed, this is important for observational porpoises due to the finite 
-spectral resolution. Seguro? Que es baja resolucion y que es alta
-resolucion en este contexto?}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.3]{f12.eps}
-\end{center}
-\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
-   \label{fig:3p_res}} 
-\end{figure}
 

### 2014-02-11 paper/ms.tex
fixing small things

@@
     different velocities rotational velocities for spherical
-    distributions with $\tau_{H}=10^{7}$. The left (right) panel shows
-    the central (homogeneous) photon distribution. All photons were
-    taken into  account regardless of their final direction of propagation.
+    distributions in all the models. The continous (dashed) line represents the 
+    central (homogeneous) source distributions.
     \label{fig:differentvelocities}}  
@@
 In the next subsections we characterize the line morphology by
-the half-width at half intensity and the peak maxima. In order to
-interpret the morphological changes in the line we also report the
+the full width at half maximum (FWHM) and the location of the peak maxima. In order to interpret the morphological changes in the line we also report the
 median number of scatter for each \ly photon in the
@@
 scalar to be determined as a fit to the data. With this test we want
-to know to what extent the new velocity witdth can be expressed as a
-quadratic sum of the two relevant velocities in the problem. We find
-that for $\lambda = 3.895$ ($\lambda= 1.982$) for the central
-(homogeneous) sources.
+to know to what extent the new velocity width can be expressed as a
+quadratic sum of the two relevant velocities in the problem. By
+fitting simultaneously all the data points corresponding to central
+and homogeneous models we find $\lambda_{\rm c} = 3.9 \pm$ and
+$\lambda_{\rm h}= 1.9\pm $ respectively.
 
@@
   width for the static case. $\lambda$ is a constat determined from
-  the radiative transfer results it is $\lambda_{\rm c}=XX$ and
-  $\lambda_{\rm h}=YY$ for the central and homogeneous source
+  the radiative transfer results it is $\lambda_{\rm c}=3.9\pm$ and
+  $\lambda_{\rm h}=1.9\pm$ for the central and homogeneous source
   distribution, respectively.

### 2014-02-11 paper/ms.tex
minor changes

@@
 
-In the next subsections we characterize the line morphology by
-the full width at half maximum (FWHM) and the location of the peak maxima. In order to interpret the morphological changes in the line we also report the
-median number of scatter for each \ly photon in the
+In the next subsections we characterize the line morphology by the
+full width at half maximum (FWHM) and the location of the peak
+maxima. In order to interpret the morphological changes in the line we
+also report the median number of scatter for each \ly photon in the
 simulation. For the models where dust is included we measure the 
@@
 \begin{figure*}
-    \includegraphics[width=1.0\textwidth]{f2.eps}
-    \caption{Half-width for the non-dusty models as a function of
-      rotational velocity $V_{\rm max}$. Continuous (dashed) lines
-      correspond to central (homogeneous) source
-      distributions. \label{fig:widthvsvelocity}} 
+\begin{center}
+  \includegraphics[width=0.9\textwidth]{f2.eps}
+\end{center}
+  \caption{FWHM for the non-dusty models as a function of
+    rotational velocity $V_{\rm max}$. The left panel shows the
+    results in velocity units while the right panel normalizes
+    the data by the FWHM in the static case. 
+    Continuous (dashed) lines  correspond to central (homogeneous)
+    source distributions. The straight lines represent the fit to
+    the data using the expresion in Eq. (\ref{eq:fwhm}).
+    \label{fig:widthvsvelocity}} 
 \end{figure*}
@@
 \begin{figure}
-    \includegraphics[scale=0.4]{f3.eps}
+    \includegraphics[scale=0.35]{f3.eps}
 \caption{Position of the peak maxima as a function of rotational
@@
 
-We use the full width at half maximum (FWHM), $W$, to quantify the line
-broadening. Figure \ref{fig:widthvsvelocity} shows how $W$ increases
-with rotational velocity. {\bf Here we need to check the numbers to
-  say something more specific.}
-
-We parameterize the dependency of the linewidth as $W^2 =
-W_{0}^2 + V_{\rm max}^2/\lambda^2$, where $W_{0}$ is the
-velocity width in the static case and $\lambda$ is a positive
-scalar to be determined as a fit to the data. With this test we want
-to know to what extent the new velocity width can be expressed as a
-quadratic sum of the two relevant velocities in the problem. By
-fitting simultaneously all the data points corresponding to central
-and homogeneous models we find $\lambda_{\rm c} = 3.9 \pm$ and
-$\lambda_{\rm h}= 1.9\pm $ respectively.
+We use the full width at half maximum (FWHM) to quantify the line
+broadening. Figure \ref{fig:widthvsvelocity} shows how $FWHM$ increases
+with rotational velocity both for the central an homogeneous source
+distributions.  We parameterize the dependency of the linewidth as
+\begin{equation}
+ FWHM^2 = FWHM_{0}^2 + V_{\rm max}^2/\lambda^2,
+\label{eq:fwhm}
+\end{equation}
+%
+where $FWHM_{0}$ is the
+velocity width in the static case and $\lambda$ is a positive scalar
+to be determined as a fit to the data. With this test we want to know
+to what extent the new velocity width can be expressed as a quadratic
+sum of the two relevant velocities in the problem. We fit
+simultaneously all the points corresponding to central and homogeneous
+models to find $\lambda_{\rm c} = 3.9 \pm$ and $\lambda_{\rm h}=
+1.9\pm $ respectively.
 
@@
 \begin{figure}
-    \includegraphics[scale=0.4]{f4.eps}
+    \includegraphics[scale=0.35]{f4.eps}
 \caption{Logarithm of the average number of scatterings as function of
@@
 \begin{figure}
-  \includegraphics[scale=0.4]{f6.eps}
+  \includegraphics[scale=0.35]{f6.eps}
   \caption{Escape fraction as a function of rotational velocity. All
@@
 \begin{figure}
-  \includegraphics[scale=0.4]{f7.eps}
+  \includegraphics[scale=0.35]{f7.eps}
   \caption{Escape fraction as a function of the
@@
 \begin{center}
-  \includegraphics[scale=0.4]{f8.eps}
+  \includegraphics[scale=0.35]{f8.eps}
   \caption{The two small circles show the two different spherical
@@
 \begin{figure}
-  \includegraphics[scale=0.4]{f9.eps}
+  \includegraphics[scale=0.35]{f9.eps}
   \caption{$\mu$ histogram showing the orientation effects for the different
@@
 \begin{figure*}
-\includegraphics[scale=0.4]{f11.eps}
+\begin{center}
+\includegraphics[scale=0.35]{f11.eps}
+\end{center}
 \caption{Triple peaked profiles for three different off-center positions

### 2014-02-11 paper/ms.tex
I am hungry

@@
 
-\begin{figure}
+\begin{figure*}
+\begin{center}
   \includegraphics[scale=0.35]{f6.eps}
-  \caption{Escape fraction as a function of rotational velocity. All
+  \includegraphics[scale=0.35]{f7.eps}
+\end{center}
+  \caption{Effects of rotaation on the escape fraction. Left
+    panel. Escape fraction as a function of rotational velocity. All
     these models have $\tau_{a}=1$. The continuous (dashed) lines
-    correspond to central (homogeneous) models.
-    \label{fig:efvsv}}
-\end{figure}
+    correspond to central (homogeneous) models. Right panel. Escape
+    fraction as a    function of the product $(a\tau_{\rm
+      H})^{1/3}\tau_{a}$. The    analytic solution for the infinite
+    slab is shown as a continuous    line. Different lines correspond
+    to different rotational    velocities.     \label{fig:efvsv}} 
+\end{figure*}
 
-\begin{figure}
-  \includegraphics[scale=0.35]{f7.eps}
-  \caption{Escape fraction as a function of the
-    product $(a\tau_{\rm H})^{1/3}\tau_{a}$. The analytic solution for
-    the infinite slab is shown as a continuous line. Different dashed
-    lines correspond to different rotational velocities.
-    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
-    \label{fig:efvsNeufeld}}   
-\end{figure}
+%\begin{figure}
+%  \caption{
+
+%    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
+%    \label{fig:efvsNeufeld}}   
+%\end{figure}
 
@@
 \subsection{Anisotropy and off-centered emission}
+\label{sec:off-center}
 
-\label{sec:off-center}
 \begin{figure}
@@
   \includegraphics[scale=0.35]{f8.eps}
-  \caption{The two small circles show the two different spherical
-    off-centered emitting regions with respect to the larger spherical
-    gas distribution. The angular velocity vector is
-    defined to be along the $\hat{\i}$ direction (outwards the
-    page). In order to study a possible anysotropy we place an
-    observer along the the $\hat{\j}$ direction. The vector
-    $\hat{k}_{\rm out}$ represents the outgoing direction of an
-    escaping \ly photon. 
+\end{center}
+\caption{Schematic representation of the geometry for the off-center
+  emission. The large circle represents the gas distribution and the
+    two smaller circles the off-centered \ly emitting regions. The angular
+    velocity vector lies along $\hat{k}$ direction
+    towards the reader. The vector $\hat{k}_{\rm out}$ represents the
+    outgoing direction of an escaping \ly photon and the observer is
+    placed along the $\hat{j}$ direction. The distribution of $\Theta$
+    angles is used to study potential emission anisotropies. 
     \label{fig:OCspheres}}
-
-\end{center}
 \end{figure}
@@
   \includegraphics[scale=0.35]{f9.eps}
-  \caption{$\mu$ histogram showing the orientation effects for the different
-  distributions central(Points line), homogeneous(Dashed) and off-Center(Solid line).  
+  \caption{Histogram of $\mu\equiv\cos\Theta$ for the 
+    central (dotted), homogeneous (dashed) and off-center (solid
+    line) distributions. Deviations from a flat distribution signal the presence of
+    spatial emission anisotropies. 
     \label{fig:muhisto}} 

### 2014-02-12 paper/ms.tex
escape graction table

@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{c c}
+\hline \hline
+Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
+\hline \hline
+Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
+Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
+Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
+Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
+Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
+Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
 \begin{figure*}
@@
 In this case the $\mu$ distribution is not homogeneous as shown in
-Figure \ref{fig:muhisto}. The off-center emision shows a variation at
-the level of $20\%$ in intensity with the angle $\Theta$. {\bf Como se
-ven los plots de otras velocidades y tau? Tambien son variaciones del
-20\%?}. This variation implies that that the line is more intense in
+Figure \ref{fig:muhisto}. The off-center emision shows a variation of flux at
+the levels of $10\% - 28\%$ in intensity with the angle $\Theta$. In general 
+models with a larger $\tau_{H}$ present a higher variation in the flux.
+This variation implies that that the line is more intense in
 the plane perpendicular to the rotation axis.

### 2014-02-12 paper/ms.tex
finishing table2.
Lambda errors added

@@
 The panel focus on the results for all of our symmetric models
- $\tau_{H}=10^{6}, 10^{6}, 10^{5}$, showing that the
+ $\tau_{H}=(10^{6}, 10^{6}, 10^{5}$), showing that the
 influence of rotation is present both when the photons are either
@@
 velocities, a result that is evident for the homogeneously distributed
-sources as shown in right panel in Figure \ref{fig:differentvelocities}.
+sources as shown in the dashed lines of Figure \ref{fig:differentvelocities}.
 
@@
 simultaneously all the points corresponding to central and homogeneous
-models to find $\lambda_{\rm c} = 3.9 \pm$ and $\lambda_{\rm h}=
-1.9\pm $ respectively.
+models to find $\lambda_{\rm c} = 3.9 \pm 3.17\times 10^{-17}$ and $\lambda_{\rm h}=
+1.9\pm 3.07\times 10^{-10}$ respectively.
 
@@
 scatterings $\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$
-for different velocities. In this setup the number of scatterings is
+for different velocities. In this set-up the number of scatterings is
 proportional to the optical depth, with $\langle N_{\rm
@@
   scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
-representsfactors of $(0.66, 0.59, 0.55)$ lower than the centrally
+represents factors of $(0.66, 0.59, 0.55)$ lower than the centrally
 emitted photons. In contrast the analytic solution for the homogeneous
@@
 dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
-such histogram in the case $\tau_{\rm H}=10^5$ for the
+such histograms in the case $\tau_{\rm H}=10^5$ for the
 static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
@@
 \end{tabular}
+\caption{
+ Escape fraction values for all of the models. } 
+\label{table:escape}
 \end{center}
@@
 to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
-all the values for the escape fraction {\bf We also need a table
-  listing the escape  fraction values.}
+all the values for the escape fraction.
 

### 2014-02-12 paper/ms.tex
Fig7. albedo corrected

@@
 \hline \hline
-Homogeneous $10^{5}$& $0.2637, 0.2661, 0.3091, 0.3570, 0.3709$ \\
-Homogeneous $10^{6}$ & $0.2894, 0.2891, 0.3096, 0.3607, 0.3937$ \\
-Homogeneous $10^{7}$ &$ 0.2279, 0.2298, 0.2318, 0.2547, 0.2813 $\\
-Central $10^{5}$ & $0.0966, 0.0966, 0.0965, 0.0965, 0.0965$ \\
-Central $10^{6}$ & $0.0663, 0.665, 0.0665, 0.0665, 0.665$ \\
-Central $10^{7}$ & $0.0149, 0.0158, 0.0158, 0.0158, 0.0158$ \\
+Homogeneous $10^{5}$& $\ 0.2637\  0.2661\  0.3091\  0.3570\  0.3709$ \\
+Homogeneous $10^{6}$ & $\ 0.2894\  0.2891\  0.3096\  0.3607\  0.3937$ \\
+Homogeneous $10^{7}$ &$\ 0.2279\  0.2298\  0.2318\  0.2547\  0.2813 $\\
+Central $10^{5}$ & $\ 0.0966\  0.0966\  0.0965\  0.0965\  0.0965$ \\
+Central $10^{6}$ & $\ 0.0663\  0.0665\  0.0665\  0.0665\  0.0665$ \\
+Central $10^{7}$ & $\ 0.0149\  0.0158\  0.0158\  0.0158\  0.0158$ \\
 \hline
@@
 \end{center}
-  \caption{Effects of rotaation on the escape fraction. Left
+  \caption{Effects of rotation on the escape fraction. Left
     panel. Escape fraction as a function of rotational velocity. All
@@
 
-In Figure \ref{fig:efvsNeufeld} we put these results in the context of
+In the right pnael of Figure \ref{fig:efvsv} we put these results in the context of
 the analytic solution for the infinite slab \citep{Neufeld90}. In
@@
 $(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
-in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in Figure
-\ref{fig:efvsNeufeld} show the results for the different rotational
+in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
+\ref{fig:efvsv} show the results for the different rotational
 velocities. First of all we note that the escape fraction does not

### 2014-02-13 paper/ms.tex
font size in histograms
rewriting the conclusions

@@
 We use the full width at half maximum (FWHM) to quantify the line
-broadening. Figure \ref{fig:widthvsvelocity} shows how $FWHM$ increases
+broadening. Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
 with rotational velocity both for the central an homogeneous source
@@
 \begin{equation}
- FWHM^2 = FWHM_{0}^2 + V_{\rm max}^2/\lambda^2,
+ {\rm FWHM}^2 = {\rm FWHM}_{0}^2 + V_{\rm max}^2/\lambda^2,
 \label{eq:fwhm}
@@
 %
-where $FWHM_{0}$ is the
+where FWHM$_{0}$ is the
 velocity width in the static case and $\lambda$ is a positive scalar
@@
 models to find $\lambda_{\rm c} = 3.9 \pm 3.17\times 10^{-17}$ and $\lambda_{\rm h}=
-1.9\pm 3.07\times 10^{-10}$ respectively.
+1.9\pm 3.07\times 10^{-10}$ respectively.  {\bf EL ERROR ES de $10^{-17}???$}
 
@@
 \begin{center}
-\begin{tabular}{c c}
+\begin{tabular}{c ccc ccc}
 \hline \hline
-Model, $\tau_{H}$ & $\ V_{max}(km\ s^{-1})$ $0, 50, 100, 200, 300$ \\
-\hline \hline
-Homogeneous $10^{5}$& $\ 0.2637\  0.2661\  0.3091\  0.3570\  0.3709$ \\
-Homogeneous $10^{6}$ & $\ 0.2894\  0.2891\  0.3096\  0.3607\  0.3937$ \\
-Homogeneous $10^{7}$ &$\ 0.2279\  0.2298\  0.2318\  0.2547\  0.2813 $\\
-Central $10^{5}$ & $\ 0.0966\  0.0966\  0.0965\  0.0965\  0.0965$ \\
-Central $10^{6}$ & $\ 0.0663\  0.0665\  0.0665\  0.0665\  0.0665$ \\
-Central $10^{7}$ & $\ 0.0149\  0.0158\  0.0158\  0.0158\  0.0158$ \\
+Sources & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
+& &  &  & (\kms) & & \\ 
+& & 0 & 50 & 100 &200 & 300\\ \hline 
+Homogeneous & $10^{5}$& 0.263 & 0.266 &  0.309 &  0.357 &  0.370  \\
+           & $10^{6}$ & 0.289 &  0.289 &   0.309 &  0.360 &  0.393 \\
+         &$10^{7}$ &  0.227 &  0.229 &  0.231 &  0.254 &  0.281 \\
+Central & $10^{5}$ &  0.096 & 0.097 & 0.096 &  0.096 & 0.096 \\
+  &$10^{6}$ & 0.066 & 0.066 &  0.066 &  0.066 &  0.066 \\
+ &$10^{7}$ & 0.015 &  0.016 & 0.016 & 0.016 & 0.015 \\
 \hline
@@
 \caption{
- Escape fraction values for all of the models. } 
+ Escape fraction values for all dusty models. } 
 \label{table:escape}
@@
 
-In the right pnael of Figure \ref{fig:efvsv} we put these results in the context of
+In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
 the analytic solution for the infinite slab \citep{Neufeld90}. In
@@
 
-Quantitatively the main results of our study are summarized in the
-following items.
+Quantitatively the main results of our study are summarized as follows.
 
@@
 \item The line width increases with rotational velocity. The line with
-  approximately follows the functional form $W^2 = W_{
-    0}^2 + (V_{\rm max}/\lambda)^2$ where $W_{0}$ indicates the line
+  approximately following the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
+    0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
   width for the static case. $\lambda$ is a constat determined from
@@
 \item A single peaked line emerges for high rotational velocities in
-  the case of homgeneously distributed sources. The cases of single
-  peaked lines occur when the rotational velocity is larger than the
-  line width measured in the static case.
+  the case of homgeneously distributed sources. These cases occur when
+  the rotational velocity is larger than hFWHM$_0$.
 
 \item For central sources we find that the number of scatterings
-does not significantly decrease with rotation, this is due to the 
+does not significantly decrease with rotation. This is due to the 
 fact that the vast majority of scatterings events are resonant, 
 during which the mean free path is very short and the effect of gas
-bulk rotation is not enough to affect \ly photons.
-The escape fraction does not depend on the rotational velocity neither
-the position of the peaks, but there is an increase 
-in the flux on the central parts of the line for high rotational 
-velocities.
+bulk rotation is not enough to affect \ly photons. In consequence, 
+the escape fraction neither the position of the peaks depende on the
+rotational velocity. However, there is a flux increase with rotational
+velocity in the central parts of the line.
 
@@
 that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings and on average 
-with $40\%$ less scatterings than in the static case. This makes highly improbable 
-that a photon's frequency can move away from the line's center. 
-In \S \ref{sec:widthpeak} For typical column densities of $N_{HI}=1e^{19}-1e^{20}$, 
-we find that rotational velocities of 100-300 \kms broaden the line profile up 
-to a factor of $2-3$ in comparison to the static case. Simultaneously, the
-flux in the line center also increases with rotational velocity. This
-increase induces the transition from a double peak to a single peak
-line in the models where the radiation sources are homogeneously
-distributed. Also the escape fraction increase by factors of $2-10$ with 
-respect to the slab with centrally sources.
+escape with less than $10$ scatterings. The avarage number of
+scatterings decreases a $40\%$ compared to the static case. 
+The reduction in the number of scattering decreases the probability
+for a photon to move away from the line's center. This is also
+translated into an increase of the escape fraction by a factor of
+$\sim 2$ with respect to the static situation.
 
-\item For non-symmetric sources we find that three peak profiles
-could emerge for models in which the rotational velocity is the necessary 
-to give rise to a central peak, but not that high to decrease the
-amount of photons in the wings. When initial off-center sources are 
-selected from the outer parts of the galaxy the wings of the line are stronger.
-Also we do not find any considerable asymmetries in the line produced by off-center 
-emission.
+\item The spatial anisotropies in the emission are always at a level
+  below the $10\%$ deviation from static models.
+
+\item For off-centered emission triple peaked profiles can emerge
+  under two conditions: the emission occurs close to th sphere's
+  surface and the rotational velocity is half the FWHM in the static
+  case.   
 \end{itemize}

### 2014-02-13 paper/ms.tex
figures
spelling

@@
 to the peculiar velocities of the Hydrogen atom that absorbed and
-reemitted the photon. If dust is present, the photon can interact
+re-emitted the photon. If dust is present, the photon can interact
 either with a Hydrogen atom or dust grain. In the case of a dust
@@
 direction of propagation. In our case we select the initial frequency
-to be exactly the \ly restframe frequency ($x=0$) and the direction of
+to be exactly the \ly rest-frame frequency ($x=0$) and the direction of
 propagation to be random following an flat probability distribution
@@
 \begin{center}
-  \includegraphics[width=1.0\textwidth]{f1.eps}
+  \includegraphics[width=0.8\textwidth]{f1.eps}
 \end{center}
@@
     different velocities rotational velocities for spherical
-    distributions in all the models. The continous (dashed) line represents the 
+    distributions in all the models. The continuous (dashed) line represents the 
     central (homogeneous) source distributions.
@@
 escape fraction as a function of rotational velocity. Finally, we make
-an estimate of the anisotriopic emission of the models in comparison
+an estimate of the anisotropic emission of the models in comparison
 with static spheres.
@@
 \begin{center}
-  \includegraphics[width=0.9\textwidth]{f2.eps}
+  \includegraphics[width=0.8\textwidth]{f2.eps}
 \end{center}
@@
     source distributions. The straight lines represent the fit to
-    the data using the expresion in Eq. (\ref{eq:fwhm}).
+    the data using the expression in Eq. (\ref{eq:fwhm}).
     \label{fig:widthvsvelocity}} 
@@
 \begin{figure}
-    \includegraphics[scale=0.35]{f3.eps}
+\begin{center}
+  \includegraphics[width=0.40\textwidth]{f3.eps}
+\end{center}
 \caption{Position of the peak maxima as a function of rotational
@@
 There are three clear effects on the line's morphology as the
-rotational veloctiy increases. First, the line
+rotational velocity increases. First, the line
 broadens; second, the double peaks reduce their intensity; and third,
 the intensity at the line center rises. The two last effects give the
-impresion that the double peaks are merger into one at high rotational
+impression that the double peaks are merger into one at high rotational
 velocities, a result that is evident for the homogeneously distributed
@@
 with rotational velocity both for the central an homogeneous source
-distributions.  We parameterize the dependency of the linewidth as
+distributions.  We parameterize the dependency of the line width as
 \begin{equation}
@@
 \begin{figure}
-    \includegraphics[scale=0.35]{f4.eps}
+\begin{center}
+    \includegraphics[width=0.40\textwidth]{f4.eps}
+\end{center}
 \caption{Logarithm of the average number of scatterings as function of
@@
 \begin{center}
-  \includegraphics[scale=0.35]{f5_1.eps}
-  \includegraphics[scale=0.35]{f5_2.eps}
-  \includegraphics[scale=0.35]{f5_3.eps}
-  \includegraphics[scale=0.35]{f5_4.eps}    
+  \includegraphics[width=0.45\textwidth]{f5_1.eps}
+  \includegraphics[width=0.45\textwidth]{f5_2.eps}
+  \includegraphics[width=0.45\textwidth]{f5_3.eps}
+  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
 \end{center}
@@
 shifts from the center as the amount of neutral hydrogen
-increases. This can be precisely quantifyied in the static slab
+increases. This can be precisely quantified in the static slab
 with central sources where the maxima position are related to
@@
 \hline \hline
-Sources & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
-& &  &  & (\kms) & & \\ 
+Source & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
+Distribution& &  &  & (\kms) & & \\ 
 & & 0 & 50 & 100 &200 & 300\\ \hline 
@@
 \begin{center}
-  \includegraphics[scale=0.35]{f6.eps}
-  \includegraphics[scale=0.35]{f7.eps}
+  \includegraphics[width=0.40\textwidth]{f6.eps}
+  \includegraphics[width=0.40\textwidth]{f7.eps}
 \end{center}
@@
 the models with low optical depth. For instance, in models with
-$\tau_{\rm H}=10^5$, the static scape fraction is $0.26$ and increases
+$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
 to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
@@
   single excursion, porque explica eso la fraccion de escape?}
- %we are in a regime where the condition for the analytic expectations
- %($a\tau_{h}\gg 1$) does not hold.
 
@@
 \begin{center}
-  \includegraphics[scale=0.35]{f8.eps}
+  \includegraphics[width=0.40\textwidth]{f8.eps}
 \end{center}
@@
     placed along the $\hat{j}$ direction. The distribution of $\Theta$
-    angles is used to study potential emission anisotropies. 
+    angles is used to study potential emission anisotropy. 
     \label{fig:OCspheres}}
@@
 \begin{figure}
-  \includegraphics[scale=0.35]{f9.eps}
+  \includegraphics[width=0.42\textwidth]{f9.eps}
   \caption{Histogram of $\mu\equiv\cos\Theta$ for the 
@@
     line) distributions. Deviations from a flat distribution signal the presence of
-    spatial emission anisotropies. 
+    spatial emission anisotropy. 
     \label{fig:muhisto}} 
@@
 \begin{center}
-\includegraphics[scale=0.35]{f10.eps}
+\includegraphics[width=0.90\textwidth]{f10.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[scale=0.35]{f11.eps}
+\includegraphics[width=0.90\textwidth]{f11.eps}
 \end{center}
@@
 
-An estimator for the anysotropy is represented by
+An estimator for the anisotropy is represented by
 %
@@
 spherical regions we define to test for this effect. Each has a radius
-of $0.5R$, where $R$ is the radius of the gaseus sphere. With an
+of $0.5R$, where $R$ is the radius of the gaseous sphere. With an
 observer located along the $\hat{j}$ direction, we pick two possible
@@
 In this case the $\mu$ distribution is not homogeneous as shown in
-Figure \ref{fig:muhisto}. The off-center emision shows a variation of flux at
+Figure \ref{fig:muhisto}. The off-center emission shows a variation of flux at
 the levels of $10\% - 28\%$ in intensity with the angle $\Theta$. In general 
@@
 We also explore the effects of off-centered emission in the line
-morphology. Figure \ref{fig:OC_profiles} show sthe spectra for the two
+morphology. Figure \ref{fig:OC_profiles} show the spectra for the two
 off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
@@
 
-The off-centered cases with hints of triple peaked emision motivate us
+The off-centered cases with hints of triple peaked emission motivate us
 to explore this in more detail. The first condition is to increase the
@@
 feature. Namely, if the rotational velocity is close to half the HFWM
-of the line, the triple peaks are more likely to occurr. This is the
+of the line, the triple peaks are more likely to occur. This is the
 same threshold that in the case of centered emission marks the
@@
 The presence of single peaked profiles has been associated to
-inflow/outflow dynamics \citep{XXX}. In this paper we show that gas
-bulk rotation can also be considered as a probable origin for that
-behavior, provided that the observed single peak is highly
+inflow/outflow dynamics \citep{Verhamme06,DijkstraKramer}. In this
+paper we show that gas bulk rotation can also be considered as a
+probable origin for that behavior, provided that the observed single peak is highly
 symmetric. Similarly, in the case of double peaked lines with a high
@@
     0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
-  width for the static case. $\lambda$ is a constat determined from
+  width for the static case. $\lambda$ is a constant determined from
   the radiative transfer results it is $\lambda_{\rm c}=3.9\pm$ and
@@
 \item A single peaked line emerges for high rotational velocities in
-  the case of homgeneously distributed sources. These cases occur when
-  the rotational velocity is larger than hFWHM$_0$.
+  the case of homogeneously distributed sources. These cases occur when
+  the rotational velocity is larger than FWHM$_0$.
 
@@
 bulk rotation is not enough to affect \ly photons. In consequence, 
-the escape fraction neither the position of the peaks depende on the
+the escape fraction neither the position of the peaks depends on the
 rotational velocity. However, there is a flux increase with rotational
@@
 that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings. The avarage number of
+escape with less than $10$ scatterings. The average number of
 scatterings decreases a $40\%$ compared to the static case. 
@@
 
-\item The spatial anisotropies in the emission are always at a level
-  below the $10\%$ deviation from static models.
+\item The spatial anisotropy in the emission is always below the
+  $10\%$ level deviation from static models.
 
 \item For off-centered emission triple peaked profiles can emerge
-  under two conditions: the emission occurs close to th sphere's
+  under two conditions: the emission occurs close to the sphere's
   surface and the rotational velocity is half the FWHM in the static
@@
 morphological features such as high central line flux, single peak
-profiles and multi-peaked profiles could be explained by gas bulk 
+profiles and multiple-peaked profiles could be explained by gas bulk 
 rotation present in these LAEs.
 
-\section*{Acknowledgements}
+\section*{Acknowledgments}
 

### 2014-02-14 paper/ms.tex
lambda errors

@@
 simultaneously all the points corresponding to central and homogeneous
-models to find $\lambda_{\rm c} = 3.9 \pm 3.17\times 10^{-17}$ and $\lambda_{\rm h}=
-1.9\pm 3.07\times 10^{-10}$ respectively.  {\bf EL ERROR ES de $10^{-17}???$}
+models to find $\lambda_{\rm c} = 3.9 \pm 0.041$ and $\lambda_{\rm h}=
+1.9\pm 0.062$ respectively.
 
@@
   $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
-  line) and for different rotational velocities.  
+  line) and for different rotational velocities. And $\theta$ represents the angle 
+  between the rotation axes $\hat{k}$ and the observer line of sight.
    \label{fig:3p_profiles}} 
@@
 
-We also explore the effects of off-centered emission in the line
+We also explore the effects of the off-centered emission in the line
 morphology. Figure \ref{fig:OC_profiles} show the spectra for the two

### 2014-02-14 paper/ms.tex
soem typos corrected

@@
 
-Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
+Left panel of Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
 fraction as a function of the rotational velocity. The curves for the
@@
 increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
-that is explained since there is a transition from a opaque to an extremely opaque medium
-which affect affects how \ly photons escape from the medium: single flight 
+that is explained since there is a transition from an opaque to an extremely opaque medium
+which affects how the \ly photons escape from the medium: single flight 
 vs. single excursion. {\bf Que quiere decir eso de single flight y
@@
 and optical depth must balance each other in order to show this feature
-feature. Namely, if the rotational velocity is close to half the HFWM
+feature. Namely, if the rotational velocity is close to half the FWHM
 of the line, the triple peaks are more likely to occur. This is the

### 2014-02-15 paper/ms.tex
paper update! almost the final version

@@
 with rotational velocity both for the central an homogeneous source
-distributions.  We parameterize the dependency of the line width as
+distributions.  We parametrize the dependency of the line width as
 \begin{equation}
@@
     fraction as a    function of the product $(a\tau_{\rm
-      H})^{1/3}\tau_{a}$. The    analytic solution for the infinite
-    slab is shown as a continuous    line. Different lines correspond
-    to different rotational    velocities.     \label{fig:efvsv}} 
+      H})^{1/3}\tau_{A}$, where $\tau_{A}$ is taking into account the albedo. The    analytic solution for the infinite
+    slab is shown as a continuous    line. Different lines corresponds
+    to different rotational velocities for the homogeneous models.     \label{fig:efvsv}} 
 \end{figure*}
-
-%\begin{figure}
-%  \caption{
-
-%    {\bf IS THE ALBEDO TAKEN INTO ACCOUNT?}
-%    \label{fig:efvsNeufeld}}   
-%\end{figure}
 
@@
 Neufeld's set-up the analytic solution depends uniquely on the product
-$(a\tau_{\rm   H})^{1/3}\tau_{a}$, an approximation that is valid only
+$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ and $A$ is the albedo
+, an approximation that is valid only
 in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
 \ref{fig:efvsv} show the results for the different rotational
-velocities. First of all we note that the escape fraction does not
-increase from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
+velocities for the homogeneous models. First of all we note that the escape fraction does not
+increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
 that is explained since there is a transition from an opaque to an extremely opaque medium
-which affects how the \ly photons escape from the medium: single flight 
-vs. single excursion. {\bf Que quiere decir eso de single flight y
-  single excursion, porque explica eso la fraccion de escape?}
+which affects how the \ly photons escape from the medium.
 
@@
 However, we find some cases where there is a possible signature of
-three peaks. This is only present in some models ($\tau = 10^6,
-V=100$\kms and $\tau = 10^7, V=300$\kms) and could be the result of
+three peaks. This is only present in some models ($\tau_{\rm H} = 10^6,
+V=100$\kms and $\tau_{\rm H} = 10^7, V=300$\kms) and could be the result of
 two competing effects: the rise in the line's center as the photons in

### 2014-02-16 paper/ms.tex
Final Version for Mark

@@
 
-A basic understanding of the quantitative behavior of the \ly line
+A basic understanding of the quantitative behaviour of the \ly line
 has been reached through analytic studies in the case of a static
@@
 The panel focus on the results for all of our symmetric models
- $\tau_{H}=(10^{6}, 10^{6}, 10^{5}$), showing that the
+ $\tau_{H}=(10^{5}, 10^{6}, 10^{7}$), showing that the
 influence of rotation is present both when the photons are either
@@
 \kms. By inspection we find that in all cases the transition has
-occurred when the rotational velocity is larger than half width .
+occurred when the rotational velocity is larger than half width.
 
@@
     fraction as a    function of the product $(a\tau_{\rm
-      H})^{1/3}\tau_{A}$, where $\tau_{A}$ is taking into account the albedo. The    analytic solution for the infinite
+      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
     slab is shown as a continuous    line. Different lines corresponds
@@
 Neufeld's set-up the analytic solution depends uniquely on the product
-$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ and $A$ is the albedo
-, an approximation that is valid only
-in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in the right panel of Figure
-\ref{fig:efvsv} show the results for the different rotational
+$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ , an approximation 
+that is valid only in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in
+ the right panel of Figure \ref{fig:efvsv} show the results for the different rotational
 velocities for the homogeneous models. First of all we note that the escape fraction does not
@@
 paper we show that gas bulk rotation can also be considered as a
-probable origin for that behavior, provided that the observed single peak is highly
+probable origin for that behaviour, provided that the observed single peak is highly
 symmetric. Similarly, in the case of double peaked lines with a high
@@
   width for the static case. $\lambda$ is a constant determined from
-  the radiative transfer results it is $\lambda_{\rm c}=3.9\pm$ and
-  $\lambda_{\rm h}=1.9\pm$ for the central and homogeneous source
+  the radiative transfer results it is $\lambda_{\rm c}=3.9\pm0.041$ and
+  $\lambda_{\rm h}=1.9\pm0.062$ for the central and homogeneous source
   distribution, respectively.

### 2014-02-19 paper/ms.tex
Marks New comments

@@
 velocities in the range $0-300$ \kms and neutral hydrogen optical
-depths in the range $\tau_{\rm H}=10^{5}-10^{7}$. We also consider two
-kinds of spatial distribution for the radiation sources with respect
-to the sphere: central and homogeneous. Our main finding is that the
-line width and the intensity at the line's center increase with
-rotational velocity. For homogeneously distributed sources the line
-becomes single peaked at rotational velocities larger than the line
-width in the static case. Under the same
-conditions the escape fraction increases $\sim 30\%$. For radiation
-sources located off-center, the line morphology presents a range of
-single, double and triple peaks. We show how these results are useful
-to interpret recent spectroscopic results of distant $z\sim 2-3$ star
-forming galaxies.
+depths in the range $\tau_{\rm H}=10^{5}-10^{7}$. We consider cases 
+of a single central \lya source, and a uniform distribution of sources. 
+Our main finding are that the escape fraction of \lya photons, and
+the intensity at the line center increase with rotational velocity. 
+For homogeneously distributed sources the line becomes single peaked 
+at rotational velocities larger than the line width in the static case.
+For radiation sources located off-center, the line morphology presents 
+a range of single, double and triple peaks. We show how these results 
+are useful to interpret recent spectroscopic results of distant 
+$z\sim 2-3$ star forming galaxies.
 
@@
 galaxies
-\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}.
+\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012,Finkelstein2013}.
 The galaxies detected using this method receive the 
@@
 configurations, such as uniform slabs
-\citep{Harrington73,Neufeld90} and uniform spheres
+\citep{Adams72,Harrington73,Neufeld90} and uniform spheres
 \citep{Dijkstra06}. Analytic studies of configurations including
@@
 \citep{Hansen06} and expanding/contracting shell/spherical geometries started to
-be studied \citep{Verhamme06,Dijkstra06}. Similar codes have applied
+be studied \citep{Verhamme06,Dijkstra06,Ahn2014}. Similar codes have applied
 these results to semi-analytic models of galaxy formation \citep{Orsi12} and
@@
 our work on two independent Monte Carlo based radiative transfer codes
-CLARA \citep{CLARA} and XX \citep{DijkstraKramer} .
+CLARA \citep{CLARA} and \citep{DijkstraKramer}.
 
@@
 respect to the $z$ axis. Following \cite{Zheng2013} we make the study
-of the anisotropic emission in terms of this angle..
+of the anisotropic emission in terms of this angle.
 
@@
 \caption{
-  List of the physical parameters that define the spherical models 
-  simulated in our Monte Carlo calculations. For each parameter we
-  vary the values in the range listed in the last column. Taking into
-  account all the possible combinations we end up with $60$ different
-  models.} 
+  Summary of Physical Parameters of our Monte Carlo Simulations.} 
 \label{table:models}
@@
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
-values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively
+values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively and
+$V_{\mathrm{max}}=300$ \kms.
 
-From Figure \ref{fig:Nscatt} is also clear that for the homogeneous
-distribution there is a clear decrease of $\langle N_{\rm
+From Figure \ref{fig:Nscatt} for the homogeneous
+distribution there is a decrease of $\langle N_{\rm
   scatt}\rangle$ as the $V_{\rm max}$ increases. For instance, for
@@
 
-In this case we find that for a static sphere $\langle N_{\rm
+For the homogeneous static sphere we find that $\langle N_{\rm
   scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
 represents factors of $(0.66, 0.59, 0.55)$ lower than the centrally
-emitted photons. In contrast the analytic solution for the homogeneous
+emitted photons. While for the homogeneous rotating sphere at 
+$V_{\rm{max}}=300\kms$ we find that $\langle N_{\rm
+  scatt}\rangle=(0.38, 0.34, 0.42)\tau_{\rm   H}$ which represents 
+  factors of $(0.26, 0.34, 0.46)$ lower than the corresponding central
+  case.  In contrast the analytic solution for the homogeneous
 slab gives	 $0.72$ times less scatterings in the homogeneous case than
-in the central one.
+in the central one
 
@@
 velocities for the homogeneous models. First of all we note that the escape fraction does not
-increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, a fact
-that is explained since there is a transition from an opaque to an extremely opaque medium
-which affects how the \ly photons escape from the medium.
+increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, This
+ counter-intuitive result is a consequence of the transition into the 'extremely' opaque regime,
+  which occurs roughly when $a\tau_{\rm{H}} > 10^{3}$ e.g. \citep{Neufeld90}.
 
@@
 rotation. However, some galaxies in those groups have a high flux between
-the two peaks; an effect that can be induced by rotation. The same
-argument applies to galaxies in the group IV in which the flux
+the two peaks; this could indicate the presence of rotation 
+and \lya photons leaking though low column density holes, as in \citep{Behrens2014}.
+ The same argument applies to galaxies in the group IV in which the flux
 in between of the two peaks is high ($ \geq 70 \%$ of the intensity in

### 2014-02-19 paper/ms.tex
My final version before submitted finally !!

@@
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
-\altaffiltext{2}{Max Planck Institute for Astrophysics, Karl-Schwarzschild-Str. 1, 85741, Garching, Germany}
+\altaffiltext{2}{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}
 
@@
 
-A basic understanding of the quantitative behaviour of the \ly line
+A basic understanding of the quantitative behavior of the \ly line
 has been reached through analytic studies in the case of a static
@@
     \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
-      show the homogeneous (central) source distribution. Left
-      corresponds to the static case and right
+      show the homogeneous (central) source distribution. Left panels 
+      corresponds to the static case and right panels corresponds to
       $V_{\rm max}=300\kms$. The color scale is logarithmic on the
@@
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
-values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$, respectively and
+values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively and
 $V_{\mathrm{max}}=300$ \kms.
@@
   $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
-  line) and for different rotational velocities. And $\theta$ represents the angle 
-  between the rotation axes $\hat{k}$ and the observer line of sight.
+  line) and for different rotational velocities. And $\theta$ represents the usual
+  polar angle.
    \label{fig:3p_profiles}} 
@@
 Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
-distribution for an sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
+distribution for a sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
   max}=200$\kms. The dashed and dotted lines represent the homogeneous
 and central source distribution, respectively. This shows that the
-the  anisotropy induced by rotation is at the $3\%$ level. We
+ anisotropy induced by rotation is at the $3\%$ level. We
 performed the same test with all the models and find that the
@@
 
-Furthermore, taking into account all the models that do not event present hints for
+Furthermore, taking into account all the models that do not present hints for
 a triple peaked emission it would seem that the rotational velocity
-and optical depth must balance each other in order to show this feature
-feature. Namely, if the rotational velocity is close to half the FWHM
+and optical depth must balance each other in order to show this feature.
+ Namely, if the rotational velocity is close to half the FWHM
 of the line, the triple peaks are more likely to occur. This is the
@@
 rotation effects, while the asymmetric cases naturally arise in
-outflow/inflow models \citep{Verhamme2008, Dijkstra06}. Among the 91
+outflow/inflow models \citep{Ahn2014,Verhamme2008, Dijkstra06}. Among the 91
 LAEs, 8 reveal triple peaked profiles with a central peak and two
@@
 paper we show that gas bulk rotation can also be considered as a
-probable origin for that behaviour, provided that the observed single peak is highly
+probable origin for that behavior, provided that the observed single peak is highly
 symmetric. Similarly, in the case of double peaked lines with a high
@@
 scatterings decreases a $40\%$ compared to the static case. 
-The reduction in the number of scattering decreases the probability
+The reduction in the number of scatterings decreases the probability
 for a photon to move away from the line's center. This is also
@@
 
+The data and source code and instructions to
+replicate the results of this paper can be found
+here {\texttt{https://github.com/jngaravitoc/RotationLyAlpha}}.
+Thanks to the IPython community \citep{IPython} and to the matplotlib
+community \citep{matplotlib}.
+
 \bibliographystyle{apj}

### 2014-02-20 paper/ms.tex
authors, emails, keywords

@@
 
-\title{The impact of gas bulk rotation on the Lyman-$\alpha$ line} 
-\author{
-  Juan N. Garavito-Camargo\altaffilmark{1},
-  Jaime E. Forero-Romero\altaffilmark{1},
-  Mark Dijkstra\altaffilmark{2}
-}
+\title{The impact of gas bulk rotation on the Lyman $\alpha$ line} 
+\shorttitle{Rotation effects on the Lyman $\alpha$ line}
+\shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}
+\author{ Juan N. Garavito-Camargo and Jaime E. Forero-Romero}
+\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
+No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
+\email{jn.garavito57@uniandes.edu.co}
+\email{je.forero@uniandes.edu.co}
+\author{Mark Dijkstra}
+\affil{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}
+\email{mark.dijkstra@astro.uio.no }
 
-\altaffiltext{1}{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
-No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
-\altaffiltext{2}{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}
-
+\keywords{galaxies: high-redshift --- line: formation --- methods: numerical ---  radiative transfer}
 \begin{abstract}
@@
 \end{abstract}
-
-\begin{keywords}
-{galaxies: high-redshift, galaxies: star formation, line: formation}
-\end{keywords}
 
@@
 scale is logarithmic in the number of photons at a certain value
-$x$-$N_{\rm scatt}$.
+$xN_{\rm scatt}$.
 

### 2014-02-20 paper/ms.tex
mi version

@@
 \newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
-\newcommand{\lya}{{Lyman$\alpha$~}}
+\newcommand{\lya}{{Lyman $\alpha$~}}
 \newcommand{\clara}{{\texttt{CLARA}}~}
@@
 Our main finding are that the escape fraction of \lya photons, and
-the intensity at the line center increase with rotational velocity. 
+the intensity at the line center increases with rotational velocity. 
 For homogeneously distributed sources the line becomes single peaked 
-at rotational velocities larger than the line width in the static case.
+at rotational velocities larger than half the line width in the static case.
 For radiation sources located off-center, the line morphology presents 
@@
 our work on two independent Monte Carlo based radiative transfer codes
-CLARA \citep{CLARA} and \citep{DijkstraKramer}.
+presented in \cite{CLARA} and \cite{DijkstraKramer}.
 
@@
 and list the different physical parameters in the simulated grid of
-models. In the next \S \ref{sec:results} we present the results of the
-simulations, with special detail to quantities in the line that show a
+models. In \S \ref{sec:results} we present the results of the
+simulations, with special detail to quantities that show a
 clear evolution as a function of the sphere rotational velocity. In \S
 \ref{sec:discussion} we discuss the implications of our results in the
-interpretation of LAEs observations. In the last section we present
-our conclusions.
+interpretation of LAEs observations with high resolution
+spectroscoy. In the last section we present our conclusions.
 
@@
 a thorough observational account of rotation in galaxies beyond
-$z>1.0$. Event at low red-shifts there is a great
+$z>1.0$. Even at low redshifts there is a great
 variation in the shape of the rotation curve as observed in HI
@@
 following a solid rotation behavior. Second, beyond a certain radius
-the rotation curve tends to flatten.
-
-An ab-initio description of realistic rotation curves in simulations
-depends on having access to the dynamic evolution of all mass components
-in the galaxy: stars, gas and dark matter. Such level of realism is
-extremely complex to achieve, specially if one wants to get a
-systematic description based on statistics of simulated objects.
+the rotation curve tends to flatten.  An ab-initio description of
+such realistic rotation curves in simulations depends on having access to
+the dynamic evolution of all mass components in the galaxy: stars, gas
+and dark matter. Such level of realism is extremely complex to
+achieve, specially if one wants to get a systematic description based
+on statistics of simulated objects.
 
@@
 of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
-define the angle $\Theta$ by $\cos\Theta = \hat{k}\cdot
-\hat{k}_{out}$, that is the polar angle of the outgoing photon with
-respect to the $z$ axis. Following \cite{Zheng2013} we make the study
-of the anisotropic emission in terms of this angle.
+define the angle $\Theta$ by $\cos\Theta = \hat{k}_{\rm obs}\cdot
+\hat{k}_{\rm out}$, that is the angle of the outgoing photon with
+respect to the directions towards the observer. Following
+\cite{Zheng2013} we make the study of the anisotropic emission in
+terms of this angle.
 
@@
 
-The codes follow the individual scatterings of \ly photons as it
-travels through a 3D distribution of neutral Hydrogen. At each
+The codes follow the individual scatterings of \ly photons as they
+travel through a 3D distribution of neutral Hydrogen. At each
 scattering the frequency of the photon (in the laboratory frame) and
@@
 temperature $T$, Hydrogen optical depth $\tau_{\rm H}$, dust optical
-depth $\tau_{\rm a}$ and the bulk velocity field $\vec{v}$. Here we
+depth $\tau_{\rm a}$ and the bulk velocity field $\vec{v}$. Our codes
 treat the gas as homogeneous in density ($\tau_{\rm H}$, $\tau_{\rm
@@
 \caption{Shape of the \ly line for
-    different velocities rotational velocities for spherical
-    distributions in all the models. The continuous (dashed) line represents the 
-    central (homogeneous) source distributions.
+    different maximum rotational velocities. The continuous (dashed)
+    line represents the central (homogeneous) source distributions. 
     \label{fig:differentvelocities}}  
@@
 variations of the input parameters. Table \ref{table:models}
-summarizes the models.
+summarizes the different parameters.
 
@@
 The central result of this paper is summarized in Figure
-\ref{fig:differentvelocities}. It shows the evident
+\ref{fig:differentvelocities}. It shows the clear
 impact of rotation on the morphology of the emergent \ly line.
@@
 escape fraction as a function of rotational velocity. Finally, we make
-an estimate of the anisotropic emission of the models in comparison
-with static spheres.
+an estimate of the impact of anisotropic emission.
 
@@
 broadens; second, the double peaks reduce their intensity; and third,
-the intensity at the line center rises. The two last effects give the
+the intensity at the line center rises. The last two effects merge to give the
 impression that the double peaks are merger into one at high rotational
@@
 with rotational velocity both for the central an homogeneous source
-distributions.  We parametrize the dependency of the line width as
+distributions.  We parametrize the dependency of the line width with
+$V_{\rm max}$ as
 \begin{equation}
@@
 simultaneously all the points corresponding to central and homogeneous
-models to find $\lambda_{\rm c} = 3.9 \pm 0.041$ and $\lambda_{\rm h}=
-1.9\pm 0.062$ respectively.
+models to find $\lambda_{\rm c} = 3.89 \pm 0.04$ and $\lambda_{\rm h}=
+1.98\pm 0.06$ respectively.
 
@@
 \ref{fig:maximumsvsvelocity} where it is clear that for central
-sources there are always two peaks with fixed positions as the rotational
-velocity changes. However, in the case of homogeneously emitted
-sources the maxima position remain close to constant until some
-velocity threshold the line becomes single peaked with $x_{\rm m}=0$
-\kms. By inspection we find that in all cases the transition has
-occurred when the rotational velocity is larger than half width.
+sources there are two peaks with fixed positions as the rotational
+velocity changes, with the only exception of the model with $\tau_{\rm
+  H}=10^6$ and $V_{\rm max}=300$\kms. However, in the case of
+homogeneously emitted sources the maxima position remain fixed until
+some velocity threshold is reachd and the line becomes single peaked
+with $x_{\rm m}=0$. By inspection we find that in all cases the
+transition has occurred when the rotational velocity is larger than
+half the FWHM.
 
 One possible explanation for the emergence of the single peak in the
-homogeneous source systems is that some photons close to the surface
+homogeneous systems is that some photons close to the surface
 (a sort of photosphere) can escape with a low number of scatterings,
@@
 However, for the central emission the transition to a single peak is
-never completed in the range of explored parameters. The absence
+almost never completed in the range of explored parameters. The absence
 of a single peak phase could be partially explained by the absence of a
-photosphere, in this case the average number of scatterings to escape
+photosphere. In this case the average number of scatterings to escape
 should remain close to constant as the rotational velocity
@@
       show the homogeneous (central) source distribution. Left panels 
-      corresponds to the static case and right panels corresponds to
+      corresponds to the static case and right panels correspond to
       $V_{\rm max}=300\kms$. The color scale is logarithmic on the
@@
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
-values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively and
-$V_{\mathrm{max}}=300$ \kms.
+values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
 
-From Figure \ref{fig:Nscatt} for the homogeneous
-distribution there is a decrease of $\langle N_{\rm
-  scatt}\rangle$ as the $V_{\rm max}$ increases. For instance, for
+In Figure \ref{fig:Nscatt} we can see the decrease of $\langle N_{\rm
+  scatt}\rangle$ as $V_{\rm max}$ increases in the homogeneous
+source distribution. For instance, for
 $\tau_{\rm H}=10^5$ the average number of scatterings decreases by
@@
   factors of $(0.26, 0.34, 0.46)$ lower than the corresponding central
-  case.  In contrast the analytic solution for the homogeneous
-slab gives	 $0.72$ times less scatterings in the homogeneous case than
-in the central one
+  case.
 
@@
 scale is logarithmic in the number of photons at a certain value
-$xN_{\rm scatt}$.
+$x-N_{\rm scatt}$.
 
@@
   \caption{Effects of rotation on the escape fraction. Left
-    panel. Escape fraction as a function of rotational velocity. All
+    panel, escape fraction as a function of rotational velocity. All
     these models have $\tau_{a}=1$. The continuous (dashed) lines
-    correspond to central (homogeneous) models. Right panel. Escape
+    correspond to central (homogeneous) models. Right panel, escape
     fraction as a    function of the product $(a\tau_{\rm
       H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
-    slab is shown as a continuous    line. Different lines corresponds
-    to different rotational velocities for the homogeneous models.     \label{fig:efvsv}} 
+    slab is shown as a continuous    line. Different lines correspond
+    to different rotational velocities for the homogeneous models.     
+    \label{fig:efvsv}} 
 \end{figure*}
@@
   $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
-  line) and for different rotational velocities. And $\theta$ represents the usual
-  polar angle.
+  line) and for different rotational velocities. $\theta$ represents
+  the position of the observer as mesured with the polar angle.
    \label{fig:3p_profiles}} 
@@
 observer located along the $\hat{j}$ direction, we pick two possible
-positions to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
-this configuration the emitting sphere centered on $+C\hat{k}$ moves
-away from the observer and the sphere centered on $-C\hat{j}$ moves
-towards the observer.
+positions to center the spheres along the $\hat{i}$ axis: $\pm C\hat{i}$. In
+this configuration the emitting sphere centered on $+C\hat{i}$ moves
+towards the observer and the sphere centered on $-C\hat{j}$ moves
+away from the observer.
 
-In this case the $\mu$ distribution is not homogeneous as shown in
+In this case the $\mu$ distribution is not homogeneous as it is shown in
 Figure \ref{fig:muhisto}. The off-center emission shows a variation of flux at
@@
 models with a larger $\tau_{H}$ present a higher variation in the flux.
-This variation implies that that the line is more intense in
-the plane perpendicular to the rotation axis.
 
@@
 observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
-asymmetry in the line morphology.
+asymmetry in the line morphology within the range of explored velocities.
 
 However, we find some cases where there is a possible signature of
-three peaks. This is only present in some models ($\tau_{\rm H} = 10^6,
-V=100$\kms and $\tau_{\rm H} = 10^7, V=300$\kms) and could be the result of
-two competing effects: the rise in the line's center as the photons in
-the photosphere escape in a single excursion and the broadening in the
-two peaks as the photons closer from the center have to scatter to
-escape. We examine in greater detail these cases in the next
-sub-section.
+triple peaked emission. This is only present in some models
+($\tau_{\rm H} = 10^6, V=100$\kms and $\tau_{\rm H} = 10^7,
+V=300$\kms) and could be the result of two competing effects: the rise
+in the line's center as the photons in the photosphere escape in a
+single excursion and the broadening in the two peaks as the photons
+closer from the center have to scatter to escape. We examine in
+greater detail these cases in the next sub-section.
 
@@
 the two peaks; this could indicate the presence of rotation 
-and \lya photons leaking though low column density holes, as in \citep{Behrens2014}.
- The same argument applies to galaxies in the group IV in which the flux
+and \ly photons leaking though low column density holes, as in \cite{Behrens2014}. The same argument applies to galaxies in the group IV in which the flux
 in between of the two peaks is high ($ \geq 70 \%$ of the intensity in
 the highest peak). Finally, the triple peaked lines in Galaxies in
-Group V can be easily reproduced by rotation with off-centered
+Group V can be reproduced by rotation with off-centered
 emission given the right amount of asymmetry between the emitting
@@
 peaked lines as the rotational velocity increases. In the case of
-off-centered emission result into triple peaked lines for certain
+off-centered emission we obtain triple peaked lines for certain
 values of optical depth and rotational velocities.
@@
 
-\item The line width increases with rotational velocity. The line with
-  approximately following the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
+\item The line width increases with rotational velocity. The line width
+  approximately follows the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
     0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
-  width for the static case. $\lambda$ is a constant determined from
-  the radiative transfer results it is $\lambda_{\rm c}=3.9\pm0.041$ and
-  $\lambda_{\rm h}=1.9\pm0.062$ for the central and homogeneous source
+  width for the static case and $\lambda$ is a constant determined from
+  the radiative transfer results it is $\lambda_{\rm c}=3.89\pm0.04$ and
+  $\lambda_{\rm h}=1.98\pm0.06$ for the central and homogeneous source
   distribution, respectively.
@@
   the case of homogeneously distributed sources. These cases occur when
-  the rotational velocity is larger than FWHM$_0$.
+  the rotational velocity is larger than half FWHM$_0$.
 
@@
 scatterings decreases a $40\%$ compared to the static case. 
-The reduction in the number of scatterings decreases the probability
+This reduction in the number of scatterings decreases the probability
 for a photon to move away from the line's center. This is also
@@
 
-\item The spatial anisotropy in the emission is always below the
-  $10\%$ level deviation from static models.
+\item The spatial anisotropy induced by rotation in the emission is
+  usually below the $10\%$ level.
 
 \item For off-centered emission triple peaked profiles can emerge
-  under two conditions: the emission occurs close to the sphere's
-  surface and the rotational velocity is half the FWHM in the static
-  case.   
+  under two joint conditions: the emission occurs close to the sphere's
+  surface and the rotational velocity is close to half the FWHM in the
+  static case.   
 \end{itemize}
@@
 profiles and multiple-peaked profiles could be explained by gas bulk 
-rotation present in these LAEs.
+rotation present in these LAEs. We defer the study of triple peaked
+emission in the context of gas bulk rotation to a future publication
+(Remolina-Gutierrez et al., in preparation).
 
@@
 
-The data and source code and instructions to
+The data, source code and instructions to
 replicate the results of this paper can be found
 here {\texttt{https://github.com/jngaravitoc/RotationLyAlpha}}.
-Thanks to the IPython community \citep{IPython} and to the matplotlib
-community \citep{matplotlib}.
+Most of our code benefits from the work of the IPython and Matplotlib
+communities \citep{IPython,matplotlib}.
 

### 2014-04-12 paper/ms.tex
\and
referee response, Done: introduction and Fig1

@@
 \shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}
-\author{ Juan N. Garavito-Camargo and Jaime E. Forero-Romero}
+\author{ Juan N. Garavito-Camargo, Jaime E. Forero-Romero}
 \affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
@@
 \email{je.forero@uniandes.edu.co}
+\and
 \author{Mark Dijkstra}
@@
 be studied \citep{Verhamme06,Dijkstra06,Ahn2014}. Similar codes have applied
-these results to semi-analytic models of galaxy formation \citep{Orsi12} and
+these results to semi-analytic models of galaxy formation \citep{Orsi12, GAREL2012} and
 results of large hydrodynamic simulations
@@
  in simplified configurations that vary the density and wind
- characteristics \citep{Zheng2013}.
+ characteristics \citep{Zheng2013,BEHRENS2014}.
 
@@
     line represents the central (homogeneous) source distributions. 
+    This profiles were obtained integrating the flux of photons 
+	over all directions, this means we made histograms of the 
+	numbers of photons escaping the galaxy with a given frequency.
     \label{fig:differentvelocities}}  
@@
 \ref{fig:differentvelocities}. It shows the clear
-impact of rotation on the morphology of the emergent \ly line.
+impact of rotation on the morphology of the emergent \ly line,
+This profiles were obtained integrating the flux of photons 
+ over all directions, this means we made histograms of the 
+ numbers of photons escaping the galaxy with a given frequency
 The panel focus on the results for all of our symmetric models

### 2014-04-15 paper/ms.tex
advances

@@
 \shorttitle{Rotation effects on the Lyman $\alpha$ line}
+
 \shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}
+
 \author{ Juan N. Garavito-Camargo, Jaime E. Forero-Romero}
@@
 For homogeneously distributed sources the line becomes single peaked 
-at rotational velocities larger than half the line width in the static case.
-For radiation sources located off-center, the line morphology presents 
-a range of single, double and triple peaks. We show how these results 
-are useful to interpret recent spectroscopic results of distant 
+at rotational velocities larger than half the line width in the static
+case. We also find that this anisotripic velocity configuration does
+not induce any significant anisotropy in the spectral properties.
+For radiation sources located off-center, the line morphology
+presents  a range of single, double and triple peaks. We show how
+these results  are useful to interpret recent spectroscopic results of distant 
 $z\sim 2-3$ star forming galaxies.
@@
 be studied \citep{Verhamme06,Dijkstra06,Ahn2014}. Similar codes have applied
-these results to semi-analytic models of galaxy formation \citep{Orsi12, GAREL2012} and
+these results to semi-analytic models of galaxy formation \citep{Orsi12, Garel2012} and
 results of large hydrodynamic simulations
@@
  in simplified configurations that vary the density and wind
- characteristics \citep{Zheng2013,BEHRENS2014}.
+ characteristics \citep{Zheng2013,Behrens2014}.
 
@@
     line represents the central (homogeneous) source distributions. 
-    This profiles were obtained integrating the flux of photons 
+    These profiles were obtained integrating the flux of photons 
 	over all directions, this means we made histograms of the 
@@
 those galaxies \citep{Kulas12}, we find that only the case of triple
-peaked emission for the most massive object $\tau_{\rm H}, 10^{7}$,
-$V_{\rm max}=200\kms$ would have a chance to be spectrally resolved.
+peaked emission for the most massive object $\tau_{\rm H}=10^{7}$,
+$V_{\rm max}=200\kms$ would have a chance to be spectrally
+resolved. We note that observations of triple peaked systems with
+higher resolution spectrographs have been reported  by
+\cite{Chonis2013}, however the large velocity off-sets ($\sim
+1000$\kms) from the systemic redshift favor the hypothesis of an
+interacting system, including emission from shocked and fluorecing
+gas, as the origin of the triple peaked emission.
 
@@
 
+\item In spite of the asymmetry induced by rotation the spatial
+  anisotropy in the emission is usually below the
+  $10\%$ level. This justifies our consideration of angle-averaged
+  effects to quantify the emission line of rotating clouds.
+
 \item The line width increases with rotational velocity. The line width
@@
 $\sim 2$ with respect to the static situation.
-
-\item The spatial anisotropy induced by rotation in the emission is
-  usually below the $10\%$ level.
 

### 2014-04-17 paper/referee-reply.tex
Fig2. comments about the FWHM

\documentclass[12pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[spanish]{babel}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Response to the referee}

\begin{document}

\date{}
\maketitle

\section*{Outflow + Rotation}

We want to study the pure effect of rotation on the spectra, off course it would
be interesting to study the effect of rotation on systems with outflows, this paper
is under preparation by M.C Remolina-Gutierrez et al.

\section*{Details}

\subsection*{Introduction}

This changes were performed.

\subsection*{Fig.1}

\begin{itemize}
\item Description about how we build Fig.1 (Done)
\item Fig 1. remove x notation (Done)
\end{itemize}

\subsection*{Fig.2}

Explanation (Done)\\
We don't fit a gaussian , we measure the width by finding
the closest points to the half maximum in our histogram numerically.

\subsection*{Fig.3}

\subsection*{Fig4 and 6}

Waiting for the cluster in germany!

\subsection*{Fig5}

\end{document}

### 2014-04-17 code/photosphere_test.py
photosphere test

@@ -1,0 +1,51 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+
+data_in = np.loadtxt("../data/Homogeneous/V3005tHOM_in.ascii")
+data_out = np.loadtxt("../data/Homogeneous/V3005tHOM_out.ascii")
+
+
+nscatt = data_out[:,8]
+
+x = data_in[:,0]
+y = data_in[:,1]
+z = data_in[:,2]
+
+X = np.amax(x)
+Y = np.amax(y)
+Z = np.amax(z)
+
+R = (X + Y + Z) /3.0
+
+index_low = np.where(nscatt<100)
+x_low = x[index_low]
+y_low = y[index_low]
+z_low = z[index_low]
+
+
+index_high = np.where(nscatt>100)
+
+x_high = x[index_high]
+y_high = y[index_high]
+z_high = z[index_high]
+
+#print np.amax(x_high),np.amax(x_low)
+#print len(x_high), len(x_low)
+N =  float(len(nscatt))
+
+
+r_low = np.sqrt(x_low**2 + y_low**2 + z_low**2)
+r_high = np.sqrt(x_high**2 + y_high**2 + z_high**2)
+
+hist_l, bin_edges_l = np.histogram(r_low)
+hist_h, bin_edges_h = np.histogram(r_high)
+
+plt.plot(bin_edges_l[:-1]/R, hist_l[:]/N, c = 'r', linewidth=2.5, label='Nscatt<100')
+plt.plot(bin_edges_h[:-1]/R, hist_h[:]/N, c = 'g', linewidth=2.5, label=('Nscatt>100'))
+plt.legend(loc='best')
+plt.ylabel("Number of photons", fontsize=25)
+plt.xlabel("Radius", fontsize=25)
+plt.savefig("photosphere_test.png")
+plt.show()
+

### 2014-04-20 code/New_widths_and_Maxima.py
Widths and Maxima fiexed bugs

@@ -1,0 +1,125 @@
+import numpy as np
+import sys
+from scipy.interpolate import interp1d
+
+def reading_data(filename):
+    data = np.loadtxt("../data/Homogeneous/"+filename)
+    kz = data[:,5]
+    x = data[:,6]
+    return kz, x
+
+def viewing_angle(filename, angle, nbins):
+    kz, x = reading_data(filename)
+    index01 = np.where((abs(kz)<0.1))
+    index02 = np.where((abs(kz)<0.2) & (abs(kz)>0.1))
+    index03 = np.where((abs(kz)<0.3) & (abs(kz)>0.2))
+    index04 = np.where((abs(kz)<0.4) & (abs(kz)>0.3))
+    index05 = np.where((abs(kz)<0.5) & (abs(kz)>0.4))
+    index06 = np.where((abs(kz)<0.6) & (abs(kz)>0.5))
+    index07 = np.where((abs(kz)<0.7) & (abs(kz)>0.6))
+    index08 = np.where((abs(kz)<0.8) & (abs(kz)>0.7))
+    index09 = np.where((abs(kz)<0.9) & (abs(kz)>0.8))
+    index10 = np.where((abs(kz)<1.0) & (abs(kz)>0.9))
+    
+    x01 = x[index01]
+    x02 = x[index02]
+    x03 = x[index03]
+    x04 = x[index04]
+    x05 = x[index05]
+    x06 = x[index06]
+    x07 = x[index07]
+    x08 = x[index08]
+    x09 = x[index09]
+    x10 = x[index10]
+    
+    hist, bins = np.histogram(x, bins=nbins)
+    hist01, bins01 = np.histogram(x01, bins=nbins)
+    hist02, bins02 = np.histogram(x02, bins=nbins)
+    hist03, bins03 = np.histogram(x03, bins=nbins)
+    hist04, bins04 = np.histogram(x04, bins=nbins)
+    hist05, bins05 = np.histogram(x05, bins=nbins)
+    hist06, bins06 = np.histogram(x06, bins=nbins)
+    hist07, bins07 = np.histogram(x07, bins=nbins)
+    hist08, bins08 = np.histogram(x08, bins=nbins)
+    hist09, bins09 = np.histogram(x09, bins=nbins)
+    
+    if angle == 1:
+        return hist01, bins01
+    
+    if angle == 2:
+        return hist02, bins02
+    
+    if angle == 3:
+        return hist03, bins03
+    
[…]

### 2014-04-20 code/New_widths_and_Maxima.py
cleaning nans

@@ -4,8 +4,12 @@ from scipy.interpolate import interp1d
 
 def reading_data(filename):
     data = np.loadtxt("../data/Homogeneous/"+filename)
+    initpos=data[:,0]	    
+    index_clean = np.where(~np.isnan(initpos))
+    data = data[index_clean[0],:]
     kz = data[:,5]
     x = data[:,6]
+
     return kz, x
 
 def viewing_angle(filename, angle, nbins):

### 2014-04-20 code/New_widths_and_Maxima.py
Generalized function that finds the maxima for those spectra who have a central peak

@@ -101,20 +101,25 @@ def widths(filename, angle, bins): #there is a bug in this function
             print abs(x[i]*2.0)
 
 def maxima(filename, angle, bins):
-    hist, x = interpolate(filename, angle, bins) #implement the interpolation
-    index1 = np.where(x>0)
-    hist1 = hist[index1]
-    x1 = x[index1]
-    index11 = np.where(hist1 == np.amax(hist1))
-    maximo1 = np.amax(hist1)
-    x2 = x1[index11]
-    index2 = np.where(x<0)
-    hist2 = hist[index2]
-    x3 = x[index2]
-    index31 = np.where(hist2 == np.amax(hist2))
-    x4 = x3[index31]
-    maximo2 = np.amax(hist2)
-    print float(x2), float(x4)
+    hist, x = interpolate(filename, angle, bins) 
+    maxima = np.where(hist==np.amax(hist))
+    x_m = x[maxima]
+    if abs(x_m) < 0.2*np.amax(x):
+	print float(x_m)
+    else:
+    	index1 = np.where(x>0)
+    	hist1 = hist[index1]
+    	x1 = x[index1]
+    	index11 = np.where(hist1 == np.amax(hist1))
+    	maximo1 = np.amax(hist1)
+    	x2 = x1[index11]
+    	index2 = np.where(x<0)
+    	hist2 = hist[index2]
+    	x3 = x[index2]
+    	index31 = np.where(hist2 == np.amax(hist2))
+    	x4 = x3[index31]
+    	maximo2 = np.amax(hist2)
+    	print float(x2), float(x4)
 
 filename = sys.argv[1]
 angle = float(sys.argv[2])

### 2014-04-21 code/New_widths_and_Maxima.py
generalized to central sources

@@ -2,8 +2,11 @@ import numpy as np
 import sys
 from scipy.interpolate import interp1d
 
-def reading_data(filename):
-    data = np.loadtxt("../data/Homogeneous/"+filename)
+def reading_data(filename, distribution):
+    if distribution == 0:
+	data = np.loadtxt("../data/Homogeneous/"+filename)
+    elif distribution ==1:
+        data = np.loadtxt("../data/Central/"+filename)
     initpos=data[:,0]	    
     index_clean = np.where(~np.isnan(initpos))
     data = data[index_clean[0],:]
@@ -12,8 +15,8 @@ def reading_data(filename):
 
     return kz, x
 
-def viewing_angle(filename, angle, nbins):
-    kz, x = reading_data(filename)
+def viewing_angle(filename, angle, nbins, distribution):
+    kz, x = reading_data(filename, distribution)
     index01 = np.where((abs(kz)<0.1))
     index02 = np.where((abs(kz)<0.2) & (abs(kz)>0.1))
     index03 = np.where((abs(kz)<0.3) & (abs(kz)>0.2))
@@ -78,15 +81,15 @@ def viewing_angle(filename, angle, nbins):
         return hist10, bins10
 
 
-def interpolate(filename, angle, nbins):
-    hist, bins = viewing_angle(filename, angle, nbins)
+def interpolate(filename, angle, nbins, distribution):
+    hist, bins = viewing_angle(filename, angle, nbins, distribution)
     f2 = interp1d(bins[:-1], hist[:], kind='cubic')
     xnew = np.linspace(bins[0], bins[-2], 2000)
     return f2(xnew), xnew
 
 
 def widths(filename, angle, bins): #there is a bug in this function
-    hist, x = interpolate(filename, angle, bins) #implement de interpolation
+    hist, x = interpolate(filename, angle, bins, distribution) #implement de interpolation
     width = (abs(np.amin(x)) + abs(np.amax(x))) / 2.0
     index = np.where(abs(x) > width/2.0)
     half_max = max(hist) / 2.
@@ -100,8 +103,8 @@ def widths(filename, angle, bins): #there is a bug in this function
         if Y[i] == np.amin(Y):
             print abs(x[i]*2.0)
 
-def maxima(filename, angle, bins):
-    hist, x = interpolate(filename, angle, bins) 
+def maxima(filename, angle, bins, distribution):
[…]

### 2014-04-21 code/New_widths_and_Maxima.py
minor bug fixed

@@ -88,7 +88,7 @@ def interpolate(filename, angle, nbins, distribution):
     return f2(xnew), xnew
 
 
-def widths(filename, angle, bins): #there is a bug in this function
+def widths(filename, angle, bins, distribution): #there is a bug in this function
     hist, x = interpolate(filename, angle, bins, distribution) #implement de interpolation
     width = (abs(np.amin(x)) + abs(np.amax(x))) / 2.0
     index = np.where(abs(x) > width/2.0)
@@ -131,8 +131,8 @@ mode = float(sys.argv[4])
 distribution = float(sys.argv[5])
 
 if mode == 0:
-	widths(filename, angle, bins)
+	widths(filename, angle, bins, distribution)
 if mode == 1:
-	maxima(filename, angle, bins)
+	maxima(filename, angle, bins, distribution)
 
 

### 2014-04-21 paper/ms.tex
Fig2. comments about the FWHM
2d Histograms of spectra (Homgeneous, Central)
sec 3 a little bit of text

@@
 simulations of individual
-galaxies\citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Meanwhile, recent
+galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Meanwhile, recent
 developments have been focused on the systematic study of clumpy
@@
 of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
-define the angle $\Theta$ by $\cos\Theta = \hat{k}_{\rm obs}\cdot
-\hat{k}_{\rm out}$, that is the angle of the outgoing photon with
-respect to the directions towards the observer. Following
-\cite{Zheng2013} we make the study of the anisotropic emission in
-terms of this angle.
+define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
+\hat{k}_{\rm \hat{k}}$, that is the angle of the line of sight with
+respect to the direction of the angular velocity. Following the notation
+implemented in \cite{Zheng2013}. %we make the study of the anisotropic emission in
+%terms of this angle.
 
@@
   a}$) and temperature.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.8\textwidth]{spectraCentral.eps}
+\end{center}
+\caption{Central.
+    \label{fig:CentralSpec}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.8\textwidth]{spectraHOM.eps}
+\end{center}
+\caption{Homogeneous
+    \label{fig:HOMSpec}}  
+\end{figure*}
 
@@
 
-The central result of this paper is summarized in Figure
-\ref{fig:differentvelocities}. It shows the clear
+The central results of this paper is summarized in Figures
+\ref{fig:CentralSpec} and \ref{fig:HOMSpec}. These figures shows
+that rotation fix a preferred axis for both photons distributions, 
+this implies that our systems doesn't have spherical symmetry and
+we have to take into account the viewing angle $\theta$ for all
+of our posterior analysis.
+
+Figure \ref{fig:differentvelocities} shows the clear
 impact of rotation on the morphology of the emergent \ly line,
 This profiles were obtained integrating the flux of photons 
- over all directions, this means we made histograms of the 
+ over the angle $\theta = \pi/2$, this means we made histograms of the 
  numbers of photons escaping the galaxy with a given frequency
@@
 \begin{center}
-  \includegraphics[width=0.8\textwidth]{f2.eps}
+  \includegraphics[width=0.8\textwidth]{widths.eps}
 \end{center}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.40\textwidth]{f3.eps}
+  \includegraphics[width=0.8\textwidth]{maxima.eps}
 \end{center}
@@
   peaked. \label{fig:maximumsvsvelocity}}  
-\end{figure}
+\end{figure*}
 
@@
 We use the full width at half maximum (FWHM) to quantify the line
-broadening. Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
+broadening. For this we measure the width by finding
+the closest points to the half maximum in our histogram numerically. 
+ Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
 with rotational velocity both for the central an homogeneous source
@@
 
+\iffalse
 \subsection{Anisotropy and off-centered emission}
@@
 gas, as the origin of the triple peaked emission.
+\fi
 

### 2014-04-23 code/New_widths_and_Maxima.py
minor changes

@@ -1,5 +1,6 @@
 import numpy as np
 import sys
+import matplotlib.pyplot as plt
 from scipy.interpolate import interp1d
 
 def reading_data(filename, distribution):
@@ -107,8 +108,11 @@ def maxima(filename, angle, bins, distribution):
     hist, x = interpolate(filename, angle, bins, distribution) 
     maxima = np.where(hist==np.amax(hist))
     x_m = x[maxima]
+    plt.scatter(x, hist)
+    #plt.show()
     if abs(x_m) < 0.2*np.amax(x):
-	print float(x_m)
+	print float(abs(x_m))
+	plt.axvline(x_m)
     else:
     	index1 = np.where(x>0)
     	hist1 = hist[index1]
@@ -122,8 +126,11 @@ def maxima(filename, angle, bins, distribution):
     	index31 = np.where(hist2 == np.amax(hist2))
     	x4 = x3[index31]
     	maximo2 = np.amax(hist2)
-    	print float(x2), float(x4)
-
+	X = 0.5* (abs(x2) + abs(x4) )
+    	print float(X), abs(x2), abs(x4)
+    	plt.axvline(x2)
+	plt.axvline(x4)
+    plt.show()
 filename = sys.argv[1]
 angle = float(sys.argv[2])
 bins = float(sys.argv[3])

### 2014-04-23 code/New_widths_and_Maxima.py
New maxima funciton

@@ -108,29 +108,14 @@ def maxima(filename, angle, bins, distribution):
     hist, x = interpolate(filename, angle, bins, distribution) 
     maxima = np.where(hist==np.amax(hist))
     x_m = x[maxima]
-    plt.scatter(x, hist)
+    #plt.scatter(x, hist)
+    index = np.where(hist == np.amax(hist))
+    maximo1 = np.amax(hist)
+    x2 = x[index]
+    print abs(x2)
+    #plt.axvline(x2)
     #plt.show()
-    if abs(x_m) < 0.2*np.amax(x):
-	print float(abs(x_m))
-	plt.axvline(x_m)
-    else:
-    	index1 = np.where(x>0)
-    	hist1 = hist[index1]
-    	x1 = x[index1]
-    	index11 = np.where(hist1 == np.amax(hist1))
-    	maximo1 = np.amax(hist1)
-    	x2 = x1[index11]
-    	index2 = np.where(x<0)
-    	hist2 = hist[index2]
-    	x3 = x[index2]
-    	index31 = np.where(hist2 == np.amax(hist2))
-    	x4 = x3[index31]
-    	maximo2 = np.amax(hist2)
-	X = 0.5* (abs(x2) + abs(x4) )
-    	print float(X), abs(x2), abs(x4)
-    	plt.axvline(x2)
-	plt.axvline(x4)
-    plt.show()
+
 filename = sys.argv[1]
 angle = float(sys.argv[2])
 bins = float(sys.argv[3])

### 2014-04-23 paper/ms.tex
update

@@
 broadens; second, the double peaks reduce their intensity; and third,
-the intensity at the line center rises. The last two effects merge to give the
+the intensity at the line center rises, this effects are present for 
+all the viewing angles. The last two effects merge to give the
 impression that the double peaks are merger into one at high rotational
@@
 We use the full width at half maximum (FWHM) to quantify the line
-broadening. For this we measure the width by finding
-the closest points to the half maximum in our histogram numerically. 
+broadening. For this we measure the width by interpolating dots in 
+our spectra this would produce a continuous spectra which makes easier
+to find the half maximum in our histogram numerically, just finding the 
+values of the width at the half maximum.
+
  Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
-with rotational velocity both for the central an homogeneous source
-distributions.  We parametrize the dependency of the line width with
+with rotational velocity both for the central (continuous lines) an 
+homogeneous (dashed lines) sources, for $\theta=\pi/2$.
+ We parametrize the dependency of the line width with
 $V_{\rm max}$ as

### 2014-04-23 code/New_widths_and_Maxima.py

@@ -108,13 +108,13 @@ def maxima(filename, angle, bins, distribution):
     hist, x = interpolate(filename, angle, bins, distribution) 
     maxima = np.where(hist==np.amax(hist))
     x_m = x[maxima]
-    #plt.scatter(x, hist)
+    plt.scatter(x, hist)
     index = np.where(hist == np.amax(hist))
     maximo1 = np.amax(hist)
     x2 = x[index]
-    print abs(x2)
-    #plt.axvline(x2)
-    #plt.show()
+    print float(abs(x2))
+    plt.axvline(x2)
+    plt.show()
 
 filename = sys.argv[1]
 angle = float(sys.argv[2])

### 2014-04-24 paper/ms.tex
More text + figures etc..

@@
 
-\shortauthors{Garavito-Camargo, Forero-Romero \& Dijstra}
+\shortauthors{Garavito-Camargo, Forero-Romero \& Dijkstra}
 
@@
 Figure \ref{fig:differentvelocities} shows the clear
-impact of rotation on the morphology of the emergent \ly line,
+impact of rotation on the morphology of the emergent \ly line.
 This profiles were obtained integrating the flux of photons 
- over the angle $\theta = \pi/2$, this means we made histograms of the 
+ over the angle $\theta = \pi/2$, this means we have made histograms of the 
  numbers of photons escaping the galaxy with a given frequency
@@
 simulation. For the models where dust is included we measure the 
-escape fraction as a function of rotational velocity. Finally, we make
-an estimate of the impact of anisotropic emission.
+escape fraction as a function of rotational velocity.
+
+\subsection{Rotation and the spherical symmetry}
+
+As a first approach we study the symmetry of the out-coming spectra
+taking into account the line of view ($\theta$) of an observer. Figures 
+\ref{fig:CentralSpec} and \ref{fig:HOMSpec} shows our findings, for 
+both distributions the morphology of the line change as the line 
+of sight of and observer changes. This is mainly due to the fact
+that photons propagating at $\theta = pi/2.0$ feel an stronger 
+angular momentum showing ... while photons in other direction feel
+a less contribution.
+
+We also consider possible variations in the flux with respect to $\theta$.
+ We define the flux by:
+\begin{equation}
+F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
+\end{equation}
+
+Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+$\Delta N$ is the number of photons in an angular bin $\Delta
+\Theta$. This definition satisfies the condition
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the 
+emission is characterized by a flat $F(\mu)$ distribution as 
+is shown in \ref{fig:muhisto}, this means that the amount of flux
+is the same for all of the angles.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.4\textwidth]{muhisto.eps}
+\end{center}
+\caption{Position of the peak maxima as a function of rotational
+  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
+  central (homogeneous) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:muhisto}}  
+\end{figure}
+
+Taking into account these results we perform the subsequent analysis
+for a fixed observer at $\theta = \pi/2.0$, the effect in the morphology
+of the \lya	line for different velocities is clearly shown in Figure
+ \ref{fig:differentvelocities}
 
@@
     the data using the expression in Eq. (\ref{eq:fwhm}).
-    \label{fig:widthvsvelocity}} 
+    \label{fig:widthvsmu}} 
 \end{figure*}
@@
 to find the half maximum in our histogram numerically, just finding the 
-values of the width at the half maximum.
+values of the width at the half maximum. In Figure \ref{fig:widthvsmu}
+the effect of the viewing angle is shown, the main effects here are that 
+as $\mu$ increase the FWHM decrease this is also explained by the same argument
+of section XX. The second effect is that clearly as $\rm{V_{max}}$ increase 
+the FWHM also increase.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.8\textwidth]{f2.eps}
+\end{center}
+\caption{Position of the peak maxima as a function of rotational
+  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
+  central (homogeneous) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:widthsvsvelocity}}  
+\end{figure*}
 
@@
 %
-where FWHM$_{0}$ is the
-velocity width in the static case and $\lambda$ is a positive scalar
-to be determined as a fit to the data. With this test we want to know
+where FWHM$_{0}$ is the velocity width in the static case and $\lambda$ 
+is a positive scalar to be determined as a fit to the data. 
+With this test we want to know
 to what extent the new velocity width can be expressed as a quadratic

### 2014-04-24 paper/ms.tex
new plot and some text

@@
 define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
-\hat{k}_{\rm \hat{k}}$, that is the angle of the line of sight with
+\hat{k}$, that is the angle of the line of sight with
 respect to the direction of the angular velocity. Following the notation
@@
 %terms of this angle.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.4\textwidth]{f8.eps}
+\end{center}
+\caption{Geometry
+    \label{fig:CentralSpec}}  
+\end{figure}
 
@@
 of sight of and observer changes. This is mainly due to the fact
-that photons propagating at $\theta = pi/2.0$ feel an stronger 
-angular momentum showing ... while photons in other direction feel
+that photons propagating at $\theta = \pi/2.0$ feels ... while photons in other direction feel
 a less contribution.
@@
 \begin{center}
+  \includegraphics[width=0.8\textwidth]{f2.eps}
+\end{center}
+\caption{Position of the peak maxima as a function of rotational
+  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
+  central (homogeneous) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:widthsvsvelocity}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
   \includegraphics[width=0.8\textwidth]{maxima.eps}
@@
 the FWHM also increase.
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.8\textwidth]{f2.eps}
-\end{center}
-\caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  central (homogeneous) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
-  peaked. \label{fig:widthsvsvelocity}}  
-\end{figure*}
 
@@
 \subsection{Average Number of Scatterings}
+
+\begin{figure}
+\begin{center}
+    \includegraphics[width=0.40\textwidth]{nscattvsmu.eps}
+\end{center}
+\caption{Logarithm of the average number of scatterings as function of
+  $\mu$. This is the general behavior for all models in particular this model
+  is for $\tau=10^{5}$ and $V_{max}=300 km/s^{-1}$. \label{fig:Nscattvsmu}}    
+\end{figure}
 

### 2014-04-24 paper/ms.tex
new abstract

@@
 \author{Mark Dijkstra}
-\affil{Institute of Theoretical Astrophysics, University of Oslo, Postboks 1029, 0858 Oslo, Norway}
+\affil{Institute of Theoretical Astrophysics, University of Oslo,
+  Postboks 1029, 0858 Oslo, Norway} 
 \email{mark.dijkstra@astro.uio.no }
 
-\keywords{galaxies: high-redshift --- line: formation --- methods: numerical ---  radiative transfer}
+\keywords{galaxies: high-redshift --- line: formation --- methods:
+  numerical ---  radiative transfer} 
 \begin{abstract}
@@
 emission line in distant galaxies. We model a galaxy as a sphere with
-a homogeneous mixture of dust and hydrogen at a constant
+an homogeneous mixture of dust and hydrogen at a constant
 temperature. These spheres have a solid-body rotation with maximum
@@
 of a single central \lya source, and a uniform distribution of sources. 
-Our main finding are that the escape fraction of \lya photons, and
-the intensity at the line center increases with rotational velocity. 
-For homogeneously distributed sources the line becomes single peaked 
-at rotational velocities larger than half the line width in the static
-case. We also find that this anisotripic velocity configuration does
-not induce any significant anisotropy in the spectral properties.
-For radiation sources located off-center, the line morphology
-presents  a range of single, double and triple peaks. We show how
-these results  are useful to interpret recent spectroscopic results of distant 
-$z\sim 2-3$ star forming galaxies.
-
+Our main result is that rotation introduces a dependence of the
+line morphology with  viewing angle. Observations parallel to the
+rotation axis yield lines similar to the static case. The greatest
+difference is observed perpendicular to the rotation axis where the
+intensity at the line center increases with rotational velocity.  For
+homogeneously distributed sources the line becomes single peaked  at
+rotational velocities larger than half the line width in the static
+case. However, rotation does not not induce any significant anisotropy
+in the total line intensity or in the escape fraction. 
 \end{abstract}

### 2014-04-24 paper/ms.tex
revised intro

@@
 studies focused on homogeneous and static media
-\citep{Ahn00,Ahn01,Zheng02}; Later on, the effects of clumpy media
+\citep{Ahn00,Ahn01,Zheng02}. Later on, the effects of clumpy media
 \citep{Hansen06} and expanding/contracting shell/spherical geometries started to
@@
 interpretation of LAEs observations with high resolution
-spectroscoy. In the last section we present our conclusions.
+spectroscopy. In the last section we present our conclusions.
 
@@
 radiative transfer calculations the thermal velocity is
-$v_{th}=12.8$\kms.
+$v_{\rm th}=12.8$\kms.
 

### 2014-04-24 paper/ms.tex
code description

@@
 direction as the $\hat{k}$ unit vector. With these definitions we can
-write the angular velocity as $\omega=V_{\rm max}/R$.
+write the norm of the angular velocity as $\omega=V_{\rm max}/R$.
 
@@
 propagation to be random following an flat probability distribution
-over the sphere.
+over the sphere. A different initization that uses a Gaussian with a
+velocity with equal to the thermal velocity, $12.8$\kms in our case,
+should not introduce noticeable change given that our rotational
+velocities span the range $100$-$300$\kms and the lines have velocity
+widths on the order of $100$-$500$\kms.
 
@@
 \begin{center}
-  \includegraphics[width=0.8\textwidth]{spectraCentral.eps}
+  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
 \end{center}
-\caption{Central.
-    \label{fig:CentralSpec}}  
+\caption{
+2D histogram showing the number of photons that escape with frecuency
+$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
+rotationa axis. The rotational velocity ($0,100,200,300$\kms)
+increases from left to right and the optical depth ($10^5$, $10^6$,
+$10^7$) from top to bottom. 
+\label{fig:CentralSpec} }   
 \end{figure*}

### 2014-04-24 paper/ms.tex
updated section 2 including captions

@@
 For each photon in the simulation we have its initial position inside
-the sphere, direction of propagation $\hat{k}_{in}$ and reduced
-frequency $x_{in}$. The photon's propagation stops once they cross the
+the sphere, direction of propagation $\hat{k}_{\rm in}$ and reduced
+frequency $x_{\rm in}$. The photon's propagation stops once they cross the
 surface of the sphere. At this point we store the position, the outgoing direction
-of propagation $\hat{k}_{out}$ and the reduced frequency $x_{out}$. We
-define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm obs}\cdot
-\hat{k}$, that is the angle of the line of sight with
-respect to the direction of the angular velocity. Following the notation
-implemented in \cite{Zheng2013}. %we make the study of the anisotropic emission in
-%terms of this angle.
+of propagation $\hat{k}_{\rm out}$ and the reduced frequency $x_{\rm
+  out}$. We now define the angle $\theta$ by $\cos\theta = \hat{k}_{\rm out}\cdot
+\hat{k}\equiv \mu$, it is the angle of the outgoing photons with 
+respect to the direction of the angular velocity. We use the variable $\mu$ to
+study the anisotropy induced by rotation. Figure \ref{fig:geometry}
+shows the geometry of the problem and the important variables.
 
@@
 \end{center}
-\caption{Geometry
-    \label{fig:CentralSpec}}  
+\caption{Geometry of the gas distribution. The angular velocity vector
+  is parallel to the unit vector $\hat{k}$. In order to describe the
+  departures from spherical symmetry we use the polar angle $\theta$
+  formed by the direction of the outgoing photons with respecto to the
+  $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
+  report to present our results.
+    \label{fig:geometry}}  
 \end{figure}
@@
 increases from left to right and the optical depth ($10^5$, $10^6$,
-$10^7$) from top to bottom. 
+$10^7$) from top to bottom. The \ly photons are initialized at the
+center of the sphere.
 \label{fig:CentralSpec} }   
@@
 \begin{center}
-  \includegraphics[width=0.8\textwidth]{spectraHOM.eps}
+  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
 \end{center}
-\caption{Homogeneous
-    \label{fig:HOMSpec}}  
+\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
+  initialized homogeneously throughout the sphere.
+    \label{fig:HomSpec}}  
 \end{figure*}
@@
 Additionally, we have used two independently developed Monte Carlo
-codes \citep{CLARA,DijkstraKramer} to perform the calculations of the
-non-dusty models. The results we report are robust in the sense
-that they are obtained by both codes.
+codes \citep{CLARA,DijkstraKramer} to perform the calculations. The
+results we report are robust in the sense that they are obtained by
+both codes.
 
@@
 
-The central results of this paper is summarized in Figures
-\ref{fig:CentralSpec} and \ref{fig:HOMSpec}. These figures shows
+The central results of this paper are summarized in Figures
+\ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
+of escape frequency $x$ and escape angle parameterized by
+$\cos\theta$.
+
 that rotation fix a preferred axis for both photons distributions, 

### 2014-04-24 paper/ms.tex
new structure

@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
-\end{center}
-\caption{
-2D histogram showing the number of photons that escape with frecuency
-$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
-rotationa axis. The rotational velocity ($0,100,200,300$\kms)
-increases from left to right and the optical depth ($10^5$, $10^6$,
-$10^7$) from top to bottom. The \ly photons are initialized at the
-center of the sphere.
-\label{fig:CentralSpec} }   
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
-\end{center}
-\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
-  initialized homogeneously throughout the sphere.
-    \label{fig:HomSpec}}  
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.8\textwidth]{f1.eps}
-\end{center}
-\caption{Shape of the \ly line for
-    different maximum rotational velocities. The continuous (dashed)
-    line represents the central (homogeneous) source distributions. 
-    These profiles were obtained integrating the flux of photons 
-	over all directions, this means we made histograms of the 
-	numbers of photons escaping the galaxy with a given frequency.
-    \label{fig:differentvelocities}}  
-\end{figure*}
-
 \subsection{Grid of Simulated Galaxies}
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
+\end{center}
+\caption{
+2D histogram showing the number of photons that escape with frecuency
+$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
+rotationa axis. The rotational velocity ($0,100,200,300$\kms)
+increases from left to right and the optical depth ($10^5$, $10^6$,
+$10^7$) from top to bottom. The \ly photons are initialized at the
+center of the sphere.
+\label{fig:CentralSpec} }   
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
+\end{center}
+\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
+  initialized homogeneously throughout the sphere.
+    \label{fig:HomSpec}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f1.eps}
+\end{center}
+\caption{Shape of the \ly line for different maximum rotational
+  velocities for a viewing angle perpendicular to the rotation axis
+  ($|\mu|\sim 0$). The continuous (dashed) line represents the central
+  (homogeneous) source distributions.  The panels follow the same
+  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
+    \label{fig:differentvelocities}}  
+\end{figure*}
+
 \section{Results}
@@
 
-The central results of this paper are summarized in Figures
+The central results of this paper are evident in Figures
 \ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
-of escape frequency $x$ and escape angle parameterized by
-$\cos\theta$.
+of escape frequency $x$ and escape angle $\theta$ parameterized by
+$|\mu|$ after verifying that the solutions are symmetric with respect to
+$\mu=0$.  Making a selection around a given value of $\mu$ gives us the
+line detected by an observer located at an angle $\theta$ with respect
+to the rotation axis.
 
-that rotation fix a preferred axis for both photons distributions, 
-this implies that our systems doesn't have spherical symmetry and
-we have to take into account the viewing angle $\theta$ for all
-of our posterior analysis.
+From these Figures we can see that the line properties change with
+rotational velocity and depend on the viewing angle $\theta$.  In the
+next subsections we describe in  detail the changes of the morphology
+with velocity, optical depth and viewing angle. We characterize the
+line morphology by its total intensity, the full width at half maximum
+(FWHM) and the location of the peak maxima. In order to interpret the
+morphological changes in the line we also report the median number of
+scatter for each \ly photon in the simulation. For the models where
+dust is included we measure the escape fraction as a function of
+rotational velocity.
 
-Figure \ref{fig:differentvelocities} shows the clear
-impact of rotation on the morphology of the emergent \ly line.
-This profiles were obtained integrating the flux of photons 
- over the angle $\theta = \pi/2$, this means we have made histograms of the 
- numbers of photons escaping the galaxy with a given frequency
-The panel focus on the results for all of our symmetric models
- $\tau_{H}=(10^{5}, 10^{6}, 10^{7}$), showing that the
-influence of rotation is present both when the photons are either
-homogeneously or centrally initialized over the gas volume.
+\subsection{Line Morphology}
+\label{sec:angles}
 
-In the next subsections we characterize the line morphology by the
-full width at half maximum (FWHM) and the location of the peak
-maxima. In order to interpret the morphological changes in the line we
-also report the median number of scatter for each \ly photon in the
-simulation. For the models where dust is included we measure the 
-escape fraction as a function of rotational velocity.
+The first column in both Figures \ref{fig:CentralSpec} and
+\ref{fig:HomSpec} shows that for the static sphere the line properties
+are independent of $|\mu|$, as it is expected due
+to the spherical symmetry. However, for increasing rotational
+velocities, at a fixed optical depth, there are clear signs that this
+symmetry is broken.
 
-\subsection{Rotation and the spherical symmetry}
+If the viewing angle is aligned witht the rotation axis, $|\mu|\sim
+1$, the \ly line keeps a double peak with some changes as a function
+of the rotational velocity that are easier to spot in models where the
+\ly photons are homogeneously distributen than in the case of central
+emission.
 
-As a first approach we study the symmetry of the out-coming spectra
-taking into account the line of view ($\theta$) of an observer. Figures 
-\ref{fig:CentralSpec} and \ref{fig:HOMSpec} shows our findings, for 
-both distributions the morphology of the line change as the line 
-of sight of and observer changes. This is mainly due to the fact
-that photons propagating at $\theta = \pi/2.0$ feels ... while photons in other direction feel
-a less contribution.
+However, for a line of sight perpendicular to the rotation
+axis, $|\mu|\sim 0$, the impact of rotation is larger.  This is clear
+in  Figure \ref{fig:differentvelocities} where we present the
+different line morphologies for $|\mu|\sim 0$ for both the homogeneous
+and central configurations. The panels have the same distribution as
+Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
 
-We also consider possible variations in the flux with respect to $\theta$.
+There are three clear effects on the line's morphology as the
+rotational velocity increases. First, the line broadens; second, the
+double peaks reduce their intensity; and third, the intensity at the
+line center rises. The last two effects merge to give the
+impression that the double peaks are merger into one at high rotational
+velocities, a result that is evident for the homogeneously distributed
+sources as shown in the dashed lines of Figure
+\ref{fig:differentvelocities}.
+
+In
+
+\subsection{Integrated Line Intensity}
+
+We consider possible variations in the integrated flux with respect to
+$\theta$.
+
 We define the flux by:
@@
 
+We
+
 \begin{figure}
@@
 \end{center}
-\caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  central (homogeneous) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
-  peaked. \label{fig:muhisto}}  
+\caption{Integrated flux distribution, $F(\mu)$, as a function of the
+  viewing angle as parameterized by $\mu$. We show the results for the
+  homogeneous source distribution in models with rotational velocities
+  $0,100,200,300$\kms and  optical depths $10^5$, $10^6$, $10^7$. We
+  see that the distribution is flat, meaning that the flux for all
+  viewing angles is the same. The results for the central sources are
+  similar. 
+\label{fig:muhisto}}
 \end{figure}
 
-Taking into account these results we perform the subsequent analysis
-for a fixed observer at $\theta = \pi/2.0$, the effect in the morphology
-of the \lya	line for different velocities is clearly shown in Figure
- \ref{fig:differentvelocities}
-
-\subsection{Line width and peak maxima}
+\subsection{Full Width at Half Maximum}
 \label{sec:widthpeak}
@@
 
-There are three clear effects on the line's morphology as the
-rotational velocity increases. First, the line
-broadens; second, the double peaks reduce their intensity; and third,
-the intensity at the line center rises, this effects are present for 
-all the viewing angles. The last two effects merge to give the
-impression that the double peaks are merger into one at high rotational
-velocities, a result that is evident for the homogeneously distributed
-sources as shown in the dashed lines of Figure \ref{fig:differentvelocities}.
-
 We use the full width at half maximum (FWHM) to quantify the line
@@
 1.98\pm 0.06$ respectively.
+
+\subsection{Peaks Positions}
+\label{sec:peaks}
 
@@
 
+\subsection{Dusty Clouds: Escape Fraction}
+\label{sec:escapefraction}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{c ccc ccc}
+\hline \hline
+Source & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
+Distribution& &  &  & (\kms) & & \\ 
+& & 0 & 50 & 100 &200 & 300\\ \hline 
+Homogeneous & $10^{5}$& 0.263 & 0.266 &  0.309 &  0.357 &  0.370  \\
+           & $10^{6}$ & 0.289 &  0.289 &   0.309 &  0.360 &  0.393 \\
+         &$10^{7}$ &  0.227 &  0.229 &  0.231 &  0.254 &  0.281 \\
+Central & $10^{5}$ &  0.096 & 0.097 & 0.096 &  0.096 & 0.096 \\
+  &$10^{6}$ & 0.066 & 0.066 &  0.066 &  0.066 &  0.066 \\
+ &$10^{7}$ & 0.015 &  0.016 & 0.016 & 0.016 & 0.015 \\
+\hline
+\end{tabular}
+\caption{
+ Escape fraction values for all dusty models. } 
+\label{table:escape}
+\end{center}
+\end{table}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.40\textwidth]{f6.eps}
+  \includegraphics[width=0.40\textwidth]{f7.eps}
+\end{center}
+  \caption{Effects of rotation on the escape fraction. Left
+    panel, escape fraction as a function of rotational velocity. All
+    these models have $\tau_{a}=1$. The continuous (dashed) lines
+    correspond to central (homogeneous) models. Right panel, escape
+    fraction as a    function of the product $(a\tau_{\rm
+      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
+    slab is shown as a continuous    line. Different lines correspond
+    to different rotational velocities for the homogeneous models.     
+    \label{fig:efvsv}} 
+\end{figure*}
+
+In the case of dusty clouds, all changes in the average number
+of scatterings presented in the previous subsection have a direct
+bearing on the escape fraction. From the results we have just obtained
+we can predict that for central source distributions the escape
+fraction will barely change, while larger effects should be expected
+for homogeneously distributed sources.
+
+Left panel of Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
+fraction as a function of the rotational velocity. The curves for the
+central source distribution stay flat, while for the homogeneous case
+there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
+the models with low optical depth. For instance, in models with
+$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
+to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
+all the values for the escape fraction.
+
+In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
+the analytic solution for the infinite slab \citep{Neufeld90}. In
+Neufeld's set-up the analytic solution depends uniquely on the product
+$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ , an approximation 
+that is valid only in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in
+ the right panel of Figure \ref{fig:efvsv} show the results for the different rotational
+velocities for the homogeneous models. First of all we note that the escape fraction does not
+increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, This
+ counter-intuitive result is a consequence of the transition into the 'extremely' opaque regime,
+  which occurs roughly when $a\tau_{\rm{H}} > 10^{3}$
+  e.g. \citep{Neufeld90}.
+
 \subsection{Average Number of Scatterings}
+\label{sec:scatterings}
 
@@
 
-\subsection{Dusty Clouds: Escape Fraction}
-\label{sec:escapefraction}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{c ccc ccc}
-\hline \hline
-Source & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
-Distribution& &  &  & (\kms) & & \\ 
-& & 0 & 50 & 100 &200 & 300\\ \hline 
-Homogeneous & $10^{5}$& 0.263 & 0.266 &  0.309 &  0.357 &  0.370  \\
-           & $10^{6}$ & 0.289 &  0.289 &   0.309 &  0.360 &  0.393 \\
-         &$10^{7}$ &  0.227 &  0.229 &  0.231 &  0.254 &  0.281 \\
-Central & $10^{5}$ &  0.096 & 0.097 & 0.096 &  0.096 & 0.096 \\
-  &$10^{6}$ & 0.066 & 0.066 &  0.066 &  0.066 &  0.066 \\
- &$10^{7}$ & 0.015 &  0.016 & 0.016 & 0.016 & 0.015 \\
-\hline
-\end{tabular}
-\caption{
- Escape fraction values for all dusty models. } 
-\label{table:escape}
-\end{center}
-\end{table}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.40\textwidth]{f6.eps}
-  \includegraphics[width=0.40\textwidth]{f7.eps}
-\end{center}
-  \caption{Effects of rotation on the escape fraction. Left
-    panel, escape fraction as a function of rotational velocity. All
-    these models have $\tau_{a}=1$. The continuous (dashed) lines
-    correspond to central (homogeneous) models. Right panel, escape
-    fraction as a    function of the product $(a\tau_{\rm
-      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
-    slab is shown as a continuous    line. Different lines correspond
-    to different rotational velocities for the homogeneous models.     
-    \label{fig:efvsv}} 
-\end{figure*}
-
-In the case of dusty clouds, all changes in the average number
-of scatterings presented in the previous subsection have a direct
-bearing on the escape fraction. From the results we have just obtained
-we can predict that for central source distributions the escape
-fraction will barely change, while larger effects should be expected
-for homogeneously distributed sources.
-
-Left panel of Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
-fraction as a function of the rotational velocity. The curves for the
-central source distribution stay flat, while for the homogeneous case
-there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
-the models with low optical depth. For instance, in models with
-$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
-to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
-all the values for the escape fraction.
-
-In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
-the analytic solution for the infinite slab \citep{Neufeld90}. In
-Neufeld's set-up the analytic solution depends uniquely on the product
-$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ , an approximation 
-that is valid only in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in
- the right panel of Figure \ref{fig:efvsv} show the results for the different rotational
-velocities for the homogeneous models. First of all we note that the escape fraction does not
-increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, This
- counter-intuitive result is a consequence of the transition into the 'extremely' opaque regime,
-  which occurs roughly when $a\tau_{\rm{H}} > 10^{3}$ e.g. \citep{Neufeld90}.
-
-\iffalse
-\subsection{Anisotropy and off-centered emission}
-\label{sec:off-center}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.40\textwidth]{f8.eps}
-\end{center}
-\caption{Schematic representation of the geometry for the off-center
-  emission. The large circle represents the gas distribution and the
-    two smaller circles the off-centered \ly emitting regions. The angular
-    velocity vector lies along $\hat{k}$ direction
-    towards the reader. The vector $\hat{k}_{\rm out}$ represents the
-    outgoing direction of an escaping \ly photon and the observer is
-    placed along the $\hat{j}$ direction. The distribution of $\Theta$
-    angles is used to study potential emission anisotropy. 
-    \label{fig:OCspheres}}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=0.42\textwidth]{f9.eps}
-  \caption{Histogram of $\mu\equiv\cos\Theta$ for the 
-    central (dotted), homogeneous (dashed) and off-center (solid
-    line) distributions. Deviations from a flat distribution signal the presence of
-    spatial emission anisotropy. 
-    \label{fig:muhisto}} 
-\end{figure}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.90\textwidth]{f10.eps}
-\end{center}
-\caption{\ly profiles for the off-centered emission. Dashed/solid
-  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
-   \label{fig:OC_profiles}} 
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.90\textwidth]{f11.eps}
-\end{center}
-\caption{Triple peaked profiles for three different off-center positions
-  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
-  line) and for different rotational velocities. $\theta$ represents
-  the position of the observer as mesured with the polar angle.
-   \label{fig:3p_profiles}} 
-\end{figure*}
-
-Rotation breaks the spherical symmetry of the static model and
-introduces the rotation axis as a preferred direction. This motivates
-us to study the anisotropy of the outgoing photons. In order to study
-possible deviations with respect to an isotropic flux we follow
-\cite{Zheng2013} to estimate the flux as a function of the angle
-$\Theta$ formed by the outgoing photons and the observer. Figure
-\ref{fig:OCspheres} presents a geometric scheme to clarify the
-definition of all relevant directions in the problem.
-
-An estimator for the anisotropy is represented by
-%
-\begin{equation}
-F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
-\end{equation} 
-%
-where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
-$\Delta N$ is the number of photons in a angular bin $\Delta
-\Theta$. This definition satisfies the condition
-$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the isotropic
-emission is characterized by a flat $F(\mu)$ distribution.
-
-Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
-distribution for a sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
-  max}=200$\kms. The dashed and dotted lines represent the homogeneous
-and central source distribution, respectively. This shows that the
- anisotropy induced by rotation is at the $3\%$ level. We
-performed the same test with all the models and find that the
-variation in $\mu$ does not depend on the rotational velocity;
-however, high optical depth values can increase the variation of
-$\mu$ up to a $15\%$.
-
-We also explore a different source of anisotropy by studying the effect
-of radiation sources located in off-centered spheres with respect to
-the gas distribution. Figure \ref{fig:OCspheres} shows the two
-spherical regions we define to test for this effect. Each has a radius
-of $0.5R$, where $R$ is the radius of the gaseous sphere. With an
-observer located along the $\hat{j}$ direction, we pick two possible
-positions to center the spheres along the $\hat{i}$ axis: $\pm C\hat{i}$. In
-this configuration the emitting sphere centered on $+C\hat{i}$ moves
-towards the observer and the sphere centered on $-C\hat{j}$ moves
-away from the observer.
-
-In this case the $\mu$ distribution is not homogeneous as it is shown in
-Figure \ref{fig:muhisto}. The off-center emission shows a variation of flux at
-the levels of $10\% - 28\%$ in intensity with the angle $\Theta$. In general 
-models with a larger $\tau_{H}$ present a higher variation in the flux.
-
-We also explore the effects of the off-centered emission in the line
-morphology. Figure \ref{fig:OC_profiles} show the spectra for the two
-off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
-only use photons that have outgoing directions aligned with the
-observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
-asymmetry in the line morphology within the range of explored velocities.
-
-However, we find some cases where there is a possible signature of
-triple peaked emission. This is only present in some models
-($\tau_{\rm H} = 10^6, V=100$\kms and $\tau_{\rm H} = 10^7,
-V=300$\kms) and could be the result of two competing effects: the rise
-in the line's center as the photons in the photosphere escape in a
-single excursion and the broadening in the two peaks as the photons
-closer from the center have to scatter to escape. We examine in
-greater detail these cases in the next sub-section.
-
-\subsection{Triple Peaked Profiles}
-\label{sec:3p}
-
-The off-centered cases with hints of triple peaked emission motivate us
-to explore this in more detail. The first condition is to increase the
-number of photons in the radiative transfer calculation. In the line
-profiles presented in the previous subsection, only $\sim 10^4$ photons
-have the geometric conditions to build the line profile. We run a few
-models with $N_{\gamma} = 10^6$ in order to improve the statistics and
-explore smaller radii for the off-centered spheres.
-
-We re-simulate four models that presented some signs of triple peaked
-profiles: $V_{\rm max}=50\kms$, $\tau_{\rm H}=10^{5}$; $V_{\rm
-  max}=100\kms$, $\tau_{H}=10^{6}$; $V_{\rm max}=150\kms$, $\tau_{\rm
-  H}=10^6$; and $V_{\rm max}=200\kms$, $\tau_{\rm H}=10^{7}$. We
-select the photons that were emitted within spheres of radius $0.25R$
-centered at $C=(0.25R, 0.5R, 0.75R)$, following the same
-geometry presented in Figure \ref{fig:OCspheres}.
-
-Figure \ref{fig:3p_profiles} summarizes the results for all these
-models. In all cases the stronger triple peaked signatures is
-presented by the emitting spheres close centered at $0.75R$ close to
-the surface. Emitting spheres closer to the center do not show clear
-signatures for a triple peaked emission.
-
-Furthermore, taking into account all the models that do not present hints for
-a triple peaked emission it would seem that the rotational velocity
-and optical depth must balance each other in order to show this feature.
- Namely, if the rotational velocity is close to half the FWHM
-of the line, the triple peaks are more likely to occur. This is the
-same threshold that in the case of centered emission marks the
-difference between double and single peaked lines.
-
-Are these features observable with current instrumental capabilities?
-As an order of magnitude estimate we can consider that the width of
-each one of the triple peaks is close to $1/3$ of the FWHM of the line
-at a given $V_{\rm max}$. For the cases we have studied in this
-subsection those values would be close to $50\kms$, $100\kms$ and
-$200\kms$ for optical depths of $10^5$, $10^6$, and $10^7$
-respectively. At a redshift of $z\sim 2-3$ each one of these widths
-is multiplied by factors of $z+1\sim 3-4$. Considering a nominal value
-for the resolution of $\Delta v=200\kms$ for a Near-IR spectrograph capable of observing
-those galaxies \citep{Kulas12}, we find that only the case of triple
-peaked emission for the most massive object $\tau_{\rm H}=10^{7}$,
-$V_{\rm max}=200\kms$ would have a chance to be spectrally
-resolved. We note that observations of triple peaked systems with
-higher resolution spectrographs have been reported  by
-\cite{Chonis2013}, however the large velocity off-sets ($\sim
-1000$\kms) from the systemic redshift favor the hypothesis of an
-interacting system, including emission from shocked and fluorecing
-gas, as the origin of the triple peaked emission.
-\fi
-
 \section{Discussion}
@@
  \ly line. In this section we discuss the implications of these
- findings for the interpretation of available observational data. Our
- discussion focuses on the qualitative aspects of diverse
- morphological features observed by \cite{Kulas12} and \cite{Yamada2012}
-
-We follow a classification of \ly profiles made by
-\cite{Kulas12}. They presented observational results for star forming
-galaxies at $z=2$-$3$ with multiple peaks in their \ly emission.
-They classified the observed lines into five groups. In Group I the
-red peak is stronger than the blue, while in Group II the blue peak is
-stronger, in both cases the peaks are symmetrically located around the
-line center. In Group III the blue peak also dominates but there is an
-overall redward shift of the zero point. Group IV presents two similar
-peaks symmetrically located around the zero point and Group V galaxies show
-three peaks.
-
-The asymmetries in Groups I, II  and III cannot be explained by
-rotation. However, some galaxies in those groups have a high flux between
-the two peaks; this could indicate the presence of rotation 
-and \ly photons leaking though low column density holes, as in \cite{Behrens2014}. The same argument applies to galaxies in the group IV in which the flux
-in between of the two peaks is high ($ \geq 70 \%$ of the intensity in
-the highest peak). Finally, the triple peaked lines in Galaxies in
-Group V can be reproduced by rotation with off-centered
-emission given the right amount of asymmetry between the emitting
-region and neutral hydrogen distribution.
-
-Another relevant sample of observations was presented by \cite{Yamada2012} 
-for 91 LAEs at $z=3.1$. They find that $\sim 33 \%$ of the galaxies present 
-a single peak profile. Some of the peaks have a strong symmetry, while
-others do not. The symmetric single peaked profile can be explained by
-rotation effects, while the asymmetric cases naturally arise in
-outflow/inflow models \citep{Ahn2014,Verhamme2008, Dijkstra06}. Among the 91
-LAEs, 8 reveal triple peaked profiles with a central peak and two
-smaller peaks at the redder and bluer side, a feature that is present
-in our off-center emission models with rotation Figure \ref{fig:3p_profiles}.
+ findings for the interpretation of available observational data.
 
@@
 
-\item For off-centered emission triple peaked profiles can emerge
-  under two joint conditions: the emission occurs close to the sphere's
-  surface and the rotational velocity is close to half the FWHM in the
-  static case.   
 \end{itemize}
@@
 morphological features such as high central line flux, single peak
-profiles and multiple-peaked profiles could be explained by gas bulk 
-rotation present in these LAEs. We defer the study of triple peaked
-emission in the context of gas bulk rotation to a future publication
-(Remolina-Gutierrez et al., in preparation).
+profiles  could be explained by gas bulk  rotation present in these
+LAEs.
 

### 2014-04-24 paper/ms.tex
caption

@@
   homogeneous source distribution in models with rotational velocities
-  $0,100,200,300$\kms and  optical depths $10^5$, $10^6$, $10^7$. We
+  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$. We
   see that the distribution is flat, meaning that the flux for all

### 2014-04-26 paper/ms.tex
fig size
updated FWHM section

@@
 
-The central results of this paper are evident in Figures
+The central results of this paper are summarized in Figures
 \ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
-of escape frequency $x$ and escape angle $\theta$ parameterized by
-$|\mu|$ after verifying that the solutions are symmetric with respect to
-$\mu=0$.  Making a selection around a given value of $\mu$ gives us the
-line detected by an observer located at an angle $\theta$ with respect
-to the rotation axis.
+of the escape frequency $x$ and outgoing angle $\theta$ parameterized by
+$|\mu|$. Constructing the emission line with photons around a value
+of $\mu$ would gives us the emission detected by an observer located at an
+angle $\theta$ with respect to the rotation axis. We have veryfied
+that the solutions are indeed symmetric with respect to $\mu=0$.
 
@@
 
-There are three clear effects on the line's morphology as the
-rotational velocity increases. First, the line broadens; second, the
-double peaks reduce their intensity; and third, the intensity at the
-line center rises. The last two effects merge to give the
-impression that the double peaks are merger into one at high rotational
-velocities, a result that is evident for the homogeneously distributed
-sources as shown in the dashed lines of Figure
-\ref{fig:differentvelocities}.
-
-In
+For this case of $|\mu|\sim 0$, there are three clear effects on the
+line's morphology as the rotational velocity increases. First, the
+line broadens; second, the double peaks reduce their intensity; and
+third, the intensity at the line center rises. The last two effects
+merge to give the impression that the double peaks are merged into one
+at high rotational velocities, a result that is evident for the
+homogeneously distributed sources as shown in the dashed lines of
+Figure \ref{fig:differentvelocities}.
 
 \subsection{Integrated Line Intensity}
-
-We consider possible variations in the integrated flux with respect to
-$\theta$.
-
-We define the flux by:
-\begin{equation}
-F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
-\end{equation}
-
-Where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
-$\Delta N$ is the number of photons in an angular bin $\Delta
-\Theta$. This definition satisfies the condition
-$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the 
-emission is characterized by a flat $F(\mu)$ distribution as 
-is shown in \ref{fig:muhisto}, this means that the amount of flux
-is the same for all of the angles.
-
-We
 
@@
 
+We consider possible variations in the integrated flux with respect to
+$\theta$. We define the normalized flux seen by an observer at an
+angle $\mu$ by: \begin{equation}
+F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
+\end{equation} 
+%
+where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+$\Delta N$ is the number of photons in an angular bin $\Delta
+\Theta$. This definition satisfies the condition
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.
+
+Figure \ref{fig:muhisto} shows a flat $F(\mu)$ for all models. It
+means that in spite of the different morphologies, the integrated flux
+is the same for all sight angles.
+
 \subsection{Full Width at Half Maximum}
@@
 \begin{center}
-  \includegraphics[width=0.8\textwidth]{widths.eps}
+  \includegraphics[width=0.95\textwidth]{widths.eps}
+\end{center}
+  \caption{FWHM for the non-dusty models as a function of the viewing
+  angle parameterized by $\mu\equiv\cos\theta$. 
+  Continuous (dashed) lines  correspond to central (homogeneous)
+  source distributions. The general trend is of an decreasing FWHM as
+  the line of sight becomes parallel to the rotation axis. 
+  \label{fig:widthvsmu}} 
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f2.eps}
 \end{center}
@@
   the data using the expression in Eq. (\ref{eq:fwhm}).
-    \label{fig:widthvsmu}} 
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.8\textwidth]{f2.eps}
-\end{center}
-\caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  central (homogeneous) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
-  peaked. \label{fig:widthsvsvelocity}}  
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.8\textwidth]{maxima.eps}
-\end{center}
-\caption{Position of the peak maxima as a function of rotational
-  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  central (homogeneous) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
-  peaked. \label{fig:maximumsvsvelocity}}  
+  \label{fig:widthsvsvelocity}}
 \end{figure*}
@@
 We use the full width at half maximum (FWHM) to quantify the line
-broadening. For this we measure the width by interpolating dots in 
-our spectra this would produce a continuous spectra which makes easier
-to find the half maximum in our histogram numerically, just finding the 
-values of the width at the half maximum. In Figure \ref{fig:widthvsmu}
-the effect of the viewing angle is shown, the main effects here are that 
-as $\mu$ increase the FWHM decrease this is also explained by the same argument
-of section XX. The second effect is that clearly as $\rm{V_{max}}$ increase 
-the FWHM also increase.
+broadening. We measure this width from the velocity histogram by
+finding the values of the velocities at half maximum. We use linear
+interpolation between histogram points to get a more precise value for
+this width.
 
- Figure \ref{fig:widthvsvelocity} shows how the FWHM increases
-with rotational velocity both for the central (continuous lines) an 
-homogeneous (dashed lines) sources, for $\theta=\pi/2$.
- We parametrize the dependency of the line width with
-$V_{\rm max}$ as
+Figure \ref{fig:widthvsmu} shows the FWHM for all models as a function
+of the viewing angle. The FWHM increases for decreasing values of
+$\mu$ increases and increasing values of $V_{\rm max}$. In Figure
+\ref{fig:widthvsvelocity} we fix $|\mu|<0.1$ and show the FWHM as a
+function of rotational velocity. For this case we parametrize the
+dependency of the line width with  $V_{\rm max}$ as
+
 \begin{equation}
@@
 is a positive scalar to be determined as a fit to the data.
-With this test we want to know
-to what extent the new velocity width can be expressed as a quadratic
-sum of the two relevant velocities in the problem. We fit
-simultaneously all the points corresponding to central and homogeneous
-models to find $\lambda_{\rm c} = 3.89 \pm 0.04$ and $\lambda_{\rm h}=
-1.98\pm 0.06$ respectively.
 
-\subsection{Peaks Positions}
+With this test we want to know to what extent the new velocity width
+can be expressed as a quadratic sum of the two relevant velocities in
+the problem. We fit simultaneously all the points corresponding to
+central and homogeneous models to find $\lambda_{\rm c} = XX \pm
+XX$ and $\lambda_{\rm h}= XX\pm XX$ respectively.
+
+\subsection{Line Maxima}
 \label{sec:peaks}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{maxima.eps}
+\end{center}
+\caption{Position of the line maxima as a function of rotational
+  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
+  central (homogeneous) source distributions. A value of $x_{\rm
+    max}=0$ indicates that line becomes single
+  peaked. \label{fig:maximumsvsvelocity}}  
+\end{figure*}
 

### 2014-04-26 paper/ms.tex
peak maxima

@@
 \subsection{Line Maxima}
-\label{sec:peaks}
+\label{sec:maxima}
 
@@
 
-In order to quantify the transition to a single peak we measure the
-position for the peak maxima as a function of the rotational
-velocity. Our results are presented in Figure
-\ref{fig:maximumsvsvelocity} where it is clear that for central
-sources there are two peaks with fixed positions as the rotational
-velocity changes, with the only exception of the model with $\tau_{\rm
-  H}=10^6$ and $V_{\rm max}=300$\kms. However, in the case of
-homogeneously emitted sources the maxima position remain fixed until
-some velocity threshold is reachd and the line becomes single peaked
-with $x_{\rm m}=0$. By inspection we find that in all cases the
-transition has occurred when the rotational velocity is larger than
-half the FWHM.
+We quantify the transition to a single peak by measuring the peak
+maxima position as a function of the viewing angle and the rotational 
+velocity. The results are presented in Figure
+\ref{fig:maximumsvsvelocity}. There are three interesting features
+that deserved attention. First For $|\mu|\sim 1.0$ and central sources
+the two peaks have the same position regardless of the rotational
+velocity. Second, in the same homogeneous models we see that for increasing
+rotational velocities the line becomes single peaked, $x_{m}\sim
+0$\kms as $|\mu|\sim 0.0$.
 

### 2014-04-29 paper/ms.tex
number of scatterings

@@
 \end{center}
-\caption{Position of the line maxima as a function of rotational
-  velocity $V_{\rm max}$. Continuous (dashed) lines correspond to
-  central (homogeneous) source distributions. A value of $x_{\rm
-    max}=0$ indicates that line becomes single
+\caption{Position of the line maxima as a function of maximum
+  rotational   velocity $V_{\rm max}$. Continuous (dashed) lines
+  correspond to   central (homogeneous) source distributions. A value
+  of $x_{\rm     max}=0$ indicates that line becomes single
   peaked. \label{fig:maximumsvsvelocity}}
@@
 
-We quantify the transition to a single peak by measuring the peak
-maxima position as a function of the viewing angle and the rotational 
-velocity. The results are presented in Figure
-\ref{fig:maximumsvsvelocity}. There are three interesting features
-that deserved attention. First For $|\mu|\sim 1.0$ and central sources
-the two peaks have the same position regardless of the rotational
-velocity. Second, in the same homogeneous models we see that for increasing
-rotational velocities the line becomes single peaked, $x_{m}\sim
-0$\kms as $|\mu|\sim 0.0$.
-
-One possible explanation for the emergence of the single peak in the
-homogeneous systems is that some photons close to the surface
-(a sort of photosphere) can escape with a low number of scatterings,
-allowing them to stay close to the line's center. Increasing the
-rotational velocity $V_{\rm max}$ reduces the optical depth making the
-photosphere region effectively larger, increasing the number of
-photons escaping close to the line's center.
-
-However, for the central emission the transition to a single peak is
-almost never completed in the range of explored parameters. The absence
-of a single peak phase could be partially explained by the absence of a
-photosphere. In this case the average number of scatterings to escape
-should remain close to constant as the rotational velocity
-increases. The rise in intensity at the line's center could instead
-mean that the scattering in a medium with bulk motion are inefficient
-in driving photons outside that frequency region.
-
-In order to explore our interpretation for these two scenarios we now 
-quantify the effect of rotation on the number of scatterings.
+We measure the peak maxima poisition to quantify the transition from
+double into single peak. We do this as a function of the viewing angle
+$\theta$ and the maximum rotational velocity. The results are
+summarized in Figure  \ref{fig:maximumsvsvelocity}. There are two
+interesting features that deserve attention. First, for a viewing angle
+parallel to the rotationa axis ($\mu\sim 1.0$) the maxima of all
+models are similar regardless of the rotational velocity. Second, at a
+viewing angle perpendicular to the rotation axis ($\mu\sim 0.0$) there
+is a good fraction of models that become single peaked, a feature that
+appears more frequently for homogeneously distributed sources when all
+the other parameters are equal.
 
@@
     to different rotational velocities for the homogeneous models.     
-    \label{fig:efvsv}} 
+    \label{fig:escape_fraction}} 
 \end{figure*}
 
-In the case of dusty clouds, all changes in the average number
-of scatterings presented in the previous subsection have a direct
-bearing on the escape fraction. From the results we have just obtained
-we can predict that for central source distributions the escape
-fraction will barely change, while larger effects should be expected
-for homogeneously distributed sources.
+We now estimate the escape fraction $f_{\rm esc}$ for the dusty models. Our main
+result is that we do not find any dependence with the viewing angle
+but there is a strong dependence with the rotational velocity for the
+homogeneous models.
 
-Left panel of Figure \ref{fig:efvsv} confirm these expectations. It shows the escape
-fraction as a function of the rotational velocity. The curves for the
-central source distribution stay flat, while for the homogeneous case
-there is a clear rise with rotational velocity.  Rotation has a higher relative impact in
-the models with low optical depth. For instance, in models with
-$\tau_{\rm H}=10^5$, the static escape fraction is $0.26$ and increases
-to $0.37$ for $V_{\rm max}=300$ \kms. Table \ref{table:escape} lists
-all the values for the escape fraction.
+The left panel in Figure \ref{fig:escape_fraction} summarizes our
+results. The left panel shows the escape fraction as a function of the
+rotational velocity. To construct this Figure we take into account all
+the photons regardless of its outgoing direction. We observe that the
+curves for the central source distribution stay flat, while for the
+homogeneous case there is a clear rise with rotational velocity.
+Rotation has a higher relative impact in the models with low optical
+depth. For instance, in models with $\tau_{\rm H}=10^5$, the static
+escape fraction is $0.26$ and increases to $0.37$ for $V_{\rm
+  max}=300$ \kms. Table \ref{table:escape} lists all the values for
+the escape fraction.
 
-In the right panel of Figure \ref{fig:efvsv} we put these results in the context of
-the analytic solution for the infinite slab \citep{Neufeld90}. In
-Neufeld's set-up the analytic solution depends uniquely on the product
-$(a\tau_{\rm   H})^{1/3}\tau_{A}$ where $\tau_{A} = (1 - A)\tau_{a}$ , an approximation 
-that is valid only in the limit $a\tau_{\rm   H}\gg 1$. The dashed lines in
- the right panel of Figure \ref{fig:efvsv} show the results for the different rotational
-velocities for the homogeneous models. First of all we note that the escape fraction does not
-increase significantly from $\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$, This
- counter-intuitive result is a consequence of the transition into the 'extremely' opaque regime,
-  which occurs roughly when $a\tau_{\rm{H}} > 10^{3}$
-  e.g. \citep{Neufeld90}.
+In the right panel of Figure \ref{fig:escape_fraction} we put these
+results in the context of the analytic solution for the infinite slab
+\citep{Neufeld90}. In Neufeld's set-up the analytic solution depends
+uniquely on the product $(a\tau_{\rm   H})^{1/3}\tau_{A}$ where
+$\tau_{A} = (1 - A)\tau_{a}$, valid only in the limit $a\tau_{\rm
+  H}\gg 1$. The dashed lines in  the right panel of Figure
+\ref{fig:escape_fraction} show the results for the different
+rotational velocities for the homogeneous models. First of all we note
+that the escape fraction does not increase significantly from
+$\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$. This
+counter-intuitive result is a consequence of the transition into the
+'extremely' opaque regime,  which occurs roughly when $a\tau_{\rm{H}}
+> 10^{3}$  e.g. \citep{Neufeld90}.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-    \includegraphics[width=0.40\textwidth]{nscattvsmu.eps}
+    \includegraphics[width=0.45\textwidth]{nscattvsmu.eps}
+    \includegraphics[width=0.45\textwidth]{f4.eps}
 \end{center}
 \caption{Logarithm of the average number of scatterings as function of
-  $\mu$. This is the general behavior for all models in particular this model
-  is for $\tau=10^{5}$ and $V_{max}=300 km/s^{-1}$. \label{fig:Nscattvsmu}}    
-\end{figure}
-
-\begin{figure}
-\begin{center}
-    \includegraphics[width=0.40\textwidth]{f4.eps}
-\end{center}
-\caption{Logarithm of the average number of scatterings as function of
-  rotational velocity. Continuous (dashed) lines represent an
-  central (homogeneous) distribution of sources. \label{fig:Nscatt}}    
-\end{figure}
+  $\mu$ (left panel) and the maximum rotational velocity $V_{\rm
+    max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
+  $V_{max}=300$\kms but this independence of the independence between
+  $N_{\rm scatt}$ and $\mu$ is kept for all models. 
+  In the right panel the continuous (dashed) lines represent an
+  central (homogeneous) distribution of sources; this shows the clear
+  decrease in the number of scatterings for the homogenously
+  distributed sources.
+\label{fig:Nscatt} }    
+\end{figure*}
 
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{f5_1.eps}
-  \includegraphics[width=0.45\textwidth]{f5_2.eps}
-  \includegraphics[width=0.45\textwidth]{f5_3.eps}
-  \includegraphics[width=0.45\textwidth]{f5_4.eps}    
+  \includegraphics[width=0.48\textwidth]{f5_1.eps}
+  \includegraphics[width=0.48\textwidth]{f5_2.eps}
+  \includegraphics[width=0.48\textwidth]{f5_3.eps}
+  \includegraphics[width=0.48\textwidth]{f5_4.eps}    
 \end{center}
@@
 
-The number of scatterings affects the escape frequency of a \ly photon.
+%% One possible explanation for the emergence of the single peak in the
+%% homogeneous systems is that some photons close to the surface
+%% (a sort of photosphere) can escape with a low number of scatterings,
+%% allowing them to stay close to the line's center. Increasing the
+%% rotational velocity $V_{\rm max}$ reduces the optical depth making the
+%% photosphere region effectively larger, increasing the number of
+%% photons escaping close to the line's center.
+
+%% However, for the central emission the transition to a single peak is
+%% harder to reach in the range of explored parameters. 
+%% In this case the average number of scatterings to escape
+%% should remain close to constant as the rotational velocity
+%% increases. The rise in intensity at the line's center could instead
+%% mean that the scattering in a medium with bulk motion are inefficient
+%% in driving photons outside that frequency region.
+
+%% In order to explore our interpretation for these two scenarios we now 
+%% quantify the effect of rotation on the number of scatterings.
+
+The number of scatterings affects the escape frequency of a \ly
+photon. Studying this quantity can help us in claryfying two results
+that we have observed for homogeneous models in the previous sections:
+the quick emergence of a single peak and the increase in the escape
+fraction.
+
+A possible explanation for these two results is that some photons
+close to the surface can escape with a low number of scatterings. This
+has a two-fold consequence: the escaping photons do not have time to
+scatter away from the line's center and also have less chances to find
+an absorbing dust grain.
+
+In Figure \ref{fig:Nscatt} we show the average number of scatterings
+$\langle N_{\rm scatt}\rangle$ as a function of the cosinus of the
+outgoing angle $|\cos\theta|$ and the rotational velocity
+$V_{\rm max}$. From the right panel observe that the number of
+scatterings and the outgoing angle are independent. This plot
+corresponds to the specific case of the central model with $\tau=10^5$ and
+$V_{\rm max}=300$\kms; but we have veryfied that this holds for all
+models. This allows us to focus to use all the photons in the
+simulations regardless of their value of $\cos\theta$.
+
+In the right panel of Figure \ref{fig:Nscatt} we observe how the
+average number of scatterings decreases for larger rotational
+velocities in the case of homogenous source distributions. For instance, for
+$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
+$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case. For
+the central source distribution the average number of scatterings
+$\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$.
+
 In static cases, a large value of the optical depth correlates with a
-high number of scatterings, increasing the probability of finding a
-\ly photon far from the line's center. As a result the peak maxima
-shifts from the center as the amount of neutral hydrogen
-increases. This can be precisely quantified in the static slab
-with central sources where the maxima position are related to
-the optical depth and the temperature as $x_{m}=\pm 1.066(a\tau_{\rm
-  H})^{1/3}$ \citep{Harrington73}. In the same model the average
+high number of scatterings.  This can be precisely quantified in the
+static slab. In this model for centrally emitted sources the average
 number of scatterings depends only on the optical depth $\langle
@@
 
-In Figure \ref{fig:Nscatt} we show the average number of scatterings
-$\langle N_{\rm scatt}\rangle$ as a function of the rotational velocity
-$V_{\rm max}$. For the central source distribution the average number of
-scatterings $\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$
-for different velocities. In this set-up the number of scatterings is
-proportional to the optical depth, with $\langle N_{\rm
+We perform a similar quantification of in our speherical setup for the
+scatic spheres. We find that for the central model the number of
+scatterings is proportional to the optical depth, with $\langle N_{\rm
   scatt}\rangle= (1.50, 1.00, 0.92)\tau_{\rm   H}$ for optical depth
 values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
+For the homogeneous static sphere we find that $\langle N_{\rm
+  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, thisrepresents
+factors of $(0.66, 0.59, 0.55)$ lower than the centrally  emitted photons.
 
-In Figure \ref{fig:Nscatt} we can see the decrease of $\langle N_{\rm
-  scatt}\rangle$ as $V_{\rm max}$ increases in the homogeneous
-source distribution. For instance, for
-$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
-$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case.
+For the homogeneous rotating sphere at  $V_{\rm{max}}=300\kms$ we find
+that $\langle N_{\rm   scatt}\rangle=(0.38, 0.34, 0.42)\tau_{\rm   H}$
+which represents   factors of $(0.26, 0.34, 0.46)$ lower than the
+corresponding central case.
 
-For the homogeneous static sphere we find that $\langle N_{\rm
-  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this
-represents factors of $(0.66, 0.59, 0.55)$ lower than the centrally
-emitted photons. While for the homogeneous rotating sphere at 
-$V_{\rm{max}}=300\kms$ we find that $\langle N_{\rm
-  scatt}\rangle=(0.38, 0.34, 0.42)\tau_{\rm   H}$ which represents 
-  factors of $(0.26, 0.34, 0.46)$ lower than the corresponding central
-  case.
-
-In order to gain a deeper understanding of these results and explain
-the results for the maxima in the line morphology we make 2D
+In order to gain a deeper understanding of these results  we make 2D
 histograms for the number of scatterings as a function of the outgoing
-dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
-such histograms in the case $\tau_{\rm H}=10^5$ for the
+dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we these 
+results in the case $\tau_{\rm H}=10^5$ for the
 static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the

### 2014-04-29 code/Finding_histograms_with_viewing_angle.py
program for make histograms taking into account the viewing angle

@@ -1,0 +1,95 @@
+import numpy as np
+import sys
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+def reading_data(filename, distribution):
+    if distribution == 0:
+        data = np.loadtxt("../data/Homogeneous/"+filename)
+    elif distribution ==1:
+        data = np.loadtxt("../data/Central/"+filename)
+    initpos=data[:,0]
+    index_clean = np.where(~np.isnan(initpos))
+    data = data[index_clean[0],:]
+    kz = data[:,5]
+    x = data[:,6]
+
+    return kz, x
+
+def viewing_angle(filename, angle, nbins, distribution):
+    kz, x = reading_data(filename, distribution)
+    index01 = np.where((abs(kz)<0.1))
+    index02 = np.where((abs(kz)<0.2) & (abs(kz)>0.1))
+    index03 = np.where((abs(kz)<0.3) & (abs(kz)>0.2))
+    index04 = np.where((abs(kz)<0.4) & (abs(kz)>0.3))
+    index05 = np.where((abs(kz)<0.5) & (abs(kz)>0.4))
+    index06 = np.where((abs(kz)<0.6) & (abs(kz)>0.5))
+    index07 = np.where((abs(kz)<0.7) & (abs(kz)>0.6))
+    index08 = np.where((abs(kz)<0.8) & (abs(kz)>0.7))
+    index09 = np.where((abs(kz)<0.9) & (abs(kz)>0.8))
+    index10 = np.where((abs(kz)<1.0) & (abs(kz)>0.9))
+
+    x01 = x[index01]
+    x02 = x[index02]
+    x03 = x[index03]
+    x04 = x[index04]
+    x05 = x[index05]
+    x06 = x[index06]
+    x07 = x[index07]
+    x08 = x[index08]
+    x09 = x[index09]
+    x10 = x[index10]
+
+    hist, bins = np.histogram(x, bins=nbins)
+    hist01, bins01 = np.histogram(x01, bins=nbins)
+    hist02, bins02 = np.histogram(x02, bins=nbins)
+    hist03, bins03 = np.histogram(x03, bins=nbins)
+    hist04, bins04 = np.histogram(x04, bins=nbins)
+    hist05, bins05 = np.histogram(x05, bins=nbins)
+    hist06, bins06 = np.histogram(x06, bins=nbins)
+    hist07, bins07 = np.histogram(x07, bins=nbins)
+    hist08, bins08 = np.histogram(x08, bins=nbins)
[…]

### 2014-04-29 code/Finding_histograms_with_viewing_angle.py
Figure3 and minor updates

@@ -40,16 +40,16 @@ def viewing_angle(filename, angle, nbins, distribution):
     x09 = x[index09]
     x10 = x[index10]
 
-    hist, bins = np.histogram(x, bins=nbins)
-    hist01, bins01 = np.histogram(x01, bins=nbins)
-    hist02, bins02 = np.histogram(x02, bins=nbins)
-    hist03, bins03 = np.histogram(x03, bins=nbins)
-    hist04, bins04 = np.histogram(x04, bins=nbins)
-    hist05, bins05 = np.histogram(x05, bins=nbins)
-    hist06, bins06 = np.histogram(x06, bins=nbins)
-    hist07, bins07 = np.histogram(x07, bins=nbins)
-    hist08, bins08 = np.histogram(x08, bins=nbins)
-    hist09, bins09 = np.histogram(x09, bins=nbins)
+    hist, bins = np.histogram(x, bins=nbins, normed=True)
+    hist01, bins01 = np.histogram(x01, bins=nbins, normed=True)
+    hist02, bins02 = np.histogram(x02, bins=nbins, normed=True)
+    hist03, bins03 = np.histogram(x03, bins=nbins, normed=True)
+    hist04, bins04 = np.histogram(x04, bins=nbins, normed=True)
+    hist05, bins05 = np.histogram(x05, bins=nbins, normed=True)
+    hist06, bins06 = np.histogram(x06, bins=nbins, normed=True)
+    hist07, bins07 = np.histogram(x07, bins=nbins, normed=True)
+    hist08, bins08 = np.histogram(x08, bins=nbins, normed=True)
+    hist09, bins09 = np.histogram(x09, bins=nbins, normed=True)
 
     if angle == 1:
         for i in range(len(hist)):

### 2014-05-01 code/New_widths_and_Maxima.py
x_{m} & km\ s^{-1}

@@ -126,5 +126,7 @@ if mode == 0:
 	widths(filename, angle, bins, distribution)
 if mode == 1:
 	maxima(filename, angle, bins, distribution)
+if mode == 2:
+	viewing_angle(filename, angle, bins, distribution)
 
 

### 2014-05-01 code/Escape_fraciton.py
generalized escape fraction code

@@ -1,0 +1,126 @@
+import numpy as np
+import sys
+import matplotlib.pyplot as plt
+from scipy.interpolate import interp1d
+
+def reading_data(filename, distribution):
+    if distribution == 0:
+	data = np.loadtxt("../data/Homogeneous/"+filename)
+    elif distribution ==1:
+        data = np.loadtxt("../data/Central/"+filename)
+    initpos=data[:,0]	    
+    index_clean = np.where(~np.isnan(initpos))
+    data = data[index_clean[0],:]
+    kz = data[:,5]
+    nscatt = data[:,6]
+
+    return kz, nscatt
+
+def viewing_angle(filename, angle, distribution):
+    kz, nscatt = reading_data(filename, distribution)
+    index01 = np.where((abs(kz)<0.1))
+    index02 = np.where((abs(kz)<0.2) & (abs(kz)>0.1))
+    index03 = np.where((abs(kz)<0.3) & (abs(kz)>0.2))
+    index04 = np.where((abs(kz)<0.4) & (abs(kz)>0.3))
+    index05 = np.where((abs(kz)<0.5) & (abs(kz)>0.4))
+    index06 = np.where((abs(kz)<0.6) & (abs(kz)>0.5))
+    index07 = np.where((abs(kz)<0.7) & (abs(kz)>0.6))
+    index08 = np.where((abs(kz)<0.8) & (abs(kz)>0.7))
+    index09 = np.where((abs(kz)<0.9) & (abs(kz)>0.8))
+    index10 = np.where((abs(kz)<1.0) & (abs(kz)>0.9))
+    
+    nscatt01 = nscatt[index01]
+    x1 = float(len(nscatt01))
+    index = np.where(nscatt01==0)
+    x2 = float(len(nscatt01[index]))
+    ef01 = x2/x1 
+
+    nscatt02 = x[index02]
+    x1 = float(len(nscatt02))
+    index = np.where(nscatt02==0)
+    x2 = float(len(nscatt02[index]))
+    ef02 = x2/x1
+
+    nscatt03 = x[index03]
+    x1 = float(len(nscatt03))
+    index = np.where(nscatt03==0)
+    x2 = float(len(nscatt03[index]))
+    ef03 = x2/x1
+
+    nscatt04 = x[index04]
+    x1 = float(len(nscatt04))
+    index = np.where(nscatt04==0)
+    x2 = float(len(nscatt04[index]))
+    ef04 = x2/x1
+
+    nscatt05 = x[index05]
[…]

### 2014-05-01 code/Escape_fraciton.py
generalized escape fraction code

@@ -123,4 +123,4 @@ def viewing_angle(filename, angle, distribution):
 
 filename = sys.argv[1]
 angle = float(sys.argv[2])
-distribution = float(sys.argv[5])
+distribution = float(sys.argv[3])

### 2014-05-01 code/Escape_fraciton.py
Escape fraction plot for the referee

@@ -12,7 +12,7 @@ def reading_data(filename, distribution):
     index_clean = np.where(~np.isnan(initpos))
     data = data[index_clean[0],:]
     kz = data[:,5]
-    nscatt = data[:,6]
+    nscatt = data[:,7]
 
     return kz, nscatt
 
@@ -35,64 +35,62 @@ def viewing_angle(filename, angle, distribution):
     x2 = float(len(nscatt01[index]))
     ef01 = x2/x1 
 
-    nscatt02 = x[index02]
+    nscatt02 = nscatt[index02]
     x1 = float(len(nscatt02))
     index = np.where(nscatt02==0)
     x2 = float(len(nscatt02[index]))
     ef02 = x2/x1
 
-    nscatt03 = x[index03]
+    nscatt03 = nscatt[index03]
     x1 = float(len(nscatt03))
     index = np.where(nscatt03==0)
     x2 = float(len(nscatt03[index]))
     ef03 = x2/x1
 
-    nscatt04 = x[index04]
+    nscatt04 = nscatt[index04]
     x1 = float(len(nscatt04))
     index = np.where(nscatt04==0)
     x2 = float(len(nscatt04[index]))
     ef04 = x2/x1
 
-    nscatt05 = x[index05]
+    nscatt05 = nscatt[index05]
     x1 = float(len(nscatt05))
     index = np.where(nscatt05==0)
     x2 = float(len(nscatt05[index]))
     ef05 = x2/x1
 
-    nscatt06 = x[index06]
+    nscatt06 = nscatt[index06]
     x1 = float(len(nscatt06))
     index = np.where(nscatt06==0)
     x2 = float(len(nscatt06[index]))
     ef06 = x2/x1
     
-    nscatt07 = x[index07]
+    nscatt07 = nscatt[index07]
     x1 = float(len(nscatt07))
     index = np.where(nscatt07==0)
     x2 = float(len(nscatt07[index]))
     ef07 = x2/x1
 
-    nscatt08 = x[index08]
+    nscatt08 = nscatt[index08]
     x1 = float(len(nscatt08))
     index = np.where(nscatt08==0)
     x2 = float(len(nscatt08[index]))
     ef08 = x2/x1
 
-    nscatt09 = x[index09]
+    nscatt09 = nscatt[index09]
     x1 = float(len(nscatt09))
     index = np.where(nscatt09==0)
     x2 = float(len(nscatt09[index]))
     ef09 = x2/x1
 
-    nscatt10 = x[index10]
[…]

### 2014-05-01 paper/ms.tex
Lambda values

@@
 \usepackage[dvips]{epsfig}
-
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 \begin{center}
-  \includegraphics[width=0.4\textwidth]{f8.eps}
+  \includegraphics[width=0.4\textwidth]{f1.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{spectraCentral.eps}
+  \includegraphics[width=0.95\textwidth]{f2.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{spectraHOM.eps}
+  \includegraphics[width=0.95\textwidth]{f3.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{f1.eps}
+  \includegraphics[width=0.95\textwidth]{f4.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.4\textwidth]{muhisto.eps}
+  \includegraphics[width=0.4\textwidth]{f5.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{widths.eps}
+  \includegraphics[width=0.95\textwidth]{f6.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{f2.eps}
+  \includegraphics[width=0.95\textwidth]{f7.pdf}
 \end{center}
@@
 the problem. We fit simultaneously all the points corresponding to
-central and homogeneous models to find $\lambda_{\rm c} = XX \pm
-XX$ and $\lambda_{\rm h}= XX\pm XX$ respectively.
+central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
+XX$ and $\lambda_{\rm h}= 0.54\pm XX$ respectively.
 
@@
 \begin{center}
-  \includegraphics[width=0.95\textwidth]{maxima.eps}
+  \includegraphics[width=0.95\textwidth]{f8.pdf}
 \end{center}

### 2014-05-15 paper/ms.tex
Conclusions uodated

@@
 broadening. We measure this width from the velocity histogram by
-finding the values of the velocities at half maximum. We use linear
+finding the values of the velocities at half maximum. We use lineal
 interpolation between histogram points to get a more precise value for
@@
 
-We measure the peak maxima poisition to quantify the transition from
+We measure the peak maxima position to quantify the transition from
 double into single peak. We do this as a function of the viewing angle
@@
 interesting features that deserve attention. First, for a viewing angle
-parallel to the rotationa axis ($\mu\sim 1.0$) the maxima of all
+parallel to the rotational axis ($\mu\sim 1.0$) the maxima of all
 models are similar regardless of the rotational velocity. Second, at a
@@
 average number of scatterings decreases for larger rotational
-velocities in the case of homogenous source distributions. For instance, for
+velocities in the case of homogeneous source distributions. For instance, for
 $\tau_{\rm H}=10^5$ the average number of scatterings decreases by
@@
 For the homogeneous static sphere we find that $\langle N_{\rm
-  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, thisrepresents
+  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents
 factors of $(0.66, 0.59, 0.55)$ lower than the centrally  emitted photons.
@@
 Our main result is that rotation clearly impacts the \ly line
-morphology. Double peaked lines can make transitions into single
-peaked lines as the rotational velocity increases. In the case of
-off-centered emission we obtain triple peaked lines for certain
-values of optical depth and rotational velocities.
+morphology. The morphology of the observed spectra for observers at different
+viewing angle $\theta$ changes while the flux remains constant for all $\theta$,
+for $\mu \sim 1$ double peaked lines can make transitions into single
+peaked lines as the rotational velocity increases.
 
@@
 
-\item In spite of the asymmetry induced by rotation the spatial
-  anisotropy in the emission is usually below the
-  $10\%$ level. This justifies our consideration of angle-averaged
-  effects to quantify the emission line of rotating clouds.
+\item Rotation induce a considerable asymmetry in the morphology 
+ of the spectra when the viewing angle $\theta$. This occurs for
+ all of our models, in particular models with $\mu\sim 1$ i.e for 
+ observes aligned with the axis of rotation the rotation does not 
+ produce a significance effect while for $\mu\sim 0$ the effect in 
+ the FWHM, and Maxima is significant and the number of scatterings.
 
-\item The line width increases with rotational velocity. The line width
+%\item In spite of the asymmetry induced by rotation the spatial
+%  anisotropy in the emission is usually below the
+%  $10\%$ level. This justifies our consideration of angle-averaged
+%  effects to quantify the emission line of rotating clouds.
+
+\item For $\mu \sim 0$ The line width increases with rotational velocity. The line width
   approximately follows the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
@@
   width for the static case and $\lambda$ is a constant determined from
-  the radiative transfer results it is $\lambda_{\rm c}=3.89\pm0.04$ and
-  $\lambda_{\rm h}=1.98\pm0.06$ for the central and homogeneous source
+  the radiative transfer results it is $\lambda_{\rm c}=XX \pm XX$ and
+  $\lambda_{\rm h}=XX\pm XX$ for the central and homogeneous source
   distribution, respectively.
@@
   the case of homogeneously distributed sources. These cases occur when
-  the rotational velocity is larger than half FWHM$_0$.
+  the rotational velocity is larger than half FWHM$_0$ and $\mu\sim 0$.
 
@@
 
-Comparing our results with recent observed LAEs we find that many 
-morphological features such as high central line flux, single peak
-profiles  could be explained by gas bulk  rotation present in these
-LAEs.
+%Comparing our results with recent observed LAEs we find that many 
+%morphological features such as high central line flux, single peak
+%profiles  could be explained by gas bulk  rotation present in these
+%LAEs.
 

### 2014-05-15 paper/ms.tex
lamda errors

@@
 central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
-XX$ and $\lambda_{\rm h}= 0.54\pm XX$ respectively.
+0.06$ and $\lambda_{\rm h}= 0.54\pm 0.1$ respectively.
 
@@
   width for the static case and $\lambda$ is a constant determined from
-  the radiative transfer results it is $\lambda_{\rm c}=XX \pm XX$ and
-  $\lambda_{\rm h}=XX\pm XX$ for the central and homogeneous source
+  the radiative transfer results it is $\lambda_{\rm c}=0.84 \pm 0.06$ and
+  $\lambda_{\rm h}=0.54\pm 0.1$ for the central and homogeneous source
   distribution, respectively.

### 2014-05-22 paper/ms.tex
paragraph on verhamme

@@
 Gas bulk rotation has a noticeable effect on the morphology of the
- \ly line. In this section we discuss the implications of these
- findings for the interpretation of available observational data.
+ \ly line. In this section we compare our findings to other
+ computational results and discuss the implications of these finding
+ in the interpretation of observational data.
+
+\cite{Verhamme12} studied \lya using two high resolution simulations
+of individual galaxies. The main purpose of the study was to asses the
+impact of two different InterStellar Medium (ISM) prescriptions. However, each simulated
+galaxy had a disc structure with a clear rotation pattern in the ISM
+and inflowing gas int the circum-galactic region. The configuration
+had an axial symmetry and they reported a strong dependence of the
+escape fraction and the total line intensity as a function of the
+$\theta$ angle. In our results, none of these two quantities has a
+dependence either on the inclination angle or the rotational
+velocity. Therefore, the effect reported by \cite{Verhamme} is
+consistent to the different hydrogen optical depth for different
+viewing angles and not as an effect of the bulk rotation.
 

### 2014-05-22 paper/ms.tex
conclusions

@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f2.pdf}
+\end{center}
+\caption{
+2D histogram showing the number of photons that escape with frecuency
+$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
+rotationa axis. The rotational velocity ($0,100,200,300$\kms)
+increases from left to right and the optical depth ($10^5$, $10^6$,
+$10^7$) from top to bottom. The \ly photons are initialized at the
+center of the sphere.
+\label{fig:CentralSpec} }   
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f3.pdf}
+\end{center}
+\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
+  initialized homogeneously throughout the sphere.
+    \label{fig:HomSpec}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f4.pdf}
+\end{center}
+\caption{Shape of the \ly line for different maximum rotational
+  velocities for a viewing angle perpendicular to the rotation axis
+  ($|\mu|\sim 0$). The continuous (dashed) line represents the central
+  (homogeneous) source distributions.  The panels follow the same
+  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
+    \label{fig:differentvelocities}}  
+\end{figure*}
+
 \subsection{Brief Description of the Radiative Transfer Codes}
@@
 \end{table}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.95\textwidth]{f2.pdf}
-\end{center}
-\caption{
-2D histogram showing the number of photons that escape with frecuency
-$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
-rotationa axis. The rotational velocity ($0,100,200,300$\kms)
-increases from left to right and the optical depth ($10^5$, $10^6$,
-$10^7$) from top to bottom. The \ly photons are initialized at the
-center of the sphere.
-\label{fig:CentralSpec} }   
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.95\textwidth]{f3.pdf}
-\end{center}
-\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
-  initialized homogeneously throughout the sphere.
-    \label{fig:HomSpec}}  
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.95\textwidth]{f4.pdf}
-\end{center}
-\caption{Shape of the \ly line for different maximum rotational
-  velocities for a viewing angle perpendicular to the rotation axis
-  ($|\mu|\sim 0$). The continuous (dashed) line represents the central
-  (homogeneous) source distributions.  The panels follow the same
-  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
-    \label{fig:differentvelocities}}  
-\end{figure*}
 
@@
 
-\cite{Verhamme12} studied \lya using two high resolution simulations
+\cite{Verhamme12} studied \ly using two high resolution simulations
 of individual galaxies. The main purpose of the study was to asses the
@@
 dependence either on the inclination angle or the rotational
-velocity. Therefore, the effect reported by \cite{Verhamme} is
-consistent to the different hydrogen optical depth for different
-viewing angles and not as an effect of the bulk rotation.
+velocity. Therefore, the effect reported by \cite{Verhamme12} is
+consistent with being a consequence of the different hydrogen optical
+depth for different viewing angles and not as an effect of the bulk
+rotation.
 
@@
 the pool of possible bulk flows responsible for that feature,
-specially if the two peaks have similar intensities. The case of
-triple peaked lines is another clear feature of gas rotation under the
-additional condition of an off-centered emission.
+specially if the two peaks have similar intensities. This highlights
+that in order to interpret the observations of \ly emitting galaxies
+it is necessary to consider the possible effect of different
+inclination angles along the line of sight.
 
@@
 This paper quantifies for the first time in the literature the effects
-of rotation in the morphology of the \ly emission line in star forming
+of gas rotation in the morphology of the \ly emission line in star forming
 galaxies.  The results are based on the study of an homogeneous sphere
@@
 
-Our main result is that rotation clearly impacts the \ly line
-morphology. The morphology of the observed spectra for observers at different
-viewing angle $\theta$ changes while the flux remains constant for all $\theta$,
-for $\mu \sim 1$ double peaked lines can make transitions into single
-peaked lines as the rotational velocity increases.
+Our main result is two-fold. First,rotation clearly impacts the \ly line
+morphology. Second, rotation introduces an anisotropy for different
+viewing angles. For viewing angles close to the poles the line is
+double peaked and it makes a transition to a single peaked line for
+high rotational velocities and viewing angles along the equator. This
+trend is stronger for spheres with homogeneusly distributed radiation
+sources.  In contrast, the total flux in the line remains independent
+of the viewing angle.
 
-Quantitatively the main results of our study are summarized as follows.
+The escape fraction remains constant for diffenret viewing angles only
+in the case of centrally distributed sources. In contrast, for an homogeneous
+distribution the escape fraction decreases with high rotation 
+fraction remain constant for different viewing angles. We showed that
+these results can be interpreted in terms of the average number of
+scatterings for the photons, a quantity that also remains constant
+independent of the viewing angle and the rotational velocity for
+centrally distributed sources and decreases for homogenously
+distributed source.
+
+Quantitatively the main results of our study are summarized as
+follows.
 
@@
 
-\item Rotation induce a considerable asymmetry in the morphology 
+\item Rotation induces a considerable asymmetry in the morphology 
  of the spectra when the viewing angle $\theta$. This occurs for
- all of our models, in particular models with $\mu\sim 1$ i.e for 
- observes aligned with the axis of rotation the rotation does not 
- produce a significance effect while for $\mu\sim 0$ the effect in 
- the FWHM, and Maxima is significant and the number of scatterings.
-
-%\item In spite of the asymmetry induced by rotation the spatial
-%  anisotropy in the emission is usually below the
-%  $10\%$ level. This justifies our consideration of angle-averaged
-%  effects to quantify the emission line of rotating clouds.
+ all of our models. The asymmetry is such that observeds with
+ $\cos\theta\equiv \mu\sim 1$, i.e. observes aligned with the rotation
+ axis, the line is double peaked while for $\mu\sim 0$ and high
+ rotation veolcities the linebecomes double peaked.
 
@@
   the radiative transfer results it is $\lambda_{\rm c}=0.84 \pm 0.06$ and
-  $\lambda_{\rm h}=0.54\pm 0.1$ for the central and homogeneous source
+  $\lambda_{\rm h}=0.54\pm 0.10$ for the central and homogeneous source
   distribution, respectively.
@@
   the case of homogeneously distributed sources. These cases occur when
-  the rotational velocity is larger than half FWHM$_0$ and $\mu\sim 0$.
+  the rotational velocity is larger than half FWHM$_0$ and $\mu\sim 1$.
 
-\item For central sources we find that the number of scatterings
-does not significantly decrease with rotation. This is due to the 
+\item 
+For central sources we find that the escape fraction does not change
+with rotational velocity nor with the viewing angle. We interpret this
+in terms of the average number of scatterings which does not
+significantly changes with rotation. This is due to the  
   fact that the vast majority of scatterings events are resonant, 
   during which the mean free path is very short and the effect of gas
-bulk rotation is not enough to affect \ly photons. In consequence, 
-the escape fraction neither the position of the peaks depends on the
-rotational velocity. However, there is a flux increase with rotational
-velocity in the central parts of the line.
+  bulk rotation is not enough to affect \ly photons.
 
-\item For homogeneous sources we find that the changes in the
-line morphology are linked to the reduction in the average number of
-scatterings. In the second part of \S \ref{sec:widthpeak} we show
-that, as rotational velocity increases, a large fraction of photons
-escape with less than $10$ scatterings. The average number of
-scatterings decreases a $40\%$ compared to the static case. 
-This reduction in the number of scatterings decreases the probability
-for a photon to move away from the line's center. This is also
-translated into an increase of the escape fraction by a factor of
-$\sim 2$ with respect to the static situation.
+\item For homogeneous sources we find that the  as rotational velocity
+  increases, the escape fraction rises by a factor of $\sim 2$ with
+  respect to the static situation. We also interpret this change in
+  terms of the average number of scatterings. In the second part of \S
+  \ref{sec:widthpeak} we show that the average number of scatterings
+  decreases a $40\%$ compared to the static case, while a large
+  fraction of photons escape with less than $10$ scatterings.
 
@@
 
-%Comparing our results with recent observed LAEs we find that many 
-%morphological features such as high central line flux, single peak
-%profiles  could be explained by gas bulk  rotation present in these
-%LAEs.
+Comparing our results with recent observed LAEs we find that many 
+morphological features such as high central line flux, single peak
+profiles  could be explained by gas bulk  rotation present in these
+LAEs.
 

### 2014-05-26 paper/ms.tex
Constant flux in the line

@@
 
+Another important issue is the \ly flux, in several systems correlation
+between the \ly flux and properties such as the peak shift has been found
+ (cites), in our study we don't find this correlation mainly because the flux remain 
+ constant for all the rotational velocities and because the flux of the line
+ is independent of the viewing angle. This last feature is shown in 
+ Fig.\ref{fig:muhisto} when clearly is seen that the flux of the line
+ does not change with the viewing angle $\theta$ as it does in systems with
+ anisotropic \ly emission \citep{Zheng2013} and most recently in
+  Outflow-Driven Cavities \citep{Behrens2014}.
+
 \section{Conclusions}

### 2014-05-26 paper/ms.tex
typos in conclusions

@@
 high rotational velocities and viewing angles along the equator. This
-trend is stronger for spheres with homogeneusly distributed radiation
+trend is stronger for spheres with homogeneously distributed radiation
 sources.  In contrast, the total flux in the line remains independent
@@
 
-The escape fraction remains constant for diffenret viewing angles only
+The escape fraction remains constant for different viewing angles only
 in the case of centrally distributed sources. In contrast, for an homogeneous
@@
 independent of the viewing angle and the rotational velocity for
-centrally distributed sources and decreases for homogenously
+centrally distributed sources and decreases for homogeneously
 distributed source.
@@
  of the spectra when the viewing angle $\theta$. This occurs for
- all of our models. The asymmetry is such that observeds with
+ all of our models. The asymmetry is such that observers with
  $\cos\theta\equiv \mu\sim 1$, i.e. observes aligned with the rotation
  axis, the line is double peaked while for $\mu\sim 0$ and high
- rotation veolcities the linebecomes double peaked.
+ rotation velocities the line becomes double peaked.
 

### 2014-05-26 paper/referee-reply.tex
update referee reply
Update in the refereee response, Viewing angle dependency

@@
 \maketitle
+
+\section{Global Comments}
+
+\subsection{Variation with the viewing angle}
+
+The problematic of anisotropy is only studied from Sect3.4, the former sections consider global quantities (spectral shapes, escape fractions, etc...).
+This is ok only if there is NO anisotropy induced by rotation, which is not obvious, a priori.
+You should make it clear from the beginning, telling that you will investigate anisotropy at the end of the paper only, because you checked that lya properties are isotropic, at least in the range of parameters that you investigated so far.\\
+
+\textbf{ We have decide to study in this paper the case in which there is No anisotropy. The part concerning the off-center emission is going to be presented in a later study\\}
+
+As explained in sect 3.4, rotation kills the spherical symmetry of your problem, and the rotation axis defines a preferential direction.
+We could expect some variation of the emerging flux, the lyman-alpha escape fraction, and the spectral shape, with viewing angle.
+From Fig8, it seems that the flux is the same in all directions for spherical distributions of sources.
+This important result is not enough emphasized.\\
+
+\textbf{We do not find the flux variation with the viewing angle and now as highlighted in the new text we emphasize more this new result, also we made a new plot Figure 5 in the paper, showing this results for both distributions (homogeneous/central) and for optical depth $\tau_{H}=10^{5}$ we choose these models because this are the ones
+that are more sensitive to rotation.\\}
+
+Do you see any difference in the spectral shape with viewing angle ?
+To illustrate this point, it would be interesting to build a 2D plot as you did on Fig 5, but replace Nb scat in ordinates by the viewing angle μ.
+We could immediatly see if there is an evolution of the shape with viewing angle or not.
+If you find NO evolution of the Lya shape with viewing angle, I think that it is an interesting counter-intuitive result, that you should advertise more.\\
+
+\textbf{Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
+We have restructure the paper this new plots now correspond to figure 1 & 2 in the paper.
+Also we emphasize this results in the results, discussion and conclusion sections.\\}
+
+What about the variation of lya escape fraction with viewing angle ?
+I propose that in the beginning of Sect.3 Results, you first emphasize that, maybe counter-intuitively, you did not find any variation of the Lya properties with viewing angle, so you will present first angle average lya properties, and you will come back to the anisotropy problematic only at the end on the paper.\\
+
+\textbf{As escape fraction depends on the number of scatterings and this is invariant for different viewing angles the escape fraction does not change with the viewing angle.
+(MAKE A PLOT AND EXPLAIN THIS BETTER)
+}
 
@@
 \subsection*{Fig5}
+\begin{figure}
+\includegraphics[scale=0.4]{Histogram2dNscattVSRadius.png}
+\end{figure}
 

### 2014-05-26 paper/referee-reply.tex
Update in the refereee response, Viewing angle dependency

@@
 \textbf{Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
-We have restructure the paper this new plots now correspond to figure 1 & 2 in the paper.
+We have restructure the paper this new plots now correspond to figure 2 & 3 in the paper.
 Also we emphasize this results in the results, discussion and conclusion sections.\\}
@@
 
-This changes were performed.
+With Orsi et al 2012, please cite also Garel et al 2012. With Zheng&Wallace 2013, please cite also Behrens et al 2014.\\
 
+\textit{This changes were performed.}
 \subsection*{Fig.1}
+
+I guess that the spectra presented in Fig1 are integrated over all directions, right ?
+You should describe explicitly how you build them.
+You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.\\
+
+\textbf{Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency.}
 
@@
 
-Explanation (Done)\\
-We don't fit a gaussian , we measure the width by finding
-the closest points to the half maximum in our histogram numerically.
+Fig.2 Can you explain how you measure the FWHM of a double-peaked profile ? Do you fit it with a gaussian ?
+
+We don't fit a gaussian, we interpolate points to the line profile and then  we measure the width by finding
+the closest points to the half maximum in our histogram.
 

### 2014-05-27 paper/referee-reply.tex
Referee reply update

@@
 \maketitle
+
+Dear referee the main changes in our paper are that we do find
 
@@
 \textbf{We do not find the flux variation with the viewing angle and now as highlighted in the new text we emphasize more this new result, also we made a new plot Figure 5 in the paper, showing this results for both distributions (homogeneous/central) and for optical depth $\tau_{H}=10^{5}$ we choose these models because this are the ones
-that are more sensitive to rotation.\\}
+that are more sensitive to rotation.}\\
 
-Do you see any difference in the spectral shape with viewing angle ?
-To illustrate this point, it would be interesting to build a 2D plot as you did on Fig 5, but replace Nb scat in ordinates by the viewing angle μ.
+Do you see any difference in the spectral shape with viewing angle?
+To illustrate this point, it would be interesting to build a 2D plot as you did on Fig 5, but replace Nb scat in ordinates by the viewing angle $\mu$.
 We could immediatly see if there is an evolution of the shape with viewing angle or not.
@@
 \textbf{Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
-We have restructure the paper this new plots now correspond to figure 2 & 3 in the paper.
+We have restructure the paper this new plots now correspond to figure 2 \& 3 in the paper.
 Also we emphasize this results in the results, discussion and conclusion sections.\\}
@@
 
-With Orsi et al 2012, please cite also Garel et al 2012. With Zheng&Wallace 2013, please cite also Behrens et al 2014.\\
+With Orsi et al 2012, please cite also Garel et al 2012. With Zheng \& Wallace 2013, please cite also Behrens et al 2014.\\
 
@@
 
+Do you have an idea why the (central source, intermediate optical depth) case with Vmax=300 has a single plateau instead of 2 peaks ? Do you find this with the two codes ?
+
 \subsection*{Fig4 and 6}
 
-Waiting for the cluster in germany!
+This is a surprising result that the number of scatterings (escape fraction) stays constant as the rotation velocity increases, for a central source, whereas the global spectral shape is altered.
+Did you try with higher/extreme values of Vmax (=1000 km/s, even if not physically motivated) ?
+Do you believe that the number of scatterings decreases with very high values, or that it is independant of the rotation velocity ?
+Is the escape fraction from a dusty rotating cloud with central source independant of the rotation velocity ?
 
 \subsection*{Fig5}
+This is a very nice figure !
+Looking at the top right panel, with its “photosphere”, I’m surprised that the distribution of Nscatt is bipolar, I would have expected a smooth transition between the 2 regimes.
+Do you have a physical explanation why photons escape after either (less than 10) or (more than 1000) scatterings, and none escape with 100 scatt ?
+To test the ’photosphere’ assumption, you could also do the radiation transfer in a cloud with the distribution of sources only in an inner sphere, and another experienment with sources only in an outer shell.
+If I understood corectly, you would expect thant the bottom spot on the top right panel is made of photons from the outer shell, and the uppper spot from photons emitted inside the cloud.
+
 \begin{figure}
@@
 
+\subsection*{End of paragraph 3.3}
+
+One sentence is not clear : we see that the escape fraction does not increase significantly from $\tau$ = 105 to $\tau = 10^{6}$.
+This counter-intuitive result....
+It sounds like you were expecting a strong increase...
+A decrease is expected from $\tau$ = 105 to $\tau$ = 106, not an increase, but indeed on the graphe we can see an unexpected (small) increase.
+I do not understand the explanation for this behaviour.
+(Mark)
+
+\subsection*{Fig8}
+
+Referred to as Figure 7 in the text (paragraph 3.4).
+To my mind, this figure illustrates the main result of your study, it has to be more demonstrative.
+On this figure, the numerical noise seems very big compare to the small number of bins, bigger than on the spectra from Fig1, how is it possible ?
+Could you re-do this figure with more photons, maybe with more bins ?
+Could you plot an histogram instead of broken lines, to ease the reading ?
+In the text, you write anisotropy induced by rotation is at the 3$\%$ level, how do to estimate this number?
+I think that the noise is at $3\%$ level, and the distribution is compatible with ’flat’.
+In the corresponding text, you first say that $F(\mu)$ does not depend on Vmax.
+Again, if real, this is an important result, that you must advertise more.
+Please show it on this Fig, by comparing F(μ) without rotation (in red, for example) to the other distributions that you get with different values of Vmax.
+Then, you mention that for high optical depth values, $F(\mu)$ (not the variations of $\mu$) can vary up to $15\%$.
+First, what do you call high optical depth ?
+your highest setup is τ = 107, not extremely high for lyman alpha ”standards’, corresponding to NHI ∼ 1020 cm−2.
+So, if you see a trend with optical depth, I encourage you to check higher optical depth regimes, corresponding better to galaxy scales.
+If you can probe that anisotropy induced by rotation is rising with optical depth, this would be an interesting result.
+If higher optical depth regimes lead to anisotropic escape, could you check the effet of anisotropy on the lya spectral shape ?
+
 \end{document}

### 2014-05-30 paper/ms.tex
revised abstract, conclusions and figure captions

--- 2014-05-26 paper/ms.tex
@@
 Our main result is that rotation introduces a dependence of the
-line morphology with  viewing angle. Observations parallel to the
-rotation axis yield lines similar to the static case. The greatest
-difference is observed perpendicular to the rotation axis where the
-intensity at the line center increases with rotational velocity.  For
+line morphology with  viewing angle. Observations with a line of sight
+parallel to the rotation axis yield line morphologies similar to the
+static case. The greatest difference is observed for lines of sight
+perpendicular to the rotation axis. In this case the intensity at the line
+center increases and the line width increase with rotational velocity.  For
 homogeneously distributed sources the line becomes single peaked  at
@@
 case. However, rotation does not not induce any significant anisotropy
-in the total line intensity or in the escape fraction. 
+in the total line intensity nor in the escape fraction. 
 \end{abstract}
@@
   $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
-  report to present our results.
+  report to present our results. Computing the spectra for photons in
+  a   narrow range of $\mu$ is equivalent to having a line-of-sight
+  oriented in that direction.  
     \label{fig:geometry}}  
@@
 2D histogram showing the number of photons that escape with frecuency
-$x$ forming an angle $\theta$ (parameterized as $\cos\theta$) with the
-rotationa axis. The rotational velocity ($0,100,200,300$\kms)
+$x$ forming an angle $\theta$ (parameterized as $|\cos\theta|$) with the
+rotation axis. The rotational velocity ($0,100,200,300$\kms)
 increases from left to right and the optical depth ($10^5$, $10^6$,
@@
 \caption{Shape of the \ly line for different maximum rotational
-  velocities for a viewing angle perpendicular to the rotation axis
+  velocities for a LoS perpendicular to the rotation axis
   ($|\mu|\sim 0$). The continuous (dashed) line represents the central
   (homogeneous) source distributions.  The panels follow the same
-  correspondence as Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
+  distribution as in Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
     \label{fig:differentvelocities}}  
@@
 \end{center}
-\caption{Integrated flux distribution, $F(\mu)$, as a function of the
+\caption{Integrated flux distribution as a function of the
   viewing angle as parameterized by $\mu$. We show the results for the
   homogeneous source distribution in models with rotational velocities
-  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$. We
-  see that the distribution is flat, meaning that the flux for all
+  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$.
+  The distributions are flat, meaning that the integrated flux for all
   viewing angles is the same. The results for the central sources are
@@
   \caption{FWHM for the non-dusty models as a function of the viewing
-  angle parameterized by $\mu\equiv\cos\theta$. 
-  Continuous (dashed) lines  correspond to central (homogeneous)
-  source distributions. The general trend is of an decreasing FWHM as
-  the line of sight becomes parallel to the rotation axis. 
+  angle parameterized by $|\cos\theta|$. Continuous (dashed) lines  correspond
+  to central (homogeneous) source distributions. The general trend is
+  of an decreasing line width as the line of sight becomes parallel to the
+  rotation axis.
   \label{fig:widthvsmu}} 
@@
     max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
-  $V_{max}=300$\kms but this independence of the independence between
-  $N_{\rm scatt}$ and $\mu$ is kept for all models. 
+  $V_{max}=300$\kms as a function of $|\cos\theta|$; the independence of
+  $N_{\rm scatt}$ with $\mu$ is present in all models. 
   In the right panel the continuous (dashed) lines represent an
-  central (homogeneous) distribution of sources; this shows the clear
+  central (homogeneous) distribution of sources; there is a clear
   decrease in the number of scatterings for the homogenously
@@
       number of photons with given values of $N_{\rm scatt}$ and
-      $x$. \label{fig:Nscatt2D}}   
+      $x$. \label{fig:Nscatt2D}. A results that stands out is in the upper
+      right panel, showing that in homogeneously distributed sources a
+      large number of photons can escape escape after a few
+      scatterings, $N_{\rm scatt}<10$.}   
 \end{figure*}
@@
 
-This paper quantifies for the first time in the literature the effects
-of gas rotation in the morphology of the \ly emission line in star forming
-galaxies.  The results are based on the study of an homogeneous sphere
+In this paper we quantified for the first time in the literature the effects
+of gas bulk rotation in the morphology of the \ly emission line in star forming
+galaxies.  Our results are based on the study of an homogeneous sphere
 of gas with solid body rotation. We explore a range of models by varying
@@
 initial distribution of \ly photons with respect to the gas
-density. As a cross-validation, we obtain our results from two
+density. As a cross-validation, we obtained our results from two
 independently developed Monte-Carlo radiative transfer codes.
 
-Our main result is two-fold. First,rotation clearly impacts the \ly line
-morphology. Second, rotation introduces an anisotropy for different
-viewing angles. For viewing angles close to the poles the line is
-double peaked and it makes a transition to a single peaked line for
-high rotational velocities and viewing angles along the equator. This
-trend is stronger for spheres with homogeneusly distributed radiation
-sources.  In contrast, the total flux in the line remains independent
-of the viewing angle.
+Two conclusions stand out from our study. First, rotation clearly impacts the \ly line
+morphology; the width and the relative intensity of the center of the
+line and its peaks are affected. Second, rotation introduces an
+anisotropy for different viewing angles. For viewing angles close to
+the poles the line is double peaked and it makes a transition to a
+single peaked line for high rotational velocities and viewing angles
+along the equator. This trend is clearer for spheres with
+homogeneously distributed radiation sources than it is for central
+sources.
 
-The escape fraction remains constant for diffenret viewing angles only
-in the case of centrally distributed sources. In contrast, for an homogeneous
-distribution the escape fraction decreases with high rotation 
-fraction remain constant for different viewing angles. We showed that
-these results can be interpreted in terms of the average number of
-scatterings for the photons, a quantity that also remains constant
-independent of the viewing angle and the rotational velocity for
-centrally distributed sources and decreases for homogenously
-distributed source.
+In contrast, we found two quantities that are invariant with respect
+to the viewing angle and the rotational velocity: the integrated flux and the escape
+fraction.  The exception are the models with homogeneously distributed
+sources, which present an escape fraction dependent on the rotational
+velocity, but still independent of the viewing angle. We showed that
+these results could be interpreted in terms of the average number of
+scatterings for the photons.
 
-Quantitatively the main results of our study are summarized as
+Quantitatively, the main results of our study are summarized as
 follows.
@@
 
-\item Rotation induces a considerable asymmetry in the morphology 
- of the spectra when the viewing angle $\theta$. This occurs for
- all of our models. The asymmetry is such that observeds with
- $\cos\theta\equiv \mu\sim 1$, i.e. observes aligned with the rotation
- axis, the line is double peaked while for $\mu\sim 0$ and high
- rotation veolcities the linebecomes double peaked.
+\item In all of our models, rotation induces changes in the line morphology
+ for different values of the angle between the rotation
+ axis and the LoS, $\theta$.  The changes are such that for 
+ $\cos\theta\equiv \mu\sim 0$, i.e. LoS perpendicular to the
+ rotation axis, and high rotational velocities the line becomes single peaked.
 
-\item For $\mu \sim 0$ The line width increases with rotational velocity. The line width
-  approximately follows the functional for  ${\rm FWHM}^2 = {\rm FWHM}_{
-    0}^2 + (V_{\rm max}/\lambda)^2$ where FWHM$_{0}$ indicates the line
-  width for the static case and $\lambda$ is a constant determined from
-  the radiative transfer results it is $\lambda_{\rm c}=0.84 \pm 0.06$ and
+\item For a viewing angle with $\mu=0$ the line width increases with rotational
+  velocity. This change approximately follows the functional form  ${\rm FWHM}^2 = {\rm FWHM}_{ 0}^2 + (V_{\rm max}/\lambda)^2$, where FWHM$_{0}$ indicates the line
+  width for the static case and $\lambda$ is a constant. We have
+  determined this constant to be  $\lambda_{\rm c}=0.84 \pm 0.06$ and
   $\lambda_{\rm h}=0.54\pm 0.10$ for the central and homogeneous source
-  distribution, respectively.
+  distributions, respectively.
 
-\item A single peaked line emerges for high rotational velocities in
-  the case of homogeneously distributed sources. These cases occur when
-  the rotational velocity is larger than half FWHM$_0$ and $\mu\sim 1$.
+\item At fixed rotational velocity the line width decreases as $|\mu|$
+  increases, i.e. the smallest value of the line width is observed for
+  a line of sight parallel to the ration axis. However the lowest
+  values are always larger than the values for the static case.
 
-\item 
-For central sources we find that the escape fraction does not change
+\item The single peaked line emerges for homogeneously distributed sources 
+  when the rotational velocity is larger than half FWHM$_0$ and $\mu\sim
+  1$.
+
+\item  For central sources we find that the escape fraction does not change
   with rotational velocity nor with the viewing angle. We interpret this
   in terms of the average number of scatterings which does not
-significantly changes with rotation. This is due to the  
+  significantly change with rotation. This is due to the  
   fact that the vast majority of scatterings events are resonant, 
@@
 LAEs.
+
+The definitive and clear impact of rotation on the \ly morphology
+suggests that this is an effect that should be taken into accunt at
+the moment of interpreting high resolution spectroscopic data. To this
+end, we defer a discussion of observed lines features in the context of gas
+bulk rotation to a future publication (Remolina-Gutierrez et al., in
+preparation).
 
@@
 
+We thank the referee for the suggestions that allowed us to greatly
+improve and better frame the interpretation of our simulations.
+
 \bibliographystyle{apj}

### 2014-05-30 paper/ms.tex
discussion

@@
 
-%% One possible explanation for the emergence of the single peak in the
-%% homogeneous systems is that some photons close to the surface
-%% (a sort of photosphere) can escape with a low number of scatterings,
-%% allowing them to stay close to the line's center. Increasing the
-%% rotational velocity $V_{\rm max}$ reduces the optical depth making the
-%% photosphere region effectively larger, increasing the number of
-%% photons escaping close to the line's center.
-
-%% However, for the central emission the transition to a single peak is
-%% harder to reach in the range of explored parameters. 
-%% In this case the average number of scatterings to escape
-%% should remain close to constant as the rotational velocity
-%% increases. The rise in intensity at the line's center could instead
-%% mean that the scattering in a medium with bulk motion are inefficient
-%% in driving photons outside that frequency region.
-
-%% In order to explore our interpretation for these two scenarios we now 
-%% quantify the effect of rotation on the number of scatterings.
-
 The number of scatterings affects the escape frequency of a \ly
@@
 
-Gas bulk rotation has a noticeable effect on the morphology of the
- \ly line. In this section we compare our findings to other
- computational results and discuss the implications of these finding
- in the interpretation of observational data.
+We now compare our findings to other computational results and discuss
+its possible implications  for the interpretation of observational data.
 
-\cite{Verhamme12} studied \ly using two high resolution simulations
-of individual galaxies. The main purpose of the study was to asses the
-impact of two different InterStellar Medium (ISM) prescriptions. However, each simulated
-galaxy had a disc structure with a clear rotation pattern in the ISM
-and inflowing gas int the circum-galactic region. The configuration
-had an axial symmetry and they reported a strong dependence of the
-escape fraction and the total line intensity as a function of the
+{\bf Galaxy simulations with gas rotation}. \cite{Verhamme12} studied \ly
+line emission in two high resolution simulations of individual
+galaxies. The main purpose of their study was to asses the impact of
+two different Inter-Stellar Medium (ISM) prescriptions. However, each
+simulated galaxy had a disc structure with a clear rotation pattern in
+the ISM and inflowing gas from the circum-galactic region. The configuration
+had an axial symmetry and they reported a strong dependence of both
+the escape fraction and the total line intensity as a function of the
 $\theta$ angle. In our results, none of these two quantities has a
 dependence either on the inclination angle or the rotational
-velocity. Therefore, the effect reported by \cite{Verhamme12} is
+velocity. We suggest that he effect reported by \cite{Verhamme12} is
 consistent with being a consequence of the different hydrogen optical
@@
 
-The presence of single peaked profiles has been associated to
-inflow/outflow dynamics \citep{Verhamme06,DijkstraKramer}. In this
-paper we show that gas bulk rotation can also be considered as a
-probable origin for that behavior, provided that the observed single peak is highly
+{\bf Single peaked lines}. The presence of single peaked profiles has
+been associated to inflow/outflow dynamics
+\citep{Verhamme06,DijkstraKramer}. In this paper we show that gas bulk
+rotation can also be considered as a probable origin for that
+behavior, provided that the observed single peak is highly
 symmetric. Similarly, in the case of double peaked lines with a high
-level of flux at the line center, rotation also deserves to be considered in
-the pool of possible bulk flows responsible for that feature,
+level of flux at the line center, rotation also deserves to be
+considered in the pool of possible bulk flows responsible for that feature,
 specially if the two peaks have similar intensities. This highlights
@@
 
-Another important issue is the \ly flux, in several systems correlation
-between the \ly flux and properties such as the peak shift has been found
- (cites), in our study we don't find this correlation mainly because the flux remain 
- constant for all the rotational velocities and because the flux of the line
- is independent of the viewing angle. This last feature is shown in 
- Fig.\ref{fig:muhisto} when clearly is seen that the flux of the line
- does not change with the viewing angle $\theta$ as it does in systems with
- anisotropic \ly emission \citep{Zheng2013} and most recently in
-  Outflow-Driven Cavities \citep{Behrens2014}.
+{\bf Systemic velocities}. There are observational measurements for the
+velocity shift between the \ly and other emission lines. In our study
+we find that the position of the peak maxima is insensitive to the
+rotational velocity of the gas. In our model the only parameter that
+can influence the peak maxima position is the optical depth.
+
+{\bf Anisotropic emission}. In our studies the integrated flux is
+constant is independent of the viewing angle. This rules out the
+possibility of having an observational indication of gas bulk rotation
+from measurements of the line equivalent width. A possible way to
+obtain an anisotropic flux with the same gas configuration is to allow
+for anisotropic emission \citep{Zheng2013,Behrens2014}. We explore
+these scenarios in future work (Remolina-Gutierrez et al., in prep.).
+
+{\bf Additional uncertainty on the \ly escape fraction}. Study of
+high redshift LAEs in numerical simulation often requires the
+estimation of the \ly escape fraction in order to compare their
+results against observations
+\citep{CLARA,Dayal2012,Forero12,Orsi12,Garel2012}. Most of these
+models estimate the escape fraction from the column density of dust and
+neutral Hydrogen. The results of our simulation suggest that the
+rotational velocity has also to be accounted for, having an impact on
+the values of the escape fractions by factors of $\sim 2$.
 

### 2014-05-30 paper/ms.tex
down to integrated line intensity

@@
 
-The central results of this paper are summarized in Figures
+The central result of this paper are summarized in Figures
 \ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
@@
 If the viewing angle is aligned witht the rotation axis, $|\mu|\sim
-1$, the \ly line keeps a double peak with some changes as a function
-of the rotational velocity that are easier to spot in models where the
-\ly photons are homogeneously distributen than in the case of central
-emission.
+1$, the \ly line keeps a double peak with minor changes with
+increasing rotational velocity. However, for a line of sight
+perpendicular to the rotation axis, $|\mu|\sim 0$, the impact of
+rotation is larger. This is clear in  Figure
+\ref{fig:differentvelocities} where we present the different line
+morphologies for $|\mu|\sim 0$ for both the homogeneous and central
+configurations. The panels have the same distribution as Figures
+\ref{fig:CentralSpec} and \ref{fig:HomSpec}.
 
-However, for a line of sight perpendicular to the rotation
-axis, $|\mu|\sim 0$, the impact of rotation is larger.  This is clear
-in  Figure \ref{fig:differentvelocities} where we present the
-different line morphologies for $|\mu|\sim 0$ for both the homogeneous
-and central configurations. The panels have the same distribution as
-Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
-
-For this case of $|\mu|\sim 0$, there are three clear effects on the
-line's morphology as the rotational velocity increases. First, the
+In the case of $|\mu|\sim 0$ there are three clear effects on the
+line morphology as the rotational velocity increases. First, the
 line broadens; second, the double peaks reduce their intensity; and
@@
 \caption{Integrated flux distribution as a function of the
-  viewing angle as parameterized by $\mu$. We show the results for the
-  homogeneous source distribution in models with rotational velocities
-  $0$\kms, $300$\kms and  optical depths $10^5$, $10^6$ and $10^7$.
-  The distributions are flat, meaning that the integrated flux for all
-  viewing angles is the same. The results for the central sources are
-  similar. 
+  viewing angle as parameterized by $\mu$. Continous (dashed)
+  correspond to central (homogeneous) source distribution.
+  The models correspond to an optical depth of $\tau_{\rm
+    H}=10^5$ and rotational velocities of $100$\kms, $200$\kms and
+  $300$\kms. The distributions are flat, meaning that the integrated
+  flux for all viewing angles is the same.
 \label{fig:muhisto}}
@@
 
-We consider possible variations in the integrated flux with respect to
-$\theta$. We define the normalized flux seen by an observer at an
-angle $\mu$ by: \begin{equation}
+Besides the change in morphology, we now consider possible variations
+in the integrated flux with respect to the viewing angle $\theta$. We
+define the normalized flux seen by an observer at an angle $\mu$ by:
+
+\begin{equation}
 F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
@@
 \Theta$. This definition satisfies the condition
-$\int_{-1}^{1}F(\mu)d\mu/2=1$.
+$\int_{-1}^{1}F(\mu)d\mu/2=1$.  In the case of perfect spherical
+simmetry one expects a flat distribution of $F(\mu)=1$.
 
-Figure \ref{fig:muhisto} shows a flat $F(\mu)$ for all models. It
-means that in spite of the different morphologies, the integrated flux
-is the same for all sight angles.
+Figure \ref{fig:muhisto} shows the results for a selection of models
+with $\tau_{\rm H}=10^{5}$, different rotational velocities and both
+for the central and homogeneous source distributions. The
+distributions do not show any trend, beyond some fluctuations below
+the $2\%$ level. This result implies that the integrated flux is
+constant for all viewing angles and all the possible models.
 
@@
 line emission in two high resolution simulations of individual
-galaxies. The main purpose of their study was to asses the impact of
+galaxies. The main purpose of their study was to assess the impact of
 two different Inter-Stellar Medium (ISM) prescriptions. However, each
@@
 bulk rotation to a future publication (Remolina-Gutierrez et al., in
-preparation).
+prep.).
 

### 2014-05-30 paper/ms.tex
results section

@@
 
-A quantitative description of the \ly line has been reached through
+A more detailed quantitative description of the \ly line has been reached through
 Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. In the last
@@
 clear evolution as a function of the sphere rotational velocity. In \S
-\ref{sec:discussion} we discuss the implications of our results in the
-interpretation of LAEs observations with high resolution
-spectroscopy. In the last section we present our conclusions.
+\ref{sec:discussion} we discuss the implications of our results. In
+the last section we present our conclusions.
 
@@
 broadening. We measure this width from the velocity histogram by
-finding the values of the velocities at half maximum. We use lineal
-interpolation between histogram points to get a more precise value for
-this width.
+finding the values of the velocities at half maximum intensity. We use
+lineal interpolation between histogram points to get a value more precise
+than the bin size used to construct the line intensity.
 
@@
 of the viewing angle. The FWHM increases for decreasing values of
-$\mu$ increases and increasing values of $V_{\rm max}$. In Figure
-\ref{fig:widthvsvelocity} we fix $|\mu|<0.1$ and show the FWHM as a
-function of rotational velocity. For this case we parametrize the
-dependency of the line width with  $V_{\rm max}$ as
+$\mu$ and increasing values of $V_{\rm max}$. In Figure
+\ref{fig:widthvsvelocity} we fix $|\mu|<0.1$, i.e. viewing angle
+perpendicular to the rotation axis, and plot the FWHM as a
+function of rotational velocity.
 
+we parametrize the dependency of the line width with  $V_{\rm max}$ as
+%
 \begin{equation}
@@
 where FWHM$_{0}$ is the velocity width in the static case and $\lambda$ 
-is a positive scalar to be determined as a fit to the data.
+is a positive scalar to be determined as a fit to the data.  With this
+test we want to know to what extent the new velocity width can be
+expressed as a quadratic sum of the two relevant velocities in the
+problem. That all the models fall into two families of straight lines,
+for central and homogeneously emitted sources, justifies this choice
+of parameterization.
 
-With this test we want to know to what extent the new velocity width
-can be expressed as a quadratic sum of the two relevant velocities in
-the problem. We fit simultaneously all the points corresponding to
-central and homogeneous models to find $\lambda_{\rm c} = 0.84 \pm
-0.06$ and $\lambda_{\rm h}= 0.54\pm 0.1$ respectively.
+We fit simultaneously all the points corresponding to each one of this
+families to find $\lambda_{\rm c} = 0.84 \pm 0.06$ and $\lambda_{\rm
+  h}= 0.54\pm 0.10$ respectively.
 
@@
 We measure the peak maxima position to quantify the transition from
-double into single peak. We do this as a function of the viewing angle
-$\theta$ and the maximum rotational velocity. The results are
+double into single peak profiles. We do this as a function of the viewing angle
+$\theta$ for different rotational velocities. The results are
 summarized in Figure  \ref{fig:maximumsvsvelocity}. There are two
@@
 models are similar regardless of the rotational velocity. Second, at a
-viewing angle perpendicular to the rotation axis ($\mu\sim 0.0$) there
-is a good fraction of models that become single peaked, a feature that
-appears more frequently for homogeneously distributed sources when all
-the other parameters are equal.
+viewing angle perpendicular to the rotation axis ($\mu\sim 0.0$) a
+good fraction of models become single peaked. This feature appears
+more frequently for homogeneously distributed sources if all the
+other parameters are equal.
 
@@
 
-We now estimate the escape fraction $f_{\rm esc}$ for the dusty models. Our main
-result is that we do not find any dependence with the viewing angle
-but there is a strong dependence with the rotational velocity for the
-homogeneous models.
+We now estimate the escape fraction $f_{\rm esc}$ for the dusty
+models. The main  result is that we do not find any dependence
+with the viewing angle but there is a strong dependence with the
+rotational velocity for the homogeneous models.
 
-The left panel in Figure \ref{fig:escape_fraction} summarizes our
-results. The left panel shows the escape fraction as a function of the
-rotational velocity. To construct this Figure we take into account all
-the photons regardless of its outgoing direction. We observe that the
+The left panel in Figure \ref{fig:escape_fraction} summarizes the
+findings about the dependence with the rotational velocity. The left
+panel shows the escape fraction as a function of the rotational
+velocity. To construct this Figure we take into account all the
+photons regardless of its outgoing direction. We observe that the 
 curves for the central source distribution stay flat, while for the
@@
 close to the surface can escape with a low number of scatterings. This
-has a two-fold consequence: the escaping photons do not have time to
+has a two consequences: the escaping photons do not have time to
 scatter away from the line's center and also have less chances to find
@@
 corresponds to the specific case of the central model with $\tau=10^5$ and
-$V_{\rm max}=300$\kms; but we have veryfied that this holds for all
-models. This allows us to focus to use all the photons in the
-simulations regardless of their value of $\cos\theta$.
+$V_{\rm max}=300$\kms, but we have veryfied that this holds for all
+models. This allows us to construct statistics using all the outgoing
+photons regardless of their value of $\cos\theta$.
 
-In the right panel of Figure \ref{fig:Nscatt} we observe how the
+The right panel of Figure \ref{fig:Nscatt} shows how the
 average number of scatterings decreases for larger rotational
@@
 
-In static cases, a large value of the optical depth correlates with a
-high number of scatterings.  This can be precisely quantified in the
-static slab. In this model for centrally emitted sources the average
-number of scatterings depends only on the optical depth $\langle
-N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}, in the case of homogeneously distributed
-sources $\langle N_{\rm   scatt}\rangle=1.16\tau_{\rm   H}$
+In order to gain a deeper understanding of these results  we make 2D
+histograms for the number of scatterings as a function of the outgoing
+dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show these 
+results in the case $\tau_{\rm H}=10^5$ for the
+static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
+results for the homogeneous (central) source distribution. The color
+scale is logarithmic in the number of photons at a certain value
+$x-N_{\rm scatt}$.
+
+The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
+high rotational velocity) supports our hypothesis about
+the photo-sphere in the homogeneous distribution. In this case most of
+the photons that left with $x\sim 0$ have escaped with less than $10$
+scatterings. This also explains the decrease in the average number of
+scatterings observed in Figure \ref{fig:Nscatt}. We have also veryfied
+that these photons are indeed emitted closer to the surface than to
+the center of the sphere.
+
+However, for a central distribution the situation is quite different
+(lower panels in Figure \ref{fig:Nscatt2D}). In this case the number
+of scatterings remains high, in the order of the optical depth, but
+the two peaks do get closer to each other. The most probable
+physical picture is that each scattering, due to the bulk velocity of
+the gas, is inefficient in driving the photon outside the line
+center.
+
+We now proceed with a more detailed quantification of the number of
+scatterings in our simulations. We guide the measurement by the fact
+that in static cases, a large value of the optical depth correlates
+with a high number of scatterings.  This has been precisely quantified
+in the case of static infinite slab. In this model for centrally
+emitted sources the average number of scatterings depends only on the
+optical depth $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
+\citep{Adams72,Harrington73}, for homogeneously distributed sources
+$\langle N_{\rm   scatt}\rangle=1.16\tau_{\rm   H}$
 \citep{Harrington73}.
@@
 We perform a similar quantification of in our speherical setup for the
-scatic spheres. We find that for the central model the number of
+static spheres. We find that for the central model the number of
 scatterings is proportional to the optical depth, with $\langle N_{\rm
@@
 corresponding central case.
-
-In order to gain a deeper understanding of these results  we make 2D
-histograms for the number of scatterings as a function of the outgoing
-dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we these 
-results in the case $\tau_{\rm H}=10^5$ for the
-static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
-results for the homogeneous (central) source distribution. The color
-scale is logarithmic in the number of photons at a certain value
-$x-N_{\rm scatt}$.
-
-The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
-high rotational velocity) supports our hypothesis about
-the photo-sphere in the homogeneous distribution. In this case most of
-the photons that left with $x\sim 0$ have escaped with less than $10$
-scatterings. This also explains the decrease in the average number of
-scatterings observed in Figure \ref{fig:Nscatt}.
-
-However, for a central distribution the situation is quite different
-(lower panels). In this case the number of scatterings remains high,
-in the order of the optical depth, but the two peaks do get closer to each
-other. Here the most probable physical picture is that each
-scattering, due to the bulk velocity of the gas, is inefficient in
-driving the photon outside the line center.
 

### 2014-06-03 paper/referee-reply.tex
escape fraction plot

@@
 }
+
+\begin{figure}
+\includegraphics[scale=0.5]{escapefractionvstheta.png}
+\caption{Escape Fraction as a function of $\mu$}
+\end{figure}
 
@@
 Again, if real, this is an important result, that you must advertise more.
-Please show it on this Fig, by comparing F(μ) without rotation (in red, for example) to the other distributions that you get with different values of Vmax.
+Please show it on this Fig, by comparing F($\mu$) without rotation (in red, for example) to the other distributions that you get with different values of Vmax.
 Then, you mention that for high optical depth values, $F(\mu)$ (not the variations of $\mu$) can vary up to $15\%$.
 First, what do you call high optical depth ?
-your highest setup is τ = 107, not extremely high for lyman alpha ”standards’, corresponding to NHI ∼ 1020 cm−2.
+your highest setup is $\tau = 10^{7}$, not extremely high for lyman alpha ”standards’, corresponding to NHI ∼ 1020 cm−2.
 So, if you see a trend with optical depth, I encourage you to check higher optical depth regimes, corresponding better to galaxy scales.
 If you can probe that anisotropy induced by rotation is rising with optical depth, this would be an interesting result.
-If higher optical depth regimes lead to anisotropic escape, could you check the effet of anisotropy on the lya spectral shape ?
+If higher optical depth regimes lead to anisotropic escape, could you check the effect of anisotropy on the lya spectral shape ?
 

### 2014-06-04 paper/referee-reply.tex
updated referee reply

@@
 \usepackage[T1]{fontenc}
-\usepackage{lmodern}
-\usepackage[spanish]{babel}
 \usepackage{amsmath}
@@
 
-\title{Response to the referee}
+\title{Response to the first report on the article draft \emph{The Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}}
+\author{Juan N. Garavito-Camargo, Jaime E. Forero-Romero, Mark Disjkstra}
+\date{\today}
 
@@
 
-\date{}
 \maketitle
+We thank the referee for a detailed report. In this occation the
+report by the referee motivated us to explore a very important aspect
+of our results that we had overlooked.
 
-Dear referee the main changes in our paper are that we do find
+At the moment of addressing the comments in the report, we
+prepared a plot suggested by the referee. The plot showed a clear
+dependence of the line morphology with the viewing angle, a result
+that we had deemed negligeable after measuring that the integrated
+flux did not have any dependence on the viewing angle
+
+The correct interpretation is that, as the referee expected, there is
+a strong effect on the morphology.
+
+This completely changed the focus of the previous version of the
+paper. We have now completely rewritten the Results and Discussion
+section in order to highlight that result. We have also completeley dropped
+sections (e.g. the asymetrical emission part) that obfuscate the main
+result of the paper.
+
+In this document we address one by one the questions in the
+report. However, we kindly ask the referee to revise directly the new
+version of the paper, given the substantial changes from the first
+version.
+
+In what follows the comments by the referee are boldfaced.
+
+Best regards, \\
+
+The Authors\\
 
@@
 
-The problematic of anisotropy is only studied from Sect3.4, the former sections consider global quantities (spectral shapes, escape fractions, etc...).
-This is ok only if there is NO anisotropy induced by rotation, which is not obvious, a priori.
-You should make it clear from the beginning, telling that you will investigate anisotropy at the end of the paper only, because you checked that lya properties are isotropic, at least in the range of parameters that you investigated so far.\\
+{\bf The problematic of anisotropy is only studied from Sect3.4, the former
+sections consider global quantities (spectral shapes, escape
+fractions, etc...). This is ok only if there is NO anisotropy induced
+by rotation, which is not obvious, a priori. You should make it clear
+from the beginning, telling that you will investigate anisotropy at
+the end of the paper only, because you checked that lya properties are
+isotropic, at least in the range of parameters that you investigated
+so far.}
 
-\textbf{ We have decide to study in this paper the case in which there is No anisotropy. The part concerning the off-center emission is going to be presented in a later study\\}
+We have decide to study in this paper the case in which there is No anisotropy. The part concerning the off-center emission is going to be presented in a later study.
 
-As explained in sect 3.4, rotation kills the spherical symmetry of your problem, and the rotation axis defines a preferential direction.
+{\bf As explained in sect 3.4, rotation kills the spherical symmetry of your problem, and the rotation axis defines a preferential direction.
 We could expect some variation of the emerging flux, the lyman-alpha escape fraction, and the spectral shape, with viewing angle.
 From Fig8, it seems that the flux is the same in all directions for spherical distributions of sources.
-This important result is not enough emphasized.\\
+This important result is not enough emphasized.}
 
-\textbf{We do not find the flux variation with the viewing angle and now as highlighted in the new text we emphasize more this new result, also we made a new plot Figure 5 in the paper, showing this results for both distributions (homogeneous/central) and for optical depth $\tau_{H}=10^{5}$ we choose these models because this are the ones
-that are more sensitive to rotation.}\\
+We do not find the flux variation with the viewing angle and now as
+highlighted in the new text we emphasize more this new result, also we
+made a new plot Figure 5 in the paper, showing this results for both
+distributions (homogeneous/central) and for optical depth
+$\tau_{H}=10^{5}$ we choose these models because this are the ones  that are more sensitive to rotation.
 
-Do you see any difference in the spectral shape with viewing angle?
+{\bf Do you see any difference in the spectral shape with viewing angle?
 To illustrate this point, it would be interesting to build a 2D plot as you did on Fig 5, but replace Nb scat in ordinates by the viewing angle $\mu$.
 We could immediatly see if there is an evolution of the shape with viewing angle or not.
-If you find NO evolution of the Lya shape with viewing angle, I think that it is an interesting counter-intuitive result, that you should advertise more.\\
+If you find NO evolution of the Lya shape with viewing angle, I think that it is an interesting counter-intuitive result, that you should advertise more.}
 
-\textbf{Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
+Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
 We have restructure the paper this new plots now correspond to figure 2 \& 3 in the paper.
-Also we emphasize this results in the results, discussion and conclusion sections.\\}
+Also we emphasize this results in the results, discussion and conclusion sections.
 
-What about the variation of lya escape fraction with viewing angle ?
-I propose that in the beginning of Sect.3 Results, you first emphasize that, maybe counter-intuitively, you did not find any variation of the Lya properties with viewing angle, so you will present first angle average lya properties, and you will come back to the anisotropy problematic only at the end on the paper.\\
+{\bf What about the variation of lya escape fraction with viewing angle ?
+I propose that in the beginning of Sect.3 Results, you first emphasize that, maybe counter-intuitively, you did not find any variation of the Lya properties with viewing angle, so you will present first angle average lya properties, and you will come back to the anisotropy problematic only at the end on the paper.}
 
-\textbf{As escape fraction depends on the number of scatterings and this is invariant for different viewing angles the escape fraction does not change with the viewing angle.
+As escape fraction depends on the number of scatterings and this is invariant for different viewing angles the escape fraction does not change with the viewing angle.
 (MAKE A PLOT AND EXPLAIN THIS BETTER)
-}
-
-\begin{figure}
-\includegraphics[scale=0.5]{escapefractionvstheta.png}
-\caption{Escape Fraction as a function of $\mu$}
-\end{figure}
 
@@
 We want to study the pure effect of rotation on the spectra, off course it would
-be interesting to study the effect of rotation on systems with outflows, this paper
-is under preparation by M.C Remolina-Gutierrez et al.
+be interesting to study the effect of rotation on systems with
+outflows, this paper is under preparation by M.C Remolina-Gutierrez et
+al.
 
@@
 
-With Orsi et al 2012, please cite also Garel et al 2012. With Zheng \& Wallace 2013, please cite also Behrens et al 2014.\\
+{\bf With Orsi et al 2012, please cite also Garel et al 2012. With Zheng \& Wallace 2013, please cite also Behrens et al 2014.}
 
-\textit{This changes were performed.}
+Added.
+
 \subsection*{Fig.1}
 
-I guess that the spectra presented in Fig1 are integrated over all directions, right ?
+{\bf I guess that the spectra presented in Fig1 are integrated over all directions, right ?
 You should describe explicitly how you build them.
-You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.\\
+You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.}
 
-\textbf{Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency.}
+Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency
 
-\begin{itemize}
-\item Description about how we build Fig.1 (Done)
-\item Fig 1. remove x notation (Done)
-\end{itemize}
+{\bf Description about how we build Fig.1}
+
+ (Done)
+{\bf Fig 1. remove x notation}
+
+(Done)
 
@@
 
-Fig.2 Can you explain how you measure the FWHM of a double-peaked profile ? Do you fit it with a gaussian ?
+{\bf Fig.2 Can you explain how you measure the FWHM of a double-peaked profile ? Do you fit it with a gaussian ?}
 
-We don't fit a gaussian, we interpolate points to the line profile and then  we measure the width by finding
-the closest points to the half maximum in our histogram.
+We e interpolate points to the line profile and then  we measure the
+width by  the closest points to the half maximum in our histogram.
 
@@
 
-Do you have an idea why the (central source, intermediate optical depth) case with Vmax=300 has a single plateau instead of 2 peaks ? Do you find this with the two codes ?
+{\bf Do you have an idea why the (central source, intermediate optical depth) case with Vmax=300 has a single plateau instead of 2 peaks ? Do you find this with the two codes ?}
+
+After close inspection in this figure the line was composed by two
+peaks, that looked like a plateau with the resolution used to
+construct the figure.
 
@@
 
-This is a surprising result that the number of scatterings (escape fraction) stays constant as the rotation velocity increases, for a central source, whereas the global spectral shape is altered.
+{\bf This is a surprising result that the number of scatterings (escape fraction) stays constant as the rotation velocity increases, for a central source, whereas the global spectral shape is altered.
 Did you try with higher/extreme values of Vmax (=1000 km/s, even if not physically motivated) ?
 Do you believe that the number of scatterings decreases with very high values, or that it is independant of the rotation velocity ?
-Is the escape fraction from a dusty rotating cloud with central source independant of the rotation velocity ?
+Is the escape fraction from a dusty rotating cloud with central source independant of the rotation velocity ?}
 
 \subsection*{Fig5}
-This is a very nice figure !
-Looking at the top right panel, with its “photosphere”, I’m surprised that the distribution of Nscatt is bipolar, I would have expected a smooth transition between the 2 regimes.
-Do you have a physical explanation why photons escape after either (less than 10) or (more than 1000) scatterings, and none escape with 100 scatt ?
-To test the ’photosphere’ assumption, you could also do the radiation transfer in a cloud with the distribution of sources only in an inner sphere, and another experienment with sources only in an outer shell.
-If I understood corectly, you would expect thant the bottom spot on the top right panel is made of photons from the outer shell, and the uppper spot from photons emitted inside the cloud.
+
+{\bf This is a very nice figure ! Looking at the top right panel, with
+  its “photosphere”, I’m surprised that the distribution of Nscatt is
+  bipolar, I would have expected a smooth transition between the 2
+  regimes. Do you have a physical explanation why photons escape after
+  either (less than 10) or (more than 1000) scatterings, and none
+  escape with 100 scatt ? To test the ’photosphere’ assumption, you
+  could also do the radiation transfer in a cloud with the
+  distribution of sources only in an inner sphere, and another
+  experienment with sources only in an outer shell. If I understood
+  corectly, you would expect thant the bottom spot on the top right
+  panel is made of photons from the outer shell, and the uppper spot
+  from photons emitted inside the cloud.}
 
@@
 
-One sentence is not clear : we see that the escape fraction does not increase significantly from $\tau$ = 105 to $\tau = 10^{6}$.
+{\bf One sentence is not clear : we see that the escape fraction does not increase significantly from $\tau$ = 105 to $\tau = 10^{6}$.
 This counter-intuitive result....
@@
 A decrease is expected from $\tau$ = 105 to $\tau$ = 106, not an increase, but indeed on the graphe we can see an unexpected (small) increase.
-I do not understand the explanation for this behaviour.
+I do not understand the explanation for this behaviour.}
+
 (Mark)
@@
 
-Referred to as Figure 7 in the text (paragraph 3.4).
-To my mind, this figure illustrates the main result of your study, it has to be more demonstrative.
-On this figure, the numerical noise seems very big compare to the small number of bins, bigger than on the spectra from Fig1, how is it possible ?
-Could you re-do this figure with more photons, maybe with more bins ?
-Could you plot an histogram instead of broken lines, to ease the reading ?
-In the text, you write anisotropy induced by rotation is at the 3$\%$ level, how do to estimate this number?
-I think that the noise is at $3\%$ level, and the distribution is compatible with ’flat’.
-In the corresponding text, you first say that $F(\mu)$ does not depend on Vmax.
-Again, if real, this is an important result, that you must advertise more.
-Please show it on this Fig, by comparing F($\mu$) without rotation (in red, for example) to the other distributions that you get with different values of Vmax.
-Then, you mention that for high optical depth values, $F(\mu)$ (not the variations of $\mu$) can vary up to $15\%$.
-First, what do you call high optical depth ?
-your highest setup is $\tau = 10^{7}$, not extremely high for lyman alpha ”standards’, corresponding to NHI ∼ 1020 cm−2.
-So, if you see a trend with optical depth, I encourage you to check higher optical depth regimes, corresponding better to galaxy scales.
-If you can probe that anisotropy induced by rotation is rising with optical depth, this would be an interesting result.
-If higher optical depth regimes lead to anisotropic escape, could you check the effect of anisotropy on the lya spectral shape ?
+{\bf Referred to as Figure 7 in the text (paragraph 3.4). To my mind,
+  this figure illustrates the main result of your study, it has to be
+  more demonstrative. On this figure, the numerical noise seems very
+  big compare to the small number of bins, bigger than on the spectra
+  from Fig1, how is it possible ? Could you re-do this figure with
+  more photons, maybe with more bins ? Could you plot an histogram
+  instead of broken lines, to ease the reading ? In the text, you
+  write anisotropy induced by rotation is at the 3$\%$ level, how do
+  to estimate this number? I think that the noise is at $3\%$ level,
+  and the distribution is compatible with ’flat’. In the corresponding
+  text, you first say that $F(\mu)$ does not depend on Vmax. Again, if
+  real, this is an important result, that you must advertise
+  more. Please show it on this Fig, by comparing F($\mu$) without rotation
+  (in red, for example) to the other distributions that you get with
+  different values of Vmax. Then, you mention that for high optical
+  depth values, $F(\mu)$ (not the variations of $\mu$) can vary up to
+  $15\%$. First, what do you call high optical depth ? your highest
+  setup is $\tau$= $10^7$, not extremely high for lyman alpha ”standards’,
+  corresponding to NHI $\sim$10$^{20}$ cm$^{-2}$. So, if you see a trend with
+  optical depth, I encourage you to check higher optical depth
+  regimes, corresponding better to galaxy scales. If you can probe
+  that anisotropy induced by rotation is rising with optical depth,
+  this would be an interesting result. If higher optical depth regimes
+  lead to anisotropic escape, could you check the effet of anisotropy
+  on the lya spectral shape?}
 

### 2014-06-04 paper/ms.tex
All figures in PDF and PNG
minor updates

@@
 rotational velocities larger than half the line width in the static
-case. However, rotation does not not induce any significant anisotropy
-in the total line intensity nor in the escape fraction. 
+case. Notably, we find that rotation does not not induce any
+significant spatial anisotropy in the integrated line flux nor in the escape
+fraction.  However, we do find in the homogeneous models a clear
+increase of the escape fraction with increasing rotational velocity.
 \end{abstract}
@@
 distributions do not show any trend, beyond some fluctuations below
-the $2\%$ level. This result implies that the integrated flux is
-constant for all viewing angles and all the possible models.
+the $2\%$ level.
+
+This is a remarkable result. In spite of that the rotation axis
+defines preferential direction, the integrated flux is the same for
+all viewing angles and all the possible models in our spherical
+distributions.
 
@@
 \begin{center}
-  \includegraphics[width=0.40\textwidth]{f6.eps}
-  \includegraphics[width=0.40\textwidth]{f7.eps}
+  \includegraphics[width=0.40\textwidth]{f10.pdf}
+  \includegraphics[width=0.40\textwidth]{f11.pdf}
 \end{center}
@@
 \begin{center}
-    \includegraphics[width=0.45\textwidth]{nscattvsmu.eps}
-    \includegraphics[width=0.45\textwidth]{f4.eps}
+    \includegraphics[width=0.45\textwidth]{f12.pdf}
+    \includegraphics[width=0.45\textwidth]{f13.pdf}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{f5_1.eps}
-  \includegraphics[width=0.48\textwidth]{f5_2.eps}
-  \includegraphics[width=0.48\textwidth]{f5_3.eps}
-  \includegraphics[width=0.48\textwidth]{f5_4.eps}    
+  \includegraphics[width=0.48\textwidth]{f14_1.pdf}
+  \includegraphics[width=0.48\textwidth]{f14_2.pdf}
+  \includegraphics[width=0.48\textwidth]{f14_3.pdf}
+  \includegraphics[width=0.48\textwidth]{f14_4.pdf}    
 \end{center}
@@
 
-Two conclusions stand out from our study. First, rotation clearly impacts the \ly line
-morphology; the width and the relative intensity of the center of the
-line and its peaks are affected. Second, rotation introduces an
+Two conclusions stand out from our study. First, rotation clearly
+impacts the \ly line morphology; the width and the relative intensity
+of the center of the line and its peaks are affected. Second, rotation introduces an
 anisotropy for different viewing angles. For viewing angles close to
@@
 
-In contrast, we found two quantities that are invariant with respect
+Remarkably, we find two quantities that are invariant with respect
 to the viewing angle and the rotational velocity: the integrated flux and the escape
-fraction.  The exception are the models with homogeneously distributed
+fraction.  The exception is the models with homogeneously distributed
 sources, which present an escape fraction dependent on the rotational

### 2014-06-04 paper/referee-reply.tex
updating the reply to the referee

@@
 \documentclass[12pt]{article}
-\usepackage[margin=1.0in]{geometry}
 \usepackage[utf8]{inputenc}
@@
 
-\title{Response to the first report on the article draft \emph{The Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}}
+\title{Response to the first report on the article draft \emph{The
+    Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}} 
 \author{Juan N. Garavito-Camargo, Jaime E. Forero-Romero, Mark Disjkstra}
@@
 \maketitle
-We thank the referee for a detailed report. In this occation the
-report by the referee motivated us to explore a very important aspect
-of our results that we had overlooked.
+We thank the referee for a detailed report. Indeed, the report
+motivated us to explore a very important aspect of our results that we
+had overlooked.
 
-At the moment of addressing the comments in the report, we
-prepared a plot suggested by the referee. The plot showed a clear
-dependence of the line morphology with the viewing angle, a result
-that we had deemed negligeable after measuring that the integrated
-flux did not have any dependence on the viewing angle
+We made a plot suggested by the referee that showed a clear
+dependence of the line morphology with the viewing angle an effect
+that we had deemed as negligeable after measuring a proxy statistic for
+it (the integrated flux).
 
@@
 
-This completely changed the focus of the previous version of the
-paper. We have now completely rewritten the Results and Discussion
-section in order to highlight that result. We have also completeley dropped
-sections (e.g. the asymetrical emission part) that obfuscate the main
-result of the paper.
+This completely changed the focus of our paper. We have now completely
+rewritten the Results and Discussion section in order to highlight
+that result. We have also completeley dropped sections (e.g. the
+asymetrical emission part) that obfuscate this main result.
 
@@
 
-We have decide to study in this paper the case in which there is No anisotropy. The part concerning the off-center emission is going to be presented in a later study.
+As we mentioned in the introduction to this letter, there is indeed
+an anisotropy in the line morphology. The paper was re-structured
+accordingly.
 
-{\bf As explained in sect 3.4, rotation kills the spherical symmetry of your problem, and the rotation axis defines a preferential direction.
-We could expect some variation of the emerging flux, the lyman-alpha escape fraction, and the spectral shape, with viewing angle.
-From Fig8, it seems that the flux is the same in all directions for spherical distributions of sources.
-This important result is not enough emphasized.}
+However, the properties that we had measured as isotropic (integrated
+flux and escape fracrion) remain anisotropic.
 
-We do not find the flux variation with the viewing angle and now as
-highlighted in the new text we emphasize more this new result, also we
-made a new plot Figure 5 in the paper, showing this results for both
-distributions (homogeneous/central) and for optical depth
-$\tau_{H}=10^{5}$ we choose these models because this are the ones  that are more sensitive to rotation.
+{\bf As explained in sect 3.4, rotation kills the spherical symmetry
+  of your problem, and the rotation axis defines a preferential
+  direction. We could expect some variation of the emerging flux, the
+  lyman-alpha escape fraction, and the spectral shape, with viewing
+  angle. From Fig8, it seems that the flux is the same in all
+  directions for spherical distributions of sources. This important
+  result is not enough emphasized.}
 
-{\bf Do you see any difference in the spectral shape with viewing angle?
-To illustrate this point, it would be interesting to build a 2D plot as you did on Fig 5, but replace Nb scat in ordinates by the viewing angle $\mu$.
-We could immediatly see if there is an evolution of the shape with viewing angle or not.
-If you find NO evolution of the Lya shape with viewing angle, I think that it is an interesting counter-intuitive result, that you should advertise more.}
+We now emphasize in the abstract, section 3.2 and the conclusions the
+result on the non-variation of the total flux with viewing angle.
 
-Thanks very much for this recommendation we made this new plot and we do find variations in the morphology of the line due to variations in the viewing angle.
-We have restructure the paper this new plots now correspond to figure 2 \& 3 in the paper.
-Also we emphasize this results in the results, discussion and conclusion sections.
+{\bf Do you see any difference in the spectral shape with viewing
+  angle? To illustrate this point, it would be interesting to build a
+  2D plot as you did on Fig 5, but replace Nb scat in ordinates by the
+  viewing angle $\mu$. We could immediatly see if there is an
+  evolution of the shape with viewing angle or not. If you find NO
+  evolution of the Lya shape with viewing angle, I think that it is an
+  interesting counter-intuitive result, that you should advertise
+  more.}
 
-{\bf What about the variation of lya escape fraction with viewing angle ?
-I propose that in the beginning of Sect.3 Results, you first emphasize that, maybe counter-intuitively, you did not find any variation of the Lya properties with viewing angle, so you will present first angle average lya properties, and you will come back to the anisotropy problematic only at the end on the paper.}
+As we metioned in the introduction to this reply, we prepared the
+suggested plot and found strong variations of the spectral shape with
+viewing angle. This result motivated us to re-structure the paper to
+emphasize it.
 
-As escape fraction depends on the number of scatterings and this is invariant for different viewing angles the escape fraction does not change with the viewing angle.
-(MAKE A PLOT AND EXPLAIN THIS BETTER)
+{\bf What about the variation of lya escape fraction with viewing
+  angle ? I propose that in the beginning of Sect.3 Results, you first
+  emphasize that, maybe counter-intuitively, you did not find any
+  variation of the Lya properties with viewing angle, so you will
+  present first angle average lya properties, and you will come back
+  to the anisotropy problematic only at the end on the paper.}
+
+We do not find any significant dependence of the escape fraction with
+the viewing angle. This is shown in Figure \ref{escape_fraction} of this
+document. We do not show this plot in the paper and only mention the
+result at the beginning of Section 3.5.
+
+\begin{figure}
+\includegraphics[scale=0.5]{escapefractionvstheta.png}
+\caption{Escape Fraction as a function of $\mu$
+\label{escape_fraction}}
+\end{figure}
 
@@
 Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency
+
+\begin{itemize}
+\item Description about how we build Fig.1 (Done)
+\item Fig 1. remove x notation (Done)
+\end{itemize}
 

### 2014-06-04 paper/ms.tex
minor updates

@@
     H}=10^5$ and rotational velocities of $100$\kms, $200$\kms and
-  $300$\kms. The distributions are flat, meaning that the integrated
-  flux for all viewing angles is the same.
+  $300$\kms. The distributions are flat in the range of models probed
+  in this paper, meaning that the integrated flux for all viewing angles is the same.
 \label{fig:muhisto}} 
@@
 defines preferential direction, the integrated flux is the same for
-all viewing angles and all the possible models in our spherical
-distributions.
+all viewing angles, at least for the range of parameters explored in
+this paper.
 

### 2014-06-04 paper/referee-reply.tex
referee reply

@@
 \begin{figure}
+\begin{center}
 \includegraphics[scale=0.5]{escapefractionvstheta.png}
+\end{center}
 \caption{Escape Fraction as a function of $\mu$
@@
 
-We want to study the pure effect of rotation on the spectra, off course it would
-be interesting to study the effect of rotation on systems with
-outflows, this paper is under preparation by M.C Remolina-Gutierrez et
-al.
+{\bf So far, the model only includes rotation. However, most observed
+  Lya spectra from LAEs, or even local galaxies, seem to be asymetric
+  towards the red wavelengths, interpreted as a sign for outflows in
+  these systems, often corroborated by others observables. Did you
+  investigate how the rotation would modify the spectra emerging from
+  expanding clouds?}
+
+We agree with the referee that this is an important point to study. 
+We have not fully investigated it yet.  This is actually research
+under development.
 
@@
 
-{\bf With Orsi et al 2012, please cite also Garel et al 2012. With Zheng \& Wallace 2013, please cite also Behrens et al 2014.}
+{\bf With Orsi et al 2012, please cite also Garel et al 2012. With
+  Zheng \& Wallace 2013, please cite also Behrens et al 2014.}
 
-Added.
+Done.
 
@@
 
-{\bf I guess that the spectra presented in Fig1 are integrated over all directions, right ?
-You should describe explicitly how you build them.
-You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.}
+{\bf I guess that the spectra presented in Fig1 are integrated over
+  all directions, right ? You should describe explicitly how you build
+  them. You could skip the x notation in absciss, as it is not used in
+  the discussion, whereas the velocity is used to compare to FWHM, on
+  Fig2.}
 
-Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency
-
-\begin{itemize}
-\item Description about how we build Fig.1 (Done)
-\item Fig 1. remove x notation (Done)
-\end{itemize}
-
-{\bf Description about how we build Fig.1}
-
- (Done)
-{\bf Fig 1. remove x notation}
-
-(Done)
+Now this figure is the Fig.4 in the paper. Given the depence on the
+viewing angle we decided to construct the plots for a line-of-sight
+perpendicular to the rotation axis ($\theta=\pi/2$). This is
+explicitly describe in the figure and the caption. We have also
+changed the $x$ notation to velocities.
 
@@
 
-{\bf Fig.2 Can you explain how you measure the FWHM of a double-peaked profile ? Do you fit it with a gaussian ?}
+{\bf Fig.2 Can you explain how you measure the FWHM of a double-peaked
+  profile ? Do you fit it with a gaussian ?}
 
-We e interpolate points to the line profile and then  we measure the
-width by  the closest points to the half maximum in our histogram.
+We do not make a gaussian fit. We build first a histogram for the
+outgoing frequencies. Then we interpolate between the points of the
+histogram to find the half maxima intensity values and their
+corresponding frequencies.
 
@@
 
-{\bf Do you have an idea why the (central source, intermediate optical depth) case with Vmax=300 has a single plateau instead of 2 peaks ? Do you find this with the two codes ?}
+{\bf Do you have an idea why the (central source, intermediate optical
+  depth) case with Vmax=300 has a single plateau instead of 2 peaks ?
+  Do you find this with the two codes ?}
 
-After close inspection in this figure the line was composed by two
-peaks, that looked like a plateau with the resolution used to
+After close inspection if this figure the line was composed by two 
+peaks that looked like a plateau with the resolution used to
 construct the figure.
+
+However, this plateau is not present in Fig. 4 anymore because we do
+not build the line from all the outgoing photons, but instead take
+into account the line of sight for the observation.
 
@@
 
-{\bf This is a surprising result that the number of scatterings (escape fraction) stays constant as the rotation velocity increases, for a central source, whereas the global spectral shape is altered.
-Did you try with higher/extreme values of Vmax (=1000 km/s, even if not physically motivated) ?
-Do you believe that the number of scatterings decreases with very high values, or that it is independant of the rotation velocity ?
-Is the escape fraction from a dusty rotating cloud with central source independant of the rotation velocity ?}
+{\bf This is a surprising result that the number of scatterings
+  (escape fraction) stays constant as the rotation velocity increases,
+  for a central source, whereas the global spectral shape is
+  altered. Did you try with higher/extreme values of Vmax (=1000 km/s,
+  even if not physically motivated) ? Do you believe that the number
+  of scatterings decreases with very high values, or that it is
+  independant of the rotation velocity ? Is the escape fraction from a
+  dusty rotating cloud with central source independant of the rotation
+  velocity ?}
+
+(MARK)
 
@@
 
+We followed the suggestion by the referee to construct a new
+plot. For the model with homogeneously distributed sources we now the
+initial and final states for every photon. With this information we
+prepare the plot in Figure \ref{nscatt} of this document. It is a 2D
+histogram of the number of scatterings and the initial radius showing
+the starting radius. Indeed, most of the photons that escaped after
+less than 10 scatterings were emitted in the external part of the
+sphere $R>0.8R_{max}$. However, there is a minority of photons that
+have a similar emission radius but only managed to escape after $10^4$
+scatterings.
+
 \begin{figure}
-  \includegraphics[scale=0.4]{Histogram2dNscattVSRadius.png}
+\begin{center}
+  \includegraphics[scale=0.6]{Histogram2dNscattVSRadius.png}
+\end{center}
+\caption{\label{nscatt} 2D histogram of the number of scatterings and
+  the number. The color scale is linear in the number of photons in
+  each bin.}
 \end{figure}
@@
 
-{\bf One sentence is not clear : we see that the escape fraction does not increase significantly from $\tau$ = 105 to $\tau = 10^{6}$.
-This counter-intuitive result....
-It sounds like you were expecting a strong increase...
-A decrease is expected from $\tau$ = 105 to $\tau$ = 106, not an increase, but indeed on the graphe we can see an unexpected (small) increase.
-I do not understand the explanation for this behaviour.}
+{\bf One sentence is not clear : we see that the escape fraction does
+  not increase significantly from $\tau$ = 105 to $\tau =
+  10^{6}$. This counter-intuitive result.... It sounds like you were
+  expecting a strong increase... A decrease is expected from $\tau$ =
+  105 to $\tau$ = 106, not an increase, but indeed on the graphe we
+  can see an unexpected (small) increase. I do not understand the
+  explanation for this behaviour.}
 
-(Mark)
+(MARK)
 
@@
 
+We have prepared Figure 5 that shows the $F(\mu)$ distribution for
+different velocities and optical depths. Indeed, the distributions are
+consistent with flat (within the noise levels) for all the models
+studied in our paper.
+
+We did not try many more models with higher optical depths. We expect
+to do that in the near future to complete a study that could be
+immediatly comparable against observations.
+
 \end{document}

### 2014-06-04 paper/ms.tex
single flight clarification

@@
 rotational velocities for the homogeneous models. First of all we note
-that the escape fraction does not increase significantly from
-$\tau_{\rm H}=10^{5}$ to $\tau_{\rm H}=10^{6}$. This
-counter-intuitive result is a consequence of the transition into the
-'extremely' opaque regime,  which occurs roughly when $a\tau_{\rm{H}}
-> 10^{3}$  e.g. \citep{Neufeld90}.
+that the escape fraction increases slightly from $\tau_{\rm H}=10^5$ to
+$\tau_{\rm H}=10^{6}$, which is counterintuitive as we expected that increasing
+$\tau_{\rm H}$ requires more scattering before the photon escapes, which would
+increase the probability that photons are destroyed by dust.
+
+However, this naive interpretation is incorrect: increasing $\tau_{\rm
+  H}$ from $10^{5}$ to $10^{6}$ causes us to transition from the
+'optically thick' to  the 'extremely optically thick'
+  regime. In the optically thick regime, Lya  photons can escape in
+  'single flight' which corresponds to a scenario in which the
+  photon resonantly scatters $10^4-10^5$ times until it is scattered
+  into the wing of the line ($x\sim 3-4$). At these frequencies the
+  medium is optically thin, and the photons can escape efficiently in
+  a single flight. In contrast, in an extremely optically thick medium \ly
+  photons escape in a `single excursion' \citep{Adams72}. Here, photons
+that are scattered into the wing of the line escape from the medium in
+a sequence of wing scattering events.In both cases, \ly photons
+resonantly scatter $10^4$-$10^5$ times. Because we keep our clouds the same
+size, the mean free path of Lya photons that scatter resonantly is 10
+times larger for the case $\tau_{\rm H}=10^5$ than for $\tau_{\rm
+  H}=10^6$. If we compute the average distance $D$ travelled by \ly
+photons through a medium of size $R$ as a function of line center
+optical depth $\tau_{\rm H}$, then we find that during the transition
+from optically thick to extremely optically thick the mean traversed
+distance $D$ actually decreases slightly.  This decrease is unique to
+this transition region, and $D$ generally increases with $\tau_{\rm H}$ at other
+values of $\tau_{\rm H}$.
 

### 2014-06-08 paper/ms.tex
includes analytical solution

@@
 
+\appendix
+\section{Analytic Expression for Ly$\alpha$ Spectrum
+  emerging from Rotating Cloud}
+
+Ly$\alpha$ scattering through a an optically thick gas cloud that is
+undergoing solid-body rotation (i.e. the angular speed around the
+rotation axis is identical for each hydrogen atom) proceeds identical
+as in a static cloud. While scattering events off atoms within the
+rotating cloud impart Doppler boosts on the Ly$\alpha$ photon, these
+Doppler boost are only there in the lab-frame. In the frame of the
+rotating gas cloud, all atoms are stationary w.r.t each other, and the
+scattering process proceeds identical as in the static
+case\footnote{An alternative - more quantitative way - to view this is
+  to consider the path of an individual photon: say the photon travels
+  a distance corresponding to $\tau=1$, scatters by 90 degrees, then
+  travels another distance corresponding to $\tau=1$. It is easy to
+  show that the point where the photon ends up is independent of the
+  assumed rotation velocity of the cloud.}. This explains why the
+escape fraction of Ly$\alpha$ photon is independent of the rotation
+velocity off the cloud, irrespective of the rotation speed.
+
+The spectrum emerging of photons emerging from a rotating gas cloud is
+also identical as for the static case in a frame that is co-rotating
+with the cloud. However, the surface of cloud now moves in the
+lab-frame. Each surface-element on the rotating cloud now has a bulk
+velocity w.r.t a distant observer. In order to compute the spectrum
+emerging from this rotation cloud, we have to sum over all surface
+elements (weighted by their intensity).
+
+To provide an analytic description of this emerging spectrum, we adopt
+the geometry shown in Fig~1 (note this differs slightly from the main
+body of the paper. My `observer'  sits along the x-axis. I think yours
+sits along the z-axis. We have to makes sure this is done consistently
+throughout the paper).  
+\begin{figure*}[h]
+\centerline{\includegraphics[width=85mm]{scheme1.pdf}
+\includegraphics[width=85mm]{scheme2.pdf}}
+\caption[]{Adopted geometry for evaluating the analytic spectrum.}
+\label{fig:scheme}
+\end{figure*} 
+The sightline to the observer \& rotation define the $x-z$ plane.
+The observer sits along the axis.
+The {\it left panel} in Fig~1 shows the view from the $y-axis$.
+The rotation axis makes an angle $i$ with respect to the z-axis.
+We sum up spectra from individual patches by integrating over the impact parameter $b$, and angle $\phi$.
+Each $(b,\phi)$ corresponds to a point on the sphere.
+This point has a velocity vector ${\bf v}(b,\phi,i)$, which we denote with ${\bf v}$ for brevity.
+
+\begin{displaymath}
+J(x,i)=2\pi \int_0^Rdb \hs b \int_0^{2\pi}d\phi \hs
+S(b,\phi)J(x,b,\phi,i) \approx 2\pi \int_0^Rdb \hs b
+\int_0^{2\pi}d\phi \hs J(x,b,\phi,i)\\ \nonumber
+\end{displaymath}
+
+\begin{displaymath}
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)} 
+\end{displaymath}
+
+The velocity $v_b$ is the component of ${\bf v}$ projected onto the line-of-sight. This component is given by
+\begin{equation}
+v_{\rm b}(b,\phi,i)=v_{\rm rot}\sqrt{1-(b/R)^2\cos^2 \phi}\hs \cos i
+\hs \sin \beta 
+\end{equation}
+
+\begin{equation}
+\tan \beta= \frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
+\end{equation}
+%
+The quantity $S(b,\phi)$ denotes the surface brightness of the sphere at $(b,\phi)$.
+We have assumed in our analytic calculations that $S(b,\phi)$ is constant.
+The assumption $S(b,\phi)=$ constant corresponds to $I(\mu) \propto \mu$ at the surface, where $\mu$ denotes the cosine of the angle of the propagation direction of the outgoing photon and the normal to the spheres surface: a fixed $db$ corresponds to a physical length $ds = db/\mu$ on the sphere.
+If $I(\mu)$ were constant, this would imply that the sphere should appear brighter per unit $b$.
+A constant surface brightness profile requires the directional dependence for $I(\mu) \propto \mu$ to correct for this.
+Indeed, this is what is expected for the escape of Ly$\alpha$ photons from static, extremely opaque media (see Ahn, Lee \& Lee, 2001; their Fig~4 and accompanying discussion).
+
+It is worth stressing that the analytic calculation is clearly not a complete analytic calculation, and we do not expect perfect agreement: we {\it assumed} a functional form for the surface brightness profile [or for $I(\mu)$].
+It is important to realise that $I(\mu)$ itself may depend on the spectrum.
+I.e., analytic solutions exist for $J(x) = \int_0^1 I(x,\mu) d\mu$ at the boundary, and {\it approximate} expressions for $I(\mu) =\int dx I(x,\mu)$, but none for $I(x,\mu)$ itself.
+\\
+
+%\begin{figure*}[h]
+%\centerline{\includegraphics[width=85mm,angle=270]{spec.eps}}
+%\caption[]{Comparison between analytic ({\it red solid lines}) \& Monte-Carlo ({\it blac%k histograms}) calculations of spectra.
+Left panel shows spectrum when the observer looks down the rotation axis.
+The right panel shows the spectra when the angle between the line-of-sight and rotation axis is ~45 degrees.
+Note that here $\mu \equiv \cos i$.}
+%\label{fig:scheme}
+%\end{figure*}
+
+Fig~2 shows some examples of analytic vs.
+full MC spectra.
+The area under all spectra are normalised to $1$.
+The MC simulations used $10^5$ photons.
+The two methods clearly give good agreement, though not perfect.
+In particular, Fig~3 shows that the MC gives rise to a spectrum that is slightly more concentrated to the centre.
+It is easy to get better agreement my modifying the surface brightness profile (e.g.
+if $S(b)=2-b$, then the analytic calculation agrees better) In any case, the analytic calculation closely captures the results obtained from the full calculations from the MC simulations.
+As such, they are extremely useful \& provide us with a quick tool to verify our calculations at the first order level.
+
+%\begin{figure*}[h]
+%\centerline{\includegraphics[width=85mm,angle=270]{spec2.eps}}
+%\caption[]{Same as Fig~2. Right panel is now when $\cos i > 0.98$.}
+%\label{fig:scheme}
+%\end{figure*} 
+%\end{document}
+
 \bibliographystyle{apj}

### 2014-06-14 code/analytic_solution.c
starting to write C code for the analytic solution

@@ -1,0 +1,30 @@
+#include <stdio.h>
+#include <math.h>
+#include <stdlib.h>
+#define NPOINTS 1000
+#define TEMP 10000
+#define USAGE "analytic_solution.x tau velocity(km/s) viewing_angle(degrees)"
+
+/*
+  This codes computes an analytic solutions for the Lya radiation 
+  transfer problem of a rotating sphere.
+
+  The solution was computed by Mark Dijsktra and is published in the 
+  paper: Garavito-Camargo, Forero-Romero, Dijstra, ApJ ....
+
+  Author: Jaime E. Forero-Romero (Uniandes)
+  Creation date: 14-Jun-2014
+
+  Modifications:
+*/
+
+
+int main(int argc, char **argv){
+  int i;
+  float *x;
+  if(argc!=4){
+    fprintf(stderr, "USAGE: %s\n", USAGE);
+  }
+    
+  return 0;
+}

### 2014-06-14 code/analytic_solution.c
first full version of C code implementing the analytic solution

@@ -1,8 +1,10 @@
 #include <stdio.h>
 #include <math.h>
 #include <stdlib.h>
-#define NPOINTS 1000
-#define TEMP 10000
+#define NPOINTS 500
+#define TEMP 10000.0
+#define R 1.0
+#define PI 3.141592653589793238462643383279502884197169
 #define USAGE "analytic_solution.x tau velocity(km/s) viewing_angle(degrees)"
 
 /*
@@ -10,7 +12,7 @@
   transfer problem of a rotating sphere.
 
   The solution was computed by Mark Dijsktra and is published in the 
-  paper: Garavito-Camargo, Forero-Romero, Dijstra, ApJ ....
+  paper: Garavito-Camargo, Forero-Romero, Dijkstra, ApJ ....
 
   Author: Jaime E. Forero-Romero (Uniandes)
   Creation date: 14-Jun-2014
@@ -18,13 +20,75 @@
   Modifications:
 */
 
-
+double J_surface(double x, double b, double phi, double i_angle, double tau0, double v_rot);
 int main(int argc, char **argv){
-  int i;
-  float *x;
+  int i, j, k;
+  double *x;
+  double *j_int;
+  double min_x=-50.0;
+  double max_x= 50.0;
+  double delta_x = (max_x-min_x)/NPOINTS;
+  double delta_phi = 2.0*PI/NPOINTS;
+  double delta_b = 0.9999/NPOINTS;
+  double tau, v_rot, i_angle;
+  double b, phi;
+
   if(argc!=4){
     fprintf(stderr, "USAGE: %s\n", USAGE);
   }
-    
+
+  tau = atof(argv[1]);
+  v_rot = atof(argv[2]);
+  i_angle = atof(argv[3]);
+  i_angle = i_angle*PI/180.0;
+  
+  fprintf(stderr, "%f %f %f\n", tau, v_rot, i_angle);
+
+  if(!(x=malloc(sizeof(double)*NPOINTS))){
+    fprintf(stderr, "Problem with memory allocation");
+    exit(1);
+  }
+
+  if(!(j_int=malloc(sizeof(double)*NPOINTS))){
+    fprintf(stderr, "Problem with memory allocation");
+    exit(1);
+  }
+
+  for(i=0;i<NPOINTS;i++){
[…]

### 2014-06-15 code/analytic_solution.c
exit(1) option added in C code

@@ -35,6 +35,7 @@ int main(int argc, char **argv){
 
   if(argc!=4){
     fprintf(stderr, "USAGE: %s\n", USAGE);
+    exit(1);
   }
 
   tau = atof(argv[1]);

### 2014-06-17 paper/ms.tex
includes plots for the analytic solutions
going through the paper

@@
 impact of gas bulk rotation on the morphology of the Lyman $\alpha$ 
-emission line in distant galaxies. We model a galaxy as a sphere with
-an homogeneous mixture of dust and hydrogen at a constant
-temperature. These spheres have a solid-body rotation with maximum
-velocities in the range $0-300$ \kms and neutral hydrogen optical
-depths in the range $\tau_{\rm H}=10^{5}-10^{7}$. We consider cases 
-of a single central \lya source, and a uniform distribution of sources. 
+emission line in distant galaxies. 
+We model a galaxy as a sphere with an homogeneous mixture of dust and
+hydrogen at a constant temperature. 
+These spheres have a solid-body rotation with maximum velocities in
+the range $0-300$ \kms and neutral hydrogen optical depths in the
+range $\tau_{\rm H}=10^{5}-10^{7}$. 
+We consider cases of a single central \lya source, and a uniform
+distribution of sources.  
 Our main result is that rotation introduces a dependence of the
-line morphology with  viewing angle. Observations with a line of sight
-parallel to the rotation axis yield line morphologies similar to the
-static case. The greatest difference is observed for lines of sight
-perpendicular to the rotation axis. In this case the intensity at the line
-center increases and the line width increase with rotational velocity.  For
-homogeneously distributed sources the line becomes single peaked  at
-rotational velocities larger than half the line width in the static
-case. Notably, we find that rotation does not not induce any
-significant spatial anisotropy in the integrated line flux nor in the escape
-fraction.  However, we do find in the homogeneous models a clear
-increase of the escape fraction with increasing rotational velocity.
+line morphology with  viewing angle. 
+Observations with a line of sight parallel to the rotation axis yield
+line morphologies similar to the static case. 
+For lines of sight perpendicular to the rotation axis the intensity at the line
+center and the line width increase with rotational velocity.   
+Along the same sight, the line becomes single peaked  at rotational
+velocities close to half the line width in the static case. 
+Notably, we find that rotation does not induce any significant spatial
+anisotropy in the integrated line flux nor in the escape fraction. 
+We provide an analytical expression for the outgoing line intensity
+that accounts for the velocity and viewing angle trends reported here.
 \end{abstract}
@@
 the sphere, direction of propagation $\hat{k}_{\rm in}$ and reduced
-frequency $x_{\rm in}$. The photon's propagation stops once they cross the
+frequency $x_{\rm in}$. 
+The photon's propagation stops once they cross the
 surface of the sphere. At this point we store the position, the outgoing direction
@@
 $x$ forming an angle $\theta$ (parameterized as $|\cos\theta|$) with the
-rotation axis. The rotational velocity ($0,100,200,300$\kms)
-increases from left to right and the optical depth ($10^5$, $10^6$,
-$10^7$) from top to bottom. The \ly photons are initialized at the
-center of the sphere.
+rotation axis. 
+The rotational velocity ($0,100,200,300$\kms) increases from left to
+right and the optical depth ($10^5$, $10^6$, $10^7$) from top to
+bottom. 
+The \ly photons are initialized at the center of the sphere. 
+Two main results can be read from this figure.
+First, the line morphology depends on the viewing angle. 
+Second, the line can become single peaked for high rotational
+velocities.
 \label{fig:CentralSpec} }   
@@
 
-Here we briefly describe the relevant points for the two radiative
-transfer codes we have used. For a detailed description we refer the
-reader to the original papers \cite{CLARA,DijkstraKramer}.
+Here we briefly describe the relevant characteristics of the two
+radiative transfer codes we have used.  
+For a detailed description we refer the reader to the original papers
+\cite{CLARA,DijkstraKramer}.
 
 The codes follow the individual scatterings of \ly photons as they
-travel through a 3D distribution of neutral Hydrogen. At each
-scattering the frequency of the photon (in the laboratory frame) and
-its direction of propagation change. This change in frequency is due
-to the peculiar velocities of the Hydrogen atom that absorbed and
-re-emitted the photon. If dust is present, the photon can interact
-either with a Hydrogen atom or dust grain. In the case of a dust
-interaction the photon can be either absorbed or scattered, this
-probability is encoded in the dust albedo, $A$, which we chose to be
-$1/2$. In order to obtain accurate values for the escape fraction of
+travel through a 3D distribution of neutral Hydrogen. 
+The frequency of the photon (in the laboratory frame) and
+its direction of propagation change at every scattering. 
+This change in frequency is due to the peculiar velocities of the
+Hydrogen absorbing and re-emitting the photon. 
+Once the photons escape the gas distribution we store their direction of
+propagation and frequency at their last scattering.
+
+The initialization process for the \ly photons especifies its
+position, frequency and direction of propagation. 
+We select the initial frequency to be exactly the \ly rest-frame
+frequency in the restframe of the gas and the direction of propagation
+to be random following an flat probability distribution over the sphere.  
+It means that for photons emitted from the center of the sphere
+$x_{\rm in}=0$, while photons emitted at some radii with a peculiar
+velocity $\vec{v}$ have initial values $x_{in}$ depending on its direction of
+propagation: $x_{\rm   in}=\vec{v}\cdot\hat{k}_{\rm in}/v_{\rm th}$.
+We do not include the effect of turbulent velocities in the
+initialization.
+We neglect this given that the induced perturbation should be on the
+close to the thermal velocity, $12.8$\kms, which is one order of
+magnitude smaller than the velocity widths ($100$-$500$\kms) in the
+static case.
+
+If dust is present, the photon can interact either with a Hydrogen
+atom or dust grain.
+In the case of a dust interaction the photon can be either absorbed or
+scattered.
+This probability is encoded in the dust albedo, $A$, which we chose
+to be $1/2$. 
+In order to obtain accurate values for the escape fraction of
 photons in the presence of dust, we do not use any accelerating
-mechanism in the radiative transfer. Once the photons escape the gas
-distribution we store their direction at their direction of
-propagation and frequency at their last scattering.
-
-The photons are thus emitted in some region of the gas distribution
-and follow a random walk in space and frequency until they escape the
-gas distribution or are absorbed by a dust grain. The initialization
-process for the \ly photons has to specify its position, frequency and
-direction of propagation. In our case we select the initial frequency
-to be exactly the \ly rest-frame frequency ($x=0$) and the direction of
-propagation to be random following an flat probability distribution
-over the sphere. A different initization that uses a Gaussian with a
-velocity with equal to the thermal velocity, $12.8$\kms in our case,
-should not introduce noticeable change given that our rotational
-velocities span the range $100$-$300$\kms and the lines have velocity
-widths on the order of $100$-$500$\kms.
-
-The gas is completely defined by its geometry (i.e. sphere or slab),
-temperature $T$, Hydrogen optical depth $\tau_{\rm H}$, dust optical
-depth $\tau_{\rm a}$ and the bulk velocity field $\vec{v}$. Our codes
-treat the gas as homogeneous in density ($\tau_{\rm H}$, $\tau_{\rm
-  a}$) and temperature.
+mechanism in the radiative transfer.
+
+The codes treat the gas as homogeneous in density and temperature.  
+This implies that the cas is completely defined by its geometry
+(i.e. sphere or slab), temperature $T$, Hydrogen optical depth
+$\tau_{\rm H}$, dust optical depth $\tau_{\rm a}$ and the bulk
+velocity field $\vec{v}$.
 
@@
 In the Monte Carlo calculations we follow the propagation of $N_{\gamma}=10^5$
-numerical photons through different spherical galaxies. For each galaxy
-we vary at least one of the following parameters: the maximum
+numerical photons through different spherical galaxies. 
+For each galaxy we vary at least one of the following parameters: the maximum
 rotational velocity $V_{\rm max}$, the hydrogen optical depth $\tau_{H}$,
 the dust optical depth $\tau_{a}$ and the initial distribution of photons
-with respect to the gas. There are $60$ models initial combining all
-variations of the input parameters. Table \ref{table:models}
-summarizes the different parameters.
+with respect to the gas. 
+In total there are $48$ different models combining all the possible
+different variations in the input parameters.
+Table \ref{table:models} lists the different parameters we used to
+generate the models.
 
 Additionally, we have used two independently developed Monte Carlo
-codes \citep{CLARA,DijkstraKramer} to perform the calculations. The
-results we report are robust in the sense that they are obtained by
-both codes.
+codes \citep{CLARA,DijkstraKramer} to perform the calculations. 
+The results and trends we report are observed in both codes.
 
@@
 Physical Parameter (units) & Symbol & Values\\\hline
-Velocity (\kms) & $V_{\rm max}$&$0,\ 50,\ 100,\ 200,\ 300$\\
+Velocity (\kms) & $V_{\rm max}$&$0,\ \ 100,\ 200,\ 300$\\
 Hydrogen Optical Depth & $\tau_{H} $ & $10^{5},\ 10^{6},\ 10^{7}$\\
@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.40\textwidth]{f10.pdf}
-  \includegraphics[width=0.40\textwidth]{f11.pdf}
-\end{center}
-  \caption{Effects of rotation on the escape fraction. Left
-    panel, escape fraction as a function of rotational velocity. All
-    these models have $\tau_{a}=1$. The continuous (dashed) lines
-    correspond to central (homogeneous) models. Right panel, escape
-    fraction as a    function of the product $(a\tau_{\rm
-      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
-    slab is shown as a continuous line. Different lines correspond
-    to different rotational velocities for the homogeneous models.     
-    \label{fig:escape_fraction}} 
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%  \includegraphics[width=0.40\textwidth]{f10.pdf}
+%  \includegraphics[width=0.40\textwidth]{f11.pdf}
+%\end{center}
+%  \caption{Effects of rotation on the escape fraction. Left
+%    panel, escape fraction as a function of rotational velocity. All
+%    these models have $\tau_{a}=1$. The continuous (dashed) lines
+%    correspond to central (homogeneous) models. Right panel, escape
+%    fraction as a    function of the product $(a\tau_{\rm
+%      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
+%    slab is shown as a continuous line. Different lines correspond
+%    to different rotational velocities for the homogeneous models.     
+%    \label{fig:escape_fraction}} 
+%\end{figure*}
 
@@
 \begin{center}
-    \includegraphics[width=0.45\textwidth]{f12.pdf}
-    \includegraphics[width=0.45\textwidth]{f13.pdf}
-\end{center}
-\caption{Logarithm of the average number of scatterings as function of
-  $\mu$ (left panel) and the maximum rotational velocity $V_{\rm
-    max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
-  $V_{max}=300$\kms as a function of $|\cos\theta|$; the independence of
-  $N_{\rm scatt}$ with $\mu$ is present in all models. 
-  In the right panel the continuous (dashed) lines represent an
-  central (homogeneous) distribution of sources; there is a clear
-  decrease in the number of scatterings for the homogenously
-  distributed sources. 
-\label{fig:Nscatt} }    
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
   \includegraphics[width=0.48\textwidth]{f14_1.pdf}
@@
       number of photons with given values of $N_{\rm scatt}$ and
-      $x$. \label{fig:Nscatt2D}. A results that stands out is in the upper
-      right panel, showing that in homogeneously distributed sources a
-      large number of photons can escape escape after a few
-      scatterings, $N_{\rm scatt}<10$.}   
+      $x$. \label{fig:Nscatt2D}. }
 \end{figure*}
@@
 
-%\begin{figure*}[h]
-%\centerline{\includegraphics[width=85mm,angle=270]{spec.eps}}
-%\caption[]{Comparison between analytic ({\it red solid lines}) \& Monte-Carlo ({\it blac%k histograms}) calculations of spectra.
-Left panel shows spectrum when the observer looks down the rotation axis.
-The right panel shows the spectra when the angle between the line-of-sight and rotation axis is ~45 degrees.
-Note that here $\mu \equiv \cos i$.}
-%\label{fig:scheme}
-%\end{figure*}
-
 Fig~2 shows some examples of analytic vs.
@@
 
-%\begin{figure*}[h]
-%\centerline{\includegraphics[width=85mm,angle=270]{spec2.eps}}
-%\caption[]{Same as Fig~2. Right panel is now when $\cos i > 0.98$.}
-%\label{fig:scheme}
-%\end{figure*} 
-%\end{document}
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{vary_vel.pdf}
+  \includegraphics[width=0.48\textwidth]{vary_angle.pdf}
+\end{center}
+\caption{
+Comparison of the Monte Carlo results agains the analytic solution.
+\label{fig:comparison} }   
+\end{figure*}
 

### 2014-06-17 code/analytic_solution.c
no change, removed empty line

@@ -83,7 +83,7 @@ double J_surface(double x, double b, double phi, double i_angle, double tau0, do
   v_thermal = 12.85*sqrt(TEMP/10000.0);
   a = 4.7E-4*(12.85/v_thermal);
   
-  beta = atan(b*sin(phi)/sqrt(R*R - b*b));
+   beta = atan(b*sin(phi)/sqrt(R*R - b*b));
   
   x_b = (v_rot/v_thermal) * sqrt(1.0- (b/R)*(b/R)*(cos(phi)*cos(phi))) * 
     cos(i_angle) * sin(beta);

### 2014-06-17 paper/ms.tex
rewriting the paper

@@
 range $\tau_{\rm H}=10^{5}-10^{7}$. 
-We consider cases of a single central \lya source, and a uniform
-distribution of sources.  
+We consider two types of source distributions: single central and a
+homogeneoulsy distributed in the sphere. 
 Our main result is that rotation introduces a dependence of the
@@
 anisotropy in the integrated line flux nor in the escape fraction. 
-We provide an analytical expression for the outgoing line intensity
-that accounts for the velocity and viewing angle trends reported here.
+We provide an analytical expression for the outgoing \lya spectrum of
+a rotating cloud which accounts for the velocity and viewing angle
+trends observed in the simulations.
 \end{abstract}
@@
 The galaxies detected using this method receive the 
-name of \ly emitters (LAEs). A detailed examination of this galaxy
-population has diverse implications for galaxy formation, reionization
-and the large scale structure of the Universe. Attempts to fully
-exploit the physical information included in the \ly line require an
-understanding of all the physical factors involved in shaping the
-line. Due to the resonant nature of this line, these physical factors
-notably include temperature, density and bulk velocity field of the neutral
-Hydrogen in the emitting galaxy and its surroundings.
+name of \ly emitters (LAEs). 
+A detailed examination of this galaxy population has diverse
+implications for galaxy formation, reionization and the large scale
+structure of the Universe.  
+Attempts to fully exploit the physical information included in the \ly
+line require an understanding of all the physical factors involved in
+shaping the  line. 
+Due to the resonant nature of this line, these physical factors
+notably include temperature, density and bulk velocity field of the
+neutral Hydrogen in the emitting galaxy and its surroundings.
 
@@
 \citep{Adams72,Harrington73,Neufeld90} and uniform spheres
-\citep{Dijkstra06}. Analytic studies of configurations including
-some kind of bulk flow only include the case of a sphere with a Hubble
-like expansion flow \citep{LoebRybicki}.
-
-A more detailed quantitative description of the \ly line has been reached through
-Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. In the last
-two decades these studies have become popular due to the
-availability of computing power. Early into the 21st century, the first
+\citep{Dijkstra06}. 
+Analytic studies of configurations including some kind of bulk flow
+only include the case of a sphere with a Hubble like expansion flow
+\citep{LoebRybicki}.
+
+A more detailed quantitative description of the \ly line has been
+reached through Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. 
+In the last two decades these studies have become popular due to the
+availability of computing power. 
+Early into the 21st century, the first
 studies focused on homogeneous and static media
-\citep{Ahn00,Ahn01,Zheng02}. Later on, the effects of clumpy media
-\citep{Hansen06} and expanding/contracting shell/spherical geometries started to
-be studied \citep{Verhamme06,Dijkstra06,Ahn2014}. Similar codes have applied
-these results to semi-analytic models of galaxy formation \citep{Orsi12, Garel2012} and
-results of large hydrodynamic simulations
-\citep{CLARA,Forero12,Behrens13}. Recently, Monte Carlo codes have also
-been applied to the results of high resolution hydrodynamic
-simulations of individual
-galaxies \citep{Laursen09,Barnes11,Verhamme12,Yajima12}. Meanwhile, recent
-developments have been focused on the systematic study of clumpy
-outflows \citep{DijkstraKramer}and anisotropic velocity configurations
-\citep{Zheng2013}.
+\citep{Ahn00,Ahn01,Zheng02}. 
+Later on, the effects of clumpy media \citep{Hansen06} and
+expanding/contracting shell/spherical geometries started to be studied
+\citep{Ahn03,Verhamme06,Dijkstra06}.  
+Similar codes have applied these results to semi-analytic models of
+galaxy formation \citep{Orsi12, Garel2012} and results of large
+hydrodynamic simulations \citep{CLARA,Forero12,Behrens13}. 
+Recently, Monte Carlo codes have also been applied to the results of
+high resolution hydrodynamic simulations of individual galaxies
+\citep{Laursen09,Barnes11,Verhamme12,Yajima12}. 
+Meanwhile, recent  developments have been focused on the systematic
+study of clumpy outflows \citep{DijkstraKramer} and anisotropic
+velocity configurations \citep{Zheng2013}.
 
@@
 \ref{sec:discussion} we discuss the implications of our results. In
-the last section we present our conclusions.
+the last section we present our conclusions. The Appendix presents the
+derivation of an analytic expression that can be helpful to interpret
+to first order the main trends observed in the Monte Carlo simulations.
 
@@
 We select the initial frequency to be exactly the \ly rest-frame
-frequency in the restframe of the gas and the direction of propagation
+frequency in the gas reference frame and the direction of propagation
 to be random following an flat probability distribution over the sphere.  
@@
 The central result of this paper are summarized in Figures
-\ref{fig:CentralSpec} and \ref{fig:HomSpec}. They show 2D histograms
-of the escape frequency $x$ and outgoing angle $\theta$ parameterized by
-$|\mu|$. Constructing the emission line with photons around a value
-of $\mu$ would gives us the emission detected by an observer located at an
-angle $\theta$ with respect to the rotation axis. We have veryfied
-that the solutions are indeed symmetric with respect to $\mu=0$.
+\ref{fig:CentralSpec} and \ref{fig:HomSpec}. 
+They show 2D histograms of the escape frequency $x$ and outgoing angle
+$\theta$ parameterized by $|\mu|$. 
+Taking into account only photons photons around a value
+of $|\mu|$ gives us the emission detected by an observer located at an
+angle $\theta$ with respect to the rotation axis. 
+We have veryfied that the solutions are indeed symmetric with respect
+to $\mu=0$.
 
 From these Figures we can see that the line properties change with
-rotational velocity and depend on the viewing angle $\theta$.  In the
-next subsections we describe in  detail the changes of the morphology
-with velocity, optical depth and viewing angle. We characterize the
-line morphology by its total intensity, the full width at half maximum
-(FWHM) and the location of the peak maxima. In order to interpret the
+rotational velocity and depend on the viewing angle $\theta$.  
+In the next subsections we quantify the morphology changes with with
+velocity, optical depth and viewing angle.  
+We characterize the line morphology by its total intensity, the full
+width at half maximu, (FWHM) and the location of the peak maxima. 
+In order to interpret the
 morphological changes in the line we also report the median number of
-scatter for each \ly photon in the simulation. For the models where
-dust is included we measure the escape fraction as a function of
-rotational velocity.
+scatter for each \ly photon in the simulation. 
+For the models where dust is included we measure the escape fraction
+as a function of rotational velocity.
 
@@
 are independent of $|\mu|$, as it is expected due
-to the spherical symmetry. However, for increasing rotational
-velocities, at a fixed optical depth, there are clear signs that this
-symmetry is broken.
+to the spherical symmetry. 
+However, for increasing rotational velocities, at a fixed optical
+depth, there are clear signs that this symmetry is broken.
 
 If the viewing angle is aligned witht the rotation axis, $|\mu|\sim
-1$, the \ly line keeps a double peak with minor changes with
-increasing rotational velocity. However, for a line of sight
-perpendicular to the rotation axis, $|\mu|\sim 0$, the impact of
-rotation is larger. This is clear in  Figure
-\ref{fig:differentvelocities} where we present the different line
-morphologies for $|\mu|\sim 0$ for both the homogeneous and central
-configurations. The panels have the same distribution as Figures
-\ref{fig:CentralSpec} and \ref{fig:HomSpec}.
-
-In the case of $|\mu|\sim 0$ there are three clear effects on the
-line morphology as the rotational velocity increases. First, the
-line broadens; second, the double peaks reduce their intensity; and
-third, the intensity at the line center rises. The last two effects
-merge to give the impression that the double peaks are merged into one
-at high rotational velocities, a result that is evident for the
-homogeneously distributed sources as shown in the dashed lines of
-Figure \ref{fig:differentvelocities}.
+1$, the \ly line keeps in most of the cases a double peak with minor
+changes as the rotational velocity starts to increase. 
+However, for a line of sight perpendicular to the rotation axis,
+$|\mu|\sim 0$, the impact of  rotation is larger.  
+The double peak readily transforms into a single peak.
+
+This is clear in  Figure \ref{fig:differentvelocities} where we
+present the different line morphologies for $|\mu|\sim 0$ in the
+homogeneous and central configurations.  
+The panels have the same distribution as Figures \ref{fig:CentralSpec}
+and \ref{fig:HomSpec}.    
+There are three clear effects on the line morphology as the rotational
+velocity increases.  
+First, the line broadens; second, the double peaks reduce their intensity; and
+third, the intensity at the line centre rises. 
+The last two effects are combined to give the impression that the double
+peaks are merged into a single one at high rotational velocities.
 
@@
   $300$\kms. The distributions are flat in the range of models probed
-  in this paper, meaning that the integrated flux for all viewing angles is the same.
+  in this paper, meaning that the integrated flux for all viewing
+  angles is the same.
 \label{fig:muhisto}} 
@@
 
-Besides the change in morphology, we now consider possible variations
-in the integrated flux with respect to the viewing angle $\theta$. We
-define the normalized flux seen by an observer at an angle $\mu$ by:
+We now consider possible variations in the integrated flux with
+respect to the viewing angle $\theta$. 
+To this end we  define the normalized flux seen by an observer at an
+angle $\mu$ by:
 
@@
 %
-where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
+where $\mu=\cos\theta$, $N$ is the total number of outgoing photons,
 $\Delta N$ is the number of photons in an angular bin $\Delta
@@
 $\int_{-1}^{1}F(\mu)d\mu/2=1$.  In the case of perfect spherical
-simmetry one expects a flat distribution of $F(\mu)=1$.
+simmetry one expects a flat distribution with $F(\mu)=1$.
 
 Figure \ref{fig:muhisto} shows the results for a selection of models
-with $\tau_{\rm H}=10^{5}$, different rotational velocities and both
-for the central and homogeneous source distributions. The
-distributions do not show any trend, beyond some fluctuations below
-the $2\%$ level.
-
-This is a remarkable result. In spite of that the rotation axis
-defines preferential direction, the integrated flux is the same for
-all viewing angles, at least for the range of parameters explored in
-this paper.
+with $\tau_{\rm H}=10^{5}$, ifferent rotational velocities and the two
+types of source distributions.
+This Figure shows that $F(\mu)$ is consistent with being flat, apart
+from some statistical fluctuations on the order of \%2.
+
+This is a remarkable result. 
+In spite of that the rotation axis defines preferential direction, the
+integrated flux is the same for all viewing angles, at least for the
+range of parameters explored in this paper.
 
@@
 \caption{FWHM for the non-dusty models as a function of
-  rotational velocity $V_{\rm max}$. The left panel shows the
-  results in velocity units while the right panel normalizes
-  the data by the FWHM in the static case. 
+  rotational velocity $V_{\rm max}$ for observers located
+  perpendicular to the rotation axis. 
+  The left panel shows the results in velocity units while the right
+  panel normalizes the data by the FWHM in the static case. 
   Continuous (dashed) lines  correspond to central (homogeneous)
-  source distributions. The straight lines represent the fit to
-  the data using the expression in Eq. (\ref{eq:fwhm}).
+  source distributions. 
+  The straight lines represent the fit to the data using the
+  expression in Eq. (\ref{eq:fwhm}). 
   \label{fig:widthsvsvelocity}}
@@
 We use the full width at half maximum (FWHM) to quantify the line
-broadening. We measure this width from the velocity histogram by
-finding the values of the velocities at half maximum intensity. We use
-lineal interpolation between histogram points to get a value more precise
-than the bin size used to construct the line intensity.
+broadening. 
+We measure this width from the line intensity histogram by finding the
+values of the velocities at half maximum intensity.
+We use lineal interpolation between histogram points to get a value
+more precise than the bin size used to construct the histogram.
 
 Figure \ref{fig:widthvsmu} shows the FWHM for all models as a function
-of the viewing angle. The FWHM increases for decreasing values of
-$\mu$ and increasing values of $V_{\rm max}$. In Figure
-\ref{fig:widthvsvelocity} we fix $|\mu|<0.1$, i.e. viewing angle
-perpendicular to the rotation axis, and plot the FWHM as a
-function of rotational velocity.
-
-we parametrize the dependency of the line width with  $V_{\rm max}$ as
+of the viewing angle. 
+The FWHM increases for decreasing values of $\mu$ (movement from the
+poles to the equator) and increasing values of $V_{\rm max}$. 
+In Figure
+\ref{fig:widthsvsvelocity} we fix $|\mu|<0.1$, i.e. viewing angle
+perpendicular to the rotation axis, to plot the FWHM as a function of
+rotational velocity.
+
+Ee parametrize the dependency of the line width with  $V_{\rm max}$ as
 %
@@
 where FWHM$_{0}$ is the velocity width in the static case and $\lambda$ 
-is a positive scalar to be determined as a fit to the data.  With this
-test we want to know to what extent the new velocity width can be
+is a positive scalar to be determined as a fit to the data.  
+With this test we want to know to what extent the new velocity width can be
 expressed as a quadratic sum of the two relevant velocities in the
-problem. That all the models fall into two families of straight lines,
-for central and homogeneously emitted sources, justifies this choice
-of parameterization.
-
-We fit simultaneously all the points corresponding to each one of this
-families to find $\lambda_{\rm c} = 0.84 \pm 0.06$ and $\lambda_{\rm
-  h}= 0.54\pm 0.10$ respectively.
+problem.
+
+All the models fall into a single familiy of lines in the plane shown
+in the right panel of Figure \ref{fig:widthsvsvelocity}, justifying
+the choice of our parameterization.
+We fit simultaneously all the points in two separate groups, central
+and homogeneous sources.
+We find that these values are $\lambda_{\rm c} = 0.83 \pm 0.06$ and
+$\lambda_{\rm    h}= 0.82\pm 0.05$ respectively.
 
@@
 \appendix
-\section{Analytic Expression for Ly$\alpha$ Spectrum
+\section{Analytic Expression for the Ly$\alpha$ Spectrum
   emerging from Rotating Cloud}
@@
 rotation axis is identical for each hydrogen atom) proceeds identical
-as in a static cloud. While scattering events off atoms within the
-rotating cloud impart Doppler boosts on the Ly$\alpha$ photon, these
-Doppler boost are only there in the lab-frame. In the frame of the
-rotating gas cloud, all atoms are stationary w.r.t each other, and the
-scattering process proceeds identical as in the static
+as in a static cloud. 
+While scattering events off atoms within the rotating cloud impart
+Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only
+there in the lab-frame. 
+In the frame of the rotating gas cloud, all atoms are stationary w.r.t
+each other, an the scattering process proceeds identical as in the static
 case\footnote{An alternative - more quantitative way - to view this is
   to consider the path of an individual photon: say the photon travels
-  a distance corresponding to $\tau=1$, scatters by 90 degrees, then
+  a distance corresponding to $\tau=1$, scatters by $90$ degrees, then
   travels another distance corresponding to $\tau=1$. It is easy to
   show that the point where the photon ends up is independent of the
-  assumed rotation velocity of the cloud.}. This explains why the
-escape fraction of Ly$\alpha$ photon is independent of the rotation
-velocity off the cloud, irrespective of the rotation speed.
-
-The spectrum emerging of photons emerging from a rotating gas cloud is
+  assumed rotation velocity of the cloud.}. 
+This explains why the escape fraction of Ly$\alpha$ photon is
+independent of the rotation velocity off the cloud.
+
+The spectrum of \lya photons emerging from a rotating gas cloud is
 also identical as for the static case in a frame that is co-rotating
@@
 To provide an analytic description of this emerging spectrum, we adopt
-the geometry shown in Fig~1 (note this differs slightly from the main
-body of the paper. My `observer'  sits along the x-axis. I think yours
-sits along the z-axis. We have to makes sure this is done consistently
-throughout the paper).  
+the geometry shown in Fig~\ref{fig:scheme}. 
+Note that this differs from the scheme in Fig~1 from the main body of
+the paper.
+
 \begin{figure*}[h]
@@
 \end{figure*}
+
 The sightline to the observer \& rotation define the $x-z$ plane. 
-The observer sits along the axis.
-The {\it left panel} in Fig~1 shows the view from the $y-axis$.
-The rotation axis makes an angle $i$ with respect to the z-axis.
-We sum up spectra from individual patches by integrating over the impact parameter $b$, and angle $\phi$.
+The {\it left panel} in Fig~\ref{fig:scheme} shows the view from the $y$-axis. 
+The observer sits along the $x$ axis. 
+The rotation axis makes an angle $i$ with respect to the $z$-axis. 
+We sum up spectra from individual patches by integrating over the
+impact parameter $b$, and angle $\phi$. 
 Each $(b,\phi)$ corresponds to a point on the sphere. 
-This point has a velocity vector ${\bf v}(b,\phi,i)$, which we denote with ${\bf v}$ for brevity.
+This point has a velocity vector ${\bf v}(b,\phi,i)$, which we denote
+with ${\bf v}$ for brevity.
+
+The intensity at the surface point $(b,\phi)$ is
+
+\begin{displaymath}
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
+    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
+      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)},
+\end{displaymath} 
+%
+where $x_b\equiv v_{b}/v_{\rm th}$, and $v_b$ is the component of ${\bf v}$ projected onto the line-of-sight. This component is given by
+\begin{equation}
+v_{\rm b}(b,\phi,i)=V_{\rm max}\sqrt{1-(b/R)^2\cos^2 \phi}\hs \cos i
+\hs \sin a,
+\end{equation}
+%
+where
+
+\begin{equation}
+\tan a = \frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
+\end{equation}
+
+In order to compute to total intensity we integrate over $b$ and
+$\phi$ with a weight wigen by the surface brightness of the
+sphere at $(b,\phi)$, $S(b,\phi)$.
 
@@
 S(b,\phi)J(x,b,\phi,i) \approx 2\pi \int_0^Rdb \hs b
-\int_0^{2\pi}d\phi \hs J(x,b,\phi,i)\\ \nonumber
+\int_0^{2\pi}d\phi \hs J(x,b,\phi,i)\\ \nonumber.
 \end{displaymath}
-
-\begin{displaymath}
-J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)} 
-\end{displaymath}
-
-The velocity $v_b$ is the component of ${\bf v}$ projected onto the line-of-sight. This component is given by
-\begin{equation}
-v_{\rm b}(b,\phi,i)=v_{\rm rot}\sqrt{1-(b/R)^2\cos^2 \phi}\hs \cos i
-\hs \sin \beta 
-\end{equation}
-
-\begin{equation}
-\tan \beta= \frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
-\end{equation}
 %
-The quantity $S(b,\phi)$ denotes the surface brightness of the sphere at $(b,\phi)$.
-We have assumed in our analytic calculations that $S(b,\phi)$ is constant.
-The assumption $S(b,\phi)=$ constant corresponds to $I(\mu) \propto \mu$ at the surface, where $\mu$ denotes the cosine of the angle of the propagation direction of the outgoing photon and the normal to the spheres surface: a fixed $db$ corresponds to a physical length $ds = db/\mu$ on the sphere.
-If $I(\mu)$ were constant, this would imply that the sphere should appear brighter per unit $b$.
-A constant surface brightness profile requires the directional dependence for $I(\mu) \propto \mu$ to correct for this.
-Indeed, this is what is expected for the escape of Ly$\alpha$ photons from static, extremely opaque media (see Ahn, Lee \& Lee, 2001; their Fig~4 and accompanying discussion).
-
-It is worth stressing that the analytic calculation is clearly not a complete analytic calculation, and we do not expect perfect agreement: we {\it assumed} a functional form for the surface brightness profile [or for $I(\mu)$].
-It is important to realise that $I(\mu)$ itself may depend on the spectrum.
-I.e., analytic solutions exist for $J(x) = \int_0^1 I(x,\mu) d\mu$ at the boundary, and {\it approximate} expressions for $I(\mu) =\int dx I(x,\mu)$, but none for $I(x,\mu)$ itself.
-\\
-
-Fig~2 shows some examples of analytic vs.
-full MC spectra.
-The area under all spectra are normalised to $1$.
-The MC simulations used $10^5$ photons.
-The two methods clearly give good agreement, though not perfect.
-In particular, Fig~3 shows that the MC gives rise to a spectrum that is slightly more concentrated to the centre.
-It is easy to get better agreement my modifying the surface brightness profile (e.g.
-if $S(b)=2-b$, then the analytic calculation agrees better) In any case, the analytic calculation closely captures the results obtained from the full calculations from the MC simulations.
-As such, they are extremely useful \& provide us with a quick tool to verify our calculations at the first order level.
+In the last expression we assume that $S(b,\phi)$ is constant. 
+This corresponds to $I(\mu) \propto \mu$ at the surface, where $\mu$
+denotes the cosine of the angle of the propagation direction of the
+outgoing photon and the normal to the spheres surface: a fixed $db$
+corresponds to a physical length $ds = db/\mu$ on the sphere.  
+If $I(\mu)$ were constant, this would imply that the sphere should
+appear brighter per unit $b$. 
+A constant surface brightness profile requires the directional
+dependence for $I(\mu) \propto \mu$ to correct for this. 
+Indeed, this is what is expected for the escape of Ly$\alpha$ photons
+from static, extremely opaque media (see \cite{Ahn01}; their
+Fig~4 and accompanying discussion).
+
+It is worth stressing that the analytic calculation is clearly not a
+complete analytic calculation, and we do not expect perfect agreement:
+we {\it assumed} a functional form for the surface brightness profile
+[or for $I(\mu)$].
+
+It is important to realise that $I(\mu)$ itself may
+depend on the spectrum. I.e., analytic solutions exist for $J(x) =
+\int_0^1 I(x,\mu) d\mu$ at the boundary, and {\it approximate}
+expressions for $I(\mu) =\int dx I(x,\mu)$, but none for $I(x,\mu)$
+itself.
+
+Fig~\ref{fig:comparison}shows some examples of analytic vs. full MC
+spectra.
+The area under the spectra is the same in all cases. 
+The left panel shows the results for different rotational velocitiies
+in the case of $\tau_{H}=10^7$ and an observer located perpendicular
+to the axis of rotation ($\mu=0$ in the notation of the main body of
+the paper, $i=0$ in the scheme of Fig~\ref{fig:scheme}). 
+The right panel shows the results for different viewing angles in the
+case of $\tau_{H}=10^7$ and a rotational velocity of $V_{\rm
+  max}=300$\kms.
+
+The two methods clearly give good agreement, though not perfect. In
+particular, the left panel shows that the MC gives rise to a spectrum that is
+slightly more concentrated towards the line centre. 
+It is easy to get better agreement my modifying the surface brightness
+profile (e.g. if $S(b)=2-b$, then the analytic calculation agrees
+better).
+In any case, the analytic calculation closely captures the results
+obtained from the full calculations from the MC simulations.  
+As such, they are extremely useful and provide us with a quick tool to
+verify our calculations at the first order level.
 
@@
 \caption{
-Comparison of the Monte Carlo results agains the analytic solution.
+Comparison of the Monte Carlo results agains the analytic
+solution. The left panel explores the results of different velocities.
+The right panel presents the results for two different observers:
+paralel and perpendicular to the rotationa axsi, $\mu=1$ and $\mu=0$
+respectively.
 \label{fig:comparison} }   

### 2014-06-17 paper/ms.tex
new revised version

@@
 Notably, we find that rotation does not induce any significant spatial
-anisotropy in the integrated line flux nor in the escape fraction. 
-We provide an analytical expression for the outgoing \lya spectrum of
+anisotropy in the integrated line flux, in the escape fraction or the
+average number of scatterings. 
+We also provide an analytical expression for the outgoing \lya spectrum of
 a rotating cloud which accounts for the velocity and viewing angle
-trends observed in the simulations.
+trends observed in our Monte Carlo simulations.
 \end{abstract}
@@
 
-Ee parametrize the dependency of the line width with  $V_{\rm max}$ as
+We parametrize the dependency of the line width with  $V_{\rm max}$ as
 %
@@
   of $x_{\rm     max}=0$ indicates that line becomes single
-  peaked. \label{fig:maximumsvsvelocity}}
+  peaked. \label{fig:maximumvsvelocity}}
 \end{figure*}
 
-We measure the peak maxima position to quantify the transition from
-double into single peak profiles. We do this as a function of the viewing angle
-$\theta$ for different rotational velocities. The results are
-summarized in Figure  \ref{fig:maximumsvsvelocity}. There are two
-interesting features that deserve attention. First, for a viewing angle
-parallel to the rotational axis ($\mu\sim 1.0$) the maxima of all
-models are similar regardless of the rotational velocity. Second, at a
-viewing angle perpendicular to the rotation axis ($\mu\sim 0.0$) a
-good fraction of models become single peaked. This feature appears
-more frequently for homogeneously distributed sources if all the
-other parameters are equal.
+We measure the peak maxima position, $x_m$, to quantify the transition from
+double into single peak profiles. 
+In Figure \ref{fig:maximumvsvelocity} we show the dependence of $x_m$ with
+the viewing angle parameterized by $|\cos\theta|$ for different
+rotational velocities.
+There are two interesting features that deserve attention. 
+First, for a viewing angle parallel to the rotational axis ($\mu\sim
+1.0$) the maxima of all models with the same kind of source
+initialization are similar regardless of the rotational velocity.  
+Second, at a viewing angle perpendicular to the rotation axis ($\mu\sim 0.0$) a
+large fraction of models become single peaked. 
+This feature appears more frequently for homogeneously distributed
+sources if all the other parameters are equal.
 
@@
 \begin{center}
-\begin{tabular}{c ccc ccc}
+\begin{tabular}{c cccccc}
 \hline \hline
-Source & $\tau_{H}$ & & & $\ V_{\rm max}$& & \\
-Distribution& &  &  & (\kms) & & \\ 
-& & 0 & 50 & 100 &200 & 300\\ \hline 
-Homogeneous & $10^{5}$& 0.263 & 0.266 &  0.309 &  0.357 &  0.370  \\
-            & $10^{6}$ & 0.289 &  0.289 &   0.309 &  0.360 &  0.393 \\
-            &$10^{7}$ &  0.227 &  0.229 &  0.231 &  0.254 &  0.281 \\
-Central & $10^{5}$ &  0.096 & 0.097 & 0.096 &  0.096 & 0.096 \\
-  		&$10^{6}$ & 0.066 & 0.066 &  0.066 &  0.066 &  0.066 \\
- 		&$10^{7}$ & 0.015 &  0.016 & 0.016 & 0.016 & 0.015 \\
+Source & $\tau_{H}$ & &  $\ V_{\rm max}$& & \\
+Distribution& &    & (\kms) & & \\ 
+& & 0 & 100 &200 & 300\\ \hline 
+Homogeneous & $10^{5}$& 0.263 &  0.263 &  0.263 &  0.263  \\
+            & $10^{6}$ & 0.291 &   0.292 &  0.293 &  0.293 \\
+            &$10^{7}$ &  0.228 &  0.228 &  0.228 &  0.228 \\
+Central & $10^{5}$ &  0.096 & 0.096 &  0.096 & 0.096 \\
+  		&$10^{6}$ & 0.066 &  0.066 &  0.066 &  0.066 \\
+ 		&$10^{7}$ & 0.015 & 0.016 & 0.016 & 0.015 \\
 \hline
@@
 
-%\begin{figure*}
-%\begin{center}
-%  \includegraphics[width=0.40\textwidth]{f10.pdf}
-%  \includegraphics[width=0.40\textwidth]{f11.pdf}
-%\end{center}
-%  \caption{Effects of rotation on the escape fraction. Left
-%    panel, escape fraction as a function of rotational velocity. All
-%    these models have $\tau_{a}=1$. The continuous (dashed) lines
-%    correspond to central (homogeneous) models. Right panel, escape
-%    fraction as a    function of the product $(a\tau_{\rm
-%      H})^{1/3}\tau_{A}$. The    analytic solution for the infinite
-%    slab is shown as a continuous line. Different lines correspond
-%    to different rotational velocities for the homogeneous models.     
-%    \label{fig:escape_fraction}} 
-%\end{figure*}
-
 We now estimate the escape fraction $f_{\rm esc}$ for the dusty
-models. The main  result is that we do not find any dependence
-with the viewing angle but there is a strong dependence with the
-rotational velocity for the homogeneous models.
-
-The left panel in Figure \ref{fig:escape_fraction} summarizes the
-findings about the dependence with the rotational velocity. The left
-panel shows the escape fraction as a function of the rotational
-velocity. To construct this Figure we take into account all the
-photons regardless of its outgoing direction. We observe that the 
-curves for the central source distribution stay flat, while for the
-homogeneous case there is a clear rise with rotational velocity.
-Rotation has a higher relative impact in the models with low optical
-depth. For instance, in models with $\tau_{\rm H}=10^5$, the static
-escape fraction is $0.26$ and increases to $0.37$ for $V_{\rm
-  max}=300$ \kms. Table \ref{table:escape} lists all the values for
-the escape fraction.
-
-In the right panel of Figure \ref{fig:escape_fraction} we put these
-results in the context of the analytic solution for the infinite slab
-\citep{Neufeld90}. In Neufeld's set-up the analytic solution depends
+models. 
+The main  result is that we do not find any significant dependence
+with either the viewing angle nor the rotational velocity.  
+For completeness we list in Table \ref{table:escape} the scape
+fraction for all models.
+
+We now put these results in the context of the analytic solution for
+the infinite slab\citep{Neufeld90}.   
+In Neufeld's set-up the analytic solution depends
 uniquely on the product $(a\tau_{\rm   H})^{1/3}\tau_{A}$ where
 $\tau_{A} = (1 - A)\tau_{a}$, valid only in the limit $a\tau_{\rm
-  H}\gg 1$. The dashed lines in  the right panel of Figure
-\ref{fig:escape_fraction} show the results for the different
-rotational velocities for the homogeneous models. First of all we note
-that the escape fraction increases slightly from $\tau_{\rm H}=10^5$ to
-$\tau_{\rm H}=10^{6}$, which is counterintuitive as we expected that increasing
-$\tau_{\rm H}$ requires more scattering before the photon escapes, which would
-increase the probability that photons are destroyed by dust.
-
-However, this naive interpretation is incorrect: increasing $\tau_{\rm
-  H}$ from $10^{5}$ to $10^{6}$ causes us to transition from the
-'optically thick' to  the 'extremely optically thick'
-  regime. In the optically thick regime, Lya  photons can escape in
+  H}\gg 1$. 
+At fixed values of $\tau_{a}$ the escape fraction monotonically
+decreases with increasing values of $\tau_{\rm H}$. 
+This expectation holds for the central sources. 
+But in the case of homogeneous sources the escape fraction increases
+slightly from $\tau_{\rm H}=10^5$ to $\tau_{\rm H}=10^{6}$
+
+The naive interpretation of the analytic solution does not seem to
+hold for photons emitted far from the sphere's center. 
+We suggest that increasing $\tau_{\rm H}$ from $10^{5}$ to $10^{6}$ causes a
+transition from the 'optically thick' to  the 'extremely optically
+thick' regime for a noticeable fraction of the photons in the
+homogeneous source distribution.
+
+In the optically thick regime, \lya  photons can escape in
 'single flight' which corresponds to a scenario in which the
 photon resonantly scatters $10^4-10^5$ times until it is scattered
-  into the wing of the line ($x\sim 3-4$). At these frequencies the
-  medium is optically thin, and the photons can escape efficiently in
-  a single flight. In contrast, in an extremely optically thick medium \ly
-  photons escape in a `single excursion' \citep{Adams72}. Here, photons
-that are scattered into the wing of the line escape from the medium in
-a sequence of wing scattering events.In both cases, \ly photons
-resonantly scatter $10^4$-$10^5$ times. Because we keep our clouds the same
-size, the mean free path of Lya photons that scatter resonantly is 10
-times larger for the case $\tau_{\rm H}=10^5$ than for $\tau_{\rm
-  H}=10^6$. If we compute the average distance $D$ travelled by \ly
+into the wing of the line ($x\sim 3-4$). 
+At these frequencies the medium is optically thin, and the photons can
+escape efficiently in a single flight. 
+In contrast, in an extremely optically thick medium \ly
+  photons escape in a `single excursion' \citep{Adams72}. 
+Here, photons that are scattered into the wing of the line escape from
+the medium in a sequence of wing scattering events. 
+In both cases, \ly photons resonantly scatter $10^4$-$10^5$ times. 
+Because we keep our clouds the same size, the mean free path of Lya
+photons that scatter resonantly is 10 times larger for the case
+$\tau_{\rm H}=10^5$ than for $\tau_{\rm H}=10^6$. 
+If we compute the average distance $D$ travelled by \ly
 photons through a medium of size $R$ as a function of line center
@@
 from optically thick to extremely optically thick the mean traversed
-distance $D$ actually decreases slightly.  This decrease is unique to
-this transition region, and $D$ generally increases with $\tau_{\rm H}$ at other
-values of $\tau_{\rm H}$.
+distance $D$ actually decreases slightly.  
+This decrease is unique to this transition region, and $D$ generally
+increases with $\tau_{\rm H}$ at other values of $\tau_{\rm H}$.
 
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{f14_1.pdf}
-  \includegraphics[width=0.48\textwidth]{f14_2.pdf}
-  \includegraphics[width=0.48\textwidth]{f14_3.pdf}
-  \includegraphics[width=0.48\textwidth]{f14_4.pdf}    
-\end{center}
-    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
-      show the homogeneous (central) source distribution. Left panels 
-      corresponds to the static case and right panels correspond to
-      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
-      number of photons with given values of $N_{\rm scatt}$ and
-      $x$. \label{fig:Nscatt2D}. }
+    \includegraphics[width=0.45\textwidth]{f12.pdf}
+    \includegraphics[width=0.45\textwidth]{f13.pdf}
+\end{center}
+\caption{Logarithm of the average number of scatterings as function of
+  $\mu$ (left panel) and the maximum rotational velocity $V_{\rm
+max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
+  $V_{max}=300$\kms as a function of $|\cos\theta|$; the independence of
+  $N_{\rm scatt}$ with $\mu$ is present in all models.
+  In the right panel the continuous (dashed) lines represent an
+  central (homogeneous) distribution of sources; there is a clear
+  decrease in the number of scatterings for the homogenously
+  distributed sources.
+\label{fig:Nscatt} }
 \end{figure*}
 
+%\begin{figure*}
+%\begin{center}
+%  \includegraphics[width=0.48\textwidth]{f14_1.pdf}
+%  \includegraphics[width=0.48\textwidth]{f14_2.pdf}
+%  \includegraphics[width=0.48\textwidth]{f14_3.pdf}
+%  \includegraphics[width=0.48\textwidth]{f14_4.pdf}    
+%\end{center}
+%    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
+%      show the homogeneous (central) source distribution. Left panels 
+%      corresponds to the static case and right panels correspond to
+%      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
+%      number of photons with given values of $N_{\rm scatt}$ and
+%      $x$. \label{fig:Nscatt2D}. }
+%\end{figure*}
+
 The number of scatterings affects the escape frequency of a \ly
-photon. Studying this quantity can help us in claryfying two results
-that we have observed for homogeneous models in the previous sections:
-the quick emergence of a single peak and the increase in the escape
-fraction.
-
-A possible explanation for these two results is that some photons
-close to the surface can escape with a low number of scatterings. This
-has a two consequences: the escaping photons do not have time to
-scatter away from the line's center and also have less chances to find
-an absorbing dust grain.
+photon. 
+Studying this quantity can help us in claryfying the independence of
+the integrated flux and the escape fraction with respect to the
+rotational velocity.
 
@@
 outgoing angle $|\cos\theta|$ and the rotational velocity
-$V_{\rm max}$. From the right panel observe that the number of
-scatterings and the outgoing angle are independent. This plot
-corresponds to the specific case of the central model with $\tau=10^5$ and
-$V_{\rm max}=300$\kms, but we have veryfied that this holds for all
-models. This allows us to construct statistics using all the outgoing
-photons regardless of their value of $\cos\theta$.
-
-The right panel of Figure \ref{fig:Nscatt} shows how the
-average number of scatterings decreases for larger rotational
-velocities in the case of homogeneous source distributions. For instance, for
-$\tau_{\rm H}=10^5$ the average number of scatterings decreases by
-$61\%$ at $V_{\rm max}=300\kms$ in comparison to the static case. For
-the central source distribution the average number of scatterings
-$\langle N_{\rm   scatt}\rangle$ changes less than $0.5\%$.
-
-In order to gain a deeper understanding of these results  we make 2D
-histograms for the number of scatterings as a function of the outgoing
-dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show these 
-results in the case $\tau_{\rm H}=10^5$ for the
-static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
-results for the homogeneous (central) source distribution. The color
-scale is logarithmic in the number of photons at a certain value
-$x-N_{\rm scatt}$.
-
-The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
-high rotational velocity) supports our hypothesis about
-the photo-sphere in the homogeneous distribution. In this case most of
-the photons that left with $x\sim 0$ have escaped with less than $10$
-scatterings. This also explains the decrease in the average number of
-scatterings observed in Figure \ref{fig:Nscatt}. We have also veryfied
-that these photons are indeed emitted closer to the surface than to
-the center of the sphere.
-
-However, for a central distribution the situation is quite different
-(lower panels in Figure \ref{fig:Nscatt2D}). In this case the number
-of scatterings remains high, in the order of the optical depth, but
-the two peaks do get closer to each other. The most probable
-physical picture is that each scattering, due to the bulk velocity of
-the gas, is inefficient in driving the photon outside the line
-center.
-
-We now proceed with a more detailed quantification of the number of
-scatterings in our simulations. We guide the measurement by the fact
-that in static cases, a large value of the optical depth correlates
-with a high number of scatterings.  This has been precisely quantified
-in the case of static infinite slab. In this model for centrally
-emitted sources the average number of scatterings depends only on the
-optical depth $\langle N_{\rm  scatt}\rangle=1.612\tau_{\rm   H}$
-\citep{Adams72,Harrington73}, for homogeneously distributed sources
-$\langle N_{\rm   scatt}\rangle=1.16\tau_{\rm   H}$
-\citep{Harrington73}.
-
-We perform a similar quantification of in our speherical setup for the
-static spheres. We find that for the central model the number of
+$V_{\rm max}$. 
+From the right panel observe that the number of scatterings and the
+outgoing angle are independent. 
+This plot corresponds to the specific case of the central model with
+$\tau=10^5$ and $V_{\rm max}=300$\kms, but we have veryfied that this
+holds for all models.
+
+The right panel of Figure \ref{fig:Nscatt} shows how the average
+number of scatterings is also independent from the rotational
+velocity. 
+The lower number of average scatterings in the homogeneous source
+distribution is due to a purely geometrical effect.
+Photons emitted close to the surface go through less scatterings
+before escaping.
+
+%In order to gain a deeper understanding of these results  we make 2D
+%histograms for the number of scatterings as a function of the outgoing
+%dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show these 
+%results in the case $\tau_{\rm H}=10^5$ for the
+%static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
+%results for the homogeneous (central) source distribution. The color
+%scale is logarithmic in the number of photons at a certain value
+%$x-N_{\rm scatt}$.
+
+%The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
+%high rotational velocity) supports our hypothesis about
+%the photo-sphere in the homogeneous distribution. In this case most of
+%the photons that left with $x\sim 0$ have escaped with less than $10$
+%scatterings. This also explains the decrease in the average number of
+%scatterings observed in Figure \ref{fig:Nscatt}. We have also veryfied
+%that these photons are indeed emitted closer to the surface than to
+%the center of the sphere.
+
+%However, for a central distribution the situation is quite different
+%(lower panels in Figure \ref{fig:Nscatt2D}). In this case the number
+%of scatterings remains high, in the order of the optical depth, but
+%the two peaks do get closer to each other. The most probable
+%physical picture is that each scattering, due to the bulk velocity of
+%the gas, is inefficient in driving the photon outside the line
+%center.
+
+In static configurations it is expected that the optical depth correlates number of
+scatterings.  
+This has been precisely quantified in the case of static infinite
+slab. 
+In that model for centrally emitted sources the average number of
+scatterings depends only on the optical depth $\langle N_{\rm
+  scatt}\rangle=1.612\tau_{\rm   H}$ \citep{Adams72,Harrington73}, for
+homogeneously distributed sources $\langle N_{\rm
+  scatt}\rangle=1.16\tau_{\rm   H}$ \citep{Harrington73}.
+
+In our case we find that for the central model the number of
 scatterings is proportional to the optical depth, with $\langle N_{\rm
@@
 values of $\tau_{\rm H} = (10^{5}, 10^{6}, 10^{7})$ respectively.
-For the homogeneous static sphere we find that $\langle N_{\rm
-  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$, this represents
-factors of $(0.66, 0.59, 0.55)$ lower than the centrally  emitted photons.
-
-For the homogeneous rotating sphere at  $V_{\rm{max}}=300\kms$ we find
-that $\langle N_{\rm   scatt}\rangle=(0.38, 0.34, 0.42)\tau_{\rm   H}$
-which represents   factors of $(0.26, 0.34, 0.46)$ lower than the
-corresponding central case.
+For the homogeneous sources we find that $\langle N_{\rm
+  scatt}\rangle= (0.99, 0.59, 0.51)\tau_{\rm   H}$.
 
@@
 
+\subsection{Towards an analytical description}
+
+There are three key results that allows us to build an analyitical description to
+first order of our results: the independence of the integrated flux,
+the number of scatterings and the escape fraction with the rotational
+velocity and the viewing angle.
+
+One way to understand these results is that actually a rotating sphere
+is not very different from a static one. We can think that in the
+frame of the rotating gas cloud all atoms are stationary with respect
+to each other, making the scattering process proceeed identical as in
+the static case.  
+While scattering events off atoms within the rotating cloud impart
+Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only
+there in the lab-frame.  
+In the frame of the rotating gas cloud, all atoms are stationary with
+respect to each othe and the scattering process proceeds identical as
+in the static case.
+
+An alternative - more quantitative way - to view this is   to consider
+the path of an individual photon: say the photon travels  a distance
+corresponding to $\tau=1$, scatters by $90$ degrees, then travels
+another distance corresponding to $\tau=1$. 
+It is easy to show that the point where the photon ends up is
+independent of the assumed rotation velocity of the cloud.
+
+The spectrum of \lya photons emerging from a rotating gas cloud is
+also identical as for the static case in a frame that is co-rotating
+with the cloud. However, the surface of cloud now moves in the
+lab-frame. Each surface-element on the rotating cloud now has a bulk
+velocity with respect to a distant observer. In order to compute the
+spectrum one can integrate over all the surface elements in the
+sphere with their corresponding shift in velocity and an additional
+weight by the surface intensity.
+
+Fig~\ref{fig:comparison} shows some examples of analytic vs. full MC
+spectra using this approach (the implementation details are in the Appendix).
+The left panel shows the results for different rotational velocitiies
+in the case of $\tau_{H}=10^7$ and an observer located perpendicular
+to the axis of rotation ($i=0$ in the scheme of Fig~\ref{fig:scheme}
+in the Appendix). 
+The right panel shows the results for different viewing angles in the
+case of $\tau_{H}=10^7$ and a rotational velocity of $V_{\rm
+  max}=300$\kms.
+
+The two methods clearly give good agreement, though not perfect. In
+particular, the left panel shows that the MC gives rise to a spectrum that is
+slightly more concentrated towards the line centre. 
+It is easy to get better agreement my modifying the surface brightness
+profile (e.g. if $S(b)=2-b$, then the analytic calculation agrees
+better).
+In any case, the analytic calculation closely captures the results
+obtained from the full calculations from the MC simulations.  
+As such, they are extremely useful and provide us with a quick tool to
+verify our calculations at the first order level.
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{fig10a.pdf}
+  \includegraphics[width=0.49\textwidth]{fig10b.pdf}
+\end{center}
+\caption{
+Comparison of the Monte Carlo results agains the analytic
+solution. The left panel explores the results of different velocities.
+The right panel presents the results for two different observers:
+paralel and perpendicular to the rotationa axsi, $\mu=1$ and $\mu=0$
+respectively.
+\label{fig:comparison} }   
+\end{figure*}
+
+\subsection{Impact on the interpretation of simulated and
+  observational data}
+
 We now compare our findings to other computational results and discuss
@@
 line emission in two high resolution simulations of individual
-galaxies. The main purpose of their study was to assess the impact of
-two different Inter-Stellar Medium (ISM) prescriptions. However, each
-simulated galaxy had a disc structure with a clear rotation pattern in
-the ISM and inflowing gas from the circum-galactic region. The configuration
-had an axial symmetry and they reported a strong dependence of both
+galaxies. 
+The main purpose of their study was to assess the impact of two
+different Inter-Stellar Medium (ISM) prescriptions. 
+However, each simulated galaxy had a disc structure with a clear rotation pattern in
+the ISM and inflowing gas from the circum-galactic region. 
+The configuration had an axial symmetry and they reported a strong dependence of both
 the escape fraction and the total line intensity as a function of the
-$\theta$ angle. In our results, none of these two quantities has a
-dependence either on the inclination angle or the rotational
-velocity. We suggest that he effect reported by \cite{Verhamme12} is
+$\theta$ angle. 
+From our study, none of these two quantities has a dependence either
+on the inclination angle or the rotational velocity. 
+We suggest that he effect reported by \cite{Verhamme12} is
 consistent with being a consequence of the different hydrogen optical
@@
 
+{\bf Zero impact on the \ly escape fraction}. Study of
+high redshift LAEs in numerical simulation often requires the
+estimation of the \ly escape fraction in order to compare their
+results against observations
+\citep{CLARA,Dayal2012,Forero12,Orsi12,Garel2012}. Most of these
+models estimate the escape fraction from the column density of dust and
+neutral Hydrogen. The results of our simulation suggest that the
+rotational velocity does not induce additional uncertainties in those
+estimates.
+
 {\bf Single peaked lines}. The presence of single peaked profiles has
 been associated to inflow/outflow dynamics
-\citep{Verhamme06,DijkstraKramer}. In this paper we show that gas bulk
-rotation can also be considered as a probable origin for that
+\citep{Verhamme06,DijkstraKramer}. 
+Gas bulk rotation can also be considered as a probable origin for that
 behavior, provided that the observed single peak is highly
-symmetric. Similarly, in the case of double peaked lines with a high
+symmetric. 
+Similarly, in the case of double peaked lines with a high
 level of flux at the line center, rotation also deserves to be
 considered in the pool of possible bulk flows responsible for that feature,
-specially if the two peaks have similar intensities. This highlights
+specially if the two peaks have similar intensities. 
+This highlights
 that in order to interpret the observations of \ly emitting galaxies
@@
 
-{\bf Additional uncertainty on the \ly escape fraction}. Study of
-high redshift LAEs in numerical simulation often requires the
-estimation of the \ly escape fraction in order to compare their
-results against observations
-\citep{CLARA,Dayal2012,Forero12,Orsi12,Garel2012}. Most of these
-models estimate the escape fraction from the column density of dust and
-neutral Hydrogen. The results of our simulation suggest that the
-rotational velocity has also to be accounted for, having an impact on
-the values of the escape fractions by factors of $\sim 2$.
-
 \section{Conclusions}
@@
 In this paper we quantified for the first time in the literature the effects
-of gas bulk rotation in the morphology of the \ly emission line in star forming
-galaxies.  Our results are based on the study of an homogeneous sphere
-of gas with solid body rotation. We explore a range of models by varying
-the rotational speed, hydrogen optical depth, dust optical depth and
-initial distribution of \ly photons with respect to the gas
-density. As a cross-validation, we obtained our results from two
-independently developed Monte-Carlo radiative transfer codes.
-
-Two conclusions stand out from our study. First, rotation clearly
-impacts the \ly line morphology; the width and the relative intensity
-of the center of the line and its peaks are affected. Second, rotation introduces an
-anisotropy for different viewing angles. For viewing angles close to
-the poles the line is double peaked and it makes a transition to a
-single peaked line for high rotational velocities and viewing angles
-along the equator. This trend is clearer for spheres with
-homogeneously distributed radiation sources than it is for central
-sources.
-
-Remarkably, we find two quantities that are invariant with respect
-to the viewing angle and the rotational velocity: the integrated flux and the escape
-fraction.  The exception is the models with homogeneously distributed
-sources, which present an escape fraction dependent on the rotational
-velocity, but still independent of the viewing angle. We showed that
-these results could be interpreted in terms of the average number of
-scatterings for the photons.
+of gas bulk rotation in the morphology of the \ly emission line in
+star forming galaxies.   
+Our results are based on the study of an homogeneous sphere
+of gas with solid body rotation. 
+We explore a range of models by varying the rotational speed, hydrogen
+optical depth, dust optical depth and initial distribution of \ly
+photons with respect to the gas density. 
+As a cross-validation, we obtained our results from two independently
+developed Monte-Carlo radiative transfer codes.
+
+Two conclusions stand out from our study. 
+First, rotation clearly impacts the \ly line morphology; the width and
+the relative intensity of the center of the line and its peaks are
+affected. 
+Second, rotation introduces an anisotropy for different viewing
+angles. 
+For viewing angles close to the poles the line is double peaked and it
+makes a transition to a single peaked line for high rotational
+velocities and viewing angles along the equator. 
+This trend is clearer for spheres with homogeneously distributed
+radiation sources than it is for central sources.
+
+Remarkably, we find three quantities that are invariant with respect
+to the viewing angle and the rotational velocity: the integrated flux,
+the escape fraction and the average number of scatterings.
+These results helped us to construct the outgoing spectra of a
+rotating sphere as a supeposition of spectra coming from a static
+configuration. This description is useful to describe the main
+quantitative features of the Monte Carlo simulations.
 
@@
   width for the static case and $\lambda$ is a constant. We have
-  determined this constant to be  $\lambda_{\rm c}=0.84 \pm 0.06$ and
-  $\lambda_{\rm h}=0.54\pm 0.10$ for the central and homogeneous source
+  determined this constant to be  $\lambda_{\rm c}=0.83 \pm 0.06$ and
+  $\lambda_{\rm h}=0.82\pm 0.05$ for the central and homogeneous source
   distributions, respectively.
@@
   increases, i.e. the smallest value of the line width is observed for
-  a line of sight parallel to the ration axis. However the lowest
-  values are always larger than the values for the static case.
-
-\item The single peaked line emerges for homogeneously distributed sources 
-  when the rotational velocity is larger than half FWHM$_0$ and $\mu\sim
-  1$.
-
-\item  For central sources we find that the escape fraction does not change
-  with rotational velocity nor with the viewing angle. We interpret this
+  a line of sight parallel to the ration axis.
+
+\item The single peaked line emerges at viewing angles $\mu\sim 1$ for
+  when the rotational velocity is close to than half the FWHM$_0$.
+
+\item  The escape fraction does not change with rotational velocity
+  nor with the viewing angle. We interpret this
   in terms of the average number of scatterings which does not
@@
 
-\item For homogeneous sources we find that the  as rotational velocity
-  increases, the escape fraction rises by a factor of $\sim 2$ with
-  respect to the static situation. We also interpret this change in
-  terms of the average number of scatterings. In the second part of \S
-  \ref{sec:widthpeak} we show that the average number of scatterings
-  decreases a $40\%$ compared to the static case, while a large
-  fraction of photons escape with less than $10$ scatterings.
-
 \end{itemize}
 
-Comparing our results with recent observed LAEs we find that many 
+Comparing our results with recent observed LAEs we find that 
 morphological features such as high central line flux, single peak
@@
 as in a static cloud. 
-While scattering events off atoms within the rotating cloud impart
-Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only
-there in the lab-frame. 
-In the frame of the rotating gas cloud, all atoms are stationary w.r.t
-each other, an the scattering process proceeds identical as in the static
-case\footnote{An alternative - more quantitative way - to view this is
-  to consider the path of an individual photon: say the photon travels
-  a distance corresponding to $\tau=1$, scatters by $90$ degrees, then
-  travels another distance corresponding to $\tau=1$. It is easy to
-  show that the point where the photon ends up is independent of the
-  assumed rotation velocity of the cloud.}. 
-This explains why the escape fraction of Ly$\alpha$ photon is
-independent of the rotation velocity off the cloud.
-
-The spectrum of \lya photons emerging from a rotating gas cloud is
-also identical as for the static case in a frame that is co-rotating
-with the cloud. However, the surface of cloud now moves in the
-lab-frame. Each surface-element on the rotating cloud now has a bulk
-velocity w.r.t a distant observer. In order to compute the spectrum
-emerging from this rotation cloud, we have to sum over all surface
-elements (weighted by their intensity).
+In order to compute the spectrum emerging from this rotation cloud, we
+have to sum over all surface elements weighted by their intensity.
 
@@
 \begin{figure*}[h]
-\centerline{\includegraphics[width=85mm]{scheme1.pdf}
-\includegraphics[width=85mm]{scheme2.pdf}}
+\centerline{\includegraphics[width=85mm]{fig11a.pdf}
+\includegraphics[width=85mm]{fig11b.pdf}}
 \caption[]{Adopted geometry for evaluating the analytic spectrum.}
@@
 
-Fig~\ref{fig:comparison}shows some examples of analytic vs. full MC
-spectra.
-The area under the spectra is the same in all cases. 
-The left panel shows the results for different rotational velocitiies
-in the case of $\tau_{H}=10^7$ and an observer located perpendicular
-to the axis of rotation ($\mu=0$ in the notation of the main body of
-the paper, $i=0$ in the scheme of Fig~\ref{fig:scheme}). 
-The right panel shows the results for different viewing angles in the
-case of $\tau_{H}=10^7$ and a rotational velocity of $V_{\rm
-  max}=300$\kms.
-
-The two methods clearly give good agreement, though not perfect. In
-particular, the left panel shows that the MC gives rise to a spectrum that is
-slightly more concentrated towards the line centre. 
-It is easy to get better agreement my modifying the surface brightness
-profile (e.g. if $S(b)=2-b$, then the analytic calculation agrees
-better).
-In any case, the analytic calculation closely captures the results
-obtained from the full calculations from the MC simulations.  
-As such, they are extremely useful and provide us with a quick tool to
-verify our calculations at the first order level.
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{vary_vel.pdf}
-  \includegraphics[width=0.48\textwidth]{vary_angle.pdf}
-\end{center}
-\caption{
-Comparison of the Monte Carlo results agains the analytic
-solution. The left panel explores the results of different velocities.
-The right panel presents the results for two different observers:
-paralel and perpendicular to the rotationa axsi, $\mu=1$ and $\mu=0$
-respectively.
-\label{fig:comparison} }   
-\end{figure*}
-
 \bibliographystyle{apj}

### 2014-06-25 paper/ms.tex
version to the coauthors
edits by mark, updates in the analytical solution

@@
   nor with the viewing angle. We interpret this
-  in terms of the average number of scatterings which does not
-  significantly change with rotation. This is due to the  
+  in terms of the average number of scatterings which do not 
+  significantly change with rotation or viewing angle. This is due to the  
   fact that the vast majority of scatterings events are resonant, 
@@
 
-Ly$\alpha$ scattering through a an optically thick gas cloud that is
-undergoing solid-body rotation (i.e. the angular speed around the
+Ly$\alpha$ scattering through an optically thick gas cloud that is
+undergoing solid-body rotation (i.e. in which the angular speed around the
 rotation axis is identical for each hydrogen atom) proceeds identical
-as in a static cloud. 
-In order to compute the spectrum emerging from this rotation cloud, we
-have to sum over all surface elements weighted by their intensity.
-
-To provide an analytic description of this emerging spectrum, we adopt
-the geometry shown in Fig~\ref{fig:scheme}. 
-Note that this differs from the scheme in Fig~1 from the main body of
+as in a static cloud. In order to compute the spectrum emerging from a rotating cloud, we sum
+the spectra emerging from all surface elements of the cloud, weighted by their intensity.
+
+We adopt the geometry shown in Fig~\ref{fig:scheme} to derive an analytic expression of this emerging spectrum,
+Note that this geometry differs from the scheme shown in Fig~1 in the main body of
 the paper. 
-
+%
 \begin{figure*}[h]
@@
 \end{figure*} 
-
-The sightline to the observer \& rotation define the $x-z$ plane. 
+%
+The sightline to the observer \& rotation axis define the $x-z$ plane. 
 The {\it left panel} in Fig~\ref{fig:scheme} shows the view from the $y$-axis. 
@@
 with ${\bf v}$ for brevity.
-
-The intensity at the surface point $(b,\phi)$ is
+The magnitude of ${\bf v}$ is $|{\bf v}|=V_{\rm max}R'/R$.
+Here $R'=\sqrt{R^2 -s^2}$, in which $s$ denotes the distance of the point $(b,\phi)$ to the plane perpendicular to the rotation axis and through the origin (see the {\it left panel} of Fig~\ref{fig:scheme}).
+This distance $s$ is given by $s=|-\sin i\sqrt{R^2-b^2}+ b \cos \phi \cos i|$.\\
+
+The spectrum of the flux emerging from the surface at point $(b,\phi)$ is
 
@@
 \begin{equation}
-v_{\rm b}(b,\phi,i)=V_{\rm max}\sqrt{1-(b/R)^2\cos^2 \phi}\hs \cos i
-\hs \sin a,
+v_{\rm b}(b,\phi,i)=V_{\rm max}\frac{\sqrt{R^2 -s^2}}{R}\cos i  \hs \cos a,
+\end{equation} where the factor $\cos i$ accounts for the projection onto the $x-y$ plane, and the factor $\cos a$ for the subsequent projection onto the line-of-sight.
+The {\it right panel} of Figure~\ref{fig:scheme} shows that this angle $a$ can be computed from
+%
+\begin{equation}
+\tan [90^{\circ}- a]=\frac{c}{d}=\frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
 \end{equation}
-%
-where
-
-\begin{equation}
-\tan a = \frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
-\end{equation}
 
 In order to compute to total intensity we integrate over $b$ and
-$\phi$ with a weight wigen by the surface brightness of the
+$\phi$ with a weight given by the surface brightness of the
 sphere at $(b,\phi)$, $S(b,\phi)$.
@@
 Indeed, this is what is expected for the escape of Ly$\alpha$ photons
-from static, extremely opaque media (see \cite{Ahn01}; their
+from static, extremely opaque media (see \citet{Ahn01}; their
 Fig~4 and accompanying discussion).
 
-It is worth stressing that the analytic calculation is clearly not a
+It is worth stressing that this derivation should not be viewed as a
 complete analytic calculation, and we do not expect perfect agreement:
 we {\it assumed} a functional form for the surface brightness profile
-[or for $I(\mu)$].
-
-It is important to realise that $I(\mu)$ itself may
-depend on the spectrum. I.e., analytic solutions exist for $J(x) =
-\int_0^1 I(x,\mu) d\mu$ at the boundary, and {\it approximate}
-expressions for $I(\mu) =\int dx I(x,\mu)$, but none for $I(x,\mu)$
-itself.
+[or for $I(\mu)$]. Moreover, $I(\mu)$ itself may depend on frequency $x$. In other words, analytic solutions exist for $J(x) =
+\int_0^1 I(x,\mu) d\mu$ at the boundary of the sphere, and {\it approximate}
+expressions for $I(\mu) =\int dx I(x,\mu)$, but {\it not} for $I(x,\mu)$
+itself. The spectra we obtained from the Monte-Carlo calculations naturally include the proper $I(x,\mu)$, and are therefore expected to be more accurate.
 

### 2014-06-25 code/analytic_solution.c
new implementation of the analytic solution in C

@@ -78,16 +78,18 @@ int main(int argc, char **argv){
 
 double J_surface(double x, double b, double phi, double i_angle, double tau0, double v_rot){
   double final, v_thermal, a;
-  double beta, x_b, arg_in;
+  double beta, x_b, arg_in, s;
 
   v_thermal = 12.85*sqrt(TEMP/10000.0);
   a = 4.7E-4*(12.85/v_thermal);
   
-   beta = atan(b*sin(phi)/sqrt(R*R - b*b));
-  
-  x_b = (v_rot/v_thermal) * sqrt(1.0- (b/R)*(b/R)*(cos(phi)*cos(phi))) * 
-    cos(i_angle) * sin(beta);
-  
+  beta = PI/2.0 - atan(b*sin(phi)/sqrt(R*R - b*b));
+
+  s = abs((-sin(i_angle) * sqrt(R*R - b*b)) + (b * cos(phi) * cos(i_angle)));  
+
+  x_b = (v_rot/v_thermal) * sqrt(1.0- (s/R)*(s/R)) * cos(i_angle) * cos(beta);  
+
+
   arg_in = pow(fabs(x-x_b),3.0)/(a*tau0);
   arg_in = arg_in * sqrt((2.0*PI*PI*PI)/27.0);
   final = pow((x-x_b),2)/(1.0+cosh(arg_in)) * (sqrt(PI)/(sqrt(24.0)*a*tau0));

### 2014-06-25 code/analytic_solution.c
minor update in C analytic code to have less x points

@@ -1,7 +1,8 @@
 #include <stdio.h>
 #include <math.h>
 #include <stdlib.h>
-#define NPOINTS 500
+#define NPOINTS 1000
+#define NPOINTSX 100
 #define TEMP 10000.0
 #define R 1.0
 #define PI 3.141592653589793238462643383279502884197169
@@ -27,7 +28,7 @@ int main(int argc, char **argv){
   double *j_int;
   double min_x=-50.0;
   double max_x= 50.0;
-  double delta_x = (max_x-min_x)/NPOINTS;
+  double delta_x = (max_x-min_x)/NPOINTSX;
   double delta_phi = 2.0*PI/NPOINTS;
   double delta_b = 0.9999/NPOINTS;
   double tau, v_rot, i_angle;
@@ -45,7 +46,7 @@ int main(int argc, char **argv){
   
   fprintf(stderr, "%f %f %f\n", tau, v_rot, i_angle);
 
-  if(!(x=malloc(sizeof(double)*NPOINTS))){
+  if(!(x=malloc(sizeof(double)*NPOINTSX))){
     fprintf(stderr, "Problem with memory allocation");
     exit(1);
   }
@@ -55,7 +56,7 @@ int main(int argc, char **argv){
     exit(1);
   }
 
-  for(i=0;i<NPOINTS;i++){
+  for(i=0;i<NPOINTSX;i++){
     x[i] = min_x + delta_x*i;    
 
     j_int[i] = 0.0;
@@ -68,7 +69,7 @@ int main(int argc, char **argv){
     }
   }
 
-  for(i=0;i<NPOINTS;i++){
+  for(i=0;i<NPOINTSX;i++){
     fprintf(stdout, "%f %f\n", x[i], j_int[i]);
   }
   

### 2014-06-30 paper/ms.tex
typos

@@
 $\int_{-1}^{1}F(\mu)d\mu/2=1$.  In the case of perfect spherical
-simmetry one expects a flat distribution with $F(\mu)=1$.
+symmetry one expects a flat distribution with $F(\mu)=1$.
 
 Figure \ref{fig:muhisto} shows the results for a selection of models
-with $\tau_{\rm H}=10^{5}$, ifferent rotational velocities and the two
+with $\tau_{\rm H}=10^{5}$, different rotational velocities and the two
 types of source distributions.
@@
   \caption{FWHM for the non-dusty models as a function of the viewing
-  angle parameterized by $|\cos\theta|$. Continuous (dashed) lines  correspond
+  angle parametrized by $|\cos\theta|$. Continuous (dashed) lines  correspond
   to central (homogeneous) source distributions. The general trend is
@@
 
-All the models fall into a single familiy of lines in the plane shown
+All the models fall into a single family of lines in the plane shown
 in the right panel of Figure \ref{fig:widthsvsvelocity}, justifying
-the choice of our parameterization.
+the choice of our parametrization.
 We fit simultaneously all the points in two separate groups, central
@@
 In Figure \ref{fig:maximumvsvelocity} we show the dependence of $x_m$ with
-the viewing angle parameterized by $|\cos\theta|$ for different
+the viewing angle parametrized by $|\cos\theta|$ for different
 rotational velocities.
@@
   central (homogeneous) distribution of sources; there is a clear
-  decrease in the number of scatterings for the homogenously
+  decrease in the number of scatterings for the homogeneously
   distributed sources.
@@
 photon. 
-Studying this quantity can help us in claryfying the independence of
+Studying this quantity can help us in clarifying the independence of
 the integrated flux and the escape fraction with respect to the
@@
 This plot corresponds to the specific case of the central model with
-$\tau=10^5$ and $V_{\rm max}=300$\kms, but we have veryfied that this
+$\tau=10^5$ and $V_{\rm max}=300$\kms, but we have verified that this
 holds for all models.
@@
 
-There are three key results that allows us to build an analyitical description to
+There are three key results that allows us to build an analytical description to
 first order of our results: the independence of the integrated flux,
@@
 frame of the rotating gas cloud all atoms are stationary with respect
-to each other, making the scattering process proceeed identical as in
+to each other, making the scattering process proceed identical as in
 the static case.  
@@
 spectra using this approach (the implementation details are in the Appendix).
-The left panel shows the results for different rotational velocitiies
+The left panel shows the results for different rotational velocities
 in the case of $\tau_{H}=10^7$ and an observer located perpendicular
@@
 \caption{
-Comparison of the Monte Carlo results agains the analytic
+Comparison of the Monte Carlo results against the analytic
 solution. The left panel explores the results of different velocities.
 The right panel presents the results for two different observers:
-paralel and perpendicular to the rotationa axsi, $\mu=1$ and $\mu=0$
+paralel and perpendicular to the rotational axis, $\mu=1$ and $\mu=0$
 respectively.
@@
 Gas bulk rotation can also be considered as a probable origin for that
-behavior, provided that the observed single peak is highly
+behaviour, provided that the observed single peak is highly
 symmetric. 
@@
 These results helped us to construct the outgoing spectra of a
-rotating sphere as a supeposition of spectra coming from a static
+rotating sphere as a superposition of spectra coming from a static
 configuration. This description is useful to describe the main
@@
 The definitive and clear impact of rotation on the \ly morphology
-suggests that this is an effect that should be taken into accunt at
+suggests that this is an effect that should be taken into account at
 the moment of interpreting high resolution spectroscopic data. To this

### 2014-07-02 paper/ms.tex
new version with updated discussion, concluiosns and notation in the analytical solution

@@
 range $\tau_{\rm H}=10^{5}-10^{7}$. 
-We consider two types of source distributions: single central and a
-homogeneoulsy distributed in the sphere. 
+We consider two types of source distributions in the sphere: central and a
+homogeneous.
 Our main result is that rotation introduces a dependence of the
-line morphology with  viewing angle. 
+line morphology with  viewing angle and rotational velocity. 
 Observations with a line of sight parallel to the rotation axis yield
 line morphologies similar to the static case. 
-For lines of sight perpendicular to the rotation axis the intensity at the line
+For lines of sight perpendicular to the rotation axis both the intensity at the line
 center and the line width increase with rotational velocity.   
-Along the same sight, the line becomes single peaked  at rotational
+Along the same line of sight, the line becomes single peaked  at rotational
 velocities close to half the line width in the static case. 
 Notably, we find that rotation does not induce any significant spatial
-anisotropy in the integrated line flux, in the escape fraction or the
-average number of scatterings. 
-We also provide an analytical expression for the outgoing \lya spectrum of
-a rotating cloud which accounts for the velocity and viewing angle
-trends observed in our Monte Carlo simulations.
+anisotropy in the integrated line flux, the escape fraction or the
+average number of scatterings. From this, we conclude that the \lya scattering
+through a rotating solid-body proceeds identical to the static
+case. The only difference is the doppler shift from the different
+regions in the sphere that move with respect to the observer. This
+allows us to derive an analytic approximation for the viewing-angle
+and rotational velocity of the emerging spectrum.
 \end{abstract}
@@
 respect to the direction of the angular velocity. We use the variable $\mu$ to
-study the anisotropy induced by rotation. Figure \ref{fig:geometry}
+study the anisotropy induced by rotation. Fig. \ref{fig:geometry}
 shows the geometry of the problem and the important variables.
@@
 \end{center}
-\caption{Same as Figure \ref{fig:CentralSpec} for \ly photons
+\caption{Same as Fig. \ref{fig:CentralSpec} for \ly photons
   initialized homogeneously throughout the sphere.
@@
   (homogeneous) source distributions.  The panels follow the same
-  distribution as in Figures \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
+  distribution as in Fig.s \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
     \label{fig:differentvelocities}}  
@@
 
-The central result of this paper are summarized in Figures
+The central result of this paper are summarized in Fig.s
 \ref{fig:CentralSpec} and \ref{fig:HomSpec}. 
@@
 
-From these Figures we can see that the line properties change with
+From these Fig.s we can see that the line properties change with
 rotational velocity and depend on the viewing angle $\theta$.  
@@
 
-The first column in both Figures \ref{fig:CentralSpec} and
+The first column in both Fig.s \ref{fig:CentralSpec} and
 \ref{fig:HomSpec} shows that for the static sphere the line properties
@@
 
-This is clear in  Figure \ref{fig:differentvelocities} where we
+This is clear in  Fig. \ref{fig:differentvelocities} where we
 present the different line morphologies for $|\mu|\sim 0$ in the
 homogeneous and central configurations.  
-The panels have the same distribution as Figures \ref{fig:CentralSpec}
+The panels have the same distribution as Fig.s \ref{fig:CentralSpec}
 and \ref{fig:HomSpec}.    
@@
 
-Figure \ref{fig:muhisto} shows the results for a selection of models
+Fig. \ref{fig:muhisto} shows the results for a selection of models
 with $\tau_{\rm H}=10^{5}$, different rotational velocities and the two
 types of source distributions.
-This Figure shows that $F(\mu)$ is consistent with being flat, apart
+This Fig. shows that $F(\mu)$ is consistent with being flat, apart
 from some statistical fluctuations on the order of \%2.
@@
 
-Figure \ref{fig:widthvsmu} shows the FWHM for all models as a function
+Fig. \ref{fig:widthvsmu} shows the FWHM for all models as a function
 of the viewing angle. 
@@
 poles to the equator) and increasing values of $V_{\rm max}$. 
-In Figure
+In Fig.
 \ref{fig:widthsvsvelocity} we fix $|\mu|<0.1$, i.e. viewing angle
@@
 All the models fall into a single family of lines in the plane shown
-in the right panel of Figure \ref{fig:widthsvsvelocity}, justifying
+in the right panel of Fig. \ref{fig:widthsvsvelocity}, justifying
 the choice of our parametrization.
@@
 double into single peak profiles. 
-In Figure \ref{fig:maximumvsvelocity} we show the dependence of $x_m$ with
+In Fig. \ref{fig:maximumvsvelocity} we show the dependence of $x_m$ with
 the viewing angle parametrized by $|\cos\theta|$ for different
@@
 
-In Figure \ref{fig:Nscatt} we show the average number of scatterings
+In Fig. \ref{fig:Nscatt} we show the average number of scatterings
 $\langle N_{\rm scatt}\rangle$ as a function of the cosinus of the
@@
 
-The right panel of Figure \ref{fig:Nscatt} shows how the average
+The right panel of Fig. \ref{fig:Nscatt} shows how the average
 number of scatterings is also independent from the rotational
@@
 %histograms for the number of scatterings as a function of the outgoing
-%dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show these 
+%dimensionless frequency $x$. In Fig. \ref{fig:Nscatt2D} we show these 
 %results in the case $\tau_{\rm H}=10^5$ for the
@@
 
-%The top right panel of Figure \ref{fig:Nscatt2D} (homogeneous sources,
+%The top right panel of Fig. \ref{fig:Nscatt2D} (homogeneous sources,
 %high rotational velocity) supports our hypothesis about
@@
 %scatterings. This also explains the decrease in the average number of
-%scatterings observed in Figure \ref{fig:Nscatt}. We have also veryfied
+%scatterings observed in Fig. \ref{fig:Nscatt}. We have also veryfied
 %that these photons are indeed emitted closer to the surface than to
@@
 %However, for a central distribution the situation is quite different
-%(lower panels in Figure \ref{fig:Nscatt2D}). In this case the number
+%(lower panels in Fig. \ref{fig:Nscatt2D}). In this case the number
 %of scatterings remains high, in the order of the optical depth, but
@@
 
-There are three key results that allows us to build an analytical description to
-first order of our results: the independence of the integrated flux,
-the number of scatterings and the escape fraction with the rotational
-velocity and the viewing angle.
-
-One way to understand these results is that actually a rotating sphere
-is not very different from a static one. We can think that in the
-frame of the rotating gas cloud all atoms are stationary with respect
-to each other, making the scattering process proceed identical as in
-the static case.  
+There is a key result of our simulatios that allows us to build an
+analytical description for the outgoing spectra.
+It is the independence of the following three quantities with the rotational
+velocity and the viewing angle: integrated flux, average number of
+scatterings and escape fraction.
+
+One way to understand this is that a rotating sphere
+is practically identical from a static one. 
+In the frame of the rotating gas cloud all atoms are in fact
+stationary with respect to each other, making the scattering process
+proceed identical as in the static case.  
 While scattering events off atoms within the rotating cloud impart
@@
 there in the lab-frame.  
-In the frame of the rotating gas cloud, all atoms are stationary with
-respect to each othe and the scattering process proceeds identical as
-in the static case.
+Therefore, in the frame of the rotating gas cloud all atoms are
+stationary with respect to each othe and the scattering process
+proceeds identical as in the static case.
 
@@
 another distance corresponding to $\tau=1$. 
-It is easy to show that the point where the photon ends up is
-independent of the assumed rotation velocity of the cloud.
+The point where the photon ends up is independent of the assumed
+rotation velocity of the cloud.
 
@@
 also identical as for the static case in a frame that is co-rotating
-with the cloud. However, the surface of cloud now moves in the
-lab-frame. Each surface-element on the rotating cloud now has a bulk
-velocity with respect to a distant observer. In order to compute the
+with the cloud. 
+However, the surface of cloud now moves in the lab-frame. 
+Each surface-element on the rotating cloud now has a bulk
+velocity with respect to a distant observer. 
+In order to compute the
 spectrum one can integrate over all the surface elements in the
@@
 
-Fig~\ref{fig:comparison} shows some examples of analytic vs. full MC
+Fig~\ref{fig:comparison} shows some examples of analytic versus full MC
 spectra using this approach (the implementation details are in the Appendix).
@@
 
-The two methods clearly give good agreement, though not perfect. In
-particular, the left panel shows that the MC gives rise to a spectrum that is
+The two methods clearly give good agreement, though not perfect. 
+In particular, the left panel shows that the MC gives rise to a spectrum that is
 slightly more concentrated towards the line centre. 
@@
 
-{\bf Anisotropic emission}. In our studies the integrated flux is
-constant is independent of the viewing angle. This rules out the
-possibility of having an observational indication of gas bulk rotation
-from measurements of the line equivalent width. A possible way to
-obtain an anisotropic flux with the same gas configuration is to allow
-for anisotropic emission \citep{Zheng2013,Behrens2014}. We explore
-these scenarios in future work (Remolina-Gutierrez et al., in prep.).
-
 \section{Conclusions}
@@
   when the rotational velocity is close to than half the FWHM$_0$.
-
-\item  The escape fraction does not change with rotational velocity
-  nor with the viewing angle. We interpret this
-  in terms of the average number of scatterings which do not 
-  significantly change with rotation or viewing angle. This is due to the  
-  fact that the vast majority of scatterings events are resonant, 
-  during which the mean free path is very short and the effect of gas
-  bulk rotation is not enough to affect \ly photons.
-
 \end{itemize}
@@
 \begin{equation}
-v_{\rm b}(b,\phi,i)=V_{\rm max}\frac{\sqrt{R^2 -s^2}}{R}\cos i  \hs \cos a,
-\end{equation} where the factor $\cos i$ accounts for the projection onto the $x-y$ plane, and the factor $\cos a$ for the subsequent projection onto the line-of-sight.
-The {\it right panel} of Figure~\ref{fig:scheme} shows that this angle $a$ can be computed from
+v_{\rm b}(b,\phi,i)=V_{\rm max}\frac{\sqrt{R^2 -s^2}}{R}\cos i  \hs
+\cos a,
+\end{equation}
+where $\beta = 90^{\circ}-a$.
+The factor $\cos i$ accounts for the projection onto the $x-y$ plane, and the factor $\cos a$ for the subsequent projection onto the line-of-sight.
+The {\it right panel} of Fig.~\ref{fig:scheme} shows that this angle $a$ can be computed from
 %
 \begin{equation}
-\tan [90^{\circ}- a]=\frac{c}{d}=\frac{ b\sin \phi}{\sqrt{R^2 -b^2}}.
+\tan \beta =\tan[90^{\circ}-a]=\frac{c}{d}=\frac{ b\sin \phi}{\sqrt{R^2 -b^2}},
 \end{equation}
+%
 

### 2014-07-02 paper/referee-reply.tex
before mark
updated referee reply

@@
 \maketitle
-We thank the referee for a detailed report. Indeed, the report
-motivated us to explore a very important aspect of our results that we
-had overlooked.
+We thank the referee for a detailed report. It prompted us to explore
+a very important aspect of our results that we had overlooked. Namely,
+the dependence of the line morphology as a function of viewing
+angle. In the revision process we have also corrected a mistake in the
+initialization procedure for the MC calculations. This also allowed us
+to derive an analytical solution that reproduced the main features of
+the MC results.
 
-We made a plot suggested by the referee that showed a clear
-dependence of the line morphology with the viewing angle an effect
-that we had deemed as negligeable after measuring a proxy statistic for
-it (the integrated flux).
+The improvement in these three aspects (line anisotropy, photon initialization,
+analytical solution) has led us to rewrite the Results and Discussion
+section. We have also completeley dropped sections (e.g. the asymetrical emission
+part) that obfuscate the new main results of the paper.
 
-The correct interpretation is that, as the referee expected, there is
-a strong effect on the morphology.
-
-This completely changed the focus of our paper. We have now completely
-rewritten the Results and Discussion section in order to highlight
-that result. We have also completeley dropped sections (e.g. the
-asymetrical emission part) that obfuscate this main result.
-
-In this document we address one by one the questions in the
-report. However, we kindly ask the referee to revise directly the new
-version of the paper, given the substantial changes from the first
-version.
+Given the substantial changes from the first version, 
+we kindly ask the referee to revise again in detail the new manuscript.
 
@@
 As we mentioned in the introduction to this letter, there is indeed
-an anisotropy in the line morphology. The paper was re-structured
-accordingly.
-
-However, the properties that we had measured as isotropic (integrated
-flux and escape fracrion) remain anisotropic.
+an anisotropy in the line morphology. The paper is now re-structured
+to highlight this result.
 
@@
 We do not find any significant dependence of the escape fraction with
-the viewing angle. This is shown in Figure \ref{escape_fraction} of this
-document. We do not show this plot in the paper and only mention the
-result at the beginning of Section 3.5.
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.5]{escapefractionvstheta.png}
-\end{center}
-\caption{Escape Fraction as a function of $\mu$
-\label{escape_fraction}}
-\end{figure}
+the viewing angle. This is now shown in Figure 9 of the paper.
 
@@
 histogram to find the half maxima intensity values and their
-corresponding frequencies.
+corresponding frequencies. This is now clear in the text.
 
@@
 
+The result is found in both codes.
+
 \subsection*{Fig4 and 6}
@@
 
-(MARK)
+This results is not surprising if one considers that the scatterings
+proceed as in the static case. In the co-rotating frame everything
+happens exactly as in the estatic case.
+
+We have also veryfied that for high rotational velocities of 1000 km/s
+the results for the escape fraction, number of scatterings and integrated total
+flux remain constant.
 
@@
 
-We followed the suggestion by the referee to construct a new
-plot. For the model with homogeneously distributed sources we now the
-initial and final states for every photon. With this information we
-prepare the plot in Figure \ref{nscatt} of this document. It is a 2D
-histogram of the number of scatterings and the initial radius showing
-the starting radius. Indeed, most of the photons that escaped after
-less than 10 scatterings were emitted in the external part of the
-sphere $R>0.8R_{max}$. However, there is a minority of photons that
-have a similar emission radius but only managed to escape after $10^4$
-scatterings.
+Actully this plot is incorrect due to the wrong initialization of the
+photons in the homogeneous case. In that situation the frequency of
+the photons must be changed according to the dot product between the
+bulk velocity and propagation direction. This is mentioned in section
+2.2.
 
-\begin{figure}
-\begin{center}
-  \includegraphics[scale=0.6]{Histogram2dNscattVSRadius.png}
-\end{center}
-\caption{\label{nscatt} 2D histogram of the number of scatterings and
-  the number. The color scale is linear in the number of photons in
-  each bin.}
-\end{figure}
+With this changes we find that the total number of scatterings does
+not change with rotational velocity.
 
@@
 
-(MARK)
+We have included the following paragraphs in the paper:
+
+\begin{quote}
+The naive interpretation of the analytic solution does not seem to
+hold for photons emitted far from the sphere's center. 
+We suggest that increasing $\tau_{\rm H}$ from $10^{5}$ to $10^{6}$ causes a
+transition from the 'optically thick' to  the 'extremely optically
+thick' regime for a noticeable fraction of the photons in the
+homogeneous source distribution.
+
+In the optically thick regime, lya  photons can escape in
+'single flight' which corresponds to a scenario in which the
+photon resonantly scatters $10^4-10^5$ times until it is scattered
+into the wing of the line ($x\sim 3-4$). 
+At these frequencies the medium is optically thin, and the photons can
+escape efficiently in a single flight. 
+In contrast, in an extremely optically thick medium lya
+  photons escape in a `single excursion' (Adams 72). 
+Here, photons that are scattered into the wing of the line escape from
+the medium in a sequence of wing scattering events. 
+In both cases, lya photons resonantly scatter $10^4$-$10^5$ times. 
+Because we keep our clouds the same size, the mean free path of Lya
+photons that scatter resonantly is 10 times larger for the case
+$\tau_{\rm H}=10^5$ than for $\tau_{\rm H}=10^6$. 
+If we compute the average distance $D$ travelled by lya
+photons through a medium of size $R$ as a function of line center
+optical depth $\tau_{\rm H}$, then we find that during the transition
+from optically thick to extremely optically thick the mean traversed
+distance $D$ actually decreases slightly.  
+This decrease is unique to this transition region, and $D$ generally
+increases with $\tau_{\rm H}$ at other values of $\tau_{\rm H}$.   
+\end{quote}
 
@@
 
-We did not try many more models with higher optical depths. We expect
-to do that in the near future to complete a study that could be
-immediatly comparable against observations.
+We did not try models with higher optical depths due to the
+limitation in available computing time to perform the
+calculations. However, the analytical solution provides sufficient
+information to quantify the anisotropy level.
 

### 2014-07-02 code/analytic_solution.c
C code with the new version of the analytic solution by mark

@@ -64,7 +64,8 @@ int main(int argc, char **argv){
       for(k=0;k<NPOINTS;k++){
 	phi = delta_phi*j;
 	b = delta_b*k;
-	j_int[i] += J_surface(x[i], b, phi, i_angle, tau, v_rot) * b * delta_phi * delta_b;
+	j_int[i] += 
+	  J_surface(x[i], b, phi, i_angle, tau, v_rot) * b * delta_phi * delta_b;
       }
     }
   }
@@ -80,15 +81,15 @@ int main(int argc, char **argv){
 double J_surface(double x, double b, double phi, double i_angle, double tau0, double v_rot){
   double final, v_thermal, a;
   double beta, x_b, arg_in, s;
-
+  
   v_thermal = 12.85*sqrt(TEMP/10000.0);
   a = 4.7E-4*(12.85/v_thermal);
   
-  beta = PI/2.0 - atan(b*sin(phi)/sqrt(R*R - b*b));
+  beta = atan(b*sin(phi)/sqrt(R*R - b*b));
 
-  s = abs((-sin(i_angle) * sqrt(R*R - b*b)) + (b * cos(phi) * cos(i_angle)));  
+  s = -(sin(i_angle) * sqrt(R*R - b*b)) + (b * cos(phi) * cos(i_angle));  
 
-  x_b = (v_rot/v_thermal) * sqrt(1.0- (s/R)*(s/R)) * cos(i_angle) * cos(beta);  
+  x_b = (v_rot/v_thermal) * sqrt(1.0- (s/R)*(s/R)) * cos(i_angle) * sin(beta);  
 
 
   arg_in = pow(fabs(x-x_b),3.0)/(a*tau0);

### 2014-07-04 paper/ms.tex
minor updated
fixed typos

@@
   departures from spherical symmetry we use the polar angle $\theta$
-  formed by the direction of the outgoing photons with respecto to the
+  formed by the direction of the outgoing photons with respect to the
   $z$-axis. We define define the variable $\mu\equiv\cos\theta$ to
@@
 \caption{
-2D histogram showing the number of photons that escape with frecuency
-$x$ forming an angle $\theta$ (parameterized as $|\cos\theta|$) with the
+2D histogram showing the number of photons that escape with frequency
+$x$ forming an angle $\theta$ (parametrized as $|\cos\theta|$) with the
 rotation axis. 
@@
 
-The initialization process for the \ly photons especifies its
+The initialization process for the \ly photons specifies its
 position, frequency and direction of propagation. 
@@
 They show 2D histograms of the escape frequency $x$ and outgoing angle
-$\theta$ parameterized by $|\mu|$. 
+$\theta$ parametrized by $|\mu|$. 
 Taking into account only photons photons around a value
@@
 angle $\theta$ with respect to the rotation axis. 
-We have veryfied that the solutions are indeed symmetric with respect
+We have verified that the solutions are indeed symmetric with respect
 to $\mu=0$.
@@
 We characterize the line morphology by its total intensity, the full
-width at half maximu, (FWHM) and the location of the peak maxima. 
+width at half maximum, (FWHM) and the location of the peak maxima. 
 In order to interpret the
@@
 
-If the viewing angle is aligned witht the rotation axis, $|\mu|\sim
+If the viewing angle is aligned with the rotation axis, $|\mu|\sim
 1$, the \ly line keeps in most of the cases a double peak with minor
@@
 \caption{Integrated flux distribution as a function of the
-  viewing angle as parameterized by $\mu$. Continous (dashed)
+  viewing angle as parametrized by $\mu$. Continuous (dashed)
   correspond to central (homogeneous) source distribution.
@@
 
-There is a key result of our simulatios that allows us to build an
+There is a key result of our simulations that allows us to build an
 analytical description for the outgoing spectra.
@@
 Therefore, in the frame of the rotating gas cloud all atoms are
-stationary with respect to each othe and the scattering process
+stationary with respect to each other and the scattering process
 proceeds identical as in the static case.

### 2014-07-07 paper/ms.tex
new edits in discussion section

@@
 range $\tau_{\rm H}=10^{5}-10^{7}$. 
-We consider two types of source distributions in the sphere: central and a
+We consider two types of source distributions in the sphere: central and 
 homogeneous.
@@
 the last section we present our conclusions. The Appendix presents the
-derivation of an analytic expression that can be helpful to interpret
-to first order the main trends observed in the Monte Carlo simulations.
+derivation of an analytic expression to interpret
+the main trends observed in the Monte Carlo simulations.
 
@@
 For a detailed description we refer the reader to the original papers
-\cite{CLARA,DijkstraKramer}.
+\cite{CLARA} and \cite{DijkstraKramer}.
 
@@
 $x_{\rm in}=0$, while photons emitted at some radii with a peculiar
-velocity $\vec{v}$ have initial values $x_{in}$ depending on its direction of
+velocity $\vec{v}$ have initial values $x_{\rm in}$ depending on its direction of
 propagation: $x_{\rm   in}=\vec{v}\cdot\hat{k}_{\rm in}/v_{\rm th}$.
@@
 The codes treat the gas as homogeneous in density and temperature.  
-This implies that the cas is completely defined by its geometry
+This implies that the gas is completely defined by its geometry
 (i.e. sphere or slab), temperature $T$, Hydrogen optical depth
@@
 Table \ref{table:models} lists the different parameters we used to
-generate the models.
-
-Additionally, we have used two independently developed Monte Carlo
-codes \citep{CLARA,DijkstraKramer} to perform the calculations. 
-The results and trends we report are observed in both codes.
+generate the models. The results and trends we report are observed in both 
+Monte Carlo codes.
 
@@
 
-The central result of this paper are summarized in Fig.s
+The main results of this paper are summarized in Fig.
 \ref{fig:CentralSpec} and \ref{fig:HomSpec}. 
@@
 
-From these Fig.s we can see that the line properties change with
+From these figures we can see that the line properties change with
 rotational velocity and depend on the viewing angle $\theta$.  
@@
 For the models where dust is included we measure the escape fraction
-as a function of rotational velocity.
+as a function of rotational velocity and viewing angle.
 
@@
 
-The first column in both Fig.s \ref{fig:CentralSpec} and
+The first column in both Fig. \ref{fig:CentralSpec} and
 \ref{fig:HomSpec} shows that for the static sphere the line properties
@@
 homogeneous and central configurations.  
-The panels have the same distribution as Fig.s \ref{fig:CentralSpec}
+The panels have the same distribution as Fig. \ref{fig:CentralSpec}
 and \ref{fig:HomSpec}.    
@@
 $\Delta N$ is the number of photons in an angular bin $\Delta
-\Theta$. This definition satisfies the condition
+\theta$. This definition satisfies the condition
 $\int_{-1}^{1}F(\mu)d\mu/2=1$.  In the case of perfect spherical
@@
 types of source distributions.
-This Fig. shows that $F(\mu)$ is consistent with being flat, apart
+This shows that $F(\mu)$ is consistent with being flat, apart
 from some statistical fluctuations on the order of \%2.
@@
 In spite of that the rotation axis defines preferential direction, the
-integrated flux is the same for all viewing angles, at least for the
+integrated flux is the same for all viewing angles in the
 range of parameters explored in this paper.
@@
 
-In the optically thick regime, \lya  photons can escape in
+In the optically thick regime, \ly  photons can escape in
 'single flight' which corresponds to a scenario in which the
@@
 One way to understand this is that a rotating sphere
-is practically identical from a static one. 
-In the frame of the rotating gas cloud all atoms are in fact
-stationary with respect to each other, making the scattering process
-proceed identical as in the static case.  
+is identical from a static one. 
 While scattering events off atoms within the rotating cloud impart
@@
 The main purpose of their study was to assess the impact of two
-different Inter-Stellar Medium (ISM) prescriptions. 
+different ISM prescriptions. 
 However, each simulated galaxy had a disc structure with a clear rotation pattern in
@@
 that in order to interpret the observations of \ly emitting galaxies
-it is necessary to consider the possible effect of different
+it is necessary to consider the possible effect of rotation and different
 inclination angles along the line of sight.
@@
 velocity shift between the \ly and other emission lines. In our study
-we find that the position of the peak maxima is insensitive to the
-rotational velocity of the gas. In our model the only parameter that
-can influence the peak maxima position is the optical depth.
+we find that the position of the peak maxima can suddenly change with
+rotation and viewing angle. Namely the line can become single peaked
+for high rotational velocities and viewing angles perpendicular to the
+rotation axis. This highlights the importance of considering rotation
+in the interpretation of systemic velocity observations.
 
@@
  axis and the LoS, $\theta$.  The changes are such that for 
- $\cos\theta\equiv \mu\sim 0$, i.e. LoS perpendicular to the
+ a viewing angle perpendicular to the
  rotation axis, and high rotational velocities the line becomes single peaked.
 
-\item For a viewing angle with $\mu=0$ the line width increases with rotational
-  velocity. This change approximately follows the functional form  ${\rm FWHM}^2 = {\rm FWHM}_{ 0}^2 + (V_{\rm max}/\lambda)^2$, where FWHM$_{0}$ indicates the line
+\item The line width increases with rotational
+  velocity. For a viewing angle perpendicular to the rotation axis
+  This change approximately follows the functional form  ${\rm FWHM}^2
+  = {\rm FWHM}_{ 0}^2 + (V_{\rm max}/\lambda)^2$, where FWHM$_{0}$
+  indicates the line 
   width for the static case and $\lambda$ is a constant. We have
@@
 suggests that this is an effect that should be taken into account at
-the moment of interpreting high resolution spectroscopic data. To this
-end, we defer a discussion of observed lines features in the context of gas
-bulk rotation to a future publication (Remolina-Gutierrez et al., in
-prep.).
+the moment of interpreting high resolution spectroscopic data. In
+particular it is relevant to consider the joint effect of rotation the
+and ubiquitous outflows (Remolina-Gutierrez et al., in prep.).
 

### 2014-07-07 paper/ms.tex
new caption figure 9

@@
 \caption{Logarithm of the average number of scatterings as function of
-  $\mu$ (left panel) and the maximum rotational velocity $V_{\rm
-max}$. The left panel shows the behaviour for $\tau=10^{5}$ and
-  $V_{max}=300$\kms as a function of $|\cos\theta|$; the independence of
-  $N_{\rm scatt}$ with $\mu$ is present in all models.
-  In the right panel the continuous (dashed) lines represent an
-  central (homogeneous) distribution of sources; there is a clear
-  decrease in the number of scatterings for the homogeneously
-  distributed sources.
+  $\mu$ (left) and the maximum rotational velocity $V_{\rm
+max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
+  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$; the independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is present in all models.
 \label{fig:Nscatt} }
 \end{figure*}
-
-%\begin{figure*}
-%\begin{center}
-%  \includegraphics[width=0.48\textwidth]{f14_1.pdf}
-%  \includegraphics[width=0.48\textwidth]{f14_2.pdf}
-%  \includegraphics[width=0.48\textwidth]{f14_3.pdf}
-%  \includegraphics[width=0.48\textwidth]{f14_4.pdf}    
-%\end{center}
-%    \caption{2D histogram of $N_{\rm scatt}$ vs $x$. The upper (lower) panels
-%      show the homogeneous (central) source distribution. Left panels 
-%      corresponds to the static case and right panels correspond to
-%      $V_{\rm max}=300\kms$. The color scale is logarithmic on the
-%      number of photons with given values of $N_{\rm scatt}$ and
-%      $x$. \label{fig:Nscatt2D}. }
-%\end{figure*}
 

### 2014-07-07 paper/ms.tex
new paragraph s by mark

@@
 slightly more concentrated towards the line centre. 
-It is easy to get better agreement my modifying the surface brightness
-profile (e.g. if $S(b)=2-b$, then the analytic calculation agrees
-better).
+It is possible to get better agreement my modifying the surface brightness
+profile.
 In any case, the analytic calculation closely captures the results
@@
 its possible implications  for the interpretation of observational data.
+
+{\bf Escape at Line Center.} Our models have shown that rotation
+enhances the flux density at line center (see Fig.     \ref{fig:differentvelocities}). It has
+recently been proposed that galaxies with Lya spectral lines that
+contain flux at line center may be `leaking' ionizing (LyC) photons
+\citep{2014arXiv1404.2958V,Behrens2014}. The main reason for this possible
+connection is that the escape of ionizing (LyC) photons requires
+$N_{\rm HI} < 10^{17} $cm$^{-2}$. The same low column densities facilitate the escape of
+\ly photons at (or close to) line center. Our work suggests that
+rotation may provide an alternative explanation.
+
+{\bf Single peaked lines}. The presence of single peaked profiles has
+been associated to inflow/outflow dynamics
+\citep{Verhamme06,DijkstraKramer}. 
+Gas bulk rotation can also be considered as a probable origin for that
+behaviour, provided that the observed single peak is highly
+symmetric. 
+Similarly, in the case of double peaked lines with a high
+level of flux at the line center, rotation also deserves to be
+considered in the pool of possible bulk flows responsible for that feature,
+specially if the two peaks have similar intensities.
+
+{\bf Systemic velocities}. There are observational measurements for the
+velocity shift between the \ly and other emission lines. In our study
+we find that the position of the peak maxima can suddenly change with
+rotation and viewing angle. Namely the line can become single peaked
+for high rotational velocities and viewing angles perpendicular to the
+rotation axis.
 
@@
 models estimate the escape fraction from the column density of dust and
-neutral Hydrogen. The results of our simulation suggest that the
+neutral Hydrogen. The results of our simulation indicate that the
 rotational velocity does not induce additional uncertainties in those
 estimates.
-
-{\bf Single peaked lines}. The presence of single peaked profiles has
-been associated to inflow/outflow dynamics
-\citep{Verhamme06,DijkstraKramer}. 
-Gas bulk rotation can also be considered as a probable origin for that
-behaviour, provided that the observed single peak is highly
-symmetric. 
-Similarly, in the case of double peaked lines with a high
-level of flux at the line center, rotation also deserves to be
-considered in the pool of possible bulk flows responsible for that feature,
-specially if the two peaks have similar intensities. 
-This highlights
-that in order to interpret the observations of \ly emitting galaxies
-it is necessary to consider the possible effect of rotation and different
-inclination angles along the line of sight.
-
-{\bf Systemic velocities}. There are observational measurements for the
-velocity shift between the \ly and other emission lines. In our study
-we find that the position of the peak maxima can suddenly change with
-rotation and viewing angle. Namely the line can become single peaked
-for high rotational velocities and viewing angles perpendicular to the
-rotation axis. This highlights the importance of considering rotation
-in the interpretation of systemic velocity observations.
 
@@
 particular it is relevant to consider the joint effect of rotation the
-and ubiquitous outflows (Remolina-Gutierrez et al., in prep.).
+and ubiquitous outflows (Remolina-Gutierrez et al., in prep.)
+because rotation can lead to enhanced escape of \ly at line center, which
+has also been associated with escape of ionizing (LyC) photons
+\cite{Behrens2014,2014arXiv1404.2958V}
 

### 2014-08-07 paper/referee-reply.tex
typos
new referee reply (2nd report)

--- 2014-06-04 paper/referee-reply.tex
@@
 
-\title{Response to the first report on the article draft \emph{The
+\title{Response to the second report on the article draft \emph{The
     Impact of Gas Bulk Rotation on the Lyman-$\alpha$ line.}} 
@@
 \maketitle
-We thank the referee for a detailed report. Indeed, the report
-motivated us to explore a very important aspect of our results that we
-had overlooked.
-
-We made a plot suggested by the referee that showed a clear
-dependence of the line morphology with the viewing angle an effect
-that we had deemed as negligeable after measuring a proxy statistic for
-it (the integrated flux).
-
-The correct interpretation is that, as the referee expected, there is
-a strong effect on the morphology.
-
-This completely changed the focus of our paper. We have now completely
-rewritten the Results and Discussion section in order to highlight
-that result. We have also completeley dropped sections (e.g. the
-asymetrical emission part) that obfuscate this main result.
-
-In this document we address one by one the questions in the
-report. However, we kindly ask the referee to revise directly the new
-version of the paper, given the substantial changes from the first
-version.
 
@@
 
-\section{Global Comments}
+\section*{Global Comments}
 
-\subsection{Variation with the viewing angle}
+\subsection*{Variations with viewing angle... again}
 
-{\bf The problematic of anisotropy is only studied from Sect3.4, the former
-sections consider global quantities (spectral shapes, escape
-fractions, etc...). This is ok only if there is NO anisotropy induced
-by rotation, which is not obvious, a priori. You should make it clear
-from the beginning, telling that you will investigate anisotropy at
-the end of the paper only, because you checked that lya properties are
-isotropic, at least in the range of parameters that you investigated
-so far.}
+{\bf Figs 2 and 3 are very nice.
+They illustrate clearly the evolution of spectral shape with viewing angle.
+Note that the x label is wrong, it is not Vmax.
+It also needs a color bar to explicit the scale between a red pixel and a green/blue pixel.
+Because...
+to my eyes, there is an obvious third result illustrated on these Figs, which is that much less photons seem to escape at the equator than along the poles: the red pixels are concentrated towards the pole, whereas there seems to be less light emerging from equatorial directions.
+But if the dynamical range between red and blue is very small, maybe it’s ok, given that the equatorial spectrum is broader...
+How did you select photons when you did this Fig 2 ?
+Did you select them on $\cos\theta|$?
+You should select only one side, one hemisphere, otherwise you count twice more photons anywhere else than along the equator.
+Did you select a peculiar $\varphi$ ?
+Or did you sum over the azimuthal direction ?
+In order to avoid this impression that less photons escape at equator, you should indeed sum over $\varphi$.
+However, these selection biases would also affect the static case, whereas the first column looks ok to me, it seems that the same “intensity” is escaping from all directions for this column, and not for the others.
+It is in strong contradiction with your Fig 5. How do you explain this ?
+Furthermore, I would have expected the contrary, with more photons escaping at the equator, where the velocity field is stronger, than through the poles, where everything is static...
+However, Ly$\alpha$ radiation transfer effects can often be far from intuitiv.}
 
-As we mentioned in the introduction to this letter, there is indeed
-an anisotropy in the line morphology. The paper was re-structured
-accordingly.
+\subsection*{intrinsic spectrum on Fig 4}
 
-However, the properties that we had measured as isotropic (integrated
-flux and escape fracrion) remain anisotropic.
+{\bf From your Figs 6 and 7, it seems that the results for central and homogeneous cases are very comparable.
+I would like to see the shape and FWHM of the intrinsic spectra (I mean before transfer) in the case of homogeneous sources, for the static case, as the fiducial case, and when Vmax=100,200,300 km/s, along the equatorial direction.
+I would like to infer how much of the broadening of the line is really due to transfer effects.
+Could you make a figure where you compare the intrinsic and emerging spectra along
+the equatorial plane ?}
 
-{\bf As explained in sect 3.4, rotation kills the spherical symmetry
-  of your problem, and the rotation axis defines a preferential
-  direction. We could expect some variation of the emerging flux, the
-  lyman-alpha escape fraction, and the spectral shape, with viewing
-  angle. From Fig8, it seems that the flux is the same in all
-  directions for spherical distributions of sources. This important
-  result is not enough emphasized.}
+\subsection*{Sect 4.1 : Rotation = Static ?}
 
-We now emphasize in the abstract, section 3.2 and the conclusions the
-result on the non-variation of the total flux with viewing angle.
+{\bf I don’t understand the reasonning that rotation would act on the Ly$\alpha$ transfer as a static medium, since Ly$\alpha$ photons are “co-rotating”.
+You mention this argument once in the “answer to referee” document, and once in the text Sect.
+4.1, with a sentence which reads absurd : a rotating sphere is identical from a static one.
+At least, it is not well formulated.
+It seems to me that your argument should be right for any kind of motion.
+Why would it be specific to rotation ?
+In other words, you could exchange the word “rotation” with the word “outflow” or “inflow” in your reasonning, right ?
+“While scattering events off atoms within the outflowing cloud impart Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only there in the lab-frame.
+Therefore, in the frame of the outflowing gas cloud all atoms are stationnary with respect to each other and the scattering process proceeds identical as in the static case.”.
+However, all atoms in a rotating/outflowing/infalling cloud are not stationary with respect to each other, otherwise the cloud would be static!
+Your reasonning is true at the scale of each cell, but not at global scale.
+I did not understand the alternative -more quantitative- explanation better.
+Can you develop this point ?
+Maybe, to convince me, you could look at the redistribution of frequencies after one single diffusion ( 1/ in all directions, 2/ along the rotation axis, 3/ in the equator plane), emitting your photons at a radius r = 0.9 R, and comapre them with the same redistributions in the static case.
+If they are identical, you are right, rotation does not have any effect...
+if they are different, multiple scatterings will have a cumulative effect on the spectral shape, but also on the probalility to escape more easily in some directions than others...
+I understand that this implies new simulations and more time, but I would really appreciate to see these plots.
+}
 
-{\bf Do you see any difference in the spectral shape with viewing
-  angle? To illustrate this point, it would be interesting to build a
-  2D plot as you did on Fig 5, but replace Nb scat in ordinates by the
-  viewing angle $\mu$. We could immediatly see if there is an
-  evolution of the shape with viewing angle or not. If you find NO
-  evolution of the Lya shape with viewing angle, I think that it is an
-  interesting counter-intuitive result, that you should advertise
-  more.}
+\subsection*{Angular variation of the distribution of escaping directions}
 
-As we metioned in the introduction to this reply, we prepared the
-suggested plot and found strong variations of the spectral shape with
-viewing angle. This result motivated us to re-structure the paper to
-emphasize it.
-
-{\bf What about the variation of lya escape fraction with viewing
-  angle ? I propose that in the beginning of Sect.3 Results, you first
-  emphasize that, maybe counter-intuitively, you did not find any
-  variation of the Lya properties with viewing angle, so you will
-  present first angle average lya properties, and you will come back
-  to the anisotropy problematic only at the end on the paper.}
-
-We do not find any significant dependence of the escape fraction with
-the viewing angle. This is shown in Figure \ref{escape_fraction} of this
-document. We do not show this plot in the paper and only mention the
-result at the beginning of Section 3.5.
-
-\begin{figure}
-\includegraphics[scale=0.5]{escapefractionvstheta.png}
-\caption{Escape Fraction as a function of $\mu$
-\label{escape_fraction}}
-\end{figure}
-
-\section*{Outflow + Rotation}
-
-We want to study the pure effect of rotation on the spectra, off course it would
-be interesting to study the effect of rotation on systems with
-outflows, this paper is under preparation by M.C Remolina-Gutierrez et
-al.
+{\bf It seems to me that Ly$\alpha$ photons escape a medium through the path of minimum optical depth.
+So, in a rotating cloud, where the velocity field is tangential, they might “rotate” or spiral from the center to the edge.
+To test this idea, you could look at the distribution of escaping directions from photons emerging at the pole or at the equator.
+But for this, you need to keep track of the location of escape, and not only of the direction of escape.
+Did you collect this information ?
+I would expect that photons at the equator escape more tangentially to the sphere than at the poles... But again, Ly$\alpha$ transfer is not exactly intuitiv.}
 
@@
 
-\subsection*{Introduction}
+\subsection*{Sect. 3.1}
 
-{\bf With Orsi et al 2012, please cite also Garel et al 2012. With Zheng \& Wallace 2013, please cite also Behrens et al 2014.}
+{\bf You say that “If the viewing angle is aligned with the rotation axis, $|\mu| \approx 1$, the Ly$\alpha$ line keeps in most of the cases a double peak”, isn’t it in all cases ?}
 
-Added.
+\subsection*{Sect. 3.5}
+{\bf The parameter a is not defined when you discuss Neufeld.}
 
-\subsection*{Fig.1}
+\subsection*{Fig9}
 
-{\bf I guess that the spectra presented in Fig1 are integrated over all directions, right ?
-You should describe explicitly how you build them.
-You could skip the x notation in absciss, as it is not used in the discussion, whereas the velocity is used to compare to FWHM, on Fig2.}
+{\bf Is Fig 9, left panel, for a central source ?
+Can you show the homogeneous case also ?
+You discuss in the referee repport that the distribution is not bimodal anymore.
+But it has to be different than in central case, spanning the whole range of nb scatt, because photons are emitted at every radii in the cloud, so at every optical depth.
+On the right panel, solid and dashed lines are not defined.}
 
-Now this figure is the Fig.4 in the paper. what we did was to fix a viewing angle in this case $\theta= \pi/2$ and make the histogram of the photons frequency
-
-\begin{itemize}
-\item Description about how we build Fig.1 (Done)
-\item Fig 1. remove x notation (Done)
-\end{itemize}
-
-{\bf Description about how we build Fig.1}
-
- (Done)
-{\bf Fig 1. remove x notation}
-
-(Done)
-
-\subsection*{Fig.2}
-
-{\bf Fig.2 Can you explain how you measure the FWHM of a double-peaked profile ? Do you fit it with a gaussian ?}
-
-We e interpolate points to the line profile and then  we measure the
-width by  the closest points to the half maximum in our histogram.
-
-\subsection*{Fig.3}
-
-{\bf Do you have an idea why the (central source, intermediate optical depth) case with Vmax=300 has a single plateau instead of 2 peaks ? Do you find this with the two codes ?}
-
-After close inspection in this figure the line was composed by two
-peaks, that looked like a plateau with the resolution used to
-construct the figure.
-
-\subsection*{Fig4 and 6}
-
-{\bf This is a surprising result that the number of scatterings (escape fraction) stays constant as the rotation velocity increases, for a central source, whereas the global spectral shape is altered.
-Did you try with higher/extreme values of Vmax (=1000 km/s, even if not physically motivated) ?
-Do you believe that the number of scatterings decreases with very high values, or that it is independant of the rotation velocity ?
-Is the escape fraction from a dusty rotating cloud with central source independant of the rotation velocity ?}
-
-\subsection*{Fig5}
-
-{\bf This is a very nice figure ! Looking at the top right panel, with
-  its “photosphere”, I’m surprised that the distribution of Nscatt is
-  bipolar, I would have expected a smooth transition between the 2
-  regimes. Do you have a physical explanation why photons escape after
-  either (less than 10) or (more than 1000) scatterings, and none
-  escape with 100 scatt ? To test the ’photosphere’ assumption, you
-  could also do the radiation transfer in a cloud with the
-  distribution of sources only in an inner sphere, and another
-  experienment with sources only in an outer shell. If I understood
-  corectly, you would expect thant the bottom spot on the top right
-  panel is made of photons from the outer shell, and the uppper spot
-  from photons emitted inside the cloud.}
-
-\begin{figure}
-  \includegraphics[scale=0.4]{Histogram2dNscattVSRadius.png}
-\end{figure}
-
-\subsection*{End of paragraph 3.3}
-
-{\bf One sentence is not clear : we see that the escape fraction does not increase significantly from $\tau$ = 105 to $\tau = 10^{6}$.
-This counter-intuitive result....
-It sounds like you were expecting a strong increase...
-A decrease is expected from $\tau$ = 105 to $\tau$ = 106, not an increase, but indeed on the graphe we can see an unexpected (small) increase.
-I do not understand the explanation for this behaviour.}
-
-(Mark)
-
-\subsection*{Fig8}
-
-{\bf Referred to as Figure 7 in the text (paragraph 3.4). To my mind,
-  this figure illustrates the main result of your study, it has to be
-  more demonstrative. On this figure, the numerical noise seems very
-  big compare to the small number of bins, bigger than on the spectra
-  from Fig1, how is it possible ? Could you re-do this figure with
-  more photons, maybe with more bins ? Could you plot an histogram
-  instead of broken lines, to ease the reading ? In the text, you
-  write anisotropy induced by rotation is at the 3$\%$ level, how do
-  to estimate this number? I think that the noise is at $3\%$ level,
-  and the distribution is compatible with ’flat’. In the corresponding
-  text, you first say that $F(\mu)$ does not depend on Vmax. Again, if
-  real, this is an important result, that you must advertise
-  more. Please show it on this Fig, by comparing F($\mu$) without rotation
-  (in red, for example) to the other distributions that you get with
-  different values of Vmax. Then, you mention that for high optical
-  depth values, $F(\mu)$ (not the variations of $\mu$) can vary up to
-  $15\%$. First, what do you call high optical depth ? your highest
-  setup is $\tau$= $10^7$, not extremely high for lyman alpha ”standards’,
-  corresponding to NHI $\sim$10$^{20}$ cm$^{-2}$. So, if you see a trend with
-  optical depth, I encourage you to check higher optical depth
-  regimes, corresponding better to galaxy scales. If you can probe
-  that anisotropy induced by rotation is rising with optical depth,
-  this would be an interesting result. If higher optical depth regimes
-  lead to anisotropic escape, could you check the effet of anisotropy
-  on the lya spectral shape?}
+\subsection*{Vmax = 1000 km/s}
+{\bf If you did this test and checked that the nb of scatterings and the escape fraction is still angle invariant for such a high velocity, then it is worth mentionning it.
+Because in principle, media with very high velocities should start to become transparent for Ly$\alpha$.}
 

### 2014-08-07 paper/referee-reply.tex
including new figure

@@
 
-{\bf Figs 2 and 3 are very nice.
-They illustrate clearly the evolution of spectral shape with viewing angle.
-Note that the x label is wrong, it is not Vmax.
-It also needs a color bar to explicit the scale between a red pixel and a green/blue pixel.
-Because...
-to my eyes, there is an obvious third result illustrated on these Figs, which is that much less photons seem to escape at the equator than along the poles: the red pixels are concentrated towards the pole, whereas there seems to be less light emerging from equatorial directions.
-But if the dynamical range between red and blue is very small, maybe it’s ok, given that the equatorial spectrum is broader...
-How did you select photons when you did this Fig 2 ?
-Did you select them on $\cos\theta|$?
-You should select only one side, one hemisphere, otherwise you count twice more photons anywhere else than along the equator.
-Did you select a peculiar $\varphi$ ?
-Or did you sum over the azimuthal direction ?
-In order to avoid this impression that less photons escape at equator, you should indeed sum over $\varphi$.
-However, these selection biases would also affect the static case, whereas the first column looks ok to me, it seems that the same “intensity” is escaping from all directions for this column, and not for the others.
+{\bf Figs 2 and 3 are very nice. They illustrate clearly the evolution
+  of spectral shape with viewing angle. Note that the x label is
+  wrong, it is not Vmax. It also needs a color bar to explicit the
+  scale between a red pixel and a green/blue pixel. Because... to my
+  eyes, there is an obvious third result illustrated on these Figs,
+  which is that much less photons seem to escape at the equator than
+  along the poles: the red pixels are concentrated towards the pole,
+  whereas there seems to be less light emerging from equatorial
+  directions. But if the dynamical range between red and blue is very
+  small, maybe it’s ok, given that the equatorial spectrum is
+  broader}
+
+We have correctd the xlabel. Indeed the
+concentration of photons in a narrow range of velocities along the
+poles (i.e. red values) is compensated by a broader distribution
+around the equator. The total number of photons is the same regardless
+of the $\cos\theta$ value. This is the result of the test shown in
+Figure 5.
+
+{\bf How did you select photons when you did this Fig 2 ? Did you
+  select them on $|\cos\theta|$? You should select only one side, one
+  hemisphere, otherwise you count twice more photons anywhere else
+  than along the equator. Did you select a peculiar $\varphi$ ? Or did
+  you sum over the azimuthal direction ? In order to avoid this
+  impression that less photons escape at equator, you should indeed
+  sum over $\varphi$. }
+
+The 2D distribution is symmetric on $\cos\theta$. We mention this in
+the first paragraph of the results section. Using this symmetry we select
+by $|\cos\theta|$ in order to have less noise in the 2D histograms. We
+also sum over $\varphi$.
+
+{\bf However, these selection biases would also affect the static case, whereas the first column looks ok to me, it seems that the same “intensity” is escaping from all directions for this column, and not for the others.
 It is in strong contradiction with your Fig 5. How do you explain this ?
@@
 However, Ly$\alpha$ radiation transfer effects can often be far from intuitiv.}
+
+The colors in the Figures 2 and 3 correspond to number densities
+inside a velocity-$|\cos\theta|$ pixel. The total flux is thus an
+integrated quantity over the velocity and should not be estimated from
+the pixel intensity. It is difficult to visualize
+the result from Figures 2 and 3. That's why we prepare Figure 5 to
+show that the integrated flux is independent of the angle.
 
@@
 the equatorial plane ?}
+
+The Figure is here:\\
+
+\includegraphics[width=1.0\textwidth]{../code/intrinsic_spectrum.png}
 

### 2014-08-08 paper/referee-reply.tex
updated referee reply

@@
 It is in strong contradiction with your Fig 5. How do you explain this ?
-Furthermore, I would have expected the contrary, with more photons escaping at the equator, where the velocity field is stronger, than through the poles, where everything is static...
-However, Ly$\alpha$ radiation transfer effects can often be far from intuitiv.}
+Furthermore, I would have expected the contrary, with more photons
+escaping at the equator, where the velocity field is stronger, than
+through the poles, where everything is static... However, Ly$\alpha$
+radiation transfer effects can often be far from intuitiv.}
 
@@
 
-{\bf From your Figs 6 and 7, it seems that the results for central and homogeneous cases are very comparable.
-I would like to see the shape and FWHM of the intrinsic spectra (I mean before transfer) in the case of homogeneous sources, for the static case, as the fiducial case, and when Vmax=100,200,300 km/s, along the equatorial direction.
-I would like to infer how much of the broadening of the line is really due to transfer effects.
-Could you make a figure where you compare the intrinsic and emerging spectra along
-the equatorial plane ?}
+{\bf From your Figs 6 and 7, it seems that the results for central and
+  homogeneous cases are very comparable. I would like to see the shape
+  and FWHM of the intrinsic spectra (I mean before transfer) in the
+  case of homogeneous sources, for the static case, as the fiducial
+  case, and when Vmax=100,200,300 km/s, along the equatorial
+  direction. I would like to infer how much of the broadening of the
+  line is really due to transfer effects. Could you make a figure
+  where you compare the intrinsic and emerging spectra along the
+  equatorial plane ?}
 
@@
 
+Each column corresponds to $100$, $200$ and $300$km/s. The intrinsic
+spectrum for the static case is a delta function around $x=0$.
+
 \subsection*{Sect 4.1 : Rotation = Static ?}
 
-{\bf I don’t understand the reasonning that rotation would act on the Ly$\alpha$ transfer as a static medium, since Ly$\alpha$ photons are “co-rotating”.
-You mention this argument once in the “answer to referee” document, and once in the text Sect.
-4.1, with a sentence which reads absurd : a rotating sphere is identical from a static one.
-At least, it is not well formulated.
-It seems to me that your argument should be right for any kind of motion.
-Why would it be specific to rotation ?
-In other words, you could exchange the word “rotation” with the word “outflow” or “inflow” in your reasonning, right ?
-“While scattering events off atoms within the outflowing cloud impart Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only there in the lab-frame.
-Therefore, in the frame of the outflowing gas cloud all atoms are stationnary with respect to each other and the scattering process proceeds identical as in the static case.”.
-However, all atoms in a rotating/outflowing/infalling cloud are not stationary with respect to each other, otherwise the cloud would be static!
-Your reasonning is true at the scale of each cell, but not at global scale.
+{\bf I don’t understand the reasonning that rotation would act on the
+  Ly$\alpha$ transfer as a static medium, since Ly$\alpha$ photons are
+  “co-rotating”. You mention this argument once in the “answer to
+  referee” document, and once in the text Sect. 4.1, with a sentence
+  which reads absurd : a rotating sphere is identical from a static
+  one. At least, it is not well formulated.
+
+It seems to me that your argument should be right for any kind of
+motion. Why would it be specific to rotation ? In other words, you
+could exchange the word “rotation” with the word “outflow” or “inflow”
+in your reasonning, right ? “While scattering events off atoms within
+the outflowing cloud impart Doppler boosts on the Ly$\alpha$ photon,
+these Doppler boost are only there in the lab-frame. Therefore, in the
+frame of the outflowing gas cloud all atoms are stationnary with
+respect to each other and the scattering process proceeds identical as
+in the static case.”. However, all atoms in a
+rotating/outflowing/infalling cloud are not stationary with respect to
+each other, otherwise the cloud would be static! Your reasonning is
+true at the scale of each cell, but not at global scale.
+
 I did not understand the alternative -more quantitative- explanation better.
-Can you develop this point ?
-Maybe, to convince me, you could look at the redistribution of frequencies after one single diffusion ( 1/ in all directions, 2/ along the rotation axis, 3/ in the equator plane), emitting your photons at a radius r = 0.9 R, and comapre them with the same redistributions in the static case.
-If they are identical, you are right, rotation does not have any effect...
-if they are different, multiple scatterings will have a cumulative effect on the spectral shape, but also on the probalility to escape more easily in some directions than others...
-I understand that this implies new simulations and more time, but I would really appreciate to see these plots.
-}
+Can you develop this point ? Maybe, to convince me, you could look at
+the redistribution of frequencies after one single diffusion ( 1/ in
+all directions, 2/ along the rotation axis, 3/ in the equator plane),
+emitting your photons at a radius r = 0.9 R, and comapre them with the
+same redistributions in the static case. If they are identical, you
+are right, rotation does not have any effect... if they are different,
+multiple scatterings will have a cumulative effect on the spectral
+shape, but also on the probalility to escape more easily in some
+directions than others... I understand that this implies new
+simulations and more time, but I would really appreciate to see these
+plots. } \\
+
+These are good points. The argument that you can replace the word
+'rotating' with 'outflowing' was interesting, and briefly confused
+us. However, there is a clear difference between the two cases. For a
+cloud undergoing solid body rotation, we can draw a line between any
+two atoms within it, and their relative velocity along this line is
+zero (apart from the relative velocity as a result of Thermal motion),
+irrespective of the rotation velocity of the cloud. This relative
+velocity is what is relevant for the RT. In contrast, if one repeats
+the same exercise for the outflowing/inflowing case, then will be a
+relative velocity between two atoms which depends on the
+outflow/inflow velocity.\\
+
+We can further illustrate this point by having one photon be emitted
+in the center of the rotating cloud into the plane of the equator, and
+another in the direction of the pole. Let both photons travel $\tau=1$
+(at line center), and then scatter by 90 degrees, preserve its
+frequency in the frame of the atom, and then again travel $tau=1$. In
+both cases, the photon travels the same distance. In the LAB-frame,
+both photons will have different frequencies, but not in the frame of
+the gas.\\
+
+The situation described above is clearly unique to solid-body
+rotation. It does not apply to non-solid body rotation, which we
+intend to study in upcoming work. We think our own + the referees
+confusion only emphasizes that even this `simplified' problem of
+solid-body rotation is highly non-trivial. We have attempted to
+clarify this further in \S 3.X
 
@@
 
-{\bf It seems to me that Ly$\alpha$ photons escape a medium through the path of minimum optical depth.
-So, in a rotating cloud, where the velocity field is tangential, they might “rotate” or spiral from the center to the edge.
-To test this idea, you could look at the distribution of escaping directions from photons emerging at the pole or at the equator.
-But for this, you need to keep track of the location of escape, and not only of the direction of escape.
-Did you collect this information ?
-I would expect that photons at the equator escape more tangentially to the sphere than at the poles... But again, Ly$\alpha$ transfer is not exactly intuitiv.}
+{\bf It seems to me that Ly$\alpha$ photons escape a medium through
+  the path of minimum optical depth. So, in a rotating cloud, where
+  the velocity field is tangential, they might “rotate” or spiral from
+  the center to the edge. To test this idea, you could look at the
+  distribution of escaping directions from photons emerging at the
+  pole or at the equator. But for this, you need to keep track of the
+  location of escape, and not only of the direction of escape. Did you
+  collect this information ?
+
+I would expect that photons at the equator escape more tangentially to
+the sphere than at the poles... But again, Ly$\alpha$ transfer is not
+exactly intuitiv.}
+
+We have looked into this. We selected two different sets of
+photons. The first one escapes through the north pole and the second
+around the equator in a region with $0<\varphi<90$. For each set we
+compute the dot product $\mu\equiv\hat{k}_{out}\cdot\hat{r}_{out}$,
+where $\hat{r}_{out}$ is the unit vector in the radial direction for
+each photon. We plot the distributions for $\mu$ for two different
+$\tau_H$. In each plot we find that the two distributions (equator and
+pole) are virtually the same:
+
+\begin{center}
+\includegraphics[width=0.6\textwidth]{../code/surface_mu_tau5_diff_pos.png}
+\includegraphics[width=0.6\textwidth]{../code/surface_mu_tau7_diff_pos.png}
+\end{center}
+
+The distribution is also insensitive to the rotational velocity:
+
+\begin{center}
+\includegraphics[width=0.6\textwidth]{../code/surface_mu_t5_diff_v.png}
+\end{center}
+
+The only trend can be found for different optical depths:
+
+\begin{center}
+\includegraphics[width=0.6\textwidth]{../code/surface_mu_diff_tau.png}
+\end{center}
 
@@
 
-{\bf You say that “If the viewing angle is aligned with the rotation axis, $|\mu| \approx 1$, the Ly$\alpha$ line keeps in most of the cases a double peak”, isn’t it in all cases ?}
+{\bf You say that “If the viewing angle is aligned with the rotation
+  axis, $|\mu| \approx 1$, the Ly$\alpha$ line keeps in most of the
+  cases a double peak”, isn’t it in all cases ?}
 
@@
 
-{\bf Is Fig 9, left panel, for a central source ?
-Can you show the homogeneous case also ?
-You discuss in the referee repport that the distribution is not bimodal anymore.
-But it has to be different than in central case, spanning the whole range of nb scatt, because photons are emitted at every radii in the cloud, so at every optical depth.
-On the right panel, solid and dashed lines are not defined.}
+{\bf Is Fig 9, left panel, for a central source ? Can you show the
+  homogeneous case also ? You discuss in the referee repport that the
+  distribution is not bimodal anymore. But it has to be different than
+  in central case, spanning the whole range of nb scatt, because
+  photons are emitted at every radii in the cloud, so at every optical
+  depth. On the right panel, solid and dashed lines are not defined.}
 
 \subsection*{Vmax = 1000 km/s}
-{\bf If you did this test and checked that the nb of scatterings and the escape fraction is still angle invariant for such a high velocity, then it is worth mentionning it.
-Because in principle, media with very high velocities should start to become transparent for Ly$\alpha$.}
+{\bf If you did this test and checked that the nb of scatterings and
+  the escape fraction is still angle invariant for such a high
+  velocity, then it is worth mentionning it. Because in principle,
+  media with very high velocities should start to become transparent
+  for Ly$\alpha$.}
+
+For solid body rotation, the results should not depend on $v_{\rm
+  max}$ at all. We have even done calculations with $v_{\rm max}=10^6$
+km/s, and confirmed this result.
 

### 2014-08-08 paper/referee-reply.tex
updated path to the figures in the referee reply

@@
 
-\includegraphics[width=1.0\textwidth]{../code/intrinsic_spectrum.png}
+\includegraphics[width=1.0\textwidth]{./intrinsic_spectrum.png}
 
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{../code/surface_mu_tau5_diff_pos.png}
-\includegraphics[width=0.6\textwidth]{../code/surface_mu_tau7_diff_pos.png}
+\includegraphics[width=0.6\textwidth]{./surface_mu_tau5_diff_pos.png}
+\includegraphics[width=0.6\textwidth]{./surface_mu_tau7_diff_pos.png}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{../code/surface_mu_t5_diff_v.png}
+\includegraphics[width=0.6\textwidth]{./surface_mu_t5_diff_v.png}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{../code/surface_mu_diff_tau.png}
+\includegraphics[width=0.6\textwidth]{./surface_mu_diff_tau.png}
 \end{center}

### 2014-08-11 paper/ms.tex
minor change in reference
minor updates in ms
Mark's input

@@
 configurations, such as uniform slabs
-\citep{Adams72,Harrington73,Neufeld90} and uniform spheres
+\citep[][]{Adams72,Harrington73,Neufeld90} and uniform spheres
 \citep{Dijkstra06}. 
@@
 expanding/contracting shell/spherical geometries started to be studied
-\citep{Ahn03,Verhamme06,Dijkstra06}.  
+\citep{Ahn03,Verhamme06,Dijkstra06}.  For a recent review, we refer the interested reader to \citet{review}.
 Similar codes have applied these results to semi-analytic models of
@@
 \subsection{Integrated Line Intensity}
+\label{sec:intlineint}
 
@@
 with $\tau_{\rm H}=10^{5}$, different rotational velocities and the two
-types of source distributions.
-This shows that $F(\mu)$ is consistent with being flat, apart
-from some statistical fluctuations on the order of \%2.
-
-This is a remarkable result. 
-In spite of that the rotation axis defines preferential direction, the
-integrated flux is the same for all viewing angles in the
-range of parameters explored in this paper.
+types of source distributions. This shows that $F(\mu)$ is consistent with being flat, apart
+from some statistical fluctuations on the order of 2\%.
+
+This is a remarkable result: while the rotation axis defines preferential direction, the
+integrated flux is the same for all viewing angles in the range of parameters explored in this paper. {\bf This can be understood from the fact that
+{\it radiative transfer inside a sphere that undergoes solid-body rotation proceeds identical as inside a static sphere}: we can draw a line between any two atoms within the rotating cloud, and their relative velocity along this line is zero (apart from the relative velocity as a result of random thermal motion), irrespective of the rotation velocity of the cloud.
+This relative velocity is what is relevant for the radiative transfer\footnote{This point can be further illustrated by considering the path of individual photons: let a photon be emitted at line center ($x=0$), in some random direction ${\bf k}$, propagate a distance that corresponds to $\tau_0=1$, scatter fully coherently (i.e.
+$x=0$ after scattering in the gas frame) by 90$^{\circ}$, and again propagate a distance that corresponds to $\tau_0=1$.
+The position where the photon scatters next does {\it not} depend on the rotation of the cloud, nor on ${\bf k}$.}.}
 
@@
 We now estimate the escape fraction $f_{\rm esc}$ for the dusty
-models. 
-The main  result is that we do not find any significant dependence
+models. The main result is that we do not find any significant dependence
 with either the viewing angle nor the rotational velocity.
-For completeness we list in Table \ref{table:escape} the scape
+This is consistent with our finding in \S~\ref{sec:intlineint}, that radiative transfer inside the cloud does not depend on its rotational velocity.
+For completeness we list in Table \ref{table:escape} the escape
 fraction for all models.
@@
 The number of scatterings affects the escape frequency of a \ly
-photon. 
-Studying this quantity can help us in clarifying the independence of
-the integrated flux and the escape fraction with respect to the
-rotational velocity.
+photon. Studying this quantity further illustrates the independence of
+the integrated flux and the escape fraction on rotational velocity.
 
@@
 
-One way to understand this is that a rotating sphere
-is identical from a static one. 
-While scattering events off atoms within the rotating cloud impart
+As we explained in \S~\ref{sec:intlineint}, the best way to understand this is that radiative transfer inside a sphere that undergoes solid-body rotation
+proceeds identical to that inside a non-rotating sphere. While scattering events off atoms within the rotating cloud impart
 Doppler boosts on the Ly$\alpha$ photon, these Doppler boost are only
-there in the lab-frame.  
-Therefore, in the frame of the rotating gas cloud all atoms are
+there in the lab-frame. Therefore, in the frame of the rotating gas cloud all atoms are
 stationary with respect to each other and the scattering process
-proceeds identical as in the static case.
-
-An alternative - more quantitative way - to view this is   to consider
-the path of an individual photon: say the photon travels  a distance
-corresponding to $\tau=1$, scatters by $90$ degrees, then travels
-another distance corresponding to $\tau=1$. 
-The point where the photon ends up is independent of the assumed
-rotation velocity of the cloud.
-
-The spectrum of \lya photons emerging from a rotating gas cloud is
-also identical as for the static case in a frame that is co-rotating
-with the cloud. 
-However, the surface of cloud now moves in the lab-frame. 
+proceeds identical as in the static case (also see \S~\ref{sec:intlineint} for an additional more quantitative explanation).
+
+%An alternative - more quantitative way - to view this is   to consider the path of an individual photon: say the photon travels  a distance corresponding to $\tau=1$, scatters by $90$ degrees, then travels another distance corresponding to $\tau=1$.
+The point where the photon ends up is independent of the assumed rotation velocity of the cloud.
+
+This result allows us to analytically estimate the spectrum emerging from a rotating cloud:
+The spectrum of \lya photons emerging from a rotating gas cloud is identical as for the static case in a frame that is co-rotating
+with the cloud. However, the surface of cloud now moves in the lab-frame. 
 Each surface-element on the rotating cloud now has a bulk
-velocity with respect to a distant observer. 
-In order to compute the
+velocity with respect to a distant observer. In order to compute the
 spectrum one can integrate over all the surface elements in the
@@
 to the axis of rotation ($i=0$ in the scheme of Fig~\ref{fig:scheme}
-in the Appendix). 
-The right panel shows the results for different viewing angles in the
+in the Appendix). The right panel shows the results for different viewing angles in the
 case of $\tau_{H}=10^7$ and a rotational velocity of $V_{\rm
@@
 
-The two methods clearly give good agreement, though not perfect. 
-In particular, the left panel shows that the MC gives rise to a spectrum that is
+The two methods clearly give good agreement, though not perfect.  In particular, the left panel shows that the MC gives rise to a spectrum that is
 slightly more concentrated towards the line centre.
-It is possible to get better agreement my modifying the surface brightness
-profile.
+As we explain in Appendix~\ref{sec:app}, we do not expect perfect agreement, because this requires an analytic solution for the spectrum of Ly$\alpha$ photons emerging from a static, optically extremely thick cloud {\it as a function of the angle at which they escape from the sphere}.
+This solution does not exist in the literature.
+It is possible to get better agreement my modifying the surface brightness profile.
 In any case, the analytic calculation closely captures the results
@@
 contain flux at line center may be `leaking' ionizing (LyC) photons
-\citep{2014arXiv1404.2958V,Behrens2014}. The main reason for this possible
+\citep{Behrens2014,2014arXiv1404.2958V}. The main reason for this possible
 connection is that the escape of ionizing (LyC) photons requires
@@
 has also been associated with escape of ionizing (LyC) photons
-\cite{Behrens2014,2014arXiv1404.2958V}
+\citep{Behrens2014,2014arXiv1404.2958V}
 
@@
   emerging from Rotating Cloud}  
+\label{sec:app}
 

### 2014-08-11 paper/ms.tex
new ms version

@@
 
+%@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
 \begin{document}
@@
 In this paper we express a photon's frequency in terms of the
-dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_\alpha$, where
-$\nu_{\alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
-frequency,  $\Delta\nu_{\alpha} \equiv
+dimensionless variable $x\equiv (\nu -\nu_a)/\Delta\nu_{\rm D}$, where
+$\nu_{\rm \alpha}=2.46\times 10^{15}$ Hz is the Ly$\alpha$ resonance
+frequency,  $\Delta\nu_{\rm D} \equiv
 \nu_{\alpha}\sqrt{2kT/m_pc^2}\equiv \nu_av_{\rm th}/c $ is the Doppler
 broadening of the line which depends on the neutral gas temperature
-$T$ scattering the radiation or equivalently the thermal velocity
-$v_{\rm th}$ of the atoms.  For the temperature $T=10^4$K used in our
-radiative transfer calculations the thermal velocity is
-$v_{\rm th}=12.8$\kms.
+$T$ or equivalently the thermal velocity
+$v_{\rm th}$ of the atoms. We also use the parameter $a$ to define the
+relative line width as $a=\Delta\nu_{\alpha}/2\Delta\nu_{\rm D}$,
+where $\Delta\nu_{\alpha}$ is the intrinsic linewidth. For the
+temperature $T=10^4$K used in our radiative transfer calculations the
+thermal velocity is $v_{\rm th}=12.8$\kms.
 
@@
 If the viewing angle is aligned with the rotation axis, $|\mu|\sim
-1$, the \ly line keeps in most of the cases a double peak with minor
-changes as the rotational velocity starts to increase. 
+1$, the \ly line keeps a double peak with minor
+changes in the morphology as the rotational velocity increases. 
 However, for a line of sight perpendicular to the rotation axis,
@@
 This is a remarkable result: while the rotation axis defines preferential direction, the
-integrated flux is the same for all viewing angles in the range of parameters explored in this paper. {\bf This can be understood from the fact that
-{\it radiative transfer inside a sphere that undergoes solid-body rotation proceeds identical as inside a static sphere}: we can draw a line between any two atoms within the rotating cloud, and their relative velocity along this line is zero (apart from the relative velocity as a result of random thermal motion), irrespective of the rotation velocity of the cloud.
-This relative velocity is what is relevant for the radiative transfer\footnote{This point can be further illustrated by considering the path of individual photons: let a photon be emitted at line center ($x=0$), in some random direction ${\bf k}$, propagate a distance that corresponds to $\tau_0=1$, scatter fully coherently (i.e.
-$x=0$ after scattering in the gas frame) by 90$^{\circ}$, and again propagate a distance that corresponds to $\tau_0=1$.
-The position where the photon scatters next does {\it not} depend on the rotation of the cloud, nor on ${\bf k}$.}.}
+integrated flux is the same for all viewing angles in the range of parameters explored in this paper. This can be understood from the fact that
+{\it radiative transfer inside a sphere that undergoes solid-body
+  rotation proceeds identical as inside a static sphere}: we can draw
+a line between any two atoms within the rotating cloud, and their
+relative velocity along this line is zero (apart from the relative
+velocity as a result of random thermal motion), irrespective of the
+rotation velocity of the cloud. This relative velocity is what is
+relevant for the radiative transfer\footnote{This point can be further
+  illustrated by considering the path of individual photons: let a
+  photon be emitted at line center ($x=0$), in some random direction
+  ${\bf k}$, propagate a distance that corresponds to $\tau_0=1$,
+  scatter fully coherently (i.e. $x=0$ after scattering in the gas
+  frame) by 90$^{\circ}$, and again propagate a distance that
+  corresponds to $\tau_0=1$. The position where the photon scatters
+  next does {\it not} depend on the rotation of the cloud, nor on
+  ${\bf k}$.}
 
@@
 max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
-  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$; the independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is present in all models.
+  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$. In the
+  right panel the continous (dashed) lines represent the results for
+  the central (homogeneous) model. The independence of $N_{\rm scatt}$ with $\mu$ and $V_{\rm max}$ is
+  present in all models.  
 \label{fig:Nscatt} }
@@
 
-%In order to gain a deeper understanding of these results  we make 2D
-%histograms for the number of scatterings as a function of the outgoing
-%dimensionless frequency $x$. In Fig. \ref{fig:Nscatt2D} we show these 
-%results in the case $\tau_{\rm H}=10^5$ for the
-%static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
-%results for the homogeneous (central) source distribution. The color
-%scale is logarithmic in the number of photons at a certain value
-%$x-N_{\rm scatt}$.
-
-%The top right panel of Fig. \ref{fig:Nscatt2D} (homogeneous sources,
-%high rotational velocity) supports our hypothesis about
-%the photo-sphere in the homogeneous distribution. In this case most of
-%the photons that left with $x\sim 0$ have escaped with less than $10$
-%scatterings. This also explains the decrease in the average number of
-%scatterings observed in Fig. \ref{fig:Nscatt}. We have also veryfied
-%that these photons are indeed emitted closer to the surface than to
-%the center of the sphere.
-
-%However, for a central distribution the situation is quite different
-%(lower panels in Fig. \ref{fig:Nscatt2D}). In this case the number
-%of scatterings remains high, in the order of the optical depth, but
-%the two peaks do get closer to each other. The most probable
-%physical picture is that each scattering, due to the bulk velocity of
-%the gas, is inefficient in driving the photon outside the line
-%center.
-
 In static configurations it is expected that the optical depth correlates number of
@@
 proceeds identical as in the static case (also see \S~\ref{sec:intlineint} for an additional more quantitative explanation).
-
-%An alternative - more quantitative way - to view this is   to consider the path of an individual photon: say the photon travels  a distance corresponding to $\tau=1$, scatters by $90$ degrees, then travels another distance corresponding to $\tau=1$.
-The point where the photon ends up is independent of the assumed rotation velocity of the cloud.
 

### 2014-08-11 paper/ms.tex
version para mark

@@
 \newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
-
 % definition to produce a "less than or similar to" symbol
 \def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
-
 % definition to produce a "greater than or similar to" symbol
 \def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
-
 %@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{38}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Adams}(1972)}]{Adams72}
+{Adams}, T.~F. 1972, \apj, 174, 439
+
+\bibitem[{{Ahn} {et~al.}(2000){Ahn}, {Lee}, \& {Lee}}]{Ahn00}
+{Ahn}, S.-H., {Lee}, H.-W., \& {Lee}, H.~M. 2000, Journal of Korean
+  Astronomical Society, 33, 29
+
+\bibitem[{{Ahn} {et~al.}(2001){Ahn}, {Lee}, \& {Lee}}]{Ahn01}
+---. 2001, \apj, 554, 604
+
+\bibitem[{{Ahn} {et~al.}(2003){Ahn}, {Lee}, \& {Lee}}]{Ahn03}
+---. 2003, \mnras, 340, 863
+
+\bibitem[{{Auer}(1968)}]{Auer68}
+{Auer}, L.~H. 1968, \apj, 153, 783
+
+\bibitem[{{Avery} \& {House}(1968)}]{Avery68}
+{Avery}, L.~W., \& {House}, L.~L. 1968, \apj, 152, 493
+
+\bibitem[{{Barnes} {et~al.}(2011){Barnes}, {Haehnelt}, {Tescari}, \&
+  {Viel}}]{Barnes11}
+{Barnes}, L.~A., {Haehnelt}, M.~G., {Tescari}, E., \& {Viel}, M. 2011, \mnras,
+  416, 1723
+
+\bibitem[{{Behrens} {et~al.}(2014){Behrens}, {Dijkstra}, \&
+  {Niemeyer}}]{Behrens2014}
+{Behrens}, C., {Dijkstra}, M., \& {Niemeyer}, J.~C. 2014, \aap, 563, A77
+
+\bibitem[{{Behrens} \& {Niemeyer}(2013)}]{Behrens13}
+{Behrens}, C., \& {Niemeyer}, J. 2013, \aap, 556, A5
+
+\bibitem[{{Dayal} \& {Ferrara}(2012)}]{Dayal2012}
+{Dayal}, P., \& {Ferrara}, A. 2012, \mnras, 421, 2568
+
+\bibitem[{{Dijkstra}(2014)}]{review}
+{Dijkstra}, M. 2014, ArXiv e-prints, arXiv:1406.7292
+
+\bibitem[{{Dijkstra} {et~al.}(2006){Dijkstra}, {Haiman}, \&
+  {Spaans}}]{Dijkstra06}
+{Dijkstra}, M., {Haiman}, Z., \& {Spaans}, M. 2006, \apj, 649, 14
+
+\bibitem[{{Dijkstra} \& {Kramer}(2012)}]{DijkstraKramer}
+{Dijkstra}, M., \& {Kramer}, R. 2012, \mnras, 424, 1672
+
+\bibitem[{Finkelstein {et~al.}(2013)Finkelstein, Papovich, Dickinson, Song,
+  Tilvi, Koekemoer, Finkelstein, Mobasher, Ferguson, Giavalisco, Reddy, Ashby,
+  Dekel, Fazio, Fontana, Grogin, Huang, Kocevski, Rafelski, Weiner, \&
+  Willner}]{Finkelstein2013}
+Finkelstein, S.~L., Papovich, C., Dickinson, M., Song, M., Tilvi, V.,
+  Koekemoer, a.~M., Finkelstein, K.~D., Mobasher, B., Ferguson, H.~C.,
+  Giavalisco, M., Reddy, N., Ashby, M. L.~N., Dekel, a., Fazio, G.~G., Fontana,
+  a., Grogin, N.~a., Huang, J.-S., Kocevski, D., Rafelski, M., Weiner, B.~J.,
+  \& Willner, S.~P. 2013, Nature, 502, 524
+
+\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, {Knollmann}, {Cuesta}, \& {Prada}}]{CLARA}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., {Knollmann}, S.~R.,
+  {Cuesta}, A.~J., \& {Prada}, F. 2011, \mnras, 415, 3666
+
+\bibitem[{{Forero-Romero} {et~al.}(2012){Forero-Romero}, {Yepes},
+  {Gottl{\"o}ber}, \& {Prada}}]{Forero12}
+{Forero-Romero}, J.~E., {Yepes}, G., {Gottl{\"o}ber}, S., \& {Prada}, F. 2012,
+  \mnras, 419, 952
+
+\bibitem[{{Garel} {et~al.}(2012){Garel}, {Blaizot}, {Guiderdoni}, {Schaerer},
+  {Verhamme}, \& {Hayes}}]{Garel2012}
+{Garel}, T., {Blaizot}, J., {Guiderdoni}, B., {Schaerer}, D., {Verhamme}, A.,
+  \& {Hayes}, M. 2012, \mnras, 422, 310
+
+\bibitem[{{Gawiser} {et~al.}(2007){Gawiser}, {Francke}, {Lai}, {Schawinski},
+  {Gronwall}, {Ciardullo}, {Quadri}, {Orsi}, {Barrientos}, {Blanc}, {Fazio}, \&
+  {Feldmeier}}]{Gawiser2007}
+{Gawiser}, E., {Francke}, H., {Lai}, K., {Schawinski}, K., {Gronwall}, C.,
+  {Ciardullo}, R., {Quadri}, R., {Orsi}, A., {Barrientos}, L.~F., {Blanc},
+  G.~A., {Fazio}, G., \& {Feldmeier}, J.~J. 2007, \apj, 671, 278
+
+\bibitem[{{Hansen} \& {Oh}(2006)}]{Hansen06}
+{Hansen}, M., \& {Oh}, S.~P. 2006, \mnras, 367, 979
+
+\bibitem[{{Harrington}(1973)}]{Harrington73}
+{Harrington}, J.~P. 1973, \mnras, 162, 43
+
+\bibitem[{Hunter(2007)}]{matplotlib}
+Hunter, J.~D. 2007, Computing In Science \& Engineering, 9, 90
+
+\bibitem[{{Koehler} {et~al.}(2007){Koehler}, {Schuecker}, \&
+  {Gebhardt}}]{Koehler2007}
+{Koehler}, R.~S., {Schuecker}, P., \& {Gebhardt}, K. 2007, \aap, 462, 7
+
+\bibitem[{{Laursen} {et~al.}(2009){Laursen}, {Sommer-Larsen}, \&
+  {Andersen}}]{Laursen09}
+{Laursen}, P., {Sommer-Larsen}, J., \& {Andersen}, A.~C. 2009, \apj, 704, 1640
+
+\bibitem[{{Loeb} \& {Rybicki}(1999)}]{LoebRybicki}
+{Loeb}, A., \& {Rybicki}, G.~B. 1999, \apj, 524, 527
+
+\bibitem[{{Neufeld}(1990)}]{Neufeld90}
+{Neufeld}, D.~A. 1990, \apj, 350, 216
+
+\bibitem[{{Orsi} {et~al.}(2012){Orsi}, {Lacey}, \& {Baugh}}]{Orsi12}
+{Orsi}, A., {Lacey}, C.~G., \& {Baugh}, C.~M. 2012, \mnras, 425, 87
+
+\bibitem[{{Ouchi} {et~al.}(2008){Ouchi}, {Shimasaku}, {Akiyama}, {Simpson},
+  {Saito}, {Ueda}, {Furusawa}, {Sekiguchi}, {Yamada}, {Kodama}, {Kashikawa},
+  {Okamura}, {Iye}, {Takata}, {Yoshida}, \& {Yoshida}}]{Ouchi08}
+{Ouchi}, M., {Shimasaku}, K., {Akiyama}, M., {Simpson}, C., {Saito}, T.,
+  {Ueda}, Y., {Furusawa}, H., {Sekiguchi}, K., {Yamada}, T., {Kodama}, T.,
+  {Kashikawa}, N., {Okamura}, S., {Iye}, M., {Takata}, T., {Yoshida}, M., \&
+  {Yoshida}, M. 2008, \apjs, 176, 301
+
+\bibitem[{{Partridge} \& {Peebles}(1967)}]{PartridgePeebles}
+{Partridge}, R.~B., \& {Peebles}, P.~J.~E. 1967, \apj, 147, 868
+
+\bibitem[{P\'erez \& Granger(2007)}]{IPython}
+P\'erez, F., \& Granger, B.~E. 2007, Computing in Science and Engineering, 9,
+  21
+
+\bibitem[{{Rhoads} {et~al.}(2000){Rhoads}, {Malhotra}, {Dey}, {Stern},
+  {Spinrad}, \& {Jannuzi}}]{Rhoads00}
+{Rhoads}, J.~E., {Malhotra}, S., {Dey}, A., {Stern}, D., {Spinrad}, H., \&
+  {Jannuzi}, B.~T. 2000, \apjl, 545, L85
+
+\bibitem[{{Schenker} {et~al.}(2012){Schenker}, {Stark}, {Ellis}, {Robertson},
+  {Dunlop}, {McLure}, {Kneib}, \& {Richard}}]{Schenker2012}
+{Schenker}, M.~A., {Stark}, D.~P., {Ellis}, R.~S., {Robertson}, B.~E.,
+  {Dunlop}, J.~S., {McLure}, R.~J., {Kneib}, J.-P., \& {Richard}, J. 2012,
+  \apj, 744, 179
+
+\bibitem[{{Verhamme} {et~al.}(2012){Verhamme}, {Dubois}, {Blaizot}, {Garel},
+  {Bacon}, {Devriendt}, {Guiderdoni}, \& {Slyz}}]{Verhamme12}
+{Verhamme}, A., {Dubois}, Y., {Blaizot}, J., {Garel}, T., {Bacon}, R.,
+  {Devriendt}, J., {Guiderdoni}, B., \& {Slyz}, A. 2012, \aap, 546, A111
+
+\bibitem[{{Verhamme} {et~al.}(2014){Verhamme}, {Orlitova}, {Schaerer}, \&
+  {Hayes}}]{2014arXiv1404.2958V}
+{Verhamme}, A., {Orlitova}, I., {Schaerer}, D., \& {Hayes}, M. 2014, ArXiv
+  e-prints
+
+\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
+  {Maselli}}]{Verhamme06}
+{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
+
+\bibitem[{{Yajima} {et~al.}(2012){Yajima}, {Li}, {Zhu}, {Abel}, {Gronwall}, \&
+  {Ciardullo}}]{Yajima12}
+{Yajima}, H., {Li}, Y., {Zhu}, Q., {Abel}, T., {Gronwall}, C., \& {Ciardullo},
+  R. 2012, \apj, 754, 118
+
+\bibitem[{{Yamada} {et~al.}(2012){Yamada}, {Nakamura}, {Matsuda}, {Hayashino},
+  {Yamauchi}, {Morimoto}, {Kousai}, \& {Umemura}}]{Yamada2012}
+{Yamada}, T., {Nakamura}, Y., {Matsuda}, Y., {Hayashino}, T., {Yamauchi}, R.,
+  {Morimoto}, N., {Kousai}, K., \& {Umemura}, M. 2012, \aj, 143, 79
+
+\bibitem[{{Zheng} \& {Miralda-Escud{\'e}}(2002)}]{Zheng02}
+{Zheng}, Z., \& {Miralda-Escud{\'e}}, J. 2002, \apj, 578, 33
+
+\bibitem[{{Zheng} \& {Wallace}(2013)}]{Zheng2013}
+{Zheng}, Z., \& {Wallace}, J. 2013, ArXiv e-prints
+
+\end{thebibliography}
 

### 2014-08-11 paper/referee-reply.tex
update referee reply
referee repply update
udpates in the referee reply

@@
 
+  Yes it is doubles peaked in all the studies cases. This is reflected
+  in the text.
+
 \subsection*{Sect. 3.5}
 {\bf The parameter a is not defined when you discuss Neufeld.}
+
+The definition is now included in the last paragraph of the
+introduction.
 
@@
   depth. On the right panel, solid and dashed lines are not defined.}
+
+Here is the distribution for the homogeneous case. Although it is not
+noticeable in the histogram, there are various photons that escape
+with a low number of scatterings (i.e. the minimum number of
+scatterings we found for some photons is 2).
+
+We have modified the caption to define the solid and dashed lines.
+
+\begin{center}
+\includegraphics[width=0.6\textwidth]{./f9h.png}
+\end{center}
 

### 2014-08-11 paper/referee-reply.tex
updated referee reply

@@
 
+We thanks the referee for the new comments, suggestions and remars.
 In what follows the comments by the referee are boldfaced.
@@
 
-We have correctd the xlabel. Indeed the
-concentration of photons in a narrow range of velocities along the
-poles (i.e. red values) is compensated by a broader distribution
-around the equator. The total number of photons is the same regardless
-of the $\cos\theta$ value. This is the result of the test shown in
-Figure 5.
+We have correctd the xlabel. Indeed the concentration of photons in a
+narrow range of velocities along the poles (i.e. red values) is
+compensated by a broader distribution around the equator. The total
+number of photons is the same regardless of the $\cos\theta$
+value. This is the result of the test shown in Figure 5.
 
@@
 
-Each column corresponds to $100$, $200$ and $300$km/s. The intrinsic
-spectrum for the static case is a delta function around $x=0$.
+Each column corresponds to $0$, $100$, $200$ and $300$km/s.
 
@@
 solid-body rotation is highly non-trivial. We have attempted to
-clarify this further in \S 3.X
+clarify this further in \S 3.2.
 

### 2014-08-12 paper/ms.tex
arxiv version

@@
 hydrogen at a constant temperature. 
-These spheres have a solid-body rotation with maximum velocities in
+These spheres undergo solid-body rotation with maximum velocities in
 the range $0-300$ \kms and neutral hydrogen optical depths in the
@@
 velocities close to half the line width in the static case. 
-Notably, we find that rotation does not induce any significant spatial
-anisotropy in the integrated line flux, the escape fraction or the
-average number of scatterings. From this, we conclude that the \lya scattering
-through a rotating solid-body proceeds identical to the static
-case. The only difference is the doppler shift from the different
+Notably, we find that rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average number of scatterings.
+This is because Lyman α scattering through a rotating solid-body proceeds identical as in the static case.
+The only difference is the doppler shift from the different
 regions in the sphere that move with respect to the observer. This

### 2014-09-08 paper/ms.tex
new appendix figures

@@
 \begin{figure*}[h]
-\centerline{\includegraphics[width=85mm]{fig11a.pdf}
-\includegraphics[width=85mm]{fig11b.pdf}}
+\centerline{\includegraphics[width=80mm]{fig11a.pdf}
+\includegraphics[width=80mm]{fig11b.pdf}}
 \caption[]{Adopted geometry for evaluating the analytic spectrum.}
@@
 
+To further test the assumption of scattering in a rotating medium proceeding
+as in a static medium we compute the distribution of the outgoing
+angles $\mu$. The results are shown in Figure \ref{fig:surface}; it
+shows that the distribution for $\mu$ is independent of the rotational
+velocity and the location over the sphere. The only dependence comes
+with $\tau_{H}$. For higher values of the optical depth the
+distribution gets closer to $I(\mu)\propto \mu$ as expected for a
+static medium \citep{Ahn01}.
+
+%
+\begin{figure*}[h]
+\centerline{
+\includegraphics[width=0.30\textwidth]{fig12a.pdf}
+\includegraphics[width=0.30\textwidth]{fig12b.pdf}
+\includegraphics[width=0.30\textwidth]{fig12c.pdf}}
+\caption[]{Distribution of the cosine of the angle between the
+  propagation direction and the sphere's surface. The distributions
+  have been normalized to unity. Left panel: different rotational
+  velocities; middle panel: different viewing angles; right panel:
+  different optical depths. Only the optical depth has an effect on
+  the outogoing directions. This is consistent with the assumption
+  that \lya scattering in a medium with solid body rotation proceeds as in
+  a static medium.}
+\label{fig:surface}
+\end{figure*} 
+%
+
 \bibliographystyle{apj}

### 2014-09-08 paper/referee-reply.tex
new referee reply

--- 2014-08-08 paper/referee-reply.tex
@@
 
+We thanks the referee for the new minor comments. 
 In what follows the comments by the referee are boldfaced.
@@
 
-\section*{Global Comments}
+\section*{Minor Comments}
 
-\subsection*{Variations with viewing angle... again}
+{\bf About the directionallity of the escaping photons, why did you select only photons with $0 < \varphi < \pi/2$?
+Did you then normalise the blue and green curves to sample the same number of photons ?
+Now that I understood that Lya transfer in solid-body rotating cloud proceeds like in a static medium, until projection in an external, non-rotating frame, the only expected trend should be with optical depth, indeed.
+These curves show $I(\mu)$ that you discuss in the appendix, right ?
+It seems that the regimes that you investigated are not yet enough optically thick so that $I(\mu) = \propto \mu$.
+Maybe you can show these plots on the appendix, to illustrate that the analytic solution becomes better in veryoptically thick regimes.}
 
-{\bf Figs 2 and 3 are very nice. They illustrate clearly the evolution
-  of spectral shape with viewing angle. Note that the x label is
-  wrong, it is not Vmax. It also needs a color bar to explicit the
-  scale between a red pixel and a green/blue pixel. Because... to my
-  eyes, there is an obvious third result illustrated on these Figs,
-  which is that much less photons seem to escape at the equator than
-  along the poles: the red pixels are concentrated towards the pole,
-  whereas there seems to be less light emerging from equatorial
-  directions. But if the dynamical range between red and blue is very
-  small, maybe it’s ok, given that the equatorial spectrum is
-  broader}
+We did not limit the selection to $0 < \varphi < \pi/2$. The outgoing
+photons close to the surface follow are in that range, where $\varphi$
+describes the angle with respect to the normal to the surface.  The
+curves have the same normalization in each of the plots.
 
-We have correctd the xlabel. Indeed the
-concentration of photons in a narrow range of velocities along the
-poles (i.e. red values) is compensated by a broader distribution
-around the equator. The total number of photons is the same regardless
-of the $\cos\theta$ value. This is the result of the test shown in
-Figure 5.
-
-{\bf How did you select photons when you did this Fig 2 ? Did you
-  select them on $|\cos\theta|$? You should select only one side, one
-  hemisphere, otherwise you count twice more photons anywhere else
-  than along the equator. Did you select a peculiar $\varphi$ ? Or did
-  you sum over the azimuthal direction ? In order to avoid this
-  impression that less photons escape at equator, you should indeed
-  sum over $\varphi$. }
-
-The 2D distribution is symmetric on $\cos\theta$. We mention this in
-the first paragraph of the results section. Using this symmetry we select
-by $|\cos\theta|$ in order to have less noise in the 2D histograms. We
-also sum over $\varphi$.
-
-{\bf However, these selection biases would also affect the static case, whereas the first column looks ok to me, it seems that the same “intensity” is escaping from all directions for this column, and not for the others.
-It is in strong contradiction with your Fig 5. How do you explain this ?
-Furthermore, I would have expected the contrary, with more photons
-escaping at the equator, where the velocity field is stronger, than
-through the poles, where everything is static... However, Ly$\alpha$
-radiation transfer effects can often be far from intuitiv.}
-
-The colors in the Figures 2 and 3 correspond to number densities
-inside a velocity-$|\cos\theta|$ pixel. The total flux is thus an
-integrated quantity over the velocity and should not be estimated from
-the pixel intensity. It is difficult to visualize
-the result from Figures 2 and 3. That's why we prepare Figure 5 to
-show that the integrated flux is independent of the angle.
-
-\subsection*{intrinsic spectrum on Fig 4}
-
-{\bf From your Figs 6 and 7, it seems that the results for central and
-  homogeneous cases are very comparable. I would like to see the shape
-  and FWHM of the intrinsic spectra (I mean before transfer) in the
-  case of homogeneous sources, for the static case, as the fiducial
-  case, and when Vmax=100,200,300 km/s, along the equatorial
-  direction. I would like to infer how much of the broadening of the
-  line is really due to transfer effects. Could you make a figure
-  where you compare the intrinsic and emerging spectra along the
-  equatorial plane ?}
-
-The Figure is here:\\
-
-\includegraphics[width=1.0\textwidth]{./intrinsic_spectrum.png}
-
-Each column corresponds to $100$, $200$ and $300$km/s. The intrinsic
-spectrum for the static case is a delta function around $x=0$.
-
-\subsection*{Sect 4.1 : Rotation = Static ?}
-
-{\bf I don’t understand the reasonning that rotation would act on the
-  Ly$\alpha$ transfer as a static medium, since Ly$\alpha$ photons are
-  “co-rotating”. You mention this argument once in the “answer to
-  referee” document, and once in the text Sect. 4.1, with a sentence
-  which reads absurd : a rotating sphere is identical from a static
-  one. At least, it is not well formulated.
-
-It seems to me that your argument should be right for any kind of
-motion. Why would it be specific to rotation ? In other words, you
-could exchange the word “rotation” with the word “outflow” or “inflow”
-in your reasonning, right ? “While scattering events off atoms within
-the outflowing cloud impart Doppler boosts on the Ly$\alpha$ photon,
-these Doppler boost are only there in the lab-frame. Therefore, in the
-frame of the outflowing gas cloud all atoms are stationnary with
-respect to each other and the scattering process proceeds identical as
-in the static case.”. However, all atoms in a
-rotating/outflowing/infalling cloud are not stationary with respect to
-each other, otherwise the cloud would be static! Your reasonning is
-true at the scale of each cell, but not at global scale.
-
-I did not understand the alternative -more quantitative- explanation better.
-Can you develop this point ? Maybe, to convince me, you could look at
-the redistribution of frequencies after one single diffusion ( 1/ in
-all directions, 2/ along the rotation axis, 3/ in the equator plane),
-emitting your photons at a radius r = 0.9 R, and comapre them with the
-same redistributions in the static case. If they are identical, you
-are right, rotation does not have any effect... if they are different,
-multiple scatterings will have a cumulative effect on the spectral
-shape, but also on the probalility to escape more easily in some
-directions than others... I understand that this implies new
-simulations and more time, but I would really appreciate to see these
-plots. } \\
-
-These are good points. The argument that you can replace the word
-'rotating' with 'outflowing' was interesting, and briefly confused
-us. However, there is a clear difference between the two cases. For a
-cloud undergoing solid body rotation, we can draw a line between any
-two atoms within it, and their relative velocity along this line is
-zero (apart from the relative velocity as a result of Thermal motion),
-irrespective of the rotation velocity of the cloud. This relative
-velocity is what is relevant for the RT. In contrast, if one repeats
-the same exercise for the outflowing/inflowing case, then will be a
-relative velocity between two atoms which depends on the
-outflow/inflow velocity.\\
-
-We can further illustrate this point by having one photon be emitted
-in the center of the rotating cloud into the plane of the equator, and
-another in the direction of the pole. Let both photons travel $\tau=1$
-(at line center), and then scatter by 90 degrees, preserve its
-frequency in the frame of the atom, and then again travel $tau=1$. In
-both cases, the photon travels the same distance. In the LAB-frame,
-both photons will have different frequencies, but not in the frame of
-the gas.\\
-
-The situation described above is clearly unique to solid-body
-rotation. It does not apply to non-solid body rotation, which we
-intend to study in upcoming work. We think our own + the referees
-confusion only emphasizes that even this `simplified' problem of
-solid-body rotation is highly non-trivial. We have attempted to
-clarify this further in \S 3.X
-
-\subsection*{Angular variation of the distribution of escaping directions}
-
-{\bf It seems to me that Ly$\alpha$ photons escape a medium through
-  the path of minimum optical depth. So, in a rotating cloud, where
-  the velocity field is tangential, they might “rotate” or spiral from
-  the center to the edge. To test this idea, you could look at the
-  distribution of escaping directions from photons emerging at the
-  pole or at the equator. But for this, you need to keep track of the
-  location of escape, and not only of the direction of escape. Did you
-  collect this information ?
-
-I would expect that photons at the equator escape more tangentially to
-the sphere than at the poles... But again, Ly$\alpha$ transfer is not
-exactly intuitiv.}
-
-We have looked into this. We selected two different sets of
-photons. The first one escapes through the north pole and the second
-around the equator in a region with $0<\varphi<90$. For each set we
-compute the dot product $\mu\equiv\hat{k}_{out}\cdot\hat{r}_{out}$,
-where $\hat{r}_{out}$ is the unit vector in the radial direction for
-each photon. We plot the distributions for $\mu$ for two different
-$\tau_H$. In each plot we find that the two distributions (equator and
-pole) are virtually the same:
-
-\begin{center}
-\includegraphics[width=0.6\textwidth]{./surface_mu_tau5_diff_pos.png}
-\includegraphics[width=0.6\textwidth]{./surface_mu_tau7_diff_pos.png}
-\end{center}
-
-The distribution is also insensitive to the rotational velocity:
-
-\begin{center}
-\includegraphics[width=0.6\textwidth]{./surface_mu_t5_diff_v.png}
-\end{center}
-
-The only trend can be found for different optical depths:
-
-\begin{center}
-\includegraphics[width=0.6\textwidth]{./surface_mu_diff_tau.png}
-\end{center}
-
-\section*{Details}
-
-\subsection*{Sect. 3.1}
-
-{\bf You say that “If the viewing angle is aligned with the rotation
-  axis, $|\mu| \approx 1$, the Ly$\alpha$ line keeps in most of the
-  cases a double peak”, isn’t it in all cases ?}
-
-\subsection*{Sect. 3.5}
-{\bf The parameter a is not defined when you discuss Neufeld.}
-
-\subsection*{Fig9}
-
-{\bf Is Fig 9, left panel, for a central source ? Can you show the
-  homogeneous case also ? You discuss in the referee repport that the
-  distribution is not bimodal anymore. But it has to be different than
-  in central case, spanning the whole range of nb scatt, because
-  photons are emitted at every radii in the cloud, so at every optical
-  depth. On the right panel, solid and dashed lines are not defined.}
-
-\subsection*{Vmax = 1000 km/s}
-{\bf If you did this test and checked that the nb of scatterings and
-  the escape fraction is still angle invariant for such a high
-  velocity, then it is worth mentionning it. Because in principle,
-  media with very high velocities should start to become transparent
-  for Ly$\alpha$.}
-
-For solid body rotation, the results should not depend on $v_{\rm
-  max}$ at all. We have even done calculations with $v_{\rm max}=10^6$
-km/s, and confirmed this result.
+We have included these plots in the appendix and extended the
+discussion in the direction suggested by the referee.
 

### 2014-09-09 code/Finding_histograms_with_viewing_angle.py
minor bug

@@ -50,13 +50,13 @@ def viewing_angle(filename, angle, nbins, distribution):
     hist07, bins07 = np.histogram(x07, bins=nbins, normed=True)
     hist08, bins08 = np.histogram(x08, bins=nbins, normed=True)
     hist09, bins09 = np.histogram(x09, bins=nbins, normed=True)
+    hist10, bins10 = np.histogram(x10, bins=nbins, normed=True)
 
     if angle == 1:
-        for i in range(len(hist)):
-		print hist01[i], bins01[i]
+        return hist01, bins01 
 
     if angle == 2:
-        return hist02, bins02
+         return hist02, bins02
 
     if angle == 3:
         return hist03, bins03
@@ -81,6 +81,22 @@ def viewing_angle(filename, angle, nbins, distribution):
 
     if angle == 10:
         return hist10, bins10
+    """ 
+    plt.plot(bins01[:-1], hist01, c='k', linewidth=2.5) 
+    plt.plot(bins02[:-1], hist02, c='k', linewidth=2.5)
+    plt.plot(bins03[:-1], hist03, c='k', linewidth=2.5)
+    plt.plot(bins04[:-1], hist04, c='k', linewidth=2.5)
+    plt.plot(bins05[:-1], hist05, c='k', linewidth=2.5)
+    plt.plot(bins06[:-1], hist06, c='k', linewidth=2.5)
+    plt.plot(bins07[:-1], hist07, c='k', linewidth=2.5)
+    plt.plot(bins08[:-1], hist08, c='k', linewidth=2.5)
+    plt.plot(bins09[:-1], hist09, c='k', linewidth=2.5)
+    """
+    #lt.plot(bins03[:-1], hist03, c='k', linewidth=2.5)
+    
+    #plt.xlabel("$x$", fontsize=30)    
+    #plt.savefig(filename+str(angle)+".png")
+ 
 
 filename = sys.argv[1]
 angle = float(sys.argv[2])
@@ -88,8 +104,16 @@ bins = float(sys.argv[3])
 mode = float(sys.argv[4])
 distribution = float(sys.argv[5])
 
-viewing_angle(filename, angle, bins, distribution)
+hist, bins = viewing_angle(filename, angle, bins, distribution)
 
+for i in range(len(hist)):
+	print hist[i], bins[i]
 
-
+##
[…]

### 2014-09-10 paper/ms.tex
updated paper with referee comments
Marks comment on the abstract

@@
 allows us to derive an analytic approximation for the viewing-angle
-and rotational velocity of the emerging spectrum.
+dependence of the emerging spectrum, as a function of rotational velocity.
 \end{abstract}
@@
   ($|\mu|\sim 0$). The continuous (dashed) line represents the central
-  (homogeneous) source distributions.  The panels follow the same
+  (homogeneous) source distributions. The continuous thin line
+represents the intrinsic homogeneous spectrum. The panels follow the same
   distribution as in Fig.s \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
     \label{fig:differentvelocities}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.95\textwidth]{f4-2.pdf}
+\end{center}
+\caption{Shape of the \ly line for different maximum rotational
+  velocities for a LoS perpendicular to the rotation axis
+  ($|\mu|\sim 1$). The continuous (dashed) line represents the central
+  (homogeneous) source distributions.  The continuous thin line
+represent the intrinsic homogeneous spectrum. The panels follow the same
+  distribution as in Fig.s \ref{fig:CentralSpec} and \ref{fig:HomSpec}.
+    \label{fig:differentvelocities2}}
 \end{figure*}

### 2014-09-10 paper/referee-reply.tex
new referee reply

@@
 
+{\bf The color bar in Fig 2 and 3 has no units. Indeed, there is only a factor of $2$ in “flux” between a
+red and a green pixel, so the broadening of the line compensates the change in color with $\theta$. I still
+believe that you should comment on this in the text, because the visual impression is really that
+there are less photons escaping along the equator than along the rotational axis. Especially when
+you look at the top right panel.}\\
+
+Thank you very for notest this, we put the right units and also we comment on that in the text.\\
+
+{\bf could you add the intrinsic spectra for uniform sources on Fig4 ? And maybe add a fig5 which
+would be the same as Fig4, but for $\theta = 0$? To illustrate the 2 extreme cases.}\\
+
+About Fig 4. we add the intrinsic spectra, and we add an aditional figure showing the case $\theta=0$ to illustrate the 2 extremes
+cases. When we add the intrinsic spectra we cut the plot to the heigh of the rotation spectra because the intrinsic spetra is to high 
+and the details of the rotation spectra can not be apreciated.\\
+
 {\bf About the directionallity of the escaping photons, why did you select only photons with $0 < \varphi < \pi/2$?
@@
 It seems that the regimes that you investigated are not yet enough optically thick so that $I(\mu) = \propto \mu$.
-Maybe you can show these plots on the appendix, to illustrate that the analytic solution becomes better in veryoptically thick regimes.}
+Maybe you can show these plots on the appendix, to illustrate that the analytic solution becomes better in veryoptically thick regimes.}\\
 

### 2014-09-10 paper/referee-reply.tex
Minor changes

@@
 
-Thank you very for notest this, we put the right units and also we comment on that in the text.\\
+Thank you very for noticing this. We have put the right units and also we have added a comment in the text.\\
 
@@
 
-About Fig 4. we add the intrinsic spectra, and we add an aditional figure showing the case $\theta=0$ to illustrate the 2 extremes
-cases. When we add the intrinsic spectra we cut the plot to the heigh of the rotation spectra because the intrinsic spetra is to high 
-and the details of the rotation spectra can not be apreciated.\\
+We have followed your advice and modified figure 4 and 5 accordingly.\\
 
@@
 We did not limit the selection to $0 < \varphi < \pi/2$. The outgoing
-photons close to the surface follow are in that range, where $\varphi$
+photons close to the surface are in that range, where $\varphi$
 describes the angle with respect to the normal to the surface.  The
-curves have the same normalization in each of the plots.
+curves have the same normalization in each plot.
 

### 2014-09-10 paper/ms.tex
paper updtaed
Minor changes
minor update caption fig 10

@@
 We have verified that the solutions are indeed symmetric with respect
-to $\mu=0$.
+to $\mu=0$. We have also verified that the total flux is the same for all $\mu$.
 
@@
 \end{center}
-\caption{Logarithm of the average number of scatterings as function of
-  $\mu$ (left) and the maximum rotational velocity $V_{\rm
+\caption{2D histogram of the logarithm of the average number of scatterings as function of $\mu$ (left) and the maximum rotational velocity $V_{\rm
 max}$ (right). The left panel shows the behaviour for $\tau=10^{5}$ and
-  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$. In the
+  $V_{max}=300$\kms as a function of $\left|\cos\theta\right|$, the color indicates the number of photons per bin. In the
   right panel the continous (dashed) lines represent the results for

### 2014-09-10 paper/ms.tex

@@
 \caption[]{Distribution of the cosine of the angle between the
-  propagation direction and the sphere's surface. The distributions
-  have been normalized to unity. Left panel: different rotational
-  velocities; middle panel: different viewing angles; right panel:
-  different optical depths. Only the optical depth has an effect on
-  the outogoing directions. This is consistent with the assumption
-  that \lya scattering in a medium with solid body rotation proceeds as in
-  a static medium.}
+  propagation direction and a vector normal to the sphere's
+  surface. The distributions have been normalized to unity. Left
+  panel: different rotational velocities; middle panel: different
+  viewing angles; right panel: different optical depths. Only the
+  optical depth has an effect on the distribution of outogoing
+  directions. This is consistent with the assumption that \lya
+  scattering in a medium with solid body rotation proceeds as in a
+  static medium.} 
 \label{fig:surface}

### 2014-09-30 paper/ms.tex
solved q1, q2, q3

@@
 A more detailed quantitative description of the \ly line has been
-reached through Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. 
+reached through Monte Carlo (MC) simulations \citep{Auer68,Avery68,Adams72}. 
 In the last two decades these studies have become popular due to the
@@
 
-This is clear in  Fig. \ref{fig:differentvelocities} where we
-present the different line morphologies for $|\mu|\sim 0$ in the
+This is clear in  Fig. \ref{fig:differentvelocities} and in Fig. 
+\ref{fig:differentvelocities2} where we
+present the different line morphologies for $|\mu|\sim 0$ and 
+$|\mu|\sim 1 $ for the
 homogeneous and central configurations.  
@@
 particular it is relevant to consider the joint effect of rotation the
-and ubiquitous outflows (Remolina-Gutierrez et al., in prep.)
+and ubiquitous outflows (M.C. Remolina-Gutierrez et al., in prep.)
 because rotation can lead to enhanced escape of \ly at line center, which
